### 2014-06-20 notes-snrs/snr_notes.tex
Init commit (ignored raw/repro Chandra data)

\documentclass[10pt]{article}

\usepackage[margin=1in, letterpaper]{geometry}
\usepackage{parskip}

\usepackage{amsthm, amsmath, amssymb}
% \usepackage{gensymb}  % For use of degree symbol
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}

\usepackage{enumerate} % For use of (a), (b), et cetera
\usepackage{booktabs} % Tables
\usepackage[margin=10pt, labelfont=bf, labelsep=period,
justification=justified]{caption} % Captions in figure floats

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = blue,
	pdfauthor = {Aaron Tran},
	pdfkeywords = {x-ray, SNR, notes},
	pdftitle = {Supernova remnants and stuff - \today},
%	pdfsubject = {},
	pdfpagemode = UseNone
}

% Don't indent paragraphs
\setlength\parindent{0em}

% ===============
% Useful commands
% ===============
\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\; \mt{#1}} % vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % tex.stackexchange.com/q/55701

\newcommand{\Chandra}{\textit{Chandra}}

\begin{document}

\begin{center}
    \Large{Some notes on SNRs}

    \normalsize
    Aaron Tran \\
    \today \\
\end{center}

These notes are assembled for my own self-edification, to learn about (1) X-ray
astronomy, both physics and observational pipeline, (2) supernovae and their
remnants, and (3) Tycho's SNR, and the physics relevant to my summer project.
Information comes from the literature, \Chandra\ info from the CXC, various
textbooks, and discussions with my mentors Brian Williams and Rob Petre.
Information may easily be wrong and I make no claims to accuracy/quality,
though I will aim to cite sources where possible.

This is a summer 2014 internship project under the auspices of GSFC and CRESST.
Mentors are Dr. Robert Petre and Dr. Brian J. Williams.

% =========
% Logistics
% =========
\section{GSFC logistics}

Notes from 1st meeting, Tues May 27.

Some things to attend.  July X-ray meeting to be moved.
\begin{itemize}
    \item 662 meeting -- 1st Friday of every month, 10:30am, Rm W120
    \item Coffee (just socializing) -- Weds 10am
    \item ASD colloquium -- Tues 3:45p (3:30p meet speaker), Rm W150
    \item GSFC colloquium -- Fri 3:30p, Bldg 3, Goett Auditorium
\end{itemize}

% ============
% Introduction
% ============
\section{Introduction}

A little bit about the project.  Builds on Ressler et al. (ApJ, in press).
Goal is to obtain FWHM of Tycho filaments.

If there is time, we will proceed to try perhaps Kepler, even Cas A (both are
quite a mess).  SN 1006 was HARDER than Tycho, really... so this is supposed to
be fairly straightforward!

% ===============
% X-ray astronomy
% ===============
\section{X-ray astronomy}

First, where are X-rays on the EM spectrum?  X-rays generally have energies
from $0.1$ to $100 \unit{keV}$.  They are divided into \emph{soft} and
\emph{hard} X-rays, where the division is at a few ($1$--$10$) keV.  Beyond
$\abt 100 \unit{keV}$ we move into gamma rays; below $\abt 0.1 \unit{keV}$ we
move back into ultraviolet.

Next, what emits X-rays?  What processes are probed?
X-ray emitting temperatures are about $10^6$ to $10^7$ K.
% TODO fill this in

Finally, what instruments conduct X-ray astronomy? The big ones are \Chandra,
\emph{XMM-Newton}, and \emph{Suzaku} (older ones incl. Einstein, ASCA, ROSAT).
Swift does have X-ray capability, but is designed for GRB detection; its X-ray,
UV, and optical imaging are for GRB afterglows.  It is also handy for transient
detection (e.g., if a nearby SN goes off...).  K. Dyer has put together a nice
\href{http://www.aoc.nrao.edu/~kdyer/useful/sat.html}
{table of past/present x-ray satellites}.

Nearby, NuSTAR is covering hard X-rays ($10$ to $100\unit{keV}$).  Fermi is
very far away, at $20\unit{MeV}$ to $\abt 50\unit{GeV}$.  In UV, the optical
astronomers kind of cover the near UV (e.g., HST).  GALEX, FUSE, EVUE also have
been flown but seem to be done?  Low end of extreme UV is $\abt 0.1\unit{keV}$.

Apparently, the tie between radio and X-ray observations is due to the imaging
of \emph{synchrotron radiation}?  So we can probe very energetic processes in
both bands.

% ---------
% Radiation
% ---------
\subsection{Radiative processes}

Synchrotron radiation, thermal (line) emission, etc.
% TODO study this

% =======
% Chandra
% =======
\section{\Chandra\ observations}

Our SNR observations are generally made with ACIS-I (occasionally ACIS-S).
ACIS has energy range about $0.7$ to $8 \unit{keV}$, see Figure \ref{fig:area}.
The suffixes (I,S) refer to the CCD array configuration, square for I and lined
up for S. No grating is used. Gratings would be used for spectroscopy --
perhaps HETG with ACIS-S (up to 1000 bins from $0.4$ to $10 \unit{keV}$).

How does ACIS work?  It's a CCD that enables photon counting, basically.
As Rob as noted, we get four pieces of information: time, energy, polarization,
and location on the sky.  We don't really care about time/polarization here
(since we are neglecting, or correcting for, proper motion).

The spectral resolution is frequency dependent (of course), but also \emph{row
number} dependent (i.e., depends on where on the CCD you strike).  The FWHM
resolution is around $100$--$300 \unit{keV}$, with decreasing resolution at
higher energy (FWHM scales as sqrt of energy); this assumes that a charge
transfer inefficiency correction is applied in CIAO.
Spectral resolution depends on how well we can measure the
energy deposited (in the form of mobilized charges, electron-hole pairs) by
each photon.  Apparently, the front-illuminated (FI) CCDs were damaged because
they were previously left in the focal plane during radiation belt passages.
So now they move it each time, which has minimized the damage!

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\textwidth]{fig_chandra_area.png}
    \caption{On-axis effective areas for \Chandra\ instruments, predicted for
    Cycle 16 observations (2015?). Plot is for an integrated point source (?).
    Modified from \Chandra\ Cycle 16 POG, Figure 1.3.}
    \label{fig:area}
\end{figure}

Observations are broken into exposure chunks of $\abt10$ to $180 \unit{ksec}$,
limited by radiation belts and thermal considerations.

Information about specific observation runs are on \Chandra\
\href{http://cda.harvard.edu/chaser/}{WebChaSeR}
(simply search `Tycho' or `SN 1006').  Here you can get raw data, which can be
processed with CIAO and CALDB.
Information about the ACIS instrument is in
\href{http://cxc.harvard.edu/proposer/POG/html/chap6.html}{Chapter 6} of the
\href{http://cxc.harvard.edu/proposer/POG/html/index.html}{proposer's guide}.

% =================
% Supernova physics
% =================
\section{Supernova physics}
Velocities of forward
shock in supernovae are about $10^4$ km/s.  Very fast, very energetic.

About the ISM:
\href{notes}{http://ay201b.wordpress.com/2011/04/12/course-notes/}

% ===========
% Tycho's SNR
% ===========
\section{Tycho's SNR (SN 1572)}

Hayato et al., ApJ 2010, estimate
1. expansion velocity $\abt 4000$ to $5000 \unit{km/s}$, depending on which
spectral line you're looking at (Si, S, Ar faster than Fe K$\alpha$).
2. subsequently estimate Tycho's SNR to be $\abt 4 \unit{kpc}$ away from Earth

(I think this is still faster than usual ISM sound speed???)

For comparison, Sgr A* is $>8\unit{kpc}$ from Earth; the Milky Way is $\abt 34
\unit{kpc}$ across.  Andromeda is $\abt 780 \unit{kpc}$ away from us. (all this
from Wikipedia... just to give a sense of scale.  Our closest star (Proxima
Centauri) is about 1 parsec away.

Aliases: G120.1+1.4 Tycho, 3C10, SN1572
Bibliography on Tycho, up to 2009:
\href{Green's SNR catalogue}
{http://www.mrao.cam.ac.uk/surveys/snrs/snrs.G120.1+1.4.html}
Also more papers (up to 2014) \href{here}
{http://www.physics.umanitoba.ca/snr/SNRcat/SNRrecord.php?id=G120.1p01.4}

Acciari et al. 2011 ApJL, find TeV gamma rays in a smush, around the SNR
BEAUTIFUL picture of a CO cloud possibly interacting, and the gamma ray
emissions is offset as well.  Short, sweet paper.

Giordano et al. 2012 ApJ, Fermi LAT observation of Tycho.
Describe emission as due to pion decays from cosmic-ray acceleration into ISM.
\href{iop}{http://iopscience.iop.org/2041-8205/744/1/L2/}

B field amplification (2004)
\href{arxiv}{http://arxiv.org/pdf/astro-ph/0409453v2.pdf}
(Tycho and similar)
Nonthermal filaments study (2005)
\href{iop}{http://iopscience.iop.org/0004-637X/621/2/793/pdf/0004-637X\_621\_2\_793.pdf}

\subsection{SN 1006}

%\begin{table}[t]
%\centering
%\caption{Comparison of predicted and observed frequency aliasing.
%Predicted uncertainties are estimated from maximum observed fluctuation in
%oscilloscope measurements of signal period; we are unable to estimate and
%include error in sampling frequency.
%Observed uncertainty is set to frequency resolution $\sim 10 \unit{kHZ}$, set
%by discrete Fourier transform (number of samples and sample rate).}
%\begin{tabular}{@{}rrr@{}}
%    \toprule
%    & \multicolumn{2}{c}{$f_{\mt{aliased}} \unit{(MHz)}$} \\
%    \cmidrule(l){2-3}
%    $f_{\mt{sig}} \unit{(MHz)}$ & predicted & observed \\
%    \midrule
%    0.88 & $0.88 \pm 0.003$ & $0.87 \pm 0.01$ \\
%    3.52 & $3.52 \pm 0.02$ & $3.52 \pm 0.01$ \\
%    6.16 & $3.84 \pm 0.08$ & $3.83 \pm 0.01$ \\
%    7.92 & $2.08 \pm 0.04$ & $2.09 \pm 0.01$ \\
%    8.80 & $1.20 \pm 0.03$ & $1.21 \pm 0.01$ \\
%    26.4 & $3.60 \pm 0.3$ & $3.61 \pm 0.01$ \\
%    \bottomrule
%\end{tabular}
%\end{table}

\end{document}

### 2014-06-20 code/ciaoreg2spec.py

@@ -1,0 +1,56 @@
+"""
+Script to generate spectra for CIAOREG region file
+Aaron Tran
+June 12, 2014
+
+Currently: you MUST initialize CIAO before running this script!
+"""
+
+import argparse
+from ciao_contrib.runtool import *
+
+def main():
+    """ Blah"""
+    parser = argparse.ArgumentParser(description=
+             'Generate individual spectra for regions in a CIAO region file.')
+    parser.add_argument('ciaoreg', help='CIAO region file for specextract
+                        stack')
+    parser.add_argument('obsid_dir', help='Chandra ObsID directory (with repro/
+                        from chandra_repro')
+    parser.add_argument('outroot', help='Stem of output spectra')
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='verbose mode')
+
+    args = parser.parse_args()
+    cr, obsdir, outroot = args.ciaoreg, args.obsid_dir, args.outroot
+    verbose = args.verbose
+
+    print 'Face it this is low priority for now.'
+    print 'This is merely a wrapper for ciao\'s own functionality'
+    print 'The next script down the line is important, however'
+
+    ## Run the first time only, then don't reset
+    # Set bad pixel file, evt2 file, default specextract parameters
+    # TESTING WHETHER WE NEED THIS, IF WE SPECIFY
+    # EVT FILE IN SPECEXTRACT
+    # Nope.  Just punlearn ardlib first and you're good!!!
+    punlearn ardlib
+    punlearn specextract
+    acis_set_ardlib acisf10095_repro_bpix1.fits verbose=1 absolutepath=yes
+    pset specextract verbose=2
+
+    # These are all set correctly by default, but just in case...
+    pset specextract weight=yes
+    pset specextract weightrmf=no
+    pset specextract combine=no
+    pset specextract bkgresp=yes
+
+    $evt2 = "acisf10095_repro_evt2.fits"
+
+    pset specextract infile="$evt2[sky=@profiles_good_cutback.ciaoreg]"
+    pset specextract outroot="spectra/region-n"
+    specextract mode=h  # Do not prompt
+
+
+if __name__ == '__main__':
+    main()

### 2014-06-20 code/ds9projplotter.py

@@ -1,0 +1,173 @@
+"""
+Plot intensity profiles from a three band image (you pick the bands)
+by parsing a ds9 region file with projection-type regions.
+Also saves profile data if so desired
+
+Relies on pyds9 to extract 2D projection plots.
+This will probably be replaced with a better program/approach, since
+1. ds9's projection is a bit of a blackbox
+2. code is rather slow since it has to plot data, write/read data every time
+   (I couldn't find a way to just get numbers/values from plots directly)
+but, it does work.
+
+Fig. 7 of Ressler et al. [ApJ, in review/press?] illustrates what we're doing
+
+pyds9 documentation: http://hea-www.harvard.edu/RD/pyds9/
+DS9 XPA reference: http://ds9.si.edu/ref/xpa.html
+
+Aaron Tran
+June 12, 2014
+(last modified June 17, 2014)
+"""
+
+import argparse
+import matplotlib.pyplot as plt
+import numpy as np
+import os
+
+from fplot import fplot, show_mplrc_settings
+import ds9
+
+
+def main():
+    """Run from command line as, e.g.,
+    python ds9projplotter.py -v '../data/profiles_all.reg' '../plots/plt'
+    """
+    parser = argparse.ArgumentParser(description=
+             'Plot profiles from DS9 region files with projections')
+
+    parser.add_argument('infile', help='Input DS9 region file (fk5 coords)')
+    parser.add_argument('outroot', help='Stem of output plots')
+    # RGB files for profiles
+    parser.add_argument('-r', '--red', help='red band FITS file',
+        default='../data/0.7-1kev_mosaic_unbin.fits')
+    parser.add_argument('-g', '--green', help='green band FITS file',
+        default='../data/1-2kev_mosaic_unbin.fits')
+    parser.add_argument('-b', '--blue', help='blue band FITS file',
+        default='../data/2-7kev_mosaic_unbin.fits')
+    # Labels for legends
+    parser.add_argument('--rlabel', help='red band label',
+        default='0.7-1 keV')
+    parser.add_argument('--glabel', help='green band label',
+        default='1-2 keV')
+    parser.add_argument('--blabel', help='blue band label',
+        default='2-7 keV')
+    # Additional flags
+    parser.add_argument('-d', '--data',
+                        help='Save projection data to directory stem')
+    parser.add_argument('-v', '--verbose', action='store_true',
[…]

### 2014-06-20 code/spec_fitplot.py

@@ -1,0 +1,156 @@
+"""
+Perform phabs*powerlaw XSPEC fit to spectra and output
+plots and fit parameters
+Aaron Tran
+2014 June 17
+(last modified: 2014 June 17)
+
+Initialize HEASOFT (`heainit`) before running this script!
+Run script with 32-bit python (use `arch -i386 python ...`)
+Run script from directory of actual spectra (so that XSPEC can resolve relative
+links to response and background files.
+"""
+
+import argparse
+import os
+import re
+
+import xspec as xs
+
+def main():
+    """Main method"""
+    # argparse boilerplate
+    parser = argparse.ArgumentParser(description=
+             'Apply XSPEC model fits and make plots for set of spectra')
+    parser.add_argument('specroot', help='Directory stem for spectra')
+    parser.add_argument('plotroot', help='Output stem for plots')
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='verbose mode')
+
+    args = parser.parse_args()
+    specroot, pltroot = args.specroot, args.plotroot
+    verbose = args.verbose
+
+    # Get number of spectra to update (count grouped spectrum files)
+    n = get_nspec(specroot)
+    if verbose:
+        print '\n{} spectra to process'.format(n)
+
+    # Check plot output directory, create if needed
+    check_dir(pltroot)
+
+    # Set up XSPEC
+    init_xspec(verbose)
+
+    # Process spectra one by one
+    for num in xrange(n):
+        # Create paths, with assumptions about filename structure
+        # Check that grouped spectrum exists
+        grp_path = '{}_src{:d}_grp.pi'.format(specroot, num+1)
+        plt_path = '{}_src{:d}_grp.ps'.format(pltroot, num+1)
+        log_path = grp_path[:-3] + '.fitlog'
+        if not os.path.isfile(grp_path):
+            print 'Bad path: {}'.format(grp_path)
+            raise Exception('ERROR: file does not exist!')
+        if verbose:
+            print '\nProcessing file: {}'.format(grp_path)
+            print 'Output plot: {}'.format(plt_path)
+
+        process_spectrum_file(grp_path, plt_path, log_path)
+
+    if verbose:
+        print '\nDone!'
+
+
+# ========================
+# Methods to control XSPEC
+# ========================
+
[…]

### 2014-06-20 code/spec_linkbg.py

@@ -1,0 +1,196 @@
+"""
+Script to link region spectra with nearest backgrounds
+Aaron Tran
+June 12, 2014
+(last modified: June 16, 2014)
+
+Initialize CIAO before running this script!
+"""
+
+import argparse
+import os
+import re
+
+from ciao_contrib.runtool import dmhedit, dmhistory
+
+def main():
+    """Parse user input and update spectra background links
+    KEY ASSUMPTION: numbering of region, background spectra
+    MUST match numbering/ordering of region, background CIAOREG files
+    """
+    parser = argparse.ArgumentParser(description=
+             ('Link spectra to closest background spectra (modifies FITS '
+             'header keywords). Example usage: '
+             'python spec_linkbg.py -v ../data/profiles_good_2.ciaoreg '
+             '../data/profiles_bg.ciaoreg ../data/spectra/good-2/reg '
+             '../data/spectra/bkg/bkg'))
+
+    parser.add_argument('regfile', help='CIAO region file for spectra to link')
+    parser.add_argument('bkgfile', help='CIAO region file for backgrounds')
+    parser.add_argument('regroot', help='Directory stem for region spectra')
+    parser.add_argument('bkgroot', help='Directory stem for bkg spectra')
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='verbose mode')
+
+    args = parser.parse_args()
+    regfile, bkgfile = args.regfile, args.bkgfile
+    regroot, bkgroot = args.regroot, args.bkgroot
+    verbose = args.verbose
+    
+    if verbose:
+        print 'Regions and backgrounds from files:'
+        print ' Regions: {}'.format(os.path.abspath(regfile))
+        print ' Backgrounds: {}'.format(os.path.abspath(bkgfile))
+        print '\nLinking spectra with filename roots:'
+        print ' Regions: {}'.format(os.path.abspath(regroot))
+        print ' Backgrounds: {}'.format(os.path.abspath(bkgroot))
+
+    # CIAO numbering starts at 1, not 0, hence the key numbering...
+    # Centers, used as keys, should be unique.  But, if not unique,
+    # then doesn't mtter which number is used
+    if verbose:
+        print '\nParsing center coordinates'
+    reg_ctrs = get_centers(regfile, verbose)
[…]

### 2014-06-20 data/ds9-tycho-rgb.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+echo "Region file to load?"
+read reg
+
+ds9 -view layout vertical \
+    -colorbar orientation vertical \
+    -rgb \
+    -red 0.7-1kev_mosaic.fits \
+        -scale limits 4e-8 2.1e-6 \
+    -green 1-2kev_mosaic.fits \
+        -scale limits 4e-8 2.42e-6 \
+    -blue 2-7kev_mosaic.fits \
+        -scale limits 3e-8 1.5e-6 \
+    -rgb lock scale yes \
+    -histequ \
+    -regions $reg

### 2014-07-17 model-guide/model-code-guide.tex
Debugged model code works?, save multipanel plots
Debug intensity profile computation in Sean's model code.
Remove unused code, move code for better flow, add comments.
Save circulated version of multipanel plots (with last tweaks to
various plots).  First draft of guide to model physics and code
implementation.

\documentclass[10pt]{article}

\usepackage[margin=1in, letterpaper]{geometry}
\usepackage{parskip}

\usepackage{amsthm, amsmath, amssymb}
% \usepackage{gensymb}  % For use of degree symbol
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}

\usepackage{enumerate} % For use of (a), (b), et cetera
\usepackage{booktabs} % Tables
\usepackage[margin=20pt, labelfont=bf, labelsep=period,
justification=justified]{caption} % Captions in figure floats

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = blue,
	pdfauthor = {Aaron Tran},
	pdfkeywords = {x-ray, SNR, notes},
	pdftitle = {Supernova remnants and stuff - \today},
%	pdfsubject = {},
	pdfpagemode = UseNone
}

% Don't indent paragraphs
\setlength\parindent{0em}

% ===============
% Useful commands
% ===============
\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\; \mt{#1}} % vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % tex.stackexchange.com/q/55701
\newcommand{\del}{\nabla}
\newcommand{\ptl}{\partial} % Laziness

\newcommand{\Chandra}{\textit{Chandra}}

% ===============
% Document proper
% ===============
\begin{document}

\begin{center}
    \Large{Brief review of SNR filament models of Ressler et al.}

    \normalsize{Aaron Tran}\\
    \today \\
\end{center}

% ============
% Introduction
% ============
\section{Introduction}

\subsection{Thin synchrotron rim physics}

Accelerating ISM/CSM particles in the forward shocks of supernovae emit
synchrotron radiation.  Emission is strong in the shock's immediate wake, but
dies off quickly downstream as particles radiate and lose energy. The radiation
from a spherical blast wave, then, is shell-like with bright X-ray and radio
rims/filaments due to line-of-sight projection.  These filaments have finite
and energy-dependent widths, set by:
\begin{itemize}
  \item \emph{synchrotron losses}.  At the shock, high energy electrons
  efficiently radiate harder x-ray photons.  As electrons are advected
  downstream while radiating, they radiate at lower energies and lose energy
  more slowly.  Synchrotron losses depend on (1) the initial electron energy
  distribution, and (2) the gradual decrease of electron energies downstream of
  the shock.
  \item \emph{diffusion}.  Random motion with respect to bulk plasma advection.
  Higher energy electrons diffuse and travel further downstream than would be
  expected from pure advection; hence, higher energy radiation may be seen
  farther downstream of the shock than expected.
  Higher energy particles may also diffuse \emph{ahead} of the shock, possibly
  giving rise to a so-called ``cosmic-ray shock precursor''.  Note that this is
  distinct from radiative precursors (e.g., Ghavamian et al., 2000).
\end{itemize}

\begin{figure}[!ht]
  \centering
  \includegraphics[scale=0.3]{doodle.jpg}
  \caption{Crude doodle of particle acceleration at a shock.
  The shock propagates into a thin, low density ISM and bounces particles
  around like crazy.  Higher energy particles diffuse randomly both behind
  and ahead of the shock.  Lower energy particles are advected \emph{backwards}
  in a reference frame co-moving with the shock. Bulk velocity, pressure, and
  density ramp down behind the shock following the Sedov-Taylor solution (?).}
  \label{fig:shock}
\end{figure}

Synchrotron losses and particle diffusion are in turn both controlled by
(1) the injected electron spectrum, and (2) the amplified magnetic field.
The amplified magnetic field may be constant, or vary in space -- e.g.
magnetic damping predicts a rapid fall off of amplification behind the shock.
Diffusion is also controlled by the nature of turbulence in the shocked plasma,
quantified by a turbulent energy/wavenumber spectrum or similar.

Synchrotron losses cause the rims to \emph{thin} with increasing energy, with
higher energy emission closer to the shock front; the characteristic length
scale falls off with radiation frequency as $l \propto \nu^{-1/2}$.  Diffusion
weakens this energy dependence, as the rims smear out more at higher energies.

\subsection{What can be said}

The width-energy dependence of synchrotron rims, and their absolute widths,
is determined by the ambient conditions (magnetic field amplification, plasma
turbulence) that control particle acceleration and diffusion.  By measuring the
energy scaling, we deduce properties of particle diffusion; by measuring the
absolute widths, we deduce information about magnetic field strength
and diffusion in some combination of parameters.

Sean considers several models that simultaneously constrain magnetic fields and
particle diffusion parameters from width measurements of these thin filaments.
The key measurables are:
\begin{itemize}
  \item magnetic field strength $B_0$ (and damping parameters, if relevant)
  \item diffusion coefficient constant $\eta_2$
  \item diffusion scaling $\mu$ (set by turbulent energy spectrum).
\end{itemize}

Here I retrace and explain relevant equations and fitting procedures from
Sean's paper; table, figure, and equation references are from the version of
record at \href{http://dx.doi.org/10.1088/0004-637X/790/2/85}
{doi:10.1088/0004-637X/790/2/85}.

% ============================
% Synchrotron rim width models
% ============================
\section{Filament width models -- theory}

Filament widths are determined by electron transport downstream of the forward
shock.  The 1-D transport equation for electron distribution $f(E,x)$
(where $E$ is electron energy, $x$ is radial coordinate) is:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
where $C$ is an arbitrary sink/source term, $D$ is diffusion coefficient, and
$\vec{v}$ is bulk/advective plasma velocity.  With some simplifications
(1-D flow, neglect time-dependence, compressible flow unimportant,
space-independent diffusion coefficient), we obtain:
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
\]
Here we have neglected two terms: $(2 D / r) (\ptl f /\ptl r)$ and
$f (\del\cdot\vec{v})$. Both terms are negligible provided that rim width
(characteristic lengthscale for $f$) is much smaller than remnant shock radius.

Two models, which both solve this transport equation, are fitted to rim width
measurements in Tables 7 and 8.  The models differ in choice of source/sink
terms ($C$) to describe synchrotron energy losses (in practice, the models
differ substantially in implementation as described further on).

% -------------------------
% Castrophic dump model (6)
% -------------------------
\subsection{Catastrophic dump model}

This model is described by equations (5--11) in Sean's paper, with (being
explicit about energy dependence):
\[
  C = -\frac{f(E,x)}{\tau_{\mt{synch}}(E)}\text{,}
\]
i.e., electrons dump their energy over a synchrotron cooling time and do not
decrease in energy as they are advected.

The model predicts rim widths (equation 6) with an approximate projection
factor $\beta = 4.6$; this implicitly assumes spherical symmetry and the
$\delta$-function approximation for synchrotron emissivity (Ballet, 2006).

References: Parizot et al. (2006), V\"{o}lk et al. (1981), Berezhko and
V\"{o}lk (2004), Ballet (2006).

% -------------------------------------
% continuous loss model (12), (14)-(16)
% -------------------------------------
\subsection{Continuous loss model}

This model is described by equations (12) and (14)-(16) in Sean's paper, with:
\[
  C = K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\]
representing an injected electron spectrum and an energy loss term.  Note that
$b B^2 E^2$ is proportional to synchrotron radiative power (Condon and Ransom,
\href{http://www.cv.nrao.edu/course/astr534/SynchrotronPower.html}{ERA}).

Equation (12) admits an integral form solution for particle distribution
(or, electron energy spectrum) $f(E,x)$ given by equations (14--17).
The single-particle synchrotron emissivity is integrated over the particle
distribution to obtain the full synchrotron emissivity $j_\nu$ of
our electron population (equation 20).  Then the emissivity is integrated over
lines of sight to obtain intensity profiles $I_\nu(r)$ (equation 21).
We obtain model predictions for filament FWHMs from these intensity profiles.

The single-particle synchrotron emissivity is tabulated in Appendix 2 of
Pacholczyk (1970).

References: Berezhko et al. (2003), Berezhko and V\"{o}lk (2004),
Cassam-Chena\"{i} et al. (2007), Morlino et al. (2010), and Rettig and Pohl
(2012).

% ===================
% Abbreviated summary
% ===================
\section{Filament width models -- fitting}

Tables 7, 8 summarize results from the two different models.  The key outputs
are $\eta_2$ and $B_0$ for various values of $\mu$; $\eta_2$ quantifies
diffusion strength while $B_0$ is magnetic field strength.
Sean argued that strong energy-dependence ruled out magnetic damping and did
not present fit results for magnetic damping models in SN 1006.

Why was $\mu$ fixed?  I speculate that it might have been necessary to make
fitting tractable / give useful output (note: \emph{non-linear} fitting with
3 points and 3 unknowns is not necessarily fully determined?).

All equations use the generalized diffusion coefficient $D \propto E^\mu$.

\subsection{Catastrophic dump model}

This is an analytic approximation; please see the relevant assumptions and
approximations above.  Equation (6), multiplied by a projection factor
$\beta=4.6$, is fit directly to measured rim widths as a function of energy.  
The predicted rim width is given by:
\[
  \mt{FWHM} = \frac{2\beta D / v_d}
              {\sqrt{1 + 4D/\left(v_d^2 \tau_{\mt{synch}}\right) } - 1}
\]
Table 7 presents fit results with errors that appear to be taken
from diagonal elements of the covariance matrix (which may not be safe for
non-linear fits -- needs to be checked).

Some remarks:
\begin{itemize}
  \item For Tycho, as we have 4-5 energy bands available, fitting three
  parameters ($\mu$, $\eta_2$, $B_0$) simultaneously may be tractable.
  \item As we fit equation (6) to measurements directly, we don't calculate
  $m_E$ anywhere.  However, the fit results specify $m_E(E)$ as equation (23).
  Equation (23) is only valid for the approximate model of equation (6).
  \item We could convolve the general synchrotron emissivity (equation 20) with
  the exponential electron spectrum $f(E,x)$, as is done for the complex model.
  But, probably not necessary (as this is already just an approximation).
\end{itemize}

The code for this model is given in {\tt{Widthfun.py}}.

\subsection{Continuous loss model}

The solution to equation (12) gives filament intensity profiles and hence FWHMs
to manually fit rim width measurements.  Given input parameters $\mu, \eta_2,
B_0$, FWHMs in each energy band are computed as follows:
\begin{enumerate}
  \item Integrate and solve for $f(E,x)$ using one of equations (14--16).
    Use equation (17) or (24) for the function $z(x)$ in equations (14--16),
    depending on whether you want a loss-limited or magnetically damped model.
    Change variables to make Green's function integrals numerically tractable.
  \item Compute synchrotron emissivity $j_\nu$ by integrating single-particle
    synchrotron emissivity $G(y)$ over particle distribution $f(E,x)$;
    $G(y)$ is tabulated in Pacholczyk (1970) (and interpolated as needed??).
  \item Compute intensity profile $I_\nu(r)$ by integrating emissivity $j_\nu$
    along lines of sight.
  \item Calculate FWHM of intensity profile.
\end{enumerate}
All integrals are evaluated numerically. This is resolution dependent
(discretizing electron energy, radial coordinate, line of sight coordinate),
but it should not matter too much.

Sean's manual fitting procedure computed the FWHM at 2 keV and the exponent
$m_E$ value at 2 keV (calculated from predicted FWHMs at 2 keV and 1 keV).
Per his guide, he chose $\eta_2$ to best fit $m_E$ value, then varied $B_0$ to
fit the FWHM (as $m_E$ is insensitive to $B_0$).  He ignored the FWHM at 0.7
keV for this procedure.  It would be ideal, per Sean's emails, to improve the
code to find best fit values for all FWHMs simultaneously.

The code for this model is given in {\tt{FullEfflength.f}}.  Sean's guide says
there is code for the magnetic damping model, but I'm not sure where it is.  My
guess is that it's buried in the functions for numerically evaluating equations
(14--16), which I have not gone through in detail yet.

\section{Interpretation}

TBD...

% ----------
% Appendix A
% ----------
\section*{Appendix A: clarifying code implementation of various equations}

Mainly for documentation / reference.

\subsection*{Scaled diffusion coefficient $\eta_2$}

The diffusion coefficient is defined as $D(E) = \eta D_B(E_h) (E/E_h)^\mu$
where $E_h$ is an arbitrary fiducial energy.
Let $D(\text{2 keV}) = \eta_2 D_B(\text{2 keV})$ and
define $E_2 = \text{2 keV}$ to obtain:
\[
  \eta D_B(E_h) \left(\frac{E_2}{E_h}\right)^\mu = \eta_2 D_B(E_2)
\]
Therefore:
\[
    \eta = \eta_2 \left(\frac{E_2}{E_h}\right)^{1 - \mu}
\]
This relates our arbitrary pick of $\eta_2$ to characterize the diffusion
coefficient, to the ``true'' value of $\eta$.  Note that $\eta$ is dependent on
fiducial energy $E_h$ while $\eta_2$ is not; they agree for $E_h = E_2$.

Here I clarify some variable definitions in Sean's original code, using
primed letters to refer to simulation variables (as opposed to variables given
in the manuscript).  Both model codes take an input parameter $\eta_2'$ and
internally define $\eta'$ as:
\[
  \eta' = \eta_2' \left( \frac{\nu_2}{c_m B_0} \right)^{(1-\mu)/2}
        = \eta_2' (E_2)^{1-\mu}\text{.}
\]
Here, $\nu_2 = c_m (E_2)^2 B$ is the characteristic synchrotron radiation
frequency.  The diffusion coefficient is subsequently:
\[
  D = \eta' \frac{C_d}{B_0} E^\mu
    = \eta_2' (E_2)^{1-\mu} \frac{C_d}{B_0} E^\mu
    = \eta_2' \frac{C_d E_2}{B_0} \left(\frac{E}{E_2}\right)^\mu
    = \eta_2' D_B\left(E_2\right) \left(\frac{E}{E_2}\right)^\mu\text{.}
\]
Happily, $\eta_2' = \eta_2$, as expected.  But clearly $\eta' \neq \eta$.
The two are related as:
\[
  \eta' = \eta_2 (E_2)^{1-\mu}
        = \eta \left(\frac{E_h}{E_2}\right)^{1 - \mu} (E_2)^{1-\mu}
        = \eta (E_h)^{1-\mu}
\]
and, this is consistent Sean's explanation that the manual fitting searches a
grid in the parameter space of $(B_0, \eta E_h^{1-\mu})$.

I'm not sure I fully understand the rationale behind introducing both $E_h$ and
$\eta_2$ -- e.g., why not simply fix $E_h = \text{2 keV}$, and use $\eta_2$
throughout?  The discussion of the diffusion coefficient (equation 33) hints at
this, but I don't think it's obvious that $\eta$ depends on the choice of
fiducial energy $E_h$ (Sean mentions this as a ``degeneracy'' in the choice of
$\eta$ and $E_h$).

\subsection*{Synchrotron emissivity integration (equation (20))}

Equation (20) is best evaluated as an integral over scaled frequency
$y = \nu / (c_1 E^2 B)$, as Pacholczyk (1970) tabulates the 1-particle
synchrotron emissivity in terms of $y$.  Remember that $E$ here is electron
energy, whereas $\nu$ and $y$ describe radiation energy/frequency.
Change variables as:
\[
    dy = -\frac{2y}{E} dE = -2 y^{3/2} \sqrt{\frac{c_1 B}{\nu}} dE
\]
The integral becomes:
\begin{align*}
    j_\nu(x) &= c_3 B \int_0^\infty G(y) f(x,E) dE \\
             &= c_3 \sqrt{\frac{\nu B}{c_1}}
                \int_0^\infty \frac{1}{2} y^{-3/2} G(y) f(x,E(y)) dy\text{.}
\end{align*}

Some caveats:
\begin{itemize}
    \item I have no idea where $c_3$ and $c_1$ come from.  The value of $c_1$
        is given in Table 2 and (from {\tt fglists.dat}) appears to give the
        ``critical frequency'' $\nu_c = c_1 E^2 B$, which is not the same as
        the primary radiation frequency $\nu_m = c_m E^2 B$ ???
    \item I don't know where the expression for synchrotron emissivity comes
        from (which should explain what the hell $c_3$ is).  I don't know the
        assumptions invoked in Pacholczyk's tabulation of $G(y)$.
    \item See my notes in the modified version of Sean's code -- the
        normalization seems a bit weird / inconsistent, though it could make
        sense.  We're off by a factor of $c_3 / (4 \sqrt{c_1})$.
\end{itemize}

I will follow this up by reading Pacholczyk and Rybicki \& Lightman, which will
hopefully explain some of the notation.

% ----------
% Appendix B
% ----------
\section*{Appendix B: synchrotron power spectrum and parameters}

Here I should double-check all of Sean's provided constants, and
present a derivation of the synchrotron power spectrum (to better understand
what Sean's doing).

\subsection*{Sanity checks on constants}

Need to verify synchrotron constants $b$, $C_d$, $c_m$.  Shock radius and
velocity are different for Tycho (and shock velocity varies with azimuthal
angle for Tycho).  Also, double check the values from Pacholczyk (1970).

\end{document}

### 2014-07-17 code-models/FullEfflength.py

@@ -1,0 +1,74 @@
+"""
+A reimplementation of Sean's model code in Python, for clarity?
+Also just to make sense of the code
+
+Try to introduce more abstraction
+
+Aaron Tran
+2014 July 15
+"""
+
+import lmfit
+import numpy as np
+import scipy as sp
+import scipy.optimize as opt
+
+# Physical parameters
+
+COMP_RATIO = 4.0  # Rankine-Hugoniot
+V0 = 5.0 * 1e8 / compratio  # As measured by Satoru et al., cm/s
+R_S = 2.96e19  # tan(943.7") * 2.2 kpc
+R_S_ARC = 900.0  # R_S in arcseconds from Green's SNR catalog
+ALPHA = 6.0  # Spectral index
+S = 2.0*alpha + 1.0
+
+# Constants
+
+C_M = 1.82e18  # For max synchrotron frequency
+C_1 = 6.27e18  # For synchrotron emissivity
+A = 1.57e-3  # For synchrotron loss time
+NUKEV = 2.417989e17  # 1 keV photon frequency
+
+# Options
+ICUT = 0  # 1 for cut-off, 0 for no cut-off
+IFIT = 1  # 1 for fitting version of code
+IPLOT = 0  # 1 for plotting version of code
+
+# Grid parameters
+IRMAX = 400  # Resolution on intensity profile
+IRADMAX = 100  # Resolution on tabulated electron distribution
+IXMAX = 500  # Resolution along line of sight for integration
+
+
+def main(Bfield, eta2, mu):
+    """BLAH"""
+    eta = eta2 * (2.0*NUKEV / (C_M * Bfield))**(-(mu-1.0)/2.0)
+    # A ton of parameters get set here
+
+    fex = pacholczyk_tab(...)
+
+    for nu in nugraph:
+        disttab = tabulate_e_distr(...)  # 2-D np.array in particle energy, r
+        jnu = emisx(...)  # either a function or a table over radial pos x
+
+def emisx(r, nu, B, emis1, radtab, disttab, imu):
+    """Numerically integrate 1-particle synchrotron emissivity (emis1) over
+    electron distribution to obtain full emissivity j_\nu"""
+    pass
+
+# utilities
+
+def interp(x, xdat, ydat):
+    """Linear interpolation of data at x; xdat MUST be sorted (for speed)"""
+    ind = np.searchsorted(xdat, x)  # xdat[ind-1] < x < xdat[ind]
[…]

### 2014-07-17 code-models/FullEfflength_mod.f

@@ -4,26 +4,14 @@
 ! B0 = magnetic field, eta2 = scaled diffusion coefficient at 2 keV
 ! mu = spectral index of diffusion coefficient power law dependence
 !
-! Reference: Ressler et al., ApJ, in press
+! Reference: Ressler et al., 2014, ApJ
 !
 ! UPDATED by Aaron Tran for application to Tycho's SNR
 ! Summer 2014
 !
-! Major changes (so far, if documented):
-! Retab, edit spacing/comments for readability
-!
-! There are number of FORTRAN extensions/etc in use, I think.
-! so I'll walk through the file and try to clean things up.
-! I am not being entirely consistent on enforcing line lengths etc
-! though I'm trying to use 4-space indentation throughout
-! and generally be fixed width compliant.
-!
 ! Statement labels right aligned from column 5
 ! Continuation ampersands on column 6
 ! Exclamation points for all comments (even though not FORTRAN 77)
-!
-! continue/goto structures in electron distribution calculations
-! need to be cleaned
 ! ----------------------------------------------------------------------
 
       program Fullefflength
@@ -47,6 +35,14 @@
           double precision disttab(100, 1000), radtab(1000)
           double precision distgraph(1000)
           double precision eta, mu, eta2
+
+          ! ADDITION: explicit variable declarations
+          ! to avoid type mismatch (and bugs and things)
+          ! BUT I think variables E, B are wrong anyways...
+          double precision E, B, s
+          double precision emisx  ! function
+          double precision Distgraphr  ! function
+          integer ir
 
           integer icut, ifit, iplot
 
@@ -87,8 +83,9 @@
 
           open(242, file = 'widthcut2.dat')
           open(243, file = 'distint.dat')
-          open(119, file = 'disttab.dat')
-          open(225, file='FLUX.dat')  ! Doesn't appear to be in use, as
+          ! open(119, file = 'disttab.dat')  ! Doesn't seem to be in use?
+                                             ! No other references to 119
+          open(225, file='FLUX.dat')  ! Doesn't seem to be in use, as
                                       ! lines are commented out below
                                       ! Superseded by widthcut2.dat?
 
@@ -115,19 +112,19 @@
           endif
 
 ! Read frequency-dep. synchrotron emissivity table to common block
+! variables xex, fex
[…]

### 2014-07-17 code-models/FullEfflength.py
Fix emissivity integral in model, small tweaks

@@ -51,9 +51,18 @@ def main(Bfield, eta2, mu):
         disttab = tabulate_e_distr(...)  # 2-D np.array in particle energy, r
         jnu = emisx(...)  # either a function or a table over radial pos x
 
-def emisx(r, nu, B, emis1, radtab, disttab, imu):
+def emisx(r, nu, B, radtab, disttab):
     """Numerically integrate 1-particle synchrotron emissivity (emis1) over
-    electron distribution to obtain full emissivity j_\nu"""
+    electron distribution to obtain full emissivity j_\nu
+    Inputs:
+        r: radial coordinate (TODO: scaled, arcsec, ??)
+        nu: radiation frequency in Hz
+        radtab: table of radial coords, on which electron distr is sampled
+                (set by iradmax; compare irmax for intensity tables)
+        disttab: electron distribution function, gridded as:
+                 xex(j) (particle energy / radiation frequency), radial coord
+    Output: j_\nu(r), r = radial dist, j_\nu a scalar (float)
+    """
     pass
 
 # utilities

### 2014-07-19 writeups/code-deep-review.tex
Add code guide, B-damping code; check f(E,x) funcs
Added model code guide oriented towards how to use, fit with code.
Add Sean's B-damping version of code from email.
Reviewed and made small edits to electron distribution function
calculations in model code.  Finished reviewing Sean's model code.

--- 2014-07-17 model-guide/model-code-guide.tex
@@
 \end{center}
+
+\tableofcontents
 
@@
 
-% ----------
+% ==========
 % Appendix A
-% ----------
-\section*{Appendix A: clarifying code implementation of various equations}
+% ==========
+\appendix
+\section*{Appendices}
+\section{Code implementation of various equations}
 
@@
 
-\subsection*{Scaled diffusion coefficient $\eta_2$}
+% ---------------
+% Diffusion coeff
+% ---------------
+\subsection{Scaled diffusion coefficient \texorpdfstring{$\eta_2$}{eta2}}
 
@@
 
-\subsection*{Synchrotron emissivity integration (equation (20))}
+% ------------------------------------
+% Emissivity calculation / integration
+% ------------------------------------
+\subsection{Synchrotron emissivity integration (equation (20))}
 
@@
 
+% -------------------------------
+% Electron energy spectrum cutoff
+% -------------------------------
+\subsection{Electron energy spectrum cutoff}
+I don't fully understand Sean's discussion of the effects of including a cutoff
+or not -- nor the theoretical/experimental justification, for having a cutoff
+in the spectrum (need to read papers...).  Nevertheless, I can stare at
+equations and match symbols up.
+
+Sean's original code (loss-limited only) writes:
+\[
+    E_{\mt{cut}} = \left[ 8.3 \left( \frac{B_0}{100 \unit{\mu G}} \right)^{-1/2}
+                          \left( \frac{4 v_d}{10^8 \unit{cm\;s^{-1}}} \right)
+                          1.6021773
+                   \right]^{2/(1+\mu)}
+                   \left( \frac{1}{\eta E_h^{(1-\mu)}} \right)^{1/(1+\mu)}
+\]
+The magnetic damping version of the code writes:
+\[
+    E_{\mt{cut}} = 8.3 \left( \frac{B_0}{100 \unit{\mu G}} \right)^{-1/2}
+                   \left( \frac{4 v_d}{10^8 \unit{cm\;s^{-1}}} \right)
+                   1.6021773
+\]
+The random factor of $1.6021773$ converts from TeV to ergs (since we are
+working in Gaussian CGS units). Ahhhh
+
+The other issue -- the exponent on the $B_0$ term should be $-1/(1+\mu)$, and I
+don't know why the giant $2/(1+\mu)$ exponent is spanning several things.
+
+Okay, time to try rederiving $E_{\mt{cut}}$.  Then, email Sean...
+
+% -------------------------------
+% Electron distribution integrals
+% -------------------------------
+\subsection{Electron distribution calculations}
+
+First I'll reproduce the equations as seen in the code.  Then I'll 
+simplify and make corrections as needed.  I have \emph{not} rederived the
+equations from scratch.  In particular, I have no reference for the purely
+advective solution (though it should be straightforward, if tedious, to
+rederive).
+
+% Pure advection (lad/ldiff > 30)
+\subsubsection{Purely advective case}
+
+If $l_{\mt{ad}} / l_{\mt{diff}} > 30$, Sean uses an analytic/easy solution to
+the 1st order (linear, inhomogeneous) PDE:
+\[
+    v \frac{\ptl f}{\ptl x} - b B^2 E^2 \frac{\ptl f}{\ptl E}
+    = 2 b B^2 E f + K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x)
+\]
+Sean's code gives the solution:
+\[
+    f(E,x) = (E_0(x))^{-s} \left(\frac{E_0(x)}{E}\right)^2
+    \exp \left[ -E_0(x)/E_{\mt{cut}} \right] \cdot \left(8\times10^{-9}\right)
+\]
+where $E_0 = E / (1 - x/(v\tau_{\mt{synch}}))$.
+If $x / (v \tau_{\mt{synch}}) > 1$, Sean sets $f(E,x) = 0$ (qualitatively makes
+sense, but is this correct?).
+The solution is repeated 3 times in Sean's code (for $\mu > 1$, $\mu < 1$, and
+$\mu = 1$) but appears the same each time.  This is as expected, since $\mu$
+does not matter if we neglect diffusion.
+
+It is also worth noting that the ratio $l_{\mt{ad}} / l_{\mt{diff}}$ is a
+rescaled Peclet number.  Write:
+\[
+    \frac{l_{\mt{ad}}}{l_{\mt{diff}}}
+    = \frac{ v_d \tau_{\mt{synch}} }{ \sqrt{D \tau_{\mt{synch}}} }
+    = \sqrt{ \frac{ v_d^2 \tau_{\mt{synch}} }{ D } }
+    = \sqrt{ \frac{ v_d l_{\mt{ad}} }{ D } }
+    = \sqrt{\mt{Pe}}
+\]
+and thus Sean neglects diffusion for $\mt{Pe} > 900$.
+
+% General solution, remarks
+\subsubsection{General solutions -- some general notes}
+
+For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
+magnetic damping model here).
+
+The normalizations are NOT given in Sean's paper, but appear to follow
+Lerche \& Schlickeiser (1980) and Rettig \& Pohl (2012).  The variable
+$D_0 = \eta E_h^{1-\mu} C_d / B = D(E) / E^\mu$ is oft-seen in these
+normalizing prefactors.  This is simply the scaling constant for $D(E)$, though
+not really used in Sean's paper.
+
+Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
+is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
+$B$.
+
+The distribution equations are near identical for $\mu > 1$ and $\mu < 1$,
+but the limits are not the same.  Hence the distinct numerical implementations.
+
+% mu < 1
+\subsubsection{Solution for \texorpdfstring{$\mu < 1$}{mu lt 1}}
+Change variables and evaluate equation (15) as a single integral.
+Let $n = 1 - t^2$. Then $dn = -2t dt = -2\sqrt{1-n}dt$;
+this kills the denominator $\sqrt{1-n}$.  Numerically integrate:
+\[
+    f(E,x) = \frac{Q_0 E^{-(\mu/2 + 1/2 + s)}}
+            {2 \sqrt{\pi \alpha b B^2 D_0 (1-\mu)}} 
+            \int_0^1 dt 2 (1-t^2)^{ (s+\mu-2) / (1-\mu) }
+            \exp[ - \mathtt{argexp} ]
+\]
+with exponential argument
+\[
+    \mathtt{argexp} = \frac{n^{-1/(1-\mu)} E}{E_{\mt{cut}}}
+    + \frac{(1 - \mu)
+        \left[ l_{\mt{ad}}/\alpha \left(1 - n^{1/(1-\mu)}\right) - x \right]^2}
+        {4 l_{\mt{diff}}^2 (1-n) / \alpha}
+    \text{ .}
+\]
+If $n=1$ ($t=0$), Sean sets $\mathtt{argexp} = 10^{35}$ to prevent blowup.
+This zeroes the integrand (recall we are performing a sum).
+
+% mu = 1
+\subsubsection{Solution for \texorpdfstring{$\mu = 1$}{mu eq 1}}
+Break equation (14) into a two piece integral.
+The first piece integrates over $n\in [1,e]$ ($t\in[0,1]$).
+Let $n = e^{t^2}$ with $dn = 2 n \sqrt{\ln(n)} dt$.
+This kills the denominator $\sqrt{\ln(n)}$.
+
+The second piece integrates over $n=[e,\infty)$ ($y\in[0,1]$).
+Change variables as:
+\begin{align*}
+    n &= \frac{y}{(1-y^2)^q} + n_{\mt{min}} \\
+    dn &= \left( \frac{1}{(1-y^2)^q} + \frac{2qy^2}{(1 - y^2)^{q+1}} \right) dy
+\end{align*}
+where $n_{\mt{min}} = e$ and $q = 2$ appears to be an arbitrary exponent (?).
+
+Now, the piece-wise integral is:
+\[
+    \frac{Q_0 E^{-(1+s)}}
+         { 2 \sqrt{ \pi \alpha b B^2 D_0 } }
+    \left[
+        \int_0^1 dt \; 2 e^{(1-s) t^2} \exp[ - \mathtt{argexp} ]
+        \; + \;
+        \int_0^1 dy \left(\frac{(2q-1) y^2 + 1}{(1 - y^2)^{q+1}}\right)
+                    \left(\frac{n^{-s}}{ \sqrt{\ln(n)} }\right)
+                    \exp[ - \mathtt{argexp} ]
+    \right]
+\]
+with exponential argument (same for both integrals):
+\[
+    \mathtt{argexp} = \frac{n E}{E_{\mt{cut}}}
+        + \frac{ \left[ l_{\mt{ad}}/\alpha (1 - 1/n) - x \right]^2 }
+        { 4 l_{\mt{diff}}^2 /alpha \ln(n) }
+    \text{ .}
+\]
+
+% mu > 1
+\subsubsection{Solution for \texorpdfstring{$\mu > 1$}{mu gt 1}}
+Break equation (16) into a two piece integral.
+The first piece integrates over $n\in[1,2]$ ($t\in[0,1]$).
+Change variables as $n=1+t^2$ with $dn = 2\sqrt{n-1} dt$.
+This kills the denominator $\sqrt{n-1}$.
+
+The second piece integrates over $n\in[2,\infty]$ ($y\in[0,1]$).
+Change variables as $n = y / (1-y^2)^q + n_{\mt{min}}$ again,
+but with $n_{\mt{min}} = 2$ this time!
+
+Now, the piece-wise integral is:
+\begin{align*}
+    \frac{Q_0 E^{-(\mu/2 + 1/2 + s)}}
+         {2 \sqrt{\pi\alpha b B^2 D_0 (\mu-1)}}
+    \biggl[
+        &\int_0^1 dt \; 2 (1+t^2)^{(s+\mu-2)/(1-\mu)} \exp [ -\mathtt{argexp} ]
+        \\
+        & +\;
+        \int_0^1 dy \left(\frac{(2q-1) y^2 + 1}{(1-y^2)^{q+1}}\right)
+                    \left(\frac{n^{(s+\mu-2)/(1-\mu)}}{\sqrt{n-1}}\right)
+                    \exp[ - \mathtt{argexp}]
+    \biggr]
+\end{align*}
+with exponential argument (same for both integrals):
+\[
+    \mathtt{argexp} = \frac{n^{-1/(1-\mu)} E}{E_{\mt{cut}}}
+    + \frac{(1 - \mu)
+        \left[ l_{\mt{ad}}/\alpha \left(1 - n^{1/(1-\mu)}\right) - x \right]^2}
+        {4 l_{\mt{diff}}^2 (1-n) / \alpha}
+    \text{ .}
+\]
+This is the same $\mathtt{argexp}$ as for the $\mu < 1$ case.
+
 % ----------
@@
 % ----------
-\section*{Appendix B: synchrotron power spectrum and parameters}
+\section{Synchrotron power spectrum and parameters}
 
@@
 
-\subsection*{Sanity checks on constants}
+\subsection{Synchrotron power spectrum derivation}
+
+This follows Condon and Ransom's ERA, and Pacholczyk.
+
+\subsection{Sanity checks on constants}
 

### 2014-07-19 writeups/code-usage.tex
Add code guide, B-damping code; check f(E,x) funcs
Added model code guide oriented towards how to use, fit with code.
Add Sean's B-damping version of code from email.
Reviewed and made small edits to electron distribution function
calculations in model code.  Finished reviewing Sean's model code.

\documentclass[10pt]{article}

\usepackage[margin=1in, letterpaper]{geometry}
\usepackage{parskip}

\usepackage{amsthm, amsmath, amssymb}
% \usepackage{gensymb}  % For use of degree symbol
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}

\usepackage{enumerate} % For use of (a), (b), et cetera
\usepackage{booktabs} % Tables
\usepackage[margin=20pt, labelfont=bf, labelsep=period,
justification=justified]{caption} % Captions in figure floats

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = blue,
	pdfauthor = {Aaron Tran},
	pdfkeywords = {x-ray, SNR, notes},
	pdftitle = {Supernova remnants and stuff - \today},
%	pdfsubject = {},
	pdfpagemode = UseNone
}

% Don't indent paragraphs
\setlength\parindent{0em}

% ===============
% Useful commands
% ===============
\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\; \mt{#1}} % vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % tex.stackexchange.com/q/55701
\newcommand{\del}{\nabla}
\newcommand{\ptl}{\partial} % Laziness

\newcommand{\Chandra}{\textit{Chandra}}

% ===============
% Document proper
% ===============
\begin{document}

\begin{center}
    \Large{Guide to Sean's model codes}

    \normalsize{Aaron Tran}\\
    \today \\
\end{center}

% ============
% Introduction
% ============
\section{Introduction}

Here I give an informal explanation of Sean's model code: the code inputs and
outputs, and fitting code outputs to FWHM measurements. I do not explain the
physics or the internal calculations of the code; please see the accompanying
code review for that.

Table, figure, and equation references are from the version of record at
\href{http://dx.doi.org/10.1088/0004-637X/790/2/85}
{doi:10.1088/0004-637X/790/2/85}.

% ============================
% Synchrotron rim width models
% ============================
\section{Filament width model codes}

Two codes are used to model filament widths, which I refer to as \emph{simple}
and \emph{complex}; they are defined by transport equations (5) and (12)
respectively.  Equations (6--11), (13), (23) describe results from the simple
model; equations (12), (14--21) describe the complex model implementation.

Both models are loss-limited; Sean does not present \emph{fitting} results for
magnetic damping models (which would add more free parameters).

Both codes take inputs $B_0$, $\eta_2$, and $\mu$.
$B_0$ is downstream (amplified) magnetic field strength, $\eta_2$ is diffusion
coefficient constant at $2$ keV, and $\mu$ is the scaling exponent for
energy-dependence of the diffusion coefficient ($D \propto E^\mu$).

Both codes output \textbf{predicted filament FWHM values} as a function of
energy.  We seek values of $B_0$, $\eta_2$, and $\mu$ that give best-fit
filament FWHM predictions to our FWHM measurements.

Rephrased, we have:
\[
    w_{\mt{model}} = w(\nu; B_0, \eta_2, \mu)
\]
and we want to minimize
\[
    \chi^2 = \sum \left( \frac{w_{\mt{obs}}(\nu) - w_{\mt{model}}(\nu)}
                       { \delta w_{\mt{obs}} } \right)^2
\]

First, I explain a little more about how predicted FWHMs are calculated and
fitted to measured FWHMs, for each model.
Then, I explain how we are attempting to extend Sean's model fitting.

% --------------------------------
% Simple (catastrophic dump) model
% --------------------------------
\subsection{Simple model fitting}

The simple model gives an analytic expression for $w_{\mt{model}}(\nu;\ldots)$.
This is equation (6) times a projection factor $\beta = 4.6$.

Fitting is easy, in principle.  We can simply find a best fit curve
$w_{\mt{model}}(\nu)$, with 3 free parameters, to the measured FWHMs.
But, SN 1006 had only 3 FWHM measurements -- and, as I explain next, Sean used
only 2 of the FWHM measurements to fit the complex model.

Therefore, Sean used several fixed values of $\mu$: $0, 1/3, 1/2, 1, 1.5, 2$,
and computed best fit $B_0$ and $\eta_2$ values for the 3 FWHM measurements.
Table 7 summarizes the results of these fits.

I'm not sure why $\mu$ was fixed -- in linear least-squares, 3 free parameters
would exactly hit 3 measurements; for non-linear least-squares, the parameters
are not entirely independent so it'd be a little messier.  I could imagine that
(1) the values are just not well-constrained in such a fit, and/or
(2) Sean wanted to be consistent across both models.

% ---------------------------------
% Complex (continuous E loss) model
% ---------------------------------
\subsection{Complex model fitting}

The complex model numerically computes predicted intensity profiles
for $w_{\mt{model}}(\nu; \ldots)$, by solving equations (20--21)
FWHM values are manually extracted from the predicted profiles.

For SN 1006, the code predicts FWHM values at 0.7, 1, and 2 keV.  At some
point, Sean tried fitting as done for the simple model -- i.e., perform a
non-linear fit in free parameters $B_0$, $\eta_2$ to obtain best-fit
FWHM predictions for 3 FWHM measurements.  But, this was not implemented.

Section 4.2 describes the fitting procedure used.  Sean threw away the FWHM at
0.7 keV and computed the approximate scaling exponent
\[
    m_E(\text{2 keV}) = \frac{ \ln( \mathrm{FWHM}(\text{2 keV}) /
                                    \mathrm{FWHM}(\text{1 keV}) ) }
                             { \ln( \text{2 keV} / \text{1 keV} ) }
\]
This $m_E$ was computed for measured and predicted FWHMs at 1, 2 keV.

Sean varied $B_0$ and $\eta_2$ by hand for fixed values of $\mu$ to find best
fit values.  In practice, he chose $\eta_2$ to best fit the $m_E$ value, then
varied $B_0$ to fit the FWHM (as $m_E$ is relatively insensitive to $B_0$).
Table 8 summarizes the results of these fits.

Here, fitting $\{m_E(\text{2 kev})$, $\mathrm{FWHM}(\text{2 keV})\}$ should be
equivalent to fitting $\{\mathrm{FWHM}(\text{1 keV})$,
$\mathrm{FWHM}(\text{2 keV})\}$ instead.  We are just changing variables, and
it turns out the manual fitting is easier (predicted $m_E$ being insensitive to
fit parameter $B_0$, as noted above).  Note: this FWHM / $m_E$ matter was
clarified by email exchange with Sean on 2014 July 3.

\subsection{Results}

Just looking at Tables 7, 8, we can see that the simple model is pretty robust.
Fits weren't given for all $\mu$ values in Table 8 (Filaments 2, 5 appear to
have small $m_E$ values at 2 keV).

What do the parameters mean, or how do they affect predicted FWHM widths?
I still need to mess with this.  Roughly, per Sean's observations (to be
checked): $B_0$ controls overall FWHM widths, but doesn't affect width-energy
scaling much.  Diffusion parameters $\eta_2$ and $\mu$ are the main controls on
the width-energy scaling, as you might expect.

The effect of $\mu$ on width-energy scaling is shown in Figure 1.
The effects of both $\mu$ and $\eta_2 \sim D/D_{\mt{bohm}}$ on width-energy
scaling are shown in Figure 3.  Both decreasing $\mu$ and increasing $\eta_2$
will weaken the width-energy scaling, as the filaments are all smeared out by
diffusion, and smaller $\mu$ means diffusion is less sensitive to energy.

% ==========
% Next steps
% ==========
\section{Next steps}

The simple model is implemented for Tycho, though I have not messed with the
fits / implemented variable shock speed / etc. yet.  The fits give $B_0$
of order $100$ to $1000 \unit{\mu G}$, and $\eta_2$ of order $0.1$ to $10$ --
though the fits are not great.

As for the complex model: I reviewed Sean's code and hit/asked about all issues
I could find.
I verified the calculations against equations in Sean's paper, excepting one
calculation not mentioned in the paper which needs to be rederived.
I have not re-derived the equations in Sean's paper, or checked them against
the source papers (namely Lerche \& Schlickeiser, 1980).
The code appears to work and is giving reasonable output values.

I am porting the complex model code to Python at this time, and will attempt to
implement the non-linear fitting as done for the simple model code (and as Sean
previously attempted).

\end{document}

### 2014-07-19 code-models/FullEfflength.py

@@ -8,6 +8,8 @@ Aaron Tran
 2014 July 15
 """
 
+from __future__ import division # Or whatever
+
 import lmfit
 import numpy as np
 import scipy as sp
@@ -64,6 +66,53 @@ def emisx(r, nu, B, radtab, disttab):
     Output: j_\nu(r), r = radial dist, j_\nu a scalar (float)
     """
     pass
+
+# Electron distribution functions
+# throw this into a CLASS or something -- so I can hold CONSTANTS
+# at a class level or whatever...
+
+def distr(E, B, E_cut, r, eta_c, mu, rs, v, s):
+    """Electron distribution, from Rettig & Pohl and Lerche & Schlickeiser"""
+    
+    D0 = eta*2.083d19/B  # CHECK THIS eta (E_h)^(1-mu) * C_d / B0
+    a = 1.57e-3  # Synchrotron constant ... declare at module level
+    tau = 1. / (a * B**2 * E)
+    lad = v * tau
+    ldiff = dsqrt(D0*E**mu*tau)
+    
+    # lad/ldiff ~ sqrt(v*lad) / dsqrt(D) ~ peclet number!
+    
+    if lad/ldiff > 30:
+        return distr_adv()
+    
+    if mu > 1:
+        return distr_mgt1(E, B, E_cut, r, eta_c, mu, rs, v, s)
+        # I think this is the same as below...
+    elif mu < 1:
+        return distr_mlt1(E, B, E_cut, r, eta_c, mu, rs, v, s)
+    else:
+        return distr_rpohl(E, B, E_cut, r, eta_c, mu, rs, v, s)
+
+ 
+def distr_adv(E, B, E_cut, r, eta_c, mu, rs, v, s):
+    """If advective length much greater than diffusive lengthscale"""
+    pass
+
+
+def distr_mgt1(E, B, E_cut, r, eta_c, mu, rs, v, s):
+    """Case: mu > 1"""
+    pass
+
+
+def distr_mlt1(E, B, E_cut, r, eta_c, mu, rs, v, s):
+    """Case: mu < 1"""
+    pass
+
+
+def distr_rpohl(E, B, E_cut, r, eta_c, mu, rs, v, s):
+    """Case: mu = 1"""
+    pass
+
 
 # utilities
 

### 2014-07-19 code-models/FullefflengthPohlab.f

@@ -1,0 +1,1105 @@
+	program Fullefflengthab
+
+	
+       double precision cm, ecut
+       double precision B0, v0, rs, alpha
+       double precision nu0, nu, ab, emis1
+       double precision a, nugraph(100)
+       double precision r, delr(40), rgraph(10000,40)
+       double precision dx, integrand, integral
+       Double Precision compratio
+       double precision distr, Bfield
+       double precision intensitygraph(40,10000)
+       double precision xex(100), fex(100)
+       double precision nuroll,x, rho
+       double precision width(40), advection(40)
+       double precision rmin, norms(40)
+       double precision intensity, fluxplat(40), fluxpeak(40)
+       double precision gammaplat(40), gammapeak(40)
+       double precision rtab(1000), inttab(1000), titab(1000)
+       double precision brtab(1000), bttab(1000), altab(1000)
+       double precision bgraph(1000), en, rad, delrad, c1
+       double precision disttab(100, 10000), radtab(10000)
+       double precision distgraph(10000), Bmin, B, slopeemis
+       double precision disttab1(100,10000), emistab(10000)
+       double precision spline,BIATX(1000)
+       DOUBLE PRECISION BCOEF(1000), GTAU(1000), Q(112640), T(1006)
+
+    
+       common/xrays/xex, fex, ir
+   
+
+!Physics Parameters
+       compratio = 4d0
+       v0 = 5*1.d8/compratio
+       ab =.05d0
+       Bmin =5d-6
+       rs = 2.96e19    !Modified from nufit code....distance is now 2.2 kpc, so rs is found from tan(943.7'')*2.2 kpc 
+       alpha = .6d0
+       s = 2d0*alpha+1d0
+       
+       
+!Constants
+       cm = 1.82d18
+       c1 = 6.27e18
+       a = 1.57d-3
+       
+!Options
+	   icut = 0
+	   
+	   
[…]

### 2014-07-22 writeups/code-deep-review.tex
First fit to full model code output, B field only
Modify model code to work with f2py, start testing Python f2py wrapper
code

@@
 
+Conclusion -- equate the loss and acceleration times as:
+\[
+    \tau_{\mt{accel}} \propto \frac{D}{v_s^2}
+    \sim \frac{1}{b B^2 E} = \tau_{\mt{synch}}
+\]
+taking $D = \eta (C_D E_h / B) (E/E_h)^\mu$ as usual.
+The scaling factors are correct, and the $\eta$ term indeed
+should be $\eta E_h^{1-\mu}$, so that is correct.  The only weird part is
+rederiving the prefactor, for which you must refer to several constants and
+assumptions in Parizot et al. (2006); they treat spatial dependence and other
+stuff in more detail.
+
+So, for now, I shall trust Sean's judgement and just move forward with the
+code.  In fact, it is the magnetic damping model that needs an extra factor of
+$\eta^{-1/2}$ (and consequently Sean's equation (18) is also incorrect).
+
 % -------------------------------
@@
 rederive).
+
+The normalizations are NOT given in Sean's paper, but appear to follow
+Lerche \& Schlickeiser (1980) and Rettig \& Pohl (2012).  The variable
+$D_0 = \eta E_h^{1-\mu} C_d / B = D(E) / E^\mu$ is oft-seen in these
+normalizing prefactors.  This is simply the scaling constant for $D(E)$, though
+not really used in Sean's paper.
+
+\textbf{Not checked}: what is the role of $\alpha$ in all of this?!  Part of
+the normalization and other factors above.  Low priority...
+
+For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
+magnetic damping model here).  The distribution equations are near identical
+for $\mu > 1$ and $\mu < 1$, but the limits are not the same.  Hence the
+distinct numerical implementations.
+Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
+is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
+$B$.
 
@@
 and thus Sean neglects diffusion for $\mt{Pe} > 900$.
-
-% General solution, remarks
-\subsubsection{General solutions -- some general notes}
-
-For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
-magnetic damping model here).
-
-The normalizations are NOT given in Sean's paper, but appear to follow
-Lerche \& Schlickeiser (1980) and Rettig \& Pohl (2012).  The variable
-$D_0 = \eta E_h^{1-\mu} C_d / B = D(E) / E^\mu$ is oft-seen in these
-normalizing prefactors.  This is simply the scaling constant for $D(E)$, though
-not really used in Sean's paper.
-
-Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
-is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
-$B$.
-
-The distribution equations are near identical for $\mu > 1$ and $\mu < 1$,
-but the limits are not the same.  Hence the distinct numerical implementations.
 

### 2014-07-22 writeups/code-usage.tex
First fit to full model code output, B field only
Modify model code to work with f2py, start testing Python f2py wrapper
code

@@
 What do the parameters mean, or how do they affect predicted FWHM widths?
-I still need to mess with this.  Roughly, per Sean's observations (to be
+I am still messing with this.  Roughly, per Sean's observations (to be
 checked): $B_0$ controls overall FWHM widths, but doesn't affect width-energy
@@
 The effects of both $\mu$ and $\eta_2 \sim D/D_{\mt{bohm}}$ on width-energy
-scaling are shown in Figure 3.  Both decreasing $\mu$ and increasing $\eta_2$
+scaling are shown in Figure 3.  Both increasing $\mu$ and increasing $\eta_2$
 will weaken the width-energy scaling, as the filaments are all smeared out by
-diffusion, and smaller $\mu$ means diffusion is less sensitive to energy.
+diffusion.  Larger $\mu$ means diffusion is stronger at higher energies, which
+more strongly counteracts thinning with energy from synchrotron losses.
+
+Finally, the effect of $\mu$ on width-energy scaling is stronger for larger
+$\eta_2$ (Figure 3).  Figure 3 also suggests how degeneracy might occur --
+e.g., multiple pairs of $\eta_2$, $\mu$ can reproduce $m_E = -0.15$, and we can
+have strong variation in $\eta_2$ with just a small variation in $\mu$.  In
+principle, the absolute widths should also help constrain the best set of
+values, but it may simply not be a very strong constraint -- which we'll see
+from $\Delta\chi^2 \leq 2.7$ errors, for example.
 

### 2014-07-22 code-models/FullEfflength_mod_wrapper.py

@@ -1,0 +1,181 @@
+"""
+Code to f2py-ize FullEfflength_mod.f
+and attempt to run fits...
+
+FullEfflength_mod.f modified appropriately
+(just revert to older version as needed)
+
+Based on code-profiles/fwhm-process.ipynb setup for the simpler code
+(just a prototype).  I will probably use this code for both models, to
+consolidate global constants + fit work all in one place.
+
+Aaron Tran
+2014 July 21
+"""
+
+import lmfit
+import matplotlib.pyplot as plt
+import numpy as np
+from numpy import f2py
+import scipy as sp
+from scipy import optimize
+
+with open('FullEfflength_mod.f', 'r') as f:
+    fsource = ''.join(list(f))
+np.f2py.compile(fsource, modulename='fullmodel', verbose=1)
+import fullmodel as fm
+fm.readfglists()
+
+def main():
+    """Docstring me"""
+
+
+# =========================
+# Run fits for whatever SNR
+# =========================
+
+def apply_fit():
+    """Just testing..."""
+    kevs = np.array([0.7, 1., 2.])
+    #data4 = np.array([29, 23.9, 16.6])
+    #eps4 = np.array([.9, .39, .45])
+    data5 = np.array([33.75, 27.2, 24.75 ])
+    eps_data5 = np.array([2.37,.62,.61])
+
+    data, eps = data5, eps_data5
+
+    #p = lmfit.Parameters()
+    #p.add('B0', value=1e-4, min=1e-6, max=1e-2)
+    #p.add('eta2', value=1, vary=False) #min=0, max=1e4)
+    #p.add('mu', value=1, vary=False)
+
+    #res = lmfit.minimize(width_cont, p,
+    #               args=(kevs, data, eps),
+    #               method='leastsq')
+
+    #print lmfit.printfuncs.report_fit(res.params)
+
+    f = lambda b: width_cont(b, kevs, data, eps)
+
+    popt, pcov = sp.optimize.leastsq(f, np.array([1e-4]), epsfcn=1e-6)
+
+    #en_plt = np.linspace(0.6, 2.1, 10)
+    #plt.errorbar(kevs, data, eps, fmt='bo')
+    #plt.plot(en_plt, width_cont(p, en_plt), '-k')
+    #plt.xlabel('Observation energy (keV)')
+    #plt.ylabel('FWHM (arcsec)')
+    #plt.show()
+
+    #return res
+    return popt, pcov
+
+
+def params_sn1006():
+    """Configure parameters for SN1006
+    output: 
+    """
[…]

### 2014-07-22 code-models/Widthfun_mod.py

@@ -1,91 +1,0 @@
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Jan 27 16:50:04 2014
-
-@author: Sean
-"""
-import numpy
-import lmfit
-import matplotlib.pyplot as plt
-
-data1 = numpy.array([35.5, 31.94, 25.34])
-eps_data1 = numpy.array([1.73, .97, 1.71])
-data2 = numpy.array([23.02, 17.46, 15.3])
-eps_data2 = numpy.array([.35,.139, .559])
-data3 = numpy.array([49.14, 42.76,29.34])
-eps_data3 = numpy.array([1.5, .718, .767])
-data4 = numpy.array([29, 23.9, 16.6])
-eps_data4 = numpy.array([.9, .39, .45])
-data5 = numpy.array([33.75, 27.2, 24.75 ])
-eps_data5 = numpy.array([2.37,.62,.61])
-
-
-data = data5
-eps_data = eps_data5
-def Width(params,data,eps_data):
-    
-    B0 = params['B0'].value
-    eta2 = params['eta2'].value
-    mu =2
-    
-    vd = 5e8/4.0
-    b = 1.57e-3
-    Cd = 2.083e19
-    cm = 1.82e18
-    rs = 2.96e19
-    rsarc = 900.
-    nu2 = 4.8359e17
-    nu = numpy.array([.7*4.8359e17/2, 4.8359e17/2, 4.8359e17])
-    
-    eta = eta2*numpy.sqrt(nu2/cm/B0)**(1-mu)
-    E = numpy.sqrt(nu/cm/B0)
-    tsynch = 1.0/b/B0**2/E
-
-    D = eta*Cd*E**mu/B0
-    a = 2*D/vd/(numpy.sqrt(1+(4*D/vd**2/tsynch))-1)*4.6  # Factor of 4.6 tacked to equation (6) ??????
-    
-    return (a/rs*rsarc-data)/eps_data
-    
-    
-
-
-params = lmfit.Parameters()
-params.add('B0',value = 1e-4, min = 1e-6, max = 1e-3)
-params.add('eta2',value = 1, min = 0, max = 1e4)
-
-result =lmfit.minimize(Width,params,method='leastsq',args = (data,eps_data) )
-
-print result.chisqr
-
-print params
-
-
[…]

### 2014-09-04 manuscript/tycho-paper.tex
Outline paper, file cleanup, more data/debugging
Paper, bibliography, requisite cls/sty files to commit
Organize debugging notes/logs, more debugging (see my notes)
Code setup to run error computations, this week

\documentclass[manuscript]{aastex}  % one-column, double-spaced
% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
% \documentclass[preprint2]{aastex}  % double-column, single-spaced
% \documentclass[preprint2,longabstract]{aastex}  % if abstract doesn't fit

% \documentclass[apjl]{emulateapj}
% \documentclass[apj]{emulateapj}

\shorttitle{Synchrotron Rims in Tycho's SNR}  % <~ 44 char
\shortauthors{XXX et al.}  % Max three
\slugcomment{Not to appear in Nonlearned J., 45.}  % short title pg comment

%% ==================================================================== %%
%% README for track changes                                             %%
%% To add/remove text or add comments, use the following commands:      %%
%%                                                                      %%
%%       \note[editor]{The note}                                        %%
%%     \annote[editor]{Text to annotate}{The note}                      %%
%%        \add[editor]{Text to add}                                     %%
%%     \remove[editor]{Text to remove}                                  %%
%%     \change[editor]{Text to remove}{Text to add}                     %%
%%                                                                      %%
%% Using trackchanges.sty (http://trackchanges.sourceforge.net/)        %%
%%                                                                      %%
%% If you prefer to just edit directly, that works as well.             %%
%% ==================================================================== %%

\usepackage[inline]{trackchanges}

% Up to 5 editors
\addeditor{Rob}
\addeditor{Sean}
\addeditor{Steve}
\addeditor{Aaron}
\addeditor{Brian}

%% ============
%% Bibliography
%% ============
%\biboptions{semicolon}  % natbib options

%% ===============
%% Custom packages
%% ===============

% aas.org/authors/author-names-non-roman-alphabets
% \usepackage{CJK}

% Manuscript formatting
%\usepackage{lineno}

% Math, symbols, links, inline typesetting
%\usepackage{amsthm, amsmath, amssymb}
%\usepackage{amsmath}
%\usepackage{enumerate}  % For use of (a), (b), etc.
%\usepackage{hyperref}

% Figures, tables, floats, page layout (see also deluxetable)
%\usepackage[pdftex]{graphicx}
\usepackage{booktabs}
%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
%\usepackage{pdflscape}  % rotate pages (Texlive)

%% ==============
%% Extra commands
%% ==============
\newcommand{\mt}{\mathrm}
\newcommand{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
\newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701

% Sets, operators
\newcommand{\ints}{\mathbb{Z}}
\newcommand{\ptl}{\partial}
\newcommand{\del}{\nabla}

%% =====================
%% AASTeX utilities etc.
%% =====================

% Object linking: https://aas.org/object-linking/introduction-object-linking
% \objectname[SNR G120.2+01.4]{Tycho's SNR}
% \objectname[M1]{Crab nebula}
% \object{NGC 6397}

% Dataset linking: https://aas.org/data-sets/data-set-linking
% \dataset{ADS/Sa.ASCA\#X/86008020}
% \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum}

% Possibly useful items:
% \footnote{footnote}
% \notetoeditor{note}  % Appears in manuscript footnotes, not in preprints
% \begin{mathletters}  % Add lettering to -eqnarrays- align, eqns
% \end{mathletters}  % e.g., number (4a), (4b) vs. (4), (5)
% \url{http://google.com}

% AASTeX symbol macros
% A 90\degr~angle, an ion: \ion{Ca}{2}, \slantfrac{40}{59} (why slantfrac?).

% Figures, tables
% AASTeX provides \plotone{z.eps}, \plottwo{a.eps}{b.eps}, \plotfiddle (?!)

% Tables -- refer to author guide / sample.tex when needed.

\begin{document}

% ========================
% Title, authors, abstract
% ========================
\title{Energy Dependent X-Ray Rim Width in Tycho's Supernova Remnant}

%\begin{CJK*}{UTF8}{gbsn}
\author{
Robert Petre\altaffilmark{1},
Sean M. Ressler\altaffilmark{2},
Stephen P. Reynolds\altaffilmark{3},
Aaron Tran\altaffilmark{1,4},
Brian J. Williams\altaffilmark{1,5}
}
%\end{CJK*}

\altaffiltext{1}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
\altaffiltext{2}{Dept. Physics, University of California,
    Berkeley, CA 94720, USA}
\altaffiltext{3}{Dept. Physics, North Carolina State University,
    Raleigh, NC 27695, USA}
\altaffiltext{4}{CRESST, University of Maryland, College Park, MD 20742}
\altaffiltext{5}{NASA Postdoctoral Program Fellow}

\begin{abstract}
\note[Aaron]{Copy pasted from NASA abstract, not reviewed}
Young supernova remnants may exhibit thin (~1--10\% of shock radius) X-ray rims
of synchrotron radiation from forward shock-accelerated electrons that travel
downstream of the shock and quickly cease to radiate. Rim widths limited by
radiative energy losses should decrease with energy and require magnetic field
amplification $10$--$100\times$ that expected from adiabatic shock compression.
Damped magnetic fields behind rims may produce thin rims without strong field
amplification but require energy-independent rim widths. We measured rim widths
around Tycho's supernova remnant in 5 energy bands using a 750 ks Chandra
observation. Rims narrow with increasing energy, favoring loss-limited
radiation over magnetic damping. Observed widths are best fit by electron
transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work.
Inferred magnetic fields, diffusion coefficients, and diffusion-energy scaling
may constrain models for cosmic ray acceleration in supernova remnants and
plasma turbulence in astrophysical shocks.
\note[Aaron]{Keywords from Sean's paper}
\end{abstract}

\keywords{acceleration of particles ---
    ISM: individual objects (Tycho's SNR) ---
    ISM: magnetic fields ---
    ISM: supernova remnants ---
    X-rays: ISM}

% ============
% Introduction
% ============
\note[Aaron]{a lot of preliminary text copy-pasted from poster or my own
notes, so explanations may be a bit simplistic}

\section{Introduction}

\note[Aaron]{most text below is copy-pasted from my own notes -- explanation
may be too simplistic}

Accelerating ISM/CSM particles in the forward shocks of supernovae emit
synchrotron radiation.  Emission is strong in the shock's immediate wake, but
dies off quickly downstream as particles radiate and lose energy. The radiation
from a spherical blast wave, then, is shell-like with bright X-ray and radio
rims/filaments due to line-of-sight projection.  These filaments have finite
and energy-dependent widths, set by:
\begin{itemize}
  \item \emph{synchrotron losses}.  At the shock, high energy electrons
  efficiently radiate harder x-ray photons.  As electrons are advected
  downstream while radiating, they radiate at lower energies and lose energy
  more slowly.  Synchrotron losses depend on (1) the initial electron energy
  distribution, and (2) the gradual decrease of electron energies downstream of
  the shock.
  \item \emph{diffusion}.  Random motion with respect to bulk plasma advection.
  Higher energy electrons diffuse and travel further downstream than would be
  expected from pure advection; hence, higher energy radiation may be seen
  farther downstream of the shock than expected.
  Higher energy particles may also diffuse \emph{ahead} of the shock, possibly
  giving rise to a so-called ``cosmic-ray shock precursor''.  Note that this is
  distinct from radiative precursors \citep[e.g.,][]{ghavamian2000}.
\end{itemize}

\subsection{Abbreviated review of prior work for context}

Basic observables \citep[e.g.,][]{bamba2003, bamba2005-hist, bamba2005-vela,
parizot2006} and consequences.

Testable model predictions of magnetic damping \citep{pohl2005}.

\citet{ressler2014} found rim narrowing in the remnant of SN 1006,

Equivocal results by \citet{araya2010} for Cas A.

\subsection{Our work}

We make measurements to distinguish between these two end member scenarios.
\note[Aaron]{paper roadmap} First we review our measurements,
explain the relevant model physics and governing equations,
explain our fitting procedure.

Then we discuss the implications of our fits and models

% ============
% Observations
% ============
\section{Observations}

We used archival \textit{Chandra} observations of Tycho
(\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs 10093--10097},
\dataset[ADS/Sa.CXO\#obs/10902]{10902--10906})
obtained with the ACIS-I CCD between 2009 Apr 11 and 2009 May 5.
The total exposure time is $734 \unit{ks}$.
The data are divided into five energy bands:
0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
We excise counts between 1.7--2 keV to avoid \ion{Si}{13} (He$\alpha$) line
emission prevalent in the remnant's thermal ejecta.

Thirteen regions were selected with the following criteria in mind:
\note[Aaron]{itemized lists are just for outlining}
\begin{itemize}
    \item Nonthermal filaments should be singular and localized (i.e., either
        no overlapping or completely overlapping rims -- this rules out parts
        of NE limb)
    \item Nonthermal filaments should have sufficient signal-to-noise ratio
        that we can identify a clear FWHM in all bands (rules out a lot of
        faint southern wisps)
    \item Avoid plumes of thermal emission: identify spatially from images,
        esp. in lower energy bands (0.7--1 keV, 1--2 keV)
        (e.g.,~\ref{fig:snr}, eastern side), identify spectrally from emission
        lines.
\end{itemize}

\begin{figure}
    \plotone{figures/f0-snr.eps}
    \caption{RGB image of Tycho with region selections overlaid.  Bands are
    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue)}
    \label{fig:snr}
\end{figure}

Discuss point-spread function if that may be a point of contention.
Show that it is not a problem for us (simply say that all rims are at
least ~1 arcsec and hence are spatially resolved? Compare,
\citet{bamba2005-hist} measured upstream/downstream scale widths separately?)

\subsection{Filament width measurements}
\begin{figure*}
    \plotone{figures/f0-prfs.pdf}
    \caption{Some semblance of a caption.}
    \label{fig:profiles}
\end{figure*}

\subsection{Filament spectra}

And we shall purify the remnant's rims
that they may show us how they do thin
discriminating damped models.

\begin{figure}
    \plotone{figures/f0-spec.pdf}
    \caption{Another caption \citep{fermi1949}}
    \label{fig:spec}
\end{figure}

Finally, here are some numbers!

%\begin{table}
%\end{table}

% =======================
% Filament width modeling
% =======================
\section{Filament width models}

Cite \citet{ressler2014} vigorously here.  Just present the governing transport
equations (with variables), namely that from:
\[
  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
  = C + \del \cdot \left( D \del f \right)
\]
we obtain (1-D time-independent flow, neglect compressible flow?!,
space-independent diffusion coefficient):
\[
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
\]
and by random selection of the source/sink term $C$ we obtain either a
simplified model:
\begin{equation}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0
\end{equation}
where this is equation (6) of \citet{ressler2014}; we also look at
\begin{equation}
    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
      \left(bB^2E^2f\right)
\end{equation}
which is equation (12) of \citet{ressler2014}.

% ===================
% Results (best fits)
% ===================

\section{Results}

Let's just say if any fit runs to $\eta_2 = 10^5$ or $B_0 = 10$ mG (for Tycho),
we deem it effectively unconstrained.

\begin{table}
% Here I'm following the AASTeX sample...
%\tabletypesize{\scriptsize}
\caption{Full model best fit parameters, region 1.\label{tab:fit1}}
\begin{tabular}{@{}rllr@{}}
\toprule
{} & \multicolumn{3}{c}{Region 1} \\
\cmidrule(l){2-4}
$\mu$ (-) & $\eta_2$ (-) & $B_0$ ($\mu$G) & $\chi^2$\\
\midrule
0.00 & ${19.1}^{+19}_{-7.1}$ & ${784}^{+1.2 \times 10^{2}}_{-72}$ & 57.5590\\
0.33 & ${56}^{+75}_{-29}$ & $930^{+190}_{-140}$ & 34.6006\\
0.50 & ${92}^{+160}_{-54}$ & ${1010}^{+260}_{-180}$ & 25.5737\\
1.00 & ${370}^{+3300}_{-310}$ & ${1260}^{+4500}_{-440}$ & 9.7750\\
1.50 & ${23}^{+32}_{-10}$ & ${623}^{+130}_{-67}$ & 8.7937\\
2.00 & ${11.4}^{+5.2}_{-3.3}$ & ${512}^{+34}_{-26}$ & 9.5862\\
\bottomrule
\end{tabular} 
\end{table}

Table reference goes here~\ref{tab:fit1}.

% ==========
% Discussion
% ==========
\section{Discussion}

What do all these numbers with their errors mean?

% ==========
% Conclusion
% ==========
\section{Conclusions}

In conclusion, crazy B field amplification is not that weird.  Magnetic damping
can be ruled out and our result is robust throughout the remnant.

\acknowledgments

The scientific results reported in this article are based on data obtained from
the Chandra Data Archive.

{\it Facilities:} \facility{CXO (ACIS-I)}

\appendix

\section{Appendix material}

Appendix text if so desired.

\bibliographystyle{apj}  % AASTeX journal macros (for abbrevs) supplied by ADS
\bibliography{refs-snr}

\end{document}

### 2014-09-04 code-models/models_exec.py

@@ -144,10 +144,15 @@ class Fitter(object):
         if appr == 'simp':
             res = self.fitter_simp(mu)
         elif appr == 'full':
-            self._vprint('Starting from best grid value')
-            eta2, B0, fwhms, chisqr = self.grid_best(mu)
-            res = self.fitter_full(mu, eta2=eta2, B0=B0, eta2_free=True,
-                                   **kwargs)
+            if ('eta2' in kwargs) and ('B0' in kwargs):
+                self._vprint('Starting from provided initial guesses:',
+                             'eta2 = {:0.3f},'.format(kwargs['eta2']),
+                             'B0 = {:0.3f}'.format(kwargs['B0']*1e6))
+            else:
+                self._vprint('Starting from best grid value')
+                eta2, B0, fwhms, chisqr = self.grid_best(mu)
+                res = self.fitter_full(mu, eta2=eta2, B0=B0, eta2_free=True,
+                                       **kwargs)
         else:
             raise Exception('Invalid model choice')
         
@@ -332,23 +337,31 @@ class Fitter(object):
             x_ret = one_dir_root(f, x, x_lim, **kwargs)
 
         else:
-            self._vprint('Found error crossing on grid')
+            self._vprint('Found error crossing on grid;',
+                         'idx = {} in [0,{}]'.format(idx, len(xgrid)-1))
             idx_adj = idx - sgn  # Move backwards
 
             # Need to verify bracketing points; move backwards if needed
             if idx == idx_init:
                 self._vprint('Did not move on grid, checking backwards')
-                while (((sgn > 0 and xgrid[idx_adj] > x0)
-                        or (sgn < 0 and xgrid[idx_adj] < x0))
-                       and f(xgrid[idx_adj]) > 0):  # Yuck
-                    self._vprint('Moved threshold back by one')
+                while ((sgn > 0 and (idx_adj >= 0 and x0 < xgrid[idx_adj])) or
+                      (sgn < 0 and (idx_adj < len(xgrid) and xgrid[idx_adj] < x0))):  # YUCK
+                    check_f_adj = f(xgrid[idx_adj])
+                    if check_f_adj < 0:
+                        break  # We found crossing
                     idx_adj -= sgn
                     idx -= sgn
+                    self._vprint('Moved threshold back by one;',
+                                 'idx = {}, idx_adj = {}'.format(idx, idx_adj))
+                if check_f_adj >= 0:
+                    self._vprint('Could not bracket crossing w/grid resolution?!')
[…]

### 2014-09-04 manuscript/regen.sh

@@ -1,0 +1,7 @@
+#!/bin/sh
+
+pdflatex ${1}.tex
+bibtex ${1}
+pdflatex ${1}.tex
+pdflatex ${1}.tex
+open ${1}.pdf

### 2014-09-09 manuscript/tycho-paper.tex
New error annealing method, paper work
Search from initial grid index, but no longer "anneals" from grid values;
uses unidirectional rootfinder throughout.  Separate tables from paper.
Remove grid rootfinder and its test methods

@@
 % \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
-% \documentclass[preprint2]{aastex}  % double-column, single-spaced
-% \documentclass[preprint2,longabstract]{aastex}  % if abstract doesn't fit
-
-% \documentclass[apjl]{emulateapj}
-% \documentclass[apj]{emulateapj}
+% \documentclass[iop, apj, twocolappendix]{emulateapj}
 
@@
 \shortauthors{XXX et al.}  % Max three
-\slugcomment{Not to appear in Nonlearned J., 45.}  % short title pg comment
+\slugcomment{Draft, \today}  % short title pg comment
 
@@
 %%                                                                      %%
-%% Using trackchanges.sty (http://trackchanges.sourceforge.net/)        %%
-%%                                                                      %%
-%% If you prefer to just edit directly, that works as well.             %%
 %% ==================================================================== %%
 
-\usepackage[inline]{trackchanges}
-
-% Up to 5 editors
+\usepackage[inline]{trackchanges}  % trackchanges.sourceforge.net
 \addeditor{Rob}
@@
 
-%% ============
-%% Bibliography
-%% ============
-%\biboptions{semicolon}  % natbib options
-
-%% ===============
-%% Custom packages
-%% ===============
-
-% aas.org/authors/author-names-non-roman-alphabets
-% \usepackage{CJK}
-
-% Manuscript formatting
-%\usepackage{lineno}
-
-% Math, symbols, links, inline typesetting
-%\usepackage{amsthm, amsmath, amssymb}
-%\usepackage{amsmath}
-%\usepackage{enumerate}  % For use of (a), (b), etc.
-%\usepackage{hyperref}
-
-% Figures, tables, floats, page layout (see also deluxetable)
-%\usepackage[pdftex]{graphicx}
+\usepackage{amsmath}  % amsthm, amssymb
+\usepackage{hyperref}
+% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
 \usepackage{booktabs}
@@
 
-%% ==============
-%% Extra commands
-%% ==============
 \newcommand{\mt}{\mathrm}
@@
 \newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
-
-% Sets, operators
-\newcommand{\ints}{\mathbb{Z}}
 \newcommand{\ptl}{\partial}
@@
 
-%% =====================
-%% AASTeX utilities etc.
-%% =====================
-
-% Object linking: https://aas.org/object-linking/introduction-object-linking
-% \objectname[SNR G120.2+01.4]{Tycho's SNR}
-% \objectname[M1]{Crab nebula}
-% \object{NGC 6397}
-
-% Dataset linking: https://aas.org/data-sets/data-set-linking
-% \dataset{ADS/Sa.ASCA\#X/86008020}
-% \dataset[ADS/Sa.HST#Y0Q70101T]{HST FOS spectrum}
-
-% Possibly useful items:
-% \footnote{footnote}
-% \notetoeditor{note}  % Appears in manuscript footnotes, not in preprints
-% \begin{mathletters}  % Add lettering to -eqnarrays- align, eqns
-% \end{mathletters}  % e.g., number (4a), (4b) vs. (4), (5)
-% \url{http://google.com}
-
-% AASTeX symbol macros
-% A 90\degr~angle, an ion: \ion{Ca}{2}, \slantfrac{40}{59} (why slantfrac?).
-
-% Figures, tables
-% AASTeX provides \plotone{z.eps}, \plottwo{a.eps}{b.eps}, \plotfiddle (?!)
-
-% Tables -- refer to author guide / sample.tex when needed.
+% This paper
+\newcommand{\tsup}{\textsuperscript}
+\newcommand{\Chandra}{\textit{Chandra}\ }
+\defcitealias{ressler2014}{R14}
 
@@
 
-% ========================
-% Title, authors, abstract
-% ========================
 \title{Energy Dependent X-Ray Rim Width in Tycho's Supernova Remnant}
@@
 
-\altaffiltext{1}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
-\altaffiltext{2}{Dept. Physics, University of California,
-    Berkeley, CA 94720, USA}
-\altaffiltext{3}{Dept. Physics, North Carolina State University,
-    Raleigh, NC 27695, USA}
+\affil{
+\tsup{1}NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA \\
+\tsup{2}Dept. Physics, University of California, Berkeley, CA 94720, USA \\
+\tsup{3}Dept. Physics, North Carolina State University, Raleigh, NC 27695, USA
+}
+
+%\altaffiltext{1}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
+%\altaffiltext{2}{Dept. Physics, University of California,
+%    Berkeley, CA 94720, USA}
+%\altaffiltext{3}{Dept. Physics, North Carolina State University,
+%    Raleigh, NC 27695, USA}
 \altaffiltext{4}{CRESST, University of Maryland, College Park, MD 20742}
@@
 amplification but require energy-independent rim widths. We measured rim widths
-around Tycho's supernova remnant in 5 energy bands using a 750 ks Chandra
+around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
 observation. Rims narrow with increasing energy, favoring loss-limited
@@
 plasma turbulence in astrophysical shocks.
-\note[Aaron]{Keywords from Sean's paper}
 \end{abstract}
 
+% Six keywords, alphabetical order
 \keywords{acceleration of particles ---
@@
     ISM: supernova remnants ---
+    shock waves ---
     X-rays: ISM}
@@
 % ============
-\note[Aaron]{a lot of preliminary text copy-pasted from poster or my own
-notes, so explanations may be a bit simplistic}
-
 \section{Introduction}
 
+% -------------------
+% Background / review
+% -------------------
+\subsection{What are thin rims?}
+
+Define thin rims (hereafter, thin rims).
 \note[Aaron]{most text below is copy-pasted from my own notes -- explanation
 may be too simplistic}
+
+Somewhere here, define upstream/downstream of shock (makes sense in reference
+frame of shock).
 
@@
 and energy-dependent widths, set by:
-\begin{itemize}
-  \item \emph{synchrotron losses}.  At the shock, high energy electrons
-  efficiently radiate harder x-ray photons.  As electrons are advected
-  downstream while radiating, they radiate at lower energies and lose energy
-  more slowly.  Synchrotron losses depend on (1) the initial electron energy
-  distribution, and (2) the gradual decrease of electron energies downstream of
-  the shock.
-  \item \emph{diffusion}.  Random motion with respect to bulk plasma advection.
+(1) \emph{synchrotron losses}.  At the shock, high energy electrons efficiently
+radiate harder x-ray photons.  As electrons are advected downstream while
+radiating, they radiate at lower energies and lose energy more slowly.
+Synchrotron losses depend on the initial electron energy distribution and the
+gradual decrease of electron energies downstream of the shock.
+(2) \emph{diffusion}.  Random motion with respect to bulk plasma advection.
 Higher energy electrons diffuse and travel further downstream than would be
 expected from pure advection; hence, higher energy radiation may be seen
-  farther downstream of the shock than expected.
-  Higher energy particles may also diffuse \emph{ahead} of the shock, possibly
-  giving rise to a so-called ``cosmic-ray shock precursor''.  Note that this is
-  distinct from radiative precursors \citep[e.g.,][]{ghavamian2000}.
-\end{itemize}
+farther downstream of the shock than expected. Higher energy particles may also
+diffuse \emph{ahead} of the shock, possibly giving rise to a so-called
+``cosmic-ray shock precursor''.  Note that this is distinct from radiative
+precursors \citep[e.g.,][]{ghavamian2000}.
 
-\subsection{Abbreviated review of prior work for context}
+Mention relevance to: cosmic ray acceleration, turbulent field amplification,
+(note assumptions in re proton/electron spectra).  Cut-off energy of injected
+electrons?  Broadly, all astrophysical shock processes: AGN jets, galaxy
+clusters \citep{van-weeren2010}, PWNe, et cetera.  Usual background,
+utility spiel.
 
-Basic observables \citep[e.g.,][]{bamba2003, bamba2005-hist, bamba2005-vela,
-parizot2006} and consequences.
+% ------------------------
+% Measurements and meaning
+% ------------------------
+\subsection{Prior measurements and inferred physical parameters}
 
+Models for particle transport.  Bohm, sub-Bohm diffusion.
 Testable model predictions of magnetic damping \citep{pohl2005}.
 
-\citet{ressler2014} found rim narrowing in the remnant of SN 1006,
+Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
+bamba2005-hist, bamba2005-vela, parizot2006} and consequences.
+Conclusion that magnetic fields are amplified.
 
 Equivocal results by \citet{araya2010} for Cas A.
+\citet{ressler2014} found rim narrowing in the remnant of SN 1006.
 
-\subsection{Our work}
+% -----------
+% Tycho's SNR
+% -----------
+\subsection{Tycho's SNR}
+Why Tycho's supernova remnant (hereafter, Tycho)?
 
-We make measurements to distinguish between these two end member scenarios.
-\note[Aaron]{paper roadmap} First we review our measurements,
-explain the relevant model physics and governing equations,
-explain our fitting procedure.
+Like SN 1006, Tycho has well defined synchrotron rims associated with expansion
+into a low-density ISM \note[Aaron]{justification: high density ISM would
+prevent the forward shock from running ahead of the thermal ejecta?}.
+\citet{williams2013} favor mean pre-shock ISM density $\abt 0.2 \unit{cm^{-3}}$
+from \textit{Spitzer} observations of shocked ISM dust emission,
+\note[Aaron]{is this proton or electron density?  Or are they equal pre-shock?
+Text mentions $n_e = 1.2 n_p$ \emph{post}-shock.}
+consistent with Tycho's X-ray expansion \citep{katsuda2010}.
+Compare w/ SN 1006 pre-shock density $n_p \abt 0.15$--$0.3 \unit{cm^{-3}}$
+\citep{raymond2007, heng2007, winkler2013}.
 
-Then we discuss the implications of our fits and models
+Like all historical SNe, Tycho is close enough that we
+can spatially resolve these rims with \Chandra and say something useful.
 
-% ============
-% Observations
-% ============
-\section{Observations}
+Any other remarks? (comparison to core-collapse SNe? no compact object to mess
+things up? or is that flatly trivial)
 
-We used archival \textit{Chandra} observations of Tycho
-(\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs 10093--10097},
-\dataset[ADS/Sa.CXO\#obs/10902]{10902--10906})
-obtained with the ACIS-I CCD between 2009 Apr 11 and 2009 May 5.
-The total exposure time is $734 \unit{ks}$.
-The data are divided into five energy bands:
-0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
-We excise counts between 1.7--2 keV to avoid \ion{Si}{13} (He$\alpha$) line
-emission prevalent in the remnant's thermal ejecta.
+% -------------
+% Paper roadmap
+% -------------
+\subsection{Our work (paper roadmap)}
 
-Thirteen regions were selected with the following criteria in mind:
-\note[Aaron]{itemized lists are just for outlining}
-\begin{itemize}
-    \item Nonthermal filaments should be singular and localized (i.e., either
-        no overlapping or completely overlapping rims -- this rules out parts
-        of NE limb)
-    \item Nonthermal filaments should have sufficient signal-to-noise ratio
-        that we can identify a clear FWHM in all bands (rules out a lot of
-        faint southern wisps)
-    \item Avoid plumes of thermal emission: identify spatially from images,
-        esp. in lower energy bands (0.7--1 keV, 1--2 keV)
-        (e.g.,~\ref{fig:snr}, eastern side), identify spectrally from emission
-        lines.
-\end{itemize}
+We make measurements to distinguish between the two end member scenarios.
+Our procedure, in both measurement and rim width modeling, follows that of
+\citet{ressler2014} (hereafter, \citetalias{ressler2014}) with only slight
+modifications.
+We first select regions around Tycho's forward shock for analysis, measure
+rim widths, and verify that rim spectra are free of thermal line emission.
+Using two models for particle transport, we fit measured widths...
 
-\begin{figure}
-    \plotone{figures/f0-snr.eps}
-    \caption{RGB image of Tycho with region selections overlaid.  Bands are
-    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue)}
-    \label{fig:snr}
-\end{figure}
+We discuss the implications of our fits and models for magnetic shock
+amplification (lending credence to previous estimates, in disfavoring magnetic
+field amplification), and discuss particle diffusion/acceleration at the shock.
 
-Discuss point-spread function if that may be a point of contention.
-Show that it is not a problem for us (simply say that all rims are at
-least ~1 arcsec and hence are spatially resolved? Compare,
-\citet{bamba2005-hist} measured upstream/downstream scale widths separately?)
+Any further results (constraints on precursors, etc).
 
-\subsection{Filament width measurements}
-\begin{figure*}
-    \plotone{figures/f0-prfs.pdf}
-    \caption{Some semblance of a caption.}
-    \label{fig:profiles}
-\end{figure*}
+Consequences, implications, why is this worthwhile?
 
-\subsection{Filament spectra}
+% =============================
+% Transport models, observables
+% =============================
+\section{Transport models}
 
-And we shall purify the remnant's rims
-that they may show us how they do thin
-discriminating damped models.
+We first briefly review the models we consider for particle transport; a fuller
+exposition is given by \citetalias{ressler2014}.
 
-\begin{figure}
-    \plotone{figures/f0-spec.pdf}
-    \caption{Another caption \citep{fermi1949}}
-    \label{fig:spec}
-\end{figure}
-
-Finally, here are some numbers!
-
-%\begin{table}
-%\end{table}
-
-% =======================
-% Filament width modeling
-% =======================
-\section{Filament width models}
-
-Cite \citet{ressler2014} vigorously here.  Just present the governing transport
-equations (with variables), namely that from:
+Just present the governing transport equations.  From:
 \[
@@
 \]
-and by random selection of the source/sink term $C$ we obtain either a
+and by selection of the source/sink term $C$ we obtain either a
 simplified model:
-\begin{equation}
+\begin{equation} \label{eq:simp-mod}
     v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
@@
 \end{equation}
-where this is equation (6) of \citet{ressler2014}; we also look at
-\begin{equation}
+where this is equation (6) of \citetalias{ressler2014}; we also look at
+\begin{equation} \label{eq:full-mod}
     v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
@@
 \end{equation}
-which is equation (12) of \citet{ressler2014}.
+which is equation (12) of \citetalias{ressler2014}.
 
-% ===================
-% Results (best fits)
-% ===================
+\note[Aaron]{EXPLAIN what the equations mean.  How do we eventually back out a filament
+shape, filament width?  Just a few sentences.}
 
+Bibdesk -- mark up all the papers I've really gone through and understood.
+Then, add the relevant citations and notes, to be sure I haven't missed or
+misunderstood anything.
+
+% ============
+% Observations
+% ============
+\section{Observations}
+
+% TODO go through and double check tenses.
+
+We measured synchrotron rim widths from an archival \Chandra
+ACIS-I observation of Tycho
+(RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
+between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
+\dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
+\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
+The total exposure time is $734 \unit{ks}$.
+Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
+unbinned with ACIS spatial resolution $0.492\arcsec$.
+Merged and corrected events were divided into five energy bands:
+0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV;
+we excluded 1.7--2 keV counts to avoid \ion{Si}{13} (He$\alpha$) line
+emission, prevalent in the remnant's thermal ejecta, which could contaminate
+our nonthermal profile measurements.
+
+We selected 13 regions in 5 distinct filaments around Tycho's shock
+(Figure~\ref{fig:snr}) based on the following criteria:
+(1) filaments should be singular and localized; multiple filaments must not
+overlap or completely overlap (rules out parts of NE limb);
+(2) filaments should have clear FWHMs in all bands, compared to background
+signal or downstream thermal emission (rules out some faint southern wisps);
+(3) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
+images; this rules out, e.g., areas of strong nonthermal and thermal emission
+on Tycho's eastern limb.
+
+\begin{figure}
+    \plotone{figures/f0-snr.eps}
+    \caption{RGB image of Tycho with region selections overlaid.  Bands are
+    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
+    \note[Aaron]{Temporary figure; regions need re-numbering.}}
+    \label{fig:snr}
+\end{figure}
+
+Discuss point-spread function if that may be a point of contention.
+Show that it is not a problem for us (simply say that all rims are at
+least ~1 arcsec and hence are spatially resolved? Compare,
+\citet{bamba2005-hist} measured upstream/downstream scale widths separately?)
+
+% --------------------------
+% FWHM measurement procedure
+% --------------------------
+\subsection{Filament width measurements}
+
+We obtained radial intensity profiles by integrating along the shock in each
+region.  Intensity profiles peak sharply at/behind the shock, demarcating our
+thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
+and then fall off until thermal emission from ejecta picks up at Tycho's
+``contact discontinuity'' \citep{warren2005}.
+
+We fit rim profiles, obtained by integrating intensity along the shock in each
+region, to a piecewise two-exponential model:
+\begin{equation} \label{eq:prof}
+    h(x) =
+    \begin{cases}
+        A_u \exp \left(\frac{x_0 - x}{w_u}\right) + C_u, &x \geq x_0 \\
+        A_d \exp \left(\frac{x - x_0}{w_d}\right) + C_d, &x < x_0
+    \end{cases}
+\end{equation}
+where $h(x)$ is profile height and $x$ is radial distance from remnant center.
+The rim model, which we emphasize is strictly empirical, has 6 free parameters
+$A_u, x_0, w_u, w_d, C_u, C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
+continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
+bamba2005-hist} and differs slightly from that of \citetalias{ressler2014}.
+To fit only the nonthermal rim in each intensity profile, we smoothed profiles
+with a 21-point ($\abt 10\arcsec$) Hanning window and bounded the fit
+domain at the first local data minimum downstream of rim peak; the fit domain
+extends upstream to the region's outer edge.
+
+\begin{figure}
+    \plotone{figures/f0-prfs.pdf}
+    \caption{Profile fits for Region 1}
+    \label{fig:profiles}
+\end{figure}
+
+From the fitted profiles we extracted a full width at half maximum (FWHM) for
+each region and each energy band.
+\note[Aaron]{We did NOT subtract out $\min(C_u, C_d)$ before measuring FWHM
+(fix this?).  May mention effect of using slightly different models for FWHMs}
+We could not resolve a FWHM in regions 2, 6, 8, 9, and 11 \note[Aaron]{KEEP
+UPDATED} at 0.7--1 keV (Table~\ref{tab:flmt2} \note[Aaron]{UPDATE depending on
+how we present/tabulate FWHMs}); in these regions, the downstream FWHM bound
+would extend outside the fit domain.  We were able to resolve FWHMs for all
+regions at higher energy bands (1--7 keV).
+
+To estimate FWHM uncertainties, we horizontally stretched each best-fit
+profile by mapping radial coordinate $x$ to
+$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
+parameter; this yields a new profile $h'(x) = h(x'(x))$.
+We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
+yielding confidence limits on our measured FWHMs
+
+% ----------------
+% Filament spectra
+% ----------------
+\subsection{Filament spectra}
+
+As a ``back-verification'', we check that our rims' X-ray spectra
+are clear of thermal line emission.
+
+In each radial profile, we select an interval containing FWHM bounds from all
+energy bands.  We
+
+Each rim is divided into an upstream
+
+From our model fits and we divide the rim into an upstream and downstream region;
+the
+
+And we shall purify the remnant's rims\\
+that they may show us how they do thin\\
+discriminating damped models.
+
+\begin{figure}
+    \plotone{figures/f0-spec.pdf}
+    \caption{Spectra from Region 1 (I think?)}
+    \label{fig:spec}
+\end{figure}
+
+This also gives a post-hoc / further filter on intermediate results --
+we can quantify the thermal emission...
+
+We further constrain thermal emission by checking that spectral fits
+favor pure continuum emission over continuum with Gaussian components for
+\ion{Si}{13} and \ion{S}{15} He$\alpha$ lines at $\abt 1.8$, $2.4$ keV.
+
+HERE I should mention any upper bounds on spectral lines (Equivalent width or
+what have you).  Since this is not a ``result'', being ancillary to our work.
+
+% -------------
+% Model fitting
+% -------------
+\subsection{Filament model fitting}
+
+Explain why we are fixing $\mu$.
+Explain why we also give results with $\eta_2$ fixed at $1$.
+
+To perform fits, we tabulated a large grid for fixed values of $\mu$ and shock
+velocity $v_s$.
+
+If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10 \unit{mG}$ (for Tycho),
+we deem it effectively unconstrained.
+
+A few remnant-specific parameters enter into the model calculations.  We take
+electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
+\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
+remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
+shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
+\citep{green2009}.  Tycho's forward shock velocity varies azimuthally by up to
+a factor of 2; we interpolate the data of \citet{williams2013} to estimate
+individual shock velocities for each of our regions.
+
+As the full continuous loss model must be numerically solved, its predicted
+rim widths are subject to resolution error in the numerical integrals.  We
+chose our integration resolutions such that the fractional error associated
+with halving/doubling our resolution is less than $1\%$ for the
+parameter space relevant to our filaments. \note[Aaron]{rewrite -- unclear.
+Need to verify $1\%$ claim + check Pacholczyk table resolution...}
+
+% =======================
+% Results, FWHMs and fits
+% =======================
 \section{Results}
 
-Let's just say if any fit runs to $\eta_2 = 10^5$ or $B_0 = 10$ mG (for Tycho),
-we deem it effectively unconstrained.
+We present results here.  Explain a bit about how we divvy up / present the
+results.  Also, for each region, give the relevant shock velocity value.  Or, a
+range of values.
+We do X to the FWHMs (geometric/arithmetic average) within each filament.
+We also consider global FWHMs average.
+
+% --------------------
+% FWHM results, tables
+% --------------------
+\subsection{Measured FWHMs, energy dependence, etc}
+
+\begin{table*}
+\scriptsize
+\centering
+\caption{Filament 2 full width at half max measurements.
+Exponent $m_E$ estimated point to point.\label{tab:flmt2}}
+\input{tab-fwhms.tex}
+\tablecomments{Mean FWHMs computed by arithmetic mean, errors from blah}
+\end{table*}
+
+Table~\ref{tab:flmt2} lists some numbers from Filament 2.  As previously noted
+we could not resolve FWHMs for some regions in the 0.7--1 keV band.
+
+Error estimates / magnitudes.
+
+Mention the number of counts.  This might impact our decision to go back and
+slice regions smaller (if we do that).
+
+% -------------------------
+% Model fit results, tables
+% -------------------------
+\subsection{Model}
+
+Table reference goes here (Table~\ref{tab:fit1}).
+Explain error values on parameters.
 
 \begin{table}
-% Here I'm following the AASTeX sample...
-%\tabletypesize{\scriptsize}
+\centering
 \caption{Full model best fit parameters, region 1.\label{tab:fit1}}
-\begin{tabular}{@{}rllr@{}}
-\toprule
-{} & \multicolumn{3}{c}{Region 1} \\
-\cmidrule(l){2-4}
-$\mu$ (-) & $\eta_2$ (-) & $B_0$ ($\mu$G) & $\chi^2$\\
-\midrule
-0.00 & ${19.1}^{+19}_{-7.1}$ & ${784}^{+1.2 \times 10^{2}}_{-72}$ & 57.5590\\
-0.33 & ${56}^{+75}_{-29}$ & $930^{+190}_{-140}$ & 34.6006\\
-0.50 & ${92}^{+160}_{-54}$ & ${1010}^{+260}_{-180}$ & 25.5737\\
-1.00 & ${370}^{+3300}_{-310}$ & ${1260}^{+4500}_{-440}$ & 9.7750\\
-1.50 & ${23}^{+32}_{-10}$ & ${623}^{+130}_{-67}$ & 8.7937\\
-2.00 & ${11.4}^{+5.2}_{-3.3}$ & ${512}^{+34}_{-26}$ & 9.5862\\
-\bottomrule
-\end{tabular} 
+\input{tab-fits.tex}
 \end{table}
-
-Table reference goes here~\ref{tab:fit1}.
 
@@
 
+Magnetic field amplification numbers -- how do they compare with previous
+studies?  What is the azimuthal variation (and significance thereof)?
+
+Diffusion -- sub-Bohm diffusion?
+
+\subsection{Comparisons to Cas A (pulled from Sean's \LaTeX\ source)}
+
+\note[Aaron]{for my own reference/reading/thinking (temporary)}
+
+A detailed application of our results to other SNRs such as Cas A will
+require much more extensive analysis, but we can use the published
+filament widths of Araya et al. (2010) for Cas A to get preliminary
+estimates of the magnetic field strength and diffusion coefficient by
+applying our model. In their data, it appears that the filaments in
+Cas A shrink by a factor of $\sim 0.8$ between 0.3 and 3 keV, while the
+filament widths appear to be energy-independent between 3 and 6 keV.
+Qualitatively, this is consistent with the loss-limited model, as our
+parameter $m_{\rm E}$ is predicted to decrease with energy.  For the
+lower energy range of 0.3--3 keV, reproducing $m_{\rm E}\sim -0.1$
+(equivalent to the factor of 0.8 drop in size) requires magnetic
+fields on the order of 200-500 $\mu$G and diffusion coefficients about
+$5 \times D_{\rm Bohm}$(3 keV), about an order of magnitude higher
+than the values one obtains by neglecting the energy dependence. One
+can also see directly from Figure~\textbf{?!} that $\mu < 1$ models
+of the diffusion coefficient are excluded for $m_{\rm E}\sim -0.1$.
+
+To quickly compare how our results will differ from those of other authors, we
+applied the analytic approximation of Equation 22 and Equation 9 to the FWHMs
+presented by Araya et al. (2010) for Cas A. Here we used $m_{\rm E} = \log(
+{\rm FWHM}(3keV)/{\rm FWHM}(.3keV))/\log(10)$ and fit the filaments at a photon
+energy of 3 keV.  Hence $\eta_3 \equiv D/D_{\rm Bohm}(3 keV)$. Using the same
+parameters, our results are shown in Table~\ref{tab:Araya}. To fit the energy
+dependence of the FWHM (i.e. $m_{\rm E}$), we required higher diffusion
+coefficients and, consequently, magnetic fields about an order of magnitude
+higher than their results. We note here that values of $\mu<1$ were unable to
+reproduce the data and that the diffusion coefficients cited by Araya et al.
+(2010) are below the minimally allowed Bohm value ($\eta_3 = 1$).
+
+We intended this comparison solely as a qualitative analysis, and thus did not
+rigorously keep track of uncertainties or extend the comparison to the full
+numerical calculation. The conclusion is clear, however, which is that
+considering the measured value of $m_{\rm E}$ can have a dramatic effect.
+
+\begin{table*}[h]
+\caption{Best fit parameters for the filaments of Cas A based on data from
+Araya et. al (2010) in varying values of $\mu$ (Approximate Analytic Results)
+Dashes denote places where fits were unobtainable.}
+\centering
+\begin{tabular}{c c c c c c c c c}
+\hline \hline
+  &\multicolumn{2}{c}{$\mu = 1$} & \multicolumn{2}{c}{$\mu = 1.5$} & \multicolumn{2}{c}{$\mu = 2$} & \multicolumn{2}{c}{Araya et. al} \\
+  & & & & & &  &\multicolumn{2}{c}{($\mu = 1$)} \\
+$Filament$ &$\eta_{3}$ & $B_{0}$ &$\eta_{3}$ & $B_{0}$ & $\eta_{3}$ & $B_{0}$& $\eta_{3}$ & $B_{0}$ \\ [.5ex]
+1 & 6.5  & 750 $\mu$G & 2 & 567 $\mu$G & 1.1 & 506 $\mu$G & 0.12 & 72 $\mu$G \\
+2 & 3.6 & 710 $\mu$G & 1.4 & 582 $\mu$G & - & - & 0.02 & 37 $\mu$G\\
+3 & 3.2 &  710 $\mu$G& 1.3 & 589 $\mu$G& - & - & 0.02 & 53 $\mu$G\\
+4 & 3.1& 515 $\mu$G & 1.3 & 430 $\mu$G & -& - & 0.02 & 40 $\mu$G \\
+5 & 10.7 & 1163 $\mu$G & 2.5 & 809 $\mu$G & 1.3&  706 $\mu$G & 0.025 & 52 $\mu$G \\
+6 & 5.7 & 844 $\mu$G & 1.9 & 650 $\mu$G  & 1 & 583 $\mu$G & 0.1 & 56 $\mu$G \\
+7 & 8.3 & 872 $\mu$G & 2.2 & 635 $\mu$G& 1.2 & 560 $\mu$G & 0.15 & 66 $\mu$G\\
+8 & 13 & 1010 $\mu$G & 2.7 & 738 $\mu$G & 1.4 & 639 $\mu$G & 0.02 & 35 $\mu$G\\
+9 & 4.7 & 605 $\mu$G & 1.7 & 479 $\mu$G & - & -& 0.02 & 29 $\mu$G\\
+
+\hline
+\hline
+\end{tabular}
+\label{tab:Araya}
+\end{table*}
+
+\subsection{End of Sean's Cas A analysis}
+
+Lalala.
+
 % ==========
@@
 
-In conclusion, crazy B field amplification is not that weird.  Magnetic damping
-can be ruled out and our result is robust throughout the remnant.
+In conclusion, crazy B field amplification is not that weird.
+Magnetic damping can be ruled out and our result is robust throughout the remnant.
 
+% ================
+% Acknowledgements
+% ================
 \acknowledgments
@@
 The scientific results reported in this article are based on data obtained from
-the Chandra Data Archive.
+the \Chandra Data Archive.
+This research has made use of NASA's Astrophysics Data System.
 
@@
 
+% ========
+% Appendix
+% ========
 \appendix
 
-\section{Appendix material}
+For comparison to \citetalias{ressler2014}, we present our full model results
+employing 2 energy bands (as in \citetalias{ressler2014}) and all 3 energy
+bands (0.7--1, 1--2, 2--7 keV).  The simple model results are identical,
+although the errors obtained from my procedure are larger.
 
-Appendix text if so desired.
+\section{SN 1006 results, 2 energy bands}  % Use numberedappendix option for emulateapj
 
-\bibliographystyle{apj}  % AASTeX journal macros (for abbrevs) supplied by ADS
+Tables tables tables tables
+
+\section{SN 1006 results, 3 energy bands}
+
+Tables tables tables tables
+
+\section{Discussion}
+
+Lalalalala.  Beautiful numbers!
+
+% ==========
+% References
+% ==========
+\bibliographystyle{apj}  % AASTeX journal macros are supplied in ADS entries
 \bibliography{refs-snr}

### 2014-09-09 code-models/models_exec.py

@@ -126,9 +126,6 @@ class Fitter(object):
         return models.simple_fit(self.snr, self.kevs, self.data, self.eps,
                                  mu, **kwargs)
 
-    # TODO rminarc issue to be addressed (!)
-    # TODO stderr scaling issue to be addressed (!!)
-
     def get_fit(self, mu, appr, **kwargs):
         """Simple or full fit + manual 1-sigma errors
         **kwargs passed to models.full_fit, if appr='full'
@@ -160,8 +157,6 @@ class Fitter(object):
 
         return res
 
-    # TODO rminarc issue must also be addressed by error searching...
-
     def get_errs(self, res, appr, method='manual', ci_vals=(0.683,), **kwargs):
         """Find dictionary of confidence intervals
 
@@ -173,7 +168,7 @@ class Fitter(object):
             **kwargs are passed to relevant functions
                 method='lmfit': maxiter=200, prob_func=None
                                 (see lmfit.conf_interval docstring)
-                method='manual': eps=None, adapt=True, anneal=True
+                method='manual': adapt=True, anneal=True
                                  (anneal keyword only if appr='full')
         Output:
             confidence interval dictionary
@@ -188,7 +183,8 @@ class Fitter(object):
                 if conf_intv != 0.683:
                     print ('Warning: requested CI={}. But, stderr only '
                            'gives 68.3% errors').format(conf_intv)
-                return res.params[pstr].stderr, res.params[pstr].stderr
+                v, s = res.params[pstr].value, res.params[pstr].stderr
+                return v - s, v + s
         elif method == 'manual':
             f = lambda *args: self.get_bounds(*args, appr=appr,
                                 verbose=self._verbose, **kwargs)
@@ -206,8 +202,6 @@ class Fitter(object):
     # ----------------------------
     # Model specific error finding
     # ----------------------------
-
-    # TODO: review TODOs throughout error seeking method.
 
     def get_bounds(self, conf_intv, res, pstr, appr='full', anneal=True,
                    **kwargs):
@@ -239,35 +233,36 @@ class Fitter(object):
 
         # Best fit quantities
         p_init = res.params[pstr].value
-        p_stderr = res.params[pstr].stderr
[…]

### 2014-09-09 code-models/models_exec_manual.py

@@ -1,0 +1,131 @@
+"""
+Code to work with full model code interactively
+
+Aaron Tran
+September 2014
+"""
+
+from __future__ import division
+
+import matplotlib.pyplot as plt
+import numpy as np
+
+import lmfit
+
+def main():
+    pass
+
+def manual_err(fobj, conf_intv):
+    """Interactively find errors for (fobj or user-provided) best fit
+
+    fobj.get_fit(...)
+    for each free parameter:
+        (i) user fixes one param's value
+        (ii) user inputs guesses for all remaining free params
+        (iii) compute chi-sqr value (whether from user guesses, or a fit
+             starting from user guesses)
+        (iv) if chi-sqr value is LESS than error threshold,
+              go back to (i) and choose new fixed value
+        (v) if chi-sqr value is GREATER Than error threshold,
+            give user choice to 1. give new guesses for free params,
+            2. try refitting, 3. go back to (1) and choose new fixed value,
+        (vi) in BOTH cases, give user option to STOP and keep this best
+             param
+        (vii) also do this TWICE to get upper/lower bounds
+    return error bounds...
+    """
+
+
+def manual_fit(snr, kevs, data, eps):
+    """Interactively prompts user for values of B0, eta2, mu
+    Prints FWHMs, residuals, and chi-squared values in the process
+    And, plots the data + fitted model
+    Also prints m_E, computed point to point (just for comparison)
+
+    Note: doesn't really deal with bad input
+
+    Input: snr object and data (x, y, eps) to be fitted
+    Output: lmfit.Parameters object with best obtained fit values
+    """
+
+    print 'Manual fitting routine: enter q to print best fit and quit.\n'
+
+    chisq_best = float('inf')
+    w_model_best = None
+    p_best = None
+
+    while True:
+        B0 = _get_float('Enter B0 (G): ')
+        eta2 = _get_float('Enter eta2 (-): ')
+        mu = _get_float('Enter mu (-): ')
+
+        if any(np.isnan([B0, eta2, mu])):
+            break  # Received exit/quit request
+
+        p = lmfit.Parameters()
+        p.add('B0', value=B0)
+        p.add('eta2', value=eta2)
+        p.add('mu', value=mu)
+
+        adj = _get_float('Change model settings? Enter 0/1 for no/yes: ')
+        if adj == 0:
+            w_model = width_cont(p, kevs, snr)
[…]

### 2014-09-09 code-models/snr_catalog.py

@@ -45,6 +45,39 @@ def kpc2cm(x):
 # Set SNR physical parameters here
 # ================================
 
+def make_kepler():
+    """Physical parameters, model/fit settings for Tycho's SNR
+    WARNING: if darc is changed, must change vs as well!
+    """
+    k = SupernovaRemnant('Kepler')
+    
+    kepler.dkpc = 4.0  # Distance to remnant in kpc (!) TODO verify
+                       # 4kpc from Vink (2008) kinematic study
+                       # Could be up to 7 kpc?!?!?! (Patnaude et al., 2012)
+    kepler.rsarc = 180 # Shock radius (arcsec) from Green's SNR catalog
+    kepler.s = 2.28  # e- spectrum index, 2.3 = 2*0.65 + 1;
+                     # 0.64 = radio spectral index, Green's SNR catalog
+                     # TODO get a source on this?!
+
+    kepler.vs = 4.2e8  # Shock velocity, cm/s
+                       # TODO verify, 4.2e8 from Vink (2008) kinematic study
+    kepler.cratio = 4.0  # Compression ratio, strong adiabatic shock (R-H)
+
+    # Model grid settings, resolutions
+    kepler.icut = True
+    #kepler.rminarc = 20  # Default rminarc, arcsec
+    kepler.irmax = 400  # Currently unchanged from SN 1006
+    kepler.iradmax = 100
+    kepler.ixmax = 500
+
+    # Fitting default initial guesses, bounds
+    #kepler.par_init = {'mu': 1.0, 'eta2': 1.0, 'B0': 300e-6}
+    #kepler.par_lims = {'mu': (0., 2.),
+    #                  'eta2': (1e-16, 1e5),  # model code div by zero on eta2=0
+    #                  'B0': (1e-6, 1e-2)}
+
+    return kepler
+
 def make_tycho():
     """Physical parameters, model/fit settings for Tycho's SNR
     WARNING: if darc is changed, must change vs as well!
@@ -55,6 +88,12 @@ def make_tycho():
     tycho.rsarc = 240  # Shock radius (arcsec) from Green's SNR catalog
     tycho.s = 2.3  # e- spectrum index, 2.3 = 2*0.65 + 1;
                    # 0.65 = radio spectral index
+                   # TODO is this right?  One src. is Eriksen et al. 2011
+                   # which cites Kothes et al. 2006, for alpha=0.65
[…]

### 2014-09-09 manuscript/regen.sh

@@ -1,7 +1,7 @@
 #!/bin/sh
 
-pdflatex ${1}.tex
-bibtex ${1}
-pdflatex ${1}.tex
-pdflatex ${1}.tex
-open ${1}.pdf
+pdflatex tycho-paper.tex
+bibtex tycho-paper
+pdflatex tycho-paper.tex
+pdflatex tycho-paper.tex
+open tycho-paper.pdf

### 2014-09-10 manuscript/tycho-paper.tex
Tablepalooza paper draft, fit avg Tycho fwhms
Parse lots of manual output (code coming soon) to add tables to draft
Set up Tycho fitting ipynb to work on average FWHMs

@@
-\documentclass[manuscript]{aastex}  % one-column, double-spaced
+% \documentclass[manuscript]{aastex}  % one-column, double-spaced
 % \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
-% \documentclass[iop, apj, twocolappendix]{emulateapj}
+\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
+% \documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 
-\title{Energy Dependent X-Ray Rim Width in Tycho's Supernova Remnant}
+\title{Energy Dependent X-Ray Rim Widths in Tycho's Supernova Remnant}
 
@@
 Compare w/ SN 1006 pre-shock density $n_p \abt 0.15$--$0.3 \unit{cm^{-3}}$
-\citep{raymond2007, heng2007, winkler2013}.
+\citep{raymond2007, heng2007, winkler2013}.  \note[Aaron]{ISM gradients?}
 
@@
 
-Any other remarks? (comparison to core-collapse SNe? no compact object to mess
-things up? or is that flatly trivial)
+Previous estimates of Tycho fields/diffusion (something similar to Sean's table
+for SN 1006?).  CR acceleration.
 
@@
 
-\note[Aaron]{EXPLAIN what the equations mean.  How do we eventually back out a filament
-shape, filament width?  Just a few sentences.}
+Explain how the transport models constrain diffusion via $m_E$, define $m_E$.
+Explain how we back out a filament shape/width from these models
 
-Bibdesk -- mark up all the papers I've really gone through and understood.
-Then, add the relevant citations and notes, to be sure I haven't missed or
-misunderstood anything.
+\subsection{Magnetic damping}
+
+We also consider a magnetically damped field of form
+\[
+    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
+\]
+following \citetalias[Section 3.2]{ressler2014}.
 
@@
 % TODO go through and double check tenses.
-
+\note[Aaron]{inconsistent present/past tense usage}
 We measured synchrotron rim widths from an archival \Chandra
@@
 \dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
-The total exposure time is $734 \unit{ks}$.
+The total exposure time was $734 \unit{ks}$.
 Level 1 \Chandra data were reprocessed with CIAO 4.6 and CALDB 4.6.1.1 and kept
@@
 \begin{figure}
-    \plotone{figures/f0-snr.eps}
+    %\plotone{figures/f0-snr.pdf}
+    \centering
+    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
     \caption{RGB image of Tycho with region selections overlaid.  Bands are
@@
 
-\begin{figure}
-    \plotone{figures/f0-prfs.pdf}
-    \caption{Profile fits for Region 1}
-    \label{fig:profiles}
-\end{figure}
-
 From the fitted profiles we extracted a full width at half maximum (FWHM) for
@@
 We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
-yielding confidence limits on our measured FWHMs
+yielding confidence limits on our measured FWHMs.
 
@@
 
-As a ``back-verification'', we check that our rims' X-ray spectra
-are clear of thermal line emission.
+We extracted and fitted spectra for all regions to confirm that our rim width
+measurements are not contaminated by thermal line emission.
+We divided each region into an upstream and downstream band.  The upstream band
+is the smallest sub-region containing FWHM bounds from all energy bands.
+The downstream band extends from the back of the rim (where the upstream band
+ends) to the rim model fit's (equation~\eqref{eq:prof}) downstream limit.
+Figure~\ref{fig:spec} plots an example profile (Region 1, 4.5--7 keV) with the
+downstream/upstream selections highlighted in light blue/gray respectively.
+We fitted spectra from each region to an absorbed power law between $0.5$ and $7$
+keV in XSPEC.
 
-In each radial profile, we select an interval containing FWHM bounds from all
-energy bands.  We
-
-Each rim is divided into an upstream
-
-From our model fits and we divide the rim into an upstream and downstream region;
-the
-
-And we shall purify the remnant's rims\\
-that they may show us how they do thin\\
-discriminating damped models.
-
-\begin{figure}
-    \plotone{figures/f0-spec.pdf}
-    \caption{Spectra from Region 1 (I think?)}
-    \label{fig:spec}
-\end{figure}
-
-This also gives a post-hoc / further filter on intermediate results --
-we can quantify the thermal emission...
-
-We further constrain thermal emission by checking that spectral fits
-favor pure continuum emission over continuum with Gaussian components for
-\ion{Si}{13} and \ion{S}{15} He$\alpha$ lines at $\abt 1.8$, $2.4$ keV.
-
-HERE I should mention any upper bounds on spectral lines (Equivalent width or
-what have you).  Since this is not a ``result'', being ancillary to our work.
+TODO?! We also fit the spectra to absorbed power law models with 1 and 2
+additional Gaussian components for \ion{Si}{13} and \ion{S}{15} He$\alpha$
+lines at $\abt 1.8$, $2.4$ keV.  We compute some equivalent width, or compare
+the goodness-of-fit with and without the additional lines, to rule out the
+presence of a line (but, cf. \citet{protassov2002} on line detection
+statistics!).
 
@@
 
+We fitted the two transport models given by Equations~\eqref{eq:simp-mod} and
+\eqref{eq:full-mod} to the measured data.  Here we present only the full
+model (equation~\eqref{eq:full-mod}) fits.  \note[Aaron]{Could we present the
+full model alone, given that the numbers / qualitative trends for both models
+are fairly similar?  In \citetalias{ressler2014} Sean used the simple model to
+build intuition and gain physical insight, to great effect.  But, will we need
+that here?}
+
 Explain why we are fixing $\mu$.
@@
 To perform fits, we tabulated a large grid for fixed values of $\mu$ and shock
-velocity $v_s$.
-
-If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10 \unit{mG}$ (for Tycho),
-we deem it effectively unconstrained.
+velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10 \unit{mG}$,
+we deem it effectively unconstrained (only a few fits do so, and only to the
+$\eta_2$ limit).
+Note that we do not allow / consider fits with $\eta_2$ negative (may be
+trivial, just note parameter bounds).
 
@@
 
-We present results here.  Explain a bit about how we divvy up / present the
-results.  Also, for each region, give the relevant shock velocity value.  Or, a
-range of values.
+Explain a bit about how we divvy up / present the results.  What values are we
+averaging, where do our errors come from?
+For each region, give the relevant shock velocity value (and a range of
+values?).
 We do X to the FWHMs (geometric/arithmetic average) within each filament.
-We also consider global FWHMs average.
 
@@
 % --------------------
-\subsection{Measured FWHMs, energy dependence, etc}
+\subsection{Rim fits, spectra, and width measurements}
 
-\begin{table*}
+We give figures and tables with rim profile fit information.
+
+\begin{figure}
+    \plotone{figures/f0-prfs.pdf}
+    \caption{Profile fits for Region 1}
+    \label{fig:profiles}
+\end{figure}
+
+\begin{table*}[h]
 \scriptsize
@@
 
+\begin{figure}
+    \plotone{figures/f0-spec.pdf}
+    \caption{Spectra from Region 1 (I think?)}
+    \label{fig:spec}
+\end{figure}
+
+Here, mention any upper bounds on spectral lines (equivalent width or w/e).
+Since this is not a ``result'', being ancillary to our work.
+
+Table of best fit chi-squares, power law indices for spectral fits...
+
 % -------------------------
@@
 % -------------------------
-\subsection{Model}
+\subsection{Model fit results}
 
-Table reference goes here (Table~\ref{tab:fit1}).
-Explain error values on parameters.
+Here are some fit results for a subset of regions, just those contained in
+Filament 1 (Table~\ref{tab:fit}).  Errors are estimated by 
+Explain error values on parameters
 
-\begin{table}
+\begin{table*}
+\scriptsize
 \centering
-\caption{Full model best fit parameters, region 1.\label{tab:fit1}}
-\input{tab-fits.tex}
-\end{table}
+\caption{Full model best fit parameters, Filament 1.
+    \label{tab:fit}}
+\input{tab-fits-flmt1.tex}
+\end{table*}
+
+Table~\ref{tab:fit-avg-fwhm} shows best fits to averaged FWHMs (averaged FWHMs
+not shown).  For FWHM errors, I use the standard error of the mean (with some
+minor nuances; I am using sample standard deviation).
+
+\begin{table*}
+\scriptsize
+\centering
+\caption{Full model best fit parameters for filament-averaged FWHMs.
+    \label{tab:fit-avg-fwhm}}
+\input{tab-fits-avg.tex}
+\end{table*}
+
+Finally, Table~\ref{tab:fit-avg-par} shows averaged best-fit parameters for
+Filament 1 only, at this time.  The parameter errors are standard errors from
+the averaging process and may reflect the presence of outliers.
+
+\begin{table*}
+\scriptsize
+\centering
+\caption{Average of best-fit parameters for individual regions
+    \label{tab:fit-avg-par}}
+\input{tab-fits-par-avg.tex}
+\end{table*}
+
+\begin{table*}
+\scriptsize
+\centering
+\caption{Full model best fit parameters, Filament ??, with $\eta_2 = 1$ fixed}
+%    \label{tab:fit-avg-par}}
+%\input{tab-fits-par-avg.tex}
+Coming soon...
+\end{table*}
 
@@
 What do all these numbers with their errors mean?
+Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
+
+How meaningful are our parameter estimates and errors?
 
@@
 
-Diffusion -- sub-Bohm diffusion?
+Diffusion -- sub-Bohm diffusion in Filament 4?
 
-\subsection{Comparisons to Cas A (pulled from Sean's \LaTeX\ source)}
+Constraints on diffusion / B field, if any.  What impact this has for models of
+B amplification etc.
 
-\note[Aaron]{for my own reference/reading/thinking (temporary)}
+% ==========
+% Conclusion
+% ==========
+\section{Conclusions}
+
+In conclusion, crazy B field amplification is not that weird.
+Magnetic damping can be ruled out and our result is robust throughout the remnant.
+
+% ================
+% Acknowledgements
+% ================
+\acknowledgments
+
+The scientific results reported in this article are based on data obtained from
+the \Chandra Data Archive.
+This research has made use of NASA's Astrophysics Data System.
+
+{\it Facilities:} \facility{CXO (ACIS-I)}
+
+\clearpage
+
+% ========
+% Appendix
+% ========
+\appendix
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+% --------------
+% SN 1006 tables
+% --------------
+\section{Full model validation, SN 1006 (DRAFT ONLY)}
+
+For comparison to \citetalias{ressler2014}, we reproduce Sean's table
+(Table~\ref{tab:sean} and present full model fits with 2 and 3 energy bands
+(Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
+We don't compare simple model results, as they are identical (only the error
+calculations differ).
+The procedure of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
+the same.  Sean used $m_E$ at 2 keV instead of the $1$--$2$ keV width for
+fitting, whereas I used both widths.  But, it should not matter much as
+the fit often has $\chi^2 \sim 0$, either way (depending on the exact
+measurements and values of $\mu$).
+
+Please take the errors with a grain of salt.  They are automatically
+generated and \textbf{have not been manually validated}.  Some values may be
+invalid, where my error-finding code failed and gave a best, conservative guess
+of the error.
+
+\begin{table}[h]
+\scriptsize
+\centering
+\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}}
+\label{tab:sean}
+\input{tab-sean.tex}
+\end{table}
+
+\begin{table*}[h]
+\scriptsize
+\centering
+\caption{SN 1006 best fit parameters, 2 highest energy bands (full model)}
+\label{tab:sn1006-2band}
+\input{tab-sn1006-2band.tex}
+\end{table*}
+
+\begin{table*}[h]
+\scriptsize
+\centering
+\caption{SN 1006 best fit parameters, 3 energy bands (full model)}
+\label{tab:sn1006-3band}
+\input{tab-sn1006-3band.tex}
+\end{table*}
+
+% ------------------
+% Sean's Cas A table
+% ------------------
+\section{Sean's Cas A comparison (DRAFT ONLY)}
+
+This is dredged from the \LaTeX source for Sean's paper, available on arXiv.
+I put this here just for my own reference.
 
@@
 energy of 3 keV.  Hence $\eta_3 \equiv D/D_{\rm Bohm}(3 keV)$. Using the same
-parameters, our results are shown in Table~\ref{tab:Araya}. To fit the energy
+parameters, our results are shown in Table~\ref{tab:araya}. To fit the energy
 dependence of the FWHM (i.e. $m_{\rm E}$), we required higher diffusion
@@
 
-\begin{table*}[h]
+\begin{table}[h]
+\tiny
+\centering
 \caption{Best fit parameters for the filaments of Cas A based on data from
@@
 Dashes denote places where fits were unobtainable.}
-\centering
-\begin{tabular}{c c c c c c c c c}
-\hline \hline
-  &\multicolumn{2}{c}{$\mu = 1$} & \multicolumn{2}{c}{$\mu = 1.5$} & \multicolumn{2}{c}{$\mu = 2$} & \multicolumn{2}{c}{Araya et. al} \\
-  & & & & & &  &\multicolumn{2}{c}{($\mu = 1$)} \\
-$Filament$ &$\eta_{3}$ & $B_{0}$ &$\eta_{3}$ & $B_{0}$ & $\eta_{3}$ & $B_{0}$& $\eta_{3}$ & $B_{0}$ \\ [.5ex]
-1 & 6.5  & 750 $\mu$G & 2 & 567 $\mu$G & 1.1 & 506 $\mu$G & 0.12 & 72 $\mu$G \\
-2 & 3.6 & 710 $\mu$G & 1.4 & 582 $\mu$G & - & - & 0.02 & 37 $\mu$G\\
-3 & 3.2 &  710 $\mu$G& 1.3 & 589 $\mu$G& - & - & 0.02 & 53 $\mu$G\\
-4 & 3.1& 515 $\mu$G & 1.3 & 430 $\mu$G & -& - & 0.02 & 40 $\mu$G \\
-5 & 10.7 & 1163 $\mu$G & 2.5 & 809 $\mu$G & 1.3&  706 $\mu$G & 0.025 & 52 $\mu$G \\
-6 & 5.7 & 844 $\mu$G & 1.9 & 650 $\mu$G  & 1 & 583 $\mu$G & 0.1 & 56 $\mu$G \\
-7 & 8.3 & 872 $\mu$G & 2.2 & 635 $\mu$G& 1.2 & 560 $\mu$G & 0.15 & 66 $\mu$G\\
-8 & 13 & 1010 $\mu$G & 2.7 & 738 $\mu$G & 1.4 & 639 $\mu$G & 0.02 & 35 $\mu$G\\
-9 & 4.7 & 605 $\mu$G & 1.7 & 479 $\mu$G & - & -& 0.02 & 29 $\mu$G\\
-
-\hline
-\hline
-\end{tabular}
-\label{tab:Araya}
-\end{table*}
-
-\subsection{End of Sean's Cas A analysis}
-
-Lalala.
-
-% ==========
-% Conclusion
-% ==========
-\section{Conclusions}
-
-In conclusion, crazy B field amplification is not that weird.
-Magnetic damping can be ruled out and our result is robust throughout the remnant.
-
-% ================
-% Acknowledgements
-% ================
-\acknowledgments
-
-The scientific results reported in this article are based on data obtained from
-the \Chandra Data Archive.
-This research has made use of NASA's Astrophysics Data System.
-
-{\it Facilities:} \facility{CXO (ACIS-I)}
-
-% ========
-% Appendix
-% ========
-\appendix
-
-For comparison to \citetalias{ressler2014}, we present our full model results
-employing 2 energy bands (as in \citetalias{ressler2014}) and all 3 energy
-bands (0.7--1, 1--2, 2--7 keV).  The simple model results are identical,
-although the errors obtained from my procedure are larger.
-
-\section{SN 1006 results, 2 energy bands}  % Use numberedappendix option for emulateapj
-
-Tables tables tables tables
-
-\section{SN 1006 results, 3 energy bands}
-
-Tables tables tables tables
-
-\section{Discussion}
-
-Lalalalala.  Beautiful numbers!
+\label{tab:araya}
+\input{tab-sean-casA.tex}
+\end{table}
 

### 2014-09-10 code-models/models_disp.py

@@ -310,51 +310,67 @@ class LatexTable(object):
                 ind += 1
         self.rows.append(self.rspec.format(*args))
 
-    # TODO this code is pretty gross
-    # Both the 2-err and 1-err case.  But it kinda does what I want.
+    # TODO this code is very gross
+    # Sept. 10 -- forget the precision business.  Let the user deal with
+    # proper rounding, report more than needed in floating pt form
 
     def fmt_num_2err(self, num, errpos, errneg):
-        """Format number w/error nicely.
-        It's imperfect and doesn't agree w/ rounding of Ressler,
-        but it's simpler this way...
-        DEAR GOD THIS CODE IS DISGUSTING
-        """
-        num_exp = int(np.floor(np.log10(num))) if num != 0. else 0
-        err_min = abs(min(errpos, errneg))
-        err_exp = int(np.floor(np.log10(err_min))) if err_min != 0. else 0
+        nstr = '{:0.3g}',format(num)
+        estr_pos = '{:0.2g}'.format(errpos)
+        estr_neg = '{:0.2g}'.format(errneg)
 
-        prec = num_exp - err_exp + 2 # Print to precision + 1, allowed by error
-        if prec <= 0:
-            prec = 1  # Enforce minimum precision
-
-        # Use string formatting to handle rounding
-        numstr = ('{:0.'+str(prec)+'g}').format(num)
-        errstr_pos = ('+{:0.2g}').format(errpos)
-        errstr_neg = ('-{:0.2g}').format(errneg)
-
-        numstr = self.expstr2latex(numstr)
-        errstr_pos = self.expstr2latex(errstr_pos)
-        errstr_neg = self.expstr2latex(errstr_neg)
-        return numstr, errstr_pos, errstr_neg
-
+        return strfl(nstr), strfl(estr_pos), strfl(estr_neg)
+    
     def fmt_numerr(self, num, err):
-        """Format number w/error nicely.
-        It's imperfect and doesn't agree w/ rounding of Ressler,
-        but it's simpler this way...
-        """
-        num_exp = int(np.floor(np.log10(num))) if num != 0. else 0
-        err_exp = int(np.floor(np.log10(err))) if err != 0. else 0
-        prec = num_exp - err_exp + 2 # Print to precision + 1, allowed by error
-        if prec <= 0:
-            prec = 1  # Enforce minimum precision
+        nstr = '{:0.3g}'.format(num)
[…]

### 2014-09-10 code-models/models_exec.py

@@ -331,7 +331,7 @@ class Fitter(object):
         """
         sgn = int(np.sign(x_lim - x0))
         self._vprint('Seeking error in {} direction;'.format(sgn),
-                     'start: {:0.4e},'.format(xgrid[idx]),
+                     'start: {:0.4e} (idx={}),'.format(xgrid[idx], idx),
                      'limit: {:0.4e}'.format(x_lim))
         if sgn == 0:
             self._vprint('Warning: sgn == 0 (?!), returning limit')
@@ -345,16 +345,26 @@ class Fitter(object):
                 xstep = xgrid[idx - sgn_srch]
             return abs(xgrid[idx] - xstep)
 
+        # KEY ASSUMPTION:
+        # if sgn < 0, then x_lim < xgrid[idx] < x0
+        # if sgn > 0, then x0 < xgrid[idx] < x_lim
 
-        f_init = f(xgrid[idx])
+        # In practice, don't worry about x_lim
+        if (sgn < 0 and xgrid[idx] < x0) or (sgn > 0 and x0 < xgrid[idx]):
+            x_init = xgrid[idx]  # xgrid[idx] gives a better start position
+        else:
+            self._vprint('Searching outside grid')
+            x_init = x0  # idx at grid edge
+
+        f_init = f(x_init)
 
         if f_init < 0:
             self._vprint('Not crossed error bound, moving forward')
-            return one_dir_root(f, xgrid[idx], x_lim, eps=get_eps(sgn),
+            return one_dir_root(f, x_init, x_lim, eps=get_eps(sgn),
                                 **kwargs)
         elif f_init > 0:
             self._vprint('Found error crossing on grid, moving back')
-            return one_dir_root(f, xgrid[idx], x0, eps=get_eps(-1*sgn),
+            return one_dir_root(f, x_init, x0, eps=get_eps(-1*sgn),
                                 **kwargs)
         else:
             self._vprint('A miracle has occurred, we are at crossing (?!)')

### 2014-09-13 manuscript/paper-tycho.tex
Kepler regions, Tycho tables & avg fwhms/errs
First round of Kepler region picks. Generate more Tycho fit tables and
compute averaged FWHMs/errors for fits. Update code to fit with only 1
free param (B0 xor eta2).  Fix misc. bugs, more work on paper

--- 2014-09-10 manuscript/tycho-paper.tex
@@
-% \documentclass[manuscript]{aastex}  % one-column, double-spaced
-% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
-\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
+% \documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
+\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
+% \documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
 % \documentclass[iop, apj, numberedappendix]{emulateapj}
@@
 \usepackage{amsmath}  % amsthm, amssymb
-\usepackage{hyperref}
 % \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
@@
 %\usepackage{pdflscape}  % rotate pages (Texlive)
+\usepackage{hyperref}
 
-\newcommand{\mt}{\mathrm}
-\newcommand{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
-\newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
-\newcommand{\ptl}{\partial}
-\newcommand{\del}{\nabla}
+\newcommand*{\mt}{\mathrm}
+\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
+\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
+\newcommand*{\ptl}{\partial}
+\newcommand*{\del}{\nabla}
 
 % This paper
-\newcommand{\tsup}{\textsuperscript}
-\newcommand{\Chandra}{\textit{Chandra}\ }
+\newcommand*{\tsup}{\textsuperscript}
+\newcommand*{\Chandra}{\textit{Chandra}\ }
+\newcommand*\mean[1]{\bar{#1}}
 \defcitealias{ressler2014}{R14}
@@
 
-We first briefly review the models we consider for particle transport; a fuller
-exposition is given by \citetalias{ressler2014}.
+We briefly review our particle transport models and relevant equations for our
+modeling; a fuller review and exposition is given by \citetalias{ressler2014}.
+\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
+derived equations should we give?}
 
-Just present the governing transport equations.  From:
+\note[Aaron]{Double check against Rettig/Pohl}
+The electron distribution which gives rise to the observed synchrotron
+radiation is injected at the forward shock and transported by advection
+and plasma diffusion, following the advection-diffusion equation:
 \[
@@
 we obtain (1-D time-independent flow, neglect compressible flow?!,
-space-independent diffusion coefficient):
+space-independent diffusion coefficient (did we neglect the spherical
+coordinate terms?)):
 \[
@@
 \end{equation}
-where this is equation (6) of \citetalias{ressler2014}; we also look at
+where this is equation (5) of \citetalias{ressler2014}; we also look at
 \begin{equation} \label{eq:full-mod}
@@
 Explain how we back out a filament shape/width from these models
+
+\subsection{Energy dependent widths, diffusion}
+
+\begin{itemize}
+    \item Bohm diffusion: $D(E) = \eta C_d E / B$
+    \item Generalized diffusion: $D(E) = \eta C_d E^\mu / B = \eta_h D(E_h)
+        (E/E_h)^\mu$
+\end{itemize}
+
+Explain the use of fiducial energy -- this makes sense and eases discussion,
+but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
+murky to me.
+
+For the simple model, we have equation (6) of \citetalias{ressler2014}:
+\[
+    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
+\]
+which we relate to full width half max by projection factor $\beta = 4.6$
+so that $w = \beta a$, assuming (1) electron distribution exponential in radial
+coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
+\citep{ballet2006}.
+
+For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
+electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
+\citet{rettig2012};
+
+\subsection{Tycho parameters}
+
+Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
+energy following Rettig and Pohl (again cite Sean's paper).
+We use an electron spectrum cut-off energy of:
+\[
+    E_{\mt{cut}} =
+        \left(8.3\unit{TeV}\right)^{2/(1+\mu)}
+        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)}
+        \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
+    \left[
+        \frac{E_h^{\mu - 1}}{\eta}
+    \right]^{1 / (1 + \mu)}
+\]
+which is equation~(19) of \citetalias{ressler2014}.
+\note[Aaron]{This differs from Sean's presentation -- I drew this from the
+Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
+the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
+$E_h$ ?!  Come back to this shortly.}
 
@@
 We obtained radial intensity profiles by integrating along the shock in each
-region.  Intensity profiles peak sharply at/behind the shock, demarcating our
+region.  Plotted and fitted profiles are reported in vignetting and
+exposure-corrected \note[Aaron]{double check CIAO guides} intensity units;
+error bars are computed from raw count data assuming Poisson statistics.
+Intensity profiles peak sharply at/behind the shock, demarcating our
 thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
@@
 
-We fit rim profiles, obtained by integrating intensity along the shock in each
-region, to a piecewise two-exponential model:
+We fitted rim profiles, obtained by integrating intensity along the shock in
+each region, to a piecewise two-exponential model:
 \begin{equation} \label{eq:prof}
@@
 parameter; this yields a new profile $h'(x) = h(x'(x))$.
-We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
-yielding confidence limits on our measured FWHMs.
+We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
+and the stretched or compressed FWHMs as upper/lower bounds on our reported
+FWHMs.
+
+Finally, we took a geometric average of rim widths $w_i(E)$ in each filament,
+with $i$ indexing each region, as
+\[
+    \mean{w}(E) = \left( \prod_{i=1}^{n} w_i(E) \right)^{1/n}
+\]
+Why?  My (Aaron's) justification:
+\begin{itemize}
+\item Arithmetic mean width is not representative of a filament's
+    spatially varying width (in practice, projected rim emission likely
+    does not arise from a spherical shell \citep[c.f.][]{hester1987}).
+    Our measurements aren't randomly distributed.
+\item I assume / guess that $m_E$ is more likely to be constant over a
+    filament length.  Intuitively, I think of $m_E$ being a proxy for the
+    relative strength of transport mechanisms, as opposed to being a function
+    of the absolute strengths of two mechanisms.  But that's not rigorous,
+    and it doesn't seem obvious $m_E$ should be more robust than width $w$
+    over a filament's length (since we're taking a first derivative, which
+    is usually more painful?).
+\item The geometric mean of FWHMs gives an arithmetic mean of ``sampled''
+    $m_E$ values by definition.  To show this explicitly (just a sanity check)
+    from the equation $w(E) = \alpha E^{m_E}$, where $\alpha$ is a throwaway
+    constant, we have $m_E = \ln(w(E)/\alpha) / \ln(E)$.  Then, $m_E$ computed
+    from geometric mean width $\mean{w}(E)$ is:
+    \begin{align*}
+        \mean{m_E}(E)
+            &= \frac{\ln\left[ \mean{w}(E) \right] - \ln\alpha}{\ln(E)} \\
+            &= \frac{\ln\left[ \left( \prod_{i=1}^{n} w_i(E) \right)^{1/n}
+                        \right] - \ln\alpha}{\ln(E)} \\
+            &= \frac{\frac{1}{n}\left(
+                         \sum_{i=1}^{n} \ln\left[w_i(E)\right]
+                     \right) - \ln\alpha}{\ln(E)} \\
+            &= \frac{\frac{1}{n} \sum_{i=1}^{n}
+                     \left( \ln\left[w_i(E)\right] - \ln\alpha \right)}
+                    {\ln(E)} \\
+            &= \sum_{i=1}^{n} (m_E)_i (E)
+    \end{align*}
+    Or, we could just say that we're taking an arithmetic mean of
+    $\ln(w_i(E))$.
+\item The geometric mean is less sensitive to outliers than the arithmetic
+    mean -- but this may not necessarily be desirable, if it hides
+    real measurement signal.
+\end{itemize}
+The counterpoints are that (1) in practice, it may not make much difference
+(especially as we only have sample size about $1$--$5$ at best), variations
+from changing up calculations are hard to distinguish from plain old
+measurement spread; (2) arithmetic mean is simpler to understand; (3)
+assumption of roughly constant widths does not look terrible in Tycho -- but I
+have not investigated this... (clearly, rims fade at edges, but at bright
+center regions do they swell or vary in width?).
+
+Errors were computed by taking standard errors on $\log w(E)$
+(i.e., $\sigma(w(E)) / \sqrt(n)$, as the CLT applies in log space) and then
+converting back to physical parameter space.  These errors are asymmetric; we
+take the maximum error in either direction as error on our FWHMs for all fits
+(but we report the asymmetric error otherwise).
+\textbf{WARNING:} this procedure is incomplete.  Because our sample sizes are
+tiny (typically, $n \sim 2$), to obtain a true 68.3\% confidence interval /
+1-sigma error, we should compute error from the Student's $t$-distribution.
+The net result is that our errors should be doubled in most cases.
+\emph{I have not yet applied this correction.}
+
+Some problems:
+\begin{itemize}
+    \item Errors are very large, as currently calculated -- they reflect the
+        assumption that $m_E$ is normally distributed, and give a statistical
+        uncertainty on population mean $m_E$.
+        (or if we used the arithmetic mean, same problem for FWHMs)
+        This throws out our very small width errors, and we want to take
+        advantage of our nice photon statistics.
+    \item Since geometric mean is strictly lower than arithmetic mean,
+        this will bias our parameter values downwards -- it's not clear which
+        approach would give more ``correct'' estimates
+\end{itemize}
+
+One approach may be to slice up the regions more thinly and accept a bit more
+uncertainty in FWHM values.  This would make it eaiser to either (1) compute
+fits to regions individually (then, errors are set by profile fitting
+uncertainty alone -- I think our estimates are still a little too small, and we
+should be using 1-sigma errors rather than 90\% CIs), and (2) average many
+FWHMs, in whatever way, and get more robust / lower error filament values.
 
@@
 
-TODO?! We also fit the spectra to absorbed power law models with 1 and 2
-additional Gaussian components for \ion{Si}{13} and \ion{S}{15} He$\alpha$
-lines at $\abt 1.8$, $2.4$ keV.  We compute some equivalent width, or compare
-the goodness-of-fit with and without the additional lines, to rule out the
-presence of a line (but, cf. \citet{protassov2002} on line detection
-statistics!).
+Background spectra were extracted from circular regions around the remnant's
+exterior; we matched each selected rim region to the nearest background region
+and subtracted the background spectrum accordingly. \note[Aaron]{rewrite for
+concision/clarity}.
+
+\note[Aaron]{TODO?!} We also fit the spectra to absorbed power law models with
+1 and 2 additional Gaussian components for \ion{Si}{13} and
+\ion{S}{15} He$\alpha$ lines \note[Aaron]{?? I think I got this from AtomDB but
+not certain of details} at $\abt 1.8$, $2.4$ keV.
+We compute some equivalent width, or compare the goodness-of-fit with and
+without the additional lines, to rule out the presence of a line
+(but cf. \citet{protassov2002} on line detection statistics!).
 
@@
 shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
-\citep{green2009}.  Tycho's forward shock velocity varies azimuthally by up to
+\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
 a factor of 2; we interpolate the data of \citet{williams2013} to estimate
@@
 
-We give figures and tables with rim profile fit information.
+To perform fits, we took a geometric average of rim widths in each energy band,
+for each filament; 
+For FWHM errors, I use the standard error of the mean (with some
+minor nuances; I am using sample standard deviation).
+PUT IN METHODS SECTION
+
+This contrasts with taking an arithmetic average of the rim widths.  The
+geometric average does not represent the expected value of FWHM measurements,
+along the rim.  However, filaments should vary in width along their lengths in
+response to
+
+A key question is whether we wish to report an average w/ errors, corresponding
+to our specific measurements (if we alter our profile fit function, or take a
+new observation of Tycho with different counts, how will our measurement
+change) -- or, if we wish to report an average w/ error that estimates the
+population spread -- if we have huge resolution / collecting power, and could
+slice up the filament in many locations and sample its FWHMs very well, what
+would be the population spread on that sample?
+
+If the FWHMs vary systematically within the filament -- an estimate of
+population spread will give errors that are too large.
+
+We might expect the FWHM energy dependence (our $m_E$) to be consistent across
+the filament, as opposed to the actual FWHM lengths.
+If we expect the FWHM energy dependence
+
+But, both values are important -- the FWHM lengths tell us about the magnetic
+field strength
+
+In Table~\ref{tab:flmt2} we report averaged widths (data and fits for
+individual filaments are given in \emph{appendix, supplement?}).
 
@@
 
-\begin{table*}[h]
+\begin{table*}
 \scriptsize
@@
 
-Here are some fit results for a subset of regions, just those contained in
-Filament 1 (Table~\ref{tab:fit}).  Errors are estimated by 
-Explain error values on parameters
+\subsubsection{Individual regions}
+
+First, Table~\ref{tab:fits-flmt1} presents full model fit results for the regions
+contained in Filament 1.  As currently presented (preliminary results), errors
+are computed by varying free parameters $B_0$, $\eta_2$ to obtain a
+$\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence limits on our fit
+parameters.
+
+\begin{table*}[ht]
+\scriptsize
+\centering
+\caption{Full model best fits for individual regions, Filament 1.
+\label{tab:fits-flmt1}}
+\input{tab-fits-flmt1.tex}
+\end{table*}
+
+\subsubsection{Combining regions, in various ways}
+
+Now, we present fit results for averaged filament FWHMs, for sanity's sake.
+Table~\ref{tab:fits-avg} presents full model fits to arithmetic average of
+FWHMs in each filament.  The model fit predictions for each filament are
+plotted in Figure~\ref{fig:fits-avg}.
 
@@
 \centering
-\caption{Full model best fit parameters, Filament 1.
-    \label{tab:fit}}
-\input{tab-fits-flmt1.tex}
+\caption{Best fits for each filament's averaged FWHMs.
+\label{tab:fits-avg}}
+\input{tab-fits-avg.tex}
 \end{table*}
 
-Table~\ref{tab:fit-avg-fwhm} shows best fits to averaged FWHMs (averaged FWHMs
-not shown).  For FWHM errors, I use the standard error of the mean (with some
-minor nuances; I am using sample standard deviation).
+\begin{figure}
+\centering
+\plottwo{figures/f0-fits-avg-flmt1.png}{figures/f0-fits-avg-flmt2.png} \\
+\plottwo{figures/f0-fits-avg-flmt3.png}{figures/f0-fits-avg-flmt4.png} \\
+\includegraphics[width=0.25\textwidth]{figures/f0-fits-avg-flmt5.png}
+\caption{Plots of best-fits to averaged FWHMs.\note[Aaron]{Update plots
+for better subplot display in final version, if we want to keep these}}
+\label{fig:fits-avg}
+\end{figure}
+
+Finally, Table~\ref{tab:fits-par-avg} shows averaged best-fit parameters.
+Parameter errors are standard errors from averaging and may reflect the
+presence of outliers (especially as the sample number is $1$--$5$).
 
@@
 \centering
-\caption{Full model best fit parameters for filament-averaged FWHMs.
-    \label{tab:fit-avg-fwhm}}
-\input{tab-fits-avg.tex}
+\caption{Filament-wide average of best-fit parameters for constituent regions.
+\label{tab:fits-par-avg}}
+\input{tab-fits-par-avg.tex}
 \end{table*}
 
-Finally, Table~\ref{tab:fit-avg-par} shows averaged best-fit parameters for
-Filament 1 only, at this time.  The parameter errors are standard errors from
-the averaging process and may reflect the presence of outliers.
+We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
+diffusion at $2 \unit{keV}$.  The results (Table~\ref{tab:fits-avg-eta2-fix})
+are relatively insensitive to $\mu$.
 
@@
 \centering
-\caption{Average of best-fit parameters for individual regions
-    \label{tab:fit-avg-par}}
-\input{tab-fits-par-avg.tex}
+\caption{Best fits with $\eta_2 = 1$ fixed, for filament averaged FWHMs.
+\label{tab:fits-avg-eta2-fix}}
+\input{tab-fits-avg-eta2-fix.tex}
 \end{table*}
 
-\begin{table*}
-\scriptsize
-\centering
-\caption{Full model best fit parameters, Filament ??, with $\eta_2 = 1$ fixed}
-%    \label{tab:fit-avg-par}}
-%\input{tab-fits-par-avg.tex}
-Coming soon...
-\end{table*}
+\subsubsection{How confidently can we reject B-damping?}
+
+Everything hinges on our error bars -- this is most important.  Our rims do
+thin consistently, in most regions (might be one or two places where they
+don't), but (1) the errors in our individual FWHMs are larger than I'm
+currently reporting because different profile fits will give a larger spread of
+FWHMs (might need to consider reduced chi-squared here, but using chi-sqr to
+select profile fit models is not physically meaningful)
 
@@
 \centering
-\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}}
-\label{tab:sean}
+\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
+\label{tab:sean}}
 \input{tab-sean.tex}
@@
 \centering
-\caption{SN 1006 best fit parameters, 2 highest energy bands (full model)}
-\label{tab:sn1006-2band}
+\caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
+\label{tab:sn1006-2band}}
 \input{tab-sn1006-2band.tex}
@@
 \centering
-\caption{SN 1006 best fit parameters, 3 energy bands (full model)}
-\label{tab:sn1006-3band}
+\caption{SN 1006 best fit parameters, 3 energy bands (full model).
+\label{tab:sn1006-3band}}
 \input{tab-sn1006-3band.tex}
@@
 Araya et. al (2010) in varying values of $\mu$ (Approximate Analytic Results)
-Dashes denote places where fits were unobtainable.}
-\label{tab:araya}
+Dashes denote places where fits were unobtainable.
+\label{tab:araya}}
 \input{tab-sean-casA.tex}

### 2014-09-13 code-models/models.py

@@ -377,7 +377,7 @@ def mind_the_gaps(x, yaux, y, dy_max, f):
 # Input: snr, kevs, data/eps/mu/(eta2,B0);   output: best fit (mu)/eta2/B0
 
 def simple_fit(snr, kevs, data, eps, mu, eta2=None, B0=None,
-    mu_free=False, eta2_free=True, B0_free=True):
+    mu_free=False, eta2_free=True, B0_free=True, **lmf_kws):
     """Perform a simple model fit (equation 6; Table 7 of Ressler et al.)
     A convenience wrapper for lmfit.minimize(objectify(width_dump), ...)
 
@@ -387,6 +387,7 @@ def simple_fit(snr, kevs, data, eps, mu, eta2=None, B0=None,
         kevs, data, eps (np.array) as usual
         mu, B0, eta2 (float) initial guesses, but mu fixed
         mu_free, eta2_free (bool) which parameters shall vary in fits?
+        **lmf_kws takes extra kwargs for lmfit.minimize (includes lsq kws)
     Output:
         lmfit.Minimizer with fit information / parameters
     """
@@ -399,11 +400,11 @@ def simple_fit(snr, kevs, data, eps, mu, eta2=None, B0=None,
               min = snr.par_lims[pstr][0], max = snr.par_lims[pstr][1])
 
     res = lmfit.minimize(objectify(width_dump), p, args=(data, eps, kevs, snr),
-                         method='leastsq')
+                         **lmf_kws)
     return res
 
 def full_fit(snr, kevs, data, eps, mu, eta2=None, B0=None, mu_free=False,
-    eta2_free=False, B0_free=True, model_kws=None, **lmf_kws):
+    eta2_free=True, B0_free=True, model_kws=None, **lmf_kws):
     """Perform full model fit (equation 12; Table 8 of Ressler et al.)
     Default fit: B0 free; mu, eta2 fixed
 
@@ -472,8 +473,7 @@ def simple_width(snr, kevs, mu, eta2, B0):
 # Input: params, kevs, snr, **kwargs; output: model FWHMs
 
 def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
-               irmax=None, iradmax=None, ixmax=None,
-               irad_adapt=True, irad_adapt_f=1.2):
+    irmax=None, iradmax=None, ixmax=None, irad_adapt=True, irad_adapt_f=1.2):
[…]

### 2014-09-13 code-models/models_disp.py

@@ -29,18 +29,28 @@ from fplot import fplot
 # ==================================
 
 def build_dataf(fit_type, conf_intv=0.683, fit_kws=None, err_kws=None):
-    """Build function f to perform fits/errs; f(mu) returns res obj with information (see src)
+    """Build function f to perform fits/errs; f(mu) returns res obj with
+    fits, errors, fit properties, etc... (see src)
 
-    At core, a wrapper function for fobj.get_fit(...), fobj.get_err(...)
-    Make internal functionality changes in those methods, please
+    f is a wrapper function for fobj.get_fit(...), fobj.get_err(...)
+    Please see the methods in `models_exec.py`, to understand how they work
+    more deeply.
+
+    Notes: fitting w/ one free param may not give sensible (manual) errors;
+    lmfit may balk.  Input options are not all fully tested, but most should
+    work (some unit tests would be nice to demonstrate that error finding does
+    what I expect it to do).
 
     Inputs:
         fit_type: 'simp' or 'full'
         conf_intv: please don't set above 0.683 or your life will suck, I guarantee
-        fit_kws (only used for full fit):
-            mu_free=False, B0_free=True (don't twiddle these)
-            eta2, B0: if you wish to provide custom (non-grid) initial guesses
-                      MUST provide guesses for both, else ignored!
+        fit_kws, *simple and full models*
+            eta2_free=True, B0_free=True
+            eta2, B0: provide custom (non-grid) initial guesses. For full
+                      model, MUST provide guesses for both, else ignored!
+            mu_free=False (I recommend not to change, esp. if using full model!
+                           likely to hit bugs, not tested)
+        fit_kws, *full model only*
             model_kws (dict):
                 rminarc, icut, irmax, iradmax, ixmax, irad_adapt, irad_adapt_f
             scale_covar=False (!) (lmfit.minimize)
@@ -71,8 +81,18 @@ def build_dataf(fit_type, conf_intv=0.683, fit_kws=None, err_kws=None):
 
         # Get better errors
         ci_man = fobj.get_errs(res, fit_type, ci_vals=(conf_intv,), **err_kws)
-        eta2_err = mex.get_ci_errors(ci_man, 'eta2', ci_val=conf_intv)
[…]

### 2014-09-13 data-kepler/ds9-kepler-rgb.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+echo "Region file to load?"
+read -e reg
+
+ds9 -rgb \
+    -red 0.7-1kev_mosaic.fits \
+        -scale limits 4e-8 3.75e-6 \
+    -green 1-2kev_mosaic.fits \
+        -scale limits 2e-8 2.2e-6 \
+    -blue 2-7kev_mosaic.fits \
+        -scale limits 5e-9 4.5e-7 \
+    -rgb lock scale yes \
+    -log \
+    -regions $reg

### 2014-09-13 manuscript/regen.sh

@@ -1,7 +1,7 @@
 #!/bin/sh
 
-pdflatex tycho-paper.tex
-bibtex tycho-paper
-pdflatex tycho-paper.tex
-pdflatex tycho-paper.tex
-open tycho-paper.pdf
+pdflatex paper-tycho.tex
+bibtex paper-tycho
+pdflatex paper-tycho.tex
+pdflatex paper-tycho.tex
+open paper-tycho.pdf

### 2014-09-14 manuscript/paper-tycho.tex
Update region/spectra pipeline, Kepler FWHMs
Update profile fitting code for Kepler data, make specextract regions.
Compute background/filament spectra.  Prune old files.

@@
 profile by mapping radial coordinate $x$ to
-$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
-parameter; this yields a new profile $h'(x) = h(x'(x))$.
+$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
+parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
+this yields a new profile $h'(x) = h(x'(x))$.
 We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7

### 2014-09-14 code-profiles/crvfit.py

@@ -1,0 +1,102 @@
+"""
+XSPEC-like functionality to freeze fit parameters
+Basically extends scipy.optimize.curve_fit
+
+Next time, use lmfit instead -- much easier
+
+Aaron Tran
+July 2014 (moved to .py Sept 2014)
+"""
+
+import numpy as np
+import scipy as sp
+
+def freeze_func(f, pars, ls_freeze):
+    """Make frozen function
+    Ex: if ls_freeze = [1,2,4], this builds expression:
+    lambda x,p0,p3,p5,p6,p7 : f(x,p0,pars[1],pars[2],p3,pars[4],p5,p6,p7)
+    """
+    lambd_args = 'x,'
+    lambd_body = 'f(x,'
+    for i in xrange(len(pars)):
+        if i in ls_freeze:
+            lambd_body += 'pars[{:d}],'.format(i)
+        else:
+            lambd_args += 'p{:d},'.format(i)
+            lambd_body += 'p{:d},'.format(i)
+
+    lambd_args = lambd_args[:-1]
+    lambd_body = lambd_body[:-1] + ')'
+
+    # To explain the `f=f, pars=pars`, see http://stackoverflow.com/q/7349785
+    # More than one way to skin a cat, though
+    lambd_str = 'lambda ' + lambd_args + ', f=f,pars=pars : ' + lambd_body
+    return eval(lambd_str)
+
+def run_frz_fit(x, y, y_err, f, pars, ls_freeze, **kwargs):
+    """Perform fit with frozen parameters
+    func has form func(x, *pars)
+    pars is a list of initial guesses
+    ls_freeze is a list of parameter indices that are to be frozen.
+    """
+
+    if len(ls_freeze) > 0:
+        fit_func = freeze_func(f, pars, ls_freeze)
+        p_fit = [pars[i] for i in xrange(len(pars)) if i not in ls_freeze]
+    else:
+        fit_func = f
+        p_fit = pars
+
+    popt, pcov = run_fit(x, y, y_err, fit_func, p_fit, **kwargs)
+
+    popt_aug = popt
+    if len(ls_freeze) > 0:
+        for i in ls_freeze:
+            popt_aug = np.insert(popt_aug, i, pars[i])
+
+    return popt, pcov, popt_aug
+
+def run_fit(x, y, y_err, f, pars, **kwargs):
+    """Convenience wrapper for sp.optimize.curve_fit"""
[…]

### 2014-09-14 code-profiles/fsmooth.py

@@ -1,0 +1,94 @@
+"""
+Functions to smooth profiles and identify extrema for fit domains.
+The first minimum downstream of the thin rim bounds the fit domain.
+
+Aaron Tran
+July 2014 (split to .py file, Sept 2014)
+"""
+
+import numpy as np
+import scipy as sp
+from scipy import optimize
+from scipy import signal
+
+
+def ind_first_min(y, **kwargs):
+    """Index of first minimum to left of global non-edge max in smoothed data
+    If no such minimum is found, return 0 (i.e., don't cut the fit domain).
+    If no max (peak) is found, return 0.
+    **kwargs (window_len, window) passed to std_smooth
+    """
+
+    # List of indices of relative minima in smoothed-y
+    y_smooth = std_smooth(y, **kwargs)
+    inds_relmin = sp.signal.argrelmin(y_smooth)[0]  # Unpack the tuple...
+
+    if len(inds_relmin) is 0:
+        return 0
+
+    # Index of global (non-edge) maximum in y
+    try:
+        ind_max = get_ind_max(y, **kwargs)
+    except ValueError:
+        return 0
+
+    # Find the largest value in inds_relmin, that's smaller than ind_max
+    max_left_min = 0
+    for ind_min in inds_relmin:
+        if ind_min > max_left_min and ind_min < ind_max:
+            max_left_min = ind_min
+
+    return max_left_min
+
+def get_ind_max(y, **kwargs):
+    """Smooths data and returns index of largest relative maximum in smoothed data
+    **kwargs (window_len, window) passed to std_smooth
+
+    If no relative maximum found,
+    """
+    ysmooth = std_smooth(y, **kwargs)
+    # Get indices of relative maxima
+    inds_relmax = sp.signal.argrelmax(ysmooth)[0]  # Unpack the tuple...
+    # Get index of the largest relative maximum
+    if len(inds_relmax) == 0:
+        raise ValueError("No relative maximum found in y for given smoothing")
+
+    idx = np.argmax(ysmooth[inds_relmax])  # idx indexes inds_relmax, now
+    return inds_relmax[idx]
+
+def std_smooth(x, window_len=21, window='hanning'):
+    """Modified from scipy cookbook (http://wiki.scipy.org/Cookbook/SignalSmooth)
+    Add reflected copies of signals at each end to address convolution edge effects
+
+    Default window length of 21 pts, empirically works well for Tycho's SNR.
+    No problems with hanning, haven't tested other windows.  Choice shouldn't matter much.
+
+    Input:
[…]

### 2014-09-14 code-profiles/ipython_nose-master/pdb_ipython_nose.py

@@ -1,26 +1,0 @@
-import types
-
-import ipython_nose
-
-test_module = types.ModuleType('test_module')
-from nose.plugins.skip import SkipTest
-
-def test_foo():
-    assert True
-
-def test_bar():
-    assert False
-
-def test_baz():
-    raise Exception()
-
-def test_quux():
-    raise SkipTest()
-
-test_module.test_foo = test_foo
-test_module.test_bar = test_bar
-test_module.test_baz = test_baz
-test_module.test_quux = test_quux
-
-plugin = ipython_nose.nose('', test_module)
-print plugin._repr_html_()

### 2014-09-14 code-reg/ds9projsplitter.py

@@ -1,0 +1,134 @@
+"""
+Script to split ds9 regions into inner/outer pieces (split into two files)
+
+Aaron Tran
+2014 July 8
+
+This script is intended for our SNR radial profiles (Tycho, Kepler, etc.).
+
+To compute spectra, select inner and outer regions delineated by
+1. rim between largest measured FWHMs.  Find lowest downstream and highest
+   upstream FWHM locations (yes, may mix limits from different bands).
+2. downstream FWHM to most downstream local minimum, i.e. boundary of fit domain
+   for profile fitting scripts.  Again, checks cut location for all bands
+   and selects the most conservative cut (largest possible region).
+
+One input region file will be split into two for specextract/XSPEC chain.
+Each file contains only inner or only outer pieces, to preserve numbering.
+
+Script makes MANY assumptions about structure of region dictionary.
+So, if dictionary structure is changed... update accordingly.
+"""
+
+import argparse
+import cPickle as pickle
+import numpy as np
+import os
+import re
+
+import regparse
+
+
+def main():
+    """Generate split regions from cmd line arguments"""
+    parser = argparse.ArgumentParser(description=
+             ('Split DS9 region file of projections into inner/outer pieces, '
+              'according to profile fit cuts and FWHMs'))
+    parser.add_argument('fitpkl', help=('Pickled region dictionary from '
+                        'profile fitting scripts'))
+    parser.add_argument('fitreg', help='DS9 fk5 region file of projections')
+    parser.add_argument('regimg', help='Valid FITS file for input regions')
+    parser.add_argument('-o', '--outreg', help=('Root name for output region '
+                        'files.  Inferred from input region file by default'))
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='Verbose mode')
+
+    # Parse arguments
+    args = parser.parse_args()
+    f_pkl, f_reg, f_img = args.fitpkl, args.fitreg, args.regimg
+    f_oreg = args.outreg
+    verbose = args.verbose
+
+    if f_oreg is None:
+        f_oreg = os.path.splitext(f_reg)[0]
+    if verbose:
[…]

### 2014-09-14 code-reg/fplot.py

@@ -1,0 +1,59 @@
+"""
+Small module with methods for matplotlib
+Goal is to make plotting easier, and ensure reproducible plots
+(and, cut down on amt of boilerplate code)
+
+fplot is intended if you are using the interactive like interface,
+rather than the object-oriented interface.  A convenience method only.
+
+This is supposed to be small enough to be okay for global import
+from fplot import *
+
+Aaron Tran
+6 June 2014
+"""
+
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+
+def main():
+    show_mplrc_settings()
+
+
+def show_mplrc_settings():
+    """Display information about matplotlibrc file"""
+    print 'Using %s' % mpl.matplotlib_fname()
+    r = mpl.rcParams
+
+    ff = r['font.family'][0]
+    print 'Font sizes for axes: %g; (x,y) ticks: (%g, %g): legend %g' % \
+          (r['axes.labelsize'], r['xtick.labelsize'],
+           r['ytick.labelsize'], r['legend.fontsize'])
+    print 'Font family %s uses face %s' % (ff, r['font.'+ff])
+
+    print 'Figure size: %s, dpi: %g' % (r['figure.figsize'], r['figure.dpi'])
+
+
+def fplot(xlab, ylab, ax=None, axargs=None, scales=None):
+    """Convenience method to set x/y labels, axis limits in one cmd
+    xlab: xlabel string
+    ylab: ylabel string
+    axargs: limits [xmin, xmax, ymin, ymax] or other string arg (e.g., 'tight')
+    scales: [xscale, yscale] (see plt.xscale(...))
+    """
+    if ax is None:
+        ax = plt.gca()
+    if scales is not None:  # Could allow to accept only one arg
+        ax.set_xscale(scales[0])
+        ax.set_yscale(scales[1])
+    ax.set_xlabel(xlab)
+    ax.set_ylabel(ylab)
+    if axargs is not None:
+        ax.axis(axargs)
+    # plt.ticklabel_format(useOffset=False, axis='x')
+    # plt.ticklabel_format(useOffset=False, axis='y')
+
+
+if __name__ == '__main__':
+    main()
+

### 2014-09-14 code-spec/mergespectra.sh

@@ -15,12 +15,20 @@ then
 fi
 
 # Tycho's SNR, Hughes 2007
-obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
-wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
-       0.053847516 0.03258367 0.04726812 0.056013404)
+#obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
+#wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
+#       0.053847516 0.03258367 0.04726812 0.056013404)
+
+# Kepler's SNR, Reynolds 2006
+obsids=(6714 6715 6716 6717 6718 7366)
+# import numpy
+# exps = np.array([157.82, 159.13, 158.02, 106.81, 107.8, 51.46])
+# print np.sum(exps)
+# print exps / np.sum(exps)
+wghts=(0.21297096 0.21473875 0.21324085 0.14413527 0.14547123 0.06944295)
 
 # Check number of regions to process
-nregs=`ls -l "${1}_${obsids[0]}_src*.pi" | wc -l`
+nregs=`ls -l ${1}_${obsids[0]}_src*.pi | wc -l`
 if [ ${nregs} != 0 ]
 then
     echo "${nregs} regions' spectra will be merged"
@@ -44,6 +52,10 @@ do
     done
     # Remove extra '+' operator
     pi_str=${pi_str:1}
+
+    echo $pi_str
+    echo $rmf_str
+    echo $arf_str
 
     # Merge pi, rmf, arf files (FTOOLS)
     mathpha units=C expr=${pi_str} outfil=${1}_src${n}.pi exposure=CALC \

### 2014-09-14 code-spec/newregion.sh

@@ -4,18 +4,21 @@
 # Modified from script by Brian J. Williams
 # Aaron Tran, 2014 July 12
 
-# Call from data/regions-[n]/ directory
+# First call heainit, then ds9&, then
+# call script from data/regions-[n]/ directory
 
-obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
-
-mkdir tmp
+# obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
+obsids=(6714 6715 6716 6717 6718 7366)
 
 for id in "${obsids[@]}";
 do
-    xpaset -p ds9 file "../../chandra/imgs_tycho/output${id}.fits"
-    xpaset -p ds9 regions format ciao
-    xpaset -p ds9 regions coord wcs
+#    xpaset -p ds9 file "../../chandra/imgs_tycho/output${id}.fits"
+    xpaset -p ds9 file "../../chandra/${id}/repro/acisf0${id}_repro_evt2.fits"
+#    xpaset -p ds9 regions format ciao
+    xpaset -p ds9 regions format ds9
+    xpaset -p ds9 regions system wcs
     xpaset -p ds9 regions load "${1}.reg"
-    xpaset -p ds9 regions coord physical
+    xpaset -p ds9 regions format ciao
+    xpaset -p ds9 regions system physical
     xpaset -p ds9 regions save "${1}_${id}.reg"
 done

### 2014-09-14 code-spec/spec_fit.py

@@ -1,0 +1,215 @@
+"""
+Perform phabs*powerlaw XSPEC fit to spectra and output
+plots and fit parameters
+Aaron Tran
+2014 June 17
+(last modified: 2014 July 12)
+
+Initialize HEASOFT (`heainit`) before running this script!
+Run script with 32-bit python (use `arch -i386 python ...`)
+Run script from directory of actual spectra (so that XSPEC can resolve relative
+links to response and background files.
+"""
+
+import argparse
+import json
+import os
+import re
+import numpy as np
+
+import xspec as xs
+
+import regparse
+
+def main():
+    """Main method"""
+    # argparse setup
+    parser = argparse.ArgumentParser(description=
+             ('Apply XSPEC model fits and output spectra/fits/data. '
+              'Run script from spectra-containing directory, '
+              'so XSPEC can locate response/background files.'))
+    parser.add_argument('specroot', help='Directory stem for spectra')
+    parser.add_argument('fittype', help=('Type of fit to apply; '
+                                         '0=phabs*po, '
+                                         '1=excise Si line, '
+                                         '2=fit Si line'), type=int)
+    parser.add_argument('plotroot', help='Output stem for plots')
+    parser.add_argument('fitproot', help='Output stem for fit logs, data')
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='verbose mode')
+    parser.add_argument('-e', '--error', action='store_true',
+                        help=('Compute/output errors from 90pct confidence lims'
+                              ' (may need user input / take extra time).'))
+
+    args = parser.parse_args()
+    specroot, pltroot, fitproot = args.specroot, args.plotroot, args.fitproot
+    ftype = args.fittype
+    verbose = args.verbose
+    wanterr = args.error
+
+    # Get number of spectra to fit (count grouped spectrum files)
+    n = regparse.count_files_regexp(specroot + r'_src[0-9]+_grp\.pi')
+    if verbose:
+        print '\n{} spectra to process'.format(n)
+        if wanterr:
+            print 'Computing errors from 90% confidence limits'
+
[…]

### 2014-09-14 code/ds9projangle.py

@@ -1,92 +1,0 @@
-"""
-Compute azimuth angle between rim regions and remnant center
-
-Aaron Tran
-2014 August 6
-"""
-
-import argparse
-from datetime import datetime
-import numpy as np
-import os
-
-import regparse
-
-RAD_2_DEG = 180. / np.pi
-
-
-def main():
-    """"""
-    parser = argparse.ArgumentParser(description=('Get azimuth angles for rim '
-                                     'regions relative to circle center.'))
-    parser.add_argument('freg', help=('DS9 region file, physical coords, of '
-                                      'projection regions around SNR'))
-    parser.add_argument('fcirc', help=('DS9 region file, physical coords, of '
-                                       'circle region centered on SNR'))
-    parser.add_argument('fout', help='Output plaintext list of az angles')
-
-    args = parser.parse_args()
-    freg, fcirc, fout = args.freg, args.fcirc, args.fout
-
-    p_circ = parse_circ(fcirc)
-
-    az_vals = []
-    rlist = regparse.load_ds9reg(freg)
-    for rstr in rlist:
-        p_proj = proj_center(rstr)
-        az = RAD_2_DEG * get_az_angle(p_circ, p_proj)
-        az_vals.append(az)
-
-    # Save some information about how az angles were computed too
-    meta = 'Source regions: {}\n'.format(os.path.abspath(freg))
-    meta += 'Remnant circle: {}\n'.format(os.path.abspath(fcirc))
-    meta += 'Angles generated: {}\n'.format(datetime.now())
-    meta += 'Remnant center: ({:0.18f}, {:0.18f})'.format(*p_circ)
-
-    np.savetxt(fout, az_vals, fmt='%.18f', header=meta)
-
-    print 'Wrote azimuth angles (degrees CCW from N) to {}'.format(fout)
-
-
-def get_az_angle(p1, p2):
-    """Azimuth angle as measured from north, going east, with p1 at center.
-    Range is [0, 2pi]"""
-    x1, y1 = p1
-    x2, y2 = p2
-    xp, yp = x2-x1, y2-y1
-    az = np.arctan2(-xp, yp)  # Measure CCW from north
-    if az < 0:
-        az = az + 2*np.pi
-    return az
-
-
-def proj_center(rstr):
-    """Compute center coordinates of projection region.
-    Partially lifted from ds9proj2ciao.py"""
[…]

### 2014-09-14 code/ds9projplotter.py

@@ -1,185 +1,0 @@
-"""
-Save intensity profiles and generate profile plots for a DS9 region file
-containing only projection-type regions.
-Generate profiles/plots for an arbitrary number of FITS files and labels.
-Fig. 7 of Ressler et al. [ApJ, in press] illustrates what we're doing
-
-Relies on pyds9 to extract 2D projection plots.
-Uses ds9's RGB frames to force projection plots to pop-up and saves data from
-the plot windows.
-
-pyds9 documentation: http://hea-www.harvard.edu/RD/pyds9/
-DS9 XPA reference: http://ds9.si.edu/ref/xpa.html
-
-Aaron Tran
-June 12, 2014
-(last modified June 23, 2014)
-"""
-
-import argparse
-import matplotlib.pyplot as plt
-import numpy as np
-import os
-
-import ds9
-
-from fplot import fplot, show_mplrc_settings
-import regparse
-
-def main():
-    """Run from command line as, e.g.,
-    python ds9projplotter.py -v '../data/profiles_all.reg' '../plots/plt'
-    """
-    parser = argparse.ArgumentParser(description=
-             ('Plot and save data from DS9 projections. '
-              'If only labels are provided, it will simply plot dat files'))
-
-    parser.add_argument('infile', help='Input DS9 region file (fk5 coords)')
-    parser.add_argument('datroot', help='Stem for output profile data')
-
-    parser.add_argument('-p', '--pltroot', help='Stem for output plots')
-    parser.add_argument('-b', '--bands', help='Bands (.fits) to be processed',
-                        nargs='*')
-
-    parser.add_argument('-l', '--labels', help='Band labels for plots/files',
-                        nargs='+')
-    parser.add_argument('-v', '--verbose', action='store_true',
-                        help='verbose mode')
-    parser.add_argument('-s', '--subplot', action='store_true',
-                        help='Generate subplot plots')
-
-    # Parse arguments
-    args = parser.parse_args()
-    regions_file = args.infile
-    pltroot, datroot = args.pltroot, args.datroot
-    bands, labels = args.bands, args.labels
-    verbose, subplot = args.verbose, args.subplot
-
-    # Check arguments for sanity
-    # If -p is supplied, output plots
-    # If -b is supplied, output data
-    if bands is None:
-        if not pltroot:
-            parser.error('Nothing to be done!  Need bands or pltroot.')
-        else:
[…]

### 2014-09-14 code/fplot.py

@@ -1,59 +1,0 @@
-"""
-Small module with methods for matplotlib
-Goal is to make plotting easier, and ensure reproducible plots
-(and, cut down on amt of boilerplate code)
-
-fplot is intended if you are using the interactive like interface,
-rather than the object-oriented interface.  A convenience method only.
-
-This is supposed to be small enough to be okay for global import
-from fplot import *
-
-Aaron Tran
-6 June 2014
-"""
-
-import matplotlib as mpl
-import matplotlib.pyplot as plt
-
-def main():
-    show_mplrc_settings()
-
-
-def show_mplrc_settings():
-    """Display information about matplotlibrc file"""
-    print 'Using %s' % mpl.matplotlib_fname()
-    r = mpl.rcParams
-
-    ff = r['font.family'][0]
-    print 'Font sizes for axes: %g; (x,y) ticks: (%g, %g): legend %g' % \
-          (r['axes.labelsize'], r['xtick.labelsize'],
-           r['ytick.labelsize'], r['legend.fontsize'])
-    print 'Font family %s uses face %s' % (ff, r['font.'+ff])
-
-    print 'Figure size: %s, dpi: %g' % (r['figure.figsize'], r['figure.dpi'])
-
-
-def fplot(xlab, ylab, ax=None, axargs=None, scales=None):
-    """Convenience method to set x/y labels, axis limits in one cmd
-    xlab: xlabel string
-    ylab: ylabel string
-    axargs: limits [xmin, xmax, ymin, ymax] or other string arg (e.g., 'tight')
-    scales: [xscale, yscale] (see plt.xscale(...))
-    """
-    if ax is None:
-        ax = plt.gca()
-    if scales is not None:  # Could allow to accept only one arg
-        ax.set_xscale(scales[0])
-        ax.set_yscale(scales[1])
-    ax.set_xlabel(xlab)
-    ax.set_ylabel(ylab)
-    if axargs is not None:
-        ax.axis(axargs)
-    # plt.ticklabel_format(useOffset=False, axis='x')
-    # plt.ticklabel_format(useOffset=False, axis='y')
-
-
-if __name__ == '__main__':
-    main()
-

### 2014-09-14 code/spec_fit.py

@@ -1,215 +1,0 @@
-"""
-Perform phabs*powerlaw XSPEC fit to spectra and output
-plots and fit parameters
-Aaron Tran
-2014 June 17
-(last modified: 2014 July 12)
-
-Initialize HEASOFT (`heainit`) before running this script!
-Run script with 32-bit python (use `arch -i386 python ...`)
-Run script from directory of actual spectra (so that XSPEC can resolve relative
-links to response and background files.
-"""
-
-import argparse
-import json
-import os
-import re
-import numpy as np
-
-import xspec as xs
-
-import regparse
-
-def main():
-    """Main method"""
-    # argparse setup
-    parser = argparse.ArgumentParser(description=
-             ('Apply XSPEC model fits and output spectra/fits/data. '
-              'Run script from spectra-containing directory, '
-              'so XSPEC can locate response/background files.'))
-    parser.add_argument('specroot', help='Directory stem for spectra')
-    parser.add_argument('fittype', help=('Type of fit to apply; '
-                                         '0=phabs*po, '
-                                         '1=excise Si line, '
-                                         '2=fit Si line'), type=int)
-    parser.add_argument('plotroot', help='Output stem for plots')
-    parser.add_argument('fitproot', help='Output stem for fit logs, data')
-    parser.add_argument('-v', '--verbose', action='store_true',
-                        help='verbose mode')
-    parser.add_argument('-e', '--error', action='store_true',
-                        help=('Compute/output errors from 90pct confidence lims'
-                              ' (may need user input / take extra time).'))
-
-    args = parser.parse_args()
-    specroot, pltroot, fitproot = args.specroot, args.plotroot, args.fitproot
-    ftype = args.fittype
-    verbose = args.verbose
-    wanterr = args.error
-
-    # Get number of spectra to fit (count grouped spectrum files)
-    n = regparse.count_files_regexp(specroot + r'_src[0-9]+_grp\.pi')
-    if verbose:
-        print '\n{} spectra to process'.format(n)
-        if wanterr:
-            print 'Computing errors from 90% confidence limits'
-
[…]

### 2014-09-14 data/old-fits/ds9-tycho-rgb-bin.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-echo "Region file to load?"
-read reg
-
-ds9 -view layout vertical \
-    -colorbar orientation vertical \
-    -rgb \
-    -red 0.7-1kev_mosaic_bin.fits \
-        -scale limits 4e-8 2.1e-6 \
-    -green 1-2kev_mosaic_bin.fits \
-        -scale limits 4e-8 2.42e-6 \
-    -blue 2-7kev_mosaic_bin.fits \
-        -scale limits 3e-8 1.5e-6 \
-    -rgb lock scale yes \
-    -histequ \
-    -regions $reg

### 2014-09-16 manuscript/paper-tycho.tex
1st round paper comments; average FWHM fit tables
Incorporate feedback from Rob/Brian into manuscript, restructure for
tables to be added.

--- 2014-09-10 manuscript/tycho-paper.tex
@@
-% \documentclass[manuscript]{aastex}  % one-column, double-spaced
+%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
 % \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
@@
 %\usepackage{pdflscape}  % rotate pages (Texlive)
+\usepackage{hyperref}
 
-\newcommand{\mt}{\mathrm}
-\newcommand{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
-\newcommand{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
-\newcommand{\ptl}{\partial}
-\newcommand{\del}{\nabla}
+\newcommand*{\mt}{\mathrm}
+\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
+\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
+\newcommand*{\ptl}{\partial}
+\newcommand*{\del}{\nabla}
 
 % This paper
-\newcommand{\tsup}{\textsuperscript}
-\newcommand{\Chandra}{\textit{Chandra}\ }
+\newcommand*{\tsup}{\textsuperscript}
+\newcommand*{\Chandra}{\textit{Chandra}\ }
+\newcommand*\mean[1]{\bar{#1}}
+\newcommand*{\tsynch}{\tau_{\mt{synch}}}
 \defcitealias{ressler2014}{R14}
@@
 
-\title{Energy Dependent X-Ray Rim Widths in Tycho's Supernova Remnant}
+\title{Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent}
 
@@
 \begin{abstract}
-\note[Aaron]{Copy pasted from NASA abstract, not reviewed}
-Young supernova remnants may exhibit thin (~1--10\% of shock radius) X-ray rims
-of synchrotron radiation from forward shock-accelerated electrons that travel
-downstream of the shock and quickly cease to radiate. Rim widths limited by
-radiative energy losses should decrease with energy and require magnetic field
-amplification $10$--$100\times$ that expected from adiabatic shock compression.
-Damped magnetic fields behind rims may produce thin rims without strong field
+\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
+remnants may exhibit thin (~1--10\% of shock radius) X-ray rims of synchrotron
+radiation from forward shock-accelerated electrons that travel downstream of
+the shock and quickly cease to radiate. Rim widths limited by radiative energy
+losses should decrease with energy and require magnetic field amplification
+$10$--$100\times$ that expected from adiabatic shock compression.  Damped
+magnetic fields behind rims may produce thin rims without strong field
 amplification but require energy-independent rim widths. We measured rim widths
@@
 transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
-particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work.
-Inferred magnetic fields, diffusion coefficients, and diffusion-energy scaling
-may constrain models for cosmic ray acceleration in supernova remnants and
-plasma turbulence in astrophysical shocks.
+particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
+on SN 1006. Inferred magnetic fields, diffusion coefficients, and
+diffusion-energy scaling may constrain models for cosmic ray acceleration in
+supernova remnants and plasma turbulence in astrophysical shocks.
 \end{abstract}
@@
 
-% -------------------
-% Background / review
-% -------------------
-\subsection{What are thin rims?}
+\note[Aaron]{this first draft of intro structure is mostly set (in terms of
+material, number of paragraphs).}
 
-Define thin rims (hereafter, thin rims).
-\note[Aaron]{most text below is copy-pasted from my own notes -- explanation
-may be too simplistic}
+% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
+Forward shock accelerated ISM/CSM particles in young supernova remnants emit
+synchrotron radiation strongly in the shock's immediate wake but quickly turn
+off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
+morphology with bright X-ray and radio rims/filaments due to line-of-sight
+projection (hereafter, thin rims).
+Seminal observations \& interpretations of these filaments, interpretation in
+context of DSA.
+People (such as the authors of this manuscript) are trying to model these
+filaments and figure out what's going on.
+Why do we care about these models?  They tell us something about what happens
+behind the shock, and perhaps what's going on at the shock.  We get at the
+plasma turbulence, magnetic field turbulence and structure, electron injection.
+Applications to: cosmic ray acceleration, turbulent field amplification, (note
+assumptions in re proton/electron spectra).  Cut-off energy of injected
+electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
+PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
+AGN jets, galaxy clusters \citep{van-weeren2010}, cosmological shocks?!
+\citep{miniati2000, ryu2008}, other cool stuff.  See relevant reviews
+\citep{blandford1987}.
 
-Somewhere here, define upstream/downstream of shock (makes sense in reference
-frame of shock).
+% What makes these shocks?
+The widths of these X-ray rims are thought to be controlled by a combination of
+synchrotron losses, particle transport, and magnetic fields immediately
+downstream of the shock.  Synchrotron losses depend on the initial electron
+energy distribution and the gradual decrease of electron energies downstream of
+the shock.  At the shock, high energy electrons efficiently radiate harder
+synchrotron X-ray photons; as they are transported away from the shock, they
+radiate at lower energies and lose energy more slowly.  The transport process
+is driven by both bulk plasma advection away from the shock at downstream
+velocity $v_d = v_s / r$, where $v_s$ is shock velocity and $r$ the compression
+ratio, and diffusion ... (driven by collisionless particle interaction,
+magnetic field turbulence, ????? fill in details) with respect to bulk
+advection.  Energy-dependent diffusion (e.g., diffusion coefficient $D \propto
+E$ for Bohm diffusion) allows higher energy electrons to diffuse further
+upstream or downstream than would be expected from pure advection; in
+particular, diffusion upstream of the shock may give rise to a shock precursor
+\citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.  Finally, the magnetic
+field strength may be quickly damped behind the shock, so that electrons may
+not radiate as efficiently and thin rims would reflect the spatial structure of
+the field, rather than efficient particle acceleration (and losses) and/or
+efficient synchrotron cooling \citep{pohl2005}.  \note[Aaron]{I need to read up
+on particle transport, diffusion, plasma physics!}
 
-Accelerating ISM/CSM particles in the forward shocks of supernovae emit
-synchrotron radiation.  Emission is strong in the shock's immediate wake, but
-dies off quickly downstream as particles radiate and lose energy. The radiation
-from a spherical blast wave, then, is shell-like with bright X-ray and radio
-rims/filaments due to line-of-sight projection.  These filaments have finite
-and energy-dependent widths, set by:
-(1) \emph{synchrotron losses}.  At the shock, high energy electrons efficiently
-radiate harder x-ray photons.  As electrons are advected downstream while
-radiating, they radiate at lower energies and lose energy more slowly.
-Synchrotron losses depend on the initial electron energy distribution and the
-gradual decrease of electron energies downstream of the shock.
-(2) \emph{diffusion}.  Random motion with respect to bulk plasma advection.
-Higher energy electrons diffuse and travel further downstream than would be
-expected from pure advection; hence, higher energy radiation may be seen
-farther downstream of the shock than expected. Higher energy particles may also
-diffuse \emph{ahead} of the shock, possibly giving rise to a so-called
-``cosmic-ray shock precursor''.  Note that this is distinct from radiative
-precursors \citep[e.g.,][]{ghavamian2000}.
+% Energy dependence.
+Moreover, these controlling mechanisms predict different scalings for rim width
+as a function of energy.  Loss-limited rims should scale as $w \propto
+\nu^{-1/2}$.  Diffusion weakens this energy dependence by smearing out rims at
+all energies (even for energy-independent diffusion), yielding a slower
+drop-off in rim widths when diffusion dominates.  Magnetic damping, at a
+length scale where it may be considered a relevant control on rim widths (i.e.,
+length scale comparable to filament width) predicts energy-independent rim
+widths -- intuitively, if the magnetic field turns off, synchrotron radiation
+turns off regardless of electron energy.  \citet{ressler2014} give a much
+fuller exposition of the relative effects of advection, diffusion, and magnetic
+field damping.
 
-Mention relevance to: cosmic ray acceleration, turbulent field amplification,
-(note assumptions in re proton/electron spectra).  Cut-off energy of injected
-electrons?  Broadly, all astrophysical shock processes: AGN jets, galaxy
-clusters \citep{van-weeren2010}, PWNe, et cetera.  Usual background,
-utility spiel.
+% Which one is right?
+Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
+bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
+magnetic fields are amplified according to loss-limited model.  How could this
+be plausible?  There are possible explanations -- field amplification from
+plasma instabilities, evidence for stronger compression ratios?
+\citep{blondin2001}.  Numerical simulations and theory on this matter
+accounting for streaming instabilities, CR escape / energy losses, MHD
+equations, all sorts of things I can't keep track of.  But, magnetic damping
+model offers a tantalizing alternate explanation, and has not been tested.
+Equivocal results by \citet{araya2010} for Cas A.
+\citet{rettig2012} proposed discriminating based on filament spectra -- the
+expectation is that damped spectra are softer, loss-limited harder.
+\citet{ressler2014} developed the idea of investigating energy dependence and
+found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
+model.
 
-% ------------------------
-% Measurements and meaning
-% ------------------------
-\subsection{Prior measurements and inferred physical parameters}
+% Why Tycho's SNR
+To test these models, we turn to the filaments of Tycho's supernova remnant
+(hereafter, Tycho).
+Like all historical SNe, Tycho is close enough that we can spatially
+resolve these rims with \Chandra and say something useful.  Like SN 1006, Tycho
+has well defined synchrotron rims associated with expansion into a low-density
+ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
+\unit{cm^{-3}}$ from \textit{Spitzer} observations of shocked ISM dust
+emission, consistent with Tycho's X-ray expansion rate \citep{katsuda2010}; SN
+1006, by comparison, has pre-shock density $\abt 0.01$--$0.1 \unit{cm^{-3}}$ at
+its nonthermal NE, SW limbs \citep{acero2007}.
+\note[Aaron]{More disjointed}
+Mention molecular cloud interaction \citep{reynoso1999}? Maybe below in region
+selection as well.
+Previous estimates of Tycho fields/diffusion (something similar to Sean's table
+for SN 1006?).  CR acceleration (aside: \citet{eriksen2011}) evidence in Tycho,
+if relevant.
 
-Models for particle transport.  Bohm, sub-Bohm diffusion.
-Testable model predictions of magnetic damping \citep{pohl2005}.
-
-Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
-bamba2005-hist, bamba2005-vela, parizot2006} and consequences.
-Conclusion that magnetic fields are amplified.
-
-Equivocal results by \citet{araya2010} for Cas A.
-\citet{ressler2014} found rim narrowing in the remnant of SN 1006.
-
-% -----------
-% Tycho's SNR
-% -----------
-\subsection{Tycho's SNR}
-Why Tycho's supernova remnant (hereafter, Tycho)?
-
-Like SN 1006, Tycho has well defined synchrotron rims associated with expansion
-into a low-density ISM \note[Aaron]{justification: high density ISM would
-prevent the forward shock from running ahead of the thermal ejecta?}.
-\citet{williams2013} favor mean pre-shock ISM density $\abt 0.2 \unit{cm^{-3}}$
-from \textit{Spitzer} observations of shocked ISM dust emission,
-\note[Aaron]{is this proton or electron density?  Or are they equal pre-shock?
-Text mentions $n_e = 1.2 n_p$ \emph{post}-shock.}
-consistent with Tycho's X-ray expansion \citep{katsuda2010}.
-Compare w/ SN 1006 pre-shock density $n_p \abt 0.15$--$0.3 \unit{cm^{-3}}$
-\citep{raymond2007, heng2007, winkler2013}.  \note[Aaron]{ISM gradients?}
-
-Like all historical SNe, Tycho is close enough that we
-can spatially resolve these rims with \Chandra and say something useful.
-
-Previous estimates of Tycho fields/diffusion (something similar to Sean's table
-for SN 1006?).  CR acceleration.
-
-% -------------
 % Paper roadmap
-% -------------
-\subsection{Our work (paper roadmap)}
-
-We make measurements to distinguish between the two end member scenarios.
+\note[Aaron]{roadmap}
+We measure Tycho's rim widths, following the work of \citet{ressler2014}
+(hereafter, \citetalias{ressler2014}) in the remnant of SN 1006.  
+We make measurements to distinguish between two main scenarios
+(explain how diffusion/advection competition come into this).
 Our procedure, in both measurement and rim width modeling, follows that of
-\citet{ressler2014} (hereafter, \citetalias{ressler2014}) with only slight
-modifications.
+\citetalias{ressler2014} with only slight modifications.
 We first select regions around Tycho's forward shock for analysis, measure
@@
 Using two models for particle transport, we fit measured widths...
-
 We discuss the implications of our fits and models for magnetic shock
@@
 field amplification), and discuss particle diffusion/acceleration at the shock.
-
-Any further results (constraints on precursors, etc).
-
-Consequences, implications, why is this worthwhile?
+Any further misc. applications (constraints on precursors, etc).
 
@@
 % =============================
-\section{Transport models}
+\section{Electron transport models}\label{sec:transport}
 
-We first briefly review the models we consider for particle transport; a fuller
-exposition is given by \citetalias{ressler2014}.
+We briefly review relevant particle transport models that we use to fit our
+measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
+\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
+derived equations should we give?}  In particular, the transport models 
+account for both advection and diffusion simultaneously, as opposed to
+considering the lengthscales separately with advection dominating below a
+critical energy and diffusion, above
+\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
+\note[Aaron]{clarify, be more specific}.
+The effects of varying various parameters, especially in regards to filament
+energy dependence, are explored in detail by \citetalias{ressler2014}.
 
-Just present the governing transport equations.  From:
+% TODO Choose names for these models and refer to them consistently, throughout
+% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
+%      notation is being used)
+\note[Aaron]{Double check against Rettig/Pohl.  Variable definitions will be
+added when equations/exposition is closer to final state.}
+The electron distribution which gives rise to the observed synchrotron
+radiation is injected at the forward shock and transported by advection
+and plasma diffusion, following the advection-diffusion equation:
 \[
@@
 \]
-we obtain (1-D time-independent flow, neglect compressible flow?!,
+By considering only steady-state transport and some other assumptions
+(1-D flow (did we neglect the spherical coord terms?), neglect compressible flow?!,
 space-independent diffusion coefficient):
 \[
-    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C
+    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
 \]
-and by selection of the source/sink term $C$ we obtain either a
-simplified model:
+The source/sink term $C$ reflects assumptions about the injected electron
+energy spectrum and its time/space evolution.
+A first approximation is to treat electrons as having constant energy, but
+dumping energy catastrophically after a synchrotron timescale
+$\tsynch$ \note[Aaron]{define this -- either Section~\ref{sec:transport} before jumping into
+transport models, or in the intro}, yielding:
 \begin{equation} \label{eq:simp-mod}
@@
 \end{equation}
-where this is equation (6) of \citetalias{ressler2014}; we also look at
+where this is equation (5) of \citetalias{ressler2014}.
+Equation~\eqref{eq:simp-mod} has a convenient analytic solution (note that
+neglecting diffusion, this is $\ptl f/\ptl x \propto -f/(\tsynch v_d)$.
+A more advanced model is given by accounting for continuous radiation energy
+losses while electrons are transported downstream, given as:
 \begin{equation} \label{eq:full-mod}
@@
 Explain how we back out a filament shape/width from these models
+
+\subsection{Energy dependent widths, diffusion}
+
+Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
+\[
+    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
+\]
+Explain the use of fiducial energy -- this makes sense and eases discussion,
+but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
+murky.
+
+For the simple model, we have equation (6) of \citetalias{ressler2014}:
+\begin{equation} \label{eq:simp-width}
+    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
+\end{equation}
+which we relate to full width half max by projection factor $\beta = 4.6$
+so that $w = \beta a$, assuming (1) electron distribution exponential in radial
+coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
+\citep{ballet2006}.
+
+For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
+electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
+\citet{rettig2012}; DETAILS.
+Ultimately, we integrate numerically computed electron distributions $f(E,x)$
+over energy to obtain synchrotron emissivity as
+\[
+    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
+\]
+where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
+$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is the one-particle synchrotron
+emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
+\citep{pacholczyk1970}.  Integrating emissivity over lines of sight yields
+\begin{equation} \label{eq:intensity}
+    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
+                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
+\end{equation}
+where $s$ is the line-of-sight coordinate.
+
+\subsection{Tycho parameters}
+
+Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
+energy following Rettig and Pohl (again cite Sean's paper).
+We use an electron spectrum cut-off energy of:
+\begin{align*}
+    E_{\mt{cut}} =
+        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
+        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
+        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
+        \left[
+            \frac{E_h^{\mu - 1}}{\eta}
+        \right]^{1 / (1 + \mu)}
+\end{align*}
+which is equation~(19) of \citetalias{ressler2014}.
+\note[Aaron]{This differs from Sean's presentation -- I drew this from the
+Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
+the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
+$E_h$ ?!  Come back to this shortly.}
 
@@
 \section{Observations}
+\label{sec:observations}
 
 % TODO go through and double check tenses.
-\note[Aaron]{inconsistent present/past tense usage}
-We measured synchrotron rim widths from an archival \Chandra
-ACIS-I observation of Tycho
+We measured synchrotron rim full widths at half maximum (FWHMs) from an
+archival \Chandra ACIS-I observation of Tycho
 (RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
@@
 Merged and corrected events were divided into five energy bands:
-0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV;
-we excluded 1.7--2 keV counts to avoid \ion{Si}{13} (He$\alpha$) line
-emission, prevalent in the remnant's thermal ejecta, which could contaminate
-our nonthermal profile measurements.
+0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
+We excluded 1.7--2 keV energy range to avoid the \ion{Si}{13} (He$\alpha$)
+emission line at 1.85 keV, prevalent in the remnant's thermal ejecta, which
+\remove[Brian]{could} \remove[Aaron]{would} \add[Aaron]{may}
+\note[Aaron]{since some profiles are practically uncontaminated?}
+contaminate our nonthermal profile measurements.
 
@@
 (Figure~\ref{fig:snr}) based on the following criteria:
-(1) filaments should be singular and localized; multiple filaments must not
-overlap or completely overlap (rules out parts of NE limb);
-(2) filaments should have clear FWHMs in all bands, compared to background
-signal or downstream thermal emission (rules out some faint southern wisps);
-(3) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
-images; this rules out, e.g., areas of strong nonthermal and thermal emission
-on Tycho's eastern limb.
+(1) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
+images; this rules out, e.g., areas of strong thermal emission on Tycho's eastern limb.
+(2) filaments should be singular and localized; that is, multiple filaments
+should either not overlap or completely overlap (rules out parts of NE limb);
+(3) filaments should have clear FWHMs bands; i.e., a peak should be evident
+above the background signal or downstream thermal emission (rules out some
+faint southern wisps) \note[Aaron]{wishy-washy qualitative}.
 
 \begin{figure}
+    \centering
     %\plotone{figures/f0-snr.pdf}
-    \centering
     \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
@@
     0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
-    \note[Aaron]{Temporary figure; regions need re-numbering.}}
+    \note[Aaron]{Temporary figure; regions need re-numbering.}
+    \note[Aaron]{We could show the spectrum extraction regions on here too?
+    Maybe too cluttered.}}
     \label{fig:snr}
@@
 
-Discuss point-spread function if that may be a point of contention.
-Show that it is not a problem for us (simply say that all rims are at
-least ~1 arcsec and hence are spatially resolved? Compare,
-\citet{bamba2005-hist} measured upstream/downstream scale widths separately?)
+All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
+\textit{Chandra}'s point-spread function.
+
+% ----------------
+% Filament spectra
+% ----------------
+\subsection{Filament spectra}
+\label{sec:spec}
+
+We extracted spectra for all regions to check that rim width measurements are
+not affected by contaminating thermal line emission.  In each region, we
+selected upstream and downstream sections \note[Aaron]{any better word than
+`section'?} from which to extract spectra.
+The upstream section is the smallest sub-region that contains the measured FWHM
+bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
+captures the thin rim.
+The downstream section extends from the back of the rim (where the upstream
+section ends) to the rim model fit's
+(equation~\eqref{eq:prof}) downstream limit.
+Figure~\ref{fig:spec} plots an example profile (4.5--7 keV) with the
+downstream and upstream sections highlighted; the dividing line is set at the
+\textbf{???--???} energy band's downstream FWHM limit (see Figure~\ref{fig:profiles}).
+Background spectra were extracted from circular regions around the remnant's
+exterior \note[Aaron]{give size in arcsec?}; each region's spectra used the
+closest background region's spectrum \note[Aaron]{a bit awkward}.
+
+% TODO must match fig:profiles!  Keep both figures' region numbers updated and
+% consistent.
+\begin{figure}
+    \plotone{figures/f0-spec.pdf}
+    \caption{Example spectra and fits from Region 1. Left: example profile
+    ($4.5$--$7 \unit{keV}$) with highlighted downstream (blue) and upstream
+    (grey) sections. These sections are fixed for Region 1, regardless of
+    energy band (to be absolutely clear).  Middle: downstream spectrum with
+    fitted absorbed power law; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
+    clearly visible.  Right: upstream spectrum with fitted absorbed power law
+    shows that the thin rim is not contaminated by line emission.}
+    \label{fig:spec}
+\end{figure}
+
+We fit $0.5$--$7 \unit{keV}$ spectra from each region's upstream and downstream
+sections to an absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) with
+spectral index $n$, hydrogen column density $n_H$, and a normalization as free
+parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
+$\chi^2$s for all regions.  Spectra from thin rims (upstream sections) are
+well-fit by the power law model alone; spectra from sections downstream of the
+rims are generally poorly-fit, reflecting thermal contamination primarily from
+\ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$ keV.
+Although most downstream spectra show thermal contamination, some regions
+(e.g., 3, 4 on Tycho's northwestern limb) are reasonably well-fit by an
+absorbed power law as well due to a larger distance between the forward shock
+and contact discontinuity.
+Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
+synchrotron radiation spectra for ???? population of electrons
+\note[Aaron]{citation for e- distr. indices?}. Best fit column densities have
+range ($0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$) consistent with previous
+fits to Tycho's nonthermal rims \citep{hwang2002} but somewhat larger than
+values reported from radio and optical? HI absorption line measurements
+($\abt0.5 \times 10^{22}$ in radio \citep{albinson1986} per \citet{hwang2002};
+$\abt0.35 \times 10^{22}$ by \citet{kothes2004}, $\abt 0.4 \times 10^{22}$ from
+extinction--gas ratio (references in \citet{black1984})...).
+% TODO keep stated ranges of spectral indices, column densities up to date
+
+\note[Aaron]{On rob's suggestion of fitting thermal model -- can we get away
+with just fitting line emission and constraining from there? or is the
+whole NEI apparatus needed.  If we add thermal components -- report spectral
+indices and show better fit / spectral softening (confirmation)?}
+
+% TODO short script to build table from saved spectra fits
+% TODO keep region numbers updated (discussion of good/bad downstream spectra)
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Absorbed power law fit parameters for all regions' upstream and
+    downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
+    are consistent with a lack of thermal emission, whereas downstream spectra
+    are often poorly-fit by an absorbed power law due to line
+    emission (e.g., Figure~\ref{fig:spec}).\label{tab:spec}}
+    \input{tab-spec.tex}
+\end{table}
+
+Table~\ref{tab:spec} confirms that our region selections are practically free
+of thermal line emission, as already suggested by visual inspection
+(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2
+\unit{keV}$ photons should further limit any thermal contamination, as
+the $1.85 \unit{keV}$ Si line emission is over a third of Tycho's thermal flux
+as detected by \Chandra \citep{hwang2002}.  We may safely proceed to model our
+measured rim widths as being due entirely to nonthermal radiation
+\note[Aaron]{horrid phrasing}.
 
@@
 \subsection{Filament width measurements}
+\label{sec:fwhms}
 
-We obtained radial intensity profiles by integrating along the shock in each
-region.  Intensity profiles peak sharply at/behind the shock, demarcating our
-thin rims, \note[Aaron]{abt 2--3 arcsec; measure this or report $w_u$?}
-and then fall off until thermal emission from ejecta picks up at Tycho's
-``contact discontinuity'' \citep{warren2005}.
+% TODO keep mentioned number of regions updated!
+% TODO regions 2,3; 6,7 should be stretched forward a little more
+%      just to be more consistent (just from eyeballing...)
+We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
+shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
+energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
+8$--$24\arcsec$) in each region.  \note[Aaron]{Box dimensions are all over the
+place} Plotted and fitted profiles are reported in vignetting and
+exposure-corrected \note[Aaron]{double check CIAO guides} intensity units;
+error bars are computed from raw count data assuming Poisson statistics.
+Intensity profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
+demarcating our thin rims, and then fall off until thermal emission from ejecta
+picks up at Tycho's contact discontinuity \citep{warren2005}.
 
-We fit rim profiles, obtained by integrating intensity along the shock in each
-region, to a piecewise two-exponential model:
+We fitted rim profiles, obtained by integrating intensity along the shock in
+each region, to a piecewise two-exponential model:
 \begin{equation} \label{eq:prof}
@@
 where $h(x)$ is profile height and $x$ is radial distance from remnant center.
-The rim model, which we emphasize is strictly empirical, has 6 free parameters
-$A_u, x_0, w_u, w_d, C_u, C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
+The rim model, which we emphasize is strictly empirical, has 6 free parameters:
+$A_u, x_0, w_u, w_d, C_u$, and $C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
 continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
 bamba2005-hist} and differs slightly from that of \citetalias{ressler2014}.
-To fit only the nonthermal rim in each intensity profile, we smoothed profiles
-with a 21-point ($\abt 10\arcsec$) Hanning window and bounded the fit
-domain at the first local data minimum downstream of rim peak; the fit domain
-extends upstream to the region's outer edge.
+To fit only the nonthermal rim in each intensity profile, we selected the fit
+domain for each profile as follows.  The downstream bound was set at the first
+local data minimum downstream of the rim peak, as identified by smoothing the
+profiles with a 21-point ($\abt 10\arcsec$) Hanning window.  The upstream bound
+was set at the profile's outer edge (i.e., no data were removed).
 
+\begin{figure*}[ht]
+    \plotone{figures/f0-prfs.pdf}
+    \caption{Profile fits for Region 1}
+    \label{fig:profiles}
+\end{figure*}
+
+% TODO do all the work, but with different FWHM calculation -- to confirm
+%      that it doesn't make a big difference...
+% TODO subtract $\min(C_u, C_d)$ from profiles before getting FWHM, then
+%      come back and edit the text.
+% TODO keep region numbers here updated!
 From the fitted profiles we extracted a full width at half maximum (FWHM) for
-each region and each energy band.
-\note[Aaron]{We did NOT subtract out $\min(C_u, C_d)$ before measuring FWHM
-(fix this?).  May mention effect of using slightly different models for FWHMs}
-We could not resolve a FWHM in regions 2, 6, 8, 9, and 11 \note[Aaron]{KEEP
-UPDATED} at 0.7--1 keV (Table~\ref{tab:flmt2} \note[Aaron]{UPDATE depending on
-how we present/tabulate FWHMs}); in these regions, the downstream FWHM bound
-would extend outside the fit domain.  We were able to resolve FWHMs for all
-regions at higher energy bands (1--7 keV).
+each region and each energy band.  We could not resolve a FWHM in regions 2, 6,
+8, 9, and 11 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
+the downstream FWHM bound would extend outside the fit domain or we could not
+find an acceptable fit to equation~\eqref{eq:prof}.  We were able to resolve
+FWHMs for all regions at higher energy bands (1--7 keV).
 
@@
 profile by mapping radial coordinate $x$ to
-$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x))$ with $\xi$ an arbitrary stretching
-parameter; this yields a new profile $h'(x) = h(x'(x))$.
-We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7,
-yielding confidence limits on our measured FWHMs.
-
-% ----------------
-% Filament spectra
-% ----------------
-\subsection{Filament spectra}
-
-We extracted and fitted spectra for all regions to confirm that our rim width
-measurements are not contaminated by thermal line emission.
-We divided each region into an upstream and downstream band.  The upstream band
-is the smallest sub-region containing FWHM bounds from all energy bands.
-The downstream band extends from the back of the rim (where the upstream band
-ends) to the rim model fit's (equation~\eqref{eq:prof}) downstream limit.
-Figure~\ref{fig:spec} plots an example profile (Region 1, 4.5--7 keV) with the
-downstream/upstream selections highlighted in light blue/gray respectively.
-We fitted spectra from each region to an absorbed power law between $0.5$ and $7$
-keV in XSPEC.
-
-TODO?! We also fit the spectra to absorbed power law models with 1 and 2
-additional Gaussian components for \ion{Si}{13} and \ion{S}{15} He$\alpha$
-lines at $\abt 1.8$, $2.4$ keV.  We compute some equivalent width, or compare
-the goodness-of-fit with and without the additional lines, to rule out the
-presence of a line (but, cf. \citet{protassov2002} on line detection
-statistics!).
+$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
+parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
+this yields a new profile $h'(x) = h(x'(x))$.
+We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
+and the stretched or compressed FWHMs as upper/lower bounds on our reported
+FWHMs.
 
@@
 \subsection{Filament model fitting}
+\label{sec:fits}
 
+% Fit data to models
 We fitted the two transport models given by Equations~\eqref{eq:simp-mod} and
-\eqref{eq:full-mod} to the measured data.  Here we present only the full
-model (equation~\eqref{eq:full-mod}) fits.  \note[Aaron]{Could we present the
-full model alone, given that the numbers / qualitative trends for both models
-are fairly similar?  In \citetalias{ressler2014} Sean used the simple model to
-build intuition and gain physical insight, to great effect.  But, will we need
-that here?}
+\eqref{eq:full-mod} to our measured rim widths as a function of energy.
+Although our profiles are summed counts from a continuous energy range, we
+assigned each width measurement to the lower energy limit of its band
+(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
+model profile widths at $0.7 \unit{keV}$). \note[Aaron]{bad wording}
+We also average the positive and negative error bars on each FWHM measurement
+(Table~\ref{tab:fwhms}) for least squares fitting.
+% Averaging/merging/synthesizing, somehow, our results
+Rim widths from each region are fitted separately; we consider filament and
+remnant-wide physical parameters by averaging best fit parameters for each
+region in Section~\ref{sec:fit-results}.
 
-Explain why we are fixing $\mu$.
-Explain why we also give results with $\eta_2$ fixed at $1$.
-
-To perform fits, we tabulated a large grid for fixed values of $\mu$ and shock
-velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10 \unit{mG}$,
-we deem it effectively unconstrained (only a few fits do so, and only to the
-$\eta_2$ limit).
-Note that we do not allow / consider fits with $\eta_2$ negative (may be
-trivial, just note parameter bounds).
+% Model knobs and how we twiddled them
+We have three parameters to vary (more if we consider magnetic damping).
+They are diffusion-energy scaling exponent $\mu$, normalized diffusion
+coefficient $\eta_2$, and magnetic field strength $B_0$.
+Explain why we are fixing $\mu$ (forward reference best fit figures).
+We consider $\mu = 0, 1/3, 1/2, 1, 3/2, 2$; recall that $\mu = 1/3$ and $1/2$
+respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
+energy spectra.  Explain why we also give results with $\eta_2$ fixed at $1$.
 
@@
 shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
-\citep{green2009}.  Tycho's forward shock velocity varies azimuthally by up to
+\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
 a factor of 2; we interpolate the data of \citet{williams2013} to estimate
 individual shock velocities for each of our regions.
+\note[Aaron]{this might belong in Section~\ref{sec:transport}?}
 
-As the full continuous loss model must be numerically solved, its predicted
-rim widths are subject to resolution error in the numerical integrals.  We
-chose our integration resolutions such that the fractional error associated
-with halving/doubling our resolution is less than $1\%$ for the
-parameter space relevant to our filaments. \note[Aaron]{rewrite -- unclear.
-Need to verify $1\%$ claim + check Pacholczyk table resolution...}
+% How to do the fit
+The simple model is readily fit from equation~\eqref{eq:simp-width}.
+The full model is numerically computed following the procedure laid out in
+\emph{section ?!}, yielding intensity profiles from equation~\eqref{eq:intensity} for each
+energy band and hence a model full width at half maximum.
+For least squares fitting purposes, the full model is treated as a black box
+that takes in physical parameters
+% TODO modify tables to match what is stated here -- in regards to parameters
+% being effectively unbounded.
+% TODO for extreme values in tables -- go back and double check chi^2 space
+To perform full model fits, we tabulated a large grid for fixed values of $\mu$
+and shock velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10
+\unit{mG}$, we deem it effectively unconstrained (only a few fits do so, and
+only to the $\eta_2$ limit).  Note that we do not allow / consider fits with
+$\eta_2$ negative (may be trivial, just note parameter bounds).  As the full
+continuous loss model must be numerically solved, its predicted rim widths are
+subject to resolution error in the numerical integrals.  We chose our
+integration resolutions such that the fractional error associated with
+halving/doubling our resolution is less than $1\%$ for the parameter space
+relevant to our filaments. \note[Aaron]{rewrite -- unclear.  Need to verify
+1\% claim and check Pacholczyk table resolution (and possibly Bessel
+function numbers)...}
+
+% Errors
+Finally, we computed errors on our best fit parameters by varying each
+parameter and obtaining a new best fit model, with one less degree of freedom,
+to find the limit s.t. $\Delta \chi^2 = 1$ to obtain a roughly 1-sigma error.
+Granted, this is not guaranteed correct for nonlinear fits (that $\Delta \chi^2
+= 1$ corresponds to a $68.3$\% confidence limit), but should be good enough.
 
@@
 
-Explain a bit about how we divvy up / present the results.  What values are we
-averaging, where do our errors come from?
-For each region, give the relevant shock velocity value (and a range of
-values?).
-We do X to the FWHMs (geometric/arithmetic average) within each filament.
-
 % --------------------
@@
 % --------------------
-\subsection{Rim fits, spectra, and width measurements}
+\subsection{Rim widths}
+\label{sec:fwhm-results}
 
-We give figures and tables with rim profile fit information.
+In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
+As previously noted, we could not resolve FWHMs for some regions in the 0.7--1 keV band.
+NOTE very low counts/numbers of regions for some averages (typically 1--2, see
+Figure~\ref{fig:snr}).
 
-\begin{figure}
-    \plotone{figures/f0-prfs.pdf}
-    \caption{Profile fits for Region 1}
-    \label{fig:profiles}
-\end{figure}
+Mention the number of counts in individual profiles?
+May affect whether we go back and take smaller regions, or not.
 
-\begin{table*}[h]
+% TODO give individual regions' FWHMs and m_E values
+\begin{table*}[ht]
     \scriptsize
     \centering
-\caption{Filament 2 full width at half max measurements.
-Exponent $m_E$ estimated point to point.\label{tab:flmt2}}
-\input{tab-fwhms.tex}
-\tablecomments{Mean FWHMs computed by arithmetic mean, errors from blah}
+    \caption{Averaged filaments NO UPDATE THIS\label{tab:fwhms}}
+    \input{tab-fwhms-ave-arith.tex}
+    \input{tab-fwhms-ave-geom.tex}
+    \tablecomments{Errors computed as standard errors of mean, see text}
 \end{table*}
-
-Table~\ref{tab:flmt2} lists some numbers from Filament 2.  As previously noted
-we could not resolve FWHMs for some regions in the 0.7--1 keV band.
-
-Error estimates / magnitudes.
-
-Mention the number of counts.  This might impact our decision to go back and
-slice regions smaller (if we do that).
-
-\begin{figure}
-    \plotone{figures/f0-spec.pdf}
-    \caption{Spectra from Region 1 (I think?)}
-    \label{fig:spec}
-\end{figure}
-
-Here, mention any upper bounds on spectral lines (equivalent width or w/e).
-Since this is not a ``result'', being ancillary to our work.
-
-Table of best fit chi-squares, power law indices for spectral fits...
 
@@
 \subsection{Model fit results}
+\label{sec:fit-results}
 
-Here are some fit results for a subset of regions, just those contained in
-Filament 1 (Table~\ref{tab:fit}).  Errors are estimated by 
-Explain error values on parameters
+% TODO keep updated -- give tables for ONE region with both simple, full fits
+We find that the simpler catastrophic dump model (equation~\eqref{eq:simp-mod})
+produces the same qualitative trends seen in the full continuous energy loss
+model.
+The first row of Table~\ref{tab:fits} compares simple and full model fits for
+Region 1(?).
+The key differences are \emph{blah}.  The errors are comparable, the parameters
+are comparable but shifted by X amount; this is consistent in all filaments?
+(details tbd).  Consequently, we present only the full model fits for all other
+filaments in Table~\ref{tab:fits}.  However, the simple model is useful for
+building intuition and we will refer to its results in the following discussion
+(?); \citetalias{ressler2014} also give examples of simple model fits in SN
+1006 \note[Aaron]{sentence maybe unnecessary}.
+
+% Individual region fit results
+Table~\ref{tab:fits} presents full model fit results for all regions
+considered. Errors are computed by varying free parameters $B_0$,
+$\eta_2$ to obtain $\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence
+limits on our fit parameters.
+
+HERE we show two examples of fits -- one where the models just happen to fit
+the data very nicely, and one where the models are way off (enormous $\chi^2$
+and/or errors too small).  We specifically choose to highlight the most extreme
+cases, to emphasize that our fits are hit-and-miss in practice.
+We also show the simple model fits here to illustrate the similar qualitative
+behavior between simple/full model fits.
+
+% TODO Assemble table of regions
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Full model best fits for individual regions, Filament 1.
+    \label{tab:fits}}
+    \input{tab-fits-flmt1.tex}  % TODO CHANGE/UPDATE THIS
+\end{table*}
+
+In Figure~\ref{fig:fits} we plot the full model fits for the same regions
+tabulated in Table~\ref{tab:fits}
+
+% TODO Assemble all the individual plots.
+\begin{figure}[ht]
+    \centering
+    \plottwo{figures/f0-fits-avg-flmt1.png}{figures/f0-fits-avg-flmt2.png} \\
+    \plottwo{figures/f0-fits-avg-flmt3.png}{figures/f0-fits-avg-flmt4.png} \\
+    \plottwo{figures/f0-fits-avg-flmt5.png}{figures/f0-box.png}
+    \plottwo{figures/f0-fits-avg-flmt1-geom.png}{figures/f0-fits-avg-flmt2-geom.png} \\
+    \plottwo{figures/f0-fits-avg-flmt3-geom.png}{figures/f0-fits-avg-flmt4-geom.png} \\
+    \plottwo{figures/f0-fits-avg-flmt5-geom.png}{figures/f0-box.png}
+    \caption{Plots of best-fits to averaged FWHMs (arithmetic, geometric avg).
+    \note[Aaron]{Need better subplot display in final version, if we keep these}}
+    \label{fig:fits-all}
+\end{figure}
+
+% Individual region fits with eta2=1 fixed
+We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
+diffusion at $2 \unit{keV}$.  We found that the best fit $B_0$ is relatively
+insensitive to $\mu$; for all regions, $B_0$ varies by no more than XXX ($\abt 10$)\% from
+the value at $\mu = 1$ (with larger $B_0$ at smaller $\mu$ and vice versa).
+\note[Aaron]{compute/verify this}.
+Therefore, we show only best fits with $\mu = 1$ and $\eta_2 = 1$ fixed in
+Table~\ref{tab:fits-avg-eta2-fix}).
 
@@
     \centering
-\caption{Full model best fit parameters, Filament 1.
-    \label{tab:fit}}
-\input{tab-fits-flmt1.tex}
+    \caption{Best fits with $\eta_2 = 1$ fixed, for filament averaged FWHMs.
+    \label{tab:fits-avg-eta2-fix}}
+    \input{tab-fits-avg-eta2-fix.tex}
 \end{table*}
 
-Table~\ref{tab:fit-avg-fwhm} shows best fits to averaged FWHMs (averaged FWHMs
-not shown).  For FWHM errors, I use the standard error of the mean (with some
-minor nuances; I am using sample standard deviation).
+% Averaged fit results
+In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
+constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
+reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
+of the mean \note[Aaron]{may need to scale by $\abt 2 \times$ to get 1-sigma
+confidence interval since our sample sizes are so small}.  We note that both
+averages and errors are strongly affected by outliers from extreme best fit
+values, as can be seen in Table~\ref{tab:fits-all} -- especially as the typical
+number of regions per filament (i.e., our sample size) is quite small.
 
@@
     \centering
-\caption{Full model best fit parameters for filament-averaged FWHMs.
-    \label{tab:fit-avg-fwhm}}
-\input{tab-fits-avg.tex}
-\end{table*}
-
-Finally, Table~\ref{tab:fit-avg-par} shows averaged best-fit parameters for
-Filament 1 only, at this time.  The parameter errors are standard errors from
-the averaging process and may reflect the presence of outliers.
-
-\begin{table*}
-\scriptsize
-\centering
-\caption{Average of best-fit parameters for individual regions
-    \label{tab:fit-avg-par}}
+    \caption{Filament-wide average of best-fit parameters for constituent regions.
+    \label{tab:fits-avg}}
     \input{tab-fits-par-avg.tex}
@@
 
-\begin{table*}
-\scriptsize
-\centering
-\caption{Full model best fit parameters, Filament ??, with $\eta_2 = 1$ fixed}
-%    \label{tab:fit-avg-par}}
-%\input{tab-fits-par-avg.tex}
-Coming soon...
-\end{table*}
+% Global fits...
+Finally, we report a global average of best fit parameters from all regions.
+We could toss this into Table~\ref{tab:fits-avg}.  Reported errors are
+again standard errors of the mean (not CI, use CI? I dunno), which gives an
+idea of the spread of our measurements.
+
+Plot of best fit parameters with $\mu=1$ as a function of azimuth angle, with
+error bars or something similar?
 
@@
 
-What do all these numbers with their errors mean?
+\subsection{How confidently can we reject B-damping?}
+
+Everything hinges on our error bars -- this is most important.  Our rims do
+thin consistently, in most regions (might be one or two places where they
+don't), but (1) the errors in our individual FWHMs are larger than I'm
+currently reporting because different profile fits will give a larger spread of
+FWHMs (might need to consider reduced chi-squared here, but using chi-sqr to
+select profile fit models is not physically meaningful)
+
+It would be helpful to average $m_E$ values together, under the
+assumption that they should be somewhat consistent within a given filament.
+Then report the values and errors observed.
+
+Recall that our FWHMs (Table~\ref{tab:fwhms}) have a large range of values,
+IF magnetic damping is relevant in controlling filament widths, we might, e.g.,
+expect a maximum filament width at which $m_E$ sharply levels off, being now
+restricted by the magnetic field turn off.  We simply do not observe this in
+our data between $0.7$--$7 \unit{keV}$.  We must conclude that, as in SN 1006
+\citepalias{ressler2014}, magnetic damping cannot be relevant to our
+observations.
+
+What is the smallest damping scale length that is (roughly) consistent with all 
+of our observations?
+
+\subsection{Interpretation of fit parameters}
+
+Magnetic field $B_0$: despite the large range of fit quality, we can give
+fairly robust lower bounds.  Give lowest bound?  Consistent with previous
+studies, Tycho requires strong magnetic field amplification -- up to ??? times
+the expected value of $\abt 10 \unit{\mu G}$ from a strong adiabatic shock with
+compression ratio $r=4$ and typical galactic magnetic field strength of $\abt
+2$--$3 \unit{\mu G}$ \citep{lyne1989, han2006}.
+
+Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.
+
 Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
 
-How meaningful are our parameter estimates and errors?
+\subsection{Bohm diffusion}
+
+Fixing $\mu = 1$ and $\eta_2 = 1$ in Table~\ref{tab:fits-avg} is equivalent to
+assuming Bohm diffusion, as most previous studies have done.
+We should find/show that our result is very similar to theirs, in terms of
+$B_0$ estimates, and this may be the easiest way to back out any estimates of
+azimuthal magnetic field variation.
 
@@
 
-Constraints on diffusion / B field, if any.  What impact this has for models of
-B amplification etc.
+\subsection{Other things}
+
+Precursors, rim position variation (none obvious from preliminary look; see
+Figure~\ref{fig:peak-pos}), steepness of the filament rise?
+
+\begin{figure}
+    \centering
+    \plotone{figures/f0-peak-pos.pdf}
+    \caption{Best-fit rim peak positions ($x_0$ in equation~\eqref{eq:prof})
+        for all regions as a function of energy band, normalized to the $2
+        \unit{keV}$ peak position.  Red line plots best linear fit to all data
+        with slope of $-0.025 \unit{arcsec/keV}$.
+        \label{fig:peak-pos}}
+\end{figure}
 
@@
 
-\begin{table}[h]
-\scriptsize
+\begin{table}[ht]
+    \tiny
     \centering
-\caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}}
-\label{tab:sean}
+    \caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
+    \label{tab:sean}}
     \input{tab-sean.tex}
@@
 
-\begin{table*}[h]
-\scriptsize
+\begin{table*}[ht]
+    \tiny
     \centering
-\caption{SN 1006 best fit parameters, 2 highest energy bands (full model)}
-\label{tab:sn1006-2band}
+    \caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
+    \label{tab:sn1006-2band}}
     \input{tab-sn1006-2band.tex}
@@
 
-\begin{table*}[h]
-\scriptsize
+\begin{table*}[ht]
+    \tiny
     \centering
-\caption{SN 1006 best fit parameters, 3 energy bands (full model)}
-\label{tab:sn1006-3band}
+    \caption{SN 1006 best fit parameters, 3 energy bands (full model).
+    \label{tab:sn1006-3band}}
     \input{tab-sn1006-3band.tex}

### 2014-09-18 code/profiles/crvfit.py
Refactor profile/FWHM fits, alter folder structure
Separate profile prep (error calculation, etc) from profile fitting and
FWHM computation.  Refactored FWHM code (in vein of full model code),
change FWHM and profile fit intermediate data format.

@@ -1,0 +1,93 @@
+"""
+XSPEC-like functionality to freeze fit parameters
+Basically extends scipy.optimize.curve_fit
+
+Next time, use lmfit instead -- much easier
+
+Aaron Tran
+July 2014 (moved to .py Sept 2014)
+"""
+
+import numpy as np
+import scipy as sp
+
+def freeze_func(f, pars, ls_freeze):
+    """Make frozen function
+    Ex: if ls_freeze = [1,2,4], this builds expression:
+    lambda x,p0,p3,p5,p6,p7 : f(x,p0,pars[1],pars[2],p3,pars[4],p5,p6,p7)
+    """
+    lambd_args = 'x,'
+    lambd_body = 'f(x,'
+    for i in xrange(len(pars)):
+        if i in ls_freeze:
+            lambd_body += 'pars[{:d}],'.format(i)
+        else:
+            lambd_args += 'p{:d},'.format(i)
+            lambd_body += 'p{:d},'.format(i)
+
+    lambd_args = lambd_args[:-1]
+    lambd_body = lambd_body[:-1] + ')'
+
+    # To explain the `f=f, pars=pars`, see http://stackoverflow.com/q/7349785
+    # More than one way to skin a cat, though
+    lambd_str = 'lambda ' + lambd_args + ', f=f,pars=pars : ' + lambd_body
+    return eval(lambd_str)
+
+def run_frz_fit(x, y, y_err, f, pars, ls_freeze, **kwargs):
+    """Perform fit with frozen parameters
+    func has form func(x, *pars)
+    pars is a list of initial guesses
+    ls_freeze is a list of parameter indices that are to be frozen.
+    """
+
+    if len(ls_freeze) > 0:
+        fit_func = freeze_func(f, pars, ls_freeze)
+        p_fit = [pars[i] for i in xrange(len(pars)) if i not in ls_freeze]
+    else:
+        fit_func = f
+        p_fit = pars
+
+    popt, pcov = run_fit(x, y, y_err, fit_func, p_fit, **kwargs)
+
+    popt_aug = popt
+    if len(ls_freeze) > 0:
+        for i in ls_freeze:
+            popt_aug = np.insert(popt_aug, i, pars[i])
+
+    return popt, pcov, popt_aug
+
+def run_fit(x, y, y_err, f, pars, **kwargs):
+    """Convenience wrapper for sp.optimize.curve_fit"""
[…]

### 2014-09-18 code/profiles/fsmooth.py

@@ -1,0 +1,87 @@
+"""
+Functions to smooth profiles and identify extrema for fit domains.
+The first minimum downstream of the thin rim bounds the fit domain.
+
+Aaron Tran
+July 2014 (split to .py file, Sept 2014)
+"""
+
+import numpy as np
+import scipy as sp
+from scipy import optimize
+from scipy import signal
+
+
+def ind_first_min(y, **kwargs):
+    """Index of first minimum to left of global non-edge max in smoothed data
+    If no such minimum is found, return 0 (i.e., don't cut the fit domain).
+    If no max (peak) is found, return 0.
+    **kwargs (window_len, window) passed to std_smooth
+    """
+    y_smooth = std_smooth(y, **kwargs)
+    inds_relmin = sp.signal.argrelmin(y_smooth)[0]
+    if len(inds_relmin) is 0:
+        return 0
+
+    try:
+        ind_max = get_ind_relmax(y, **kwargs)
+    except ValueError:
+        return 0
+
+    # Find the largest value in inds_relmin, that's smaller than ind_max
+    idx = np.searchsorted(np.sort(inds_relmin), ind_max)
+    if idx == 0:  # All relmin indices are farther right than ind_max?
+        return 0
+    return inds_relmin[idx-1]
+
+def get_ind_relmax(y, **kwargs):
+    """Get index of largest relative maximum in smoothed data
+    **kwargs (window_len, window) passed to std_smooth
+
+    If no relative maximum found, throws ValueError
+    """
+    ysmooth = std_smooth(y, **kwargs)
+    inds_relmax = sp.signal.argrelmax(ysmooth)[0]
+    # Get index of the largest relative maximum
+    if len(inds_relmax) == 0:
+        raise ValueError("No relative maximum found in y for given smoothing")
+
+    idx = np.argmax(ysmooth[inds_relmax])  # idx indexes inds_relmax, now
+    return inds_relmax[idx]
+
+def std_smooth(x, window_len=21, window='hanning'):
+    """Modified from scipy cookbook (http://wiki.scipy.org/Cookbook/SignalSmooth)
+    Add reflected copies of signals at each end to address convolution edge effects
+
+    Default window length of 21 pts, empirically works well for Tycho's SNR.
+    No problems with hanning, haven't tested other windows.  Choice shouldn't matter much.
+
+    Input:
+        x: array to be smoothed
+        window_len, window: window length/type.  Best if window_len is odd,
[…]

### 2014-09-18 code/profiles/prep_profile_fit.py

@@ -1,0 +1,161 @@
+"""
+Script to prepare DS9 extracted profiles for FWHM fitting -- convert
+x-coordinate to radial distance (arcsec), compute errors, compute fit_domain by
+smoothing profiles and identifying downstream local minimum
+
+Aaron Tran
+July (June?) 2014, converted to .py from .ipynb Sept. 2014
+"""
+
+import argparse
+import numpy as np
+
+import regparse
+import fsmooth
+
+ACIS_PX2ARCSEC = 0.492  # Chandra ACIS pixel size, arcseconds
+# http://cxc.harvard.edu/proposer/POG/html/chap6.html
+
+def main():
+    """Run from command line as, e.g.,
+    python prepare_profile_fit.py 'regions-1.physreg' 'profiles/prf'
+                                  'profiles/prf-cts' --bin 1
+                                  --labels '0.7-1kev' '1-2kev' '2-7kev'
+    Generates lots of files
+    """
+    parser = argparse.ArgumentParser(description=
+             ('Make usable profile data for FWHM fitting.  Process output of '
+              'ds9projplotter.py: convert to arcsec, compute errors. '
+              'Outputs .npz and .dat files; downstream scripts use .npz, but '
+              'plaintext (.dat) is nice for archiving.'))
+    parser.add_argument('ds9physreg', help='DS9 region file, physical coords')
+    parser.add_argument('inroot', help='Intensity profiles, file root')
+    parser.add_argument('ctroot', help='Uncorrected count profiles, file root')
+    parser.add_argument('outroot', help='Output profile root')
+
+    parser.add_argument('-b', '--binsize', default=1, type=float,
+                        help=('Bin size of images used to generate profiles; '
+                        'set in CIAO\'s merge_obs, reproject_obs plists'))
+    parser.add_argument('-l', '--labels', nargs='+',
+                        help='Energy band labels for profiles; must be '
+                             'sorted & consistent for subsequent analysis')
+
+    parser.add_argument('-w', '--window', default='hanning',
+                        help=('Window type for smoothing to set fit domain. '
+                        'Options: flat, hanning, hamming, bartlett, blackman '
+                        '(see fsmooth.std_smooth)'))
[…]

### 2014-09-19 manuscript/paper-tycho.tex
Refactor profile/FWHM fits, alter folder structure
Separate profile prep (error calculation, etc) from profile fitting and
FWHM computation.  Refactored FWHM code (in vein of full model code),
change FWHM and profile fit intermediate data format.
Pickle/json model fit outputs, table generation
Code and utilities to save simple/full model fit outputs
Directories structured accordingly.  New ipynb for profile/spectra
figures and tables.  A bit more paper work.

@@
 \note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
-remnants may exhibit thin (~1--10\% of shock radius) X-ray rims of synchrotron
+remnants may exhibit thin ($\abt1$--$10$\% of shock radius) X-ray rims of synchrotron
 radiation from forward shock-accelerated electrons that travel downstream of
@@
 
-% TODO go through and double check tenses.
+% NOTE go through and double check tenses.
 We measured synchrotron rim full widths at half maximum (FWHMs) from an
@@
 
+% NOTE generate final, higher quality figure + newer figure for regions-5
 \begin{figure}
@@
     0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
-    \note[Aaron]{Temporary figure; regions need re-numbering.}
-    \note[Aaron]{We could show the spectrum extraction regions on here too?
+    \note[Aaron]{Could show the spectrum extraction regions on here too?
     Maybe too cluttered.}}
@@
 \textit{Chandra}'s point-spread function.
+Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
+still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
+Is that good enough for us?
 
@@
 
+% NOTE be consistent in usage of word 'sections'
 We extracted spectra for all regions to check that rim width measurements are
 not affected by contaminating thermal line emission.  In each region, we
-selected upstream and downstream sections \note[Aaron]{any better word than
-`section'?} from which to extract spectra.
-The upstream section is the smallest sub-region that contains the measured FWHM
+selected upstream and downstream sections from which to extract spectra.  The
+upstream section is the smallest sub-region that contains the measured FWHM
 bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
-captures the thin rim.
-The downstream section extends from the back of the rim (where the upstream
-section ends) to the rim model fit's
-(equation~\eqref{eq:prof}) downstream limit.
-Figure~\ref{fig:spec} plots an example profile (4.5--7 keV) with the
-downstream and upstream sections highlighted; the dividing line is set at the
-\textbf{???--???} energy band's downstream FWHM limit (see Figure~\ref{fig:profiles}).
-Background spectra were extracted from circular regions around the remnant's
-exterior \note[Aaron]{give size in arcsec?}; each region's spectra used the
-closest background region's spectrum \note[Aaron]{a bit awkward}.
+captures the thin rim.  The downstream section extends from the back of the rim
+(end of the upstream section) to the rim model fit's (equation~\eqref{eq:prof})
+downstream limit.  We merged spectra from all \Chandra ObsIDs and grouped the
+data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
+profile (4.5--7 keV) with the downstream and upstream sections highlighted; the
+dividing line is set at the \textbf{???--???} energy band's downstream FWHM
+limit here (see Figure~\ref{fig:profiles}).
+We extracted background spectra from circular regions (radius $\abt 30\arcsec$)
+around the remnant's exterior; each thin rim region was matched to the closest
+background region's spectrum.
+% Background region size is valid for data-tycho/bkg-2/ selections
 
-% TODO must match fig:profiles!  Keep both figures' region numbers updated and
-% consistent.
-\begin{figure}
-    \plotone{figures/f0-spec.pdf}
-    \caption{Example spectra and fits from Region 1. Left: example profile
-    ($4.5$--$7 \unit{keV}$) with highlighted downstream (blue) and upstream
-    (grey) sections. These sections are fixed for Region 1, regardless of
-    energy band (to be absolutely clear).  Middle: downstream spectrum with
-    fitted absorbed power law; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
-    clearly visible.  Right: upstream spectrum with fitted absorbed power law
-    shows that the thin rim is not contaminated by line emission.}
+% NOTE must match fig:profiles!  Keep region numbers updated and
+% consistent.  Currently, region 1 of data-tycho/regions-4/ selections
+\begin{figure*}
+    \plotone{figures/fig-specs.pdf}
+    \caption{Spectra and fits from Region 1. Left: $4.5$--$7 \unit{keV}$
+    profile with highlighted downstream (blue) and upstream (grey) sections.
+    Intensity units are arbitrary (a.u.).  Middle: downstream spectrum with
+    absorbed power law fit; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
+    clearly visible.  Right: upstream spectrum with absorbed power law fit
+    shows that the filament is likely free of thermal line emission.}
     \label{fig:spec}
-\end{figure}
+\end{figure*}
 
@@
 parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
-$\chi^2$s for all regions.  Spectra from thin rims (upstream sections) are
-well-fit by the power law model alone; spectra from sections downstream of the
-rims are generally poorly-fit, reflecting thermal contamination primarily from
-\ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$ keV.
-Although most downstream spectra show thermal contamination, some regions
-(e.g., 3, 4 on Tycho's northwestern limb) are reasonably well-fit by an
-absorbed power law as well due to a larger distance between the forward shock
-and contact discontinuity.
+$\chi^2$ values for all regions.  Spectra from thin rims (upstream sections)
+are well-fit by the power law model alone; spectra from sections downstream of
+the rims are generally poorly-fit, reflecting thermal contamination primarily
+from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$
+keV.  Although most downstream spectra show thermal contamination, some regions
+(e.g., 4, 5 on Tycho's northwestern limb) are reasonably well-fit downstream by
+an absorbed power law as well due to a larger distance between the forward
+shock and contact discontinuity.
 Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
 synchrotron radiation spectra for ???? population of electrons
-\note[Aaron]{citation for e- distr. indices?}. Best fit column densities have
-range ($0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$) consistent with previous
-fits to Tycho's nonthermal rims \citep{hwang2002} but somewhat larger than
-values reported from radio and optical? HI absorption line measurements
-($\abt0.5 \times 10^{22}$ in radio \citep{albinson1986} per \citet{hwang2002};
-$\abt0.35 \times 10^{22}$ by \citet{kothes2004}, $\abt 0.4 \times 10^{22}$ from
-extinction--gas ratio (references in \citet{black1984})...).
-% TODO keep stated ranges of spectral indices, column densities up to date
+\note[Aaron]{citation for e- distr. indices?}. Best fit column densities from
+upstream spectra, between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$, are
+consistent with previous fits to Tycho's nonthermal rims \citep{hwang2002} but
+somewhat larger than $\abt0.35$--$0.5 \times 10^{22}$ from radio and optical??
+HI absorption line measurements \citep{black1984, albinson1986, kothes2004}.
+% NOTE keep stated ranges of spectral indices, column densities up to date
 
@@
 whole NEI apparatus needed.  If we add thermal components -- report spectral
-indices and show better fit / spectral softening (confirmation)?}
+indices and reconfirm spectral softening?}
 
-% TODO short script to build table from saved spectra fits
-% TODO keep region numbers updated (discussion of good/bad downstream spectra)
+% NOTE keep region numbers updated (in discussion of good/bad downstream spectra)
 \begin{table}
@@
     downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
-    are consistent with a lack of thermal emission, whereas downstream spectra
-    are often poorly-fit by an absorbed power law due to line
-    emission (e.g., Figure~\ref{fig:spec}).\label{tab:spec}}
+    are consistent with a lack of thermal emission, but values for downstream
+    fits indicate a poor fit due to line emission.
+    \label{tab:spec}}
     \input{tab-spec.tex}
@@
 measured rim widths as being due entirely to nonthermal radiation
-\note[Aaron]{horrid phrasing}.
+\note[Aaron]{bad phrasing}.
 
@@
 
-% TODO keep mentioned number of regions updated!
-% TODO regions 2,3; 6,7 should be stretched forward a little more
+% NOTE keep mentioned number of regions updated!
+% TODO regions 2,3; 6,7 should be stretched forward a little more in regions-5
 %      just to be more consistent (just from eyeballing...)
@@
 energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
-8$--$24\arcsec$) in each region.  \note[Aaron]{Box dimensions are all over the
-place} Plotted and fitted profiles are reported in vignetting and
-exposure-corrected \note[Aaron]{double check CIAO guides} intensity units;
-error bars are computed from raw count data assuming Poisson statistics.
-Intensity profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
+8$--$24\arcsec$) in each region.  Plotted and fitted profiles are reported in
+vignetting and exposure-corrected, but arbitrary, intensity units; error bars
+are computed from raw count data assuming Poisson statistics.  Intensity
+profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
 demarcating our thin rims, and then fall off until thermal emission from ejecta
@@
 \begin{figure*}[ht]
-    \plotone{figures/f0-prfs.pdf}
-    \caption{Profile fits for Region 1}
+    \plotone{figures/fig-profiles.pdf}
+    \caption{Best fit profiles with measured FWHMs demarcated for each energy
+             band in Region 1.  Red data points are excluded from profile fit
+             domain.}
     \label{fig:profiles}
@@
 
-% TODO do all the work, but with different FWHM calculation -- to confirm
-%      that it doesn't make a big difference...
-% TODO subtract $\min(C_u, C_d)$ from profiles before getting FWHM, then
-%      come back and edit the text.
-% TODO keep region numbers here updated!
+% NOTE keep blacklisted/excluded region numbers updated!
 From the fitted profiles we extracted a full width at half maximum (FWHM) for
 each region and each energy band.  We could not resolve a FWHM in regions 2, 6,
-8, 9, and 11 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
+and 8 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
 the downstream FWHM bound would extend outside the fit domain or we could not
@@
 FWHMs for all regions at higher energy bands (1--7 keV).
+% NOTE review the FWHM rejection criterion, on the final set of regions
 
@@
 % Fit data to models
-We fitted the two transport models given by Equations~\eqref{eq:simp-mod} and
+We fit the two transport models given by Equations~\eqref{eq:simp-mod} and
 \eqref{eq:full-mod} to our measured rim widths as a function of energy.
-Although our profiles are summed counts from a continuous energy range, we
-assigned each width measurement to the lower energy limit of its band
+Although our measured radial profiles sum a continuous energy range of counts,
+we assigned each width measurement to the lower energy limit of its band
 (e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
-model profile widths at $0.7 \unit{keV}$). \note[Aaron]{bad wording}
-We also average the positive and negative error bars on each FWHM measurement
+model profile widths at $0.7 \unit{keV}$) \note[Aaron]{bad wording}.
+We also averaged the positive and negative error bars on each FWHM measurement
 (Table~\ref{tab:fwhms}) for least squares fitting.
@@
 Explain why we are fixing $\mu$ (forward reference best fit figures).
-We consider $\mu = 0, 1/3, 1/2, 1, 3/2, 2$; recall that $\mu = 1/3$ and $1/2$
+We consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
 respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
-energy spectra.  Explain why we also give results with $\eta_2$ fixed at $1$.
+energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
+fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.
 
@@
 \citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
-a factor of 2; we interpolate the data of \citet{williams2013} to estimate
-individual shock velocities for each of our regions.
-\note[Aaron]{this might belong in Section~\ref{sec:transport}?}
+a factor of 2; we interpolated shock velocities reported by
+\citet{williams2013} to estimate individual shock velocities for each region.
+\note[Aaron]{this paragraph might belong in Section~\ref{sec:transport}?}
 
@@
 halving/doubling our resolution is less than $1\%$ for the parameter space
-relevant to our filaments. \note[Aaron]{rewrite -- unclear.  Need to verify
+relevant to our filaments.
+\note[Aaron]{rewrite -- unclear.  Need to verify
 1\% claim and check Pacholczyk table resolution (and possibly Bessel
@@
 \begin{table*}[ht]
-    \scriptsize
+    \tiny
     \centering
-    \caption{Averaged filaments NO UPDATE THIS\label{tab:fwhms}}
-    \input{tab-fwhms-ave-arith.tex}
-    \input{tab-fwhms-ave-geom.tex}
-    \tablecomments{Errors computed as standard errors of mean, see text}
+    \caption{FWHMs for all regions.\label{tab:fwhms}}
+    %\input{tab-fwhms-ave-arith.tex}
+    %\input{tab-fwhms-ave-geom.tex}
+    \input{tab-fwhms.tex}
 \end{table*}
@@
 \label{sec:fit-results}
+% TODO do all the work, but with different FWHM calculation -- to confirm
+%      that it doesn't make a big difference...
 
@@
 averages and errors are strongly affected by outliers from extreme best fit
-values, as can be seen in Table~\ref{tab:fits-all} -- especially as the typical
+values, as can be seen in Table~\ref{tab:fits} -- especially as the typical
 number of regions per filament (i.e., our sample size) is quite small.
@@
 error bars or something similar?
+
+\subsection{Variations on a theme of plug \& chug}
+
+Explain briefly, effects (percentage change or similar?) of model fit parameter
+changes, results if we vary Tycho distance to $2.3 \unit{kpc}$ or $4
+\unit{kpc}$; see \citet{hayato2010}.
+
+Is it worth discussing effects of various twiddle-ables: compression ratio $r$,
+accounting for azimuthal variation in $v_s$ (compare to taking a remnant
+average)?  Sean already discussed $E_{\mt{cut}}$ (result: more high energy
+elections to damp out widening effect at high energy).
+
+(YES, ADD THIS TO DRAFT -- MAY AS WELL)
+
+Any azimuthal variations -- need the table of filament averaged parameters
+first, and possibly smaller regions.
 

### 2014-09-19 code/json_utils.py

@@ -1,0 +1,53 @@
+"""
+Utilities for working w/ Python json
+
+Aaron Tran
+September 18
+"""
+
+import json
+import numpy as np
+
+import lmfit
+
+def dump(jobj, fname, cls=None, indent=4):
+    """Using my preferred defaults"""
+    with open(fname, 'w') as fjson:
+        json.dump(jobj, fjson, cls=cls, indent=indent)
+
+def load(fname):
+    with open(fname, 'r') as fjson:
+        a = json.load(fjson)
+    return a
+
+class NumpyJSONEncoder(json.JSONEncoder):
+    """Convert nd.ndarray to list for JSON encoding
+    From http://stackoverflow.com/a/10367428
+    """
+    def default(self, obj):
+        if isinstance(obj, np.ndarray) and obj.ndim == 1:
+            return obj.tolist()
+        return json.JSONEncoder.default(self, obj)
+
+class LmfitJSONEncoder(NumpyJSONEncoder):
+    """Handle lmfit.Parameter() objects by saving useful properties to dict
+    The selection of parameters follows lmfit.Parameter.__getstate__
+    """
+    def default(self, obj):
+        if isinstance(obj, lmfit.Parameter):
+            dobj = {}
+            dobj['name'] = obj.name
+            dobj['value'] = obj.value
+            dobj['vary'] = obj.vary
+            dobj['expr'] = obj.expr
+            dobj['min'] = obj.min
+            dobj['max'] = obj.max
+            dobj['stderr'] = obj.stderr
+            dobj['correl'] = obj.correl
+            dobj['init_value'] = obj.init_value
+            return dobj
+        return NumpyJSONEncoder.default(self, obj)
+
+
+if __name__ == '__main__':
+    pass

### 2014-09-19 code/models/latex_table.py

@@ -1,0 +1,1 @@
+../prettify/latex_table.py

### 2014-09-19 code/models/models_disp.py

@@ -1,104 +1,154 @@
 """
-Code for rich iPython notebook display
-and to abstract away a lot of boilerplate kinda stuff
+Code for IPython notebook fitting -- generate and save fits
+attempting to abstract a lot of boilerplate stuff out
 
-Storage for mega methods + table, LaTeX formatting material
-(may be moved/refactored later)
+build_dataf(...), generate_fits(...) work in tandem
 
-build_dataf(...), generate_tabs_plot(...) work in tandem
-classes ListTable, LatexTable for rich output
-(ListTable, in particular, is meant to be displayed in an iPython notebook)
+factory function f(...) from build_dataf(...) outputs an lmfit.Minimizer()
+object (res) w/ lots of information attached to res.params
+Relevant properties are:
+
+    res.params.ci           dict of confidence intervals
+    res.params.info         dict of best fit parameters w/ keys:
+        'conf-intv'             CI value
+        'chisqr'                fit chisqr
+        'redchi'                fit reduced chisqr
+        'ndata'                 res.ndata
+        'nvarys'                res.nvarys
+        'nfree'                 res.nfree
+    res.params.metadata     dict of build_dataf args
+        'fit-type'              simp/full
+        'fit-kws'               eta2_free, model_kws, etc...
+        'err-kws'               manual/lmfit/stderr, eps, adapt, etc...
+
+In the "metadata" pickle:
+
+    fobj_all = {}
+    fobj_all['title'] = fobj.title
+    fobj_all['kevs'] = fobj.kevs
+    fobj_all['data'] = fobj.data
+    fobj_all['eps'] = fobj.eps
+    fobj_all['inds'] = fobj.inds
+    fobj_all['snr-pars'] = fobj.snr.config_log()
 
 Aaron Tran
 August 2014
 """
 
-
 from __future__ import division
+
+import cPickle as pickle
+import json
+import lmfit  # For type-checking, JSON serialization
 import matplotlib.pyplot as plt
 import numpy as np
 import re
 
+from json_utils import LmfitJSONEncoder
+from latex_table import LatexTable, ListTable
 import models
 import models_exec as mex
+import regdict_utils as rdu
+import regparse
 
 from fplot import fplot
 
-# ==============================================
-# Functions to save numbers/data from generators
-# ==============================================
+# ==============================
[…]

### 2014-09-19 code/nice_tables.py

@@ -1,0 +1,189 @@
+"""
+LatexTable class (also tacked on ListTable temporarily)
+
+This duplicates a LOT of functionality from `matrix2latex.py`.
+Possible implementation (using doctest syntax):
+>>> from matrix2latex import matrix2latex as m2ltx
+>>> algnmt = '@{}rr@{ $\pm$ }lr@{ $\pm$ }lr@{}'
+>>> hr = '''[[''] + 5 * [title],
+...       [r'$\mu$ (-)'] + 2 * [r'$\eta_2$ (-)] + 2 * [r'$B_0$ ($\mu$G)']
+...        + [r'$\chi^2$']]'''
+>>> fmtcol = 'stuff'  # Here parse sigfigs, depending on error
+>>> # note: fmtcol varies w/ row, not implemented in m2ltx
+>>> m2ltx(data, headerRow = hr, formatColumn = fmtcol, alignment = algnmt)
+
+
+I'd like to extend matrix2latex by adding support for data w/errors;
+* use errors to compute # of sigfigs and supply that as an argument
+* use \e in LaTeX to change exponential notation formatting, rather than
+  manually editing floats
+
+Aaron Tran
+August 2014 (originally)
+"""
+
+#import numpy as np
+import re
+
+# ========================
+# LatexTable and utilities
+# ========================
+
+def merge_latex_tables(tab1, tab2):
+    """Smush two tables together -- combine headers and rows
+    The rowspecs (precisions) of each indiv. table are preserved in rspec
+    BUT, number of rows MUST be consistent
+    """
+
+    tab3 = LatexTable([], [], '')  # The empty vessel to be filled with life
+    tab3.types = tab1.types + tab2.types  # list of types
+    tab3.cspec = tab1.cspec + tab2.cspec  # str for \begin{tabular}{...}
+    tab3.title_row = ' & '.join([tab1.title_row, tab2.title_row])  # str, row
+    tab3.labels = ' & '.join([tab1.labels, tab2.types])  # str, row
+
+    t1r = tab1.rows
+    t2r = tab2.rows
+    if len(t1r) < len(t2r):
+        t1r = t1r + (len2-len1) * [tab1.rspec]
+    elif len(t2r) < len(t1r):
+        t2r = t2r + (len1-len2) * [tab2.rspec]
+    tab3.rows = [' & '.join([r1, r2]) for r1, r2 in zip(t1r, t2r)]  # str, row
+
+    return tab3
+
+
+class LatexTable(object):
[…]

### 2014-09-19 code/profiles/fplot.py

@@ -1,1 +1,1 @@
-../code/fplot.py
+../fplot.py

### 2014-09-19 code/profiles/fwhm_tables.py

@@ -1,0 +1,122 @@
+"""
+Code to generate tables of
+1. FWHM, m_E measurements
+2. best fit data
+
+Read from specified data folders
+
+Aaron Tran
+September 2014
+"""
+
+from __future__ import division
+
+import cPickle as pickle
+from glob import glob
+import numpy as np
+
+from latex_table import LatexTable
+import regdict_utils as rdu
+
+# ===========
+# FWHM tables
+# ===========
+
+def generate_fwhm_tab(rroot, kevs, labels):
+    """LaTeX table of FWHM and m_E values from region dicts w/ FWHM data
+
+    Inputs:
+        rroot (str): filestem of region dictionaries to read
+        kevs (str): energy band positions to compute m_E (should match labels)
+        labels (list): energy band labels, strings
+        title (str): table title
+    Output: LatexTable object w/form:
+        region, 0.7-1kev, 1-2kev, 2-7kev, 0.7-1kev, 1-2kev, 2-7kev
+        1       fwhm      fwhm    fwhm    m_E       m_E     m_E
+        2       ...
+    """
+    ltab = LatexTable(['Region'] + labels + labels,
+                      ['{}'] + [2]*len(labels) + [1]*len(labels),
+                      'FWHMs (replace w/ filament headers!)',
+                      prec=2)
+
+    n_regs = rdu.get_nregs(rroot)
+    data_all = np.empty((n_regs, len(kevs))) * float('nan')
+    m_e_all = np.empty((n_regs, len(kevs))) * float('nan')
+
+    for rdict, n in rdu.regdict_load(rroot):
+        data = np.array([rdict[lab]['fwhm'] for lab in labels])
+        errs = [rdict[lab]['errs'] for lab in labels]  # neg, pos
+        eps = np.mean(errs, axis=1)  # average of errors for calculations/fits
+        inds = (np.where(np.isfinite(data)))[0]  # Consistent w/ data_init
+
+        # Compute m_E
+        kevs = np.array(kevs)  # to be sure
+        me = m_expt(kevs, data)
+        meeps = m_expt_err(kevs, data, eps)
+
+        # Build row for latex table
+        ltr_fwhm = ['{:d}'.format(n)]
+        ltr_me = []
+
+        # NOTE HUGE ASSUMPTION -- only first n indices are dropped
[…]

### 2014-09-19 code/profiles/regdict_utils.py

@@ -1,0 +1,102 @@
+"""
+Functions to get / count region dictionaries w/ a given file stem.
+Not intended to modify or populate them; please see regdict.py for that
+
+This is for code in other folders that needs access to the region dictionaries'
+stored FWHMs.  Python imports don't play nice with symlinks.
+
+To avoid circular dependency, don't import regdict.py ...
+But, this does need fsmooth to be able to plot the smoothing function.
+sigh.  Deal with this later.
+
+Aaron Tran
+September 2014
+"""
+
+import cPickle as pickle
+from glob import glob
+#from matplotlib import
+import numpy as np
+
+from fplot import fplot
+import fsmooth
+
+# =====================
+# Working with regdicts
+# =====================
+
+# Following plot settings are twiddled for "publication"-quality figures
+# May need to rasterize some data, depending on output file sizes
+
+def plot_fwhm_fit(bdict, ax):
+    """Plot cut/uncut data with FWHM fit and bounds for given band dict"""
+    x, y, y_err, c = bdict['data']
+    wlen, wtype = bdict['wlen'], bdict['wtype']
+    f = get_ffit(bdict)
+    pars = bdict['pars']
+    w = bdict['fwhm']
+    lims = bdict['lims']
+
+
+    # Plot best fit profile
+    x_m = np.linspace(x[c], x[-1], num=100)
+    ax.plot(x_m, f(x_m, *pars), '-b', alpha=1)
+    # Plot FWHMs if FWHM is resolved
+    if np.isfinite(w):
+        ax.axvline(lims[0], ls='-', c='k', lw=1, alpha=0.5)
+        ax.axvline(lims[1], ls='-', c='k', lw=1, alpha=0.5)
+    # Plot data ABOVE best fit
+    plot_smoothing_cut(bdict, ax, show_smth=False)
+
+    return ax
+
+def plot_smoothing_cut(bdict, ax, show_smth=True):
+    """Plot cut/uncut data, smoothing used to determine cut (optional)
+    Adds axis labels and sets limits
+    """
+    x, y, y_err, c = bdict['data']
+    wlen, wtype = bdict['wlen'], bdict['wtype']
+
+    # Plot data outside, inside fit domain
+    ax.errorbar(x[:c], y[:c], yerr=y_err[:c], fmt='r.', capsize=0, alpha=0.5,
+                markersize=3)
+    ax.errorbar(x[c:], y[c:], yerr=y_err[c:], fmt='k.', capsize=0, alpha=1,
[…]

### 2014-09-19 code/regions/ds9projsplitter.py

@@ -16,7 +16,7 @@ To compute spectra, select inner and outer regions delineated by
 One input region file will be split into two for specextract/XSPEC chain.
 Each file contains only inner or only outer pieces, to preserve numbering.
 
-Script makes MANY assumptions about structure of region dictionary.
+Script makes MANY assumptions about structure of region dictionaries
 So, if dictionary structure is changed... update accordingly.
 """
 
@@ -28,16 +28,20 @@ import re
 
 import regparse
 
+ACIS_PX2ARCSEC = 0.492  # Chandra ACIS pixel size, arcseconds
+# BAD practice... but I don't expect this to change anytime soon
+# If the code has to be generalized to other telescopes, deal with it then
 
 def main():
     """Generate split regions from cmd line arguments"""
     parser = argparse.ArgumentParser(description=
              ('Split DS9 region file of projections into inner/outer pieces, '
               'according to profile fit cuts and FWHMs'))
-    parser.add_argument('fitpkl', help=('Pickled region dictionary from '
-                        'profile fitting scripts'))
     parser.add_argument('fitreg', help='DS9 fk5 region file of projections')
     parser.add_argument('regimg', help='Valid FITS file for input regions')
+    parser.add_argument('fcut', help='npz file w/ spectrum cuts')
+    parser.add_argument('-b', '--binsize', default=1, type=float,
+                        help='Bin size of images used to select regions')
     parser.add_argument('-o', '--outreg', help=('Root name for output region '
                         'files.  Inferred from input region file by default'))
     parser.add_argument('-v', '--verbose', action='store_true',
@@ -45,17 +49,14 @@ def main():
 
     # Parse arguments
     args = parser.parse_args()
-    f_pkl, f_reg, f_img = args.fitpkl, args.fitreg, args.regimg
+    f_reg, f_img, f_cut = args.fitreg, args.regimg, args.fcut
+    binsize = args.binsize
     f_oreg = args.outreg
     verbose = args.verbose
-
     if f_oreg is None:
         f_oreg = os.path.splitext(f_reg)[0]
     if verbose:
         print 'Output root is {}'.format(f_oreg)
-
-    with open(f_pkl, 'r') as f:
-        regions = pickle.load(f)
 
[…]

### 2014-09-19 code/regparse.py

@@ -1,0 +1,135 @@
+"""
+Library functions for parsing DS9, CIAO region files
+and assorted useful file IO (common to multiple scripts)
+
+Aaron Tran
+2014 June 23
+(last modified: 2014 August 6)
+"""
+
+import os
+import re
+
+import ds9
+
+
+def main():
+    pass
+
+
+######################
+# Handy path functions
+######################
+
+def count_files_regexp(stem):
+    """Number of grouped files with given directory stem, where
+    the basename of the stem is a regex (use raw string as needed)
+    """
+    pattern = os.path.basename(stem)
+    if os.path.dirname(stem) == '':
+        files = [f for f in os.listdir('.') if re.match(pattern,f)]
+    else:
+        files = [f for f in os.listdir(os.path.dirname(stem))
+                 if re.match(pattern, f)]
+    return len(files)
+
+
+def check_dir(stem, verbose=False):
+    """Check if stem directory exists and create if needed"""
+    stemdir = os.path.dirname(stem)
+    if not os.path.isdir(stemdir) and stemdir is not '':
+        if verbose:
+            print 'stem {} in nonexistent directory'.format(stem)
+            print 'Creating directory {}'.format(stemdir)
+        os.makedirs(stemdir)
+
+
+#################
+# Region file I/O
+#################
+
+def load_ds9reg(fname, aux=False):
+    """List of region strings from ds9 region file;
+    headers checked for correct filetype (does not check coordsys)
+    Trailing newlines are preserved
+
+    aux (bool): returns extra header info along with region strings
+    """
+    with open(fname, 'r') as f:
+        header = f.readline()
+        settings = f.readline()
+        coordsys = f.readline()
+        if 'DS9 version 4.1' not in header:
+            print 'WARNING: potentially invalid region file'
+            print 'First line was: {}'.format(header)
+        regstrs = list(f)
+
+    if aux:
+        return regstrs, (header, settings, coordsys)
+    return regstrs
+
+
+def write_ds9reg(fname, regstrs, headers):
+    """Inverse operation for load_ds9reg(..., aux=True)
+    Does not check if file exists.
+    """
+    with open(fname, 'w') as f:
+        for h in headers:
+            f.write(h)
+        for r in regstrs:
+            f.write(r)
+
+def conv_fk5_to_phys(f_in, f_img, f_out):
[…]

### 2014-09-19 code/spectra/regparse.py

@@ -1,1 +1,1 @@
-/Users/atran3/snr-research/code-reg/regparse.py
+../regions/regparse.py

### 2014-09-20 manuscript/paper-tycho.tex
Paper table code; add/fix up paper tables
Working code to generate/format paper tables in ipynb.  Add tables for
individual regions w/ reduced chi-sqrs, tables w/ averaged fit params for all
filaments.

@@
 \newcommand*{\tsynch}{\tau_{\mt{synch}}}
+\newcommand*{\mE}{m_\mathrm{E}}
 \defcitealias{ressler2014}{R14}
@@
     X-rays: ISM}
+
+% TODO GENERAL WARNING -- DATA ARE NOT ALL FULLY CONSISTENT AT THIS TIME.
+% (spectra/profiles/fwhms/fits).  Will be corrected / good to go in final
+% revision.
 
@@
 
-Explain how the transport models constrain diffusion via $m_E$, define $m_E$.
+Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
 Explain how we back out a filament shape/width from these models
@@
 
+Discuss $\mE$, I have NOT defined this quantity below.  % TODO
+
 \subsection{Magnetic damping}
@@
 faint southern wisps) \note[Aaron]{wishy-washy qualitative}.
+We grouped regions into filaments by visual inspection of the remnant.
 
@@
     \centering
-    %\plotone{figures/f0-snr.pdf}
-    \includegraphics[width=0.35\textwidth]{figures/f0-snr.pdf}
+    \plotone{figures/f0-snr-inv.png}
     \caption{RGB image of Tycho with region selections overlaid.  Bands are
@@
     \note[Aaron]{Could show the spectrum extraction regions on here too?
-    Maybe too cluttered.}}
+    Maybe too cluttered.  Figure colors inverted to save ink.}}
     \label{fig:snr}
@@
 \note[Aaron]{citation for e- distr. indices?}. Best fit column densities from
-upstream spectra, between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$, are
+upstream spectra between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$ are
 consistent with previous fits to Tycho's nonthermal rims \citep{hwang2002} but
-somewhat larger than $\abt0.35$--$0.5 \times 10^{22}$ from radio and optical??
-HI absorption line measurements \citep{black1984, albinson1986, kothes2004}.
+somewhat larger than $\abt0.35$--$0.5 \times 10^{22} \unit{cm^{-2}}$ from radio
+and optical??  HI absorption line measurements \citep{black1984, albinson1986,
+kothes2004}.
 % NOTE keep stated ranges of spectral indices, column densities up to date
 
-\note[Aaron]{On rob's suggestion of fitting thermal model -- can we get away
+\note[Aaron]{On Rob's suggestion of fitting thermal model -- can we get away
 with just fitting line emission and constraining from there? or is the
@@
     \centering
-    \caption{Absorbed power law fit parameters for all regions' upstream and
-    downstream spectra.  The reduced $\chi^2$ values for upstream spectrum fits
-    are consistent with a lack of thermal emission, but values for downstream
-    fits indicate a poor fit due to line emission.
-    \label{tab:spec}}
+    \caption{Region spectra fit parameters\label{tab:spec}}
     \input{tab-spec.tex}
+    \tablecomments{Absorbed power law fit parameters are photon index $\Gamma$
+    and hydrogen column density $\mathrm{N_H}$.}
 \end{table}
@@
 In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
-As previously noted, we could not resolve FWHMs for some regions in the 0.7--1 keV band.
-NOTE very low counts/numbers of regions for some averages (typically 1--2, see
-Figure~\ref{fig:snr}).
+As previously noted, we could not resolve FWHMs for some regions in the
+0.7--1 keV band.  We also report $\mE$ values for all but the lowest energy
+band, computed point-to-point as $\mE(E_2) = \ln(w_2/w_1) / \ln(E_2/E_1)$ where
+$w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each energy
+band (e.g., $\mE(\text{1 keV}) = \ln(w(\text{1-1.7 keV}/w(\text{0.7-1 keV})) /
+\ln(\text{1 keV}/\text{0.7 keV})$ is computed from widths/energies.  Although
+the values of $\mE$ reflect a good deal of variability in the underlying width
+measurements, we see that most regions and energy bands display a decrease in
+rim widths as a function of energy.
 
-Mention the number of counts in individual profiles?
-May affect whether we go back and take smaller regions, or not.
-
-% TODO give individual regions' FWHMs and m_E values
 \begin{table*}[ht]
@@
     \centering
-    \caption{FWHMs for all regions.\label{tab:fwhms}}
-    %\input{tab-fwhms-ave-arith.tex}
-    %\input{tab-fwhms-ave-geom.tex}
+    \caption{Measured FWHMs for all regions.\label{tab:fwhms}}
     \input{tab-fwhms.tex}
 \end{table*}
+
+Here we have presented $\mE$ to demonstrate the fall-off of rim width energy.
+However, we emphasize that $\mE$ is currently not factored into our subsequent
+analysis.
 
@@
 \label{sec:fit-results}
+
 % TODO do all the work, but with different FWHM calculation -- to confirm
@@
 
-% TODO keep updated -- give tables for ONE region with both simple, full fits
+% NOTE keep updated -- for which region are we giving simple and full fits?
 We find that the simpler catastrophic dump model (equation~\eqref{eq:simp-mod})
@@
 The first row of Table~\ref{tab:fits} compares simple and full model fits for
-Region 1(?).
+Region 1.
 The key differences are \emph{blah}.  The errors are comparable, the parameters
 are comparable but shifted by X amount; this is consistent in all filaments?
-(details tbd).  Consequently, we present only the full model fits for all other
+(details tbd).
+Consequently, we present only the full model fits for all other
 filaments in Table~\ref{tab:fits}.  However, the simple model is useful for
@@
 limits on our fit parameters.
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for individual regions, Filament 1.
+    \label{tab:fits}}
+    \input{tab-fits-all.tex}
+\end{table}
+
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for individual regions, Filaments 2--5.
+    \label{tab:fits-pt2}}
+    \input{tab-fits-all-pt2.tex}
+\end{table}
 
@@
 
-% TODO Assemble table of regions
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{Full model best fits for individual regions, Filament 1.
-    \label{tab:fits}}
-    \input{tab-fits-flmt1.tex}  % TODO CHANGE/UPDATE THIS
-\end{table*}
-
-In Figure~\ref{fig:fits} we plot the full model fits for the same regions
+In Figure~\ref{fig:fits-all} we plot the full model fits for the same regions
 tabulated in Table~\ref{tab:fits}
 
-% TODO Assemble all the individual plots.
+% NOTE need better subplot display in final version, if we keep this
 \begin{figure}[ht]
     \centering
-    \plottwo{figures/f0-fits-avg-flmt1.png}{figures/f0-fits-avg-flmt2.png} \\
-    \plottwo{figures/f0-fits-avg-flmt3.png}{figures/f0-fits-avg-flmt4.png} \\
-    \plottwo{figures/f0-fits-avg-flmt5.png}{figures/f0-box.png}
-    \plottwo{figures/f0-fits-avg-flmt1-geom.png}{figures/f0-fits-avg-flmt2-geom.png} \\
-    \plottwo{figures/f0-fits-avg-flmt3-geom.png}{figures/f0-fits-avg-flmt4-geom.png} \\
-    \plottwo{figures/f0-fits-avg-flmt5-geom.png}{figures/f0-box.png}
-    \caption{Plots of best-fits to averaged FWHMs (arithmetic, geometric avg).
-    \note[Aaron]{Need better subplot display in final version, if we keep these}}
+    \plottwo{figures/fits-sep13/reg01.png}{figures/fits-sep13/reg02.png} \\
+    \plottwo{figures/fits-sep13/reg03.png}{figures/fits-sep13/reg04.png} \\
+    \plottwo{figures/fits-sep13/reg05.png}{figures/fits-sep13/reg06.png} \\
+    \plottwo{figures/fits-sep13/reg07.png}{figures/fits-sep13/reg08.png} \\
+    \plottwo{figures/fits-sep13/reg09.png}{figures/fits-sep13/reg10.png} \\
+    \plottwo{figures/fits-sep13/reg11.png}{figures/fits-sep13/reg12.png} \\
+    \plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
+    \caption{Fitted full model widths as a function of energy for all regions,
+    with measured data; best fit parameters are given in
+    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
+    number.}
     \label{fig:fits-all}
@@
     \centering
-    \caption{Best fits with $\eta_2 = 1$ fixed, for filament averaged FWHMs.
+    \caption{Best fits with $\eta_2 = 1$ fixed for filament averaged FWHMs.
     \label{tab:fits-avg-eta2-fix}}
@@
     \centering
-    \caption{Filament-wide average of best-fit parameters for constituent regions.
+    \caption{Filament averages of best-fit parameters for constituent regions
     \label{tab:fits-avg}}
@@
 
-It would be helpful to average $m_E$ values together, under the
+It would be helpful to average $\mE$ values together, under the
 assumption that they should be somewhat consistent within a given filament.
@@
 IF magnetic damping is relevant in controlling filament widths, we might, e.g.,
-expect a maximum filament width at which $m_E$ sharply levels off, being now
+expect a maximum filament width at which $\mE$ sharply levels off, being now
 restricted by the magnetic field turn off.  We simply do not observe this in
@@
 
-For comparison to \citetalias{ressler2014}, we reproduce Sean's table
-(Table~\ref{tab:sean} and present full model fits with 2 and 3 energy bands
-(Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
+For comparison to \citetalias{ressler2014}, we reproduce Sean's full model fit
+table (Table~\ref{tab:sean}) and present full model fits with 2 and 3 energy
+bands (Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
 We don't compare simple model results, as they are identical (only the error
 calculations differ).
-The procedure of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
-the same.  Sean used $m_E$ at 2 keV instead of the $1$--$2$ keV width for
+The procedures of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
+the same.  Sean used $\mE$ at 2 keV instead of the $1$--$2$ keV width for
 fitting, whereas I used both widths.  But, it should not matter much as
@@
 
-% ------------------
-% Sean's Cas A table
-% ------------------
-\section{Sean's Cas A comparison (DRAFT ONLY)}
-
-This is dredged from the \LaTeX source for Sean's paper, available on arXiv.
-I put this here just for my own reference.
-
-A detailed application of our results to other SNRs such as Cas A will
-require much more extensive analysis, but we can use the published
-filament widths of Araya et al. (2010) for Cas A to get preliminary
-estimates of the magnetic field strength and diffusion coefficient by
-applying our model. In their data, it appears that the filaments in
-Cas A shrink by a factor of $\sim 0.8$ between 0.3 and 3 keV, while the
-filament widths appear to be energy-independent between 3 and 6 keV.
-Qualitatively, this is consistent with the loss-limited model, as our
-parameter $m_{\rm E}$ is predicted to decrease with energy.  For the
-lower energy range of 0.3--3 keV, reproducing $m_{\rm E}\sim -0.1$
-(equivalent to the factor of 0.8 drop in size) requires magnetic
-fields on the order of 200-500 $\mu$G and diffusion coefficients about
-$5 \times D_{\rm Bohm}$(3 keV), about an order of magnitude higher
-than the values one obtains by neglecting the energy dependence. One
-can also see directly from Figure~\textbf{?!} that $\mu < 1$ models
-of the diffusion coefficient are excluded for $m_{\rm E}\sim -0.1$.
-
-To quickly compare how our results will differ from those of other authors, we
-applied the analytic approximation of Equation 22 and Equation 9 to the FWHMs
-presented by Araya et al. (2010) for Cas A. Here we used $m_{\rm E} = \log(
-{\rm FWHM}(3keV)/{\rm FWHM}(.3keV))/\log(10)$ and fit the filaments at a photon
-energy of 3 keV.  Hence $\eta_3 \equiv D/D_{\rm Bohm}(3 keV)$. Using the same
-parameters, our results are shown in Table~\ref{tab:araya}. To fit the energy
-dependence of the FWHM (i.e. $m_{\rm E}$), we required higher diffusion
-coefficients and, consequently, magnetic fields about an order of magnitude
-higher than their results. We note here that values of $\mu<1$ were unable to
-reproduce the data and that the diffusion coefficients cited by Araya et al.
-(2010) are below the minimally allowed Bohm value ($\eta_3 = 1$).
-
-We intended this comparison solely as a qualitative analysis, and thus did not
-rigorously keep track of uncertainties or extend the comparison to the full
-numerical calculation. The conclusion is clear, however, which is that
-considering the measured value of $m_{\rm E}$ can have a dramatic effect.
-
-\begin{table}[h]
-\tiny
-\centering
-\caption{Best fit parameters for the filaments of Cas A based on data from
-Araya et. al (2010) in varying values of $\mu$ (Approximate Analytic Results)
-Dashes denote places where fits were unobtainable.
-\label{tab:araya}}
-\input{tab-sean-casA.tex}
-\end{table}
-
 % ==========

### 2014-09-20 code/models/fsmooth.py

@@ -1,0 +1,1 @@
+../profiles/fsmooth.py

### 2014-09-20 code/models/models_disp.py

@@ -38,6 +38,7 @@ August 2014
 from __future__ import division
 
 import cPickle as pickle
+from glob import glob
 import json
 import lmfit  # For type-checking, JSON serialization
 import matplotlib.pyplot as plt
@@ -45,7 +46,7 @@ import numpy as np
 import re
 
 from json_utils import LmfitJSONEncoder
-from latex_table import LatexTable, ListTable
+from nice_tables import LatexTable, ListTable
 import models
 import models_exec as mex
 import regdict_utils as rdu
@@ -122,16 +123,16 @@ def save_fits(p_list, fobj, mu_vals, outroot):
     with open('{}-fobj.json'.format(outroot), 'w') as fjson:
         json.dump(fobj_all, fjson, cls=LmfitJSONEncoder, indent=4)
 
-def gen_fit_pkls(inroot, want_fobj=False):
+def load_fit_pkls(inroot, want_fobj=False):
     """Generator that iterates over each fitted region/filament
     Input:
         inroot (str) is base file stem, e.g.,
         ../../data-tycho/fwhms/model-fits/simp-man_err
     Yield, for each region fitted:
-        tuple of 1. list of Parameters(), 2. list of mu values,
-                 3. fobj_all dict w/ fitting data, if desired
+        tuple of 1. list of Parameters(), 2. list of mu values, 3., region num
+                 4. fobj_all dict w/ fitting data, if desired
     """
-    npkls = glob('{}-*-data.pkl'.format(inroot))
+    npkls = len(glob('{}-*-data.pkl'.format(inroot)))
     for n in xrange(npkls):
         fname = '{}-{:02d}-data.pkl'.format(inroot, n+1)  # Enforce ordering
         ffobj = '{}-{:02d}-fobj.pkl'.format(inroot, n+1)
@@ -140,9 +141,9 @@ def gen_fit_pkls(inroot, want_fobj=False):
         if want_fobj:
             with open(ffobj, 'r') as fpkl:
                 fobj_dict = pickle.load(fpkl)
-            yield p_list, mu_vals, fobj_dict
+            yield p_list, mu_vals, n+1, fobj_dict
         else:
-            yield p_list, mu_vals
+            yield p_list, mu_vals, n+1
 
 # =========================
 # Functions to control fits
@@ -165,10 +166,9 @@ def build_dataf(fit_type, conf_intv=0.683, fit_kws=None, err_kws=None):
         conf_intv: please don't set above 0.683 or your life will suck, I guarantee
         fit_kws, *simple and full models*
[…]

### 2014-09-20 manuscript/paper-tycho.tex
Run code with tweaked FWHMs, more paper writing

@@
 \author{
+Aaron Tran\altaffilmark{1,4},
+Brian J. Williams\altaffilmark{1,5},
 Robert Petre\altaffilmark{1},
 Sean M. Ressler\altaffilmark{2},
-Stephen P. Reynolds\altaffilmark{3},
-Aaron Tran\altaffilmark{1,4},
-Brian J. Williams\altaffilmark{1,5}
+Stephen P. Reynolds\altaffilmark{3}
 }
@@
 \note[Aaron]{this first draft of intro structure is mostly set (in terms of
-material, number of paragraphs).}
+material, number of paragraphs).  Explanations/etc may be too simplistic, I
+have more reading to do.}
 
@@
 Seminal observations \& interpretations of these filaments, interpretation in
-context of DSA.
-People (such as the authors of this manuscript) are trying to model these
-filaments and figure out what's going on.
+context of DSA.  Attempts to model filaments and figure out what's going on.
 Why do we care about these models?  They tell us something about what happens
@@
 Applications to: cosmic ray acceleration, turbulent field amplification, (note
-assumptions in re proton/electron spectra).  Cut-off energy of injected
+assumptions in re proton/electron spectra).
+Cut-off energy of injected
 electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
 PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
-AGN jets, galaxy clusters \citep{van-weeren2010}, cosmological shocks?!
-\citep{miniati2000, ryu2008}, other cool stuff.  See relevant reviews
-\citep{blandford1987}.
+AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
+\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.
 
@@
 energy distribution and the gradual decrease of electron energies downstream of
-the shock.  At the shock, high energy electrons efficiently radiate harder
-synchrotron X-ray photons; as they are transported away from the shock, they
-radiate at lower energies and lose energy more slowly.  The transport process
-is driven by both bulk plasma advection away from the shock at downstream
-velocity $v_d = v_s / r$, where $v_s$ is shock velocity and $r$ the compression
-ratio, and diffusion ... (driven by collisionless particle interaction,
-magnetic field turbulence, ????? fill in details) with respect to bulk
-advection.  Energy-dependent diffusion (e.g., diffusion coefficient $D \propto
-E$ for Bohm diffusion) allows higher energy electrons to diffuse further
-upstream or downstream than would be expected from pure advection; in
-particular, diffusion upstream of the shock may give rise to a shock precursor
-\citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.  Finally, the magnetic
-field strength may be quickly damped behind the shock, so that electrons may
-not radiate as efficiently and thin rims would reflect the spatial structure of
-the field, rather than efficient particle acceleration (and losses) and/or
-efficient synchrotron cooling \citep{pohl2005}.  \note[Aaron]{I need to read up
-on particle transport, diffusion, plasma physics!}
+the shock.  High energy electrons near the shock efficiently radiate harder
+synchrotron X-ray photons, but decline in energy as they are transported away
+from the shock; this may be seen in spectral softening downstream of the shock
+\citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
+plasma advection downstream of the shock and diffusion (\emph{driven by
+collisionless particle interaction, magnetic field turbulence, ?????  fill in
+details}) with respect to bulk advection.  Energy-dependent diffusion (e.g.,
+diffusion coefficient $D \propto E$ for Bohm diffusion) allows higher energy
+electrons to diffuse further upstream or downstream than would be expected from
+pure advection; in particular, diffusion upstream of the shock may give rise to
+a shock precursor \citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.
+Finally, the magnetic field strength may be quickly damped behind the shock, so
+that electrons may not radiate as efficiently and thin rims would reflect the
+spatial structure of the field, rather than efficient particle acceleration
+(and losses) and/or efficient synchrotron cooling \citep{pohl2005}.
 
@@
 Moreover, these controlling mechanisms predict different scalings for rim width
-as a function of energy.  Loss-limited rims should scale as $w \propto
-\nu^{-1/2}$.  Diffusion weakens this energy dependence by smearing out rims at
-all energies (even for energy-independent diffusion), yielding a slower
-drop-off in rim widths when diffusion dominates.  Magnetic damping, at a
-length scale where it may be considered a relevant control on rim widths (i.e.,
-length scale comparable to filament width) predicts energy-independent rim
-widths -- intuitively, if the magnetic field turns off, synchrotron radiation
-turns off regardless of electron energy.  \citet{ressler2014} give a much
-fuller exposition of the relative effects of advection, diffusion, and magnetic
-field damping.
+as a function of energy.  Synchrotron loss-limited rims should scale as $w
+\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
+effect at higher energies, yielding a slower drop-off in rim widths when
+diffusion dominates.  Magnetic damping, if at a length scale comparable to
+filament widths, predicts energy-independent rim widths -- intuitively, if the
+magnetic field turns off, synchrotron radiation turns off regardless of
+electron energy.  \citet{ressler2014} give a much fuller exposition of the
+relative effects of advection, diffusion, and magnetic field damping.
 
@@
 bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
-magnetic fields are amplified according to loss-limited model.  How could this
-be plausible?  There are possible explanations -- field amplification from
-plasma instabilities, evidence for stronger compression ratios?
-\citep{blondin2001}.  Numerical simulations and theory on this matter
-accounting for streaming instabilities, CR escape / energy losses, MHD
-equations, all sorts of things I can't keep track of.  But, magnetic damping
-model offers a tantalizing alternate explanation, and has not been tested.
-Equivocal results by \citet{araya2010} for Cas A.
+magnetic fields are amplified according to loss-limited model.  How?  Field
+amplification from plasma instabilities, evidence for stronger compression ratios?
+\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
+understand.
+
+Introduce $\tsynch$ and the basic intuition.
+Explain why diffusion is an important consideration
+(when did this start being recognized as relevant?).
+
+Previous work that accounted for advection/diffusion alone or separately,
+previous work that considered both simultaneously (as we do here).
+
+But, magnetic damping offers a tantalizing alternate explanation and has not
+been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
 \citet{rettig2012} proposed discriminating based on filament spectra -- the
@@
 
-% =============================
-% Transport models, observables
-% =============================
-\section{Electron transport models}\label{sec:transport}
-
+% TODO Chunk of text I don't know what to do with...
 We briefly review relevant particle transport models that we use to fit our
 measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
-\note[Aaron]{is it necessary to give Sean's equation numbers?  How many of the
-derived equations should we give?}  In particular, the transport models
+In particular, the transport models
 account for both advection and diffusion simultaneously, as opposed to
@@
 
+% =============================
+% Transport models, observables
+% =============================
+\section{Nonthermal rim modeling}\label{sec:models}
+
+\subsection{Particle transport}\label{sec:transport}
+
 % TODO Choose names for these models and refer to them consistently, throughout
@@
 %      notation is being used)
-\note[Aaron]{Double check against Rettig/Pohl.  Variable definitions will be
-added when equations/exposition is closer to final state.}
-The electron distribution which gives rise to the observed synchrotron
-radiation is injected at the forward shock and transported by advection
-and plasma diffusion, following the advection-diffusion equation:
-\[
+% TODO double check equations, exposition against Rettig/Pohl and others
+% TODO review variable definitions when closer to final draft
+The energy and space distribution of electrons at a supernova remnant
+controls the synchrotron rims we see in X-ray and radio.  We model electron
+transport from initial injection at the remnant's forward shock as following
+the advection-diffusion equation given by:
+\note[Aaron]{ApJ prefers bold vectors and vector operators, fix later}
+% TODO fix vector operators
+\begin{equation}
   \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
   = C + \del \cdot \left( D \del f \right)
-\]
-By considering only steady-state transport and some other assumptions
-(1-D flow (did we neglect the spherical coord terms?), neglect compressible flow?!,
-space-independent diffusion coefficient):
-\[
-    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
-\]
-The source/sink term $C$ reflects assumptions about the injected electron
-energy spectrum and its time/space evolution.
-A first approximation is to treat electrons as having constant energy, but
-dumping energy catastrophically after a synchrotron timescale
-$\tsynch$ \note[Aaron]{define this -- either Section~\ref{sec:transport} before jumping into
-transport models, or in the intro}, yielding:
+\end{equation}
+where $f = f(E,x)$ is electron distribution as a function of electron energy
+$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
+$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
+$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
+By considering 1-D steady-state plane transport at a constant downstream
+velocity $v_d$ \note[Aaron]{we threw out 1. spherical coordinate terms, and 2.
+compressible flow terms, I think.  Is the latter justifiable?  Makes sense for
+assumption of uniform downstream velocity -- but is this a safe assumption in
+practice?  Double check order-of-magnitude...} and a space-independent diffusion
+coefficient, we obtain:
+\begin{equation}
+    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
+\end{equation}
+The source/sink term $C$ is determined by our assumptions about the injected
+electron energy spectrum and its time/space evolution.
+
+A first approximation is to let electrons have constant energy that is dumped
+catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
+$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
+vary as $B=B(x)$.  The sink term is $C = -f / \tsynch$, yielding:
 \begin{equation} \label{eq:simp-mod}
-    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
+    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
     \frac{f}{\tau_{\mt{synch}}} = 0
 \end{equation}
-where this is equation (5) of \citetalias{ressler2014}.
-Equation~\eqref{eq:simp-mod} has a convenient analytic solution (note that
-neglecting diffusion, this is $\ptl f/\ptl x \propto -f/(\tsynch v_d)$.
+which is equation (5) of \citetalias{ressler2014}.
+\note[Aaron]{I think there should be a delta function for e- injection, but it
+probably doesn't affect the solution.  Double check.}
+Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
+\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
+maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
+\begin{equation} \label{eq;simp-fwhm}
+    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
+\end{equation}
+where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
+take $\beta = 4.6$ assuming projection from spherical shell, as derived by
+\citet{ballet2006}.
+
 A more advanced model is given by accounting for continuous radiation energy
-losses while electrons are transported downstream, given as:
+losses while electrons are transported downstream:
 \begin{equation} \label{eq:full-mod}
-    v \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
+    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
     K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
@@
 \end{equation}
-which is equation (12) of \citetalias{ressler2014}.
+which is equation (12) of \citetalias{ressler2014}.  The injected electron
+distribution is an exponentially cut-off power law with normalization $K_0$ and
+cut-off energy $E_{\mt{cut}}$; the expression for the cut-off energy is
+determined by the form of the diffusion coefficient $D$, which we discuss in
+Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
+numerically solve for electron distribution $f(E,x)$ using Green's function
+solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
+given using notation close to that of this paper by \citetalias{ressler2014}.
+The electron distribution may then be integrated to obtain synchrotron
+emissivity:
+\begin{equation} \label{eq:emissivity}
+    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
+\end{equation}
+where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
+$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
+emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
+\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
+spherical shell yields intensity:
+\begin{equation} \label{eq:intensity}
+    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
+                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
+\end{equation}
+where $s$ is the line-of-sight coordinate.  We can then compute these
+integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
+model predictions for rim FWHMs.
+
+\subsection{Diffusion energy-dependence} \label{sec:diffcoeff}
 
 Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
-Explain how we back out a filament shape/width from these models
-
-\subsection{Energy dependent widths, diffusion}
+Explain the basic interplay between diffusion and magnetic field, in
+controlling rim widths.
 
 Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
-\[
+\begin{equation}
     D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
-\]
+\end{equation}
 Explain the use of fiducial energy -- this makes sense and eases discussion,
@@
 
-For the simple model, we have equation (6) of \citetalias{ressler2014}:
-\begin{equation} \label{eq:simp-width}
-    a = \frac{2 D / v_d}{ \sqrt{ 1 + \frac{4D}{v_d^2 \tau_{\mt{synch}}}} - 1}
-\end{equation}
-which we relate to full width half max by projection factor $\beta = 4.6$
-so that $w = \beta a$, assuming (1) electron distribution exponential in radial
-coordinate $x$, and (2) spherical source \note[Aaron]{shell?}
-\citep{ballet2006}.
+Mention that different $\mu$ values arise from particular models of turbulence.
 
-For the full model (equation~\eqref{eq:full-mod}), we numerically solve for
-electron distribution $f(E,x)$ using solutions due to \citet{lerche1980} and
-\citet{rettig2012}; DETAILS.
-Ultimately, we integrate numerically computed electron distributions $f(E,x)$
-over energy to obtain synchrotron emissivity as
-\[
-    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
-\]
-where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
-$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is the one-particle synchrotron
-emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
-\citep{pacholczyk1970}.  Integrating emissivity over lines of sight yields
-\begin{equation} \label{eq:intensity}
-    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
-                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
-\end{equation}
-where $s$ is the line-of-sight coordinate.
-
-\subsection{Tycho parameters}
-
-Give numbers ($v_s$, $v_d$, $r_s$, etc.).  Give a definition of the cut-off
-energy following Rettig and Pohl (again cite Sean's paper).
 We use an electron spectrum cut-off energy of:
@@
 
-Discuss $\mE$, I have NOT defined this quantity below.  % TODO
-
 \subsection{Magnetic damping}
 
-We also consider a magnetically damped field of form
-\[
+We also consider (not really) a magnetically damped field of form
+\begin{equation}
     B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
-\]
-following \citetalias[Section 3.2]{ressler2014}.
+\end{equation}
+following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.
 
@@
 Is that good enough for us?
+(Cassam-Chena\"i et al. considered PSF effects when modeling rim widths, though
+it doesn't look like it made a big difference?)
 
@@
 \eqref{eq:full-mod} to our measured rim widths as a function of energy.
-Although our measured radial profiles sum a continuous energy range of counts,
-we assigned each width measurement to the lower energy limit of its band
+We assigned each width measurement to the lower energy limit of its energy band
 (e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
@@
 % Model knobs and how we twiddled them
-We have three parameters to vary (more if we consider magnetic damping).
-They are diffusion-energy scaling exponent $\mu$, normalized diffusion
+We have three parameters to vary (more if we consider magnetic damping):
+diffusion-energy scaling exponent $\mu$, normalized diffusion
 coefficient $\eta_2$, and magnetic field strength $B_0$.
-Explain why we are fixing $\mu$ (forward reference best fit figures).
-We consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
+To make our nonlinear fitting tractable, we fix $\mu$ in all fits and
+consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
 respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
@@
 a factor of 2; we interpolated shock velocities reported by
-\citet{williams2013} to estimate individual shock velocities for each region.
-\note[Aaron]{this paragraph might belong in Section~\ref{sec:transport}?}
+\citet{williams2013} (rescaled to $3 \unit{kpc}$ rather than $2.3 \unit{kpc}$
+to estimate individual shock velocities for each region.
+\note[Aaron]{this paragraph might belong in an earlier section?}
 
 % How to do the fit
-The simple model is readily fit from equation~\eqref{eq:simp-width}.
-The full model is numerically computed following the procedure laid out in
-\emph{section ?!}, yielding intensity profiles from equation~\eqref{eq:intensity} for each
-energy band and hence a model full width at half maximum.
+Our data are readily fit to the simple model by equation~\eqref{eq:simp-width}.
+The full model is numerically computed as detailed in
+Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
+in each energy band.
 For least squares fitting purposes, the full model is treated as a black box
@@
 
+X-ray rims are not damped -- could damping be relevant to the radio rims?
+
 \subsection{Interpretation of fit parameters}
@@
 Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.
+Would it be useful to report advective and diffusive lengthscales at 2 keV?
+Idea being that it is hard to intuit what the large numbers even mean.
+(especially for the simple model -- it sits on a plateau in chi-squared space
+where small $\eta_2$ may be disfavored, but beyond a certain point any $\eta_2$
+will do)
 

### 2014-09-22 manuscript/paper-tycho.tex
New (smaller) Tycho regions, variant FWHM tables
Add tables with simple model fits and variant FWHM calculation.
Split Tycho regions, compute new FWHMs and fits.
More paper writing.

@@
 \newcommand*{\tsynch}{\tau_{\mt{synch}}}
-\newcommand*{\mE}{m_\mathrm{E}}
+\newcommand*{\mE}{m_\mt{E}}
+\newcommand*{\Ecut}{E_{\mt{cut}}}
 \defcitealias{ressler2014}{R14}
@@
 behind the shock, and perhaps what's going on at the shock.  We get at the
-plasma turbulence, magnetic field turbulence and structure, electron injection.
+plasma and magnetic field turbulence, electron injection.
 Applications to: cosmic ray acceleration, turbulent field amplification, (note
 assumptions in re proton/electron spectra).
-Cut-off energy of injected
-electrons?  Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
+Cut-off energy of injected electrons?
+Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
 PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
@@
 % Which one is right?
-Previous measurements of basic observables \citep[e.g.,][]{bamba2003,
-bamba2005-hist, bamba2005-vela, parizot2006} and consequences.  Conclusion that
-magnetic fields are amplified according to loss-limited model.  How?  Field
+Which mechanisms are most relevant to historical SNRs?
+\note[Aaron]{need to read more / more thoroughly}
+Introduce $\tsynch$ and the basic intuition. Explain why diffusion is important
+(when did diffusion start being recognized as relevant to SNR filaments? or how was
+this shown?).
+Following Sean (i.e., taking all of his references), relevant previous
+observational studies.
+\citet{bamba2003, vink2003, yamazaki2004, ballet2006} consider advection and
+diffusion separately (with the break-point at $\Ecut$ when advective and
+diffusive length scales are equal;
+\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
+with the catastrophic dump equation.
+\citet{berezhko2003, berezhko2004, cassam-chenai2007, morlino2010, rettig2012}
+consider diffusion and advection simultaneously with the continuous loss
+equation instead.
+Conclusion that magnetic fields are amplified according to loss-limited model.  How?  Field
 amplification from plasma instabilities, evidence for stronger compression ratios?
@@
 understand.
-
-Introduce $\tsynch$ and the basic intuition.
-Explain why diffusion is an important consideration
-(when did this start being recognized as relevant?).
-
-Previous work that accounted for advection/diffusion alone or separately,
-previous work that considered both simultaneously (as we do here).
-
-But, magnetic damping offers a tantalizing alternate explanation and has not
+\citet{rettig2012} mention independent estimates of magnetic field, from
+\citet{acero2010, acciari2011} for SN 1006 and Tycho (considering gamma-ray,
+radio, X-ray data).
+
+Magnetic damping offers a tantalizing alternate explanation and has not
 been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
-\citet{rettig2012} proposed discriminating based on filament spectra -- the
+\citet{rettig2012} gave model predictions for several historical SNRs and
+proposed discriminating based on filament spectra -- the
 expectation is that damped spectra are softer, loss-limited harder.
@@
 % Why Tycho's SNR
-To test these models, we turn to the filaments of Tycho's supernova remnant
-(hereafter, Tycho).
-Like all historical SNe, Tycho is close enough that we can spatially
-resolve these rims with \Chandra and say something useful.  Like SN 1006, Tycho
-has well defined synchrotron rims associated with expansion into a low-density
-ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
-\unit{cm^{-3}}$ from \textit{Spitzer} observations of shocked ISM dust
-emission, consistent with Tycho's X-ray expansion rate \citep{katsuda2010}; SN
-1006, by comparison, has pre-shock density $\abt 0.01$--$0.1 \unit{cm^{-3}}$ at
-its nonthermal NE, SW limbs \citep{acero2007}.
-\note[Aaron]{More disjointed}
-Mention molecular cloud interaction \citep{reynoso1999}? Maybe below in region
-selection as well.
-Previous estimates of Tycho fields/diffusion (something similar to Sean's table
-for SN 1006?).  CR acceleration (aside: \citet{eriksen2011}) evidence in Tycho,
-if relevant.
+To further test these models, we turn to the remnant of Tycho's 1572 supernova
+(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
+its rims are well-resolved by \textit{Chandra}'s spatial resolution.  Tycho has
+an extensive and unusually contiguous shell of synchrotron rims around its
+periphery, consistent with expansion into a low density ISM; ISM.
+\citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
+\unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
+\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
+\citep{williams2013} and interacting with a molecular cloud on its eastern limb
+\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
+more consistent shock acceleration around its periphery than in other
+historical remnants, whether of Type Ia or CC SNe \note[Aaron]{this is not really
+justifiable, but I think it's worth noting something to this effect?}.
+CR acceleration evidence in Tycho, if relevant? \citet{eriksen2011,
+acciari2011}.
 
@@
 We measure Tycho's rim widths, following the work of \citet{ressler2014}
-(hereafter, \citetalias{ressler2014}) in the remnant of SN 1006.
+(hereafter, \citetalias{ressler2014}) on the remnant of SN 1006.
 We make measurements to distinguish between two main scenarios
@@
 $b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
-vary as $B=B(x)$.  The sink term is $C = -f / \tsynch$, yielding:
+vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
 \begin{equation} \label{eq:simp-mod}
@@
 maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
-\begin{equation} \label{eq;simp-fwhm}
+\begin{equation} \label{eq:simp-fwhm}
     w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
@@
     v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
-    K_0 E^{-s} e^{-E/E_{\mt{cut}}} \delta(x) + \frac{\ptl}{\ptl E}
+    K_0 E^{-s} e^{-E/\Ecut} \delta(x) + \frac{\ptl}{\ptl E}
       \left(bB^2E^2f\right)
@@
 distribution is an exponentially cut-off power law with normalization $K_0$ and
-cut-off energy $E_{\mt{cut}}$; the expression for the cut-off energy is
-determined by the form of the diffusion coefficient $D$, which we discuss in
+cut-off energy $\Ecut$; the cut-off energy is determined by the form of the
+diffusion coefficient $D$, which we discuss in
 Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
@@
 
+In what follows we consider both transport models, but primarily present
+results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
+the qualitative behavior of both models is comparable.
+
 \subsection{Diffusion energy-dependence} \label{sec:diffcoeff}
+
+The modus operandi of previous work has been to assume Bohm diffusion, or at
+least Bohm diffusion-energy scaling.  Bohm diffusion makes the
+assumption that particle mean free path, and hence the diffusion coefficient,
+is proportional to the particle gyroradius, yielding $D \propto E$.
+
+\citet{reynolds2004} suggested that physically motivated models of MHD
+turbulence could give rise to non-linear diffusion-energy scalings, assuming
+quasi-linear turbulence \note[Aaron]{read more}.
+Specifically, power-law energy-wavenumber spectra for Kolmogorov and Kraichnan
+turbulence predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
+
+We consider a generalized diffusion coefficient that allows arbitrary
+power-law dependence of diffusion upon energy:
+\begin{equation} \label{eq:diffcoeff}
+    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
+\end{equation}
+As the diffusion coefficient is energy dependent, we rewrite the diffusion
+coefficient in terms of a fiducial energy $E_h = 2 \unit{keV}$ throughout, with
+$\eta_2 = \eta_h$.  The constant $\eta_2$ is the diffusion coefficient at
+$2 \unit{keV}$ scaled by the Bohm diffusion value.
+\note[Aaron]{Also give some intuition of relation of $D$ and $\Ecut$ to relate to
+previous studies.}
 
@@
 
-Bohm diffusion: $D(E) = \eta C_d E / B$. Generalized diffusion writen as:
-\begin{equation}
-    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
-\end{equation}
-Explain the use of fiducial energy -- this makes sense and eases discussion,
-but linking $E_h$ and $\eta_2$ to $\eta$ and plain Bohm diffusion seems a bit
-murky.
-
-Mention that different $\mu$ values arise from particular models of turbulence.
-
-We use an electron spectrum cut-off energy of:
+With a diffusion coefficient in hand, we determine the electron spectrum
+cut-off energy by equating synchrotron loss and acceleration timescales;
+the acceleration timescale is determined from the theory of diffusive shock
+acceleration.  The cut-off energy, following \citet{parizot2006}, is given as:
 \begin{align*}
-    E_{\mt{cut}} =
+    \Ecut =
         &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
@@
 \end{align*}
-which is equation~(19) of \citetalias{ressler2014}.
 \note[Aaron]{This differs from Sean's presentation -- I drew this from the
@@
 following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.
+\note[Aaron]{Look over \citet{marcowith2010}.}
+
+Set up the calculation w/ a range of scale lengths (with $B_0$,
+$\eta_2$ chosen so that damping is the dominant control for $0.7$--$7
+\unit{keV}$), and compute FWHMs and $\mE$ values?
+
+\subsection{Previous studies of Tycho}
+
+\note[Aaron]{Should we follow \citet{ressler2014} in adding a table of prior
+magnetic field estimates?  I am uncertain of where to review previous
+literature -- introduction gives more direct motivation and context, putting
+before or in-line w/models allows us to explain who used what.  Putting
+before/after model exposition, keeps all the numbers/explanation of previous
+work in one place -- also easier to pull in discussion of other
+methods/attacks.  Right now text is rather disjointed.}
+\citet{parizot2006} derive magnetic fields of $300$--$500 \unit{\mu G}$; they
+also give both diffusion coefficients (in their $k_0$?) and $\Ecut$ values.
+\citet{rettig2012} used a measured filament lengthscale and considered
+loss-limited and magnetic damping models separately for several historical
+SNRs.  For Tycho: they report $B = 310 \unit{\mu G}$ with $\Ecut = 24
+\unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
+lengthscales, this is equivalent to our reporting of a diffusion coefficient
+(?).  With magnetic damping, they report $B = 150 \unit{\mu G}$ and a larger
+$\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
+give $80$, $230 \unit{\mu G}$ for leptonic/hadronic models for gamma-ray
+emission in Tycho.
 
@@
 it doesn't look like it made a big difference?)
+If the PSF matters, this favors some combination of stronger
+magnetic fields and weaker diffusion.
 
@@
 %      just to be more consistent (just from eyeballing...)
+% Update these numbers before final version.
 We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
@@
 and the stretched or compressed FWHMs as upper/lower bounds on our reported
-FWHMs.
+FWHMs. \note[Aaron]{Unimportant note: chi-squared values from our
+fits assume that input errors are 1-sigma.  But, taking $\Delta\chi^2 = 1$
+for our FWHM errors would shrink the errors even further, and the errors
+don't reflect uncertainty that may arise from, e.g., using different fit
+functions or taking different profiles.}
 
@@
 % Model knobs and how we twiddled them
-We have three parameters to vary (more if we consider magnetic damping):
+We varied three physical parameters (more if we consider magnetic damping):
 diffusion-energy scaling exponent $\mu$, normalized diffusion
 coefficient $\eta_2$, and magnetic field strength $B_0$.
-To make our nonlinear fitting tractable, we fix $\mu$ in all fits and
-consider $\mu = 0$, 1/3, 1/2, 1, 1.5, and 2; recall that $\mu = 1/3$ and $1/2$
-respectively correspond to predictions from Kolmogorov and Kraichnan turbulent
-energy spectra.  As $\eta_2$ is highly variable in our fits, we also consider
+To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
+$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$;
+recall that $\mu = 1/3$ and $1/2$ correspond to Kolmogorov and Kraichnan turbulence.
+As $\eta_2$ is highly variable in our fits, we also performed
 fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.
@@
 % How to do the fit
-Our data are readily fit to the simple model by equation~\eqref{eq:simp-width}.
-The full model is numerically computed as detailed in
+Equation~\eqref{eq:simp-fwhm} was directly fit to our measurements to obtain
+best-fit values of $\eta_2$ and $B_0$.
+The full model was numerically computed as detailed in
 Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
-in each energy band.
-For least squares fitting purposes, the full model is treated as a black box
-that takes in physical parameters
+in each energy band; we then varied the input parameters ($\eta_2$, $B_0$) to
+obtain a least squares best fit.
+To assist the nonlinear fitting, we tabulated a large grid of model FWHM values
+for various values of $\mu$ and shock velocity $v_s$; from a best initial grid
+value, we then used a Levenberg-Marquardt fitting routine to determine the best
+fits.
+For both simple and full fits, we deemed fits with $\eta_2 \geq 10^5$ and $B_0
+\geq 10 \unit{mG}$ effectively unconstrained; $\eta_2$ is also constrained to
+be positive .
+
 % TODO modify tables to match what is stated here -- in regards to parameters
@@
 % TODO for extreme values in tables -- go back and double check chi^2 space
-To perform full model fits, we tabulated a large grid for fixed values of $\mu$
-and shock velocity $v_s$.  If any fit runs to $\eta_2 = 10^5$ or $B_0 = 10
-\unit{mG}$, we deem it effectively unconstrained (only a few fits do so, and
-only to the $\eta_2$ limit).  Note that we do not allow / consider fits with
-$\eta_2$ negative (may be trivial, just note parameter bounds).  As the full
-continuous loss model must be numerically solved, its predicted rim widths are
+As the full model must be numerically solved, its predicted rim widths are
 subject to resolution error in the numerical integrals.  We chose our
-integration resolutions such that the fractional error associated with
-halving/doubling our resolution is less than $1\%$ for the parameter space
-relevant to our filaments.
-\note[Aaron]{rewrite -- unclear.  Need to verify
-1\% claim and check Pacholczyk table resolution (and possibly Bessel
-function numbers)...}
+integration resolutions such that the fractional error in model FWHMs
+associated with halving/doubling integration resolution is less than $1\%$ for
+the parameter space relevant to our filaments.
+\note[Aaron]{rewrite -- unclear.  Need to verify 1\% claim and check Pacholczyk
+table resolution (and possibly Bessel function numbers)...}
 
@@
 In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
-As previously noted, we could not resolve FWHMs for some regions in the
-0.7--1 keV band.  We also report $\mE$ values for all but the lowest energy
-band, computed point-to-point as $\mE(E_2) = \ln(w_2/w_1) / \ln(E_2/E_1)$ where
-$w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each energy
-band (e.g., $\mE(\text{1 keV}) = \ln(w(\text{1-1.7 keV}/w(\text{0.7-1 keV})) /
-\ln(\text{1 keV}/\text{0.7 keV})$ is computed from widths/energies.  Although
-the values of $\mE$ reflect a good deal of variability in the underlying width
-measurements, we see that most regions and energy bands display a decrease in
-rim widths as a function of energy.
+As previously noted, we could not resolve FWHMs for some regions in the 0.7--1
+keV band.  We also report $\mE$ values for all but the lowest energy band,
+computed point-to-point as: \begin{equation} \mE(E_2) =
+\frac{\ln(w_2/w_1)}{\ln(E_2/E_1)} \end{equation} where $w_1, w_2$ and $E_1,
+E_2$ are FWHMs and lower energy values for each energy band (e.g., $\mE$ at $1
+\unit{keV}$ is computed using FWHMs from $0.7$--$1 \unit{keV}$ and $1$--$1.7
+\unit{keV}$, and taking $E_2 = 1 \unit{keV}$ and $E_1 = 0.7 \unit{keV}$.
+Although the values of $\mE$ reflect a good deal of variability in the
+underlying width measurements, we see that most regions and energy bands
+display a decrease in rim widths as a function of energy.  NOTE (draft): we
+emphasize that $\mE$ is currently not considered or utilized in our subsequent
+analysis.
 
@@
 \end{table*}
-
-Here we have presented $\mE$ to demonstrate the fall-off of rim width energy.
-However, we emphasize that $\mE$ is currently not factored into our subsequent
-analysis.
 
@@
 produces the same qualitative trends seen in the full continuous energy loss
-model.
-The first row of Table~\ref{tab:fits} compares simple and full model fits for
-Region 1.
-The key differences are \emph{blah}.  The errors are comparable, the parameters
-are comparable but shifted by X amount; this is consistent in all filaments?
-(details tbd).
-Consequently, we present only the full model fits for all other
-filaments in Table~\ref{tab:fits}.  However, the simple model is useful for
-building intuition and we will refer to its results in the following discussion
-(?); \citetalias{ressler2014} also give examples of simple model fits in SN
-1006 \note[Aaron]{sentence maybe unnecessary}.
+model.  The first row of Table~\ref{tab:fits} compares simple and full model fits for
+Region 1.  In general, simple model fits are less poorly constrained (i.e.,
+fits are more likely to reach manual fitting limits).
+Where both simple and full model fits are well constrained (i.e., moderate to
+small $\eta_2$ values), the simple model favors slightly smaller $\eta_2$ and
+slightly larger $B_0$.  But this is not always true, and it is difficult to
+identify any obvious trends as both fits are quite variable across $\mu$ values
+and different regions.
+\note[Aaron]{from the table calculations, the simple model needed larger $B_0$
+values than the full model for a fixed $\eta_2$ and mean width (roughly
+speaking); this effect strengthened with larger $\eta_2$.  We're looking at
+order 10--50\% effects}.
+For the rest of our results and discussion, we consider only full model fits.
 
@@
 limits on our fit parameters.
+In Figure~\ref{fig:fits-all} we also plot the best full model fits for the same
+regions tabulated in Table~\ref{tab:fits}
+
 \begin{table}[ht]
@@
 
-HERE we show two examples of fits -- one where the models just happen to fit
-the data very nicely, and one where the models are way off (enormous $\chi^2$
-and/or errors too small).  We specifically choose to highlight the most extreme
-cases, to emphasize that our fits are hit-and-miss in practice.
-We also show the simple model fits here to illustrate the similar qualitative
-behavior between simple/full model fits.
-
-In Figure~\ref{fig:fits-all} we plot the full model fits for the same regions
-tabulated in Table~\ref{tab:fits}
-
 % NOTE need better subplot display in final version, if we keep this
@@
     \centering
+    %\epsscale{0.45}  % For manuscript layout only!
     \plottwo{figures/fits-sep13/reg01.png}{figures/fits-sep13/reg02.png} \\
@@
     Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
-    number.}
+    number.  NOTE: figures for Regions 9, 11 are incorrect.}
     \label{fig:fits-all}
@@
 Table~\ref{tab:fits-avg-eta2-fix}).
-
-\begin{table*}
+\note[Aaron]{this should be computed just for Region 1, or something similar?}
+
+\begin{table*}[ht]
     \scriptsize
@@
 averages and errors are strongly affected by outliers from extreme best fit
-values, as can be seen in Table~\ref{tab:fits} -- especially as the typical
-number of regions per filament (i.e., our sample size) is quite small.
-
-\begin{table*}
+values, as can be seen in Tables~\ref{tab:fits} and \ref{tab:fits-pt2} --
+especially as the typical number of regions per filament is quite small.
+
+\begin{table*}[ht]
     \scriptsize
@@
 % Global fits...
-Finally, we report a global average of best fit parameters from all regions.
-We could toss this into Table~\ref{tab:fits-avg}.  Reported errors are
-again standard errors of the mean (not CI, use CI? I dunno), which gives an
-idea of the spread of our measurements.
-
+Extras: we could report a global average of best fit parameters from all
+regions, or a fit to the global FWHM average.
 Plot of best fit parameters with $\mu=1$ as a function of azimuth angle, with
@@
 
-Explain briefly, effects (percentage change or similar?) of model fit parameter
-changes, results if we vary Tycho distance to $2.3 \unit{kpc}$ or $4
-\unit{kpc}$; see \citet{hayato2010}.
-
-Is it worth discussing effects of various twiddle-ables: compression ratio $r$,
+Discuss, briefly, effects of twiddle-ables: changing Tycho distance ($2.3
+\unit{kpc}$ to $4 \unit{kpc}$, see \citet{hayato2010}), compression ratio $r$,
 accounting for azimuthal variation in $v_s$ (compare to taking a remnant
-average)?  Sean already discussed $E_{\mt{cut}}$ (result: more high energy
-elections to damp out widening effect at high energy).
-
-(YES, ADD THIS TO DRAFT -- MAY AS WELL)
-
-Any azimuthal variations -- need the table of filament averaged parameters
-first, and possibly smaller regions.
+average?).  Sean already discussed $\Ecut$ (result: more high energy electrons
+to damp out narrowing at high energy, if $\Ecut$ not included).
 
@@
 
-It would be helpful to average $\mE$ values together, under the
+It might be helpful to average $\mE$ values together, under the
 assumption that they should be somewhat consistent within a given filament.
-Then report the values and errors observed.
+Then report the values and errors observed.  Again, needs more data points.
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
     \centering
@@
 \renewcommand{\thefigure}{A\arabic{figure}}
+
+% ---------------------------
+% FWHM measurement comparison
+% ---------------------------
+\section{Capped and background subtracted FWHM measurements, and simple model
+fits}
+
+Here I present full model fit results using FWHMs measured with an artificial
+cap imposed on the profile height, and the background $\min(C_u, C_d)$
+subtracted out before computing the FWHM.  The fitted profile may extend above
+the data maximum, but I find the full-width at one half of the data maximum.
+The results appear equivocal; there may be slightly smaller chi-squared values
+but it may not be statistically meaningful.
+
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for individual regions, Filament 1.}
+    \input{tab-fits-all-capsubbkg.tex}
+\end{table}
+
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for individual regions, Filaments 2--5.}
+    \input{tab-fits-all-capsubbkg-pt2.tex}
+\end{table}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Filament averages of best-fit parameters for constituent regions}
+    \input{tab-fits-par-avg-capsubbkg.tex}
+\end{table*}
+
+\begin{figure}[ht]
+    \centering
+    %\epsscale{0.45}
+    \plottwo{figures/fits-sep19-capsubbkg/reg01.png}{figures/fits-sep19-capsubbkg/reg02.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg03.png}{figures/fits-sep19-capsubbkg/reg04.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg05.png}{figures/fits-sep19-capsubbkg/reg06.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg07.png}{figures/fits-sep19-capsubbkg/reg08.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg09.png}{figures/fits-sep19-capsubbkg/reg10.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg11.png}{figures/fits-sep19-capsubbkg/reg12.png} \\
+    \plottwo{figures/fits-sep19-capsubbkg/reg13.png}{figures/f0-box.png}
+    \caption{Fitted full model widths as a function of energy for all regions,
+    with measured data; best fit parameters are given in
+    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
+    number.}
+\end{figure}
+
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Simple model best fits for individual regions, Filaments 1 and 2}
+    \input{tab-fits-all-simp.tex}
+\end{table}
+
+\begin{table}[ht]
+    \tiny
+    \centering
+    \caption{Simple model best fits for individual regions, Filaments 3--5}
+    \input{tab-fits-all-simp-pt2.tex}
+\end{table}
 
@@
 \begin{table*}[ht]
-    \tiny
+    \scriptsize
     \centering

### 2014-09-22 code/profiles/ffwhm.py

@@ -22,6 +22,8 @@ from scipy import optimize
 
 from crvfit import chi2, chi2red
 
+D_CHISQR = 2.7 # 90% confidence intervals
+
 # mega method to get everything at once because I'm lazy
 
 def get_fwhm_all(x, y, y_err, f, pars, want_err=True,y_cap=None,dx=5,**kwargs):
@@ -139,14 +141,14 @@ def get_stretch_limits(x, y, y_err, f, pars, xmax, **kwargs):
     """
 
     def chi2_threshold(xi):
-        """Threshold for chi^2 uncertainty. Output > 0 if \Delta\chi^2 > 2.7"""
+        """Threshold for chi^2 uncertainty. Output > 0 if \Delta\chi^2 > 1"""
         def chi2_stretch(xi):
             return chi2(x, y, y_err, stretch_func(f, xi, xmax, **kwargs), pars)
         chi2_stretch = np.vectorize(chi2_stretch)
 
         chi2_min = chi2(x, y, y_err, f, pars)  # same as chi2_stretch(xi=0)
 
-        return chi2_stretch(xi) - chi2_min - 2.7  # Magic number...
+        return chi2_stretch(xi) - chi2_min - D_CHISQR
 
     # Increasing positive xi (decreasing FWHM) uncertainty
     # Empirically, positive xi is better behaved than negative xi

### 2014-09-22 code/profiles/regdict.py

@@ -56,7 +56,8 @@ def main_check(inroot, labels, wlen, wtype):
             plt.title(lab)
         plt.show()
 
-def main_fwhm(inroot, outroot, labels, fitter, blacklist, wlen, wtype, **kwargs):
+def main_fwhm(inroot, outroot, labels, fitter, blacklist, wlen, wtype,
+              save=True, **kwargs):
     """Main method to compute FWHMs and generate lots of output
     Unlike other scripts, should be run in an IPython notebook.
 
@@ -72,11 +73,13 @@ def main_fwhm(inroot, outroot, labels, fitter, blacklist, wlen, wtype, **kwargs)
         blist_reg = blacklist[n_reg] if n_reg in blacklist else None
         rdict = get_fwhm_fits(rdict, n_reg, labels, fitter, blist_reg,**kwargs)
 
-        x_min, x_btw, x_max = get_cuts(rdict)
-        spec_cuts.append([n_reg, x_min, x_btw, x_max])
-        regdict_dump(rdict, n_reg, outroot)
+        if save:
+            x_min, x_btw, x_max = get_cuts(rdict)
+            spec_cuts.append([n_reg, x_min, x_btw, x_max])
+            regdict_dump(rdict, n_reg, outroot)
 
-    speccut_dump(spec_cuts, outroot)
+    if save:
+        speccut_dump(spec_cuts, outroot)
 
 # ========================================
 # Methods to create, populate region dicts

### 2014-09-22 manuscript/paper-tycho.tex
Paper text, full model simulation, more tables
Tables for Tycho regions-5, notebook to check model fit sensitivity
to eta2. More introductory text in manuscript.

@@
 % This paper
+\newcommand*\mean[1]{\bar{#1}}
+\renewcommand{\vec}[1]{\mathbf{#1}}
 \newcommand*{\tsup}{\textsuperscript}
+
 \newcommand*{\Chandra}{\textit{Chandra}\ }
-\newcommand*\mean[1]{\bar{#1}}
 \newcommand*{\tsynch}{\tau_{\mt{synch}}}
@@
 % Intro -- shocks, DSA, thin rims, filament observations; other fields/work
-Forward shock accelerated ISM/CSM particles in young supernova remnants emit
+Forward shock accelerated electrons in young supernova remnants (SNRs) emit
 synchrotron radiation strongly in the shock's immediate wake but quickly turn
@@
 morphology with bright X-ray and radio rims/filaments due to line-of-sight
-projection (hereafter, thin rims).
-Seminal observations \& interpretations of these filaments, interpretation in
-context of DSA.  Attempts to model filaments and figure out what's going on.
-Why do we care about these models?  They tell us something about what happens
-behind the shock, and perhaps what's going on at the shock.  We get at the
-plasma and magnetic field turbulence, electron injection.
-Applications to: cosmic ray acceleration, turbulent field amplification, (note
-assumptions in re proton/electron spectra).
-Cut-off energy of injected electrons?
-Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
-PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
-AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
-\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.
+projection (hereafter, thin rims).  X-ray and gamma ray imaging has provided
+several lines of indirect and direct evidence for hadron and lepton
+acceleration in SNRs \citep{uchiyama2007, aharonian2004, acero2010,
+ackermann2013}; electrons, in particular, are expected to be accelerated to
+$\abt10$--$100\unit{TeV}$ energies.  Although synchrotron emission due to
+accelerated electrons does not imply acceleration of an unseen hadronic
+component, the prevailing explanatory mechanism of diffusive shock acceleration
+(DSA) should operate on both protons and electrons; thus, observations of thin
+synchrotron rims has been often taken as supporting, indirect evidence for
+cosmic ray acceleration.  \note[Aaron]{first/second pass, very poor wording}
+
+Spectral and spatial measurements of synchrotron rims can help constrain
+physical parameters of the shock acceleration process.  Many previous workers
+have inferred magnetic field amplification at shock fronts in SNRs; a host of
+mechanisms \emph{what?!} may account for the thinness of the observed
+shocks -- much thinner than $1/12$ the forward shock radius $r_s$ as would be
+expected from a Sedov density profile \note[Aaron]{but Bamba et al. 2003 find
+consistent scale length for SN 1006?}.  \note[Aaron]{need a reference -- I
+don't have a sense of which mechanisms are most important, relevant, proven?!
+even} Many plasma physics details -- Bell's cosmic ray current instability
+\citep{bell2001} ties magnetic field amplification w/ maximum CR energy (push
+towards and just above the PeV limit).  The processes observed in SNR shocks
+are broadly relevant to many collisionless astrophysical shocks, such as
+Earth's bow shock, stellar wind-blown bubbles, starburst galaxies
+\citep{heckman1990}, jets of active galactic nuclei, galaxy clusters
+\citep{van-weeren2010}, and even cosmological shocks \citep{miniati2000,
+ryu2008}.
 
@@
 \citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
-plasma advection downstream of the shock and diffusion (\emph{driven by
-collisionless particle interaction, magnetic field turbulence, ?????  fill in
-details}) with respect to bulk advection.  Energy-dependent diffusion (e.g.,
-diffusion coefficient $D \propto E$ for Bohm diffusion) allows higher energy
-electrons to diffuse further upstream or downstream than would be expected from
-pure advection; in particular, diffusion upstream of the shock may give rise to
-a shock precursor \citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.
-Finally, the magnetic field strength may be quickly damped behind the shock, so
-that electrons may not radiate as efficiently and thin rims would reflect the
-spatial structure of the field, rather than efficient particle acceleration
-(and losses) and/or efficient synchrotron cooling \citep{pohl2005}.
+plasma advection downstream of the shock and collisionless particle diffusion
+\note[Aaron]{src?! need a simple review of plasma diffusion.  What are the
+relevant drivers of plasma diffusion?  Does it make sense to think of regimes
+of particle interaction -- e.g., thinking of single particle random
+interaction, vs. macroscopic MHD waves, or other structure?!} with respect to
+bulk advection.  In general, diffusion allows higher energy electrons to
+diffuse further upstream or downstream than would be expected from pure
+advection.  Finally, the magnetic field strength may be quickly damped behind
+the shock, so that electrons may not radiate as efficiently and thin rims would
+reflect the spatial structure of the field, rather than efficient particle
+acceleration (and losses) and/or efficient synchrotron cooling
+\citep{pohl2005}.
 
@@
 diffusion dominates.  Magnetic damping, if at a length scale comparable to
-filament widths, predicts energy-independent rim widths -- intuitively, if the
-magnetic field turns off, synchrotron radiation turns off regardless of
-electron energy.  \citet{ressler2014} give a much fuller exposition of the
-relative effects of advection, diffusion, and magnetic field damping.
+filament widths, predicts comparatively energy-independent rim widths --
+intuitively, if the magnetic field turns off, synchrotron radiation turns off
+regardless of electron energy.  \note[aaron]{this would benefit from
+numbers/quantification, I think this statement is stronger if the magnetic
+field is stronger -- compare Figure 1 of \citet{pohl2005}}\citet{ressler2014}
+give a much fuller exposition of the relative effects of advection, diffusion,
+and magnetic field damping on filament rim widths.
 
@@
 Which mechanisms are most relevant to historical SNRs?
-\note[Aaron]{need to read more / more thoroughly}
-Introduce $\tsynch$ and the basic intuition. Explain why diffusion is important
-(when did diffusion start being recognized as relevant to SNR filaments? or how was
-this shown?).
-Following Sean (i.e., taking all of his references), relevant previous
-observational studies.
-\citet{bamba2003, vink2003, yamazaki2004, ballet2006} consider advection and
-diffusion separately (with the break-point at $\Ecut$ when advective and
-diffusive length scales are equal;
+
+The primary route of attack has been to just measure the filament widths,
+determine relevant advective/diffusive lengthscales, and perhaps favor one or
+the other.  Assuming that thin rim widths are limited by synchrotron energy
+losses (loss-limited rims), you have $l_{\mt{ad}} \propto v_d \tsynch$
+gives a magnetic field...
+(how did people look at $\Ecut$ or $D$?)
+\citet{bamba2003, vink2003, yamazaki2004, ballet2006}
+More sophisticated models have followed, but the basic result is consistent --
+magnetic fields are amplified, with some amount of diffusion.
 \citet{parizot2006, araya2010} consider diffusion and advection simultaneously
@@
 equation instead.
-Conclusion that magnetic fields are amplified according to loss-limited model.  How?  Field
-amplification from plasma instabilities, evidence for stronger compression ratios?
-\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
-understand.
-\citet{rettig2012} mention independent estimates of magnetic field, from
-\citet{acero2010, acciari2011} for SN 1006 and Tycho (considering gamma-ray,
-radio, X-ray data).
-
-Magnetic damping offers a tantalizing alternate explanation and has not
+
+Some other approaches -- spectral softening \citep{cassam-chenai2007}, CD-FS
+gap \citep{warren2005}, multi-wavelength observations \citep{acero2010,
+acciari2011, morlino2012} for SN 1006 and Tycho.
+
+Magnetic damping offers a tantalizing alternative explanation and has not
 been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
+\citet{marcowith2010} did ???
 \citet{rettig2012} gave model predictions for several historical SNRs and
@@
 justifiable, but I think it's worth noting something to this effect?}.
-CR acceleration evidence in Tycho, if relevant? \citet{eriksen2011,
-acciari2011}.
 
@@
 
+% =============================
+% Transport models, observables
+% =============================
+\section{Nonthermal rim modeling}\label{sec:models}
+
 % TODO Chunk of text I don't know what to do with...
@@
 
-% =============================
-% Transport models, observables
-% =============================
-\section{Nonthermal rim modeling}\label{sec:models}
-
 \subsection{Particle transport}\label{sec:transport}
@@
 the advection-diffusion equation given by:
-\note[Aaron]{ApJ prefers bold vectors and vector operators, fix later}
+\note[Aaron]{\citet{blandford1987} take a different and more thorough tack in
+deriving the relevant transport equations, and do include the velocity
+divergence term (start w/ Vlasov equation, then transform to non-inertial?
+shock frame and tack on assumptions).  What is the best way to present this?
+I'm not sure if na\"ively citing generalized ``transport'' is sufficient.}
 % TODO fix vector operators
@@
   \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
-  = C + \del \cdot \left( D \del f \right)
+  = C + \vec{\del} \cdot \left( D \vec{\del} f \right)
 \end{equation}
@@
 % ---------------------------
-\section{Capped and background subtracted FWHM measurements, and simple model
-fits}
+\section{Additional calculations}
 
@@
 
+I also present results for simple model fits, and fits for a larger set of
+regions (22 instead of 13).
+
+\begin{table*}[ht]
+    \tiny
+    \centering
+    \caption{Measured FWHMs for all regions, capped and background subtracted.}
+    \input{tab-fwhms-capsubbkg.tex}
+\end{table*}
+
 \begin{table}[ht]
@@
     \centering
-    \caption{Full model best fits for individual regions, Filament 1.}
+    \caption{Full model best fits for individual regions, Filament 1.  Capped
+    and background subtracted FWHMs.}
     \input{tab-fits-all-capsubbkg.tex}
@@
     \centering
-    \caption{Full model best fits for individual regions, Filaments 2--5.}
+    \caption{Full model best fits for individual regions, Filaments 2--5.
+    Capped and background subtracted FWHMs.}
     \input{tab-fits-all-capsubbkg-pt2.tex}
@@
     \centering
-    \caption{Filament averages of best-fit parameters for constituent regions}
+    \caption{Filament averages of best-fit parameters for constituent regions.
+    Capped and background subtracted FWHMs.}
     \input{tab-fits-par-avg-capsubbkg.tex}
@@
     \centering
-    \caption{Simple model best fits for individual regions, Filaments 1 and 2}
+    \caption{Simple model best fits for individual regions, Filaments 1 and 2.
+    Same FWHM as in main text.}
     \input{tab-fits-all-simp.tex}
@@
     \centering
-    \caption{Simple model best fits for individual regions, Filaments 3--5}
+    \caption{Simple model best fits for individual regions, Filaments 3--5.
+    Same FWHM as in main text.}
     \input{tab-fits-all-simp-pt2.tex}
 \end{table}
+
+% -------------
+% Region 5 data
+% -------------
+
+\begin{table*}[ht]
+    \tiny
+    \centering
+    \caption{Measured FWHMs for all regions (22).}
+    \input{tab-fwhms-reg5.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for smaller regions, filaments 1--3.  Same
+    FWHM as in main text.}
+    \input{tab-fits-all-reg5.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \tiny
+    \centering
+    \caption{Full model best fits for smaller regions, filaments 4--5.  Same
+    FWHM as in main text.}
+    \input{tab-fits-all-reg5-pt2.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Filament averages of best-fit parameters for constituent regions,
+    with 22 instead of 13 regions.}
+    \input{tab-fits-par-avg-reg5.tex}
+\end{table*}
+
+\begin{figure*}
+    \centering
+    \epsscale{0.7}
+    \plotone{figures/f0-snr-reg5-inv.png}
+    \caption{RGB image of Tycho with region selections overlaid.  Bands are
+    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).}
+\end{figure*}
 
@@
 % --------------
+\clearpage
 \section{Full model validation, SN 1006 (DRAFT ONLY)}

### 2014-09-22 code/models/snr_catalog.py

@@ -99,7 +99,7 @@ def make_tycho():
                    # "filaments" within the remnant?
                    # And, Green's SNR catalog gives 0.58, not 0.65.  DAMMIT.
 
-    tycho.vs = 3.6e8 * tycho.dkpc/2.3  # Shock velocity, cm/s
+    tycho.vs = 3.6e8 * tycho.dkpc/2.3  # Average-ish shock velocity, cm/s
     # Mean of velocs from nonthermal regions, Williams et al. 2013
     tycho.cratio = 4.0  # Compression ratio, strong adiabatic shock (R-H)
 

### 2014-09-22 data-casA/ds9-casA-rgb.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+echo "Region file to load?"
+read -e reg
+
+ds9 -rgb \
+    -red 0.7-1kev_mosaic.fits \
+        -scale limits 2.5e-8 1.9e-6 \
+    -green 1-2kev_mosaic.fits \
+        -scale limits 1e-7 1e-5 \
+    -blue 2-7kev_mosaic.fits \
+        -scale limits 1e-7 1e-5 \
+    -rgb lock scale yes \
+    -log \
+    -regions $reg

### 2014-09-25 manuscript/paper-tycho.tex
More paper; full model simulations

--- 2014-09-22 manuscript/paper-tycho.tex
@@
 \begin{abstract}
-\note[Aaron]{Copy pasted from NASA abstract, not reviewed} Young supernova
-remnants may exhibit thin ($\abt1$--$10$\% of shock radius) X-ray rims of synchrotron
-radiation from forward shock-accelerated electrons that travel downstream of
-the shock and quickly cease to radiate. Rim widths limited by radiative energy
-losses should decrease with energy and require magnetic field amplification
-$10$--$100\times$ that expected from adiabatic shock compression.  Damped
-magnetic fields behind rims may produce thin rims without strong field
-amplification but require energy-independent rim widths. We measured rim widths
-around Tycho's supernova remnant in 5 energy bands using a 750 ks \Chandra
-observation. Rims narrow with increasing energy, favoring loss-limited
-radiation over magnetic damping. Observed widths are best fit by electron
-transport models requiring amplified magnetic fields $\abt0.1$--$1$ mG and
-particle diffusion $\abt1$--$10\times$ Bohm values, consistent with prior work
-on SN 1006. Inferred magnetic fields, diffusion coefficients, and
-diffusion-energy scaling may constrain models for cosmic ray acceleration in
-supernova remnants and plasma turbulence in astrophysical shocks.
+Many young supernova remnants exhibit thin X-ray bright rims of synchrotron
+radiation at their forward shocks.  Thin rims are strong evidence for strong
+magnetic field amplification, requiring shock-accelerated electrons to radiate
+and cool rapidly downstream of the shock.  But, magnetic field damping
+immediately behind the shock could produce similarly thin rims.  Synchrotron
+loss-limited rim widths should decrease with energy whereas damping limited
+rims should be relatively energy-independent.  To discriminate between models,
+we measured rim widths around Tycho's supernova remnant in 5 energy bands using
+an archival $750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing
+energy, favoring loss-limited radiation over magnetic damping and corroborating
+similar observations in the remnant of SN 1006 (Ressler et al., 2014).
+Observed widths are best fit by electron transport models requiring amplified
+magnetic fields of $\abt200$--$1000 \unit{\mu G}$ and particle diffusion
+coefficients $\abt 1$--$100\times$ Bohm values, consistent with prior work
+on Tycho's SNR.  Non-negligible diffusion results in some degeneracy between
+magnetic field strength and diffusion coefficient in setting observed rim
+widths, but strong magnetic fields are required for all measurements.  A
+different approach may be needed to better constrain diffusion at supernova
+remnant shocks.
 \end{abstract}
@@
 % ============
-\section{Introduction}
-
-\note[Aaron]{this first draft of intro structure is mostly set (in terms of
-material, number of paragraphs).  Explanations/etc may be too simplistic, I
-have more reading to do.}
+\section{Introduction} \label{sec:intro}
 
 % Intro -- shocks, DSA, thin rims, filament observations; other fields/work
-Forward shock accelerated ISM/CSM particles in young supernova remnants emit
+Forward shock accelerated electrons in young supernova remnants (SNRs) emit
 synchrotron radiation strongly in the shock's immediate wake but quickly turn
-off downstream \citep{koyama1995, reynolds1996}, producing a shell-like
-morphology with bright X-ray and radio rims/filaments due to line-of-sight
-projection (hereafter, thin rims).
-Seminal observations \& interpretations of these filaments, interpretation in
-context of DSA.  Attempts to model filaments and figure out what's going on.
-Why do we care about these models?  They tell us something about what happens
-behind the shock, and perhaps what's going on at the shock.  We get at the
-plasma and magnetic field turbulence, electron injection.
-Applications to: cosmic ray acceleration, turbulent field amplification, (note
-assumptions in re proton/electron spectra).
-Cut-off energy of injected electrons?
-Relevant to, broadly, all astrophysical shocks: Earth's bow shock,
-PWNe, SNe and/or stellar wind blown bubbles, starbursts \citep{heckman1990},
-AGN jets, galaxy clusters \citep{van-weeren2010}, and even cosmological shocks
-\citep{miniati2000, ryu2008}.  See relevant reviews \citep{blandford1987}.
+off downstream, producing a shell-like morphology with bright X-ray and radio
+rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
+synchrotron emission due to accelerated electrons does not imply acceleration
+of an unseen hadronic component, the prevailing theory of diffusive shock
+acceleration (DSA) should operate on both protons and electrons.  Observations
+of these synchrotron rims, with other lines of direct and indirect evidence,
+have built a case for hadron and lepton acceleration up to $\unit{PeV}$
+energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
+acero2010, ackermann2013} \note[Aaron]{up to PeV energies for both populations?
+Do protons reach higher energies with lower synchrotron losses?}. Efficient
+hadron acceleration, if able to convert $\abt10\%$ of a supernova's $10^{51}
+\unit{erg}$, is a prime candidate source for galactic cosmic rays up to the CR
+spectrum ``knee'' \citep{vink2012}.
+
+Spectral and spatial measurements of synchrotron rims can help constrain
+physical parameters of the shock acceleration process.  Many previous workers
+have inferred strong magnetic field amplification at SNR shocks, as electrons
+must radiate energy rapidly to account for the thinness of observed rims.
+\note[Aaron]{flesh out} Plasma physics details -- Bell's cosmic ray current
+instability \citep{bell2001} ties magnetic field amplification w/ maximum CR
+energy (push towards and just above the PeV limit).  How to get large
+compression ratios (why is 10 an upper bound suggested by Parizot), magnetic
+fields -- how far can amplification go?
+The processes observed in SNR shocks are broadly relevant to many collisionless
+astrophysical shocks, such as Earth's bow shock, stellar wind-blown bubbles,
+starburst galaxies \citep{heckman1990}, jets of active galactic nuclei, galaxy
+clusters \citep{van-weeren2010}, and even cosmological shocks
+\citep{miniati2000, ryu2008}.  Reviews of diffusive shock acceleration have
+ably highlighted the ubiquity of shock acceleration in astrophysical settings
+\note[Aaron]{too trite?} \citep[e.g.,][]{blandford1987, malkov2001}.
 
@@
 \citep[e.g.,][]{cassam-chenai2007}.  The transport process is driven by bulk
-plasma advection downstream of the shock and diffusion (\emph{driven by
-collisionless particle interaction, magnetic field turbulence, ?????  fill in
-details}) with respect to bulk advection.  Energy-dependent diffusion (e.g.,
-diffusion coefficient $D \propto E$ for Bohm diffusion) allows higher energy
-electrons to diffuse further upstream or downstream than would be expected from
-pure advection; in particular, diffusion upstream of the shock may give rise to
-a shock precursor \citep[e.g.,][]{ghavamian2000, wagner2009, laming2014}.
-Finally, the magnetic field strength may be quickly damped behind the shock, so
-that electrons may not radiate as efficiently and thin rims would reflect the
-spatial structure of the field, rather than efficient particle acceleration
-(and losses) and/or efficient synchrotron cooling \citep{pohl2005}.
+plasma advection downstream of the shock and particle diffusion with respect to
+bulk advection.  In general, diffusion allows higher energy electrons to
+diffuse further upstream or downstream than would be expected from pure
+advection.  Finally, the magnetic field strength may be quickly damped behind
+the shock, so that electrons may not radiate as efficiently and thin rims would
+reflect the spatial structure of the field, rather than efficient particle
+acceleration (and losses) and/or efficient synchrotron cooling
+\citep{pohl2005}.
 
@@
 diffusion dominates.  Magnetic damping, if at a length scale comparable to
-filament widths, predicts energy-independent rim widths -- intuitively, if the
-magnetic field turns off, synchrotron radiation turns off regardless of
-electron energy.  \citet{ressler2014} give a much fuller exposition of the
-relative effects of advection, diffusion, and magnetic field damping.
+filament widths, predicts comparatively energy-independent rim widths --
+intuitively, if the magnetic field turns off, synchrotron radiation turns off
+regardless of electron energy.  \note[Aaron]{this would benefit from
+numbers/quantification, I think this statement is stronger if the magnetic
+field is stronger -- compare Figure 1 of \citet{pohl2005}} \citet{ressler2014}
+give a much fuller exposition of the relative effects of advection, diffusion,
+and magnetic field damping on filament rim widths.
 
 % Which one is right?
-Which mechanisms are most relevant to historical SNRs?
-\note[Aaron]{need to read more / more thoroughly}
-Introduce $\tsynch$ and the basic intuition. Explain why diffusion is important
-(when did diffusion start being recognized as relevant to SNR filaments? or how was
-this shown?).
-Following Sean (i.e., taking all of his references), relevant previous
-observational studies.
-\citet{bamba2003, vink2003, yamazaki2004, ballet2006} consider advection and
-diffusion separately (with the break-point at $\Ecut$ when advective and
-diffusive length scales are equal;
-\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
-with the catastrophic dump equation.
-\citet{berezhko2003, berezhko2004, cassam-chenai2007, morlino2010, rettig2012}
-consider diffusion and advection simultaneously with the continuous loss
-equation instead.
-Conclusion that magnetic fields are amplified according to loss-limited model.  How?  Field
-amplification from plasma instabilities, evidence for stronger compression ratios?
-\citep{blondin2001}.  Lots of numerical and theoretical work that I don't
-understand.
-\citet{rettig2012} mention independent estimates of magnetic field, from
-\citet{acero2010, acciari2011} for SN 1006 and Tycho (considering gamma-ray,
-radio, X-ray data).
-
-Magnetic damping offers a tantalizing alternate explanation and has not
-been fully tested.  Equivocal results by \citet{araya2010} for Cas A.
-\citet{rettig2012} gave model predictions for several historical SNRs and
-proposed discriminating based on filament spectra -- the
-expectation is that damped spectra are softer, loss-limited harder.
-\citet{ressler2014} developed the idea of investigating energy dependence and
-found rim narrowing in the remnant of SN 1006, strongly favoring a loss-limited
-model.
+Previous work has used the typical scale width of the filaments to derive
+magnetic field estimates, among other physical parameters.  Observed
+synchrotron spectrum roll-offs at X-ray energies require corresponding cut-offs
+in the electron spectrum \citep{reynolds1998}; such a cut-off is naturally
+predicted by DSA balanced against synchrotron losses, and requires that
+diffusion and advection are both important near the electron cut-off energy
+\note[Aaron]{imprecise statement...} Whether accounting for advection and
+diffusion independently, or jointly in more sophisticated transport models, It
+became clear that magnetic field amplification was necessary to explain the
+observed filaments \citet{bamba2003, vink2003, parizot2006}.  \note[Aaron]{this
+is said 3 paragraphs above already}
+
+% Magnetic damping...
+Magnetic damping immediately behind the shock offers a tantalizing alternative
+explanation for filament rims that requires less extreme magnetic field
+amplification, and damping has not been fully tested \citep{pohl2005,
+marcowith2010}.  \citet{cassam-chenai2007} examined radio and X-ray synchrotron
+rim profiles, but found that neither damping nor synchrotron losses matched
+radio profiles particularly well.  \citet{araya2010} measured rims at multiple
+energy bands in Cas A, but suggested that the rims only narrow more weakly than
+expected and did not consider magnetic damping.  \citet{rettig2012} gave model
+predictions for several historical SNRs and proposed discriminating based on
+filament spectra -- the expectation is that damped spectra are softer,
+loss-limited harder.  \citet{ressler2014}, using deep observations of SN 1006
+from a recent \Chandra Large Project, fully developed the idea of
+differentiating damping and loss-limited scenarios by using rim width energy
+dependence and found rim narrowing in the remnant of SN 1006, strongly favoring
+a loss-limited model.
 
 % Why Tycho's SNR
-To further test these models, we turn to the remnant of Tycho's 1572 supernova
+To further test these models, we follow \citet{ressler2014} by measuring rim
+widths at multiple energies in the remnant of Tycho's 1572 supernova
 (hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
-its rims are well-resolved by \textit{Chandra}'s spatial resolution.  Tycho has
-an extensive and unusually contiguous shell of synchrotron rims around its
-periphery, consistent with expansion into a low density ISM; ISM.
-\citet{williams2013} favor mean pre-shock ISM density $\abt 0.1$--$0.2
-\unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
+its rims are well-resolved by \textit{Chandra}'s spatial resolution; the work
+is further made possible by a deep $750 \unit{ks}$ exposure of the entire
+remnant, yielding excellent count rates and allowing us to sample the rims
+quite finely.  Tycho has an extensive and unusually contiguous shell of
+synchrotron rims around its periphery, consistent with expansion into a low
+density ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt
+0.1$--$0.2 \unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
 \citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
@@
 more consistent shock acceleration around its periphery than in other
-historical remnants, whether of Type Ia or CC SNe \note[Aaron]{this is not really
-justifiable, but I think it's worth noting something to this effect?}.
-CR acceleration evidence in Tycho, if relevant? \citet{eriksen2011,
-acciari2011}.
+historical remnants, whether of Type Ia or CC SNe.
+
+Evidence for acceleration: spectral softening \citep{cassam-chenai2007}, CD-FS
+gap \citep{warren2005}, multi-wavelength observations \citep{acero2010,
+acciari2011, morlino2012} for SN 1006 and Tycho; Tycho's tiger stripes
+\citep{eriksen2011}. These further support the notion that Tycho is actively
+accelerating hadrons and leptons.
+Various questions to consider (or answer).
+Why the diversity of filament structure? How does diffusion really work?  How
+much energy is going into cosmic rays / how efficient is the acceleration
+process?  All sorts of things... (one interesting paper: \citet{caprioli2013}).
+\note[Aaron]{this para may not be necessary}
 
 % Paper roadmap
-\note[Aaron]{roadmap}
-We measure Tycho's rim widths, following the work of \citet{ressler2014}
-(hereafter, \citetalias{ressler2014}) on the remnant of SN 1006.
-We make measurements to distinguish between two main scenarios
-(explain how diffusion/advection competition come into this).
-Our procedure, in both measurement and rim width modeling, follows that of
-\citetalias{ressler2014} with only slight modifications.
-We first select regions around Tycho's forward shock for analysis, measure
-rim widths, and verify that rim spectra are free of thermal line emission.
-Using two models for particle transport, we fit measured widths...
-We discuss the implications of our fits and models for magnetic shock
-amplification (lending credence to previous estimates, in disfavoring magnetic
-field amplification), and discuss particle diffusion/acceleration at the shock.
-Any further misc. applications (constraints on precursors, etc).
-
-% TODO Chunk of text I don't know what to do with...
-We briefly review relevant particle transport models that we use to fit our
-measurements; a fuller review and exposition is given by \citetalias{ressler2014}.
-In particular, the transport models
-account for both advection and diffusion simultaneously, as opposed to
-considering the lengthscales separately with advection dominating below a
-critical energy and diffusion, above
-\citep{bamba2003, vink2003, yamazaki2004, bamba2005-hist}
-\note[Aaron]{clarify, be more specific}.
-The effects of varying various parameters, especially in regards to filament
-energy dependence, are explored in detail by \citetalias{ressler2014}.
+Our measurements and modeling closely followed and extended the procedure of
+\citet{ressler2014} (hereafter, \citetalias{ressler2014}).  We first briefly
+review relevant transport models which fully account for electron advection and
+diffusion with continuous synchrotron losses, as considered by, e.g.,
+\citet[and references therein]{berezhko2004} and \citet{rettig2012}.
+We selected and measured rim widths at several locations around Tycho's forward
+shock, verifying that selected rims are free of thermal line emission.  Using
+our model for particle transport (with DSA included, to first order, in a
+simple exponentially cut-off injected electron spectrum), we obtain estimates
+on magnetic field strength and diffusion coefficient as a function. \emph{We
+discuss the implications of our model fit results for particle transport in
+Tycho, despite a significant degeneracy between diffusion and synchrotron
+losses when diffusion is non-negligible.}
+\note[Aaron]{(tentative?)}
+\note[Aaron]{(non sub-Bohm, or anything above Bohm basically)}
 
@@
 \section{Nonthermal rim modeling}\label{sec:models}
+
+% TODO Chunk of text I don't know what to do with...
+We consider two models for particle transport to our measurements of Tycho's
+filament widths.  To best quantify width-energy dependence, we measure rim full
+widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
+measurements to these models' predictions of rim FWHMs at multiple photon
+energies.  \citetalias{ressler2014} give a fuller review of previous approaches
+to characterizing filament widths, as well as a more thorough exposition of
+model parameters and physical implications.
+
+%Early workers measured filament widths of several historical supernova remnants
+%and considered ...  Assuming that thin rim widths are limited by synchrotron
+%energy losses (loss-limited rims), you have $l_{\mt{ad}} \propto v_d \tsynch$
+%gives a magnetic field...  \citet{bamba2003, vink2003, yamazaki2004,
+%ballet2006} More sophisticated models have followed, but the basic result is
+%consistent -- magnetic fields are amplified, with some amount of diffusion.
+%\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
+%with the catastrophic dump equation.  \citet{berezhko2003, berezhko2004,
+%cassam-chenai2007, morlino2010, rettig2012} consider diffusion and advection
+%simultaneously with the continuous loss equation instead.  DSA may be
+%incorporated by direct calculation, or by assumption of a resultant electron
+%spectrum and cut-off \citep[e.g.,][]{zirakashvili2007}.
+%\citet{morlino2010}, and references therein, consider particle transport in the
+%context of nonlinear DSA neglecting particle energy losses (as would be
+%relevant for accelerated protons).  All the same principles.
 
@@
 % TODO review variable definitions when closer to final draft
+\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
+tack in deriving the relevant transport equations, drawing specifically from
+plasma physics / DSA assumptions -- I suppose much material is not relevant or
+condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
+Is na\"ively citing generalized ``transport'' is sufficient here?
+E.g., there is often a term of form $E/3 (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
+neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
+would not arise out of our equations as stated.
+See, e.g., equation (9) of \citet{skilling1975}.}
+% Transport fundamentals
 The energy and space distribution of electrons at a supernova remnant
@@
 transport from initial injection at the remnant's forward shock as following
-the advection-diffusion equation given by:
-\note[Aaron]{ApJ prefers bold vectors and vector operators, fix later}
-% TODO fix vector operators
+an advection-diffusion equation given by:
 \begin{equation}
@@
 By considering 1-D steady-state plane transport at a constant downstream
-velocity $v_d$ \note[Aaron]{we threw out 1. spherical coordinate terms, and 2.
-compressible flow terms, I think.  Is the latter justifiable?  Makes sense for
-assumption of uniform downstream velocity -- but is this a safe assumption in
-practice?  Double check order-of-magnitude...} and a space-independent diffusion
-coefficient, we obtain:
+velocity $v_d$ and a space-independent diffusion coefficient, we obtain:
 \begin{equation}
@@
 \end{equation}
-The source/sink term $C$ is determined by our assumptions about the injected
-electron energy spectrum and its time/space evolution.
-
+For simplicity, the source/sink term $C$ and diffusion coefficient $D$
+encapsulate all assumptions about the DSA-generated electron spectrum, shock
+and magnetic field structure, and time/space evolution of the particle
+distribution.  We also consider only particle transport downstream of the
+shock ($x \geq 0$).  More sophisticated treatments may explicitly treat
+magnetic fields across the shock, plasma streaming instabilities and particle
+losses, anisotropic diffusion, the DSA process and efficiency, and other
+details in great depth \citep[e.g.,][and references therein]{reville2013,
+bykov2014, ferrand2014}.
+
+% Simple model
 A first approximation is to let electrons have constant energy that is dumped
@@
     v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
-    \frac{f}{\tau_{\mt{synch}}} = 0
+    \frac{f}{\tau_{\mt{synch}}} = 0 .
 \end{equation}
-which is equation (5) of \citetalias{ressler2014}.
-\note[Aaron]{I think there should be a delta function for e- injection, but it
-probably doesn't affect the solution.  Double check.}
-Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
-\exp(-x/a)$ where $a$ is a characteristic scale length.  The full width half
-maximum (FWHM) of a thin rim produced by this ``simple'' model is given by:
+No assumptions on the injected electron source term are necessary
+\note[Aaron]{I don't have a citation, but it seems simple enough?}.
+\citet{parizot2006} employed this model to derive estimates of magnetic fields,
+diffusion coefficients, and electron spectrum cut-offs for several historical
+SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
+\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
+FWHM predicted by equation~\eqref{eq:simp-mod} is:
 \begin{equation} \label{eq:simp-fwhm}
@@
 \end{equation}
-where $\beta$ is a projection factor relating $w$ to $a$ as $w = \beta a$.  We
-take $\beta = 4.6$ assuming projection from spherical shell, as derived by
+with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
+\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
+exponential $f(E,x)$ and projection from a spherical shell, as derived by
 \citet{ballet2006}.
 
-A more advanced model is given by accounting for continuous radiation energy
-losses while electrons are transported downstream:
-\begin{equation} \label{eq:full-mod}
-    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =
-    K_0 E^{-s} e^{-E/\Ecut} \delta(x) + \frac{\ptl}{\ptl E}
-      \left(bB^2E^2f\right)
-\end{equation}
-which is equation (12) of \citetalias{ressler2014}.  The injected electron
-distribution is an exponentially cut-off power law with normalization $K_0$ and
-cut-off energy $\Ecut$; the cut-off energy is determined by the form of the
-diffusion coefficient $D$, which we discuss in
-Section~\ref{sec:diffcoeff}.  To determine rim profiles and widths, we
-numerically solve for electron distribution $f(E,x)$ using Green's function
-solutions due to \citet{lerche1980} and \citet{rettig2012}; the equations are
-given using notation close to that of this paper by \citetalias{ressler2014}.
-The electron distribution may then be integrated to obtain synchrotron
-emissivity:
+% Full model
+A more accurate model accounts for continuous synchrotron losses as electrons
+are injected from an exponentially cut-off power-law electron distribution
+(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
+\begin{align} \label{eq:full-mod}
+    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
+    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
+    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
+\end{align}
+see \citet{berezhko2004, cassam-chenai2007, morlino2010, rettig2012}; and
+references therein.  The cut-off energy is determined by the form of the
+diffusion coefficient $D$, which we discuss in Section~\ref{sec:diffcoeff}.
+(but, cf. \citet{zirakashvili2007} on the exponential cut-off assumption) To
+determine rim profiles and widths, we first numerically solve for electron
+distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
+and \citet{rettig2012}; these solutions are given by \citetalias{ressler2014}
+using notation similar to that used herein \note[Aaron]{wording}.  The electron
+distribution may then be integrated to obtain synchrotron emissivity:
 \begin{equation} \label{eq:emissivity}
@@
 where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
-$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron
-emissivity with $K_{5/3}(z)$ a modified Bessel function of the second kind
+$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
+with $K_{5/3}(z)$ a modified Bessel function of the second kind
 \citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
-spherical shell yields intensity:
+spherical remnant yields intensity as a function of radial coordinate $r$:
 \begin{equation} \label{eq:intensity}
@@
 \end{equation}
-where $s$ is the line-of-sight coordinate.  We can then compute these
-integrals (equations~\eqref{eq:emissivity},~\eqref{eq:intensity}) to obtain
-model predictions for rim FWHMs.
+where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
+from the resulting intensity profile.
 
@@
 
+% Diffusion
 \subsection{Diffusion energy-dependence} \label{sec:diffcoeff}
 
-The modus operandi of previous work has been to assume Bohm diffusion, or at
-least Bohm diffusion-energy scaling.  Bohm diffusion makes the
-assumption that particle mean free path, and hence the diffusion coefficient,
-is proportional to the particle gyroradius, yielding $D \propto E$.
-
-\citet{reynolds2004} suggested that physically motivated models of MHD
-turbulence could give rise to non-linear diffusion-energy scalings, assuming
-quasi-linear turbulence \note[Aaron]{read more}.
-Specifically, power-law energy-wavenumber spectra for Kolmogorov and Kraichnan
-turbulence predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
-
-We consider a generalized diffusion coefficient that allows arbitrary
-power-law dependence of diffusion upon energy:
+\note[Aaron]{can condense this, merge first 2 paragraphs here?}
+The modus operandi of much previous work has been to assume Bohm diffusion or
+diffusion-energy scaling ($D \propto E$).  Bohm diffusion assumes that the
+particle mean free path $\lambda$ is equal to the gyroradius $r_g = E/(eB)$,
+yielding diffusion coefficient $D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$.
+We may generalize by adding a prefactor $\eta$ such that $\lambda = \eta r_g$:
+\begin{equation} \label{eq:bohm}
+    D = \frac{\lambda c}{3} = \frac{\eta c E}{3 e B} .
+\end{equation}
+Here, and throughout, we use CGS (Gaussian) units; $c$ is the speed of light,
+$E$ is particle energy, $e$ is elementary charge, and $B$ is magnetic field.
+Bohm diffusion at $\eta = 1$ is commonly considered a lower
+limit on the diffusion coefficient at all energies, but sub-Bohm diffusion may be
+possible in turbulently amplified oblique magnetic fields
+\citep[e.g.,][]{reville2013}, and has not been well-studied.
+\note[Aaron]{I have no justification, and minimal sense, of whether this is
+correct or not.  Any treatment/discussion of Bohm diffusion?  All the papers
+seem to take it for granted} Different types of MHD turbulence, in a
+quasi-linear approximation for particle motion, may give rise to a non-linear
+energy scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
+Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence predict $D
+\propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.  For gyroradius larger
+than field coherence length, $\mu = 2$ may be relevant as well.
+\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing}
+
+In our models, we consider a generalized diffusion coefficient that with
+arbitrary power-law dependence of diffusion upon energy:
 \begin{equation} \label{eq:diffcoeff}
-    D(E) = \eta C_d E^\mu / B = \eta_h D(E_h) (E/E_h)^\mu
+    D(E) = \frac{\eta C_d E^\mu}{B}
+         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu .
 \end{equation}
-As the diffusion coefficient is energy dependent, we rewrite the diffusion
-coefficient in terms of a fiducial energy $E_h = 2 \unit{keV}$ throughout, with
-$\eta_2 = \eta_h$.  The constant $\eta_2$ is the diffusion coefficient at
-$2 \unit{keV}$ scaled by the Bohm diffusion value.
-\note[Aaron]{Also give some intuition of relation of $D$ and $\Ecut$ to relate to
-previous studies.}
-
-Explain how the transport models constrain diffusion via $\mE$, define $\mE$.
-Explain the basic interplay between diffusion and magnetic field, in
-controlling rim widths.
+This follows, e.g., \citet{parizot2006}; note that $\eta$ now has units of
+$\mathrm{erg}^{1-\mu}$.  In the right-hand side of
+equation~\eqref{eq:diffcoeff} we also rescale the diffusion coefficient to its
+value at a fiducial energy $E_h$, ; the now dimensionless $\eta_h$ is the
+diffusion coefficient scaled to the Bohm value at $E_h$.  We choose fiducial
+electron energy $E_h$ corresponding to a synchrotron photon energy of $2
+\unit{keV}$, taking the $\delta$-function approximation that an electron of
+energy $E$ radiates solely at frequency $\nu \propto E^2 B$ in a surrounding
+magnetic field.  Then $E_h \propto \sqrt{2 \unit{keV} / B}$.  The value of
+$E_h$ does depend on the user/model value of magnetic field $B$, but having
+$\eta_h$ tied to observations at $2 \unit{keV}$ gives a convenient and
+intuitive sense of diffusion strength when applied to any remnant.
 
 With a diffusion coefficient in hand, we determine the electron spectrum
-cut-off energy by equating synchrotron loss and acceleration timescales;
-the acceleration timescale is determined from the theory of diffusive shock
-acceleration.  The cut-off energy, following \citet{parizot2006}, is given as:
-\begin{align*}
+cut-off energy by equating synchrotron loss and diffusive acceleration
+timescales.  For low energies, where synchrotron losses are small (cooling time
+longer than acceleration time), electrons may be efficiently accelerated; near
+or above the cut-off energy, electrons will radiate or escape too rapidly to be
+accelerated, and so the energy spectrum drops off steeply.
+The cut-off energy adapted from \citet{parizot2006} is given as:
+\begin{align}
     \Ecut =
         &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
-        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \\
-        &\times \left(\frac{v_s}{10^8 \unit{cm/s}}\right)^{2/(1+\mu)}
-        \left[
-            \frac{E_h^{\mu - 1}}{\eta}
-        \right]^{1 / (1 + \mu)}
-\end{align*}
-\note[Aaron]{This differs from Sean's presentation -- I drew this from the
-Fortran code and it looks consistent w/ Parizot et al., but I haven't vetted
-the prefactor $8.3 \unit{TeV}$.  And, I have an extra exponent $\mu - 1$ on the
-$E_h$ ?!  Come back to this shortly.}
+        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \nonumber \\
+        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
+        \eta^{-1 / (1+\mu)} .
+\end{align}
+Note that this expression implicitly assumes (1) a strong adiabatic shock with
+compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
+downstream; see \citet{parizot2006} for a full derivation.
 
@@
 \end{equation}
-following \citetalias[Section 3.2]{ressler2014} and \citet{pohl2005}.
-\note[Aaron]{Look over \citet{marcowith2010}.}
-
-Set up the calculation w/ a range of scale lengths (with $B_0$,
-$\eta_2$ chosen so that damping is the dominant control for $0.7$--$7
-\unit{keV}$), and compute FWHMs and $\mE$ values?
+following \citet{pohl2005}.
+In the full continuous energy loss model (equation~\eqref{eq:full-mod}), it
+suffices to substitute $B = B(x)$ throughout; in the simpler model, $B(x)$
+enters through the diffusion coefficient $D = D(E,x)$ and the analytic
+expression (equation~\eqref{eq:simp-fwhm}) may no longer be valid.
+Again, \citetalias{ressler2014} detail how to integrate a damped field into the
+full model solutions.
+
+(DRAFT) We currently do not present model fits with magnetic damping, although
+in principle they are doable.  Set up the calculation w/ a range of scale
+lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
+for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?
+
+\subsection{Width-energy dependence}
+
+As discussed in Section~\ref{sec:intro}, width-energy dependence is key to
+differentiating between loss/diffusion-limited rims and magnetically damped
+rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
+terms of a scaling exponent $\mE$, defined as:
+\begin{equation}
+    w(\nu) \propto \nu^{\mE}
+\end{equation}
+where $w(\nu)$ is filament FWHM as a function of observed photon frequency
+$\nu$. We do refer to observed photons interchangeably by energy or
+frequency $\nu$; however, $E$ is reserved for electron energy.
+
+Diffusion, for our purposes, is most important in weakening the energy
+dependence of rim widths.  If both diffusion and magnetic field damping are
+negligible, and electrons are only loss-limited as they advect downstream,
+$\mE$ attains a minimum value $\mE = -0.5$ at all energies; this is the
+strongest energy-dependence possible in our models.
+Diffusion increases $\mE$ monotonically but roughly plateaus at values between
+$-0.4$ and $0$, with larger $\mu$ values yielding weaker energy-dependence
+($\mE$ closer to $0$, or even positive) \citepalias[Figure 3]{ressler2014}.
+
+If magnetic damping is a primary control on rim widths, we expect to see $\mE
+\sim -0.1$ \citepalias{ressler2014}.
+\note[Aaron]{elaborate after filling in preceding section}
 
@@
 \note[Aaron]{Should we follow \citet{ressler2014} in adding a table of prior
-magnetic field estimates?  I am uncertain of where to review previous
-literature -- introduction gives more direct motivation and context, putting
-before or in-line w/models allows us to explain who used what.  Putting
-before/after model exposition, keeps all the numbers/explanation of previous
-work in one place -- also easier to pull in discussion of other
-methods/attacks.  Right now text is rather disjointed.}
+magnetic field estimates? This could be placed here, in the intro, or in the
+discussion.}
 \citet{parizot2006} derive magnetic fields of $300$--$500 \unit{\mu G}$; they
@@
 We selected 13 regions in 5 distinct filaments around Tycho's shock
-(Figure~\ref{fig:snr}) based on the following criteria:
-(1) filaments should be clear of spatial plumes of thermal ejecta in \Chandra
-images; this rules out, e.g., areas of strong thermal emission on Tycho's eastern limb.
-(2) filaments should be singular and localized; that is, multiple filaments
-should either not overlap or completely overlap (rules out parts of NE limb);
-(3) filaments should have clear FWHMs bands; i.e., a peak should be evident
+(Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
+clear of spatial plumes of thermal ejecta in \Chandra images, which rules out,
+e.g., areas of strong thermal emission on Tycho's eastern limb; (2) filaments
+should be singular and localized; multiple filaments should either not
+overlap or completely overlap (rules out parts of NE limb); (3) filaments
+should have clear FWHMs in most energy band; i.e., a peak should be evident
 above the background signal or downstream thermal emission (rules out some
-faint southern wisps) \note[Aaron]{wishy-washy qualitative}.
-We grouped regions into filaments by visual inspection of the remnant.
+faint southern wisps) \note[Aaron]{wishy-washy qualitative}.  We grouped
+regions into filaments by visual inspection of the remnant.
 
@@
     \centering
-    \plotone{figures/f0-snr-inv.png}
+    \plotone{figures/f0-snr-reg5-inv.png}
     \caption{RGB image of Tycho with region selections overlaid.  Bands are
@@
 Is that good enough for us?
-(Cassam-Chena\"i et al. considered PSF effects when modeling rim widths, though
-it doesn't look like it made a big difference?)
-If the PSF matters, this favors some combination of stronger
-magnetic fields and weaker diffusion.
+(\citet{cassam-chenai2007} considered PSF effects when modeling rim widths,
+though it doesn't look like it made a big difference?) If the PSF matters, this
+favors some combination of stronger magnetic fields and weaker diffusion.
 
@@
 Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
-synchrotron radiation spectra for ???? population of electrons
-\note[Aaron]{citation for e- distr. indices?}. Best fit column densities from
+synchrotron radiation spectra for a steep power-law electron distribution
+\citep{vink2012}. Best fit column densities from
 upstream spectra between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$ are
@@
 % NOTE keep stated ranges of spectral indices, column densities up to date
-
-\note[Aaron]{On Rob's suggestion of fitting thermal model -- can we get away
-with just fitting line emission and constraining from there? or is the
-whole NEI apparatus needed.  If we add thermal components -- report spectral
-indices and reconfirm spectral softening?}
 
@@
 % NOTE keep mentioned number of regions updated!
-% TODO regions 2,3; 6,7 should be stretched forward a little more in regions-5
-%      just to be more consistent (just from eyeballing...)
 % Update these numbers before final version.
@@
 \geq 10 \unit{mG}$ effectively unconstrained; $\eta_2$ is also constrained to
-be positive .
+be positive.
 
@@
 parameter and obtaining a new best fit model, with one less degree of freedom,
-to find the limit s.t. $\Delta \chi^2 = 1$ to obtain a roughly 1-sigma error.
-Granted, this is not guaranteed correct for nonlinear fits (that $\Delta \chi^2
-= 1$ corresponds to a $68.3$\% confidence limit), but should be good enough.
+to find the parameter limit such that $\Delta \chi^2 = 1$ for a roughly
+1-$\sigma$ error.
 
@@
     \caption{Measured FWHMs for all regions.\label{tab:fwhms}}
-    \input{tab-fwhms.tex}
+    \input{tab-fwhms-reg5.tex}
 \end{table*}
@@
 
-% TODO do all the work, but with different FWHM calculation -- to confirm
-%      that it doesn't make a big difference...
-
 % NOTE keep updated -- for which region are we giving simple and full fits?
@@
 produces the same qualitative trends seen in the full continuous energy loss
-model.  The first row of Table~\ref{tab:fits} compares simple and full model fits for
-Region 1.  In general, simple model fits are less poorly constrained (i.e.,
-fits are more likely to reach manual fitting limits).
-Where both simple and full model fits are well constrained (i.e., moderate to
-small $\eta_2$ values), the simple model favors slightly smaller $\eta_2$ and
-slightly larger $B_0$.  But this is not always true, and it is difficult to
-identify any obvious trends as both fits are quite variable across $\mu$ values
-and different regions.
-\note[Aaron]{from the table calculations, the simple model needed larger $B_0$
-values than the full model for a fixed $\eta_2$ and mean width (roughly
-speaking); this effect strengthened with larger $\eta_2$.  We're looking at
-order 10--50\% effects}.
+model.  The first row of Table~\ref{tab:fits} compares simple and full model
+fits for Region 1 \note[Aaron]{data coming soon}.  In general, simple model
+fits are less poorly constrained (i.e., fits are more likely to reach manual
+fitting limits).  Where both simple and full model fits are well constrained
+(i.e., moderate to small $\eta_2$ values), the simple model favors slightly
+smaller $\eta_2$ and slightly larger $B_0$.  But this is not always true, and
+it is difficult to identify any obvious trends as both fits are quite variable
+across $\mu$ values and different regions.  \note[Aaron]{from the table
+calculations, the simple model needed larger $B_0$ values than the full model
+for a fixed $\eta_2$ and mean width (roughly speaking); this effect
+strengthened with larger $\eta_2$.  We're looking at order 10--50\% effects}.
 For the rest of our results and discussion, we consider only full model fits.
@@
 limits on our fit parameters.
-In Figure~\ref{fig:fits-all} we also plot the best full model fits for the same
-regions tabulated in Table~\ref{tab:fits}
-
-\begin{table}[ht]
+%In Figure~\ref{fig:fits-all} we also plot the best full model fits for the same
+%regions tabulated in Table~\ref{tab:fits}
+
+\begin{table*}[ht]
     \tiny
     \centering
-    \caption{Full model best fits for individual regions, Filament 1.
+    \caption{Full model best fits for individual regions, Filaments 1--3.
     \label{tab:fits}}
-    \input{tab-fits-all.tex}
-\end{table}
-
-\begin{table}[ht]
+    \input{tab-fits-all-reg5.tex}
+\end{table*}
+
+\begin{table*}[ht]
     \tiny
     \centering
-    \caption{Full model best fits for individual regions, Filaments 2--5.
+    \caption{Full model best fits for individual regions, Filaments 4--5.
     \label{tab:fits-pt2}}
-    \input{tab-fits-all-pt2.tex}
-\end{table}
+    \input{tab-fits-all-reg5-pt2.tex}
+\end{table*}
 
 % NOTE need better subplot display in final version, if we keep this
-\begin{figure}[ht]
-    \centering
-    %\epsscale{0.45}  % For manuscript layout only!
-    \plottwo{figures/fits-sep13/reg01.png}{figures/fits-sep13/reg02.png} \\
-    \plottwo{figures/fits-sep13/reg03.png}{figures/fits-sep13/reg04.png} \\
-    \plottwo{figures/fits-sep13/reg05.png}{figures/fits-sep13/reg06.png} \\
-    \plottwo{figures/fits-sep13/reg07.png}{figures/fits-sep13/reg08.png} \\
-    \plottwo{figures/fits-sep13/reg09.png}{figures/fits-sep13/reg10.png} \\
-    \plottwo{figures/fits-sep13/reg11.png}{figures/fits-sep13/reg12.png} \\
-    \plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
-    \caption{Fitted full model widths as a function of energy for all regions,
-    with measured data; best fit parameters are given in
-    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
-    number.  NOTE: figures for Regions 9, 11 are incorrect.}
-    \label{fig:fits-all}
-\end{figure}
+%\begin{figure}[ht]
+%    \centering
+%    %\epsscale{0.45}  % For manuscript layout only!
+%    \plottwo{figures/fits-sep13/reg01.png}{figures/fits-sep13/reg02.png} \\
+%    \plottwo{figures/fits-sep13/reg03.png}{figures/fits-sep13/reg04.png} \\
+%    \plottwo{figures/fits-sep13/reg05.png}{figures/fits-sep13/reg06.png} \\
+%    \plottwo{figures/fits-sep13/reg07.png}{figures/fits-sep13/reg08.png} \\
+%    \plottwo{figures/fits-sep13/reg09.png}{figures/fits-sep13/reg10.png} \\
+%    \plottwo{figures/fits-sep13/reg11.png}{figures/fits-sep13/reg12.png} \\
+%    \plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
+%    \caption{Fitted full model widths as a function of energy for all regions,
+%    with measured data; best fit parameters are given in
+%    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
+%    number.  NOTE: figures for Regions 9, 11 are incorrect.}
+%    \label{fig:fits-all}
+%\end{figure}
 
 % Individual region fits with eta2=1 fixed
-We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
-diffusion at $2 \unit{keV}$.  We found that the best fit $B_0$ is relatively
-insensitive to $\mu$; for all regions, $B_0$ varies by no more than XXX ($\abt 10$)\% from
-the value at $\mu = 1$ (with larger $B_0$ at smaller $\mu$ and vice versa).
-\note[Aaron]{compute/verify this}.
-Therefore, we show only best fits with $\mu = 1$ and $\eta_2 = 1$ fixed in
-Table~\ref{tab:fits-avg-eta2-fix}).
-\note[Aaron]{this should be computed just for Region 1, or something similar?}
-
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{Best fits with $\eta_2 = 1$ fixed for filament averaged FWHMs.
-    \label{tab:fits-avg-eta2-fix}}
-    \input{tab-fits-avg-eta2-fix.tex}
-\end{table*}
+%We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
+%diffusion at $2 \unit{keV}$.  We found that the best fit $B_0$ is relatively
+%insensitive to $\mu$; for all regions, $B_0$ varies by no more than XXX ($\abt
+%10$)\% from the value at $\mu = 1$ (with larger $B_0$ at smaller $\mu$ and vice
+%versa).  \note[Aaron]{compute/verify this}.  Therefore, we show only best fits
+%with $\mu = 1$ and $\eta_2 = 1$ fixed in Table~\ref{tab:fits-avg-eta2-fix}).
+%\note[Aaron]{this should be computed just for Region 1, or something similar?}
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Best fits with $\eta_2 = 1$ fixed for filament averaged FWHMs.
+%    \label{tab:fits-avg-eta2-fix}}
+%    \input{tab-fits-avg-eta2-fix.tex}
+%\end{table*}
 
@@
     \label{tab:fits-avg}}
-    \input{tab-fits-par-avg.tex}
+    \input{tab-fits-par-avg-reg5.tex}
 \end{table*}
@@
 Magnetic field $B_0$: despite the large range of fit quality, we can give
-fairly robust lower bounds.  Give lowest bound?  Consistent with previous
+fairly robust lower bounds.  Lowest bound (TBD)?  Consistent with previous
 studies, Tycho requires strong magnetic field amplification -- up to ??? times
@@
 Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
+
+We could report estimates of cut-off energy?  I don't know if that is
+helpful/meaningful for anything, unless we can tie it back to something in DSA.
 
@@
 
-In conclusion, crazy B field amplification is not that weird.
-Magnetic damping can be ruled out and our result is robust throughout the remnant.
+Our observations of filament thinning, although qualitative, are consistent
+with the observations of \citet{ressler2014} in SN 1006.
+We find that filaments narrow considerably.
+
+Filaments widths, as might be expected, do not match model predictions too
+consistently.  This may be attributed in part to spherical cow assumptions on
+Tycho's nonthermal emission and shock structure, as well as its surrounding
+medium.  This despite the fact that Tycho is the closest we have to a spherical
+cow of a SNR!
+
+We will follow up with an analysis of Kepler's supernova remnant and
+Cassiopeia A \citep[see][]{araya2010}.  Further confirmation that X-ray rims
+are not damped may suggest that any damping lengthscale must be quite a bit
+larger than the observed rims, and the damping hypothesis will need to be
+tested by continuing radio observations (???) or numerical and laboratory
+simulations.
 
@@
 % ========
-\appendix
-
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
-
-% ---------------------------
-% FWHM measurement comparison
-% ---------------------------
-\section{Capped and background subtracted FWHM measurements, and simple model
-fits}
-
-Here I present full model fit results using FWHMs measured with an artificial
-cap imposed on the profile height, and the background $\min(C_u, C_d)$
-subtracted out before computing the FWHM.  The fitted profile may extend above
-the data maximum, but I find the full-width at one half of the data maximum.
-The results appear equivocal; there may be slightly smaller chi-squared values
-but it may not be statistically meaningful.
-
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Full model best fits for individual regions, Filament 1.}
-    \input{tab-fits-all-capsubbkg.tex}
-\end{table}
-
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Full model best fits for individual regions, Filaments 2--5.}
-    \input{tab-fits-all-capsubbkg-pt2.tex}
-\end{table}
-
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{Filament averages of best-fit parameters for constituent regions}
-    \input{tab-fits-par-avg-capsubbkg.tex}
-\end{table*}
-
-\begin{figure}[ht]
-    \centering
-    %\epsscale{0.45}
-    \plottwo{figures/fits-sep19-capsubbkg/reg01.png}{figures/fits-sep19-capsubbkg/reg02.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg03.png}{figures/fits-sep19-capsubbkg/reg04.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg05.png}{figures/fits-sep19-capsubbkg/reg06.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg07.png}{figures/fits-sep19-capsubbkg/reg08.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg09.png}{figures/fits-sep19-capsubbkg/reg10.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg11.png}{figures/fits-sep19-capsubbkg/reg12.png} \\
-    \plottwo{figures/fits-sep19-capsubbkg/reg13.png}{figures/f0-box.png}
-    \caption{Fitted full model widths as a function of energy for all regions,
-    with measured data; best fit parameters are given in
-    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
-    number.}
-\end{figure}
-
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Simple model best fits for individual regions, Filaments 1 and 2}
-    \input{tab-fits-all-simp.tex}
-\end{table}
-
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Simple model best fits for individual regions, Filaments 3--5}
-    \input{tab-fits-all-simp-pt2.tex}
-\end{table}
+%\appendix
+%
+%\setcounter{table}{0}
+%\renewcommand{\thetable}{A\arabic{table}}
+%\setcounter{figure}{0}
+%\renewcommand{\thefigure}{A\arabic{figure}}
+%
+%% ---------------------------
+%% FWHM measurement comparison
+%% ---------------------------
+%\section{Additional calculations}
+%
+%Here I present full model fit results using FWHMs measured with an artificial
+%cap imposed on the profile height, and the background $\min(C_u, C_d)$
+%subtracted out before computing the FWHM.  The fitted profile may extend above
+%the data maximum, but I find the full-width at one half of the data maximum.
+%The results appear equivocal; there may be slightly smaller chi-squared values
+%but it may not be statistically meaningful.
+%
+%I also present results for simple model fits, and fits for a larger set of
+%regions (22 instead of 13).
+%
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Measured FWHMs for all regions, capped and background subtracted.}
+%    \input{tab-fwhms-capsubbkg.tex}
+%\end{table*}
+%
+%\begin{table}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fits for individual regions, Filament 1.  Capped
+%    and background subtracted FWHMs.}
+%    \input{tab-fits-all-capsubbkg.tex}
+%\end{table}
+%
+%\begin{table}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fits for individual regions, Filaments 2--5.
+%    Capped and background subtracted FWHMs.}
+%    \input{tab-fits-all-capsubbkg-pt2.tex}
+%\end{table}
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Filament averages of best-fit parameters for constituent regions.
+%    Capped and background subtracted FWHMs.}
+%    \input{tab-fits-par-avg-capsubbkg.tex}
+%\end{table*}
+%
+%\begin{figure}[ht]
+%    \centering
+%    %\epsscale{0.45}
+%    \plottwo{figures/fits-sep19-capsubbkg/reg01.png}{figures/fits-sep19-capsubbkg/reg02.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg03.png}{figures/fits-sep19-capsubbkg/reg04.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg05.png}{figures/fits-sep19-capsubbkg/reg06.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg07.png}{figures/fits-sep19-capsubbkg/reg08.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg09.png}{figures/fits-sep19-capsubbkg/reg10.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg11.png}{figures/fits-sep19-capsubbkg/reg12.png} \\
+%    \plottwo{figures/fits-sep19-capsubbkg/reg13.png}{figures/f0-box.png}
+%    \caption{Fitted full model widths as a function of energy for all regions,
+%    with measured data; best fit parameters are given in
+%    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
+%    number.}
+%\end{figure}
+%
+%\begin{table}[ht]
+%    \tiny
+%    \centering
+%    \caption{Simple model best fits for individual regions, Filaments 1 and 2.
+%    Same FWHM as in main text.}
+%    \input{tab-fits-all-simp.tex}
+%\end{table}
+%
+%\begin{table}[ht]
+%    \tiny
+%    \centering
+%    \caption{Simple model best fits for individual regions, Filaments 3--5.
+%    Same FWHM as in main text.}
+%    \input{tab-fits-all-simp-pt2.tex}
+%\end{table}
+
+% -------------
+% Region 5 data
+% -------------
+
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Measured FWHMs for all regions (22).}
+%    \input{tab-fwhms-reg5.tex}
+%\end{table*}
+%
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fits for smaller regions, filaments 1--3.  Same
+%    FWHM as in main text.}
+%    \input{tab-fits-all-reg5.tex}
+%\end{table*}
+%
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fits for smaller regions, filaments 4--5.  Same
+%    FWHM as in main text.}
+%    \input{tab-fits-all-reg5-pt2.tex}
+%\end{table*}
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Filament averages of best-fit parameters for constituent regions,
+%    with 22 instead of 13 regions.}
+%    \input{tab-fits-par-avg-reg5.tex}
+%\end{table*}
+%
+%\begin{figure*}
+%    \centering
+%    \epsscale{0.7}
+%    \plotone{figures/f0-snr-reg5-inv.png}
+%    \caption{RGB image of Tycho with region selections overlaid.  Bands are
+%    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).}
+%\end{figure*}
 
@@
 % --------------
-\section{Full model validation, SN 1006 (DRAFT ONLY)}
-
-For comparison to \citetalias{ressler2014}, we reproduce Sean's full model fit
-table (Table~\ref{tab:sean}) and present full model fits with 2 and 3 energy
-bands (Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
-We don't compare simple model results, as they are identical (only the error
-calculations differ).
-The procedures of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
-the same.  Sean used $\mE$ at 2 keV instead of the $1$--$2$ keV width for
-fitting, whereas I used both widths.  But, it should not matter much as
-the fit often has $\chi^2 \sim 0$, either way (depending on the exact
-measurements and values of $\mu$).
-
-Please take the errors with a grain of salt.  They are automatically
-generated and \textbf{have not been manually validated}.  Some values may be
-invalid, where my error-finding code failed and gave a best, conservative guess
-of the error.
-
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
-    \label{tab:sean}}
-    \input{tab-sean.tex}
-\end{table}
-
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
-    \label{tab:sn1006-2band}}
-    \input{tab-sn1006-2band.tex}
-\end{table*}
-
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{SN 1006 best fit parameters, 3 energy bands (full model).
-    \label{tab:sn1006-3band}}
-    \input{tab-sn1006-3band.tex}
-\end{table*}
+%\clearpage
+%\section{Full model validation, SN 1006 (DRAFT ONLY)}
+%
+%For comparison to \citetalias{ressler2014}, we reproduce Sean's full model fit
+%table (Table~\ref{tab:sean}) and present full model fits with 2 and 3 energy
+%bands (Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
+%We don't compare simple model results, as they are identical (only the error
+%calculations differ).
+%The procedures of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
+%the same.  Sean used $\mE$ at 2 keV instead of the $1$--$2$ keV width for
+%fitting, whereas I used both widths.  But, it should not matter much as
+%the fit often has $\chi^2 \sim 0$, either way (depending on the exact
+%measurements and values of $\mu$).
+%
+%Please take the errors with a grain of salt.  They are automatically
+%generated and \textbf{have not been manually validated}.  Some values may be
+%invalid, where my error-finding code failed and gave a best, conservative guess
+%of the error.
+%
+%\begin{table}[ht]
+%    \tiny
+%    \centering
+%    \caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
+%    \label{tab:sean}}
+%    \input{tab-sean.tex}
+%\end{table}
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
+%    \label{tab:sn1006-2band}}
+%    \input{tab-sn1006-2band.tex}
+%\end{table*}
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{SN 1006 best fit parameters, 3 energy bands (full model).
+%    \label{tab:sn1006-3band}}
+%    \input{tab-sn1006-3band.tex}
+%\end{table*}
 

### 2014-09-25 manuscript/paper-tycho.tex
New Kepler, CasA regions; run Tycho pipeline
New Kepler regions should be clean of thermal emission
Cas A regions to give sense of counts / energy bands / profile shapes
Docs to run pipelines, etc.  Minor paper updates

@@
 
-We selected 13 regions in 5 distinct filaments around Tycho's shock
+% KEEP REGION NUMBER UPDATED
+We selected 22 regions in 5 distinct filaments around Tycho's shock
 (Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
@@
 regions into filaments by visual inspection of the remnant.
+Within each filament, we chose region widths to get a similar number of counts
+at the thin rim, in each region. \note[Aaron]{wording}
+We attempted to balance signal-to-noise of each profile against having multiple
+selections for each filament (a signal-to-noise further downstream, in a
+sense); within each filament we tried to keep the number of counts in each
+region
 

### 2014-09-25 code/regions/ds9proj2box.py

@@ -34,22 +34,23 @@ def main():
     """Run from command line as python ds9proj2ciao.py -v fnamein fnameout"""
 
     parser = argparse.ArgumentParser(description=
-             'Convert DS9 region files with projections to CIAO region files')
-    
+             ('Convert DS9 region files with projections to DS9 region files'
+              'with boxes'))
+
     parser.add_argument('img', help='FITS file on which regions are defined')
     parser.add_argument('input', help='Input DS9 region file (any coords)')
-    parser.add_argument('output', help='Output CIAO region file')
+    parser.add_argument('output', help='Output DS9 region file')
     parser.add_argument('-n', '--noclean', action='store_true',
                         help='Do not remove intermediate data files')
     parser.add_argument('-v', '--verbose', action='store_true',
                         help='verbose mode')
-    
+
     # Parse arguments
     args = parser.parse_args()
     f_img = args.img
     fname_in, fname_out = args.input, args.output
     noclean, verbose = args.noclean, args.verbose
-    
+
     # Intermediate filenames
     fname_phys = fname_in + '.phys'
     fname_physproc = fname_phys + '.proc'
@@ -57,10 +58,10 @@ def main():
         print 'Verbose mode enabled'
         print 'Intermediate files:\n\t{0}\n\t{1}'.format(fname_phys,
                                                          fname_physproc)
-    
+
     # Convert ds9 file to physical coordinates
     regparse.conv_fk5_to_phys(fname_in, f_img, fname_phys)
-    
+
     # Parse file in physical coordinates, write new ds9 region file
     regstr_phys, headers = regparse.load_ds9reg(fname_phys, aux=True)
 
@@ -77,12 +78,12 @@ def main():
         print 'Writing regions to intermediate file {}'.format(fname_physproc)
     regparse.write_ds9reg(fname_physproc, regstr_physproc, headers)
 
-    # Load processed region file and save to CIAO fk5 format
+    # Load processed region file and save to DS9 fk5 format
     regparse.conv_reg_coords(fname_physproc, f_img, fname_out,
                              fmt='ds9', sys='wcs', sky='fk5')
     if verbose:
-        print 'Output written to {}'.format(fname_out)    
-    
+        print 'Output written to {}'.format(fname_out)
+
     # Cleanup
     if not noclean:
         os.remove(fname_phys)

### 2014-09-25 code/spectra/mergespectra.sh

@@ -15,17 +15,13 @@ then
 fi
 
 # Tycho's SNR, Hughes 2007
-#obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
-#wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
-#       0.053847516 0.03258367 0.04726812 0.056013404)
+obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
+wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
+       0.053847516 0.03258367 0.04726812 0.056013404)
 
 # Kepler's SNR, Reynolds 2006
-obsids=(6714 6715 6716 6717 6718 7366)
-# import numpy
-# exps = np.array([157.82, 159.13, 158.02, 106.81, 107.8, 51.46])
-# print np.sum(exps)
-# print exps / np.sum(exps)
-wghts=(0.21297096 0.21473875 0.21324085 0.14413527 0.14547123 0.06944295)
+#obsids=(6714 6715 6716 6717 6718 7366)
+#wghts=(0.21297096 0.21473875 0.21324085 0.14413527 0.14547123 0.06944295)
 
 # Check number of regions to process
 nregs=`ls -l ${1}_${obsids[0]}_src*.pi | wc -l`

### 2014-09-25 code/spectra/newregion.sh

@@ -7,13 +7,13 @@
 # First call heainit, then ds9&, then
 # call script from data/regions-[n]/ directory
 
-# obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
-obsids=(6714 6715 6716 6717 6718 7366)
+obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
+# obsids=(6714 6715 6716 6717 6718 7366)
 
 for id in "${obsids[@]}";
 do
-#    xpaset -p ds9 file "../../chandra/imgs_tycho/output${id}.fits"
-    xpaset -p ds9 file "../../chandra/${id}/repro/acisf0${id}_repro_evt2.fits"
+    xpaset -p ds9 file "../../chandra/imgs_tycho/output${id}.fits"
+#    xpaset -p ds9 file "../../chandra/${id}/repro/acisf0${id}_repro_evt2.fits"
 #    xpaset -p ds9 regions format ciao
     xpaset -p ds9 regions format ds9
     xpaset -p ds9 regions system wcs

### 2014-09-27 manuscript/paper-tycho.tex
Kepler/CasA pipeline, fits; paper cleanup
Merge projection splitting + box convert in specextract pipeline
Additional Cas A regions.  FWHMs for new Kepler regions.
Remove old tables/plots from manuscript

--- 2014-09-25 manuscript/paper-tycho.tex
@@
 
-Evidence for acceleration: spectral softening \citep{cassam-chenai2007}, CD-FS
-gap \citep{warren2005}, multi-wavelength observations \citep{acero2010,
-acciari2011, morlino2012} for SN 1006 and Tycho; Tycho's tiger stripes
-\citep{eriksen2011}. These further support the notion that Tycho is actively
-accelerating hadrons and leptons.
-Various questions to consider (or answer).
-Why the diversity of filament structure? How does diffusion really work?  How
-much energy is going into cosmic rays / how efficient is the acceleration
-process?  All sorts of things... (one interesting paper: \citet{caprioli2013}).
+Evidence for acceleration: basically, see \citet{morlino2012} for a nice review
+of evidence in Tycho.  No need to cite everything here.
+
+spectral softening \citep{cassam-chenai2007}, CD-FS gap \citep{warren2005},
+multi-wavelength observations \citep{acero2010, acciari2011, morlino2012} for
+SN 1006 and Tycho; Tycho's tiger stripes \citep{eriksen2011}. These further
+support the notion that Tycho is actively accelerating hadrons and leptons.
+Various questions to consider (or answer).  Why the diversity of filament
+structure? How does diffusion really work?  How much energy is going into
+cosmic rays / how efficient is the acceleration process?  All sorts of
+things... (one interesting paper: \citet{caprioli2013}).
 \note[Aaron]{this para may not be necessary}
@@
 overlap or completely overlap (rules out parts of NE limb); (3) filaments
-should have clear FWHMs in most energy band; i.e., a peak should be evident
-above the background signal or downstream thermal emission (rules out some
-faint southern wisps) \note[Aaron]{wishy-washy qualitative}.  We grouped
-regions into filaments by visual inspection of the remnant.
+peaks should be evident above the background signal or downstream thermal
+emission (rules out some faint southern wisps), although we selected some
+regions with poor quality peaks in the lowest energy band (0.7--1 keV) so long
+as peaks in all higher energy bands were acceptable and well-fit.
+\note[Aaron]{vague, weakly qualitative}
+We grouped regions into filaments by visual inspection of the remnant.
+Within each filament, we chose region widths to get a similar number of counts
+at the thin rim, in each region.
+We attempted to balance signal-to-noise of each profile against having multiple
+selections for each filament (a signal-to-noise further downstream, in a
+sense); within each filament we tried to keep the number of counts in each
+region roughly consistent... \note[Aaron]{wording for latter half of para}
 
@@
     \centering
-    \plotone{figures/f0-snr-reg5-inv.png}
+    \plotone{figures/f0-snr.png}
     \caption{RGB image of Tycho with region selections overlaid.  Bands are
@@
 data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
-profile (4.5--7 keV) with the downstream and upstream sections highlighted; the
-dividing line is set at the \textbf{???--???} energy band's downstream FWHM
-limit here (see Figure~\ref{fig:profiles}).
+profile (4.5--7 keV) with the downstream and upstream sections highlighted.
 We extracted background spectra from circular regions (radius $\abt 30\arcsec$)
@@
 \begin{figure*}
-    \plotone{figures/fig-specs.pdf}
-    \caption{Spectra and fits from Region 1. Left: $4.5$--$7 \unit{keV}$
+    \plotone{figures/fig-specs_01.pdf}
+    \plotone{figures/fig-specs_16.pdf}
+    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom).
+    Left: $4.5$--$7 \unit{keV}$
     profile with highlighted downstream (blue) and upstream (grey) sections.
-    Intensity units are arbitrary (a.u.).  Middle: downstream spectrum with
+    Intensity in arbitrary units (a.u.).  Middle: downstream spectrum with
     absorbed power law fit; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
     clearly visible.  Right: upstream spectrum with absorbed power law fit
-    shows that the filament is likely free of thermal line emission.}
+    shows that each region is likely free of thermal line emission.}
     \label{fig:spec}
@@
 % NOTE keep stated ranges of spectral indices, column densities up to date
+% NOTE keep example region numbers up to date
 
@@
     \input{tab-spec.tex}
-    \tablecomments{Absorbed power law fit parameters are photon index $\Gamma$
-    and hydrogen column density $\mathrm{N_H}$.}
 \end{table}
@@
 \begin{figure*}[ht]
-    \plotone{figures/fig-profiles.pdf}
+    \plotone{figures/fig-profiles_01.pdf}
+    \plotone{figures/fig-profiles_16.pdf}
     \caption{Best fit profiles with measured FWHMs demarcated for each energy
-             band in Region 1.  Red data points are excluded from profile fit
-             domain.}
+        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
+        from left to right.  Data points in red were excluded from profile
+        fitting domains as described in text.}
     \label{fig:profiles}
@@
 From the fitted profiles we extracted a full width at half maximum (FWHM) for
-each region and each energy band.  We could not resolve a FWHM in regions 2, 6,
-and 8 at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
+each region and each energy band.  We could not resolve a FWHM in 7 of 22
+regions at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
 the downstream FWHM bound would extend outside the fit domain or we could not
@@
     \caption{Measured FWHMs for all regions.\label{tab:fwhms}}
-    \input{tab-fwhms-reg5.tex}
+    \input{tab-fwhms.tex}
 \end{table*}
@@
     \label{tab:fits}}
-    \input{tab-fits-all-reg5.tex}
+    \input{tab-fits-all.tex}
 \end{table*}
@@
     \label{tab:fits-pt2}}
-    \input{tab-fits-all-reg5-pt2.tex}
+    \input{tab-fits-all-pt2.tex}
 \end{table*}
@@
     \label{tab:fits-avg}}
-    \input{tab-fits-par-avg-reg5.tex}
+    \input{tab-fits-par-avg.tex}
 \end{table*}

### 2014-09-27 code/regions/ds9proj2box.py

@@ -1,9 +1,9 @@
 """
-Convert ds9 region files to CIAO format, changing projections to boxes
+Convert ds9 region files with projections to ds9 region files with boxes
 
 Aaron Tran
 2014 June 10
-(last modified: 2014 Sept 14)
+(last modified: 2014 Sept 26)
 
 1. read DS9 file containing projection regions, fk5 coords
 2. save DS9 file in physical coords.
@@ -95,7 +95,7 @@ def main():
 
 
 def proj2box(r):
-    """Changes projection string to box string."""
+    """Changes projection string to box string (DS9 format)."""
     rtype, rnums, rprops = regparse.regparse(r)
     x1, y1, x2, y2, t = rnums
 

### 2014-09-30 manuscript/paper-tycho.tex
Kepler constants, simple fits; updated abstract
Simple model fits to Kepler FWHMs, test Cas A FWHMs.
Confirm Tycho radio spectral index.  Add revised paper (AAS) abstract,
meeting notes.

@@
 \begin{abstract}
-Many young supernova remnants exhibit thin X-ray bright rims of synchrotron
-radiation at their forward shocks.  Thin rims are strong evidence for strong
-magnetic field amplification, requiring shock-accelerated electrons to radiate
-and cool rapidly downstream of the shock.  But, magnetic field damping
-immediately behind the shock could produce similarly thin rims.  Synchrotron
-loss-limited rim widths should decrease with energy whereas damping limited
-rims should be relatively energy-independent.  To discriminate between models,
-we measured rim widths around Tycho's supernova remnant in 5 energy bands using
-an archival $750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing
-energy, favoring loss-limited radiation over magnetic damping and corroborating
-similar observations in the remnant of SN 1006 (Ressler et al., 2014).
-Observed widths are best fit by electron transport models requiring amplified
-magnetic fields of $\abt200$--$1000 \unit{\mu G}$ and particle diffusion
-coefficients $\abt 1$--$100\times$ Bohm values, consistent with prior work
-on Tycho's SNR.  Non-negligible diffusion results in some degeneracy between
-magnetic field strength and diffusion coefficient in setting observed rim
-widths, but strong magnetic fields are required for all measurements.  A
-different approach may be needed to better constrain diffusion at supernova
-remnant shocks.
+\note[Aaron]{Clone of AAS abstract}
+Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
+radiation at their forward shocks.  Thin rims have been taken to indicate that
+shock-accelerated electrons rapidly cool downstream of the shock, requiring
+strong magnetic field amplification.  But, magnetic field damping immediately
+behind the shock could produce similarly thin rims.  Synchrotron loss-limited
+rim widths should decrease with energy whereas damping limited rims should be
+relatively energy-independent.  To discriminate between models, we measured rim
+widths around Tycho's supernova remnant in 5 energy bands using an archival
+$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
+favoring loss-limited radiation over magnetic damping and corroborating similar
+observations in the remnant of SN 1006. Observed widths are best fit by
+electron transport models requiring amplified magnetic fields of
+$\abt200$--$1000 \unit{\mu G}$ and particle diffusion coefficients $\abt
+1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
+Non-negligible diffusion results in some degeneracy between magnetic field
+strength and diffusion coefficient in setting observed rim widths, but strong
+magnetic fields are required for all measurements.  A different approach may be
+needed to better constrain diffusion at supernova remnant shocks.
 \end{abstract}
@@
 % TODO GENERAL WARNING -- DATA ARE NOT ALL FULLY CONSISTENT AT THIS TIME.
-% (spectra/profiles/fwhms/fits).  Will be corrected / good to go in final
-% revision.
+% (spectra/profiles/fwhms/fits).
 
@@
 
+Brief (possibly obvious) remark: these estimates of magnetic fields should be
+lower bounds, if we neglect diffusion (and compression ratio/etc...).
+A spherical projection is the narrowest filament we can get.
+Any rippling effects, etc... hmm.  Rippling could strengthen the filament,
+making it look at little thinner actually.  But we don't know how big an effect
+that could be.  And we are looking at a tangential slice.  There is some room
+for ripples/waveforms to accumulate, of course... we see them elsewhere, we do
+see distinct filaments stacking.
+
+(maybe something useful / fun to do: what's the projection factor for a rippled
+sphere?  Estimating some wavelength from observed stripes, ripple
+lengthscale from width of filaments viewed face on (e.g. in Kepler).  Likely,
+not gonna make much difference.  But could be helpful to have an idea of how
+good/bad this assumption of a spherical shell is, and how much effect that has
+on our magnetic field estimates)
+
 Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.

### 2014-09-30 code/models/snr_catalog.py

@@ -1,7 +1,7 @@
 """
 Catalog of SNR physical parameters and synchrotron constants
 
-Aaron Tran, Summer 2014
+Aaron Tran
 2014 July 22
 """
 
@@ -18,14 +18,14 @@ SYNCH_C1 = 6.27e18  # for synchrotron emissivity (eq'n 20; see Pacholczyk)
                     # I believe C_1 = 3e/(4\pi m^3 c^5), in CGS units
                     # e = e- charge, m = e- mass, c = 3e10 cm/s
                     # i.e., prefactor for critical freq. as in
-                    # //cv.nrao.edu/course/astr534/SynchrotronSpectrum.html
+                    # cv.nrao.edu/course/astr534/SynchrotronSpectrum.html
                     # anyways this is all one giant TODO that should be typed
                     # up and thrown into the code deep review PDF
 
-CD = 2.083e19  # Bohm diffusion const; Cd = c/(3e)
+CD = 2.083e19  # Bohm diffusion const; Cd = c/(3e) (confirmed)
 BETA = 4.6  # Projection factor for exponential emissivity (Ballet, 2006)
 
-NUKEV = 2.417989e17  # Frequency of 1 keV photon
+NUKEV = 2.417989e17  # Frequency of 1 keV photon (confirmed)
 
 # ================================
 # Some convenient unit conversions
@@ -46,50 +46,69 @@ def kpc2cm(x):
 # ================================
 
 def make_kepler():
-    """Physical parameters, model/fit settings for Tycho's SNR
-    WARNING: if darc is changed, must change vs as well!
+    """Physical parameters, model/fit settings for Kepler's SNR
+    WARNING: if dkpc is changed, must change vs as well!
     """
-    k = SupernovaRemnant('Kepler')
+    kepler = SupernovaRemnant('Kepler')
 
-    kepler.dkpc = 3.3  # Distance to remnant in kpc (!) TODO verify
-                       # 4kpc from Vink (2008) kinematic study
-                       # Could be up to 7 kpc?!?!?! (Patnaude et al., 2012)
-                       # 3.3kpc from Katsuda et al. (2008)
-    kepler.rsarc = 180 # Shock radius (arcsec) from Green's SNR catalog
-    kepler.s = 2.28  # e- spectrum index, 2.3 = 2*0.65 + 1;
+    kepler.dkpc = 5    # Distance to remnant in kpc
+                       # Many conflicting results -- X-ray expansion gives
+                       # numbers of ~3.3 kpc (Katsuda et al., 2008)
[…]

### 2014-10-02 manuscript/paper-tycho.tex
Update Tycho fit data/spectra, paper results/disc
Finish pipelining all Tycho data, updated tables/plots
Incorporate all manuscript comments, tidy text up to results, flesh out
discussion.

@@
 %\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
-% \documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
+%\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
 \documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
-% \documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 \usepackage{amsmath}  % amsthm, amssymb
-% \usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
+\usepackage{CJK}  % aas.org/authors/author-names-non-roman-alphabets
 \usepackage{booktabs}
-%\usepackage[labelfont=bf, labelsep=period]{caption}  % Custom float captions
-%\usepackage{pdflscape}  % rotate pages (Texlive)
 \usepackage{hyperref}
@@
 \newcommand*{\mt}{\mathrm}
-\newcommand*{\unit}[1]{\;\mt{#1}}  % http://vemod.net/typesetting-units-in-latex
-\newcommand*{\abt}{\mathord{\sim}} % http://tex.stackexchange.com/q/55701
+\newcommand*{\unit}[1]{\;\mt{#1}}  % vemod.net/typesetting-units-in-latex
+\newcommand*{\abt}{\mathord{\sim}} % tex.stackexchange.com/q/55701
 \newcommand*{\ptl}{\partial}
@@
 \begin{document}
+%\begin{CJK}{UTF8}{gbsn}
 
@@
 
-%\begin{CJK*}{UTF8}{gbsn}
 \author{
-Aaron Tran\altaffilmark{1,4},
+Aaron Tran \altaffilmark{1,4},
+% 陳 doesn't display?
+% Also breaks emulateapj bibliography... toggle CJK env w/ AASTeX only
+%Aaron Tran (陈宏裕)\altaffilmark{1,4},
 Brian J. Williams\altaffilmark{1,5},
@@
 }
-%\end{CJK*}
 
@@
 
-%\altaffiltext{1}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
-%\altaffiltext{2}{Dept. Physics, University of California,
-%    Berkeley, CA 94720, USA}
-%\altaffiltext{3}{Dept. Physics, North Carolina State University,
-%    Raleigh, NC 27695, USA}
 \altaffiltext{4}{CRESST, University of Maryland, College Park, MD 20742}
@@
 
-% Intro -- shocks, DSA, thin rims, filament observations; other fields/work
+% What are these shock rims, what is this acceleration?
 Forward shock accelerated electrons in young supernova remnants (SNRs) emit
@@
 energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
-acero2010, ackermann2013} \note[Aaron]{up to PeV energies for both populations?
-Do protons reach higher energies with lower synchrotron losses?}. Efficient
-hadron acceleration, if able to convert $\abt10\%$ of a supernova's $10^{51}
-\unit{erg}$, is a prime candidate source for galactic cosmic rays up to the CR
-spectrum ``knee'' \citep{vink2012}.
-
-Spectral and spatial measurements of synchrotron rims can help constrain
-physical parameters of the shock acceleration process.  Many previous workers
-have inferred strong magnetic field amplification at SNR shocks, as electrons
-must radiate energy rapidly to account for the thinness of observed rims.
-\note[Aaron]{flesh out} Plasma physics details -- Bell's cosmic ray current
-instability \citep{bell2001} ties magnetic field amplification w/ maximum CR
-energy (push towards and just above the PeV limit).  How to get large
-compression ratios (why is 10 an upper bound suggested by Parizot), magnetic
-fields -- how far can amplification go?
-The processes observed in SNR shocks are broadly relevant to many collisionless
-astrophysical shocks, such as Earth's bow shock, stellar wind-blown bubbles,
-starburst galaxies \citep{heckman1990}, jets of active galactic nuclei, galaxy
-clusters \citep{van-weeren2010}, and even cosmological shocks
-\citep{miniati2000, ryu2008}.  Reviews of diffusive shock acceleration have
-ably highlighted the ubiquity of shock acceleration in astrophysical settings
-\note[Aaron]{too trite?} \citep[e.g.,][]{blandford1987, malkov2001}.
-
-% What makes these shocks?
-The widths of these X-ray rims are thought to be controlled by a combination of
+acero2010, ackermann2013}.  Efficient hadron acceleration in supernova remnant
+shocks is a prime candidate source for galactic cosmic rays up to the
+cosmic ray spectrum's ``knee'' \citep{vink2012}.
+\note[Aaron]{the discussion of hadronic acceleration isn't really relevant,
+just background information}
+
+% What can we learn from these shocks?  Why are they interesting?
+Spectral and spatial measurements of synchrotron rims can constrain physical
+parameters of the shock acceleration process.  Many previous workers have
+inferred strong magnetic field amplification at SNR shocks, as electrons must
+rapidly radiate energy to account for the thinness of observed rims
+\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
+synchrotron flux from supernova remnants steepens at X-ray energies
+\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
+spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
+\note[Aaron]{question: which came first?  observation of synchrotron
+steepening, or explanation/prediction of electron cut-off and hence synchrotron
+roll-off?  Or, even, was the electron cut-off predicted but the observable
+consequence of synchrotron roll-off not recognized until observations?} Many
+fundamental questions about the shock acceleration process remain to be
+answered.  Under what conditions do shocks accelerate particles efficiently?
+How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
+relevant observations and open questions to date.  The answers to these
+questions are broadly relevant to many astrophysical shocks, such as Earth's
+bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
+jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
+even cosmological shocks \citep{miniati2000, ryu2008}.
+% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
+% behind the shock, upstream/downstream plasma interactions and instabilities
+% These in turn affect plasma, CR dynamics -- how does the shock propagate and
+% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
+% streaming?  How efficiently are CRs accelerated?
+
+% What makes these shock rims?
+The widths of these X-ray rims are controlled by a combination of
 synchrotron losses, particle transport, and magnetic fields immediately
@@
 diffuse further upstream or downstream than would be expected from pure
-advection.  Finally, the magnetic field strength may be quickly damped behind
-the shock, so that electrons may not radiate as efficiently and thin rims would
-reflect the spatial structure of the field, rather than efficient particle
-acceleration (and losses) and/or efficient synchrotron cooling
-\citep{pohl2005}.
-
-% Energy dependence.
+advection.  Finally, the magnetic field strength may be quickly damped
+downstream of the shock, so that electrons may not radiate as efficiently and
+thin rims would reflect the spatial structure of the field, rather than
+efficient particle acceleration (and losses) and/or efficient synchrotron
+cooling \citep{pohl2005}.
+
+% Whatever makes these shock rims also imposes energy dependence
 Moreover, these controlling mechanisms predict different scalings for rim width
-as a function of energy.  Synchrotron loss-limited rims should scale as $w
-\propto \nu^{-1/2}$.  Diffusion smears out rims at all energies with stronger
-effect at higher energies, yielding a slower drop-off in rim widths when
-diffusion dominates.  Magnetic damping, if at a length scale comparable to
-filament widths, predicts comparatively energy-independent rim widths --
-intuitively, if the magnetic field turns off, synchrotron radiation turns off
-regardless of electron energy.  \note[Aaron]{this would benefit from
-numbers/quantification, I think this statement is stronger if the magnetic
-field is stronger -- compare Figure 1 of \citet{pohl2005}} \citet{ressler2014}
-give a much fuller exposition of the relative effects of advection, diffusion,
-and magnetic field damping on filament rim widths.
-
-% Which one is right?
-Previous work has used the typical scale width of the filaments to derive
-magnetic field estimates, among other physical parameters.  Observed
-synchrotron spectrum roll-offs at X-ray energies require corresponding cut-offs
-in the electron spectrum \citep{reynolds1998}; such a cut-off is naturally
-predicted by DSA balanced against synchrotron losses, and requires that
-diffusion and advection are both important near the electron cut-off energy
-\note[Aaron]{imprecise statement...} Whether accounting for advection and
-diffusion independently, or jointly in more sophisticated transport models, It
-became clear that magnetic field amplification was necessary to explain the
-observed filaments \citet{bamba2003, vink2003, parizot2006}.  \note[Aaron]{this
-is said 3 paragraphs above already}
-
-% Magnetic damping...
+as a function of energy.  In the limiting case of constant magnetic field and
+negligible particle diffusion, the rims are said to be synchrotron loss-limited
+and rim widths should narrow with increasing photon frequency $\nu$ as
+$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
+higher energies, yielding a slower drop-off in rim widths when diffusion
+dominates.  Magnetic damping, if at a length scale comparable to filament
+widths, predicts comparatively energy-independent rim widths -- intuitively, if
+the magnetic field turns off, synchrotron radiation turns off regardless of
+electron energy.
+
+% Magnetic damping?
 Magnetic damping immediately behind the shock offers a tantalizing alternative
 explanation for filament rims that requires less extreme magnetic field
-amplification, and damping has not been fully tested \citep{pohl2005,
-marcowith2010}.  \citet{cassam-chenai2007} examined radio and X-ray synchrotron
-rim profiles, but found that neither damping nor synchrotron losses matched
-radio profiles particularly well.  \citet{araya2010} measured rims at multiple
-energy bands in Cas A, but suggested that the rims only narrow more weakly than
-expected and did not consider magnetic damping.  \citet{rettig2012} gave model
-predictions for several historical SNRs and proposed discriminating based on
-filament spectra -- the expectation is that damped spectra are softer,
-loss-limited harder.  \citet{ressler2014}, using deep observations of SN 1006
-from a recent \Chandra Large Project, fully developed the idea of
-differentiating damping and loss-limited scenarios by using rim width energy
-dependence and found rim narrowing in the remnant of SN 1006, strongly favoring
-a loss-limited model.
+amplification, and the possibility of damping in SNR shocks has not been fully
+tested \citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined
+radio and X-ray synchrotron rim profiles, but found that neither damping nor
+synchrotron losses matched radio profiles particularly well.  \citet{araya2010}
+measured rims at multiple energy bands in Cas A, but suggested that the rims
+only narrow more weakly than expected and did not consider magnetic damping.
+\citet{rettig2012} gave model predictions for several historical SNRs and
+proposed discriminating based on filament spectra -- the expectation is that
+damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
+further extended the idea of discriminating between damped or loss-limited
+rims by measuring rim width energy dependence in X-ray energies and found that
+rims consistently narrowed in the remnant of SN 1006, favoring synchrotron
+loss-limited rims.
 
 % Why Tycho's SNR
-To further test these models, we follow \citet{ressler2014} by measuring rim
-widths at multiple energies in the remnant of Tycho's 1572 supernova
-(hereafter, Tycho).  Tycho, being a nearby galactic SNR, is close enough that
-its rims are well-resolved by \textit{Chandra}'s spatial resolution; the work
-is further made possible by a deep $750 \unit{ks}$ exposure of the entire
-remnant, yielding excellent count rates and allowing us to sample the rims
-quite finely.  Tycho has an extensive and unusually contiguous shell of
-synchrotron rims around its periphery, consistent with expansion into a low
-density ISM.  \citet{williams2013} favor mean pre-shock ISM density $\abt
-0.1$--$0.2 \unit{cm^{-3}}$, consistent with Tycho's X-ray expansion rate
-\citep{katsuda2010}.  Although Tycho is expanding into an ISM gradient
-\citep{williams2013} and interacting with a molecular cloud on its eastern limb
-\citep{reynoso1999}, Tycho's spherical morphology suggests that we might expect
-more consistent shock acceleration around its periphery than in other
-historical remnants, whether of Type Ia or CC SNe.
-
-Evidence for acceleration: basically, see \citet{morlino2012} for a nice review
-of evidence in Tycho.  No need to cite everything here.
-
-spectral softening \citep{cassam-chenai2007}, CD-FS gap \citep{warren2005},
-multi-wavelength observations \citep{acero2010, acciari2011, morlino2012} for
-SN 1006 and Tycho; Tycho's tiger stripes \citep{eriksen2011}. These further
-support the notion that Tycho is actively accelerating hadrons and leptons.
-Various questions to consider (or answer).  Why the diversity of filament
-structure? How does diffusion really work?  How much energy is going into
-cosmic rays / how efficient is the acceleration process?  All sorts of
-things... (one interesting paper: \citet{caprioli2013}).
-\note[Aaron]{this para may not be necessary}
+To further test these models, we follow \citet{ressler2014} (hereafter,
+\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
+remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
+extensive shell of synchrotron-dominated thin rims around its periphery; the
+rims show very little thermal emission, consistent with expansion into a low
+density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
+enough that its rims are easily resolved by \textit{Chandra} spatial
+resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from an
+archived \Chandra large project (PI: J. Hughes) also allows us to sample the
+remnant rims quite finely.  Furthermore, Tycho has been a prime target of study
+for determining whether hadrons are being accelerated in historic SNRs
+\citep[and references therein]{morlino2012}; understanding the acceleration
+process will bear upon our understanding of CR acceleration in Tycho.
+\note[Aaron]{reword/cut?}
 
 % Paper roadmap
-Our measurements and modeling closely followed and extended the procedure of
-\citet{ressler2014} (hereafter, \citetalias{ressler2014}).  We first briefly
-review relevant transport models which fully account for electron advection and
-diffusion with continuous synchrotron losses, as considered by, e.g.,
-\citet[and references therein]{berezhko2004} and \citet{rettig2012}.
-We selected and measured rim widths at several locations around Tycho's forward
-shock, verifying that selected rims are free of thermal line emission.  Using
-our model for particle transport (with DSA included, to first order, in a
-simple exponentially cut-off injected electron spectrum), we obtain estimates
-on magnetic field strength and diffusion coefficient as a function. \emph{We
-discuss the implications of our model fit results for particle transport in
-Tycho, despite a significant degeneracy between diffusion and synchrotron
-losses when diffusion is non-negligible.}
-\note[Aaron]{(tentative?)}
-\note[Aaron]{(non sub-Bohm, or anything above Bohm basically)}
+Our procedure closely follows that of \citetalias{ressler2014}.
+We first briefly review relevant transport models which fully account for
+electron advection and diffusion with continuous synchrotron losses, as
+considered by, e.g., \citet[and references therein]{berezhko2004} and
+\citet{rettig2012}.  We selected and measured rim widths at several locations
+around Tycho's forward shock, verifying that selected rims are free of thermal
+line emission.  Using our model for particle transport (with DSA included, to
+first order, in a simple exponentially cut-off injected electron spectrum), we
+obtain estimates on magnetic field strength and diffusion coefficient
+magnitude. We discuss the implications of our model fit results for
+particle transport in Tycho, despite a significant degeneracy between
+diffusion and synchrotron losses when diffusion is non-negligible.
 
@@
 
+\note[Aaron]{I am a bit uncertain on the structure/order of presentation here,
+particularly in presenting $\Ecut$ (which can be an independent observable?
+but is not considered here).  I tried to put ``enough'' to independently
+follow / re-derive all the model results.}
 % TODO Chunk of text I don't know what to do with...
@@
 model parameters and physical implications.
+
+We use CGS (Gaussian) units throughout.
+
+Any other introductory text -- emphasize that we back out two parameters,
+possibly three or more.  COME BACK after writing magnetic damping bit.
 
@@
 Is na\"ively citing generalized ``transport'' is sufficient here?
-E.g., there is often a term of form $E/3 (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
+E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
 neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
@@
 controls the synchrotron rims we see in X-ray and radio.  We model electron
-transport from initial injection at the remnant's forward shock as following
-an advection-diffusion equation given by:
-\begin{equation}
-  \frac{\ptl f}{\ptl t} + \del \cdot \left( f \vec{v} \right)
-  = C + \del \cdot \left( D \del f \right)
-\end{equation}
-where $f = f(E,x)$ is electron distribution as a function of electron energy
-$E$ and downstream distance $x$ (where the forward shock is at $x=0$ and
-$x>0$ towards the remnant's interior); $C$ is an arbitrary source/sink term,
-$D$ is the diffusion coefficient, and $\vec{v}$ is a velocity field.
-By considering 1-D steady-state plane transport at a constant downstream
-velocity $v_d$ and a space-independent diffusion coefficient, we obtain:
+advection and diffusion from initial injection at the remnant's forward shock
+assuming 1-D steady-state plane transport, with spatially homogeneous and
+isotropic diffusion, as following the equation:
 \begin{equation}
@@
 \end{equation}
-For simplicity, the source/sink term $C$ and diffusion coefficient $D$
-encapsulate all assumptions about the DSA-generated electron spectrum, shock
+Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
+and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
+towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
+the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
+shock.  We consider only particle transport downstream of the shock ($x \geq
+0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
+encapsulate all assumptions about the accelerated electron spectrum, shock
 and magnetic field structure, and time/space evolution of the particle
-distribution.  We also consider only particle transport downstream of the
-shock ($x \geq 0$).  More sophisticated treatments may explicitly treat
-magnetic fields across the shock, plasma streaming instabilities and particle
-losses, anisotropic diffusion, the DSA process and efficiency, and other
-details in great depth \citep[e.g.,][and references therein]{reville2013,
+distribution.  More sophisticated treatments may explicitly treat magnetic
+fields and diffusion across the shock, plasma streaming instabilities and
+particle losses, anisotropic diffusion, the DSA process and efficiency, and
+other details in great depth \citep[e.g.,][and references therein]{reville2013,
 bykov2014, ferrand2014}.
@@
 $b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
-vary as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
+vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
 \begin{equation} \label{eq:simp-mod}
@@
 \end{equation}
-No assumptions on the injected electron source term are necessary
-\note[Aaron]{I don't have a citation, but it seems simple enough?}.
+No assumptions on the injected electron source term are necessary.
 \citet{parizot2006} employed this model to derive estimates of magnetic fields,
@@
 \end{align}
-see \citet{berezhko2004, cassam-chenai2007, morlino2010, rettig2012}; and
-references therein.  The cut-off energy is determined by the form of the
-diffusion coefficient $D$, which we discuss in Section~\ref{sec:diffcoeff}.
-(but, cf. \citet{zirakashvili2007} on the exponential cut-off assumption) To
-determine rim profiles and widths, we first numerically solve for electron
-distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
-and \citet{rettig2012}; these solutions are given by \citetalias{ressler2014}
-using notation similar to that used herein \note[Aaron]{wording}.  The electron
-distribution may then be integrated to obtain synchrotron emissivity:
+see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
+\citet{morlino2010}, \citet{rettig2012}, and references therein.
+\citet{zirakashvili2007} have derived a different electron spectrum with a
+steeper $\exp\left(- \left(E/\Ecut\right)^2\right)$ cut-off, but we follow
+\citetalias{ressler2014} in using $E^{-s} e^{-E/\Ecut}$ for conceptual
+simplicity.  The cut-off energy is determined by the diffusion coefficient $D$,
+which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
+widths, we first numerically solve for electron distribution $f(E,x)$ using
+Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
+solutions are given by \citetalias{ressler2014} using notation similar to that
+used herein \note[Aaron]{wording}.  The electron distribution may then be
+integrated to obtain synchrotron emissivity:
 \begin{equation} \label{eq:emissivity}
@@
 
+% Moving on...
 In what follows we consider both transport models, but primarily present
 results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
-the qualitative behavior of both models is comparable.
+that the qualitative behavior of both models is comparable.
 
@@
 
-\note[Aaron]{can condense this, merge first 2 paragraphs here?}
-The modus operandi of much previous work has been to assume Bohm diffusion or
-diffusion-energy scaling ($D \propto E$).  Bohm diffusion assumes that the
-particle mean free path $\lambda$ is equal to the gyroradius $r_g = E/(eB)$,
-yielding diffusion coefficient $D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$.
-We may generalize by adding a prefactor $\eta$ such that $\lambda = \eta r_g$:
-\begin{equation} \label{eq:bohm}
-    D = \frac{\lambda c}{3} = \frac{\eta c E}{3 e B} .
-\end{equation}
-Here, and throughout, we use CGS (Gaussian) units; $c$ is the speed of light,
-$E$ is particle energy, $e$ is elementary charge, and $B$ is magnetic field.
-Bohm diffusion at $\eta = 1$ is commonly considered a lower
-limit on the diffusion coefficient at all energies, but sub-Bohm diffusion may be
-possible in turbulently amplified oblique magnetic fields
-\citep[e.g.,][]{reville2013}, and has not been well-studied.
-\note[Aaron]{I have no justification, and minimal sense, of whether this is
-correct or not.  Any treatment/discussion of Bohm diffusion?  All the papers
-seem to take it for granted} Different types of MHD turbulence, in a
-quasi-linear approximation for particle motion, may give rise to a non-linear
-energy scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
-Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence predict $D
-\propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.  For gyroradius larger
-than field coherence length, $\mu = 2$ may be relevant as well.
-\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing}
-
-In our models, we consider a generalized diffusion coefficient that with
-arbitrary power-law dependence of diffusion upon energy:
+Much previous work has assumed Bohm-like diffusion in plasma downstream of the
+shock.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
+equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
+$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
+$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
+field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
+$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
+$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
+all energies.
+\note[Aaron]{for self-edification, any justification / derivation of this
+result?  All the papers seem to take it for granted}
+However, different types of MHD turbulence may give rise to a non-linear energy
+scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
+Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
+quasi-linear approximation for particle motion,
+\note[Aaron]{I don't really know what this means}
+predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
+Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
+\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
+I have no idea what this means.}
+
+In our models, we consider a generalized diffusion coefficient with arbitrary
+power-law dependence upon energy following, e.g., \citet{parizot2006}:
 \begin{equation} \label{eq:diffcoeff}
     D(E) = \frac{\eta C_d E^\mu}{B}
-         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu .
+         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
 \end{equation}
-This follows, e.g., \citet{parizot2006}; note that $\eta$ now has units of
-$\mathrm{erg}^{1-\mu}$.  In the right-hand side of
-equation~\eqref{eq:diffcoeff} we also rescale the diffusion coefficient to its
-value at a fiducial energy $E_h$, ; the now dimensionless $\eta_h$ is the
-diffusion coefficient scaled to the Bohm value at $E_h$.  We choose fiducial
-electron energy $E_h$ corresponding to a synchrotron photon energy of $2
-\unit{keV}$, taking the $\delta$-function approximation that an electron of
-energy $E$ radiates solely at frequency $\nu \propto E^2 B$ in a surrounding
-magnetic field.  Then $E_h \propto \sqrt{2 \unit{keV} / B}$.  The value of
-$E_h$ does depend on the user/model value of magnetic field $B$, but having
-$\eta_h$ tied to observations at $2 \unit{keV}$ gives a convenient and
-intuitive sense of diffusion strength when applied to any remnant.
+where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has unites
+of $\mathrm{erg}^{1-\mu}$.
+The right-hand side of equation~\eqref{eq:diffcoeff} introduces a dimensionless
+$\eta_h$ as the diffusion coefficient scaled to the Bohm value at a fiducial
+particle energy $E_h$.  We subsequently choose the fiducial electron energy
+$E_h$ corresponding to a synchrotron photon energy of $2 \unit{keV}$, taking
+the $\delta$-function approximation that an electron of energy $E$ radiates
+solely at frequency $\nu \propto E^2 B$ in a surrounding magnetic field.  Then,
+$E_h \propto \sqrt{2 \unit{keV} / B}$.  Although the value of $E_h$ depends on
+magnetic field $B$, tying $\eta_h$ to a fixed observation energy gives a
+convenient and intuitive sense of diffusion strength regardless of the
+electron energies producing observed rims.
+\note[Aaron]{what I want to say: electron energies responsible for the rims we
+see could vary between remnants or even within a single remnant.  And, we
+cannot get a handle on diffusion at a singular electron energy or energy range,
+in all our observations.  So it's simpler to tie $\eta_h$ to observation
+energy.}
 
@@
 cut-off energy by equating synchrotron loss and diffusive acceleration
-timescales.  For low energies, where synchrotron losses are small (cooling time
-longer than acceleration time), electrons may be efficiently accelerated; near
-or above the cut-off energy, electrons will radiate or escape too rapidly to be
-accelerated, and so the energy spectrum drops off steeply.
-The cut-off energy adapted from \citet{parizot2006} is given as:
+timescales.  For low energies and small synchrotron losses (cooling time longer
+than acceleration time), electrons may be efficiently accelerated; near or
+above the cut-off energy, electrons will radiate or escape too rapidly to be
+accelerated, so the energy spectrum drops off steeply.  The cut-off energy
+adapted from \citet{parizot2006} is given as:
 \begin{align}
@@
 \end{align}
-Note that this expression implicitly assumes (1) a strong adiabatic shock with
+Note that this expression implicitly assumes (1) a strong shock with
 compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
@@
 
+% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
 We also consider (not really) a magnetically damped field of form
@@
 rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
-terms of a scaling exponent $\mE$, defined as:
+terms of a scaling exponent $\mE$ defined by:
 \begin{equation}
@@
 where $w(\nu)$ is filament FWHM as a function of observed photon frequency
-$\nu$. We do refer to observed photons interchangeably by energy or
-frequency $\nu$; however, $E$ is reserved for electron energy.
-
-Diffusion, for our purposes, is most important in weakening the energy
-dependence of rim widths.  If both diffusion and magnetic field damping are
-negligible, and electrons are only loss-limited as they advect downstream,
-$\mE$ attains a minimum value $\mE = -0.5$ at all energies; this is the
-strongest energy-dependence possible in our models.
-Diffusion increases $\mE$ monotonically but roughly plateaus at values between
-$-0.4$ and $0$, with larger $\mu$ values yielding weaker energy-dependence
-($\mE$ closer to $0$, or even positive) \citepalias[Figure 3]{ressler2014}.
-
+$\nu$, and $\mE = \mE(\nu)$ is generally energy dependent.  We may refer to
+observed photons interchangeably by energy or frequency $\nu$; however, $E$ is
+reserved for electron energy.
+
+If both diffusion and magnetic field damping are negligible (whether at a small
+range of, or all, electron energies) and electrons are only loss-limited as
+they advect downstream, $\mE$ attains a minimum value $\mE = -0.5$; this is the
+strongest energy-dependence possible in our models.  Diffusion increases $\mE$
+monotonically but roughly plateaus at values between $-0.4$ and $0$, with
+larger $\mu$ values yielding weaker energy-dependence ($\mE$ closer to $0$, or
+even positive) \citepalias[Figure 3]{ressler2014}.
+
+% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
 If magnetic damping is a primary control on rim widths, we expect to see $\mE
@@
 (RA: 00\tsup{h}25\tsup{m}19\fs0, dec: +64\arcdeg08\arcmin10\farcs0; J2000)
-between 2009 Apr 11 and 2009 May 5 (PI: John P. Hughes;
+between 2009 Apr 11 and 2009 May 5 (PI: J. Hughes;
 \dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
@@
 0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
-We excluded 1.7--2 keV energy range to avoid the \ion{Si}{13} (He$\alpha$)
-emission line at 1.85 keV, prevalent in the remnant's thermal ejecta, which
-\remove[Brian]{could} \remove[Aaron]{would} \add[Aaron]{may}
-\note[Aaron]{since some profiles are practically uncontaminated?}
-contaminate our nonthermal profile measurements.
+We excluded the 1.7--2 keV energy range to avoid any \ion{Si}{13} (He$\alpha$)
+emission at 1.85 keV, prevalent in the remnant's thermal ejecta, which
+might contaminate our nonthermal profile measurements.
 
 % KEEP REGION NUMBER UPDATED
-We selected 22 regions in 5 distinct filaments around Tycho's shock
+We selected 20 regions in 5 distinct filaments around Tycho's shock
 (Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
@@
 should be singular and localized; multiple filaments should either not
-overlap or completely overlap (rules out parts of NE limb); (3) filaments
+overlap or completely overlap (rules out parts of NE limb); (3) filament
 peaks should be evident above the background signal or downstream thermal
-emission (rules out some faint southern wisps), although we selected some
+emission (rules out faint southern filaments).  We accepted several
 regions with poor quality peaks in the lowest energy band (0.7--1 keV) so long
-as peaks in all higher energy bands were acceptable and well-fit.
-\note[Aaron]{vague, weakly qualitative}
+as peaks in all higher energy bands were clear and well-fit.
+\note[Aaron]{vague, imprecise}
 We grouped regions into filaments by visual inspection of the remnant.
-Within each filament, we chose region widths to get a similar number of counts
-at the thin rim, in each region.
-We attempted to balance signal-to-noise of each profile against having multiple
-selections for each filament (a signal-to-noise further downstream, in a
-sense); within each filament we tried to keep the number of counts in each
-region roughly consistent... \note[Aaron]{wording for latter half of para}
-
-% NOTE generate final, higher quality figure + newer figure for regions-5
+Within each filament, we chose region widths to obtain comparable counts
+at the thin rim peak.
+All measured rim widths are at least $1\arcsec$ and hence are resolved by
+\textit{Chandra}'s point-spread function (PSF), which has FWHM of
+$\abt 1\arcsec$ at $4\arcmin$ off-axis.
+
+% TODO final figure should be higher quality, use vector overlay if possible
 \begin{figure}
     \centering
-    \plotone{figures/f0-snr.png}
-    \caption{RGB image of Tycho with region selections overlaid.  Bands are
-    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).
-    \note[Aaron]{Could show the spectrum extraction regions on here too?
-    Maybe too cluttered.  Figure colors inverted to save ink.}}
-    \label{fig:snr}
+    \plotone{figures/f0-snr-inv.png}
+    \caption{RGB image of Tycho with region selections overlaid.  Image bands
+    are 0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).  Bold region
+    labels (1, 16) indicate region selections shown in
+    Figures~\ref{fig:spec},~\ref{fig:profiles}.
+    \note[Aaron]{Figure colors inverted to save ink.} \label{fig:snr}}
 \end{figure}
-
-All measured rim widths are at least $\abt 1\arcsec$ and hence are resolved by
-\textit{Chandra}'s point-spread function.
-Looking at proposer's guide, Figure 4.13 -- the off-axis PSF should
-still have FWHM of $\abt 1\arcsec$ at $4\arcmin$ (approx. Tycho's radius).
-Is that good enough for us?
-(\citet{cassam-chenai2007} considered PSF effects when modeling rim widths,
-though it doesn't look like it made a big difference?) If the PSF matters, this
-favors some combination of stronger magnetic fields and weaker diffusion.
 
@@
 upstream section is the smallest sub-region that contains the measured FWHM
-bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this region
-captures the thin rim.  The downstream section extends from the back of the rim
+bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this section
+overlies the thin rim.  The downstream section extends from the back of the rim
 (end of the upstream section) to the rim model fit's (equation~\eqref{eq:prof})
-downstream limit.  We merged spectra from all \Chandra ObsIDs and grouped the
-data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
-profile (4.5--7 keV) with the downstream and upstream sections highlighted.
-We extracted background spectra from circular regions (radius $\abt 30\arcsec$)
-around the remnant's exterior; each thin rim region was matched to the closest
-background region's spectrum.
+downstream limit.  We extracted spectra from all \Chandra ObsIDs and grouped
+the data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
+profile ($4.54$--$7 \unit{keV}$) with the downstream and upstream sections
+highlighted.  We extracted background spectra from circular regions (radius
+$\abt 30\arcsec$) around the remnant's exterior; each thin rim region's spectra
+subtracted the closest background region's spectrum.
 % Background region size is valid for data-tycho/bkg-2/ selections
 
-% NOTE must match fig:profiles!  Keep region numbers updated and
-% consistent.  Currently, region 1 of data-tycho/regions-4/ selections
+% NOTE must match fig:snr, fig:profiles!
+% Keep region numbers updated and consistent.
 \begin{figure*}
@@
     \plotone{figures/fig-specs_16.pdf}
-    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom).
-    Left: $4.5$--$7 \unit{keV}$
-    profile with highlighted downstream (blue) and upstream (grey) sections.
-    Intensity in arbitrary units (a.u.).  Middle: downstream spectrum with
-    absorbed power law fit; Si and S lines at $1.85$, $2.45 \unit{keV}$ are
-    clearly visible.  Right: upstream spectrum with absorbed power law fit
-    shows that each region is likely free of thermal line emission.}
+    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
+    rim morphology and example of rim where 0.7--1 keV peak could not be fit.
+    Left: $4.5$--$7 \unit{keV}$ profile with highlighted downstream (blue) and
+    upstream (grey) sections.  Intensity in arbitrary units (a.u.).  Middle:
+    downstream spectrum with absorbed power law fit; Si and S lines at $1.85$,
+    $2.45 \unit{keV}$ are clearly visible.  Right: upstream spectrum with
+    absorbed power law fit shows that each region is likely free of thermal
+    line
+emission.}
     \label{fig:spec}
@@
 
-We fit $0.5$--$7 \unit{keV}$ spectra from each region's upstream and downstream
-sections to an absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) with
-spectral index $n$, hydrogen column density $n_H$, and a normalization as free
-parameters.  Table~\ref{tab:spec} lists best fit parameters and reduced
-$\chi^2$ values for all regions.  Spectra from thin rims (upstream sections)
-are well-fit by the power law model alone; spectra from sections downstream of
-the rims are generally poorly-fit, reflecting thermal contamination primarily
-from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line emission at $1.85$ and $2.45$
-keV.  Although most downstream spectra show thermal contamination, some regions
-(e.g., 4, 5 on Tycho's northwestern limb) are reasonably well-fit downstream by
-an absorbed power law as well due to a larger distance between the forward
+We fit spectra from each region's upstream and downstream sections to an
+absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) between $0.5$--$7
+\unit{keV}$ with photon index $\Gamma$, hydrogen column density $N_{\mt{H}}$,
+and a normalization as free parameters.  Table~\ref{tab:spec} lists best fit
+parameters and reduced $\chi^2$ values for all regions.  Spectra from thin rims
+(upstream sections) are well-fit by the power law model alone; spectra from
+sections downstream of the rims are generally poorly-fit, reflecting thermal
+contamination primarily from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line
+emission at $1.85$ and $2.45$ keV.  Although most downstream spectra show
+thermal contamination, some regions (e.g., ?!?!, ?!?! on Tycho's northwestern limb)
+are reasonably well-fit downstream due to a larger gap between the forward
 shock and contact discontinuity.
-Upstream spectra fits spectral indices between $2.5$--$3$ are consistent with
-synchrotron radiation spectra for a steep power-law electron distribution
-\citep{vink2012}. Best fit column densities from
-upstream spectra between $0.61$--$0.78 \times 10^{22} \unit{cm^{-2}}$ are
-consistent with previous fits to Tycho's nonthermal rims \citep{hwang2002} but
-somewhat larger than $\abt0.35$--$0.5 \times 10^{22} \unit{cm^{-2}}$ from radio
-and optical??  HI absorption line measurements \citep{black1984, albinson1986,
-kothes2004}.
+Our best-fit photon indices ($2.4$--$3$) and column densities ($0.6$--$0.8
+\times 10^{22} \unit{cm^{-2}}$) from upstream spectra are consistent with
+previous spectral fits to Tycho's nonthermal rims \citep{hwang2002,
+cassam-chenai2007}.
 % NOTE keep stated ranges of spectral indices, column densities up to date
@@
 of thermal line emission, as already suggested by visual inspection
-(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2
-\unit{keV}$ photons should further limit any thermal contamination, as
-the $1.85 \unit{keV}$ Si line emission is over a third of Tycho's thermal flux
-as detected by \Chandra \citep{hwang2002}.  We may safely proceed to model our
-measured rim widths as being due entirely to nonthermal radiation
-\note[Aaron]{bad phrasing}.
+(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2 \unit{keV}$ photons
+further limits thermal contamination as $1.85 \unit{keV}$ Si line emission is
+over a third of Tycho's thermal flux as detected by \Chandra \citep{hwang2002}.
 
@@
 % NOTE keep mentioned number of regions updated!
-% Update these numbers before final version.
+% Check these (arcsec) numbers before final version.
 We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
-shock to $\abt 2$--$8\arcsec$ in front for each of our 13 regions in all five
-energy bands.  To increase signal-to-noise, we integrate along the shock ($\abt
-8$--$24\arcsec$) in each region.  Plotted and fitted profiles are reported in
-vignetting and exposure-corrected, but arbitrary, intensity units; error bars
-are computed from raw count data assuming Poisson statistics.  Intensity
-profiles peak sharply (within $\abt 2$--$3\arcsec$) behind the shock,
-demarcating our thin rims, and then fall off until thermal emission from ejecta
-picks up at Tycho's contact discontinuity \citep{warren2005}.
-
-We fitted rim profiles, obtained by integrating intensity along the shock in
-each region, to a piecewise two-exponential model:
+shock to $\abt 5$--$10\arcsec$ in front for each of our regions in all five
+energy bands.  To increase signal-to-noise, we integrate along the shock
+($5$--$23\arcsec$) in each region.  Plotted and fitted profiles are reported in
+vignetting and exposure-corrected intensity units; error bars are computed from
+raw counts assuming Poisson statistics.  Intensity profiles peak sharply
+within $\abt 2$--$3\arcsec$ behind the shock, demarcating our thin rims,
+then fall off gradually until thermal emission picks up further behind the
+shock.
+
+We fitted rim profiles to a piecewise two-exponential model:
 \begin{equation} \label{eq:prof}
@@
 where $h(x)$ is profile height and $x$ is radial distance from remnant center.
-The rim model, which we emphasize is strictly empirical, has 6 free parameters:
-$A_u, x_0, w_u, w_d, C_u$, and $C_d$ with $A_d = A_u + (C_u - C_d)$ enforcing
+The rim model, which is strictly empirical, has 6 free parameters:
+$A_u, x_0, w_u, w_d, C_u$, and $C_d$; $A_d = A_u + (C_u - C_d)$ enforces
 continuity at $x=x_0$. Our model is similar to that of \citet{bamba2003,
@@
 domain for each profile as follows.  The downstream bound was set at the first
-local data minimum downstream of the rim peak, as identified by smoothing the
+local data minimum downstream of the rim peak, identified by smoothing the
 profiles with a 21-point ($\abt 10\arcsec$) Hanning window.  The upstream bound
@@
 
-% NOTE keep blacklisted/excluded region numbers updated!
+% NOTE keep blacklisted/excluded region count updated!
 From the fitted profiles we extracted a full width at half maximum (FWHM) for
-each region and each energy band.  We could not resolve a FWHM in 7 of 22
-regions at 0.7--1 keV (Table~\ref{tab:fwhms}); in these regions, either
-the downstream FWHM bound would extend outside the fit domain or we could not
-find an acceptable fit to equation~\eqref{eq:prof}.  We were able to resolve
-FWHMs for all regions at higher energy bands (1--7 keV).
+each region and each energy band after subtracting a constant background term
+$\min(C_u, C_d)$.  We could not resolve a FWHM in 4 of 20 regions at 0.7--1 keV
+(Table~\ref{tab:fwhms}); in these regions, either the downstream FWHM bound
+would extend outside the fit domain or we could not find an acceptable fit to
+equation~\eqref{eq:prof}.  We were able to resolve FWHMs for all regions at
+higher energy bands (1--7 keV).
 % NOTE review the FWHM rejection criterion, on the final set of regions
+% We will be blacklisting by hand, and we have to explain how we chose the
+% blacklisted ones.
 
@@
 and the stretched or compressed FWHMs as upper/lower bounds on our reported
-FWHMs. \note[Aaron]{Unimportant note: chi-squared values from our
-fits assume that input errors are 1-sigma.  But, taking $\Delta\chi^2 = 1$
-for our FWHM errors would shrink the errors even further, and the errors
-don't reflect uncertainty that may arise from, e.g., using different fit
-functions or taking different profiles.}
+FWHMs.
 
@@
 \eqref{eq:full-mod} to our measured rim widths as a function of energy.
-We assigned each width measurement to the lower energy limit of its energy band
-(e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
-model profile widths at $0.7 \unit{keV}$) \note[Aaron]{bad wording}.
-We also averaged the positive and negative error bars on each FWHM measurement
-(Table~\ref{tab:fwhms}) for least squares fitting.
-% Averaging/merging/synthesizing, somehow, our results
-Rim widths from each region are fitted separately; we consider filament and
-remnant-wide physical parameters by averaging best fit parameters for each
-region in Section~\ref{sec:fit-results}.
+We mapped each width measurement to the lower energy limit of its energy band;
+e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
+model profile widths at $0.7 \unit{keV}$.  Errors in least squares fits
+average the positive and negative errors on each FWHM measurement.
 
 % Model knobs and how we twiddled them
-We varied three physical parameters (more if we consider magnetic damping):
+We varied three physical parameters (more if we consider magnetic damping fits
+explicitly):
 diffusion-energy scaling exponent $\mu$, normalized diffusion
@@
 recall that $\mu = 1/3$ and $1/2$ correspond to Kolmogorov and Kraichnan turbulence.
-As $\eta_2$ is highly variable in our fits, we also performed
-fits with $\eta_2 = 1$ fixed, coincident with Bohm diffusion at $2 \unit{keV}$.
-
-A few remnant-specific parameters enter into the model calculations.  We take
-electron spectral index $s = 2.3$ (from radio spectral index $\alpha = 0.65$,
-\citet{kothes2006} \note[Aaron]{not using $0.58$ from Green's catalog?!}),
+
+% Tycho parameters
+A few remnant-specific parameters enter into the model calculations.  We
+adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha = 0.65$
+\note[Aaron]{will change to $s= 2.16$ from $\alpha=0.58$ following
+\citet{sun2011} on next iteration}
+\citep{kothes2006},
 remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
@@
 to estimate individual shock velocities for each region.
-\note[Aaron]{this paragraph might belong in an earlier section?}
 
@@
 Equation~\eqref{eq:simp-fwhm} was directly fit to our measurements to obtain
-best-fit values of $\eta_2$ and $B_0$.
-The full model was numerically computed as detailed in
-Section~\ref{sec:transport}, yielding intensity profiles and hence model FWHMs
-in each energy band; we then varied the input parameters ($\eta_2$, $B_0$) to
-obtain a least squares best fit.
-To assist the nonlinear fitting, we tabulated a large grid of model FWHM values
-for various values of $\mu$ and shock velocity $v_s$; from a best initial grid
-value, we then used a Levenberg-Marquardt fitting routine to determine the best
-fits.
-For both simple and full fits, we deemed fits with $\eta_2 \geq 10^5$ and $B_0
-\geq 10 \unit{mG}$ effectively unconstrained; $\eta_2$ is also constrained to
-be positive.
-
-% TODO modify tables to match what is stated here -- in regards to parameters
-% being effectively unbounded.
-% TODO for extreme values in tables -- go back and double check chi^2 space
-As the full model must be numerically solved, its predicted rim widths are
-subject to resolution error in the numerical integrals.  We chose our
-integration resolutions such that the fractional error in model FWHMs
-associated with halving/doubling integration resolution is less than $1\%$ for
-the parameter space relevant to our filaments.
-\note[Aaron]{rewrite -- unclear.  Need to verify 1\% claim and check Pacholczyk
-table resolution (and possibly Bessel function numbers)...}
-
-% Errors
-Finally, we computed errors on our best fit parameters by varying each
+best-fit values of $\eta_2$ and $B_0$.  The full model was numerically computed
+as detailed in Section~\ref{sec:transport}, yielding intensity profiles and
+hence model FWHMs in each energy band.  To assist the nonlinear
+fitting, we tabulated a large grid of model FWHM values for various values of
+$\mu$, $\eta_2$, $B_0$, and shock velocity $v_s$.  From a best initial grid
+value, we used a Levenberg-Marquardt fitting routine to determine the best
+fits.  Errors on best fit parameters were computed by varying each fit
 parameter and obtaining a new best fit model, with one less degree of freedom,
@@
 1-$\sigma$ error.
+
+We required $\eta_2$ to be positive in all fits.  We also deemed
+best-fit and error bound values with $\eta_2 \geq 10^5$ and $B_0 \geq 10
+\unit{mG}$ to be effectively unconstrained. % Change this if needed.
+
+% TODO Come back after checking Pacholczyk resolution
+As the full model must be numerically solved, its predicted rim widths are
+subject to resolution error in the numerical integrals (discretization over
+radial coordinate, line-of-sight coordinate, electron distribution, Green's
+function integrals).  We chose our integration resolutions such that the
+fractional error in model FWHMs associated with halving/doubling integration
+resolution is less than $1\%$ for the parameter space relevant to our
+filaments.
 
@@
 
-In Table~\ref{tab:fwhms} we report FWHM measurements for all of our regions.
-As previously noted, we could not resolve FWHMs for some regions in the 0.7--1
-keV band.  We also report $\mE$ values for all but the lowest energy band,
-computed point-to-point as: \begin{equation} \mE(E_2) =
-\frac{\ln(w_2/w_1)}{\ln(E_2/E_1)} \end{equation} where $w_1, w_2$ and $E_1,
-E_2$ are FWHMs and lower energy values for each energy band (e.g., $\mE$ at $1
-\unit{keV}$ is computed using FWHMs from $0.7$--$1 \unit{keV}$ and $1$--$1.7
-\unit{keV}$, and taking $E_2 = 1 \unit{keV}$ and $E_1 = 0.7 \unit{keV}$.
-Although the values of $\mE$ reflect a good deal of variability in the
-underlying width measurements, we see that most regions and energy bands
-display a decrease in rim widths as a function of energy.  NOTE (draft): we
-emphasize that $\mE$ is currently not considered or utilized in our subsequent
-analysis.
+Table~\ref{tab:fwhms} reports FWHM measurements for all of our regions.
+We also report $\mE$ values for all but the lowest energy band, computed
+point-to-point between discrete energy bands as:
+\begin{equation}
+    \mE(E_2) = \frac{\ln(w_2/w_1)}{\ln(E_2/E_1)}
+\end{equation}
+where $w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each
+energy band (e.g., $\mE$ at $1 \unit{keV}$ is computed using FWHMs from
+$0.7$--$1 \unit{keV}$ and $1$--$1.7 \unit{keV}$, with $E_2 = 1
+\unit{keV}$ and $E_1 = 0.7 \unit{keV}$.  Errors on $\mE$ are propagated in
+quadrature from adjacent FWHM measurements.
 
 \begin{table*}[ht]
-    \tiny
+    \scriptsize
     \centering
-    \caption{Measured FWHMs for all regions.\label{tab:fwhms}}
+    \caption{Measured full widths at half max (FWHMs) for all regions.
+             \label{tab:fwhms}}
     \input{tab-fwhms.tex}
 \end{table*}
+
+Measured rim widths decrease with energy in most regions and energy bands.
+Although the measurement variation between measurements is quite large, shown
+dramatically in the point-wise computed $\mE$ values, the mean rim width
+decreases consistently with increasing energy.  Furthermore, mean $\mE$ values
+are consistently negative and tend smoothly towards $0$ (weaker
+energy-dependence) with increasing energy.
+
+The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
+reflecting the high quality of underlying \Chandra data as also seen in
+Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
+part to (1) our profile fitting procedure, which depends on an empirically
+chosen profile fit function which may also fit the rims non-uniquely, and (2)
+variation in Tycho's rim morphology, also demonstrated clearly in
+comparison of rims from Regions 1 and 16 in Figure~\ref{fig:profiles}.
+\note[Aaron]{review paragraph wording}
 
@@
 
-% NOTE keep updated -- for which region are we giving simple and full fits?
-We find that the simpler catastrophic dump model (equation~\eqref{eq:simp-mod})
-produces the same qualitative trends seen in the full continuous energy loss
-model.  The first row of Table~\ref{tab:fits} compares simple and full model
-fits for Region 1 \note[Aaron]{data coming soon}.  In general, simple model
-fits are less poorly constrained (i.e., fits are more likely to reach manual
-fitting limits).  Where both simple and full model fits are well constrained
-(i.e., moderate to small $\eta_2$ values), the simple model favors slightly
-smaller $\eta_2$ and slightly larger $B_0$.  But this is not always true, and
-it is difficult to identify any obvious trends as both fits are quite variable
-across $\mu$ values and different regions.  \note[Aaron]{from the table
-calculations, the simple model needed larger $B_0$ values than the full model
-for a fixed $\eta_2$ and mean width (roughly speaking); this effect
-strengthened with larger $\eta_2$.  We're looking at order 10--50\% effects}.
-For the rest of our results and discussion, we consider only full model fits.
-
-% Individual region fit results
-Table~\ref{tab:fits} presents full model fit results for all regions
-considered. Errors are computed by varying free parameters $B_0$,
-$\eta_2$ to obtain $\Delta\chi^2 = 1$, corresponding to $1$-$\sigma$ confidence
-limits on our fit parameters.
-%In Figure~\ref{fig:fits-all} we also plot the best full model fits for the same
-%regions tabulated in Table~\ref{tab:fits}
-
 \begin{table*}[ht]
@@
     \centering
-    \caption{Full model best fits for individual regions, Filaments 1--3.
+    \caption{Full model best fit for individual regions, Filaments 1--2.
     \label{tab:fits}}
@@
     \centering
-    \caption{Full model best fits for individual regions, Filaments 4--5.
+    \caption{Full model best fits for individual regions, Filaments 3--5.
     \label{tab:fits-pt2}}
@@
 
-% Individual region fits with eta2=1 fixed
-%We also computed best fits while holding $\eta_2 = 1$; i.e., requiring Bohm
-%diffusion at $2 \unit{keV}$.  We found that the best fit $B_0$ is relatively
-%insensitive to $\mu$; for all regions, $B_0$ varies by no more than XXX ($\abt
-%10$)\% from the value at $\mu = 1$ (with larger $B_0$ at smaller $\mu$ and vice
-%versa).  \note[Aaron]{compute/verify this}.  Therefore, we show only best fits
-%with $\mu = 1$ and $\eta_2 = 1$ fixed in Table~\ref{tab:fits-avg-eta2-fix}).
-%\note[Aaron]{this should be computed just for Region 1, or something similar?}
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Best fits with $\eta_2 = 1$ fixed for filament averaged FWHMs.
-%    \label{tab:fits-avg-eta2-fix}}
-%    \input{tab-fits-avg-eta2-fix.tex}
-%\end{table*}
+% Individual region fit results
+% NOTE keep updated -- for which region are we giving simple and full fits?
+Table~\ref{tab:fits} presents full model fit results for all regions
+considered.  The first row of Table~\ref{tab:fits} includes both simple and
+full model fits for Region 1 for comparison.
+We found that fits to the simpler catastrophic dump model
+(equation~\eqref{eq:simp-mod}) reproduced qualitative trends seen in the full
+continuous energy loss model, as expected.  In general, simple model fits
+yielded slightly smaller $\eta_2$ and/or slightly larger $B_0$ values; this is
+consistent with the expectation that electrons travel farther in the simple
+model than in the full model, since electrons are not subjected to continuous
+synchrotron cooling, so smaller $\eta_2$ and larger $B_0$ values are needed to
+generate thinner rim widths as compared to the full model.  Simple model fits
+were also more likely to reach manual fitting limits (i.e., allow for
+unconstrained parameter values) than full model fits.
+
+For the rest of our results and discussion, we consider only full model
+fit results in Tycho for simplicity.  We do reference the simple model to build
+intuition and give scaling relations, as was done in depth by
+\citet{parizot2006} and \citetalias{ressler2014}.
 
@@
 reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
-of the mean \note[Aaron]{may need to scale by $\abt 2 \times$ to get 1-sigma
-confidence interval since our sample sizes are so small}.  We note that both
-averages and errors are strongly affected by outliers from extreme best fit
-values, as can be seen in Tables~\ref{tab:fits} and \ref{tab:fits-pt2} --
-especially as the typical number of regions per filament is quite small.
+of the mean.  The averaged parameters and corresponding errors are strongly
+affected by outliers from extreme best fit values, as can be seen in
+Tables~\ref{tab:fits} and \ref{tab:fits-pt2} -- especially as the typical
+number of regions per filament is quite small.  We also averaged best fit
+parameters from all regions in the remnant, but the presence of outliers
+renders the averages relatively unusable.
+% TODO
+\note[Aaron]{we could also report one fit to the global FWHM averages, as was
+done by Sean?}
 
@@
 
-% Global fits...
-Extras: we could report a global average of best fit parameters from all
-regions, or a fit to the global FWHM average.
-Plot of best fit parameters with $\mu=1$ as a function of azimuth angle, with
-error bars or something similar?
+% ==========
+% Discussion
+% ==========
+\section{Discussion}
+
+\subsection{Energy dependence rules out magnetic damping for X-ray rims}
+
+% Linchpin of argument -- energy dependence at ~1 keV incompatible with damping
+% NOTE keep numbers up to date
+Our observations of strong energy-dependence, particularly at low energies
+(0.7--1 keV, 1--1.7 keV, 2--3 keV), are incompatible with magnetic damping as a
+primary control on filament widths.
+Our mean $\mE$ values with errors favor $|\mE| \gtrsim 0.25$ at $\abt 1
+\unit{keV}$, and $|\mE| \gtrsim 0.19$ at $\abt 2 \unit{keV}$.
+\note[Aaron]{calculations on magnetic damping $\mE$ go here}  % TODO FILL IN
+\citetalias{ressler2014} also argued that magnetic damping generally requires
+$|\mE| \sim 0.1$.  If thin rims are not magnetically damped at our lowest
+energy bands, the rims will not be damped at any higher energies (barring
+extreme $\mu>1$ diffusion with $\mE > 0$ that yields wider rims at higher
+energies -- and indeed that is further disfavored by the electron energy
+cut-off, as well as the fact that diffusion only begins to outpace advection
+around the same cut-off).  Our result should hold for all photon energies above
+$\abt 1 \unit{keV}$.
+
+% More quantification -- give scale lengths, field strength values.
+How robust is this result, give quantitative results.
+What is the smallest damping scale length that is (roughly) consistent with all
+of our observations?
+\note[Aaron]{See Sean's section 3.2.1 and appendix for explication of the
+magnetic damping disfavoring etc.}
+
+% Address the broader trend in mE
+The observed decrease in $|\mE|$ with increasing energy is attributable to
+diffusion, which weakens width-energy dependence at higher energies
+(even if diffusion is energy-independent with $\mu = 0$)
+\citepalias[see][Figure 5]{ressler2014}.
+\note[Aaron]{material on width scaling w/ $B_0$ and $\eta_2$. I'm not sure
+where this should go, exactly.  May be better in the next section.
+Or, this may even go in the beginning of the text, after or before introducing
+transport models?!}
+To make this more quantitative, note the scaling relations:
+\begin{equation}
+    l_{\mt{ad}} \propto v_d B_0^{-3/2} \nu^{-1/2}
+\end{equation}
+and
+\begin{equation}
+    l_{\mt{diff}} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
+\end{equation}
+As previously claimed, where advection dominates we expect $w \sim l_{\mt{ad}}
+\sim \nu^{-1/2}$.  Where diffusion and advection are comparable, we expect
+$|\mE|$ to decrease, i.e. yielding weaker energy dependence.
+\citetalias{ressler2014} give a full discussion of the relative effects of
+advection and diffusion, as well as the effect of $\Ecut$ in counterbalancing
+the effects of diffusion at higher energies; see in particular Figures 3 and 5
+of \citetalias{ressler2014}.  \note[Aaron]{might have been discussed earlier?}
+The increasing importance of diffusion at X-ray energies matches the
+synchrotron spectrum roll-off at X-ray energies as compared to radio
+observations; the criterion for synchrotron roll-off, or electron cut-off, is
+equivalent to requiring that advective and diffusive lengthscales are
+comparable.  Thus, a weakening energy dependence in X-rays is consistent with
+prior work and a welcome observation!
+\note[Aaron]{I think this is a nice result of its own, unless it's a bit
+obvious?  Importantly, the spectral roll-off observation is derived from the
+intensity of Tycho -- how much flux comes out of the rims.  But we look at the
+widths, disregarding intensity, and find a consistent result.}
+
+% Addressing the variability in width measurements
+The large variation in filament widths, and point-wise computed $\mE$ values,
+does make our claim a little shakier.  Indeed, in Region 3 we see
+\emph{increases} in filament width between multiple energy bands.
+But we have confidence on our averaged results.
+\note[Aaron]{We could also compute $\mE$ numerically from the model fit
+profiles -- basically mimicking Sean's Figures 1, 5, 6, but generating $\mE$
+numbers that effectively reflect the broad energy drop-off (or, lack thereof)
+from all measured widths.}
+
+\subsection{Model parameters: constraining magnetic fields and diffusion}
+
+We now turn to our model fit parameters, magnetic field strength and diffusion
+coefficient.
+
+%WHERE to place the width - magnetic field dependence.  Cite Parizot's paper on
+%this result, mention Sean's paper for symbols/set-up similar to our work.
+%---> BRIAN reminded me, he wanted to talk about REMNANT DISTANCE. RIGHT.
+%Throw this text in here, to discuss mE.
+%Then we backreference this equation and simply say, the physical width scales
+%linearly with the remnant distance.  The ONLY confounding factor is that shock
+%velocity changes as well. -- SO, I need to add in NUMBERS!!!!!
+
+% 1-2 paragraphs on this
+Eta2 is poorly constrained.  Explain why -- we have a strong degeneracy between
+magnetic field and eta2, especially at low mu.  Mention the sensitivity
+results.
+It is important to note that this is a limitation of our fitting model, not of
+the data.  Stacking the data, e.g. by taking larger regions or averaging FWHM
+measurements, does NOT help.
+
+But, we note that our model fits generally favor $\eta_2 > 1$ -- the lowest
+error bound on $\eta_2$ is ????. % TODO.
+
+Magnetic field $B_0$: despite the large range of fit quality, we can give
+fairly robust lower bounds.  Lowest bound is ????  Consistent with previous
+studies, Tycho requires strong magnetic field amplification -- up to ??? times
+the expected value of $\abt 10 \unit{\mu G}$ from a strong shock with
+compression ratio $r=4$ and typical galactic magnetic field strength of $\abt
+2$--$3 \unit{\mu G}$ \citep{lyne1989, han2006}.
+
+A few ways to touch this -- can we back out information from the synchrotron
+roll-off and hence $\Ecut$, to obtain diffusion coefficient independently of
+$B_0$?  Then we have a single parameter fit.
+
+We could report estimates of cut-off energy?  I don't know if that is
+helpful/meaningful for anything, unless we can tie it back to something in DSA.
+
+Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
 
@@
 
-% ==========
-% Discussion
-% ==========
-\section{Discussion}
-
-\subsection{How confidently can we reject B-damping?}
-
-Everything hinges on our error bars -- this is most important.  Our rims do
-thin consistently, in most regions (might be one or two places where they
-don't), but (1) the errors in our individual FWHMs are larger than I'm
-currently reporting because different profile fits will give a larger spread of
-FWHMs (might need to consider reduced chi-squared here, but using chi-sqr to
-select profile fit models is not physically meaningful)
-
-It might be helpful to average $\mE$ values together, under the
-assumption that they should be somewhat consistent within a given filament.
-Then report the values and errors observed.  Again, needs more data points.
-
-Recall that our FWHMs (Table~\ref{tab:fwhms}) have a large range of values,
-IF magnetic damping is relevant in controlling filament widths, we might, e.g.,
-expect a maximum filament width at which $\mE$ sharply levels off, being now
-restricted by the magnetic field turn off.  We simply do not observe this in
-our data between $0.7$--$7 \unit{keV}$.  We must conclude that, as in SN 1006
-\citepalias{ressler2014}, magnetic damping cannot be relevant to our
-observations.
-
-What is the smallest damping scale length that is (roughly) consistent with all
-of our observations?
-
-X-ray rims are not damped -- could damping be relevant to the radio rims?
-
-\subsection{Interpretation of fit parameters}
-
-Magnetic field $B_0$: despite the large range of fit quality, we can give
-fairly robust lower bounds.  Lowest bound (TBD)?  Consistent with previous
-studies, Tycho requires strong magnetic field amplification -- up to ??? times
-the expected value of $\abt 10 \unit{\mu G}$ from a strong adiabatic shock with
-compression ratio $r=4$ and typical galactic magnetic field strength of $\abt
-2$--$3 \unit{\mu G}$ \citep{lyne1989, han2006}.
-
-Brief (possibly obvious) remark: these estimates of magnetic fields should be
-lower bounds, if we neglect diffusion (and compression ratio/etc...).
-A spherical projection is the narrowest filament we can get.
-Any rippling effects, etc... hmm.  Rippling could strengthen the filament,
-making it look at little thinner actually.  But we don't know how big an effect
-that could be.  And we are looking at a tangential slice.  There is some room
-for ripples/waveforms to accumulate, of course... we see them elsewhere, we do
-see distinct filaments stacking.
-
-(maybe something useful / fun to do: what's the projection factor for a rippled
-sphere?  Estimating some wavelength from observed stripes, ripple
-lengthscale from width of filaments viewed face on (e.g. in Kepler).  Likely,
-not gonna make much difference.  But could be helpful to have an idea of how
-good/bad this assumption of a spherical shell is, and how much effect that has
-on our magnetic field estimates)
-
-Diffusion coefficient $\eta_2$, on the other hand, is a bit of a mess.
-Would it be useful to report advective and diffusive lengthscales at 2 keV?
-Idea being that it is hard to intuit what the large numbers even mean.
-(especially for the simple model -- it sits on a plateau in chi-squared space
-where small $\eta_2$ may be disfavored, but beyond a certain point any $\eta_2$
-will do)
-
-Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
-
-We could report estimates of cut-off energy?  I don't know if that is
-helpful/meaningful for anything, unless we can tie it back to something in DSA.
-
-\subsection{Bohm diffusion}
-
-Fixing $\mu = 1$ and $\eta_2 = 1$ in Table~\ref{tab:fits-avg} is equivalent to
-assuming Bohm diffusion, as most previous studies have done.
-We should find/show that our result is very similar to theirs, in terms of
-$B_0$ estimates, and this may be the easiest way to back out any estimates of
-azimuthal magnetic field variation.
-
-Magnetic field amplification numbers -- how do they compare with previous
-studies?  What is the azimuthal variation (and significance thereof)?
-
-Diffusion -- sub-Bohm diffusion in Filament 4?
+\subsection{Uncertainties what not trash heap}
+
+% discussion of uncertainties/caveats in our results
+Our FWHM measurements have a good deal of scatter.
+One possible concern is our fitting function, which may overshoot or undershoot
+our profiles, or simply fail to fit profiles that are not well-described as
+having exponential fall-offs.
+.. One way to address this is to consider other functions -- for example, a
+gently smoothed spline fit, a manually capped two-exponential function, a
+Gaussian sitting on a ramp or logistic curve, etc.
+Explain that nothing happens -- not much (but I will reaffirm this).
+.. another is simply our sampling -- we have already sought to circumvent this
+by taking multiple regions in each filament, as many as possible without overly
+compromising the quality of our radial profiles
 
@@
 
+% Summarize our results
 Our observations of filament thinning, although qualitative, are consistent
@@
 
+% Further work -- radio
+BROAD QUESTION -- Why couldn't we answer this from radio measurements?
+Rims are splattered/lost in emission from within the remnant, looking at
+\citet{cassam-chenai2007}.
+Are the rims from shock accelerated electrons, simply swamped/drowned by
+turbulence/synchrotron/bremsstrahlung in the interior? (seems that
+bremsstrahlung is unimportant at very low frequencies...)
+
+VLA data from Brian/Jack Hewitt, + Chandra X-ray data, coming November!
+They have lots of fun things to look at -- proper motion (main thing),
+polarization, etc.  Can take a look at the radio rims too and see what's up...
+
+% Further work -- other SNRs
 We will follow up with an analysis of Kepler's supernova remnant and
@@
 
+Ask a theorist: if we find a pretty global behavior, that damping is disfavored
+in all remnants -- what does that tell us about the damping?  Why
+\emph{shouldn't} damping occur on small lengthscales?
+
 % ================
@@
 
+A.T. thanks CRESST for support.
+B.J.W. NPP?
 The scientific results reported in this article are based on data obtained from
@@
 %\renewcommand{\thefigure}{A\arabic{figure}}
-%
-%% ---------------------------
-%% FWHM measurement comparison
-%% ---------------------------
-%\section{Additional calculations}
-%
-%Here I present full model fit results using FWHMs measured with an artificial
-%cap imposed on the profile height, and the background $\min(C_u, C_d)$
-%subtracted out before computing the FWHM.  The fitted profile may extend above
-%the data maximum, but I find the full-width at one half of the data maximum.
-%The results appear equivocal; there may be slightly smaller chi-squared values
-%but it may not be statistically meaningful.
-%
-%I also present results for simple model fits, and fits for a larger set of
-%regions (22 instead of 13).
-%
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Measured FWHMs for all regions, capped and background subtracted.}
-%    \input{tab-fwhms-capsubbkg.tex}
-%\end{table*}
-%
-%\begin{table}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fits for individual regions, Filament 1.  Capped
-%    and background subtracted FWHMs.}
-%    \input{tab-fits-all-capsubbkg.tex}
-%\end{table}
-%
-%\begin{table}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fits for individual regions, Filaments 2--5.
-%    Capped and background subtracted FWHMs.}
-%    \input{tab-fits-all-capsubbkg-pt2.tex}
-%\end{table}
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Filament averages of best-fit parameters for constituent regions.
-%    Capped and background subtracted FWHMs.}
-%    \input{tab-fits-par-avg-capsubbkg.tex}
-%\end{table*}
-%
-%\begin{figure}[ht]
-%    \centering
-%    %\epsscale{0.45}
-%    \plottwo{figures/fits-sep19-capsubbkg/reg01.png}{figures/fits-sep19-capsubbkg/reg02.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg03.png}{figures/fits-sep19-capsubbkg/reg04.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg05.png}{figures/fits-sep19-capsubbkg/reg06.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg07.png}{figures/fits-sep19-capsubbkg/reg08.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg09.png}{figures/fits-sep19-capsubbkg/reg10.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg11.png}{figures/fits-sep19-capsubbkg/reg12.png} \\
-%    \plottwo{figures/fits-sep19-capsubbkg/reg13.png}{figures/f0-box.png}
-%    \caption{Fitted full model widths as a function of energy for all regions,
-%    with measured data; best fit parameters are given in
-%    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
-%    number.}
-%\end{figure}
-%
-%\begin{table}[ht]
-%    \tiny
-%    \centering
-%    \caption{Simple model best fits for individual regions, Filaments 1 and 2.
-%    Same FWHM as in main text.}
-%    \input{tab-fits-all-simp.tex}
-%\end{table}
-%
-%\begin{table}[ht]
-%    \tiny
-%    \centering
-%    \caption{Simple model best fits for individual regions, Filaments 3--5.
-%    Same FWHM as in main text.}
-%    \input{tab-fits-all-simp-pt2.tex}
-%\end{table}
-
-% -------------
-% Region 5 data
-% -------------
-
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Measured FWHMs for all regions (22).}
-%    \input{tab-fwhms-reg5.tex}
-%\end{table*}
-%
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fits for smaller regions, filaments 1--3.  Same
-%    FWHM as in main text.}
-%    \input{tab-fits-all-reg5.tex}
-%\end{table*}
-%
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fits for smaller regions, filaments 4--5.  Same
-%    FWHM as in main text.}
-%    \input{tab-fits-all-reg5-pt2.tex}
-%\end{table*}
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Filament averages of best-fit parameters for constituent regions,
-%    with 22 instead of 13 regions.}
-%    \input{tab-fits-par-avg-reg5.tex}
-%\end{table*}
-%
-%\begin{figure*}
-%    \centering
-%    \epsscale{0.7}
-%    \plotone{figures/f0-snr-reg5-inv.png}
-%    \caption{RGB image of Tycho with region selections overlaid.  Bands are
-%    0.7--1 keV (red), 1--2 keV (green) and 2--7 keV (blue).}
-%\end{figure*}
 
@@
 
+%\end{CJK}
 \end{document}

### 2014-10-02 code/spectra/spec_clearbg.py

@@ -34,7 +34,7 @@ def main():
 
     # Get number of spectra to update (count ungrouped spectrum files)
     pattern = os.path.basename(specroot) + r'_src[0-9]+\.pi'
-    files = [f for f in os.listdir(os.path.dirname(specroot))
+    files = [f for f in os.listdir(os.path.dirname(os.path.abspath(specroot)))
              if re.match(pattern, f)]
     print '{} files will be modified'.format(len(files)*2)
 
@@ -52,7 +52,7 @@ def set_bkg(num, rt, verbose=False):
     """Execute CIAO dmhedit to link spectra to backgrounds
     Check that specified root points to actual files
     (but I don't check that they are FITS files with spectra)
-    
+
     Be careful -- this method modifies files
     (i.e., there is risk of data loss!)
     """

### 2014-10-04 manuscript/paper-tycho.tex
Start B-damping port; paper discussion
Clean up B-damping model + identify differences to port
Flesh out results, discussion, conclusion

@@
 
+\defcitealias{ressler2014}{R14}
 \newcommand*{\Chandra}{\textit{Chandra}\ }
@@
 \newcommand*{\Ecut}{E_{\mt{cut}}}
-\defcitealias{ressler2014}{R14}
+\newcommand*{\muG}{\unit{\mu G}}
 
@@
 electron transport models requiring amplified magnetic fields of
-$\abt200$--$1000 \unit{\mu G}$ and particle diffusion coefficients $\abt
+$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
 1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
@@
 jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
-even cosmological shocks \citep{miniati2000, ryu2008}.
+even cosmological shocks \citep{ryu2008}.
 % Expand on these questions -- plasma turbulence, Alfven waves, wave damping
@@
 enough that its rims are easily resolved by \textit{Chandra} spatial
-resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from an
-archived \Chandra large project (PI: J. Hughes) also allows us to sample the
-remnant rims quite finely.  Furthermore, Tycho has been a prime target of study
-for determining whether hadrons are being accelerated in historic SNRs
-\citep[and references therein]{morlino2012}; understanding the acceleration
-process will bear upon our understanding of CR acceleration in Tycho.
-\note[Aaron]{reword/cut?}
+resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
+(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
+Furthermore, Tycho has been a prime target of study for determining whether
+hadrons are being accelerated in historic SNRs \citep[and references
+therein]{morlino2012}; understanding the acceleration process will also bear
+upon our understanding of CR acceleration in Tycho.
+\note[Aaron]{can reword/cut?}
 
@@
 
-\note[Aaron]{I am a bit uncertain on the structure/order of presentation here,
-particularly in presenting $\Ecut$ (which can be an independent observable?
-but is not considered here).  I tried to put ``enough'' to independently
-follow / re-derive all the model results.}
-% TODO Chunk of text I don't know what to do with...
-We consider two models for particle transport to our measurements of Tycho's
-filament widths.  To best quantify width-energy dependence, we measure rim full
-widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
-measurements to these models' predictions of rim FWHMs at multiple photon
-energies.  \citetalias{ressler2014} give a fuller review of previous approaches
-to characterizing filament widths, as well as a more thorough exposition of
-model parameters and physical implications.
-
-We use CGS (Gaussian) units throughout.
-
-Any other introductory text -- emphasize that we back out two parameters,
-possibly three or more.  COME BACK after writing magnetic damping bit.
+We consider two particle transport models that we fit to measurements of
+Tycho's thin rim widths.  We measure the rim full widths at half maximum
+(FWHMs) (Section~\ref{sec:fwhms}) and use the measurements to directly assess
+width-energy dependence.  The measurements are also fit to the transport
+models' predictions of rim FWHMs at multiple photon energies.  The models
+accept three free parameters: magnetic field strength $B_0$, a scaled diffusion
+coefficient $\eta_2$, and a diffusion-energy scaling exponent $\mu$.
+
+We use CGS (Gaussian) units throughout.  Our presentation is somewhat
+abbreviated; please refer to \citetalias{ressler2014} for a fuller review and
+exposition of the transport models and relevant parameters' effect on rim
+widths.
 
@@
 % TODO Choose names for these models and refer to them consistently, throughout
-% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
-%      notation is being used)
-% TODO double check equations, exposition against Rettig/Pohl and others
-% TODO review variable definitions when closer to final draft
+% TODO define ALL symbols, synchrotron constants, etc
 \note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
 tack in deriving the relevant transport equations, drawing specifically from
-plasma physics / DSA assumptions -- I suppose much material is not relevant or
-condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
-Is na\"ively citing generalized ``transport'' is sufficient here?
+plasma physics / DSA assumptions -- I suppose that much material is not
+relevant or condensed into our diffusion coefficient $D$ (w/ stated Bohm
+diffusion).  Is na\"ively citing generalized ``transport'' is sufficient here?
 E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
@@
 
-% Moving on...
-In what follows we consider both transport models, but primarily present
-results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
-that the qualitative behavior of both models is comparable.
-
 % Diffusion
@@
 
-Much previous work has assumed Bohm-like diffusion in plasma downstream of the
-shock.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
+% Bohm, Bohm-like, and MHD/turbulence-inspired diffusion
+Much previous work has assumed Bohm-like diffusion in plasma downstream of SNR
+shocks.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
 equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
@@
 all energies.
-\note[Aaron]{for self-edification, any justification / derivation of this
-result?  All the papers seem to take it for granted}
-However, different types of MHD turbulence may give rise to a non-linear energy
+\note[Aaron]{for self-edification, any justification / derivation of Bohm
+limit?  All the papers seem to take it for granted}
+Different types of MHD turbulence may give rise to a non-linear energy
 scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
@@
 
+% Define our diffusion coefficient, introduce fiducial energy
 In our models, we consider a generalized diffusion coefficient with arbitrary
@@
 \end{equation}
-where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has unites
+where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
 of $\mathrm{erg}^{1-\mu}$.
-The right-hand side of equation~\eqref{eq:diffcoeff} introduces a dimensionless
-$\eta_h$ as the diffusion coefficient scaled to the Bohm value at a fiducial
-particle energy $E_h$.  We subsequently choose the fiducial electron energy
-$E_h$ corresponding to a synchrotron photon energy of $2 \unit{keV}$, taking
-the $\delta$-function approximation that an electron of energy $E$ radiates
-solely at frequency $\nu \propto E^2 B$ in a surrounding magnetic field.  Then,
-$E_h \propto \sqrt{2 \unit{keV} / B}$.  Although the value of $E_h$ depends on
-magnetic field $B$, tying $\eta_h$ to a fixed observation energy gives a
-convenient and intuitive sense of diffusion strength regardless of the
-electron energies producing observed rims.
-\note[Aaron]{what I want to say: electron energies responsible for the rims we
-see could vary between remnants or even within a single remnant.  And, we
-cannot get a handle on diffusion at a singular electron energy or energy range,
-in all our observations.  So it's simpler to tie $\eta_h$ to observation
-energy.}
-
+The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
+dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
+particle energy $E_h$.  This energy $E_h$ may be related to the emitted
+synchrotron photons by taking the $\delta$-function approximation that an
+electron of energy $E$ radiates at a singular frequency $\nu \propto E^2 B$ in
+a magnetic field.  Note that $\eta_h$ and $\eta$ are related as
+$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
+($\mu = 1$).
+
+% Set choice of fiducial energy, eta_2
+For subsequent analysis and model fitting, we take fiducial electron energy
+$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
+model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
+depends on magnetic field $B$ and may vary within the remnant, tying $\eta_h$
+to a fixed observation energy gives a convenient and intuitive sense of
+diffusion strength regardless of the underlying electron energies.
+We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.
+
+\subsection{Electron cut-off}
+
+% Electron cut-off energy
 With a diffusion coefficient in hand, we determine the electron spectrum
@@
         &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
-        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \nonumber \\
+        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
         &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
@@
 downstream; see \citet{parizot2006} for a full derivation.
+
+As the electron cut-off imposes a roll-off on SNR synchrotron flux,
+estimates of the synchrotron roll-off frequency may provide an independent
+observable to characterize shock conditions.
+\note[Aaron]{todo: explore this?} % TODO FILL IN LATER -- NOT IMPORTANT NOW
+\citet{miceli2013, yamazaki2014} looked at the synchrotron roll-off as a
+diagnostic for electron spectrum cut-off behavior (whether loss or age limited)
+and also infer various characteristics (particularly, $\eta > 1$ in SN 1006).
+\citet{miceli2014-cloud} use azimuthal variation in synchrotron cut-off, with
+other lines of evidence, to argue for the presence of a cloud interacting w/
+the SW limb of SN 1006.
+
+Speculation: could cloud interaction could be related to the sub-Bohm diffusion
+observation in Sean's Filament 4?  The filament has many profiles, and looking
+at Sean's data it looks like all the selections show a consistently strong drop
+in FWHM.  \citet{miceli2013} argue that the concave distortion possibly
+associated with the cloud is linked to a dip in synchrotron cut-off energies,
+which they explain as being tied to a drop in shock velocity at the
+indentation, due to the cloud.  If shock velocities are depressed, would more
+diffusion / weaker B fields be necessary to explain the observed rim widths?
+But we must still account for the quite strong width-energy drop-off!
 
@@
 
-\subsection{Width-energy dependence}
+\subsection{Width-energy dependence and some intuition} \label{sec:energydep}
 
@@
 where $w(\nu)$ is filament FWHM as a function of observed photon frequency
-$\nu$, and $\mE = \mE(\nu)$ is generally energy dependent.  We may refer to
-observed photons interchangeably by energy or frequency $\nu$; however, $E$ is
-reserved for electron energy.
-
+$\nu$.  We may refer to observed photons interchangeably by energy or frequency
+$\nu$, but $E$ is reserved for electron energy.  The exponent $\mE = \mE(\nu)$
+is generally energy dependent.
+
+We may consider advective and diffusive lengthscales for electron transport,
+which naturally give rise to scaling relations:
+\begin{equation} \label{eq:lad}
+    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
+\end{equation}
+and
+\begin{equation} \label{eq:ldiff}
+    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
+\end{equation}
 If both diffusion and magnetic field damping are negligible (whether at a small
 range of, or all, electron energies) and electrons are only loss-limited as
-they advect downstream, $\mE$ attains a minimum value $\mE = -0.5$; this is the
+they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$; this is the
 strongest energy-dependence possible in our models.  Diffusion increases $\mE$
-monotonically but roughly plateaus at values between $-0.4$ and $0$, with
-larger $\mu$ values yielding weaker energy-dependence ($\mE$ closer to $0$, or
-even positive) \citepalias[Figure 3]{ressler2014}.
+monotonically towards a value between $-1/4$ and $1/4$, depending on the value
+of $\mu$.  In practice, $\mE$ appears to plateau at values between $-0.4$ and
+$0$, with larger $\mu$ values yielding $\mE$ closer to $0$ (weaker
+energy-dependence) \citepalias[Figure 3]{ressler2014}.  This may be attributed
+in part to the electron energy cut-off, which limits the available electrons at
+higher energies and thus thins the rims slightly, shifting $\mE$ negative
+\citepalias[Figure 5]{ressler2014}.
 
@@
 \note[Aaron]{elaborate after filling in preceding section}
-
-\subsection{Previous studies of Tycho}
-
-\note[Aaron]{Should we follow \citet{ressler2014} in adding a table of prior
-magnetic field estimates? This could be placed here, in the intro, or in the
-discussion.}
-\citet{parizot2006} derive magnetic fields of $300$--$500 \unit{\mu G}$; they
-also give both diffusion coefficients (in their $k_0$?) and $\Ecut$ values.
-\citet{rettig2012} used a measured filament lengthscale and considered
-loss-limited and magnetic damping models separately for several historical
-SNRs.  For Tycho: they report $B = 310 \unit{\mu G}$ with $\Ecut = 24
-\unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
-lengthscales, this is equivalent to our reporting of a diffusion coefficient
-(?).  With magnetic damping, they report $B = 150 \unit{\mu G}$ and a larger
-$\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
-give $80$, $230 \unit{\mu G}$ for leptonic/hadronic models for gamma-ray
-emission in Tycho.
 
@@
 contamination primarily from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line
-emission at $1.85$ and $2.45$ keV.  Although most downstream spectra show
-thermal contamination, some regions (e.g., ?!?!, ?!?! on Tycho's northwestern limb)
-are reasonably well-fit downstream due to a larger gap between the forward
-shock and contact discontinuity.
-Our best-fit photon indices ($2.4$--$3$) and column densities ($0.6$--$0.8
-\times 10^{22} \unit{cm^{-2}}$) from upstream spectra are consistent with
-previous spectral fits to Tycho's nonthermal rims \citep{hwang2002,
-cassam-chenai2007}.
+emission at $1.85$ and $2.45$ keV.  Our best-fit photon indices ($2.4$--$3$)
+and column densities ($0.6$--$0.8 \times 10^{22} \unit{cm^{-2}}$) from upstream
+spectra are consistent with previous spectral fits to Tycho's nonthermal rims
+\citep{hwang2002, cassam-chenai2007}.
 % NOTE keep stated ranges of spectral indices, column densities up to date
@@
 We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
-and the stretched or compressed FWHMs as upper/lower bounds on our reported
-FWHMs.
+and took the stretched or compressed FWHMs as upper/lower bounds on our
+reported FWHMs.
 
@@
 % Model knobs and how we twiddled them
-We varied three physical parameters (more if we consider magnetic damping fits
-explicitly):
-diffusion-energy scaling exponent $\mu$, normalized diffusion
-coefficient $\eta_2$, and magnetic field strength $B_0$.
+We varied three physical parameters: diffusion-energy scaling exponent $\mu$,
+normalized diffusion coefficient $\eta_2$, and magnetic field strength $B_0$.
 To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
-$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$;
-recall that $\mu = 1/3$ and $1/2$ correspond to Kolmogorov and Kraichnan turbulence.
-
-% Tycho parameters
+$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$; recall that $\mu = 1/3$ and $1/2$
+correspond to Kolmogorov and Kraichnan turbulence.  Our fits do not consider
+a damped magnetic field with the additional parameter of scale length $a_b$,
+and so magnetic field strength $B_0$ is assumed constant downstream of the
+shock.  Below we shall show that magnetic damping cannot explain our observed
+filament widths, so we present fits assuming loss-limited rim widths only.
+% TODO Edit if I add magnetic damping material
+
+% Tycho parameters TODO change green2009 to green2014 once published in BASI
 A few remnant-specific parameters enter into the model calculations.  We
-adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha = 0.65$
+adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha =
+0.65$ \citep{kothes2006},
 \note[Aaron]{will change to $s= 2.16$ from $\alpha=0.58$ following
 \citet{sun2011} on next iteration}
-\citep{kothes2006},
-remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
-shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
+remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and shock radius
+$1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
 \citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
@@
 \begin{table*}[ht]
+    % Use \tiny for manuscript; \scriptsize for 2-column
+    %\tiny
     \scriptsize
@@
 comparison of rims from Regions 1 and 16 in Figure~\ref{fig:profiles}.
-\note[Aaron]{review paragraph wording}
+\note[Aaron]{review paragraph wording.  This may belong in the discussion?}
+
+% discussion of uncertainties/caveats in our results
+% \note[Aaron]{text blob}
+% One way to address uncertainty in the fitting function is to consider other
+% functions -- for example, a gently smoothed spline fit, a manually capped
+% two-exponential function, a Gaussian sitting on a ramp or logistic curve, etc.
+% Explain that nothing happens -- not much (but should reaffirm this or give
+% some kind of numbers).
+% Another is simply our sampling -- we have already sought to circumvent this by
+% taking multiple regions in each filament, as many as possible without overly
+% compromising the quality of our radial profiles.  This also makes no major
+% difference to our results.
 
@@
 considered.  The first row of Table~\ref{tab:fits} includes both simple and
-full model fits for Region 1 for comparison.
-We found that fits to the simpler catastrophic dump model
-(equation~\eqref{eq:simp-mod}) reproduced qualitative trends seen in the full
-continuous energy loss model, as expected.  In general, simple model fits
-yielded slightly smaller $\eta_2$ and/or slightly larger $B_0$ values; this is
-consistent with the expectation that electrons travel farther in the simple
-model than in the full model, since electrons are not subjected to continuous
-synchrotron cooling, so smaller $\eta_2$ and larger $B_0$ values are needed to
-generate thinner rim widths as compared to the full model.  Simple model fits
-were also more likely to reach manual fitting limits (i.e., allow for
-unconstrained parameter values) than full model fits.
+full model fits for Region 1 for comparison.  We found that fits to the simpler
+catastrophic dump model (equation~\eqref{eq:simp-mod}) reproduced qualitative
+trends seen in the full continuous energy loss model, as expected.  In general,
+simple model fits yielded slightly smaller $\eta_2$ and/or slightly larger
+$B_0$ values; this is consistent with the expectation that electrons travel
+farther in the simple model than in the full model. Since electrons are not
+subjected to continuous synchrotron cooling, smaller $\eta_2$ and larger $B_0$
+values are needed to generate thinner rim widths as compared to the full model.
+Simple model fits were also more likely to reach manual fitting limits (i.e.,
+allow for unconstrained parameter values) than full model fits.
 
@@
 
-% Linchpin of argument -- energy dependence at ~1 keV incompatible with damping
-% NOTE keep numbers up to date
+% Set-up the argument.  Claim that B damping is untenable.  Explain the
+% necessary observational consequences of B damping
+% NOTE keep numbers up to date -- after running Tycho calculations
 Our observations of strong energy-dependence, particularly at low energies
 (0.7--1 keV, 1--1.7 keV, 2--3 keV), are incompatible with magnetic damping as a
-primary control on filament widths.
-Our mean $\mE$ values with errors favor $|\mE| \gtrsim 0.25$ at $\abt 1
-\unit{keV}$, and $|\mE| \gtrsim 0.19$ at $\abt 2 \unit{keV}$.
-\note[Aaron]{calculations on magnetic damping $\mE$ go here}  % TODO FILL IN
-\citetalias{ressler2014} also argued that magnetic damping generally requires
-$|\mE| \sim 0.1$.  If thin rims are not magnetically damped at our lowest
-energy bands, the rims will not be damped at any higher energies (barring
-extreme $\mu>1$ diffusion with $\mE > 0$ that yields wider rims at higher
-energies -- and indeed that is further disfavored by the electron energy
-cut-off, as well as the fact that diffusion only begins to outpace advection
-around the same cut-off).  Our result should hold for all photon energies above
-$\abt 1 \unit{keV}$.
+primary remnant-wide control on filament widths.  \note[Aaron]{calculations on
+reasonable magnetic damping values of $\mE$ go here}  % TODO FILL IN
+\citetalias{ressler2014}, using the same formalism we applied to our model
+fits, stated that magnetic damping generally requires $|\mE| \lesssim 0.1$.
+Furthermore, if synchrotron rims are magnetically damped at some observation
+energy, the rims must be damped at all lower observation energies as well.
+Thus damping requires not only $\mE \sim -0.1$, but also that $\mE \sim
+-0.1$ must hold for all energies below some threshold damping energy.  Above
+this energy, advective or diffusive lengthscales may shrink below the
+damping scale length so that synchrotron losses become more restrictive on rim
+widths.
+
+% Now turn to our data and say, this is not what we see.
+% NOTE keep numbers up to date
+We observe the contrapositive: mean $\mE$ values with errors in
+Table~\ref{tab:fwhms} favor $|\mE| \gtrsim 0.25$ at $\abt 1 \unit{keV}$ and
+$|\mE| \gtrsim 0.19$ at $\abt 2 \unit{keV}$, disqualifying magnetic damping at
+energies above $\sim 1 \unit{keV}$.  If thin rims are \emph{not} magnetically
+damped at our lowest energy bands, the rims will not be damped at any higher
+energies. \note[Aaron]{belaboring the point, can make more concise}
+Within the framework of our three-parameter model ($\mu$, $\eta_2$, $B_0$), the
+only workaround would be to find $\mu > 1$ diffusion that is able to produce
+$\mE > 0$; i.e., if rims widen at higher energies they may run up against any
+presumed damping scale length.  But this is unlikely as the electron energy
+cut-off shifts $\mE$ slightly negative at high energies, and diffusion only
+becomes comparable to or stronger than advection around $E \gtrsim \Ecut$.
 
 % More quantification -- give scale lengths, field strength values.
-How robust is this result, give quantitative results.
+Elaborate.  How robust is this result, quantitatively?
 What is the smallest damping scale length that is (roughly) consistent with all
@@
 
-% Address the broader trend in mE
-The observed decrease in $|\mE|$ with increasing energy is attributable to
-diffusion, which weakens width-energy dependence at higher energies
-(even if diffusion is energy-independent with $\mu = 0$)
-\citepalias[see][Figure 5]{ressler2014}.
-\note[Aaron]{material on width scaling w/ $B_0$ and $\eta_2$. I'm not sure
-where this should go, exactly.  May be better in the next section.
-Or, this may even go in the beginning of the text, after or before introducing
-transport models?!}
-To make this more quantitative, note the scaling relations:
-\begin{equation}
-    l_{\mt{ad}} \propto v_d B_0^{-3/2} \nu^{-1/2}
-\end{equation}
-and
-\begin{equation}
-    l_{\mt{diff}} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
-\end{equation}
-As previously claimed, where advection dominates we expect $w \sim l_{\mt{ad}}
-\sim \nu^{-1/2}$.  Where diffusion and advection are comparable, we expect
-$|\mE|$ to decrease, i.e. yielding weaker energy dependence.
-\citetalias{ressler2014} give a full discussion of the relative effects of
-advection and diffusion, as well as the effect of $\Ecut$ in counterbalancing
-the effects of diffusion at higher energies; see in particular Figures 3 and 5
-of \citetalias{ressler2014}.  \note[Aaron]{might have been discussed earlier?}
+% Move on to address the broader trend in mE, where energy dependence weakens
+The observed decrease in $|\mE|$ with increasing energy may be attributed to
+diffusion, which weakens width-energy dependence at higher energies.
+As discussed in Section~\ref{sec:energydep}, where advection dominates we
+expect $w \sim l_{\mt{ad}} \propto \nu^{-1/2}$ or $\mE \approx -0.5$.  As
+diffusion outpaces advection for energies near and above the electron cut-off
+energy, $\mE$ will approach values closer to $0$.
 The increasing importance of diffusion at X-ray energies matches the
@@
 comparable.  Thus, a weakening energy dependence in X-rays is consistent with
-prior work and a welcome observation!
-\note[Aaron]{I think this is a nice result of its own, unless it's a bit
-obvious?  Importantly, the spectral roll-off observation is derived from the
-intensity of Tycho -- how much flux comes out of the rims.  But we look at the
-widths, disregarding intensity, and find a consistent result.}
+prior work.
+\note[Aaron]{I think the observation of rim narrowing with decreasing $|\mE|$
+is a nice result of its own -- the measurements and $\mE$ don't draw on any
+assumptions about the mechanism producing these thin rims.  The observation of
+a spectral roll-off depends on the intensity at various energies, how much flux
+comes off the rim, whereas this $|\mE|$ "relaxing" is independent of intensity.
+But I'm not sure if it's worth noting/discussing in particular.}
 
 % Addressing the variability in width measurements
-The large variation in filament widths, and point-wise computed $\mE$ values,
-does make our claim a little shakier.  Indeed, in Region 3 we see
-\emph{increases} in filament width between multiple energy bands.
-But we have confidence on our averaged results.
-\note[Aaron]{We could also compute $\mE$ numerically from the model fit
-profiles -- basically mimicking Sean's Figures 1, 5, 6, but generating $\mE$
-numbers that effectively reflect the broad energy drop-off (or, lack thereof)
-from all measured widths.}
-
-\subsection{Model parameters: constraining magnetic fields and diffusion}
-
-We now turn to our model fit parameters, magnetic field strength and diffusion
-coefficient.
-
-%WHERE to place the width - magnetic field dependence.  Cite Parizot's paper on
-%this result, mention Sean's paper for symbols/set-up similar to our work.
-%---> BRIAN reminded me, he wanted to talk about REMNANT DISTANCE. RIGHT.
-%Throw this text in here, to discuss mE.
-%Then we backreference this equation and simply say, the physical width scales
-%linearly with the remnant distance.  The ONLY confounding factor is that shock
-%velocity changes as well. -- SO, I need to add in NUMBERS!!!!!
-
-% 1-2 paragraphs on this
-Eta2 is poorly constrained.  Explain why -- we have a strong degeneracy between
-magnetic field and eta2, especially at low mu.  Mention the sensitivity
-results.
-It is important to note that this is a limitation of our fitting model, not of
-the data.  Stacking the data, e.g. by taking larger regions or averaging FWHM
-measurements, does NOT help.
-
-But, we note that our model fits generally favor $\eta_2 > 1$ -- the lowest
-error bound on $\eta_2$ is ????. % TODO.
-
-Magnetic field $B_0$: despite the large range of fit quality, we can give
-fairly robust lower bounds.  Lowest bound is ????  Consistent with previous
-studies, Tycho requires strong magnetic field amplification -- up to ??? times
-the expected value of $\abt 10 \unit{\mu G}$ from a strong shock with
-compression ratio $r=4$ and typical galactic magnetic field strength of $\abt
-2$--$3 \unit{\mu G}$ \citep{lyne1989, han2006}.
-
-A few ways to touch this -- can we back out information from the synchrotron
-roll-off and hence $\Ecut$, to obtain diffusion coefficient independently of
-$B_0$?  Then we have a single parameter fit.
-
-We could report estimates of cut-off energy?  I don't know if that is
-helpful/meaningful for anything, unless we can tie it back to something in DSA.
-
-Can we favor a value of $\mu$ (and hence a turbulent energy spectrum)?
-
-\subsection{Variations on a theme of plug \& chug}
-
-Discuss, briefly, effects of twiddle-ables: changing Tycho distance ($2.3
-\unit{kpc}$ to $4 \unit{kpc}$, see \citet{hayato2010}), compression ratio $r$,
-accounting for azimuthal variation in $v_s$ (compare to taking a remnant
-average?).  Sean already discussed $\Ecut$ (result: more high energy electrons
-to damp out narrowing at high energy, if $\Ecut$ not included).
-
-\subsection{Uncertainties what not trash heap}
-
-% discussion of uncertainties/caveats in our results
-Our FWHM measurements have a good deal of scatter.
-One possible concern is our fitting function, which may overshoot or undershoot
-our profiles, or simply fail to fit profiles that are not well-described as
-having exponential fall-offs.
-.. One way to address this is to consider other functions -- for example, a
-gently smoothed spline fit, a manually capped two-exponential function, a
-Gaussian sitting on a ramp or logistic curve, etc.
-Explain that nothing happens -- not much (but I will reaffirm this).
-.. another is simply our sampling -- we have already sought to circumvent this
-by taking multiple regions in each filament, as many as possible without overly
-compromising the quality of our radial profiles
-
-\subsection{Other things}
-
-Precursors, rim position variation (none obvious from preliminary look; see
-Figure~\ref{fig:peak-pos}), steepness of the filament rise?
-
-\begin{figure}[ht]
-    \centering
-    \plotone{figures/f0-peak-pos.pdf}
-    \caption{Best-fit rim peak positions ($x_0$ in equation~\eqref{eq:prof})
-        for all regions as a function of energy band, normalized to the $2
-        \unit{keV}$ peak position.  Red line plots best linear fit to all data
-        with slope of $-0.025 \unit{arcsec/keV}$.
-        \label{fig:peak-pos}}
-\end{figure}
+The large variation in filament widths and point-wise computed $\mE$ values
+renders our interpretation of $\mE$ more conjectural.  Multiple regions show both
+increases and decreases in filament widths between multiple energy bands (e.g.,
+Region 9).  But, our averaged results should mitigate this natural measurement
+spread.
+
+\subsection{Modeled diffusion and magnetic field amplification}
+
+% Discuss the degeneracy
+We now turn to our model fit parameters: magnetic field strength $B_0$ and
+scaled diffusion coefficient $\eta_2$.  Our model fit results are poorly
+constrained as the parameters $B_0$ and $\eta_2$ may covary without strongly
+altering fit quality.  Equations~\eqref{eq:lad} and $\eqref{eq:ldiff}$
+illustrate this clearly.  Varying $B_0$ changes both $l_{\mt{ad}}$ and
+$l_{\mt{diff}}$ evenly; varying $\eta_2$ (and hence $\eta$) changes only
+$l_{\mt{diff}}$, in principle.  But, if diffusion is the primary control on rim
+width -- i.e., $l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim
+l_{\mt{diff}}$) -- we see that $\eta_2$ and $B_0$ become almost entirely
+degenerate.  Ramping up particle diffusion and hence rim widths can be
+perfectly counteracted by increasing magnetic fields and forcing electrons to
+cool faster, decreasing rim widths.  If advection is the primary control on rim
+width (widths narrow rapidly with energy, at $\mE \sim -0.5$), then $\eta_2$
+becomes unimportant and the fit is better behaved with effectively one free
+parameter.  The degeneracy of $B_0$ and $\eta_2$ is generally stronger for
+smaller values of $\mu$, although there appears no clear trend as to when a
+particular fit will be ill-constrained.
+\note[Aaron]{a bit wordy}
+
+% B0 lower bounds, etc.
+A minimum magnetic field strength $B_0 \gtrsim 179 \muG$, within stated
+errors, is required throughout the remnant.  The minimum values of $B_0$ for
+each filament (1--5) are $179$, $254$, $287$, $458$, and $243 \muG$.
+We observe the smallest $B_0$ values for $\eta_2$ approaching $0$ and $\mu =
+2$; intuitively, $\mu = 2$ favors diffusion at higher energies ($>2\unit{keV}$)
+where it is most ``needed'' to reproduce the leveling off of filament widths
+and so $\mu = 2$ permits a smaller best-fit $\eta_2$ and hence smaller $B_0$.
+\note[Aaron]{$\mu=2$ bit not very important}
+Our minimum values of $B_0$ are consistent with prior estimates of
+$\abt 200$--$300 \muG$ for primarily advective transport
+\citep{volk2005, parizot2006, morlino2012} \note[Aaron]{could elaborate and
+review previous work; deferring for now}.  A larger range of values has been
+obtained ($130$--$500 \muG$) when considering additional effects, such as
+varying compression ratio and nonlinear diffusion-energy scaling
+\citep{parizot2006, cassam-chenai2007}.
+
+Consistent with previous studies, Tycho requires strong magnetic field
+amplification -- at least $\abt 20\times$ the expected value of $\abt 10 \muG$
+from a strong shock with compression ratio $r=4$ and typical galactic magnetic
+field strength of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
+
+% More detail on relevant B0 estimates follows
+
+% \citet{parizot2006} give $200 \muG$ for pure advection and $230 \muG$ for pure
+% diffusion; with both effects, they obtain $300$--$530 \muG$ depending on the
+% assumed compression ratio and diffusion-energy scaling $\mu$.
+% \citet{volk2005} combine a prediction from nonlinear acceleration with actual
+% data.  They too suggest something like $300 \muG$.
+% \citet{volk2002} give $240 \muG$ from a multiwavelength study.  Too many papers
+% from Russian theorists, seriously.
+% \citet{morlino2012} do a similar thing with newer data and favor $B_0 > 200
+% \muG$ strong magnetic fields -- it also is favored by the hadronic scenario of
+% pion decay to help explain gamma-ray observations.
+% \citet{cassam-chenai2007} take values $215 \muG$ and $130 \muG$ for different
+% particle injection efficiencies to describe the X-ray rims of Tycho; note that
+% they find an overall compression ratio $r \approx 6$ and treat the effect of CR
+% acceleration and escape on the shock hydrodynamics.
+
+% \citet{rettig2012} used a measured filament lengthscale and considered
+% loss-limited and magnetic damping models separately for several historical
+% SNRs.  For Tycho: they report $B = 310 \muG$ with $\Ecut = 24
+% \unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
+% lengthscales, this is equivalent to our reporting of a diffusion coefficient
+% (?).  With magnetic damping, they report $B = 150 \muG$ and a larger
+% $\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
+% give $80$, $230 \muG$ for leptonic/hadronic models for gamma-ray
+% emission in Tycho.
+
+% 1-2 paragraphs on eta2
+The values of $\eta_2$ in Tables~\ref{tab:fits} and \ref{tab:fits-pt2} are very
+poorly constrained.  We observe no clear trend of $\eta_2$ with $\mu$, and the
+values and error bounds on $\eta_2$ are often unreasonably large.  The extreme
+outliers limit the usefulness of the average fit parameters presented in
+Table~\ref{tab:fits-avg}.
+
+Our model fits do generally favor $\eta_2 \geq 1$, respecting the Bohm limit on
+diffusion.  The lowest error bound on $\eta_2$ in the averaged best-fit values
+is $1.2$, with minimum error bounds in each filament of order $1$--$10$.  For
+individual regions' best fits, only Regions 5 and 18 have best-fit $\eta_2$
+values falling strictly below $\eta_2 = 1$.  \note[Aaron]{I think Region 5 is
+skewed by the unusually large 0.7--1 keV FWHM.  Region 18 is a weird place, a
+smushed-out and somewhat faint filament in the NE where Bohm just bombs and rim
+widths narrow strongly.}
+
+% A quick discussion of mu
+Our fits at multiple values of $\mu$ are not especially insightful either.
+The $\chi^2_{\mt{red}}$ values for individual fits are variable and quite
+large, so they may not be reliable for favoring or disfavoring fits at
+different $\mu$ values.  But, if we ignore this caveat, we see that values
+of $\mu \geq 1$ are qualitatively favored by $\chi^2_{\mt{red}}$ in almost all
+regions.  This trend may be an partially an artifact of the correlation between
+$B_0$ and $\eta_2$ as they are not entirely independent parameters, but they
+are less correlated for larger $\mu$.  However, our computed
+$\chi^2_{\mt{red}}$ values have simply assigned a single degree of freedom to
+each parameter.  \citetalias{ressler2014} also found better model fits for $\mu
+\geq 1$ in the remnant of SN 1006 and noted that \citet{reynolds2004} favored
+$\mu \geq 1$ on grounds of better modeled remnant morphology, but it remains
+uncertain whether $\mu \geq 1$ diffusion is truly preferred.
+
+% Data quality
+We emphasize that our measurements are not data limited, as additional counts
+from averaging measurements or selecting larger regions will not improve our
+ability to constrain $B_0$ and $\eta_2$.  This is easily seen from reduced
+$\chi^2$ values in Tables~\ref{tab:fits} and \ref{tab:fits-pt2}, which
+reflect relatively tight errors in our FWHM profile measurements
+(Table~\ref{tab:fwhms}).
+
+\subsection{Tactics for constraining diffusion}
+
+A major independent observable is the synchrotron roll-off frequency.  If
+Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is
+independent of magnetic field strength and thus grants an external
+constraint on diffusion coefficient.
+In this manner, \citet{parizot2006} estimated diffusion coefficients
+$\eta = 10, 5$ for compression ratios $4, 10$ in Tycho.
+
+Speculative: we could pull out (or ourselves measure) the roll-off frequency
+from \texttt{srcut} around the remnant, then estimate a diffusion coefficient
+in each region and then get single parameter fits for magnetic field strengths?
+
+\subsection{Tycho distance estimates}
+
+In our modeling we adopted a distance $d$ to Tycho of $3 \unit{kpc}$, but
+various estimates for Tycho's distance range between $2.3$--$4 \unit{kpc}$
+\citep{hayato2010}.  A larger remnant distance would increase both physical
+filament widths and shock velocity estimates from proper motion (as used in our
+models).
+
+% lad/ldiff scalings give eta/B0 scalings
+For both simple and full models, we find roughly that $\eta_2 \propto d^2$
+while $B_0$ is approximately constant.  The advective lengthscale,
+equation~\eqref{eq:lad}, may be rearranged to obtain:
+\begin{equation}
+    B_0 = (317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
+                     \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
+                     \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
+\end{equation}
+or, more simply,
+\begin{equation}
+    B_0 \propto \left(v_d\right)^{2/3}
+                \left(l_{\mt{ad}}\right)^{-2/3} \nu^{-1/3} .
+\end{equation}
+Both $l_{\mt{ad}}$ and $v_d$ scale linearly with remnant distance $d$ and thus
+their effects cancel in determining the magnetic field.  If diffusion is the
+primary control on filament lengthscales, equation~\eqref{eq:ldiff} yields:
+\begin{equation}
+    \eta \propto \left(l_{\mt{diff}}\right)^2 B_0^{3} \nu^{-(\mu - 1)/2}
+\end{equation}
+Recall that $\eta \propto \eta_2$ as $E_h = E_2$ is constant, from
+equation~\eqref{eq:diffcoeff}.
+Similar results, primarily for magnetic field $B_0$, were previously given by
+\citet{parizot2006}.
+
+In practice, both advection and diffusion are important to our filament widths,
+but we concurrently observe the scalings $\eta_2 \propto d^2$ and $B_0$
+constant in model fits with varying distance.  When comparing full model fits
+with remnant distances of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from
+the idealized scaling is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for
+$\eta_2$.
+
+One explanation is that as varying remnant distance $d$ leaves the width-energy
+scaling $\mE$ invariant, the relative contributions of $l_{\mt{ad}}$ and
+$l_{\mt{diff}}$ should also be invariant.  Then both lengthscales should
+scale simultaneously with $d$, yielding the observed behavior.
+\note[Aaron]{need a logic check here}
+
+\subsection{Nonlinear DSA, CR-modified shocks, precursors (misc things)}
+
+Compared to our baseline assumptions for a standard strong shock ($r=4$) with
+constant magnetic field advected downstream, a treatment that permits higher
+compression ratios (from whatever instabilities or what have you) will
+generally permit weaker magnetic fields.  The reason for this, I think
+(speculating at this point due to lack of knowledge) lies in the resulting
+lower plasma velocity, which depresses the advective length scale and permits
+thinner rims more naturally (assuming diffusion not too strong).
+
+Could the gradual increase of compression ratio leading up to the shock matter,
+if CR streaming is important?  Maybe strengthen a diffusive precursor?
+
+Electron energy spectrum functional form by \citet{zirakashvili2007}, see also
+\citet{morlino2009}.
+
+Rim position variation (none obvious from preliminary look), steepness of the
+filament rise?
+% see Figure~\ref{fig:peak-pos}
+
+%\begin{figure}[ht]
+%    \centering
+%    \plotone{figures/f0-peak-pos.pdf}
+%    \caption{Best-fit rim peak positions ($x_0$ in equation~\eqref{eq:prof})
+%        for all regions as a function of energy band, normalized to the $2
+%        \unit{keV}$ peak position.  Red line plots best linear fit to all data
+%        with slope of $-0.025 \unit{arcsec/keV}$.
+%        \label{fig:peak-pos}}
+%\end{figure}
 
@@
 
-% Summarize our results
-Our observations of filament thinning, although qualitative, are consistent
-with the observations of \citet{ressler2014} in SN 1006.
-We find that filaments narrow considerably.
-
+A priori, we are confident that the rims are nonthermal and meaningful proxies
+for remnant magnetic fields and diffusion, as evidenced by our spectral fits
+and region selections.
+A posteriori, our multiple measurements when modeled (without damping) give
+diffusion and magnetic fields consistent with those derived by considering
+other observables, specifically synchrotron roll-off as derived from radio flux
+and spectral modeling from gamma ray data.
+
+% Is rim narrowing universal?  Further work on more remnants
+From these checks, and the knowledge that our data are not count limited, we
+argue that the observation of rim narrowing in Tycho is sufficient to
+rule out magnetic field damping at the lengthscales of observed X-ray rims.
+Our observations also corroborate rim narrowing as observed by
+\citet{ressler2014} in the remnant of SN 1006.  We will investigate thin rims
+in Kepler's SNR and Cas A \citep[but cf.][]{araya2010} as well.  If significant
+remnant narrowing is a common feature in young supernova remnants, strong
+magnetic fields must be sustained some distance behind the forward shock -- and
+this will need to be understood or characterized (the question becomes, why
+aren't various putative damping mechanisms relevant to SNRs?).
+\note[Aaron]{I am tempted to toss in Kepler results, to prevent duplication of
+text/exposition and maybe start making some case for loss-limited rims being a
+consistent observation.  That would be a lot of tables, though.}
+
+% Modeling limitations
 Filaments widths, as might be expected, do not match model predictions too
@@
 Tycho's nonthermal emission and shock structure, as well as its surrounding
-medium.  This despite the fact that Tycho is the closest we have to a spherical
-cow of a SNR!
+medium.  Streaming and diffusing particles may modify the shock structure;
+fluid instabilities and ISM interactions may induce wave-like instabilities in
+the forward shock's projected shape; multiple and fragmented filaments
+\citep{caprioli2013},
+even in relatively ``clean'' remnants of Type Ia SNe such as SN 1006, Tycho's
+SNR, and Kepler's SNR. \note[Aaron]{needs fact-check and reading}
 
 % Further work -- radio
-BROAD QUESTION -- Why couldn't we answer this from radio measurements?
-Rims are splattered/lost in emission from within the remnant, looking at
-\citet{cassam-chenai2007}.
-Are the rims from shock accelerated electrons, simply swamped/drowned by
-turbulence/synchrotron/bremsstrahlung in the interior? (seems that
-bremsstrahlung is unimportant at very low frequencies...)
-
-VLA data from Brian/Jack Hewitt, + Chandra X-ray data, coming November!
-They have lots of fun things to look at -- proper motion (main thing),
-polarization, etc.  Can take a look at the radio rims too and see what's up...
-
-% Further work -- other SNRs
-We will follow up with an analysis of Kepler's supernova remnant and
-Cassiopeia A \citep[see][]{araya2010}.  Further confirmation that X-ray rims
-are not damped may suggest that any damping lengthscale must be quite a bit
-larger than the observed rims, and the damping hypothesis will need to be
-tested by continuing radio observations (???) or numerical and laboratory
-simulations.
-
-Ask a theorist: if we find a pretty global behavior, that damping is disfavored
-in all remnants -- what does that tell us about the damping?  Why
-\emph{shouldn't} damping occur on small lengthscales?
+As has been noted by many workers, observations of radio synchrotron rims would
+provide strong and immediate evidence for magnetic field damping (at the
+lengthscales of said radio rims).  Previous workers have certainly tried
+\citep{cassam-chenai2007, morlino2012} but it seems not easy.
+A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
+Williams) will offer a rich dataset of sub-arcsecond observations that may
+reveal more about rim morphology and perhaps even temporal variation over a 10+
+year baseline.
 
@@
 
-A.T. thanks CRESST for support.
+A.T. thanks CRESST for support (or, any relevant grants?)
 B.J.W. NPP?
@@
 
-\clearpage
+%\clearpage
 

### 2014-10-04 code/models/FullEfflengthPohlab_mod.f

@@ -1,0 +1,852 @@
+! ----------------------------------------------------------------------
+! Sean Ressler's code w/ magnetic damping
+!
+! Cleaned up for review, before porting B damping to Python
+!
+! Statement labels right aligned from column 5
+! Continuation ampersands on column 6
+! Exclamation points for all comments
+! ----------------------------------------------------------------------
+
+      program Fullefflengthab
+        double precision cm, ecut
+        double precision B0, v0, rs, alpha
+        double precision nu0, nu, ab, emis1
+        double precision a, nugraph(100)
+        double precision r, delr(40), rgraph(10000,40)
+        double precision dx, integrand, integral
+        Double Precision compratio
+        double precision distr, Bfield
+        double precision intensitygraph(40,10000)
+        double precision xex(100), fex(100)
+        double precision nuroll,x, rho
+        double precision width(40), advection(40)
+        double precision rmin, norms(40)
+        double precision intensity, fluxplat(40), fluxpeak(40)
+        double precision gammaplat(40), gammapeak(40)
+        double precision rtab(1000), inttab(1000), titab(1000)
+        double precision brtab(1000), bttab(1000), altab(1000)
+        double precision bgraph(1000), en, rad, delrad, c1
+        double precision disttab(100, 10000), radtab(10000)
+        double precision distgraph(10000), Bmin, B, slopeemis
+        double precision disttab1(100,10000), emistab(10000)
+        double precision spline,BIATX(1000)
+        DOUBLE PRECISION BCOEF(1000), GTAU(1000), Q(112640), T(1006)
+
+        common/xrays/xex, fex, ir
+
+        !Physics Parameters
+        compratio = 4d0
+        v0 = 5*1.d8/compratio
+        ab =.05d0
+        Bmin =5d-6
+        rs = 2.96e19    !tan(943.7'')*2.2 kpc
+        alpha = .6d0
+        s = 2d0*alpha+1d0
+
+        !Constants
+        cm = 1.82d18
+        c1 = 6.27e18
+        a = 1.57d-3
+
+        !Options
+        icut = 0
+
+        !Grid Parameters
+        iradmax=400  !Grid size for e-distribution table
+        irmax =1000  !Grid size for intensity
+        ixmax = 500  !Grid size for line of sight
+        inumax = 4   !Grid size for frequency
[…]

### 2014-10-04 code/models/FullEfflength_port.py

@@ -187,6 +187,11 @@ def emisx(r, nu, B, radtab, disttab, xex, fex):
 
     integrand = fex * dist / (xex**1.5)
 
+    # TODO TODO B-damping: compute as
+    # z = 1d0-radtab(irad)
+    # Bfield = Bmin + (Bmax-Bmin)*dexp(-z/ab)  ! Bmax=B0
+    # np.sqrt(nu*Bfield)
+
     # Skip constant prefactors
     return spint.trapz(integrand, xex, axis=0) * np.sqrt(nu*B)
 

### 2014-10-04 code/models/models_disp.py

@@ -132,7 +132,7 @@ def load_fit_pkls(inroot, want_fobj=False):
         tuple of 1. list of Parameters(), 2. list of mu values, 3., region num
                  4. fobj_all dict w/ fitting data, if desired
     """
-    npkls = len(glob('{}-*-data.pkl'.format(inroot)))
+    npkls = len(glob('{}-[0-9]*-data.pkl'.format(inroot)))
     for n in xrange(npkls):
         fname = '{}-{:02d}-data.pkl'.format(inroot, n+1)  # Enforce ordering
         ffobj = '{}-{:02d}-fobj.pkl'.format(inroot, n+1)

### 2014-10-05 code/models/FullEfflength_mod.f
Add B-damping to full model
Modify e- distr functions (Fortran) and emissivity integration (Python)

@@ -80,13 +80,13 @@
           if (snrflag.eq.0) then
             call Fullefflengthsub(kevs, inumax, widtharc, B0, eta2, mu,
      &                          5d0*1.d8, 5d0*1.d8/4d0, 2.96d19, 900d0,
-     &                          2d0*0.6d0+1d0, rminarcarray, 1, 4000,
-     &                          200,1000)
+     &                          2d0*0.6d0+1d0, rminarcarray, 1, 400,
+     &                          100,500, 1, 0.05d0, 5d-6)
           elseif (snrflag.eq.1) then
             call Fullefflengthsub(kevs, inumax, widtharc, B0, eta2, mu,
      &                            4.7d0*1.d8, 4.7d0*1.d8/4d0, 1.077d19,
      &                            240d0, 2d0*0.65d0+1d0, rminarcarray,
-     &                            1, 400, 100,500)
+     &                            1, 400, 100,500, 0, 0.05d0, 5d-6)
           endif
 
           do i = 1, inumax
@@ -117,20 +117,25 @@
 !     iradmax = 100     ! Resolution on tabulated electron distribution
 !     ixmax =  500      ! Resolution along line of sight for integration
 
+!     idamp = ...
+!     ab = 0.05d0
+!     Bmin = 5d-6
+
       subroutine Fullefflengthsub(kevs, inumax, widtharc, B0, eta2, mu,
      &                            vs, v0, rs, rsarc, s, rminarc, icut,
-     &                            irmax, iradmax, ixmax)
+     &                            irmax, iradmax, ixmax,
+     &                            idamp, ab, Bmin)
           implicit none
           ! Input parameters (widtharc is for output)
           integer inumax
-          double precision mu, eta2, B0
+          double precision mu, eta2, B0, ab, Bmin
           double precision kevs(inumax), widtharc(inumax)
           ! Constants, or nominally constant inputs (SNR specific)
           double precision vs, v0, rs, rsarc, s
           double precision rminarc(inumax)
           ! Settings
           integer irmax, ixmax, iradmax
-          integer icut
+          integer icut, idamp
 
           ! "Fundamental" constants
           double precision cm, c1, a ! Synchrotron params
@@ -153,7 +158,7 @@
           double precision dx, x, rho
           integer i, ix
           double precision emis1, integrand, integral, intensity
[…]

### 2014-10-05 code/models/FullEfflength_port.py

@@ -62,14 +62,14 @@ def main():
 
 # @profile
 def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
-            iradmax, ixmax):
+            iradmax, ixmax, idamp, ab, Bmin):
     """Use numpy arrays for everything (kevs, rminarc)
 
     Note that irmax is not very important anymore.
 
     Input:
         kevs (np.ndarray)
-        B0, eta2, mu (float)
+        B0, eta2, mu (float), B0 in Gauss
         vs, v0, rs, rsarc, s (float)
         rminarc (np.ndarray)
         icut (bool, or 0/1)
@@ -77,6 +77,8 @@ def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
             irmax = resolution on intensity profile (400, SN 1006)
             iradmax = resolution on tabulated e- distribution (100, SN 1006)
             ixmax = resolution for line of sight integration (500, SN 1006)
+        idamp (bool), enable/disable damping
+        ab, Bmin (float) damping scale length btwn [0,1], Bmin in Gauss
     Output:
         np.ndarray of FWHMs for each entry in kevs
     """
@@ -106,14 +108,17 @@ def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
         # Tabulate e- distr. for fixed nu over e- energy, radial coord
         # Be careful, Fortran code hardcoded for iradmax < 1000
         # and Pacholczyk table < 100 entries
+        idamp_flag = 1 if idamp else 0  # Convert bool to int for Fortran
         radtab = np.linspace(rmin_nu, 1.0, num=iradmax)
         disttab = fullmodel.distr(np.zeros(1000), iradmax, nu, rmin_nu,
-                                  B0, Ecut, eta, mu, rs, v0, s, C_1)
+                                  B0, Ecut, eta, mu, rs, v0, s, C_1,
+                                  idamp_flag, ab, Bmin)
         disttab = disttab[:len(xex), :iradmax]  # Slice off zeros
 
         # Tabulate emissivity over radial coord
         rhotab = np.linspace(rmin_nu, 1., num=10000)  # TODO let num=irhomax?
[…]

### 2014-10-05 code/models/models.py

@@ -469,7 +469,8 @@ def simple_width(snr, kevs, mu, eta2, B0):
 # Input: params, kevs, snr, **kwargs; output: model FWHMs
 
 def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
-    irmax=None, iradmax=None, ixmax=None, irad_adapt=True, irad_adapt_f=1.2):
+    irmax=None, iradmax=None, ixmax=None, irad_adapt=True, irad_adapt_f=1.2,
+    idamp=False, damp_ab=0.05, damp_bmin=5.0e-6):
     """Width function, wrapper for Python port of full model (equation 12)
 
     All **kwargs not specified (excepting verbose) are taken from snr object
@@ -496,6 +497,10 @@ def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
                     comparatively faster than increasing grid resolution)
         irad_adapt_f: float, should be > 1; margin-of-error for rminarc in
                       adaptive calculation
+
+        idamp: boolean; toggle magnetic damping
+        damp_ab: float between [0,1], damping lengthscale if damping is on
+        damp_bmin: float, minimum magnetic field for damping
 
     Outputs:
         np.array of modeled FWHMs (arcsec) for each energy in 'kevs'
@@ -537,7 +542,8 @@ def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
         iradmax_prelim = int(iradmax / 2.)  # Just a rough calculation
 
         fwhms_prelim = fmp.fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s,
-                                   rminarc, icut, irmax, iradmax_prelim, ixmax)
+                                   rminarc, icut, irmax, iradmax_prelim, ixmax,
+                                   idamp, damp_ab, damp_bmin)
 
         # Replace error-code values
         res_msk, box_msk = _check_calc_errs(fwhms_prelim, rminarc)
@@ -568,7 +574,8 @@ def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
 
     # Python full model port
     fwhms = fmp.fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s,
-                        rminarc, icut, irmax, iradmax, ixmax)
+                        rminarc, icut, irmax, iradmax, ixmax,
+                        idamp, damp_ab, damp_bmin)
 
     res_msk, box_msk = _check_calc_errs(fwhms, rminarc)
     # Check for errors

### 2014-10-08 manuscript/paper-tycho.tex
B-damping debug, fits; cull Kepler regs
Testing/debugging B-damping calculations manually
Set up preliminary fits to explore parameter space
Cull Kepler regions-3 and run through pipeline

@@
 reveal more about rim morphology and perhaps even temporal variation over a 10+
-year baseline.
+year baseline (compare to \citet{katsuda2010-sn1006}).
 
@@
 
-%\clearpage
-
 % ========
@@
 % ========
-%\appendix
-%
-%\setcounter{table}{0}
-%\renewcommand{\thetable}{A\arabic{table}}
-%\setcounter{figure}{0}
-%\renewcommand{\thefigure}{A\arabic{figure}}
+\clearpage
+\appendix
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
+
+\section{Derivation for synchrotron roll-off and diffusion}
+
+% This is NOT optimized for 2-column layout
+
+Assume that a DSA model explains the observed e-/synchrotron spectra
+cut-off/roll-off.  We estimate e- cut-off energy by equating
+$\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
+\[
+    \frac{3r}{r-1} \frac{r D_d + D_u}{v_s^2} = \frac{1}{b B^2 \Ecut}
+\]
+(\emph{I don't know if this equality was designed to exactly obtain the electron
+cutoff energy, or is just a rough/scaling relation -- pull up Drury (1983) to
+check this})
+Following through the arguments/assumptions in Parizot et al. (2006) yields
+(using $13.3 \unit{erg} = 8.3 \unit{TeV}$):
+\[
+    \Ecut =
+        \left( 13.3 \unit{erg} \right)^{\frac{2}{1+\mu}}
+        \left( \frac{B_0}{100 \muG} \right)^{-\frac{1}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm\;s^{-1}}} \right)^{\frac{2}{1+\mu}}
+        \eta^{-\frac{1}{1+\mu}}
+\]
+Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
+invoking the delta function assumption $\nu_{\mt{cut}} = c_m \Ecut^2 B$ with
+$c_m = 1.822 \times 10^{18}$.
+(\emph{Again, I don't know if this is an equality or just a scaling.  We'd need
+to relate the electron spectrum cut-off to the derived synchrotron spectrum
+cut-off, as is done (I think) by Zirakashvili and Aharonian (2007).})
+\[
+    \nu_{\mt{cut}} = c_m
+        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \eta^{-\frac{2}{1+\mu}}
+\]
+In the case of $\mu = 1$ this yields:
+\[
+    \nu_{\mt{cut}} = (0.133 \unit{keV} / h)
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{2}
+        \eta^{-1}
+\]
+For $\mu \neq 1$ this is no longer independent of magnetic field.  But,
+there is hope.  Rewrite this in terms of $\eta_2$ using
+$\eta = \eta_2 E_2^{1-\mu}$ and write:
+\[
+    \nu_{\mt{cut}} = c_m
+        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( E_2 \right)^{-\frac{2(1-\mu)}{1+\mu}}
+        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
+\]
+With $E_2 = \left( (2 \unit{keV}/h) / (c_m B) \right)^{1/2}$, or
+$E_2 = \left( 0.2657 \unit{erg^2\;G} / B \right)^{1/2}$, we obtain:
+\[
+    \nu_{\mt{cut}} = c_m
+        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( \frac{0.2657 \unit{erg^2\;G}}{B} \right)^{-\frac{1-\mu}{1+\mu}}
+        \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
+\]
+And, the magnetic field terms cancel!  Hey presto.
+Our final usable result is:
+\[
+    \nu_{\mt{cut}} = c_m
+        \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( 0.2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
+        \left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
+\]
 

### 2014-10-08 code/models/models_exec.py

@@ -135,22 +135,13 @@ class Fitter(object):
     # Wrappers for fitting routines
     # -----------------------------
 
-    def fitter_full(self, mu, **kwargs):
-        """Full model fit (see models.full_fit for available **kwargs)"""
-        return models.full_fit(self.snr, self.kevs, self.data, self.eps,
-                               mu, **kwargs)
-
-    def fitter_simp(self, mu, **kwargs):
-        """Simple model fit (see models.simple_fit for available **kwargs)"""
-        return models.simple_fit(self.snr, self.kevs, self.data, self.eps,
-                                 mu, **kwargs)
-
     def get_fit(self, mu, appr, **kwargs):
         """Simple or full fit + manual 1-sigma errors
         **kwargs passed to models.full_fit, if appr='full'
         In particular, kws include: model_kws, method, epsfcn, maxfev, etc.
 
         Here, I specifically disable redchi-scaling for the covar matrix
+        unless specified otherwise (use kwarg 'scale_covar')
         """
         if 'scale_covar' not in kwargs:
             kwargs['scale_covar'] = False
@@ -158,7 +149,8 @@ class Fitter(object):
         self._vprint('Best {} fit, mu = {}'.format(appr, mu))
 
         if appr == 'simp':
-            res = self.fitter_simp(mu, **kwargs)
+            res = models.simple_fit(self.snr, self.kevs, self.data, self.eps,
+                                    mu, **kwargs)
 
         elif appr == 'full':
 
@@ -189,7 +181,8 @@ class Fitter(object):
             self._vprint('Initial guesses:',
                          'eta2 = {:0.3f},'.format(kwargs['eta2']),
                          'B0 = {:0.3f}'.format(kwargs['B0']*1e6))
-            res = self.fitter_full(mu, **kwargs)
+            res = models.full_fit(self.snr, self.kevs, self.data, self.eps,
+                                  mu, **kwargs)
 
         else:
             raise Exception('Invalid model choice')

### 2014-10-08 code/models/models_exec_test.py

@@ -23,7 +23,7 @@ import snr_catalog as snrcat
 # SN 1006, test data
 # ==================
 
-KEVS = np.array([0.7, 1.0, 2.0]) 
+KEVS = np.array([0.7, 1.0, 2.0])
 DATA = np.array([35.5, 31.94, 25.34])
 EPS = np.array([1.73, .97, 1.71])
 
@@ -86,7 +86,7 @@ class TestSimpModelErrorsSN1006(object):
             dstr = ('Simple fit params agree w/ Sean to min(10%,error); '
                     'SN 1006, mu={:0.2f}'.format(mu))
 
-            res = self.fobj.fitter_simp(mu)
+            res = self.fobj.get_fit(mu, 'simp')
             B0 = res.params['B0'].value
             eta2 = res.params['eta2'].value
 
@@ -104,7 +104,7 @@ class TestSimpModelErrorsSN1006(object):
     def test_fit_errors(self):
         """Simple fit: check best-fit errors correspond to d(chisqr) of +1.
         Rather poor design...
-        
+
         need res, pstr to do everything
         need ci_val, dchisqr, chisqr_best for assertions"""
 
@@ -122,8 +122,8 @@ class TestSimpModelErrorsSN1006(object):
             aeq_(x2, x_true)
 
         for mu in TAB_7:
-            
-            res = self.fobj.fitter_simp(mu)
+
+            res = self.fobj.get_fit(mu, 'simp')
             chisqr_best = res.chisqr
             ci_dict = self.fobj.get_errs(res, 'simp', method='manual',
                                          ci_vals=(0.683,))

### 2014-10-08 code/spectra/mergespectra.sh

@@ -15,13 +15,13 @@ then
 fi
 
 # Tycho's SNR, Hughes 2007
-obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
-wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
-       0.053847516 0.03258367 0.04726812 0.056013404)
+#obsids=(10093 10094 10095 10096 10097 10902 10903 10904 10906)
+#wghts=(0.1612156 0.1225565 0.2361635 0.1440111 0.1463404 \
+#       0.053847516 0.03258367 0.04726812 0.056013404)
 
 # Kepler's SNR, Reynolds 2006
-#obsids=(6714 6715 6716 6717 6718 7366)
-#wghts=(0.21297096 0.21473875 0.21324085 0.14413527 0.14547123 0.06944295)
+obsids=(6714 6715 6716 6717 6718 7366)
+wghts=(0.21297096 0.21473875 0.21324085 0.14413527 0.14547123 0.06944295)
 
 # Check number of regions to process
 nregs=`ls -l ${1}_${obsids[0]}_src*.pi | wc -l`

### 2014-10-11 manuscript/paper-tycho.tex
Tycho/SN1006 resolution errs, run B-damp tables
Check errors on single e- synchrotron emissivity table (fglists.dat),
e- distribution integrals, etc. New single e- table (fglists_mod.dat),
change several computation resolutions.
Change Tycho e- spectrum index.
Modify B-damping table set-up, start running.

@@
 
-% TODO Come back after checking Pacholczyk resolution
 As the full model must be numerically solved, its predicted rim widths are
@@
 radial coordinate, line-of-sight coordinate, electron distribution, Green's
-function integrals).  We chose our integration resolutions such that the
-fractional error in model FWHMs associated with halving/doubling integration
+function integrals).  We chose integration resolutions such that the
+fractional error in model FWHMs associated with halving or doubling integration
 resolution is less than $1\%$ for the parameter space relevant to our
-filaments.
+filaments (up to $\eta_2 = 10^3$ for loss-limited model; up to $\eta_2 = 10$
+for magnetic damping model).  In our error analysis, the maximum resolution
+errors in a small sample of parameter space are typically $0.1$--$1\%$,
+but mean and median errors are typically an order of magnitude smaller.
 

### 2014-10-11 code/models/FullEfflength_mod.f

@@ -36,12 +36,12 @@
           integer i
 
           ! Common block
-          double precision xex(100), fex(100)
+          double precision xex(200), fex(200)
           integer ir
           common /xrays/ xex, fex, ir
 
           ! Load common block first
-          call readfglists()
+          call readfglists('fglists.dat')
 
           print *, 'Enter B0'
           read *, B0            ! Gauss
@@ -82,13 +82,13 @@
      &                          5d0*1.d8, 5d0*1.d8/4d0, 2.96d19, 900d0,
      &                          2d0*0.6d0+1d0, rminarcarray, 1,
      &                          1000, 400, 500,
-     &                          1, 0.005d0, 5d-6)
+     &                          1, 0.005d0, 5d-6, 200, 50)
           elseif (snrflag.eq.1) then
             call Fullefflengthsub(kevs, inumax, widtharc, B0, eta2, mu,
      &                            4.7d0*1.d8, 4.7d0*1.d8/4d0, 1.077d19,
      &                            240d0, 2d0*0.65d0+1d0, rminarcarray,
      &                            1, 400, 100,500,
-     &                            0, 0.05d0, 5d-6)
+     &                            0, 0.05d0, 5d-6, 200, 50)
           endif
 
           do i = 1, inumax
@@ -126,7 +126,7 @@
       subroutine Fullefflengthsub(kevs, inumax, widtharc, B0, eta2, mu,
      &                            vs, v0, rs, rsarc, s, rminarc, icut,
      &                            irmax, iradmax, ixmax,
-     &                            idamp, ab, Bmin)
+     &                            idamp, ab, Bmin, itmax, inmax)
           implicit none
           ! Input parameters (widtharc is for output)
           integer inumax
@@ -136,7 +136,7 @@
           double precision vs, v0, rs, rsarc, s
           double precision rminarc(inumax)
           ! Settings
-          integer irmax, ixmax, iradmax
+          integer irmax, ixmax, iradmax, itmax, inmax
           integer icut, idamp
 
           ! "Fundamental" constants
@@ -145,7 +145,7 @@
           double precision ecut, eta  ! Derived constants
           double precision rmin(inumax) ! From rminarc(inumax)
           ! Emissivity data for common block
-          double precision xex(100), fex(100)
+          double precision xex(200), fex(200)
           integer ir  ! Should label as ifmax or so, to be consistent
 
[…]

### 2014-10-11 code/models/FullEfflength_port.py

@@ -22,7 +22,6 @@ import scipy.integrate as spint
 #import fullmodel_recompile
 #fullmodel_recompile.main()
 import fullmodel
-fullmodel.readfglists()  # !! important
 import snr_catalog as snrcat
 
 # Constants
@@ -36,24 +35,29 @@ def main():
     #B0 = raw_input('Enter B0 (Gauss): ')
     #eta2 = raw_input('Enter eta2: ')
     #mu = raw_input('Enter mu: ')
-    B0 = 40e-6
-    eta2 = 1
+    B0 = 200e-6
+    eta2 = 1.0
     mu = 1.0
 
-    irmax, iradmax, ixmax = 200, 400, 500
+    irmax, iradmax, ixmax = 200, 100, 500
     print 'irmax, iradmax, ixmax = {},{},{}'.format(irmax, iradmax, ixmax)
 
-    kevs = np.array([1., 2., 4.])
+    kevs = np.array([0.7, 1., 2., 3., 4.5])
     rminarc = 20. * np.ones(len(kevs))
 
-    #fwhms = fefflen(kevs, B0, eta2, mu, 4.52e8, 4.52e8/4, 1.077e19, 240.,
-    #                2*0.65+1, rminarc, True, irmax, iradmax, ixmax)  # Tycho
-    fwhms = fefflen(kevs, B0, eta2, mu, 5e8, 5e8/4., 2.96e19, 900.,
-                    2*0.6+1, rminarc, True, irmax, iradmax, ixmax,
-                    True, 0.001, 5e-6)  # SN 1006 with damping
-    print 'rminarc = {}'.format(rminarc)
-    for en, fwhm in zip(kevs, fwhms):
-        print '{:0.2f} keV: {:0.5f}'.format(en, fwhm)
+    # Tycho
+    fwhms = fefflen(kevs, B0, eta2, mu, 4.52e8, 4.52e8/4, 1.077e19, 240.,
+                    2*0.58+1, rminarc, True, irmax, iradmax, ixmax,
+                    False, 0.001, 5e-6, 'fglists_mod.dat',
+                    200, 50, 2000)
+    # SN 1006 with damping
+    #fwhms = fefflen(kevs, B0, eta2, mu, 5e8, 5e8/4., 2.96e19, 900.,
+    #                2*0.6+1, rminarc, True, irmax, iradmax, ixmax,
+    #                False, 0.001, 5e-6, 'fglists_mod.dat',
+    #                200, 50, 2000)
[…]

### 2014-10-11 code/models/models.py

@@ -142,7 +142,9 @@ def maketab(snr, kevs, data_min, data_max, mu_vals, eta2_vals, n_B0,
 
             # Do the heavy work of computing FWHMs for many B0 values
             eta2_dict[eta2] = maketab_gridB0(snr, p, kevs, data_min, data_max,
-                                             n_B0, f_B0_init, f_B0_step,
+                                             n_B0,
+                                             f_B0_init = f_B0_init,
+                                             f_B0_step = f_B0_step,
                                              **kwargs)
 
             # Save data regularly, but keep tabulating if save fails...
@@ -254,10 +256,18 @@ def maketab_gridB0(snr, pars, kevs, fwhms_min, fwhms_max, n_tot,
     fwhms_all = fwhms_all[uniqsrt]
     r_all = r_all[uniqsrt]
 
+    # Select only FWHMs without rminarc errors for the "filling in FWHM range"
+    # step, so that it does not get stuck at the discontinuity in r-values
+    msk = np.all(fwhms_all < snr.rsarc*0.99, axis=1)  # Collapse FWHMs
+    B0_all = B0_all[msk]
+    fwhms_all = fwhms_all[msk]
+    r_all = r_all[msk]
+
     # Fill in the gaps
     print 'Filling in FWHM range to achieve desired spacing'
     B0_all, fwhms_all, r_all = mind_the_gaps(B0_all, fwhms_all, r_all, dr,
                                              f_rscale)
+    print 'Computed FWHMS for {} values of B0'.format(len(B0_all))
 
     return B0_all, fwhms_all  # No longer need r-values
 
@@ -470,9 +480,11 @@ def simple_width(snr, kevs, mu, eta2, B0):
 # =============================
 # Input: params, kevs, snr, **kwargs; output: model FWHMs
 
+# TODO move various defaults into snr_catalog
 def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
     irmax=None, iradmax=None, ixmax=None, irad_adapt=True, irad_adapt_f=1.2,
-    idamp=False, damp_ab=0.05, damp_bmin=5.0e-6):
+    idamp=False, damp_ab=0.05, damp_bmin=5.0e-6, fgfname='fglists_mod.dat',
+    itmax=200, inmax=50, irhomax=2000):
     """Width function, wrapper for Python port of full model (equation 12)
 
     All **kwargs not specified (excepting verbose) are taken from snr object
[…]

### 2014-10-11 code/models/snr_catalog.py

@@ -88,7 +88,7 @@ def make_kepler():
     kepler.icut = True
     kepler.rminarc = 20  # Default rminarc, arcsec (remember w/ adaptive
                          # rminarc calculation, this isn't too important)
-    kepler.irmax = 400  # Currently unchanged from SN 1006
+    kepler.irmax = 200  # Currently unchanged from SN 1006
     kepler.iradmax = 100
     kepler.ixmax = 500
 
@@ -109,11 +109,10 @@ def make_tycho():
     tycho.dkpc = 3.0  # Distance to remnant in kpc (!)
     tycho.rsarc = 240  # Shock radius (arcsec) from Green's SNR catalog
                        # This is about right from image inspection.
-    tycho.s = 2.3  # e- spectrum index, 2.3 = 2*0.65 + 1;
-                   # 0.65 = radio spectral index
-                   # TODO this should be 2.16 = 2*0.58 + 1
-                   # following Sun et al. (2011)
-                   # I used 0.65 in all previous work from Kothes et al. (2006)
+    tycho.s = 2.16 # e- spectrum index, 2.16 = 2*0.58 + 1
+                   # 0.58 = radio spectral index from Sun et al. (2011)
+                   # also listed in Green's SNR catalog.
+                   # Before 2014 Oct 10 We used 0.65 from Kothes et al. (2006)
 
     tycho.vs = 3.6e8 * tycho.dkpc/2.3  # Average-ish shock velocity, cm/s
     # Mean of velocs from nonthermal regions, Williams et al. 2013
@@ -122,7 +121,7 @@ def make_tycho():
     # Model grid settings, resolutions
     tycho.icut = True
     tycho.rminarc = 20  # Default rminarc, arcsec
-    tycho.irmax = 400  # Currently unchanged from SN 1006
+    tycho.irmax = 200
     tycho.iradmax = 100
     tycho.ixmax = 500
 
@@ -151,7 +150,7 @@ def make_SN1006():
     # Model grid settings, resolutions
     sn1006.icut = True
     sn1006.rminarc = 60  # Default rminarc, arcsec
-    sn1006.irmax = 400
+    sn1006.irmax = 200
     sn1006.iradmax = 100
     sn1006.ixmax = 500
 

### 2014-10-11 code/models/tab_tycho_damping_20141010.py
Dwnstream spectra w/lines fit/excised
Update spectrum fitting code to handle both Si and S lines
Added new table with fit data (line energies/eqwidths) for manuscript

@@ -1,0 +1,92 @@
+"""
+Tabulate FWHMs for Tycho for various magnetic damping scale lengths
+Uses default shock velocity (3.6e8 * 3/2.3 = 4.696e8 cm/s ...)
+Uses default damping Bmin (5 microGauss)
+Using default rminarc
+
+151 eta2 values log-spaced between [0.01, 100] with 2x sampling in [0.1, 10].
+~50 B0 values (ask for 30), sampled to give ~linear spacing in FWHM widths
+
+data_min/data_max set to a bit smaller range than before
+
+`a_b` values I use are:
+
+    0.5,    0.05,   0.04,   0.03,
+    0.02,   0.01,   0.009,  0.008,
+    0.007,  0.006,  0.005,  0.004
+
+But, feed damping numbers into scripts as:
+
+    python tab_tycho_damping_141010.py  0.5   0.01   0.005
+    python tab_tycho_damping_141010.py  0.05  0.009  0.004
+    python tab_tycho_damping_141010.py  0.04  0.008  0.007
+    python tab_tycho_damping_141010.py  0.03  0.02   0.006
+
+to try to balance the load of calculations (I have gone diagonally in this
+table).
+
+
+Aaron Tran
+2014 October 10
+"""
+
+from __future__ import division
+
+import argparse
+from datetime import datetime
+import numpy as np
+
+import models
+import snr_catalog as snrcat
+
+# Numbers are generated from regions-4 with simple 2-exponential fit
+# Max observed FWHM for 0.7-1keV was 6.092
+# But I use 10 to be more consistent w/ general trend
+# (matches previous tables)
+TYCHO_KEVS = np.array([0.7, 1.0, 2.0, 3.0, 4.5])
+TYCHO_DATA_MIN = np.array([1.628, 1.685, 1.510, 1.465, 1.370])
+TYCHO_DATA_MAX = np.array([10.0, 8.866, 6.901, 7.508, 5.763])
+
+def main():
+    # Read damping length
+    parser = argparse.ArgumentParser(description='Table generator')
+    parser.add_argument('abvals', help='Damping lengths (%% of shock radius)',
+                        nargs='*')
+    args = parser.parse_args()
+    abvals = map(float, args.abvals)
+
+    # Set SNR parameters
+    snr = snrcat.make_tycho()
+
+    # Set data
+    kevs = TYCHO_KEVS
+    data_min = TYCHO_DATA_MIN / 1.1
+    data_max = TYCHO_DATA_MAX * 1.1
+
[…]

### 2014-10-13 manuscript/paper-tycho.tex
Dwnstream spectra w/lines fit/excised
Update spectrum fitting code to handle both Si and S lines
Added new table with fit data (line energies/eqwidths) for manuscript
Damping fit, mE LaTeX tables; SN1006 model tables
Nice tables for damping model fit outputs.
Generate FWHM tables for SN 1006 parameters

@@
 %\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
-\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
+%\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
+\documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 
+\begin{table*}
+    \footnotesize
+    \centering
+    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
+    \input{tab-spec-pt2.tex}
+\end{table*}
+
+% TODO add text explaining this table (!!!!!!!!!!!!!)
+
 Table~\ref{tab:spec} confirms that our region selections are practically free
@@
 
+\section{Best fit width-energy curve $m_\mt{E}$ values}
+
+\begin{table*}[ht]
+    \footnotesize
+    \centering
+    \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
+    \input{tab-fits-mE.tex}
+\end{table*}
+
+\clearpage
+\section{Magnetic damping best fit tables}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
+    \input{tab-fits-damp-f1.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
+    \input{tab-fits-damp-f2.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
+    \input{tab-fits-damp-f2-pt2.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
+    \input{tab-fits-damp-f3.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
+    \input{tab-fits-damp-f4.tex}
+\end{table*}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
+    \input{tab-fits-damp-f5.tex}
+\end{table*}
+
+\clearpage
 \section{Derivation for synchrotron roll-off and diffusion}
@@
 $\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
-\[
+\begin{equation}
     \frac{3r}{r-1} \frac{r D_d + D_u}{v_s^2} = \frac{1}{b B^2 \Ecut}
-\]
+\end{equation}
 (\emph{I don't know if this equality was designed to exactly obtain the electron
@@
 (using $13.3 \unit{erg} = 8.3 \unit{TeV}$):
-\[
+\begin{equation}
     \Ecut =
@@
         \eta^{-\frac{1}{1+\mu}}
-\]
+\end{equation}
 Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
@@
 cut-off, as is done (I think) by Zirakashvili and Aharonian (2007).})
-\[
+\begin{equation}
     \nu_{\mt{cut}} = c_m
@@
         \eta^{-\frac{2}{1+\mu}}
-\]
+\end{equation}
 In the case of $\mu = 1$ this yields:
-\[
+\begin{equation}
     \nu_{\mt{cut}} = (0.133 \unit{keV} / h)
@@
         \eta^{-1}
-\]
+\end{equation}
 For $\mu \neq 1$ this is no longer independent of magnetic field.  But,
@@
 Our final usable result is:
-\[
+\begin{equation}
     \nu_{\mt{cut}} = c_m
@@
         \left( \eta_2 \right)^{-\frac{2}{1+\mu}}
-\]
+\end{equation}
 

### 2014-10-13 code/models/tables/gen_scripts/tab_sn1006_damping_141013.py

@@ -1,6 +1,5 @@
 """
-Tabulate FWHMs for Tycho for various magnetic damping scale lengths
-Uses default shock velocity (3.6e8 * 3/2.3 = 4.696e8 cm/s ...)
+Tabulate FWHMs for SN1006 for various magnetic damping scale lengths
 Uses default damping Bmin (5 microGauss)
 Using default rminarc
 
@@ -17,17 +16,17 @@ data_min/data_max set to a bit smaller range than before
 
 But, feed damping numbers into scripts as:
 
-    python tab_tycho_damping_141010.py  0.5   0.01   0.005
-    python tab_tycho_damping_141010.py  0.05  0.009  0.004
-    python tab_tycho_damping_141010.py  0.04  0.008  0.007
-    python tab_tycho_damping_141010.py  0.03  0.02   0.006
+    python ....py  0.5   0.01   0.005
+    python ....py  0.05  0.009  0.004
+    python ....py  0.04  0.008  0.007
+    python ....py  0.03  0.02   0.006
 
 to try to balance the load of calculations (I have gone diagonally in this
 table).
 
 
 Aaron Tran
-2014 October 10
+2014 October 13
 """
 
 from __future__ import division
@@ -39,13 +38,14 @@ import numpy as np
 import models
 import snr_catalog as snrcat
 
-# Numbers are generated from regions-4 with simple 2-exponential fit
-# Max observed FWHM for 0.7-1keV was 6.092
-# But I use 10 to be more consistent w/ general trend
-# (matches previous tables)
-TYCHO_KEVS = np.array([0.7, 1.0, 2.0, 3.0, 4.5])
-TYCHO_DATA_MIN = np.array([1.628, 1.685, 1.510, 1.465, 1.370])
-TYCHO_DATA_MAX = np.array([10.0, 8.866, 6.901, 7.508, 5.763])
+# SN 1006 numbers (from Sean's script, originally)
+SN1006_KEVS = np.array([0.7, 1.0, 2.0])
+SN1006_DATA = {}
+SN1006_DATA[1] = np.array([35.5, 31.94, 25.34]), np.array([1.73, .97, 1.71])
+SN1006_DATA[2] = np.array([23.02, 17.46, 15.3]), np.array([.35,.139, .559])
+SN1006_DATA[3] = np.array([49.14, 42.76,29.34]), np.array([1.5, .718, .767])
+SN1006_DATA[4] = np.array([29, 23.9, 16.6]), np.array([.9, .39, .45])
[…]

### 2014-10-21 manuscript/paper-tycho.tex
SN1006 damping fits, minor notes on ms text
Damped fit tables/plots, srcutlog, paper updates
Code for plots/tables showing damped/loss-limited fits
Add XSPEC local model srcutlog from Brian
Clean up old/unused tables
Generating script for Tycho tables with smaller ab, Bmin

@@
 \begin{abstract}
-\note[Aaron]{Clone of AAS abstract}
+\note[Aaron]{Modified from AAS abstract - first pass update}
 Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
@@
 strong magnetic field amplification.  But, magnetic field damping immediately
-behind the shock could produce similarly thin rims.  Synchrotron loss-limited
-rim widths should decrease with energy whereas damping limited rims should be
-relatively energy-independent.  To discriminate between models, we measured rim
-widths around Tycho's supernova remnant in 5 energy bands using an archival
-$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
-favoring loss-limited radiation over magnetic damping and corroborating similar
-observations in the remnant of SN 1006. Observed widths are best fit by
-electron transport models requiring amplified magnetic fields of
+behind the shock could produce similarly thin rims.  We measured rim widths
+around Tycho's supernova remnant in 5 energy bands using an archival $750
+\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
+energy and are well-described by either loss-limited or magnetically damped
+models.  We are unable to distinguish between scenarios, as models for rim
+widths incorporating electron cut-offs both reproduce the observed rim
+drop-offs.  The best loss-limited fits require amplified magnetic fields of
 $\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
-1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
-Non-negligible diffusion results in some degeneracy between magnetic field
-strength and diffusion coefficient in setting observed rim widths, but strong
-magnetic fields are required for all measurements.  A different approach may be
-needed to better constrain diffusion at supernova remnant shocks.
+1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR, whereas
+magnetic damping fits permit magnetic fields of $\abt 10$--$300 \muG$ and
+comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
+Non-negligible diffusion coefficients, magnetic field strengths, and magnetic
+damping lengthscales are somewhat degenerate in setting observed rim widths and
+drop-offs.  A different approach will be needed to determine the presence of
+magnetic damping downstream of supernova remnant shocks.
 \end{abstract}
@@
 off downstream, producing a shell-like morphology with bright X-ray and radio
-rims/filaments due to line-of-sight projection \citep{koyama1995}.  Although
-synchrotron emission due to accelerated electrons does not imply acceleration
-of an unseen hadronic component, the prevailing theory of diffusive shock
-acceleration (DSA) should operate on both protons and electrons.  Observations
-of these synchrotron rims, with other lines of direct and indirect evidence,
-have built a case for hadron and lepton acceleration up to $\unit{PeV}$
-energies in young supernova remnants \citep{uchiyama2007, aharonian2004,
-acero2010, ackermann2013}.  Efficient hadron acceleration in supernova remnant
-shocks is a prime candidate source for galactic cosmic rays up to the
-cosmic ray spectrum's ``knee'' \citep{vink2012}.
-\note[Aaron]{the discussion of hadronic acceleration isn't really relevant,
-just background information}
+rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
+relatively strong synchrotron radiation, in conjunction with multiwavelength
+spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
+ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
+suggests that electrons are accelerated to PeV energies in young SNRs.
+Although synchrotron emission due to accelerated electrons does not imply
+acceleration of an unseen hadronic component, the prevailing theory of
+diffusive shock acceleration (DSA) should operate on both protons and
+electrons.  Efficient hadron acceleration in supernova remnant shocks is a
+prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
+``knee'' \citep{vink2012}.  \note[Aaron]{the discussion of hadronic
+acceleration isn't really relevant, just background information}
 
@@
 downstream of the shock, so that electrons may not radiate as efficiently and
-thin rims would reflect the spatial structure of the field, rather than
-efficient particle acceleration (and losses) and/or efficient synchrotron
-cooling \citep{pohl2005}.
+thin rims reflect the spatial structure of the field rather than efficient
+particle acceleration (and losses) and/or efficient synchrotron cooling
+\citep{pohl2005}.
 
@@
 dominates.  Magnetic damping, if at a length scale comparable to filament
-widths, predicts comparatively energy-independent rim widths -- intuitively, if
-the magnetic field turns off, synchrotron radiation turns off regardless of
+widths, also favors more energy-insensitive rim widths -- intuitively, if the
+magnetic field turns off, synchrotron radiation turns off regardless of
 electron energy.
@@
 Our procedure closely follows that of \citetalias{ressler2014}.
-We first briefly review relevant transport models which fully account for
-electron advection and diffusion with continuous synchrotron losses, as
-considered by, e.g., \citet[and references therein]{berezhko2004} and
-\citet{rettig2012}.  We selected and measured rim widths at several locations
-around Tycho's forward shock, verifying that selected rims are free of thermal
-line emission.  Using our model for particle transport (with DSA included, to
-first order, in a simple exponentially cut-off injected electron spectrum), we
-obtain estimates on magnetic field strength and diffusion coefficient
-magnitude. We discuss the implications of our model fit results for
-particle transport in Tycho, despite a significant degeneracy between
-diffusion and synchrotron losses when diffusion is non-negligible.
+We first introduce our transport models for electron advection and diffusion
+with continuous synchrotron losses.  We selected and measured rim widths at
+several locations around Tycho's forward shock, verifying that selected rims
+are free of thermal line emission.  Using our models for particle transport
+(with DSA included, to first order, in a simple exponentially cut-off injected
+electron spectrum), we predict width-energy dependence in the loss-limited and
+magnetic damping scenarios to obtain estimates on magnetic field strength and
+diffusion coefficient magnitude.  We discuss degeneracy in our model fits and
+the implications for future studies of young supernova remnant shocks.
 
@@
 
+% Could just discuss one model...
 We consider two particle transport models that we fit to measurements of
 Tycho's thin rim widths.  We measure the rim full widths at half maximum
-(FWHMs) (Section~\ref{sec:fwhms}) and use the measurements to directly assess
-width-energy dependence.  The measurements are also fit to the transport
-models' predictions of rim FWHMs at multiple photon energies.  The models
-accept three free parameters: magnetic field strength $B_0$, a scaled diffusion
-coefficient $\eta_2$, and a diffusion-energy scaling exponent $\mu$.
+(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
+model predictions of rim FWHMs at multiple photon energies, for various input
+parameters.  The models accept four free parameters: magnetic field strength
+$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
+exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
+length).
 
@@
 % TODO define ALL symbols, synchrotron constants, etc
-\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
-tack in deriving the relevant transport equations, drawing specifically from
-plasma physics / DSA assumptions -- I suppose that much material is not
-relevant or condensed into our diffusion coefficient $D$ (w/ stated Bohm
-diffusion).  Is na\"ively citing generalized ``transport'' is sufficient here?
-E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
-neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
-would not arise out of our equations as stated.
-See, e.g., equation (9) of \citet{skilling1975}.}
 % Transport fundamentals
@@
 No assumptions on the injected electron source term are necessary.
-\citet{parizot2006} employed this model to derive estimates of magnetic fields,
-diffusion coefficients, and electron spectrum cut-offs for several historical
-SNRs.  Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f
-\propto \exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim
-FWHM predicted by equation~\eqref{eq:simp-mod} is:
+\citet{parizot2006} employed this model to estimate magnetic fields, diffusion
+coefficients, and electron spectrum cut-offs for several historical SNRs.
+Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
+\exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim FWHM
+predicted by equation~\eqref{eq:simp-mod} is:
 \begin{equation} \label{eq:simp-fwhm}
@@
 \citet{morlino2010}, \citet{rettig2012}, and references therein.
-\citet{zirakashvili2007} have derived a different electron spectrum with a
-steeper $\exp\left(- \left(E/\Ecut\right)^2\right)$ cut-off, but we follow
-\citetalias{ressler2014} in using $E^{-s} e^{-E/\Ecut}$ for conceptual
-simplicity.  The cut-off energy is determined by the diffusion coefficient $D$,
+The cut-off energy is determined by the diffusion coefficient $D$,
 which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
@@
 dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
-particle energy $E_h$.  This energy $E_h$ may be related to the emitted
-synchrotron photons by taking the $\delta$-function approximation that an
-electron of energy $E$ radiates at a singular frequency $\nu \propto E^2 B$ in
-a magnetic field.  Note that $\eta_h$ and $\eta$ are related as
+particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are related as
 $\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
@@
 model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
-depends on magnetic field $B$ and may vary within the remnant, tying $\eta_h$
-to a fixed observation energy gives a convenient and intuitive sense of
-diffusion strength regardless of the underlying electron energies.
-We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.
+varies with magnetic field $B$ as $E_2 \propto B^{-1/2}$ and may vary within
+the remnant, tying $\eta_h$ to a fixed observation energy gives a convenient
+and intuitive sense of diffusion strength regardless of the underlying electron
+energies.  We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.
 
@@
 adapted from \citet{parizot2006} is given as:
-\begin{align}
+\begin{align} \label{eq:ecut}
     \Ecut =
@@
 \end{align}
-Note that this expression implicitly assumes (1) a strong shock with
-compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
-downstream; see \citet{parizot2006} for a full derivation.
-
-As the electron cut-off imposes a roll-off on SNR synchrotron flux,
-estimates of the synchrotron roll-off frequency may provide an independent
-observable to characterize shock conditions.
-\note[Aaron]{todo: explore this?} % TODO FILL IN LATER -- NOT IMPORTANT NOW
-\citet{miceli2013, yamazaki2014} looked at the synchrotron roll-off as a
-diagnostic for electron spectrum cut-off behavior (whether loss or age limited)
-and also infer various characteristics (particularly, $\eta > 1$ in SN 1006).
-\citet{miceli2014-cloud} use azimuthal variation in synchrotron cut-off, with
-other lines of evidence, to argue for the presence of a cloud interacting w/
-the SW limb of SN 1006.
-
-Speculation: could cloud interaction could be related to the sub-Bohm diffusion
-observation in Sean's Filament 4?  The filament has many profiles, and looking
-at Sean's data it looks like all the selections show a consistently strong drop
-in FWHM.  \citet{miceli2013} argue that the concave distortion possibly
-associated with the cloud is linked to a dip in synchrotron cut-off energies,
-which they explain as being tied to a drop in shock velocity at the
-indentation, due to the cloud.  If shock velocities are depressed, would more
-diffusion / weaker B fields be necessary to explain the observed rim widths?
-But we must still account for the quite strong width-energy drop-off!
-
+\citet{parizot2006} derive equation~\eqref{eq:ecut} in the case $\mu=1$
+assuming a strong shock with compression ratio 4 and isotropic magnetic
+turbulence on both sides of the shock.
+
+As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
+flux, the synchrotron roll-off frequency may provide an independent observable
+to estimate shock diffusion and is given by:
+\begin{align} \label{eq:rolloff}
+    \nu_{\mt{cut}} =
+        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
+        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
+        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
+        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
+\end{align}
+In particular, this equation is independent of magnetic field $B$ for all
+values of $\mu$ (but recall that the specific electron energies associated with
+$\eta_2$ will depend on $B$).
+
+% Magnetic damping
 \subsection{Magnetic damping}
 
-% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
-We also consider (not really) a magnetically damped field of form
+We also consider a magnetically damped field of form
 \begin{equation}
@@
 Again, \citetalias{ressler2014} detail how to integrate a damped field into the
-full model solutions.
-
-(DRAFT) We currently do not present model fits with magnetic damping, although
-in principle they are doable.  Set up the calculation w/ a range of scale
-lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
-for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?
+full model solutions to equation~\eqref{eq:full-mod}.
+
+%(DRAFT) We currently do not present model fits with magnetic damping, although
+%in principle they are doable.  Set up the calculation w/ a range of scale
+%lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
+%for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?
 
@@
 \note[Aaron]{elaborate after filling in preceding section}
+NOOOOOOOOOOOOOPE.
 
@@
 
-% KEEP REGION NUMBER UPDATED
+% NOTE keep region/filament numbering up to date
 We selected 20 regions in 5 distinct filaments around Tycho's shock
@@
     labels (1, 16) indicate region selections shown in
-    Figures~\ref{fig:spec},~\ref{fig:profiles}.
-    \note[Aaron]{Figure colors inverted to save ink.} \label{fig:snr}}
+    Figures~\ref{fig:spec},~\ref{fig:profiles}.  Filament 1: Regions 1--3,
+    filament 2: regions 4--10, filament 3: regions 11-13, filament 4:
+    regions 14--17, filament 5, regions 18--20.
+    \label{fig:snr}}
 \end{figure}
@@
 \begin{figure*}
-    \plotone{figures/fig-specs_01.pdf}
-    \plotone{figures/fig-specs_16.pdf}
-    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
+    \plotone{figures/spec_01.pdf}
+    \plotone{figures/spec_16.pdf}
+    \caption{Spectra and fits from Regions 1 (top) and 14 (bottom) show varying
     rim morphology and example of rim where 0.7--1 keV peak could not be fit.
@@
 
+% Upstream spectra and numbers
+% NOTE keep stated ranges of spectral indices, column densities up to date
 We fit spectra from each region's upstream and downstream sections to an
@@
 parameters and reduced $\chi^2$ values for all regions.  Spectra from thin rims
-(upstream sections) are well-fit by the power law model alone; spectra from
-sections downstream of the rims are generally poorly-fit, reflecting thermal
-contamination primarily from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line
-emission at $1.85$ and $2.45$ keV.  Our best-fit photon indices ($2.4$--$3$)
-and column densities ($0.6$--$0.8 \times 10^{22} \unit{cm^{-2}}$) from upstream
-spectra are consistent with previous spectral fits to Tycho's nonthermal rims
-\citep{hwang2002, cassam-chenai2007}.
-% NOTE keep stated ranges of spectral indices, column densities up to date
-% NOTE keep example region numbers up to date
-
-% NOTE keep region numbers updated (in discussion of good/bad downstream spectra)
+(upstream sections) are well-fit by the power law model alone; the best-fit
+photon indices ($2.4$--$3$) and column densities ($0.6$--$0.8 \times 10^{22}
+\unit{cm^{-2}}$) are consistent with previous spectral fits to Tycho's
+nonthermal rims \citep{hwang2002, cassam-chenai2007}.
+
+% Downstream spectra and numbers
+% NOTE keep stated ranges, region numbers up to date
+% THIS IGNORES THE REGION 19 SPECTRUM FIT (!!)
+Spectra from sections downstream of the rims are generally poorly-fit,
+reflecting thermal contamination from \ion{Si}{13} and \ion{S}{15} He$\alpha$
+line emission at $1.85$ and $2.45$ keV.  To confirm that thermal emission is
+dominated by these two lines near the shock, we also performed fits to
+downstream spectra with both lines excised ($1.7$--$2.0 \unit{keV}$,
+$2.3$--$2.6 \unit{keV}$ removed) or with both lines fitted to Gaussian
+profiles.  When the lines are excised from our fits, we obtain
+$\chi^2_{\mt{red}}$ values between $0.8$--$1.4$ excepting only Regions 5 and 20
+with $\chi^2_{\mt{red}} \sim 1.8$ due to the presence of many additional lines.
+When lines are fitted to Gaussian profiles, we find $\chi^2_{\mt{red}}$ values
+$0.83$--$1.22$, again excepting Regions 5, 20 which have $\chi^2_{\mt{red}}
+\sim 1.6$.  In both fits (lines excised or modeled), we find somewhat smaller
+best fit column densities ($0.32$--$0.74 \times 10^{22} \unit{cm^{-1}}$),
+but best fit photon indices ($2.52$--$3.05$) are consistent with those of the
+upstream spectra, confirming that the same synchrotron continuum may be
+recovered from beneath thermal line emission.
+
 \begin{table}
@@
 
-\begin{table*}
-    \footnotesize
-    \centering
-    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
-    \input{tab-spec-pt2.tex}
-\end{table*}
-
-% TODO add text explaining this table (!!!!!!!!!!!!!)
-
-Table~\ref{tab:spec} confirms that our region selections are practically free
-of thermal line emission, as already suggested by visual inspection
+% This table is still useful, just to look at the parameters
+% (or to send around to collaborators, if needed)
+%\begin{table*}
+%    \footnotesize
+%    \centering
+%    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
+%    \input{tab-spec-pt2.tex}
+%\end{table*}
+
+Our spectral fitting confirms that all selected region are practically free of
+thermal line emission, as already suggested by visual inspection
 (Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2 \unit{keV}$ photons
@@
 
-\begin{figure*}[ht]
-    \plotone{figures/fig-profiles_01.pdf}
-    \plotone{figures/fig-profiles_16.pdf}
+\begin{figure*}%[ht]
+    \plotone{figures/prfs_01.pdf}
+    \plotone{figures/prfs_16.pdf}
     \caption{Best fit profiles with measured FWHMs demarcated for each energy
-        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
+        band in Region 1 (top) and Region 14 (bottom).  Energy bands increase
         from left to right.  Data points in red were excluded from profile
@@
 for magnetic damping model).  In our error analysis, the maximum resolution
-errors in a small sample of parameter space are typically $0.1$--$1\%$,
-but mean and median errors are typically an order of magnitude smaller.
+errors in a sample of parameter space are typically $0.1$--$1\%$, but mean and
+median errors are typically an order of magnitude smaller that maximum errors.
 
@@
 
-\begin{table*}[ht]
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fit for individual regions, Filaments 1--2.
+%    \label{tab:fits}}
+%    \input{tab-fits-all.tex}
+%\end{table*}
+%
+%\begin{table*}[ht]
+%    \tiny
+%    \centering
+%    \caption{Full model best fits for individual regions, Filaments 3--5.
+%    \label{tab:fits-pt2}}
+%    \input{tab-fits-all-pt2.tex}
+%\end{table*}
+
+% Example loss-limited fits
+\begin{table}[ht]
+    \scriptsize
+    \centering
+    \caption{Best loss-limited fits for Regions 1, 16
+    \label{tab:fits-loss-ex}}
+    \input{tab-fits-loss-ex.tex}
+\end{table}
+
+% Example damping fits
+\begin{table}[ht]
+    \scriptsize
+    \centering
+    \caption{Best magnetic damping fits for Regions 1, 16
+    \label{tab:fits-damp-ex}}
+    \input{tab-fits-damp-ex.tex}
+\end{table}
+
+% NOTE: USE CHISQR HERE, NOT REDUCED CHI SQUARED.
+% Justification: comparing fits with parameters free/frozen
+% between the following two tables.
+
+% Fit results for ALL regions, mu = 1, loss-limited and damped
+\begin{table}[ht]
     \tiny
     \centering
-    \caption{Full model best fit for individual regions, Filaments 1--2.
-    \label{tab:fits}}
-    \input{tab-fits-all.tex}
-\end{table*}
-
-\begin{table*}[ht]
-    \tiny
-    \centering
-    \caption{Full model best fits for individual regions, Filaments 3--5.
-    \label{tab:fits-pt2}}
-    \input{tab-fits-all-pt2.tex}
-\end{table*}
-
-% NOTE need better subplot display in final version, if we keep this
-%\begin{figure}[ht]
-%    \centering
-%    %\epsscale{0.45}  % For manuscript layout only!
-%    \plottwo{figures/fits-sep13/reg01.png}{figures/fits-sep13/reg02.png} \\
-%    \plottwo{figures/fits-sep13/reg03.png}{figures/fits-sep13/reg04.png} \\
-%    \plottwo{figures/fits-sep13/reg05.png}{figures/fits-sep13/reg06.png} \\
-%    \plottwo{figures/fits-sep13/reg07.png}{figures/fits-sep13/reg08.png} \\
-%    \plottwo{figures/fits-sep13/reg09.png}{figures/fits-sep13/reg10.png} \\
-%    \plottwo{figures/fits-sep13/reg11.png}{figures/fits-sep13/reg12.png} \\
-%    \plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
-%    \caption{Fitted full model widths as a function of energy for all regions,
-%    with measured data; best fit parameters are given in
-%    Tables~\ref{tab:fits},~\ref{tab:fits-pt2}.  Plots are ordered by region
-%    number.  NOTE: figures for Regions 9, 11 are incorrect.}
-%    \label{fig:fits-all}
-%\end{figure}
+    \caption{Best model fits with magnetic damping, $\mu = 1$
+    \label{tab:fits-damp}}
+    \input{tab-fits-all-summary.tex}
+\end{table}
+
+% TODO LIST DOFs in FINAL VERSION
+
+% As above but with eta2=1 fixed!
+\begin{table}[ht]
+    \scriptsize
+    \centering
+    \caption{Best model fits with magnetic damping, $\mu = \eta_2 = 1$
+    \label{tab:fits-damp}}
+    \input{tab-fits-all-summary-eta2one.tex}
+\end{table}
+
+% TODO LIST DOFs in FINAL VERSION
 
@@
 
-For the rest of our results and discussion, we consider only full model
-fit results in Tycho for simplicity.  We do reference the simple model to build
-intuition and give scaling relations, as was done in depth by
-\citet{parizot2006} and \citetalias{ressler2014}.
+\begin{figure*}[ht]
+    \centering
+    \plotone{figures/full-man_err-prfs_01.pdf}
+    \plotone{figures/full-man_err-prfs_16.pdf}
+    \caption{Full model rim profile width predictions for Regions 1
+        (left) and 14 (right) with measured data.  Note that ordinate FWHM axes
+        do not match and do not originate at zero, to better show model
+        predictions and data variation.
+    \label{fig:rims}}
+\end{figure*}
+
+\begin{figure*}[ht]
+    \centering
+    %\epsscale{0.45}  % For manuscript layout only!
+    \plottwo{figures/full-man_err-energywidth-01.pdf}{figures/full-man_err-energywidth-16.pdf} \\
+    %\plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
+    \caption{Full model width predictions as a function of energy for Regions 1
+    (top) and 16 (bottom) with measured data.  Dotted/dashed curves plot
+    pure loss-limited fits with varying $\mu$, solid curve plots estimated best
+    model fit with moderate damping ($a_b < 0.01$).
+    \label{fig:fits}}
+\end{figure*}
+
+%For the rest of our results and discussion, we consider only full model
+%fit results in Tycho for simplicity.  We do reference the simple model to build
+%intuition and give scaling relations, as was done in depth by
+%\citet{parizot2006} and \citetalias{ressler2014}.
 
 % Averaged fit results
-In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
-constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
-reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
-of the mean.  The averaged parameters and corresponding errors are strongly
-affected by outliers from extreme best fit values, as can be seen in
-Tables~\ref{tab:fits} and \ref{tab:fits-pt2} -- especially as the typical
-number of regions per filament is quite small.  We also averaged best fit
-parameters from all regions in the remnant, but the presence of outliers
-renders the averages relatively unusable.
-% TODO
-\note[Aaron]{we could also report one fit to the global FWHM averages, as was
-done by Sean?}
-
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{Filament averages of best-fit parameters for constituent regions
-    \label{tab:fits-avg}}
-    \input{tab-fits-par-avg.tex}
-\end{table*}
+%In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
+%constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
+%reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
+%of the mean.  The averaged parameters and corresponding errors are strongly
+%affected by outliers from extreme best fit values, as can be seen in
+%Tables~\ref{tab:fits} and \ref{tab:fits-pt2} -- especially as the typical
+%number of regions per filament is quite small.  We also averaged best fit
+%parameters from all regions in the remnant, but the presence of outliers
+%renders the averages relatively unusable.
+%
+%\begin{table*}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Filament averages of best-fit parameters for constituent regions
+%    \label{tab:fits-avg}}
+%    \input{tab-fits-par-avg.tex}
+%\end{table*}
 
@@
 \section{Discussion}
+
+% Radio rims very much TBD!
+
+%\begin{figure*}[ht]
+%    \centering
+%    \plotone{figures/full-man_err-prfs-radio_01.pdf}
+%    \plotone{figures/full-man_err-prfs-radio_14.pdf}
+%    \caption{Full model rim profile width predictions for Regions 1
+%    (top) and 14 (bottom) with measured data.
+%    \label{fig:rims-radio}}
+%\end{figure*}
 
@@
 A major independent observable is the synchrotron roll-off frequency.  If
-Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is
-independent of magnetic field strength and thus grants an external
-constraint on diffusion coefficient.
-In this manner, \citet{parizot2006} estimated diffusion coefficients
-$\eta = 10, 5$ for compression ratios $4, 10$ in Tycho.
+Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is independent
+of magnetic field strength and thus grants another constraint on diffusion
+coefficient, within the assumption of DSA driven electron losses.  In this
+manner, \citet{parizot2006} estimated diffusion coefficients $\eta = 10, 5$ for
+compression ratios $4, 10$ in Tycho.
+
+(formula -- give here, or above?)
+(this could be rolled into results)
 
@@
 equation~\eqref{eq:lad}, may be rearranged to obtain:
-\begin{equation}
-    B_0 = (317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
-                     \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
+\begin{align}
+    B_0 = &(317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
+            \nonumber \\
+          \times \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
                  \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
-\end{equation}
+\end{align}
+% IF we keep this eqn, double check the 317 \muG carefully...
 or, more simply,
@@
 \end{equation}
-Recall that $\eta \propto \eta_2$ as $E_h = E_2$ is constant, from
-equation~\eqref{eq:diffcoeff}.
+Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
+$B_0$, from equation~\eqref{eq:diffcoeff}.
 Similar results, primarily for magnetic field $B_0$, were previously given by
@@
 % ==========
-\section{Conclusions}
+\section{Conclusion}
 
@@
 
+% ==============================
+% \mE values for best-fit curves
+% ==============================
 \section{Best fit width-energy curve $m_\mt{E}$ values}
@@
     \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
-    \input{tab-fits-mE.tex}
+    \input{suppl-fits-mE.tex}
 \end{table*}
 
+% ===============================
+% Damping best fit sea of numbers
+% ===============================
 \clearpage
@@
     \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
-    \input{tab-fits-damp-f1.tex}
+    \input{suppl-fits-damp-f1.tex}
 \end{table*}
@@
     \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
-    \input{tab-fits-damp-f2.tex}
+    \input{suppl-fits-damp-f2.tex}
 \end{table*}
@@
     \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
-    \input{tab-fits-damp-f2-pt2.tex}
+    \input{suppl-fits-damp-f2-pt2.tex}
 \end{table*}
@@
     \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
-    \input{tab-fits-damp-f3.tex}
+    \input{suppl-fits-damp-f3.tex}
 \end{table*}
@@
     \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
-    \input{tab-fits-damp-f4.tex}
+    \input{suppl-fits-damp-f4.tex}
 \end{table*}
@@
     \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
-    \input{tab-fits-damp-f5.tex}
+    \input{suppl-fits-damp-f5.tex}
 \end{table*}
 
+% ================================
+% Damping best fit tables, SN 1006
+% ================================
+\clearpage
+\section{Magnetic damping fit tables, SN 1006}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to SN1006 filaments, $\mu = 1$}
+    \input{suppl-fits-damp-sn1006.tex}
+\end{table*}
+
+\clearpage
+\section{Magnetic damping fit tables, SN 1006, no e- cutoff}
+
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{Damped fits to SN1006 filaments, $\mu = 1$, no e- cutoff}
+    \input{suppl-fits-damp-nocut-sn1006.tex}
+\end{table*}
+
+% =====================================================
+% Synchrotron roll-off energy and diffusion coefficient
+% =====================================================
 \clearpage

### 2014-10-21 code/models/FullEfflengthPohlab_mod.f

@@ -47,7 +47,7 @@
         s = 2d0*alpha+1d0
 
         ! Extra (Aaron, testing varying eta)
-        eta2 = 0.01d0
+        eta2 = 0.04d0
         eta = eta2 ! * (2d0 * 2.417989d17 / (cm*B0))**(-(mu-1d0)/2d0)
 
         !Constants

### 2014-10-21 code/models/FullEfflength_port.py

@@ -49,12 +49,12 @@ def main():
     fwhms = fefflen(kevs, B0, eta2, mu, 4.52e8, 4.52e8/4, 1.077e19, 240.,
                     2*0.58+1, rminarc, True, irmax, iradmax, ixmax,
                     False, 0.001, 5e-6, 'fglists_mod.dat',
-                    200, 50, 2000)
+                    200, 50, 2000, False)
     # SN 1006 with damping
     #fwhms = fefflen(kevs, B0, eta2, mu, 5e8, 5e8/4., 2.96e19, 900.,
     #                2*0.6+1, rminarc, True, irmax, iradmax, ixmax,
     #                False, 0.001, 5e-6, 'fglists_mod.dat',
-    #                200, 50, 2000)
+    #                200, 50, 2000, False)
     #print 'rminarc = {}'.format(rminarc)
     #for en, fwhm in zip(kevs, fwhms):
     #    print '{:0.2f} keV: {:0.5f}'.format(en, fwhm)
@@ -67,7 +67,8 @@ def main():
 
 #@profile
 def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
-            iradmax, ixmax, idamp, ab, Bmin, fgfname, itmax, inmax, irhomax):
+            iradmax, ixmax, idamp, ab, Bmin, fgfname, itmax, inmax, irhomax,
+            get_prfs):
     """Use numpy arrays for everything (kevs, rminarc)
 
     Note that irmax is not very important anymore.
@@ -94,6 +95,8 @@ def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
                       compute emissivity at irhomax pts, which is then summed
                       on line of sight (interpolating) to get intensity
                       irhomax < irmax should be okay.
+        get_prfs (bool)
+            if True, return computed intensity profile as a list of np.ndarray
     Output:
         np.ndarray of FWHMs for each entry in kevs
     """
@@ -116,6 +119,9 @@ def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
     fullmodel.readfglists(fgfname)  # !! important
 
     widths = []
+    if get_prfs:
+        rgrids = []
+        prfs = []
 
     for en_nu, rmin_nu in zip(kevs, rmin):
         # Convert keV to s^{-1}
[…]

### 2014-10-21 code/models/models.py

@@ -32,7 +32,6 @@ def chi_squared(y, y_err, y_model):
     """Compute chi-squared statistic"""
     return np.sum( ((y_model - y) / y_err)**2 )
 
-
 # =========================================
 # Tabulate FWHM values from full model code
 # =========================================
@@ -412,7 +411,7 @@ def simple_fit(snr, kevs, data, eps, mu, eta2=None, B0=None,
     return res
 
 def full_fit(snr, kevs, data, eps, mu, eta2=None, B0=None, mu_free=False,
-    eta2_free=True, B0_free=True, model_kws=None, **lmf_kws):
+    eta2_free=True, B0_free=True, ab_fit=None, model_kws=None, **lmf_kws):
     """Perform full model fit (equation 12; Table 8 of Ressler et al.)
     Default fit: B0 free; mu, eta2 fixed
 
@@ -420,6 +419,8 @@ def full_fit(snr, kevs, data, eps, mu, eta2=None, B0=None, mu_free=False,
         kevs, data, eps (np.ndarray) as usual
         mu, B0, eta2 (float) initial guesses, but mu fixed
         mu_free, eta2_free (bool) which parameters shall vary in fits?
+        ab_fit (float) if specified, allow ab to be a fit parameter
+            (if you don't want it to vary, specify via model_kws instead)
         **lmf_kws takes extra kwargs for lmfit.minimize (includes lsq kws)
         Probably should set epsfcn via **lsq_kws
 
@@ -435,8 +436,12 @@ def full_fit(snr, kevs, data, eps, mu, eta2=None, B0=None, mu_free=False,
         pval = locals()[pstr]
         if pval is None:
             pval = snr.par_init[pstr]
-        p.add(pstr, value = pval, vary = locals()[pstr+'_free'],
-              min = snr.par_lims[pstr][0], max = snr.par_lims[pstr][1])
+        p.add(pstr, value=pval, vary=locals()[pstr+'_free'],
+              min=snr.par_lims[pstr][0], max=snr.par_lims[pstr][1])
+
+    if ab_fit is not None:
+        # TODO default ab_fit settings could be stored in each SNR
+        p.add('ab', value=ab_fit, vary=True, min=0, max=1e3)
 
     res = lmfit.minimize(objectify(width_cont), p, args=(data, eps, kevs, snr),
                          kws=model_kws, **lmf_kws)
@@ -484,7 +489,7 @@ def simple_width(snr, kevs, mu, eta2, B0):
[…]

### 2014-10-21 code/srcutlog/neipkgFunctionMap.h

@@ -1,0 +1,25 @@
+//
+// Code auto-generated by initpackage (XSPEC12 local 
+// model package code generator).  Do not edit.
+// Package: neipkg
+// Function header: neipkgFunctionMap.h
+
+#ifndef    FUNCTIONMAP_H
+#define    FUNCTIONMAP_H
+
+#include    <funcType.h>
+
+class    XSModelFunction;
+
+extern    ModelFunctionMap  XSFunctionMap;
+
+void  createneipkgFunctionMap();
+
+extern "C"  {
+
+
+	xsf77Call    srcutlog_;
+}
+
+
+#endif

### 2014-10-21 code/srcutlog/srcutlog.f

@@ -1,0 +1,164 @@
+C- This code was written by Jonathan Koehane, and renamed at SPR's request
+C- srcut -- Supernova Remnant Cut-off model
+C- -- KD 
+C- 11/28/1998
+C- 
+C -       SUBROUTINE syncsr(ear, ne, param, ifl, photar)
+       SUBROUTINE srcutlog(ear, ne, param, ifl, photar)
+C---
+C Steve Reynolds simple models -- put in X-spec format
+C---
+C see ADDMOD for parameter descriptions
+C number of parameters: 2
+C      norm      1 GHz Flux in Jy 
+C	1        Radio Energy spectral index (around 0.5)  
+C	2        Break Frequency in log10 Hz
+C no intrinsic energy range limit
+C Coeficient is the 1 GHz flux in Jy
+C---
+C 08 Apr 1997 - Jonathan Keohane
+C---
+
+       INTEGER ne, ifl
+       REAL ear(0:ne), param(2), photar(ne)
+       INTEGER NMOD
+       REAL kevhz, kevfljy, logmin,  logdelta
+       PARAMETER (kevhz = 2.417988366E17, kevfljy = 1509.188961)
+C  1kev = kevhz Hz,  1 keV/(s kev cm2) = kevfljy Jy  
+C              number of bins in model
+       Parameter(NMOD = 80)
+       Parameter(logmin = -4.1, logdelta = 0.1) 
+C ---
+C 2014 Oct 17 - changed gamma to rank-1 array here and in one line below
+C to match pwlw call signature, so that it compiles successfully with
+C GNU Fortran (Homebrew gcc 4.8.3_1) 4.8.3
+C Aaron Tran (aaron.tran@berkeley.edu)
+C ---
+       REAL a, b, Ebr, Ebr2, recGhz, alphan, gamma(1)
+       REAL logR(NMOD)
+       INTEGER i, j
+       REAL  terp, t, t0, x
+
+C     10**logR is the factor by which the flux is reduced
+      DATA logR/
+     &  0.0000E+00, -.1106E-02, -.2339E-02, -.3715E-02, -.5248E-02, 
+     &  -.6956E-02, -.8859E-02, -.1098E-01, -.1333E-01, -.1595E-01, 
+     &  -.1886E-01, -.2209E-01, -.2567E-01, -.2965E-01, -.3406E-01, 
[…]

### 2014-10-23 manuscript/paper-tycho.tex
Damp params plot, paper results/disc, Tycho table
Grid of profiles over damping model parameter space.
Polish text results, restructure / start fleshing discussion
Generate new set of Tycho tables (loss-lim + damped)

@@
 
-\shorttitle{Synchrotron Rims in Tycho's SNR}  % <~ 44 char
-\shortauthors{XXX et al.}  % Max three
+\shorttitle{Tycho's Synchrotron Rims (\today)}  % <~ 44 char
+\shortauthors{XXX et al. (\today)}  % Max three
 \slugcomment{Draft, \today}  % short title pg comment
@@
 
-\title{Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent}
+\title{Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova
+Remnant}
 
@@
 energy and are well-described by either loss-limited or magnetically damped
-models.  We are unable to distinguish between scenarios, as models for rim
-widths incorporating electron cut-offs both reproduce the observed rim
-drop-offs.  The best loss-limited fits require amplified magnetic fields of
-$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
-1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR, whereas
-magnetic damping fits permit magnetic fields of $\abt 10$--$300 \muG$ and
-comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
-Non-negligible diffusion coefficients, magnetic field strengths, and magnetic
-damping lengthscales are somewhat degenerate in setting observed rim widths and
-drop-offs.  A different approach will be needed to determine the presence of
-magnetic damping downstream of supernova remnant shocks.
+scenarios, hence X-ray rim widths alone cannot discriminate between models.
+Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
+and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
+consistent with prior work on Tycho's SNR, whereas magnetic damping permits
+magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
+coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
+field strengths, and magnetic damping lengthscales are somewhat degenerate in
+setting observed rim widths and drop-offs.  Although we cannot discriminate
+from width measurements alone, a combined study of X-ray and radio profiles may
+break the observed degeneracies to confirm or rule out turbulent magnetic field
+damping downstream of supernova remnant shocks.
 \end{abstract}
@@
 % (spectra/profiles/fwhms/fits).
+
+% TODO terminology for "loss-limited" / "damped" / "constant field" / etc
+% should be well established
 
@@
 prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
-``knee'' \citep{vink2012}.  \note[Aaron]{the discussion of hadronic
-acceleration isn't really relevant, just background information}
+``knee'' \citep{vink2012}.
 
@@
 \citep{reynolds1999}, corresponding to a cut-off in the underlying electron
-spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
-\note[Aaron]{question: which came first?  observation of synchrotron
-steepening, or explanation/prediction of electron cut-off and hence synchrotron
-roll-off?  Or, even, was the electron cut-off predicted but the observable
-consequence of synchrotron roll-off not recognized until observations?} Many
+spectrum as predicted by diffusive shock acceleration \citep{webb1984}.  Many
 fundamental questions about the shock acceleration process remain to be
@@
 Our procedure closely follows that of \citetalias{ressler2014}.
-We first introduce our transport models for electron advection and diffusion
-with continuous synchrotron losses.  We selected and measured rim widths at
-several locations around Tycho's forward shock, verifying that selected rims
-are free of thermal line emission.  Using our models for particle transport
-(with DSA included, to first order, in a simple exponentially cut-off injected
-electron spectrum), we predict width-energy dependence in the loss-limited and
-magnetic damping scenarios to obtain estimates on magnetic field strength and
-diffusion coefficient magnitude.  We discuss degeneracy in our model fits and
-the implications for future studies of young supernova remnant shocks.
+We selected and measured rim widths at several locations around Tycho's forward
+shock, verifying that selected rims are free of thermal line emission.  Using a
+model for particle transport with an exponentially cut-off injected electron
+spectrum, we fit width measurements to model predictions in the loss-limited
+and magnetic damping scenarios to obtain estimates on magnetic field strength
+and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
+and the implications for future studies of young supernova remnant shocks.
 
@@
 % Could just discuss one model...
-We consider two particle transport models that we fit to measurements of
-Tycho's thin rim widths.  We measure the rim full widths at half maximum
-(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
-model predictions of rim FWHMs at multiple photon energies, for various input
-parameters.  The models accept four free parameters: magnetic field strength
-$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
-exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
-length).
-
-We use CGS (Gaussian) units throughout.  Our presentation is somewhat
-abbreviated; please refer to \citetalias{ressler2014} for a fuller review and
-exposition of the transport models and relevant parameters' effect on rim
-widths.
-
-%Early workers measured filament widths of several historical supernova remnants
-%and considered ...  Assuming that thin rim widths are limited by synchrotron
-%energy losses (loss-limited rims), you have $l_{\mt{ad}} \propto v_d \tsynch$
-%gives a magnetic field...  \citet{bamba2003, vink2003, yamazaki2004,
-%ballet2006} More sophisticated models have followed, but the basic result is
-%consistent -- magnetic fields are amplified, with some amount of diffusion.
-%\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
-%with the catastrophic dump equation.  \citet{berezhko2003, berezhko2004,
-%cassam-chenai2007, morlino2010, rettig2012} consider diffusion and advection
-%simultaneously with the continuous loss equation instead.  DSA may be
-%incorporated by direct calculation, or by assumption of a resultant electron
-%spectrum and cut-off \citep[e.g.,][]{zirakashvili2007}.
-%\citet{morlino2010}, and references therein, consider particle transport in the
-%context of nonlinear DSA neglecting particle energy losses (as would be
-%relevant for accelerated protons).  All the same principles.
+%We consider two particle transport models that we fit to measurements of
+%Tycho's thin rim widths.  We measure the rim full widths at half maximum
+%(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
+%model predictions of rim FWHMs at multiple photon energies, for various input
+%parameters.  The models accept four free parameters: magnetic field strength
+%$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
+%exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
+%length).
+
+% Twiddle-ables in our model (the most useful part, since just modeling
+% alone don't do much)
+Our model fitting explores the space of varying diffusion (a bulk
+representative of the underlying MHD turbulence and what have you)
+and considers the two scenarios of constant magnetic field (resulting in
+so-called loss-limited rims) and a damped field that falls off exponentially
+behind the forward shock, as suggested by \citet{pohl2005}.
+% this might go at the front before we launch into model details.
 
@@
 
-% TODO Choose names for these models and refer to them consistently, throughout
-% TODO define ALL symbols, synchrotron constants, etc
 % Transport fundamentals
-The energy and space distribution of electrons at a supernova remnant
-controls the synchrotron rims we see in X-ray and radio.  We model electron
-advection and diffusion from initial injection at the remnant's forward shock
-assuming 1-D steady-state plane transport, with spatially homogeneous and
-isotropic diffusion, as following the equation:
-\begin{equation}
-    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
-\end{equation}
-Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
-and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
-towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
-the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
-shock.  We consider only particle transport downstream of the shock ($x \geq
-0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
-encapsulate all assumptions about the accelerated electron spectrum, shock
-and magnetic field structure, and time/space evolution of the particle
-distribution.  More sophisticated treatments may explicitly treat magnetic
-fields and diffusion across the shock, plasma streaming instabilities and
-particle losses, anisotropic diffusion, the DSA process and efficiency, and
+The energy and space distribution of electrons at a supernova remnant's forward
+shock controls the synchrotron rims we see in X-ray and radio.  We assume that
+diffusive shock acceleration creates a power-law distribution of electrons with
+an exponential cut-off at the forward shock, located at $x = 0$ with $x > 0$
+increasing downstream of the shock, given as
+$f(E,x=0) = K_0 E^{-s} e^{-E/\Ecut}$.  Here $K_0$ is an arbitrary
+normalization, $E$ is electron energy, and the cut-off energy $\Ecut$ is given
+below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
+the radio index $\alpha$ as $s = 2\alpha + 1$.
+
+All constants and equations are given in CGS (Gaussian) units.  Our
+presentation is somewhat abbreviated, but a fuller exposition and literature
+review is given by \citetalias{ressler2014}.
+
+We model electron advection and diffusion downstream of the shock (i.e., for
+$x>0$ only) with a 1-D steady-state plane transport equation:
+\begin{equation} \label{eq:model}
+    v_d \frac{\ptl f}{\ptl x}
+    - \frac{\ptl}{\ptl x} \left(D\frac{\ptl f}{\ptl x}\right)
+    - \frac{\ptl}{\ptl E} \left(bB^2E^2f\right)
+    = K_0 E^{-s} e^{-E/\Ecut} \delta(x) ;
+\end{equation}
+this follows the work of \citet{webb1984, berezhko2004, cassam-chenai2007,
+morlino2010, rettig2012}.  Here $f = f(E,x)$ is electron distribution as a
+function of electron energy $E$ and downstream distance $x$, $D$ is the
+diffusion coefficient, and $v_d$ is plasma velocity downstream of the shock.
+The constant $b = 1.57 \times 10^{-3}$ in CGS units arises from synchrotron
+power loss at electron energy $E$ (i.e., $\ptl E/\ptl t = b B^2 E^2$).
+We have assumed isotropic diffusion and consider only processes operating
+downstream of the shock.  More sophisticated treatments may explicitly treat
+magnetic fields and diffusion across the shock, plasma streaming instabilities
+and particle losses, anisotropic diffusion, the DSA process and efficiency, and
 other details in great depth \citep[e.g.,][and references therein]{reville2013,
@@
 
-% Simple model
-A first approximation is to let electrons have constant energy that is dumped
-catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
-$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
-vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
-\begin{equation} \label{eq:simp-mod}
-    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
-    \frac{f}{\tau_{\mt{synch}}} = 0 .
-\end{equation}
-No assumptions on the injected electron source term are necessary.
-\citet{parizot2006} employed this model to estimate magnetic fields, diffusion
-coefficients, and electron spectrum cut-offs for several historical SNRs.
-Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
-\exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim FWHM
-predicted by equation~\eqref{eq:simp-mod} is:
-\begin{equation} \label{eq:simp-fwhm}
-    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
-\end{equation}
-with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
-\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
-exponential $f(E,x)$ and projection from a spherical shell, as derived by
-\citet{ballet2006}.
-
-% Full model
-A more accurate model accounts for continuous synchrotron losses as electrons
-are injected from an exponentially cut-off power-law electron distribution
-(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
-\begin{align} \label{eq:full-mod}
-    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
-    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
-    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
-\end{align}
-see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
-\citet{morlino2010}, \citet{rettig2012}, and references therein.
-The cut-off energy is determined by the diffusion coefficient $D$,
-which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
-widths, we first numerically solve for electron distribution $f(E,x)$ using
-Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
-solutions are given by \citetalias{ressler2014} using notation similar to that
-used herein \note[Aaron]{wording}.  The electron distribution may then be
-integrated to obtain synchrotron emissivity:
+To determine rim profiles and widths, we numerically solve for electron
+distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
+and \citet{rettig2012}; the solutions are given by \citetalias{ressler2014}
+using notation similar to ours.  We note, however, that the solutions for
+$f(E,x)$ in equation~\eqref{eq:model} are derived assuming that $D(x) B^2(x)$
+is constant \citep{lerche1980}; we will revisit this assumption further below.
+% TODO give section number when you revisit this
+The electron distribution may be integrated over the one-particle synchrotron
+emissivity $G(y)$ to obtain the ``total'' emissivity:
 \begin{equation} \label{eq:emissivity}
@@
 where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
-$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
-with $K_{5/3}(z)$ a modified Bessel function of the second kind
-\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
-spherical remnant yields intensity as a function of radial coordinate $r$:
+$G(y) = y \int_y^\infty K_{5/3}(z) dz$ with $K_{5/3}(z)$ a modified Bessel
+function of the second kind \citep{pacholczyk1970}.  Integrating emissivity
+over lines of sight for a spherical remnant yields intensity as a function of
+radial coordinate $r$:
 \begin{equation} \label{eq:intensity}
@@
 \end{equation}
-where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
-from the resulting intensity profile.
+where $s$ is the line-of-sight coordinate.  Finally, we compute the full width
+at half maximum (FWHM) of the resulting intensity profile to compare to our
+measurements of rim width.
 
@@
 % Bohm, Bohm-like, and MHD/turbulence-inspired diffusion
-Much previous work has assumed Bohm-like diffusion in plasma downstream of SNR
+Most previous work has assumed Bohm-like diffusion in plasma downstream of SNR
 shocks.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
@@
 $E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
-field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
-$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
-$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
-all energies.
-\note[Aaron]{for self-edification, any justification / derivation of Bohm
-limit?  All the papers seem to take it for granted}
+field.  Bohm-like diffusion encapsulates diffusion scalings of $D \propto E$,
+introducing a free prefactor $\eta$ such that $\lambda = \eta r_g$ allows for
+varying diffusion strength.  However, Bohm diffusion at $\eta = 1$ is commonly
+considered a lower limit on the diffusion coefficient at all energies.
+
 Different types of MHD turbulence may give rise to a non-linear energy
-scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
+scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
 Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
@@
 predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
-Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
-\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
-I have no idea what this means.}
+Particle gyroradii larger than field coherence length may also lead to
+$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
+and cites nothing.  I have no idea what this means.}
 
@@
 \end{equation}
-where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
-of $\mathrm{erg}^{1-\mu}$.
-The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
-dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
-particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are related as
-$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
-($\mu = 1$).
+where $\mu$ parameterizes diffusion-energy scaling and $\eta$ now has units
+of $\mt{erg}^{1-\mu}$.  The right-hand side of equation~\eqref{eq:diffcoeff}
+introduces $\eta_h$, a dimensionless diffusion coefficient scaled to the Bohm
+value at a fiducial particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are
+related as $\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like
+diffusion ($\mu = 1$).
 
@@
 
-\subsection{Electron cut-off}
-
-% Electron cut-off energy
-With a diffusion coefficient in hand, we determine the electron spectrum
+% e- cutoff energy result
+With a diffusion coefficient in hand, we may determine the electron spectrum
 cut-off energy by equating synchrotron loss and diffusive acceleration
@@
 above the cut-off energy, electrons will radiate or escape too rapidly to be
-accelerated, so the energy spectrum drops off steeply.  The cut-off energy
-adapted from \citet{parizot2006} is given as:
+accelerated to higher energies and the energy spectrum drops off steeply.  The
+cut-off energy is given as:
 \begin{align} \label{eq:ecut}
@@
 \end{align}
-\citet{parizot2006} derive equation~\eqref{eq:ecut} in the case $\mu=1$
-assuming a strong shock with compression ratio 4 and isotropic magnetic
-turbulence on both sides of the shock.
-
+This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
+shock with compression ratio 4 and isotropic magnetic turbulence on both sides
+of the shock.
+
+% srcut constraint on diffusion
 As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
@@
 In particular, this equation is independent of magnetic field $B$ for all
-values of $\mu$ (but recall that the specific electron energies associated with
-$\eta_2$ will depend on $B$).
+values of $\mu$ (but, recall that the specific electron energies associated
+with $\eta_2$ will depend on $B$).
 
 % Magnetic damping
-\subsection{Magnetic damping}
-
-We also consider a magnetically damped field of form
-\begin{equation}
-    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
-\end{equation}
-following \citet{pohl2005}.
-In the full continuous energy loss model (equation~\eqref{eq:full-mod}), it
-suffices to substitute $B = B(x)$ throughout; in the simpler model, $B(x)$
-enters through the diffusion coefficient $D = D(E,x)$ and the analytic
-expression (equation~\eqref{eq:simp-fwhm}) may no longer be valid.
-Again, \citetalias{ressler2014} detail how to integrate a damped field into the
-full model solutions to equation~\eqref{eq:full-mod}.
-
-%(DRAFT) We currently do not present model fits with magnetic damping, although
-%in principle they are doable.  Set up the calculation w/ a range of scale
-%lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
-%for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?
-
-\subsection{Width-energy dependence and some intuition} \label{sec:energydep}
-
-As discussed in Section~\ref{sec:intro}, width-energy dependence is key to
-differentiating between loss/diffusion-limited rims and magnetically damped
-rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
-terms of a scaling exponent $\mE$ defined by:
+\subsection{Magnetic fields and damping}
+
+We consider two scenarios for post-shock magnetic field: (1) a constant field
+$B(x) = B_0$, corresponding to the loss-limited rim scenario, and (2) an
+exponentially damped field of form:
+\begin{equation} \label{eq:bdamp}
+    B(x) = \left(B_0 - B_{\mt{min}}\right) \exp\left(-x / a_b\right)
+           + B_{\mt{min}}
+\end{equation}
+where $a_b$ is an $e$-folding damping lengthscale, following \citet{pohl2005}.
+A typical lengthscale for $a_b$ is $10^{16}$ to $10^{17} \unit{cm}$
+\citep{pohl2005}, corresponding to $\abt 0.1$--$1\%$ of Tycho's radius.
+Hereafter, we report $a_b$ in units of shock radius $r_s$.
+
+The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
+field, which varies in a damped model.  For simplicity, we assume that the
+shock acceleration process is set by the diffusion at the immediate shock and
+so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
+$B_0$.
+\note[Aaron]{Is this correct?  Can try rederiving the expression (particles
+penetrate some distance downstream, then back), but I'm not sure if it's even
+sensible with diffusion coefficient varying so sharply.}
+
+\subsection{Rim width-energy dependence} \label{sec:energydep}
+
+% Define \mE
+Following \citetalias{ressler2014}, we parameterize rim width-energy dependence
+in terms of a scaling exponent $\mE$ defined as:
 \begin{equation}
@@
 where $w(\nu)$ is filament FWHM as a function of observed photon frequency
-$\nu$.  We may refer to observed photons interchangeably by energy or frequency
-$\nu$, but $E$ is reserved for electron energy.  The exponent $\mE = \mE(\nu)$
-is generally energy dependent.
-
+$\nu$.  The exponent $\mE = \mE(\nu)$ is generally energy dependent.  We may
+refer to observed photons interchangeably by energy or frequency $\nu$, but $E$
+is reserved for electron energy.
+
+% Intuition: transport lengthscales in the absence of damping
 We may consider advective and diffusive lengthscales for electron transport,
@@
 \end{equation}
+The characteristic time is the synchrotron cooling time
+$\tsynch = 1 / (b B^2 E)$ with $b = 1.57 \times 10^{-3}$.
 If both diffusion and magnetic field damping are negligible (whether at a small
@@
 in part to the electron energy cut-off, which limits the available electrons at
-higher energies and thus thins the rims slightly, shifting $\mE$ negative
+higher energies and thus thins the rims slightly, decreasing $\mE$
 \citepalias[Figure 5]{ressler2014}.
 
-% TODO REVISIT THIS AFTER SETTING UP CALCULATIONS
-If magnetic damping is a primary control on rim widths, we expect to see $\mE
-\sim -0.1$ \citepalias{ressler2014}.
-\note[Aaron]{elaborate after filling in preceding section}
-NOOOOOOOOOOOOOPE.
+% Intuition: how damping affects rim widths
+We expect magnetic damping to produce comparatively energy-independent rim
+widths.  In particular, if synchrotron rims widths are set by magnetic damping
+at some observation energy, then the rims must be damped at all lower
+observation energies as well.  Then we may expect relatively stable rim widths
+below a threshold energy, then decreasing rim widths once advective or
+diffusive lengthscales fall below the damping lengthscale at higher photon
+energies.
+
+% A comment
+It may be worth noting that this rim width-energy dependence is a morphological
+manifestation of the spectral softening downstream of the forward shock, as
+observed by, e.g., \citet{cassam-chenai2007}.  So we are simply taking somewhat
+of a different approach to characterizing this softening.
 
@@
 \end{figure}
+% TODO TODO TODO UPDATE REGION # BOLDING TO MATCH DISPLAYED FILAMENTS ETC
 
@@
     \plotone{figures/spec_16.pdf}
-    \caption{Spectra and fits from Regions 1 (top) and 14 (bottom) show varying
+    \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
     rim morphology and example of rim where 0.7--1 keV peak could not be fit.
@@
     \caption{Best fit profiles with measured FWHMs demarcated for each energy
-        band in Region 1 (top) and Region 14 (bottom).  Energy bands increase
+        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
         from left to right.  Data points in red were excluded from profile
@@
 
-% Fit data to models
-We fit the two transport models given by Equations~\eqref{eq:simp-mod} and
-\eqref{eq:full-mod} to our measured rim widths as a function of energy.
-We mapped each width measurement to the lower energy limit of its energy band;
-e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to
-model profile widths at $0.7 \unit{keV}$.  Errors in least squares fits
-average the positive and negative errors on each FWHM measurement.
-
-% Model knobs and how we twiddled them
-We varied three physical parameters: diffusion-energy scaling exponent $\mu$,
-normalized diffusion coefficient $\eta_2$, and magnetic field strength $B_0$.
-To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
-$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$; recall that $\mu = 1/3$ and $1/2$
-correspond to Kolmogorov and Kraichnan turbulence.  Our fits do not consider
-a damped magnetic field with the additional parameter of scale length $a_b$,
-and so magnetic field strength $B_0$ is assumed constant downstream of the
-shock.  Below we shall show that magnetic damping cannot explain our observed
-filament widths, so we present fits assuming loss-limited rim widths only.
-% TODO Edit if I add magnetic damping material
-
-% Tycho parameters TODO change green2009 to green2014 once published in BASI
-A few remnant-specific parameters enter into the model calculations.  We
-adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha =
-0.65$ \citep{kothes2006},
-\note[Aaron]{will change to $s= 2.16$ from $\alpha=0.58$ following
-\citet{sun2011} on next iteration}
-remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and shock radius
-$1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
-\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
-a factor of 2; we interpolated shock velocities reported by
-\citet{williams2013} (rescaled to $3 \unit{kpc}$ rather than $2.3 \unit{kpc}$
-to estimate individual shock velocities for each region.
-
-% How to do the fit
-Equation~\eqref{eq:simp-fwhm} was directly fit to our measurements to obtain
-best-fit values of $\eta_2$ and $B_0$.  The full model was numerically computed
-as detailed in Section~\ref{sec:transport}, yielding intensity profiles and
-hence model FWHMs in each energy band.  To assist the nonlinear
-fitting, we tabulated a large grid of model FWHM values for various values of
-$\mu$, $\eta_2$, $B_0$, and shock velocity $v_s$.  From a best initial grid
-value, we used a Levenberg-Marquardt fitting routine to determine the best
-fits.  Errors on best fit parameters were computed by varying each fit
-parameter and obtaining a new best fit model, with one less degree of freedom,
-to find the parameter limit such that $\Delta \chi^2 = 1$ for a roughly
-1-$\sigma$ error.
+% How we ran model fits (itemize knobs, explain energy band mapping, errors,
+% fitting procedure
+We fit model FWHM predictions given by Equation~ \eqref{eq:model} to our
+measured rim widths as a function of energy by varying several physical
+parameters: magnetic field strength $B_0$, normalized diffusion coefficient
+$\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
+$B_{\mt{min}}$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
+mapped each width measurement to the lower energy limit of its energy band;
+e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
+profile widths at $0.7 \unit{keV}$.  Errors in our least squares fits average
+the positive and negative errors on each FWHM measurement.  For an input set of
+model parameters, we numerically computed intensity profiles and hence model
+FWHMs as detailed in Section~\ref{sec:transport}, and used a
+Levenberg-Marquardt fitting routine to identify best fit model parameters
+(subject to varied constraints on model parameters in the following paragraph).
+To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
+of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
+initial guesses for fitting.
+% TODO this may be obsoleted if we recompute stuff...  I only computed errors
+% on the loss-limited model, and those fits are now out of date too...
+Errors on best fit parameters were computed by varying each fit parameter and
+obtaining a new best fit model, with one less degree of freedom, to find the
+parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.
+
+% How we twiddled model knobs
+We first considered a purely loss-limited model (constant magnetic field
+$B_0$) with three parameters $\mu$, $\eta_2$, and $B_0$.  To make nonlinear
+fitting tractable, we fixed $\mu$ in all fits and considered $\mu = 0$, $1/3$,
+$1/2$, $1$, $1.5$, and $2$; recall that $\mu = 1/3$ and $1/2$ correspond to
+Kolmogorov and Kraichnan turbulence.  The remaining parameters $\eta_2$ and
+$B_0$ varied freely.
+
+% Damped case
+For damped magnetic field fits, we held the asymptotic field strength
+$B_{\mt{min}}$ inside the remnant constant at $5 \muG$, slightly higher than
+typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
+We fixed $a_b$ at $12$ different values and ran fits with $\eta_2$ and $B_0$
+free.  Formally, we do not seek a best fit value of damping length $a_b$, so
+our ``best'' damping fits report the value of $a_b$ yielding the smallest
+$\chi^2$ value.  Finally, we fixed $\mu = 1$ for all damped fits.
+
+% Variants on our fitting procedure
+To better explore the parameter space of model predictions, we also computed
+model fits with both $\eta_2 = 1$ and $\mu = 1$ fixed for both scenarios of
+constant and damped magnetic field.  We also attempted damping fits with
+$B_{\mt{min}} = 2 \muG$, somewhat on the lower end of estimated galactic
+magnetic field values.
 
@@
 
+% Tycho parameters
+A few remnant-specific parameters affect the model calculations.  We adopted
+electron spectral index $s = 2.16$ from radio spectral index $\alpha = 0.58$
+\citep{sun2011}, remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
+shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
+\citep{green2014}.  Tycho's forward shock velocity varies with azimuth by up to
+a factor of 2; we interpolated velocities reported by \citet{williams2013}
+(rescaled to $3 \unit{kpc}$) to estimate individual shock velocities for each
+region.
+
+% Model resolution error
 As the full model must be numerically solved, its predicted rim widths are
@@
 function integrals).  We chose integration resolutions such that the
-fractional error in model FWHMs associated with halving or doubling integration
-resolution is less than $1\%$ for the parameter space relevant to our
-filaments (up to $\eta_2 = 10^3$ for loss-limited model; up to $\eta_2 = 10$
-for magnetic damping model).  In our error analysis, the maximum resolution
-errors in a sample of parameter space are typically $0.1$--$1\%$, but mean and
-median errors are typically an order of magnitude smaller that maximum errors.
+fractional error in model FWHMs associated with halving or doubling each integration
+resolution (individually) is less than $1\%$ for the parameter space relevant
+to our filaments -- $\eta_2 \leq 10^3$ for the loss-limited model and $\eta_2
+\leq 10$ for the magnetic damping model).  In our error analysis, the maximum
+resolution errors in a sample of parameter space are typically $0.1$--$1\%$,
+but mean and median errors are typically an order of magnitude smaller that
+maximum errors.  Thus we expect numerical errors to be negligible.
 
@@
 
+% Present table of FWHM results
 Table~\ref{tab:fwhms} reports FWHM measurements for all of our regions.
@@
 where $w_1, w_2$ and $E_1, E_2$ are FWHMs and lower energy values for each
-energy band (e.g., $\mE$ at $1 \unit{keV}$ is computed using FWHMs from
-$0.7$--$1 \unit{keV}$ and $1$--$1.7 \unit{keV}$, with $E_2 = 1
-\unit{keV}$ and $E_1 = 0.7 \unit{keV}$.  Errors on $\mE$ are propagated in
-quadrature from adjacent FWHM measurements.
-
-\begin{table*}[ht]
+energy band -- e.g., $\mE$ at $1 \unit{keV}$ is computed using FWHMs from
+$0.7$--$1 \unit{keV}$ and $1$--$1.7 \unit{keV}$, with $E_2 = 1 \unit{keV}$ and
+$E_1 = 0.7 \unit{keV}$.  Errors on $\mE$ are propagated in quadrature from
+adjacent FWHM measurements.
+
+\begin{table*}
     % Use \tiny for manuscript; \scriptsize for 2-column
-    %\tiny
-    \scriptsize
+    \tiny
+    %\scriptsize
     \centering
@@
 
+% Observations of mE and rim widths and stuff
 Measured rim widths decrease with energy in most regions and energy bands.
@@
 
+% Errors in rim widths
 The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
@@
 Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
-part to (1) our profile fitting procedure, which depends on an empirically
-chosen profile fit function which may also fit the rims non-uniquely, and (2)
-variation in Tycho's rim morphology, also demonstrated clearly in
-comparison of rims from Regions 1 and 16 in Figure~\ref{fig:profiles}.
-\note[Aaron]{review paragraph wording.  This may belong in the discussion?}
-
-% discussion of uncertainties/caveats in our results
-% \note[Aaron]{text blob}
-% One way to address uncertainty in the fitting function is to consider other
-% functions -- for example, a gently smoothed spline fit, a manually capped
-% two-exponential function, a Gaussian sitting on a ramp or logistic curve, etc.
-% Explain that nothing happens -- not much (but should reaffirm this or give
-% some kind of numbers).
-% Another is simply our sampling -- we have already sought to circumvent this by
-% taking multiple regions in each filament, as many as possible without overly
-% compromising the quality of our radial profiles.  This also makes no major
-% difference to our results.
+part to (1) our profile fitting procedure, which depends on a somewhat
+arbitrary choice of profile fit function, and (2) variation in Tycho's rim
+morphology (see Figure~\ref{fig:profiles}).
 
@@
 
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fit for individual regions, Filaments 1--2.
-%    \label{tab:fits}}
-%    \input{tab-fits-all.tex}
-%\end{table*}
-%
-%\begin{table*}[ht]
-%    \tiny
-%    \centering
-%    \caption{Full model best fits for individual regions, Filaments 3--5.
-%    \label{tab:fits-pt2}}
-%    \input{tab-fits-all-pt2.tex}
-%\end{table*}
-
-% Example loss-limited fits
-\begin{table}[ht]
-    \scriptsize
-    \centering
-    \caption{Best loss-limited fits for Regions 1, 16
-    \label{tab:fits-loss-ex}}
-    \input{tab-fits-loss-ex.tex}
-\end{table}
-
-% Example damping fits
-\begin{table}[ht]
-    \scriptsize
-    \centering
-    \caption{Best magnetic damping fits for Regions 1, 16
-    \label{tab:fits-damp-ex}}
-    \input{tab-fits-damp-ex.tex}
-\end{table}
-
-% NOTE: USE CHISQR HERE, NOT REDUCED CHI SQUARED.
-% Justification: comparing fits with parameters free/frozen
-% between the following two tables.
-
-% Fit results for ALL regions, mu = 1, loss-limited and damped
-\begin{table}[ht]
-    \tiny
-    \centering
-    \caption{Best model fits with magnetic damping, $\mu = 1$
-    \label{tab:fits-damp}}
-    \input{tab-fits-all-summary.tex}
-\end{table}
-
-% TODO LIST DOFs in FINAL VERSION
-
-% As above but with eta2=1 fixed!
-\begin{table}[ht]
-    \scriptsize
-    \centering
-    \caption{Best model fits with magnetic damping, $\mu = \eta_2 = 1$
-    \label{tab:fits-damp}}
-    \input{tab-fits-all-summary-eta2one.tex}
-\end{table}
-
-% TODO LIST DOFs in FINAL VERSION
-
-% Individual region fit results
-% NOTE keep updated -- for which region are we giving simple and full fits?
-Table~\ref{tab:fits} presents full model fit results for all regions
-considered.  The first row of Table~\ref{tab:fits} includes both simple and
-full model fits for Region 1 for comparison.  We found that fits to the simpler
-catastrophic dump model (equation~\eqref{eq:simp-mod}) reproduced qualitative
-trends seen in the full continuous energy loss model, as expected.  In general,
-simple model fits yielded slightly smaller $\eta_2$ and/or slightly larger
-$B_0$ values; this is consistent with the expectation that electrons travel
-farther in the simple model than in the full model. Since electrons are not
-subjected to continuous synchrotron cooling, smaller $\eta_2$ and larger $B_0$
-values are needed to generate thinner rim widths as compared to the full model.
-Simple model fits were also more likely to reach manual fitting limits (i.e.,
-allow for unconstrained parameter values) than full model fits.
-
-\begin{figure*}[ht]
+% Explain our approach
+We tabulate and plot fitting results for Regions 1 and 16, the same regions
+shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
+subset of our regions, qualitative trends in fit parameters were comparable in
+most regions; our most salient observations, discussed below, are well
+exemplified by Regions 1 and 16.  Best fit results for all regions are
+summarized in Tables~\ref{tab:fits-all}, \ref{tabs:fits-all-eta2one}.  In all
+tables, we report values of $\chi^2$ rather than $\chi^2_\mt{red}$ to ease
+comparison of different fits, as we often manually stepped one or two
+parameters that were held constant in fitting.
+
+% Best fit model results and tables for Regions 1, 16.
+% Explain a bit about model shapes, and the relative similarity in shapes
+Modeled profiles with best fit FWHMs for Regions 1 and 16 are plotted in
+Figure~\ref{fig:rims}), and their derived best-fit FWHM-energy curves
+are plotted in Figure~\ref{fig:fits} alongside measured FWHMs.
+The best fit model profiles do not quite match our measured rim profiles
+(Figure~\ref{fig:profiles}).  Our transport equation does not account for
+diffusive transport upstream of the shock, projection effects from shock
+ripples or other structure, and thermal emission downstream of the thin rim.
+Hence, fitting to FWHM measurements should be less sensitive to these effects
+as compared to directly fitting entire rim profiles to model predictions.
+We also note that although Figure~\ref{fig:rims} plots model profiles for
+$\mu = 1$ only, the best-fit FWHM-energy curves show that model profiles for
+$\mu \neq 1$ give very similar FWHM-energy dependence.  This is borne out in
+our best fit parameters in Tables~\ref{tab:fits-loss} and \ref{tab:fits-damp}.
+
+\begin{figure}
     \centering
@@
     \plotone{figures/full-man_err-prfs_16.pdf}
-    \caption{Full model rim profile width predictions for Regions 1
-        (left) and 14 (right) with measured data.  Note that ordinate FWHM axes
-        do not match and do not originate at zero, to better show model
-        predictions and data variation.
+    \caption{Best fit full model rim profile width predictions for Regions 1
+        (top) and 16 (bottom) for loss-limited and damped scenarios with
+        $\mu = 1$ fixed.  Shaded regions on damped profiles indicate the
+        damping ($e$-folding) lengthscale for the magnetic field.  Note that
+        radial coordinate ($r$) axes agree in each row (same region), but not
+        in each column.
     \label{fig:rims}}
-\end{figure*}
-
-\begin{figure*}[ht]
+\end{figure}
+
+\begin{figure}
     \centering
     %\epsscale{0.45}  % For manuscript layout only!
-    \plottwo{figures/full-man_err-energywidth-01.pdf}{figures/full-man_err-energywidth-16.pdf} \\
-    %\plottwo{figures/fits-sep13/reg13.png}{figures/f0-box.png}
+    \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-01.pdf}
+    \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-16.pdf}
     \caption{Full model width predictions as a function of energy for Regions 1
@@
     pure loss-limited fits with varying $\mu$, solid curve plots estimated best
-    model fit with moderate damping ($a_b < 0.01$).
+    model fit with moderate damping ($a_b < 0.01$).  Note that ordinate FWHM
+    axes do not match and are offset from the origin to better show model
+    predictions and data variation.
     \label{fig:fits}}
-\end{figure*}
-
-%For the rest of our results and discussion, we consider only full model
-%fit results in Tycho for simplicity.  We do reference the simple model to build
-%intuition and give scaling relations, as was done in depth by
-%\citet{parizot2006} and \citetalias{ressler2014}.
-
-% Averaged fit results
-%In each filament, we averaged best fit parameters $B_0$, $\eta_2$ from each
-%constituent region to obtain filament-wide estimates on $B_0$ and $\eta_2$,
-%reported in Table~\ref{tab:fits-avg}.  Stated uncertainties are standard errors
-%of the mean.  The averaged parameters and corresponding errors are strongly
-%affected by outliers from extreme best fit values, as can be seen in
-%Tables~\ref{tab:fits} and \ref{tab:fits-pt2} -- especially as the typical
-%number of regions per filament is quite small.  We also averaged best fit
-%parameters from all regions in the remnant, but the presence of outliers
-%renders the averages relatively unusable.
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Filament averages of best-fit parameters for constituent regions
-%    \label{tab:fits-avg}}
-%    \input{tab-fits-par-avg.tex}
-%\end{table*}
+\end{figure}
+
+% Observations on qualitative trends in fit parameters
+% NOTE keep numbers updated.  # of regions "favoring" mu >= 1
+% KEEP B0 minimum number updated!!!!!
+Loss-limited fits with $\mu \lesssim 1$ generally yield larger parameter values
+and errors for both $\eta_2$ and $B_0$, and they are more likely to be
+ill-constrained (e.g., $\eta_2 > 10^3$ or $B_0 > 10^3 \muG$).  Fits with $\mu
+\gtrsim 1$ generally yield smaller $\chi^2$ values in a majority of regions
+($\abt 17$ of $20$), although we do not explore the robustness of this
+observation.  Fits for the same data, with varying $\mu$, can yield $\eta_2$
+that vary by $1$--$2$ orders of magnitude; Region 16 illustrates this
+dramatically (Table~\ref{tab:fits-loss}).
+
+Magnetically damped rims are able to fit width-energy dependence in our
+measurements at least as well as purely loss-limited rims for an acceptable
+range of $a_b$ values (Table~\ref{tab:fits-damp}).  Damped model fits show some
+variability in best fit parameters, mainly in $\eta_2$, but are generally
+better-behaved than their loss-limited counterparts.  Smaller values of $a_b$
+permit and favor smaller best fit values of $B_0$ and $\eta_2$ in all regions.
+
+% Example loss-limited fits
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Loss-limited fits for Regions 1, 16
+    \label{tab:fits-loss}}
+    \input{tab-fits-loss.tex}
+    \tablecomments{Model fits computed at several fixed values of $\mu$ with
+    $\eta_2$, $B_0$ free and constant magnetic field $B(x) = B_0$.
+    Region 1 has 2 degrees of freedom (dofs); Region 16, 3.}
+\end{table}
+
+% Example damping fits
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Magnetic damping fits for Regions 1, 16
+    \label{tab:fits-damp}}
+    \input{tab-fits-damp.tex}
+    \tablecomments{Model fits computed at several fixed values of $a_b$ with
+    $\eta_2$, $B_0$ free and damped magnetic field (equation~\eqref{eq:bdamp}).
+    Fit degrees of freedom are as in Table~\ref{tab:fits-loss}}
+\end{table}
+
+% Fit results for ALL regions, mu = 1, loss-limited and damped
+% NOTE keep # of dofs updated
+\begin{table}
+    \tiny
+    \centering
+    \caption{Best model fits for all regions, $\mu = 1$
+    \label{tab:fits-all}}
+    \input{tab-fits-all.tex}
+    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
+    best damped fits select best $a_b$ value below $0.01$ from the range shown
+    in Table~\ref{tab:fits-damp}, enforcing moderate damping.  Fits for Regions
+    1, 2, 12, 18 have 2 dofs; all others have 3.  The manual selection of a
+    best $a_b$ value may be construed as removing one more dof.}
+\end{table}
+
+In Table~\ref{tab:fits-all-eta2one} we also present best loss-limited and
+damped fits with $\eta_2 = 1$ fixed.  As before, both loss-limited and damped
+models are equally capable of fitting the observed data.
+
+% As above but with eta2=1 fixed!
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$
+    \label{tab:fits-all-eta2one}}
+    \input{tab-fits-all-eta2one.tex}
+    \tablecomments{See comments on Table~\ref{tab:fits-all-eta2one}.  Fits have
+    one additional dof as $\eta_2 = 1$ is fixed.}
+\end{table}
 
@@
 
-% Radio rims very much TBD!
-
-%\begin{figure*}[ht]
-%    \centering
-%    \plotone{figures/full-man_err-prfs-radio_01.pdf}
-%    \plotone{figures/full-man_err-prfs-radio_14.pdf}
-%    \caption{Full model rim profile width predictions for Regions 1
-%    (top) and 14 (bottom) with measured data.
-%    \label{fig:rims-radio}}
-%\end{figure*}
-
-\subsection{Energy dependence rules out magnetic damping for X-ray rims}
-
-% Set-up the argument.  Claim that B damping is untenable.  Explain the
-% necessary observational consequences of B damping
-% NOTE keep numbers up to date -- after running Tycho calculations
-Our observations of strong energy-dependence, particularly at low energies
-(0.7--1 keV, 1--1.7 keV, 2--3 keV), are incompatible with magnetic damping as a
-primary remnant-wide control on filament widths.  \note[Aaron]{calculations on
-reasonable magnetic damping values of $\mE$ go here}  % TODO FILL IN
-\citetalias{ressler2014}, using the same formalism we applied to our model
-fits, stated that magnetic damping generally requires $|\mE| \lesssim 0.1$.
-Furthermore, if synchrotron rims are magnetically damped at some observation
-energy, the rims must be damped at all lower observation energies as well.
-Thus damping requires not only $\mE \sim -0.1$, but also that $\mE \sim
--0.1$ must hold for all energies below some threshold damping energy.  Above
-this energy, advective or diffusive lengthscales may shrink below the
-damping scale length so that synchrotron losses become more restrictive on rim
-widths.
-
-% Now turn to our data and say, this is not what we see.
-% NOTE keep numbers up to date
-We observe the contrapositive: mean $\mE$ values with errors in
-Table~\ref{tab:fwhms} favor $|\mE| \gtrsim 0.25$ at $\abt 1 \unit{keV}$ and
-$|\mE| \gtrsim 0.19$ at $\abt 2 \unit{keV}$, disqualifying magnetic damping at
-energies above $\sim 1 \unit{keV}$.  If thin rims are \emph{not} magnetically
-damped at our lowest energy bands, the rims will not be damped at any higher
-energies. \note[Aaron]{belaboring the point, can make more concise}
-Within the framework of our three-parameter model ($\mu$, $\eta_2$, $B_0$), the
-only workaround would be to find $\mu > 1$ diffusion that is able to produce
-$\mE > 0$; i.e., if rims widen at higher energies they may run up against any
-presumed damping scale length.  But this is unlikely as the electron energy
-cut-off shifts $\mE$ slightly negative at high energies, and diffusion only
-becomes comparable to or stronger than advection around $E \gtrsim \Ecut$.
-
-% More quantification -- give scale lengths, field strength values.
-Elaborate.  How robust is this result, quantitatively?
-What is the smallest damping scale length that is (roughly) consistent with all
-of our observations?
-\note[Aaron]{See Sean's section 3.2.1 and appendix for explication of the
-magnetic damping disfavoring etc.}
+% --------------------------------------------
+% Commentary on data, observations, parameters
+% Any constraints on parameter values go here
+% --------------------------------------------
+\subsection{Data and model fit interpretation}
+
+\subsubsection{Width-energy dependence}
 
 % Move on to address the broader trend in mE, where energy dependence weakens
-The observed decrease in $|\mE|$ with increasing energy may be attributed to
-diffusion, which weakens width-energy dependence at higher energies.
+The observed decrease in $|\mE|$ with increasing energy in data and
+(consequently) best model fits may be attributed to diffusion, which weakens
+width-energy dependence at higher energies.
 As discussed in Section~\ref{sec:energydep}, where advection dominates we
@@
 energy, $\mE$ will approach values closer to $0$.
+
 The increasing importance of diffusion at X-ray energies matches the
@@
 prior work.
-\note[Aaron]{I think the observation of rim narrowing with decreasing $|\mE|$
-is a nice result of its own -- the measurements and $\mE$ don't draw on any
-assumptions about the mechanism producing these thin rims.  The observation of
-a spectral roll-off depends on the intensity at various energies, how much flux
-comes off the rim, whereas this $|\mE|$ "relaxing" is independent of intensity.
-But I'm not sure if it's worth noting/discussing in particular.}
 
@@
 
-\subsection{Modeled diffusion and magnetic field amplification}
-
+NOTE that my discussion of diffusion may be masked by damping effects, which
+could produce a similar effect.
+
+\subsubsection{Modeled diffusion and magnetic field amplification}
+
+% TODO THIS IS FOR LOSS LIMITED MODEL ONLY.  Trek through and UPDATE
 % Discuss the degeneracy
@@
 particular fit will be ill-constrained.
-\note[Aaron]{a bit wordy}
 
@@
 Consistent with previous studies, Tycho requires strong magnetic field
-amplification -- at least $\abt 20\times$ the expected value of $\abt 10 \muG$
-from a strong shock with compression ratio $r=4$ and typical galactic magnetic
-field strength of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
+amplification -- at least $\abt 100\times$ the typical galactic field values of
+$\abt 2$--$3 \muG$, as compared to the expected $4\times$ amplification from a
+strong shock with compression ratio $r=4$.
 
@@
 
+% TODO
+IN THE DAMPED MODEL, HOWEVER, WE SEE ...
+
+The damped model in many cases still requires magnetic fields with fairly
+strong amplification!
+BUT this also depends on eta2.
+
+\subsection{Tycho distance estimates}
+
+% TODO need to update for damping results!!!!!
+
+In our modeling we adopted a distance $d$ to Tycho of $3 \unit{kpc}$, but
+various estimates for Tycho's distance range between $2.3$--$4 \unit{kpc}$
+\citep{hayato2010}.  A larger remnant distance would increase both physical
+filament widths and shock velocity estimates from proper motion (as used in our
+models).
+
+% lad/ldiff scalings give eta/B0 scalings
+For both simple and full models, we find roughly that $\eta_2 \propto d^2$
+while $B_0$ is approximately constant.  The advective lengthscale,
+equation~\eqref{eq:lad}, may be rearranged to obtain:
+\begin{align}
+    B_0 =\; &(317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
+                \nonumber \\
+            &\times \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
+                \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
+\end{align}
+% IF we keep this eqn, double check the 317 \muG carefully...
+or, more simply,
+\begin{equation}
+    B_0 \propto \left(v_d\right)^{2/3}
+                \left(l_{\mt{ad}}\right)^{-2/3} \nu^{-1/3} .
+\end{equation}
+Both $l_{\mt{ad}}$ and $v_d$ scale linearly with remnant distance $d$ and thus
+their effects cancel in determining the magnetic field.  If diffusion is the
+primary control on filament lengthscales, equation~\eqref{eq:ldiff} yields:
+\begin{equation}
+    \eta \propto \left(l_{\mt{diff}}\right)^2 B_0^{3} \nu^{-(\mu - 1)/2}
+\end{equation}
+Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
+$B_0$, from equation~\eqref{eq:diffcoeff}.
+Similar results, primarily for magnetic field $B_0$, were previously given by
+\citet{parizot2006}.
+
+In practice, both advection and diffusion are important to our filament widths,
+but we concurrently observe the scalings $\eta_2 \propto d^2$ and $B_0$
+constant in model fits with varying distance.  When comparing full model fits
+with remnant distances of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from
+the idealized scaling is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for
+$\eta_2$.
+
+One explanation is that as varying remnant distance $d$ leaves the width-energy
+scaling $\mE$ invariant, the relative contributions of $l_{\mt{ad}}$ and
+$l_{\mt{diff}}$ should also be invariant.  Then both lengthscales should
+scale simultaneously with $d$, yielding the observed behavior.
+\note[Aaron]{need a logic check here}
+
+% -------------------------------------------------------------------------
+% Main null result -- cannot disfavor either damping or loss-limited models
+% -------------------------------------------------------------------------
+\subsection{Damping is poorly-constrained by X-ray width-energy dependence}
+
+% Explain what we see, and how it's not inconsistent with the intuition we
+% presented earlier in Section~\ref{sec:energydep}
+We see that damping works okay, honestly
+
+Only in cases of very sharp energy drop-off (data and best loss-limited fit
+$\mE \sim -0.5$) is damping really disfavored as a control on rim-widths.
+
+We note that a few scenarios occur.  Our data are fairly scattered and the best
+fit width-drop-off may not be that large.  In certain cases the damping model
+is able to ``fake'' energy-dependence by measuring the FWHM at the base of the
+rim, where it fades into a plateau of emission behind the shock; here the
+energy dependence is set by synchrotron losses.  But, it does not change the
+fact that we can get this spurious dependence with smaller fields.
+
+% ------------------------------------------------------------------
+% Next steps, observations of profiles (this might fit better above)
+% ------------------------------------------------------------------
+\subsection{Tactics for constraining diffusion}
+
+\subsubsection{Damping profiles may permit better discrimination}
+
+Rather, the more sensitive discriminant would be to see if the rim shape
+coincides with what we expect.
+
+At very small damping lengths, large FWHMs
+are more difficult to obtain as a result of the model profile behavior;
+emission downstream of the thin rim may rise above the rim half-maximum,
+causing apparent rim widths to rise sharply over a small range of $B_0$ and
+$\eta_2$.
+
+Radio -- cute little rimssssssssssssssssssss.
+
+\subsubsection{Diffusion from synchrotron roll-off}
+
+A major independent observable is the synchrotron roll-off frequency.  If
+Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is independent
+of magnetic field strength and thus grants another constraint on diffusion
+coefficient, within the assumption of DSA driven electron losses.  In this
+manner, \citet{parizot2006} estimated diffusion coefficients $\eta = 10, 5$ for
+compression ratios $4, 10$ in Tycho.
+
+(formula -- give here, or above?)
+(this could be rolled into results)
+
+Speculative: we could pull out (or ourselves measure) the roll-off frequency
+from \texttt{srcut} around the remnant, then estimate a diffusion coefficient
+in each region and then get single parameter fits for magnetic field strengths?
+
+Within the framework of simple diffusive shock acceleration, the synchrotron
+cut-off frequency grants an independent estimate of diffusion strength.
+
+% TODO results from adding this to loss-lim and damped fits.  Our qualitative
+% results will be unchanged but we should do it rigorously and all...
+% This comes after I set up regions-6
+
+% -------------------------------------------
+% Model correctness - are our results valid?!
+% -------------------------------------------
+\subsection{Model correctness}
+
 % Data quality
@@
 
-\subsection{Tactics for constraining diffusion}
-
-A major independent observable is the synchrotron roll-off frequency.  If
-Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is independent
-of magnetic field strength and thus grants another constraint on diffusion
-coefficient, within the assumption of DSA driven electron losses.  In this
-manner, \citet{parizot2006} estimated diffusion coefficients $\eta = 10, 5$ for
-compression ratios $4, 10$ in Tycho.
-
-(formula -- give here, or above?)
-(this could be rolled into results)
-
-Speculative: we could pull out (or ourselves measure) the roll-off frequency
-from \texttt{srcut} around the remnant, then estimate a diffusion coefficient
-in each region and then get single parameter fits for magnetic field strengths?
-
-\subsection{Tycho distance estimates}
-
-In our modeling we adopted a distance $d$ to Tycho of $3 \unit{kpc}$, but
-various estimates for Tycho's distance range between $2.3$--$4 \unit{kpc}$
-\citep{hayato2010}.  A larger remnant distance would increase both physical
-filament widths and shock velocity estimates from proper motion (as used in our
-models).
-
-% lad/ldiff scalings give eta/B0 scalings
-For both simple and full models, we find roughly that $\eta_2 \propto d^2$
-while $B_0$ is approximately constant.  The advective lengthscale,
-equation~\eqref{eq:lad}, may be rearranged to obtain:
-\begin{align}
-    B_0 = &(317 \muG) \left(\frac{v_d}{10^8 \unit{cm/s}}\right)^{2/3}
-            \nonumber \\
-          \times \left(\frac{l_{\mt{ad}}}{0.01 \unit{kpc}}\right)^{-2/3}
-                 \left(\frac{h\nu}{1 \unit{keV}}\right)^{-1/3}
-\end{align}
-% IF we keep this eqn, double check the 317 \muG carefully...
-or, more simply,
-\begin{equation}
-    B_0 \propto \left(v_d\right)^{2/3}
-                \left(l_{\mt{ad}}\right)^{-2/3} \nu^{-1/3} .
-\end{equation}
-Both $l_{\mt{ad}}$ and $v_d$ scale linearly with remnant distance $d$ and thus
-their effects cancel in determining the magnetic field.  If diffusion is the
-primary control on filament lengthscales, equation~\eqref{eq:ldiff} yields:
-\begin{equation}
-    \eta \propto \left(l_{\mt{diff}}\right)^2 B_0^{3} \nu^{-(\mu - 1)/2}
-\end{equation}
-Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
-$B_0$, from equation~\eqref{eq:diffcoeff}.
-Similar results, primarily for magnetic field $B_0$, were previously given by
-\citet{parizot2006}.
-
-In practice, both advection and diffusion are important to our filament widths,
-but we concurrently observe the scalings $\eta_2 \propto d^2$ and $B_0$
-constant in model fits with varying distance.  When comparing full model fits
-with remnant distances of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from
-the idealized scaling is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for
-$\eta_2$.
-
-One explanation is that as varying remnant distance $d$ leaves the width-energy
-scaling $\mE$ invariant, the relative contributions of $l_{\mt{ad}}$ and
-$l_{\mt{diff}}$ should also be invariant.  Then both lengthscales should
-scale simultaneously with $d$, yielding the observed behavior.
-\note[Aaron]{need a logic check here}
-
-\subsection{Nonlinear DSA, CR-modified shocks, precursors (misc things)}
-
-Compared to our baseline assumptions for a standard strong shock ($r=4$) with
-constant magnetic field advected downstream, a treatment that permits higher
-compression ratios (from whatever instabilities or what have you) will
-generally permit weaker magnetic fields.  The reason for this, I think
-(speculating at this point due to lack of knowledge) lies in the resulting
-lower plasma velocity, which depresses the advective length scale and permits
-thinner rims more naturally (assuming diffusion not too strong).
-
-Could the gradual increase of compression ratio leading up to the shock matter,
-if CR streaming is important?  Maybe strengthen a diffusive precursor?
-
-Electron energy spectrum functional form by \citet{zirakashvili2007}, see also
-\citet{morlino2009}.
-
-Rim position variation (none obvious from preliminary look), steepness of the
-filament rise?
-% see Figure~\ref{fig:peak-pos}
-
-%\begin{figure}[ht]
-%    \centering
-%    \plotone{figures/f0-peak-pos.pdf}
-%    \caption{Best-fit rim peak positions ($x_0$ in equation~\eqref{eq:prof})
-%        for all regions as a function of energy band, normalized to the $2
-%        \unit{keV}$ peak position.  Red line plots best linear fit to all data
-%        with slope of $-0.025 \unit{arcsec/keV}$.
-%        \label{fig:peak-pos}}
-%\end{figure}
+As $D(x) \propto 1/B(x)$, the assumption that $D(x) B^2(x)$ is constant cannot
+hold near the shock in a magnetic damping model.  This assumption was invoked
+by \citep{lerche1980} to obtain a Green's function solution to
+equation~\eqref{eq:model}, but it is not clear how breaking this assumption
+impacts our model results.
+% TODO
+Add results for fits with $d(z) \propto (1 + \Delta e^{-z/a_b})^{-2}$ here...
+
+Furthermore (even if the assumption is okay), it is not clear that the
+diffusion coefficient can or should increase exponentially behind the shock.
+Expressions for $D$ in terms of unit power per log bandwidth, which is energy
+dependent as particles scatter preferentially on certain waves or whatever...
+could $D$ just be high at the shock (and that would also suggest taking $D
+\propto 1 / B_0$ rather than $D \propto 1 / B_{\mt{min}}$, for our expression
+for cut-off energy $\Ecut$, could be a problem).
+
+Quickly remark on effect of changing compression ratio (effectively dropping
+$v_d$ downstream).  In both loss-limited and damped models, a higher
+compression ratio at the shock gives rise to a lower downstream velocity, which
+permits weaker magnetic fields and diffusion.
 
@@
 \end{table*}
+
+\clearpage
+\section{Best fit stuff with $B_{\mt{min}}=2\muG$}
+
+\begin{table}[ht]
+    \scriptsize
+    \centering
+    \caption{Best model fits for all regions, $\mu = 1$, $B_{\mt{min}}=2\muG$}
+    \input{suppl-fits-all-bmin2.tex}
+\end{table}
+
+% As above but with eta2=1 fixed!
+\begin{table}[ht]
+    \scriptsize
+    \centering
+    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$,
+        $B_{\mt{min}}=2\muG$}
+    \input{suppl-fits-all-bmin2-eta2one.tex}
+\end{table}
 

### 2014-10-23 code/models/tables/gen_scripts/tab_tycho_all_20141023.py

@@ -1,0 +1,116 @@
+"""
+Tabulate FWHMs for Tycho for
+1. no damping, all 6 mu values; four shock velocity values
+   [4.59e8, 4.76e8, 4.94e8, 5.11e8]
+   20+ B0 values (ask for 20, expect ~30)
+2. various magnetic damping scale lengths, with default shock veloc
+   (3.6e8 * 3/2.3 = 4.696e8 cm/s ...)
+   50+ B0 values (ask for 50, expect 10--70)
+
+  `a_b` values I use are:
+      0.5,    0.05,   0.04,   0.03,
+      0.02,   0.01,   0.009,  0.008,
+      0.007,  0.006,  0.005,  0.004,
+      0.003,  0.002
+
+Default rminarc, Bmin = 5 microGauss.
+151 eta2 values log-spaced between [0.01, 100] with 2x sampling in [0.1, 10].
+
+Numbers now hardcoded into table generating script (makes more sense)
+Call script with flag 0, 1, 2, 3 and it will load the correct values.
+I don't know why I didn't do this before (since the principle is that this
+script is essentially a "config" file of sorts).
+
+to try to balance the load of calculations (I have gone diagonally in this
+table).
+
+
+Aaron Tran
+2014 October 23
+"""
+
+from __future__ import division
+
+import argparse
+from datetime import datetime
+import numpy as np
+
+import models
+import snr_catalog as snrcat
+
+
+VS_VALS_ALL = [4.59e8, 4.76e8, 4.94e8, 5.11e8]
+AB_VALS_ALL = [[0.5,  0.01,  0.005],
+               [0.05, 0.009, 0.004, 0.003],
+               [0.04, 0.008, 0.007, 0.002],
+               [0.03, 0.02,  0.006]]
+
+# Numbers are generated from regions-4 with simple 2-exponential fit
+# Max observed FWHM for 0.7-1keV was 6.092
+# But I use 10 to be more consistent w/ general trend
+# (matches previous tables)
+TYCHO_KEVS = np.array([0.7, 1.0, 2.0, 3.0, 4.5])
+TYCHO_DATA_MIN = np.array([1.628, 1.685, 1.510, 1.465, 1.370])
+TYCHO_DATA_MAX = np.array([10.0, 8.866, 6.901, 7.508, 5.763])
+
+
+def main():
+    parser = argparse.ArgumentParser(description='Table generator')
[…]

### 2014-10-24 manuscript/paper-tycho.tex
Paper draft 10/24, faster adaptive errors
Paper draft sent around; adaptive error code steps more quickly
(better criteria for changing step size based on chi-sqr threshold)

@@
 \documentclass[iop, apj, numberedappendix]{emulateapj}
+
+% Customize figures/sizing for 2 column vs. manuscript printout
+\usepackage{etoolbox}
+\newtoggle{manuscript}
+%\toggletrue{manuscript}
+\togglefalse{manuscript}
 
@@
 \newcommand*{\Ecut}{E_{\mt{cut}}}
+\newcommand*{\Bmin}{B_{\mt{min}}}
 \newcommand*{\muG}{\unit{\mu G}}
@@
 \begin{abstract}
-\note[Aaron]{Modified from AAS abstract - first pass update}
 Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
@@
 upon our understanding of CR acceleration in Tycho.
-\note[Aaron]{can reword/cut?}
 
@@
 below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
-the radio index $\alpha$ as $s = 2\alpha + 1$.
+the radio index $\alpha$ as $s = 2\alpha + 1$.  \citet{zirakashvili2007} have
+derived from DSA a slightly different energy spectrum with super-exponential
+cut-off $e^{-(p/p_{\mt{cut}})^2}$, which may impact our results; we use a
+simple exponential cut-off for simplicity and consistency with
+\citetalias{ressler2014}.
 
@@
 \begin{equation} \label{eq:bdamp}
-    B(x) = \left(B_0 - B_{\mt{min}}\right) \exp\left(-x / a_b\right)
-           + B_{\mt{min}}
+    B(x) = \left(B_0 - \Bmin\right) \exp\left(-x / a_b\right)
+           + \Bmin
 \end{equation}
@@
 $B_0$.
-\note[Aaron]{Is this correct?  Can try rederiving the expression (particles
+\note[Aaron]{Is this correct?  Can rederive the expression (particles
 penetrate some distance downstream, then back), but I'm not sure if it's even
 sensible with diffusion coefficient varying so sharply.}
+
+The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
+rettig2012} assume $D(x) B^2(x)$ constant in order to make the equation
+semi-analytically tractable.  Although unphysical, we enforce this criterion by
+using a modified diffusion coefficient in our calculations following
+\citet{rettig2012}, given as:
+\begin{equation} \label{eq:ddamp}
+    D(E,x) = \frac{\eta C_d E^\mu}{B_0}
+             \left[ \frac{\Bmin}{B_0} +
+                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
+\end{equation}
+This has the unfortunate effect of strengthening the spatial-dependence of the
+diffusion coefficient, which may or may not be physical.
+\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
+will check shortly}
 
@@
 
+We shall see below that this is qualitatively correct in setting model
+predictions of rim shapes (within $\abt a_b$ of the shock front), but our
+results are complicated by the increasing importance of energy-dependent
+synchrotron losses downstream of the thin rim.  As we use FWHM as a singular
+proxy for rim shapes, our procedure is not able to discern the transition in
+shape downstream of the damped rim that may impact profile FWHMs, even as
+damping controls the main observed rim emission.
+
 % A comment
@@
     \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
+    }{
         \plotone{figures/f0-snr-inv.png}
+    }
     \caption{RGB image of Tycho with region selections overlaid.  Image bands
@@
 \begin{figure*}
-    \plotone{figures/spec_01.pdf}
+    \iftoggle{manuscript}{
+        \epsscale{0.7}
+    }{}
+    \plotone{figures/spec_01.pdf} \\
     \plotone{figures/spec_16.pdf}
@@
 \begin{figure*}%[ht]
+    \iftoggle{manuscript}{
+        \epsscale{1}
+    }{}
     \plotone{figures/prfs_01.pdf}
@@
 $\eta_2$, diffusion-energy scaling exponent $\mu$, and minimum field strength
-$B_{\mt{min}}$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
+$\Bmin$ and lengthscale $a_b$ for a damped magnetic field scenario.  We
 mapped each width measurement to the lower energy limit of its energy band;
@@
 For damped magnetic field fits, we held the asymptotic field strength
-$B_{\mt{min}}$ inside the remnant constant at $5 \muG$, slightly higher than
+$\Bmin$ inside the remnant constant at $5 \muG$, slightly higher than
 typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
@@
 constant and damped magnetic field.  We also attempted damping fits with
-$B_{\mt{min}} = 2 \muG$, somewhat on the lower end of estimated galactic
+$\Bmin = 2 \muG$, somewhat on the lower end of estimated galactic
 magnetic field values.
@@
 \begin{table*}
-    % Use \tiny for manuscript; \scriptsize for 2-column
+    \iftoggle{manuscript}{
         \tiny
-    %\scriptsize
+    }{
+        \scriptsize
+    }
     \centering
@@
 Measured rim widths decrease with energy in most regions and energy bands.
-Although the measurement variation between measurements is quite large, shown
-dramatically in the point-wise computed $\mE$ values, the mean rim width
-decreases consistently with increasing energy.  Furthermore, mean $\mE$ values
-are consistently negative and tend smoothly towards $0$ (weaker
-energy-dependence) with increasing energy.
+Although the measurement scatter is quite large, shown dramatically in the
+point-wise computed $\mE$ values, the mean rim width decreases consistently
+with increasing energy.  Furthermore, mean $\mE$ values are consistently
+negative and tend smoothly towards $0$ (weaker energy-dependence) with
+increasing energy.
 
@@
 % Explain our approach
-We tabulate and plot fitting results for Regions 1 and 16, the same regions
+We tabulate and plot detailed results for Regions 1 and 16, the same regions
 shown in Figures~\ref{fig:spec} and \ref{fig:profiles}.  Although only a small
@@
 exemplified by Regions 1 and 16.  Best fit results for all regions are
-summarized in Tables~\ref{tab:fits-all}, \ref{tabs:fits-all-eta2one}.  In all
+summarized in Tables~\ref{tab:fits-all}, \ref{tab:fits-all-eta2one}.  In all
 tables, we report values of $\chi^2$ rather than $\chi^2_\mt{red}$ to ease
@@
     \centering
-    \plotone{figures/full-man_err-prfs_01.pdf}
+    \iftoggle{manuscript}{
+        \epsscale{0.5}
+    }{}
+    \plotone{figures/full-man_err-prfs_01.pdf} \\
     \plotone{figures/full-man_err-prfs_16.pdf}
@@
         (top) and 16 (bottom) for loss-limited and damped scenarios with
-        $\mu = 1$ fixed.  Shaded regions on damped profiles indicate the
-        damping ($e$-folding) lengthscale for the magnetic field.  Note that
-        radial coordinate ($r$) axes agree in each row (same region), but not
-        in each column.
+        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Shaded
+        regions on damped profiles indicate the damping ($e$-folding)
+        lengthscale for the magnetic field.  Note that radial coordinate ($r$)
+        axes agree in each row (same region), but not in each column.
     \label{fig:rims}}
@@
     %\epsscale{0.45}  % For manuscript layout only!
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-01.pdf}
+        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-16.pdf}
+    }{
         \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-01.pdf}
         \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-16.pdf}
+    }
     \caption{Full model width predictions as a function of energy for Regions 1
@@
 ill-constrained (e.g., $\eta_2 > 10^3$ or $B_0 > 10^3 \muG$).  Fits with $\mu
-\gtrsim 1$ generally yield smaller $\chi^2$ values in a majority of regions
-($\abt 17$ of $20$), although we do not explore the robustness of this
-observation.  Fits for the same data, with varying $\mu$, can yield $\eta_2$
-that vary by $1$--$2$ orders of magnitude; Region 16 illustrates this
-dramatically (Table~\ref{tab:fits-loss}).
+\gtrsim 1$ yield smaller $\chi^2$ values in a majority of regions ($\abt 17$ of
+$20$), although we do not explore the robustness of this observation.  Fits to
+the same data with varying $\mu$ can yield $\eta_2$ varying by $1$--$2$ orders
+of magnitude; Region 16 illustrates this dramatically
+(Table~\ref{tab:fits-loss}).
 
@@
 
+Here we first explore trends in our data and best-fit diffusion and magnetic
+fields.  We then discuss discrimination of the loss-limited and damping models
+(i.e., our ability to favor or constrain a finite value of $a_b$), and possible
+paths forward to better constrain our model parameters.
+
 % --------------------------------------------
 % Commentary on data, observations, parameters
+% Tycho distance estimates, maybe compression ratio stuff...
 % Any constraints on parameter values go here
@@
 
-% Move on to address the broader trend in mE, where energy dependence weakens
-The observed decrease in $|\mE|$ with increasing energy in data and
-(consequently) best model fits may be attributed to diffusion, which weakens
-width-energy dependence at higher energies.
-As discussed in Section~\ref{sec:energydep}, where advection dominates we
-expect $w \sim l_{\mt{ad}} \propto \nu^{-1/2}$ or $\mE \approx -0.5$.  As
-diffusion outpaces advection for energies near and above the electron cut-off
-energy, $\mE$ will approach values closer to $0$.
-
-The increasing importance of diffusion at X-ray energies matches the
-synchrotron spectrum roll-off at X-ray energies as compared to radio
-observations; the criterion for synchrotron roll-off, or electron cut-off, is
-equivalent to requiring that advective and diffusive lengthscales are
-comparable.  Thus, a weakening energy dependence in X-rays is consistent with
-prior work.
-
-% Addressing the variability in width measurements
-The large variation in filament widths and point-wise computed $\mE$ values
-renders our interpretation of $\mE$ more conjectural.  Multiple regions show both
-increases and decreases in filament widths between multiple energy bands (e.g.,
-Region 9).  But, our averaged results should mitigate this natural measurement
-spread.
-
-NOTE that my discussion of diffusion may be masked by damping effects, which
-could produce a similar effect.
+% First address the broad trend of leveling energy dependence in mE)
+We suggest that our observed decrease in $|\mE|$ with increasing energy is
+caused by diffusion, which weakens width-energy dependence at higher energies.
+The photon energy at which advection and diffusion are comparably important
+($l_{\mt{ad}} = l_{\mt{diff}}$) is exactly the synchrotron roll-off energy,
+$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Then we expect diffusion to
+begin overtaking advection and depress $\mE$ towards $0$ in soft X-rays, as
+opposed to $\mE \abt -0.5$ expected when advection is important
+(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
+consistent with the framework of diffusive shock acceleration.
+
+% This conclusion is based strictly on our measurements.
+% Our transport model hard-codes this width leveling through \Ecut
+
+% Discuss variability in width measurements
+The large scatter in filament widths and hence point-wise computed $\mE$ values
+(Table~\ref{tab:fwhms}) does relegate our interpretation of $\mE$ to conjecture.
+Multiple regions show both increases and decreases in filament widths between
+energy bands, and we have seen that diffusion ($\eta_2$) is poorly constrained
+by our fit results.  Our averaged results should mitigate this natural
+measurement spread, however.
+
+% Can damping explain stuff?
+The next question is whether damping may also produce this effect, independent
+of assumptions on the shock acceleration process.  Conceptually, if damping
+controls rim widths past the cut-off energy, $|\mE|$ may slightly decrease or
+even increase as rims transition from being damping controlled to being
+diffusion loss-limited.  If damping is only important well below the cut-off
+energy, then we may see an increase in $|\mE|$ as advection becomes important.
+Although magnetic damping is able to fit observed rim widths, our model assumes
+diffusive shock acceleration in computing $\Ecut$ and hence we may not use our
+model fits to assess whether magnetic damping can independently account for
+decreasing $|\mE|$.
+
+% Curious effects of damping competing with other things
+Downstream energy losses in a well damped field (multiple $e$-folding
+lengths ($a_b$) downstream) may also introduce energy dependence in rim widths.
+Sufficiently energetic electrons will radiate and cool within the damping
+length $a_b$, but lower energy electrons will perceive a relatively constant
+field $\abt \Bmin$ downstream of the shock.  Synchrotron losses will
+``sieve'' out higher energy electrons as in the loss-limited model, and
+observed rim widths, if larger than $a_b$, may be somewhat loss-limited at low
+energies, well-confined by damping at moderate energies, then diffusion (or
+cut-off spectrum) limited at the highest energies.
+
+We revisit the effects of damping further below.  The observation of decreasing
+$|\mE|$, however, remains consistent with and expected from the theory of
+diffusive shock acceleration.
 
@@
 
-% TODO THIS IS FOR LOSS LIMITED MODEL ONLY.  Trek through and UPDATE
-% Discuss the degeneracy
+% Discuss degeneracy in loss-limited and damped models both
 We now turn to our model fit parameters: magnetic field strength $B_0$ and
-scaled diffusion coefficient $\eta_2$.  Our model fit results are poorly
-constrained as the parameters $B_0$ and $\eta_2$ may covary without strongly
-altering fit quality.  Equations~\eqref{eq:lad} and $\eqref{eq:ldiff}$
-illustrate this clearly.  Varying $B_0$ changes both $l_{\mt{ad}}$ and
-$l_{\mt{diff}}$ evenly; varying $\eta_2$ (and hence $\eta$) changes only
-$l_{\mt{diff}}$, in principle.  But, if diffusion is the primary control on rim
-width -- i.e., $l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim
-l_{\mt{diff}}$) -- we see that $\eta_2$ and $B_0$ become almost entirely
-degenerate.  Ramping up particle diffusion and hence rim widths can be
-perfectly counteracted by increasing magnetic fields and forcing electrons to
-cool faster, decreasing rim widths.  If advection is the primary control on rim
-width (widths narrow rapidly with energy, at $\mE \sim -0.5$), then $\eta_2$
-becomes unimportant and the fit is better behaved with effectively one free
-parameter.  The degeneracy of $B_0$ and $\eta_2$ is generally stronger for
-smaller values of $\mu$, although there appears no clear trend as to when a
-particular fit will be ill-constrained.
-
-% B0 lower bounds, etc.
-A minimum magnetic field strength $B_0 \gtrsim 179 \muG$, within stated
-errors, is required throughout the remnant.  The minimum values of $B_0$ for
-each filament (1--5) are $179$, $254$, $287$, $458$, and $243 \muG$.
-We observe the smallest $B_0$ values for $\eta_2$ approaching $0$ and $\mu =
-2$; intuitively, $\mu = 2$ favors diffusion at higher energies ($>2\unit{keV}$)
-where it is most ``needed'' to reproduce the leveling off of filament widths
-and so $\mu = 2$ permits a smaller best-fit $\eta_2$ and hence smaller $B_0$.
-\note[Aaron]{$\mu=2$ bit not very important}
-Our minimum values of $B_0$ are consistent with prior estimates of
-$\abt 200$--$300 \muG$ for primarily advective transport
-\citep{volk2005, parizot2006, morlino2012} \note[Aaron]{could elaborate and
-review previous work; deferring for now}.  A larger range of values has been
-obtained ($130$--$500 \muG$) when considering additional effects, such as
-varying compression ratio and nonlinear diffusion-energy scaling
-\citep{parizot2006, cassam-chenai2007}.
-
-Consistent with previous studies, Tycho requires strong magnetic field
-amplification -- at least $\abt 100\times$ the typical galactic field values of
-$\abt 2$--$3 \muG$, as compared to the expected $4\times$ amplification from a
-strong shock with compression ratio $r=4$.
+scaled diffusion coefficient $\eta_2$.  Our loss-limited fit results are poorly
+constrained as $B_0$ and $\eta_2$ may covary without strongly altering fit
+quality.  If diffusion is the primary control on rim width -- i.e.,
+$l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim l_{\mt{diff}}$) --
+then $\eta_2$ and $B_0$ become degenerate as the product $\eta^{1/2}
+B_0^{-3/2}$ exerts most control on rim width $w$.  If advection is the primary
+control on rim width (widths narrow rapidly with energy, at $\mE \sim -0.5$),
+then $\eta_2 \ll 1$ becomes unimportant and the fit is better behaved with
+effectively one free parameter.  The degeneracy of $B_0$ and $\eta_2$ is
+stronger for smaller values of $\mu$, although there appears no clear trend as
+to when a particular fit will be ill-constrained.
+
+In the damped model, a similar degeneracy is present but modified somewhat by
+the presence of damping.  For small values of $a_b$ (strong damping), increased
+diffusion $\eta_2$ can cause rim widths to \emph{narrow}, contrary to
+intuition; $B_0$ and $\eta_2$ generally covary in controlling rim widths, but
+the relationship is now less clear.  Speculatively, the opposition to
+downstream flow may be tied to the spatial variation of the diffusion
+coefficient, which gives rise to an additional term $-(\ptl D(x) / \ptl x)
+(\ptl f/\ptl x)$ that opposes downstream flow in equation~\eqref{eq:model}.
+
+% NOTE some of this discussion of parameter values could go
+% into results instead.
+
+% B0 lower bounds, etc. in loss-limited model
+In our loss-limited model fits, the minimum magnetic field strength we observe
+throughout the remnant, within stated errors, is $B_0 = 179 \muG$.  The minimum
+values of $B_0$ for each filament (1--5) are $179$, $254$, $287$, $458$, and
+$243 \muG$.  We observe the smallest $B_0$ values for $\eta_2$ approaching $0$
+and $\mu = 2$; intuitively, $\mu = 2$ gives stronger diffusion at higher
+energies ($>2\unit{keV}$) where it is most ``needed'' to reproduce the leveling
+off of filament widths and so $\mu = 2$ permits a smaller best-fit $\eta_2$ and
+hence smaller $B_0$.  Furthermore, when $\eta_2 = 1$ is fixed we find that
+$B_0$ is well-constrained in the loss-limited model, falling strictly between
+$180$--$500 \muG$ (Table~\ref{tab:fits-all-eta2one}).  In this scenario the
+range of $B_0$ values is directly correlated to the observed range of rim
+widths.  Our minimum loss-limited values of $B_0$ are consistent with prior
+estimates of $\abt 200$--$300 \muG$ for primarily advective transport
+\citep{volk2005, parizot2006, morlino2012}.  If loss-limited, Tycho's rims
+require strong magnetic field amplification -- at least $\abt 100\times$ the
+typical galactic field values of $\abt 2$--$3 \muG$, versus the expected
+$4\times$ amplification from a strong shock with compression ratio $r=4$.
+
+The damped model fits permit much smaller values of $B_0$, as expected.
+The maximum best-fit $B_0$ value observed is $600 \muG$, with most values
+typically below $300 \muG$.  The minimum value of $B_0$ is around $10$--$20
+\muG$, which is consistent with shock compression alone.
+Fixing $\Bmin = 2 \muG$ instead of $5 \muG$ generally permits smaller
+fit $B_0$ values, though both $\eta_2$ and $B_0$ still display a large spread.
 
@@
 
-% 1-2 paragraphs on eta2
-The values of $\eta_2$ in Tables~\ref{tab:fits} and \ref{tab:fits-pt2} are very
-poorly constrained.  We observe no clear trend of $\eta_2$ with $\mu$, and the
-values and error bounds on $\eta_2$ are often unreasonably large.  The extreme
-outliers limit the usefulness of the average fit parameters presented in
-Table~\ref{tab:fits-avg}.
-
-Our model fits do generally favor $\eta_2 \geq 1$, respecting the Bohm limit on
-diffusion.  The lowest error bound on $\eta_2$ in the averaged best-fit values
-is $1.2$, with minimum error bounds in each filament of order $1$--$10$.  For
-individual regions' best fits, only Regions 5 and 18 have best-fit $\eta_2$
-values falling strictly below $\eta_2 = 1$.  \note[Aaron]{I think Region 5 is
-skewed by the unusually large 0.7--1 keV FWHM.  Region 18 is a weird place, a
-smushed-out and somewhat faint filament in the NE where Bohm just bombs and rim
-widths narrow strongly.}
+% eta2
+% NOTE keep notes on eta2 < 1 updated (region 5 should be better, after I
+% remove the bad FWHM)
+The best-fit values of $\eta_2$, for both loss-limited and damped fits,
+are very poorly constrained.  In the loss-limited fits, we observe no clear
+trend of $\eta_2$ with $\mu$ (Table~\ref{tab:fits-loss}) excepting a general
+preference for smaller $\eta_2$ at $\mu > 1$.  Loss-limited fits are generally
+consistent with the Bohm limit on diffusion, favoring $\eta_2 \geq 1$; only
+Regions 5 and 18 have best-fit $\eta_2$ values strictly below $\eta_2 = 1$
+within error.  Damped fits permit smaller values of $\eta_2$ in contrast to
+loss-limited models, perhaps as stronger damping and smaller $\eta_2$ have
+cancelling effects on rim widths (recalling that in the damped model, smaller
+$\eta_2$ gives larger rim widths).
 
 % A quick discussion of mu
-Our fits at multiple values of $\mu$ are not especially insightful either.
-The $\chi^2_{\mt{red}}$ values for individual fits are variable and quite
-large, so they may not be reliable for favoring or disfavoring fits at
-different $\mu$ values.  But, if we ignore this caveat, we see that values
-of $\mu \geq 1$ are qualitatively favored by $\chi^2_{\mt{red}}$ in almost all
-regions.  This trend may be an partially an artifact of the correlation between
-$B_0$ and $\eta_2$ as they are not entirely independent parameters, but they
-are less correlated for larger $\mu$.  However, our computed
-$\chi^2_{\mt{red}}$ values have simply assigned a single degree of freedom to
-each parameter.  \citetalias{ressler2014} also found better model fits for $\mu
-\geq 1$ in the remnant of SN 1006 and noted that \citet{reynolds2004} favored
-$\mu \geq 1$ on grounds of better modeled remnant morphology, but it remains
-uncertain whether $\mu \geq 1$ diffusion is truly preferred.
-
-% TODO
-IN THE DAMPED MODEL, HOWEVER, WE SEE ...
-
-The damped model in many cases still requires magnetic fields with fairly
-strong amplification!
-BUT this also depends on eta2.
-
-\subsection{Tycho distance estimates}
-
+Our fits at multiple values of $\mu$ are not especially insightful.
+The $\chi^2$ values for individual fits are variable and quite large, so we are
+unable to favor or disfavor fits at different $\mu$ values.  But, neglecting
+caution, we observed that values of $\mu \geq 1$ are qualitatively favored by
+$\chi^2$ in almost all regions.  This trend may be an partially an artifact of
+the correlation between $B_0$ and $\eta_2$ as they are not entirely independent
+parameters, but they are less correlated for larger $\mu$; it may be said that
+fits at smaller $\mu$ may have fewer (non-integer) degrees of freedom,
+partially offsetting our observations.  \citetalias{ressler2014} also found
+better model fits for $\mu \geq 1$ in the remnant of SN 1006 and noted that
+\citet{reynolds2004} favored $\mu \geq 1$ on grounds of better modeled remnant
+morphology, but it remains uncertain whether $\mu \geq 1$ diffusion is truly
+preferred.
+
+We do not explore $\mu$ dependence extensively in the damped model, but we find
+that $\mu > 1$ permits smaller $B_0$ values and \emph{larger} $\eta_2$ values,
+in keeping with our previous discussion of the effects of $B_0$ and $\eta_2$ on
+rim width in both loss-limited and damped models.
+
+\subsubsection{Tycho distance estimates}
 % TODO need to update for damping results!!!!!
@@
 % lad/ldiff scalings give eta/B0 scalings
-For both simple and full models, we find roughly that $\eta_2 \propto d^2$
-while $B_0$ is approximately constant.  The advective lengthscale,
+In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ while
+$B_0$ is approximately constant.  The advective lengthscale,
 equation~\eqref{eq:lad}, may be rearranged to obtain:
@@
 \end{align}
-% IF we keep this eqn, double check the 317 \muG carefully...
+% TODO if we keep this equation, double check the 317 \muG carefully...
 or, more simply,
@@
 Recall that $\eta \propto \eta_2$ since $E_h = E_2$ is constant for a given
-$B_0$, from equation~\eqref{eq:diffcoeff}.
-Similar results, primarily for magnetic field $B_0$, were previously given by
-\citet{parizot2006}.
+$B_0$, from equation~\eqref{eq:diffcoeff}.  Similar results, primarily for
+magnetic field $B_0$, were previously given by \citet{parizot2006}.
 
 In practice, both advection and diffusion are important to our filament widths,
-but we concurrently observe the scalings $\eta_2 \propto d^2$ and $B_0$
-constant in model fits with varying distance.  When comparing full model fits
-with remnant distances of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from
-the idealized scaling is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for
-$\eta_2$.
-
-One explanation is that as varying remnant distance $d$ leaves the width-energy
-scaling $\mE$ invariant, the relative contributions of $l_{\mt{ad}}$ and
-$l_{\mt{diff}}$ should also be invariant.  Then both lengthscales should
-scale simultaneously with $d$, yielding the observed behavior.
+but both scalings $\eta_2 \propto d^2$ and $B_0$ constant occur in model fits
+with varying distance.  When comparing full model fits with remnant distances
+of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from the idealized scaling
+is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for $\eta_2$.  As varying
+remnant distance $d$ leaves width-energy scaling $\mE$ invariant, the relative
+contributions of $l_{\mt{ad}}$ and $l_{\mt{diff}}$ should also be invariant.
+Then both lengthscales should scale simultaneously with $d$, yielding the
+observed behavior.
 \note[Aaron]{need a logic check here}
+
+% Damping and remnant distance
+In the damped model, a larger distance $d$ will require larger damping lengths
+from magnetic turbulence; our values of $a_b$ should be unchanged, however, as
+$a_b$ here is given in units of shock radius $r_s$.
+% TODO run more fits with varying remnant distance...
+% After I've gotten new sets of numbers set up
 
@@
 
-% Explain what we see, and how it's not inconsistent with the intuition we
-% presented earlier in Section~\ref{sec:energydep}
-We see that damping works okay, honestly
-
-Only in cases of very sharp energy drop-off (data and best loss-limited fit
-$\mE \sim -0.5$) is damping really disfavored as a control on rim-widths.
-
-We note that a few scenarios occur.  Our data are fairly scattered and the best
-fit width-drop-off may not be that large.  In certain cases the damping model
-is able to ``fake'' energy-dependence by measuring the FWHM at the base of the
-rim, where it fades into a plateau of emission behind the shock; here the
-energy dependence is set by synchrotron losses.  But, it does not change the
-fact that we can get this spurious dependence with smaller fields.
+\begin{table*}[ht]
+    \scriptsize
+    \centering
+    \caption{$m_\mt{E}$ from best model fits, loss-limited and damped
+        \label{tab:fits-mE}}
+    \input{suppl-fits-mE.tex}
+    \tablecomments{Best fits correspond to those given in
+        Table~\ref{tab:fits-all}}
+\end{table*}
+
+Width-energy dependence is not as sensitive a discriminant on damping versus
+loss-limited models as may be intuitively expected.  Only in cases of very
+sharp energy drop-off (data and best loss-limited fit $\mE \sim -0.5$) is
+damping significantly disfavored as a control on rim widths (Region 18).  To
+illustrate this behavior in our fits more clearly, Table~\ref{tab:fits-mE}
+lists $\mE$ values as computed from both best loss-limited and damping fits.
+This condenses and quantifies the width-energy predictions shown in
+Figure~\ref{fig:fits}.
+
+Both loss-limited and damped fits do not perfectly capture sharp drop-offs
+(especially between $0.7$--$1 \unit{keV}$ and $1$--$2 \unit{keV}$), and the
+data are greatly scattered.  In most regions, best fit width-energy curves have
+$\mE \sim -0.2$ (Table~\ref{tab:fits-mE}).
+
+% Explain the spurious energy dependence thing
+When width-energy dependence is small, both loss-limited and damped rims give
+best fits with very similar shapes -- strong fields at the shock in both models
+give very sharp drop-offs in rim intensity.  When energy dependence is larger,
+damping profiles can only yield energy dependent rims if magnetic fields are
+fairly small (say, $\lesssim 50 \muG$) and rim half-maximums are achieved some
+distance away from the damping lengthscale.  Away from the shock, magnetic
+damping has already weakened and electron losses are controlled by synchrotron
+losses which act differentially on the range of electron energies we consider.
+% TODO horrific wording.  "act differentially?"
+
+% TODO somehow highlight this, or think of a way to differentiate the regions
+% Arbitrary yes, but I think it highlights the idea...
+Each of these cases is illustrated in Figure~\ref{fig:rims}; in Region 1 the
+damping profiles are quite distinct from the loss-limited profiles, whereas in
+Region 16 they appear quite similar.  Regions 1, 2, 4, 5, 12, and 18 are best
+fit in a damping model with fields $B_0 < 30 \muG$; the remaining regions have
+$B_0 > 80 \muG$.  These regions are the same ones characterized by larger best
+fit $\mE$ values in Table~\ref{tab:fits-mE}, with $\mE \lesssim -0.3$
+generally, especially at lower energies.  The remaining regions are
+characterized by $\mE \sim -0.2$, or $\mE$ decreasing (stronger width-energy
+dependence) at \emph{higher} energies rather than lower energies.  The effect
+of stronger energy dependence is conceptually expected in the damping model
+when the advection lengthscale falls beneath the damping lengthscale at high
+energies (Section~\ref{sec:energydep}).
 
@@
 
-\subsubsection{Damping profiles may permit better discrimination}
-
-Rather, the more sensitive discriminant would be to see if the rim shape
-coincides with what we expect.
-
-At very small damping lengths, large FWHMs
-are more difficult to obtain as a result of the model profile behavior;
-emission downstream of the thin rim may rise above the rim half-maximum,
-causing apparent rim widths to rise sharply over a small range of $B_0$ and
-$\eta_2$.
-
-Radio -- cute little rimssssssssssssssssssss.
+\subsubsection{Fits to whole damping profiles}
+
+The distinct profile shapes, of both thin rims and plateauing emission just
+downstream of the thin rims, may be more sensitive discriminants of
+loss-limited and damping models.  In particular, our best fits to data with
+moderate $\mE$ generally require small magnetic field $B_0$ and comparatively
+strong emission downstream of the thin rim, just below the rim half-maximum.
+Although the FWHMs accorded with those of the loss-limited, the profiles were
+quite different (Figure~\ref{fig:rims}).
+
+Moreover, we selected only regions on Tycho where a FWHM could be resolved.
+A subset of parameters (small damping lengths, small magnetic fields, and weak
+or even sub-Bohm diffusion) can produce weaker thin rims that do not decrease
+downstream to a half-maximum intensity; several nonthermal filaments around
+Tycho exhibit similar behavior of a weak rim at the shock, followed by strong
+downstream emission.  If profiles can be measured as far back as possible,
+while avoiding thermal emission, we may be able to place stronger constraints
+on allowed values of $B_0$, $\eta_2$, and $a_b$.
+
+\subsubsection{Radio rim measurements}
+
+Radio rims may provide an additional constraint on magnetic field structure.
+The presence of radio rims may reflect 1. age-limited electron propagation (set
+by the timescale needed to accelerate electrons and remnant expansion), 2.
+possible reverse shock accelerated electrons, or 3. magnetic damping.  In our
+steady-state transport model (equation~\eqref{eq:model}), the loss-limited
+model \emph{cannot} produce radio rims.  Thin rims of radio emission in Tycho,
+if not due to instabilities or other projected structure at the shock, can only
+be attributed to magnetic damping.  But, the bulk of radio emission in Tycho
+($r \lesssim 0.9 r_s$) may not be safely modeled as time-independent.
+
+Synchrotron radio emission is emitted by \~ GeV electrons and hence diffusion
+is essentially negligible; observed rims (or lack thereof) are primarily
+controlled by $B_0$ and $a_b$.  It further follows that we needn't worry about
+the precise electron cut-off energy, and we may be able to solve the transport
+equation analytically (or otherwise circumvent the questionable assumption that
+$D(x) B^2(x)$ is constant).  However, we note that our diffusion coefficients
+have assumed that the mean free path is set by gyroradius (linearly so if
+$\mu = 1$), and the Bohm limit $\eta = 1$ of our diffusion coefficients is
+merely an expected lower limit on diffusion.  We may need a more accurate model
+for particle diffusion at radio wavelengths.
+
+The radio emission profiles from Tycho has been explored by
+\citet{cassam-chenai2007} and \citet{morlino2012}; both studies assumed
+moderate magnetic damping downstream of the shock.  Their discussions of radio
+profiles were undertaken in context of a broader, more concerted hydrodynamic
+modeling effort (which would be necessary to consider the internal radio
+emission, rather than just the shock front emission).  In future work we will
+consider a similar analysis as carried out in this paper, using radio rims to
+help constrain X-ray rim parameters.
 
@@
 
-(formula -- give here, or above?)
-(this could be rolled into results)
-
-Speculative: we could pull out (or ourselves measure) the roll-off frequency
-from \texttt{srcut} around the remnant, then estimate a diffusion coefficient
-in each region and then get single parameter fits for magnetic field strengths?
-
-Within the framework of simple diffusive shock acceleration, the synchrotron
-cut-off frequency grants an independent estimate of diffusion strength.
-
-% TODO results from adding this to loss-lim and damped fits.  Our qualitative
-% results will be unchanged but we should do it rigorously and all...
-% This comes after I set up regions-6
+We can measure the roll-off frequency in all regions, fix the diffusion
+coefficient at a given value of $\mu$, and obtain single parameter fits for
+$B_0$ (or two parameter fits for $B_0$ and $a_b$) at each value of $\mu$.
+Conceptually, this is comparable to our fits with $\eta_2 = 1$ fixed
+(Table~\ref{tab:fits-all-eta2one}) and should not greatly affect our
+conclusions.  However, if the diffusion coefficient from the roll-off frequency
+is indeed well-constrained, then parameter estimates based on deduced diffusion
+coefficients may be more reliable.
 
@@
 from averaging measurements or selecting larger regions will not improve our
-ability to constrain $B_0$ and $\eta_2$.  This is easily seen from reduced
-$\chi^2$ values in Tables~\ref{tab:fits} and \ref{tab:fits-pt2}, which
-reflect relatively tight errors in our FWHM profile measurements
-(Table~\ref{tab:fwhms}).
-
-As $D(x) \propto 1/B(x)$, the assumption that $D(x) B^2(x)$ is constant cannot
-hold near the shock in a magnetic damping model.  This assumption was invoked
-by \citep{lerche1980} to obtain a Green's function solution to
-equation~\eqref{eq:model}, but it is not clear how breaking this assumption
-impacts our model results.
-% TODO
-Add results for fits with $d(z) \propto (1 + \Delta e^{-z/a_b})^{-2}$ here...
-
-Furthermore (even if the assumption is okay), it is not clear that the
-diffusion coefficient can or should increase exponentially behind the shock.
-Expressions for $D$ in terms of unit power per log bandwidth, which is energy
-dependent as particles scatter preferentially on certain waves or whatever...
-could $D$ just be high at the shock (and that would also suggest taking $D
-\propto 1 / B_0$ rather than $D \propto 1 / B_{\mt{min}}$, for our expression
-for cut-off energy $\Ecut$, could be a problem).
-
-Quickly remark on effect of changing compression ratio (effectively dropping
-$v_d$ downstream).  In both loss-limited and damped models, a higher
-compression ratio at the shock gives rise to a lower downstream velocity, which
-permits weaker magnetic fields and diffusion.
+ability to constrain $B_0$ and $\eta_2$.  This is easily seen from
+Figure~\ref{fig:fits} as well as large $\chi^2$ values in
+Tables~\ref{tab:fits-loss} that reflect relatively tight errors in our FWHM
+profile measurements (Table~\ref{tab:fwhms}).
+
+The exponential variation in $D(x)$ (equation~\eqref{eq:ddamp}) may not be
+physically reasonable; as we have noted above, the assumption $D(x)
+\propto 1 / B^2(x)$ gives rise to sharp gradients in diffusion coefficient and
+even inverts the effect of $\eta_2$ on our model profiles (where larger
+$\eta_2$ can cause rim widths to narrow).
+
+% TODO question: we have been ignoring intensity.  What if, e.g.,
+% with strong diffusion particles get out of the damping zone faster and don't
+% even have a chance to radiate, or something like that?
+% I have no clue... check this, double check Sean's normalizations to be safe
+
+%Expressions for $D$ in terms of unit power per log bandwidth, which is energy
+%dependent as particles scatter preferentially on certain waves or whatever...
+%could $D$ just be high at the shock (and that would also suggest taking $D
+%\propto 1 / B_0$ rather than $D \propto 1 / \Bmin$, for our expression
+%for cut-off energy $\Ecut$, could be a problem).
+
+%Quickly remark on effect of changing compression ratio (effectively dropping
+%$v_d$ downstream).  In both loss-limited and damped models, a higher
+%compression ratio at the shock gives rise to a lower downstream velocity, which
+%permits weaker magnetic fields and diffusion.
 
@@
 
-A priori, we are confident that the rims are nonthermal and meaningful proxies
-for remnant magnetic fields and diffusion, as evidenced by our spectral fits
-and region selections.
-A posteriori, our multiple measurements when modeled (without damping) give
-diffusion and magnetic fields consistent with those derived by considering
-other observables, specifically synchrotron roll-off as derived from radio flux
-and spectral modeling from gamma ray data.
-
-% Is rim narrowing universal?  Further work on more remnants
-From these checks, and the knowledge that our data are not count limited, we
-argue that the observation of rim narrowing in Tycho is sufficient to
-rule out magnetic field damping at the lengthscales of observed X-ray rims.
-Our observations also corroborate rim narrowing as observed by
-\citet{ressler2014} in the remnant of SN 1006.  We will investigate thin rims
-in Kepler's SNR and Cas A \citep[but cf.][]{araya2010} as well.  If significant
-remnant narrowing is a common feature in young supernova remnants, strong
-magnetic fields must be sustained some distance behind the forward shock -- and
-this will need to be understood or characterized (the question becomes, why
-aren't various putative damping mechanisms relevant to SNRs?).
-\note[Aaron]{I am tempted to toss in Kepler results, to prevent duplication of
-text/exposition and maybe start making some case for loss-limited rims being a
-consistent observation.  That would be a lot of tables, though.}
-
-% Modeling limitations
-Filaments widths, as might be expected, do not match model predictions too
-consistently.  This may be attributed in part to spherical cow assumptions on
-Tycho's nonthermal emission and shock structure, as well as its surrounding
-medium.  Streaming and diffusing particles may modify the shock structure;
-fluid instabilities and ISM interactions may induce wave-like instabilities in
-the forward shock's projected shape; multiple and fragmented filaments
-\citep{caprioli2013},
-even in relatively ``clean'' remnants of Type Ia SNe such as SN 1006, Tycho's
-SNR, and Kepler's SNR. \note[Aaron]{needs fact-check and reading}
+We measured the widths of thin synchrotron filaments around Tycho's supernova
+remnant and confirmed that our measured filaments are dominated by nonthermal
+emission with clearly measurable full widths at half maximum in 4--5 energy
+bands.  We find moderate narrowing of rim widths across the remnant,
+corroborating rim narrowing observed by \citet{ressler2014} in the remnant of
+SN 1006.  Our multiple measurements give loss-limited diffusion and magnetic fields
+broadly consistent with prior estimates from rim widths
+\citep[e.g.,][]{parizot2006, rettig2012} and radio and gamma ray measurements
+\citep{acciari2011, morlino2012}.  We find that magnetic damping is equally
+capable of describing our observed data.  At small energy dependence the two
+models are indistinguishable and magnetic damping fits still favor moderately
+amplified magnetic fields.  At moderate energy dependence ($\mE \sim -0.3$),
+the damping model favors weaker magnetic fields, but modeled FWHMs may not
+be truly representative of thin rim widths.
+
+As our data are not count limited, we suggest that additional proxies for
+diffusion and magnetic field are needed to establish or rule out the presence
+of damping at the shocks of young supernova remnants.  More sophisticated
+modeling of shock physics \citep[e.g.,][]{zirakashvili2014} and shock/filament
+structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
+results.  Complete rim profile fitting and subarcsecond radio profiles (as may
+be enabled by EVLA and ALMA) may better discriminate between models.
 
 % Further work -- radio
-As has been noted by many workers, observations of radio synchrotron rims would
-provide strong and immediate evidence for magnetic field damping (at the
-lengthscales of said radio rims).  Previous workers have certainly tried
-\citep{cassam-chenai2007, morlino2012} but it seems not easy.
-A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
-Williams) will offer a rich dataset of sub-arcsecond observations that may
-reveal more about rim morphology and perhaps even temporal variation over a 10+
-year baseline (compare to \citet{katsuda2010-sn1006}).
+%As has been noted by many workers, observations of radio synchrotron rims would
+%provide strong and immediate evidence for magnetic field damping (at the
+%lengthscales of said radio rims).  Previous workers have certainly tried
+%\citep{cassam-chenai2007, morlino2012} but it seems not easy.
+%A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
+%Williams) will offer a rich dataset of sub-arcsecond observations that may
+%reveal more about rim morphology and perhaps even temporal variation over a 10+
+%year baseline (compare to \citet{katsuda2010-sn1006}).
 
@@
 
-A.T. thanks CRESST for support (or, any relevant grants?)
+A.T. thanks CRESST for sponsorship/support at GSFC (any relevant grants?)
 B.J.W. NPP?
@@
 the \Chandra Data Archive.
-This research has made use of NASA's Astrophysics Data System.
+This research has made extensive use of NASA's Astrophysics Data System.
 
@@
 % ==============================
-\section{Best fit width-energy curve $m_\mt{E}$ values}
-
-\begin{table*}[ht]
-    \footnotesize
-    \centering
-    \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
-    \input{suppl-fits-mE.tex}
-\end{table*}
-
-\clearpage
-\section{Best fit stuff with $B_{\mt{min}}=2\muG$}
+%\section{Best fit width-energy curve $m_\mt{E}$ values}
+%
+%\begin{table*}[ht]
+%    \footnotesize
+%    \centering
+%    \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
+%    \input{suppl-fits-mE.tex}
+%\end{table*}
+
+\section{Best fit stuff with $\Bmin=2\muG$}
 
@@
     \centering
-    \caption{Best model fits for all regions, $\mu = 1$, $B_{\mt{min}}=2\muG$}
+    \caption{Best model fits for all regions, $\mu = 1$, $\Bmin=2\muG$}
     \input{suppl-fits-all-bmin2.tex}
@@
     \caption{Best model fits for all regions, $\mu = \eta_2 = 1$,
-        $B_{\mt{min}}=2\muG$}
+        $\Bmin=2\muG$}
     \input{suppl-fits-all-bmin2-eta2one.tex}
@@
 
+% Only show these giant tables in 2col... no need to print these
+\iftoggle{manuscript}{
+}{
     % ===============================
@@
     \end{table*}
+}
 

### 2014-10-24 code/models/models_disp.py

@@ -92,6 +92,7 @@ def build_dataf(fit_type, conf_intv=0.683, fit_kws=None, err_kws=None):
             method='manual' ('lmfit', 'stderr')
             if using 'manual':
                 anneal=True, eps=None, adapt=True (passed to mex.one_dir_root)
+                sp.optimize.brentq kwargs: xtol, rtol
             if using 'lmfit':
                 maxiter=200, prob_func=None (lmfit.conf_interval kwargs)
 

### 2014-10-28 manuscript/paper-tycho.tex
Fits w/smaller damping lengths
New Tycho FWHM tables finished; fits with ab=0.003, 0.002;
regenerate paper tables/plots that show damping fit behavior

@@
 rims by measuring rim width energy dependence in X-ray energies and found that
-rims consistently narrowed in the remnant of SN 1006, favoring synchrotron
-loss-limited rims.
+rims consistently narrowed in the remnant of SN 1006.
 
@@
 rims show very little thermal emission, consistent with expansion into a low
-density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
+density ISM \citep{williams2013}.  Tycho, being a nearby galactic SNR, is close
 enough that its rims are easily resolved by \textit{Chandra} spatial
@@
 % alone don't do much)
-Our model fitting explores the space of varying diffusion (a bulk
-representative of the underlying MHD turbulence and what have you)
-and considers the two scenarios of constant magnetic field (resulting in
-so-called loss-limited rims) and a damped field that falls off exponentially
-behind the forward shock, as suggested by \citet{pohl2005}.
+%Our model fitting explores the space of varying diffusion (a bulk
+%representative of the underlying MHD turbulence and what have you)
+%and considers the two scenarios of constant magnetic field (resulting in
+%so-called loss-limited rims) and a damped field that falls off exponentially
+%behind the forward shock, as suggested by \citet{pohl2005}.
 % this might go at the front before we launch into model details.
@@
 increasing downstream of the shock, given as
-$f(E,x=0) = K_0 E^{-s} e^{-E/\Ecut}$.  Here $K_0$ is an arbitrary
-normalization, $E$ is electron energy, and the cut-off energy $\Ecut$ is given
-below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
-the radio index $\alpha$ as $s = 2\alpha + 1$.  \citet{zirakashvili2007} have
-derived from DSA a slightly different energy spectrum with super-exponential
-cut-off $e^{-(p/p_{\mt{cut}})^2}$, which may impact our results; we use a
-simple exponential cut-off for simplicity and consistency with
-\citetalias{ressler2014}.
+\begin{equation}
+    f(E, x=0) = K_0 E^{-s} e^{-E/\Ecut} .
+\end{equation}
+Here $K_0$ is an arbitrary normalization, $E$ is electron energy, and the
+cut-off energy $\Ecut$ is given below in Section~\ref{sec:diffcoeff}; the
+spectral index $s$ is taken from the radio index $\alpha$ as $s = 2\alpha + 1$.
+\citet{zirakashvili2007} have derived from DSA a slightly different energy
+spectrum with super-exponential cut-off $e^{-(p/p_{\mt{cut}})^2}$, which may
+impact our results; we use a simple exponential cut-off for simplicity and
+consistency with \citetalias{ressler2014}.
 
@@
 model fits to assess whether magnetic damping can independently account for
-decreasing $|\mE|$.
+decreasing $|\mE|$.  This applies for loss-limited fits as well; since $\eta_2$
+varies freely, $\Ecut$ may be anywhere -- and thus the model behavior is not
+necessarily physically reasonable.
 
@@
 \end{table*}
+
+\begin{figure}
+    \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.48\textwidth]{figures/full-std_err-mE-damp-all.pdf}
+        \includegraphics[width=0.48\textwidth]{figures/full-std_err-mE-damp-log.pdf}
+    }{
+        \plotone{figures/full-std_err-mE-damp-all.pdf}
+        \plotone{figures/full-std_err-mE-damp-log.pdf}
+    }
+    \caption{Curves of $\mE$ values for best damping fits for all regions.
+        Note the sharp contrast between most curves, and a small minority that
+        blow up at low energies.
+    \label{fig:mE}}
+\end{figure}
 

### 2014-10-30 manuscript/paper-tycho.tex
Paper revision; Tycho regions 6
Paper draft sent around (update text, tables, plots);
run Tycho regions 6 through pipeline, start loss-limited fits

@@
 
-% TODO GENERAL WARNING -- DATA ARE NOT ALL FULLY CONSISTENT AT THIS TIME.
+% TODO GENERAL WARNING -- DATA MAY NOT ALL BE FULLY CONSISTENT AT THIS TIME.
 % (spectra/profiles/fwhms/fits).
-
-% TODO terminology for "loss-limited" / "damped" / "constant field" / etc
-% should be well established
 
@@
 $f(E,x)$ in equation~\eqref{eq:model} are derived assuming that $D(x) B^2(x)$
-is constant \citep{lerche1980}; we will revisit this assumption further below.
-% TODO give section number when you revisit this
-The electron distribution may be integrated over the one-particle synchrotron
-emissivity $G(y)$ to obtain the ``total'' emissivity:
+is constant \citep{lerche1980}.  The electron distribution may be integrated
+over the one-particle synchrotron emissivity $G(y)$ to obtain the ``total''
+emissivity:
 \begin{equation} \label{eq:emissivity}
@@
 
-Different types of MHD turbulence may give rise to a non-linear energy
-scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
-Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
-quasi-linear approximation for particle motion,
-\note[Aaron]{I don't really know what this means}
-predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
-Particle gyroradii larger than field coherence length may also lead to
-$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
-and cites nothing.  I have no idea what this means.}
+%Different types of MHD turbulence may give rise to a non-linear energy
+%scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
+%Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
+%quasi-linear approximation for particle motion,
+%\note[Aaron]{I don't really know what this means}
+%predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
+%Particle gyroradii larger than field coherence length may also lead to
+%$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
+%and cites nothing.  I have no idea what this means.}
 
 % Define our diffusion coefficient, introduce fiducial energy
-In our models, we consider a generalized diffusion coefficient with arbitrary
+We consider a generalized diffusion coefficient with arbitrary
 power-law dependence upon energy following, e.g., \citet{parizot2006}:
@@
 related as $\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like
-diffusion ($\mu = 1$).
+diffusion ($\mu = 1$).  Our notation matches that of \citetalias{ressler2014}.
 
@@
 \end{equation}
-This has the unfortunate effect of strengthening the spatial-dependence of the
-diffusion coefficient, which may or may not be physical.
+This does strengthens the spatial-dependence of the diffusion coefficient, as
+compared to the expected $D(x) \propto 1/B(x)$.
 \note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
@@
 % Intuition: transport lengthscales in the absence of damping
-We may consider advective and diffusive lengthscales for electron transport,
-which naturally give rise to scaling relations:
+To better intuit the effects of advection and diffusion on rim widths, we
+consider advective and diffusive lengthscales for electron transport given as:
 \begin{equation} \label{eq:lad}
@@
 range of, or all, electron energies) and electrons are only loss-limited as
-they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$; this is the
-strongest energy-dependence possible in our models.  Diffusion increases $\mE$
-monotonically towards a value between $-1/4$ and $1/4$, depending on the value
-of $\mu$.  In practice, $\mE$ appears to plateau at values between $-0.4$ and
-$0$, with larger $\mu$ values yielding $\mE$ closer to $0$ (weaker
-energy-dependence) \citepalias[Figure 3]{ressler2014}.  This may be attributed
-in part to the electron energy cut-off, which limits the available electrons at
-higher energies and thus thins the rims slightly, decreasing $\mE$
-\citepalias[Figure 5]{ressler2014}.
+they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$.  Diffusion
+increases $\mE$ monotonically from $-1/2$ to a value between $-1/4$ and $1/4$
+for $\mu = 0$ and $2$ respectively \citepalias[Figure 3]{ressler2014}.  The
+presence of an electron energy cut-off, decreases $\mE$ slightly in all cases
+due to the decreased number of electrons and hence thinner rims at higher
+energies \citepalias[Figure 5]{ressler2014}.
 
@@
 We expect magnetic damping to produce comparatively energy-independent rim
-widths.  In particular, if synchrotron rims widths are set by magnetic damping
+widths.  If synchrotron rim widths are set by magnetic damping
 at some observation energy, then the rims must be damped at all lower
-observation energies as well.  Then we may expect relatively stable rim widths
-below a threshold energy, then decreasing rim widths once advective or
-diffusive lengthscales fall below the damping lengthscale at higher photon
-energies.
+observation energies as well.  Then rim widths will be relatively constant
+(small $|\mE|$) below a threshold energy and may decrease, or even increase
+(if $\mu > 1$) once advection or diffusion become dominant controls on rim
+widths at higher photon energies (advection: $l_\mt{ad} < a_b$;
+diffusion: $a_b < l_{\mt{diff}} < l_{\mt{ad}}$).
 
@@
 % A comment
-It may be worth noting that this rim width-energy dependence is a morphological
-manifestation of the spectral softening downstream of the forward shock, as
-observed by, e.g., \citet{cassam-chenai2007}.  So we are simply taking somewhat
-of a different approach to characterizing this softening.
+%It may be worth noting that rim width-energy dependence is a morphological
+%manifestation of spectral softening downstream of the forward shock as
+%observed by, e.g., \citet{cassam-chenai2007}.  So we are simply taking somewhat
+%of a different approach to characterizing this softening.
 
@@
 \label{sec:observations}
+
+\subsection{Data and region selections}
+\label{sec:regions}
 
@@
 0.7--1 keV, 1--1.7 keV, 2--3 keV, 3--4.5 keV, and 4.5--7 keV.
-We excluded the 1.7--2 keV energy range to avoid any \ion{Si}{13} (He$\alpha$)
+We excluded the 1.7--2 keV energy range to avoid \ion{Si}{13} (He$\alpha$)
 emission at 1.85 keV, prevalent in the remnant's thermal ejecta, which
@@
 emission (rules out faint southern filaments).  We accepted several
-regions with poor quality peaks in the lowest energy band (0.7--1 keV) so long
-as peaks in all higher energy bands were clear and well-fit.
-\note[Aaron]{vague, imprecise}
-We grouped regions into filaments by visual inspection of the remnant.
-Within each filament, we chose region widths to obtain comparable counts
-at the thin rim peak.
-All measured rim widths are at least $1\arcsec$ and hence are resolved by
-\textit{Chandra}'s point-spread function (PSF), which has FWHM of
-$\abt 1\arcsec$ at $4\arcmin$ off-axis.
+regions with poor quality peaks in the lowest energy band ($0.7$--$1
+\unit{keV}$) so long as peaks in all higher energy bands were clear and
+well-fit.  We grouped regions into filaments by visual inspection of the
+remnant.  Within each filament, we chose region widths to obtain comparable
+counts at the thin rim peak.  All measured rim widths are at least $1\arcsec$
+and hence are resolved by \textit{Chandra}'s point-spread function (PSF), which
+has FWHM of $\abt 1\arcsec$ at $4\arcmin$ off-axis.
 
@@
     regions 14--17, filament 5, regions 18--20.
+    \note[Aaron]{Inverted colors for draft only}
     \label{fig:snr}}
 \end{figure}
-% TODO TODO TODO UPDATE REGION # BOLDING TO MATCH DISPLAYED FILAMENTS ETC
+% NOTE keep region # bolding updated to match displayed filaments
 
@@
 
-% NOTE be consistent in usage of word 'sections'
-We extracted spectra for all regions to check that rim width measurements are
-not affected by contaminating thermal line emission.  In each region, we
-selected upstream and downstream sections from which to extract spectra.  The
-upstream section is the smallest sub-region that contains the measured FWHM
-bounds from all energy bands (see Section~\ref{sec:fwhms}); i.e., this section
-overlies the thin rim.  The downstream section extends from the back of the rim
-(end of the upstream section) to the rim model fit's (equation~\eqref{eq:prof})
-downstream limit.  We extracted spectra from all \Chandra ObsIDs and grouped
-the data into bins of $\geq 15$ counts.  Figure~\ref{fig:spec} plots an example
-profile ($4.54$--$7 \unit{keV}$) with the downstream and upstream sections
-highlighted.  We extracted background spectra from circular regions (radius
-$\abt 30\arcsec$) around the remnant's exterior; each thin rim region's spectra
-subtracted the closest background region's spectrum.
+We extracted spectra at and immediately behind thin rims in each region
+(``'rim'', ``downstream'' spectra respectively) to confirm that rim width
+measurements are not affected by contaminating thermal line emissions.  We
+used our empirical fits of rim profile shape (Section~\ref{sec:fwhms} below)
+to select two corresponding sections in each region for spectrum extraction.
+The rim section is the smallest sub-region containing the measured FWHM bounds
+from all energy bands.  The downstream section extends from the rim section's
+downstream edge to the farthest downstream profile fit domain bound, in all
+energy bands (fits of equation~\eqref{eq:prof}); i.e., the downstream section
+is bounded by the thin rim FWHM and the intensity plateau/trough behind the
+rim.  To illustrate our selections, Figure~\ref{fig:spec} plots example rim
+profiles ($4.5$--$7 \unit{keV}$) with the downstream and rim sections
+highlighted.
+
+% Spectrum data, binning, background
+Spectra taken from all enumerated \Chandra ObsIDs (Section~\ref{sec:regions})
+were grouped into bins of $\geq 15$ counts.  We extracted background spectra
+from circular regions (radius $\abt 30\arcsec$) around the remnant's exterior;
+each region's rim and downstream spectra subtracted the closest background
+region's spectrum.
 % Background region size is valid for data-tycho/bkg-2/ selections
@@
     \caption{Spectra and fits from Regions 1 (top) and 16 (bottom) show varying
-    rim morphology and example of rim where 0.7--1 keV peak could not be fit.
-    Left: $4.5$--$7 \unit{keV}$ profile with highlighted downstream (blue) and
-    upstream (grey) sections.  Intensity in arbitrary units (a.u.).  Middle:
-    downstream spectrum with absorbed power law fit; Si and S lines at $1.85$,
-    $2.45 \unit{keV}$ are clearly visible.  Right: upstream spectrum with
-    absorbed power law fit shows that each region is likely free of thermal
-    line
-emission.}
+        rim morphology; Region 1 shows a rim where the $0.7$--$1 \unit{keV}$
+        peak could not be fit.  Left: $4.5$--$7 \unit{keV}$ profiles with
+        downstream (blue) and rim (grey) sections highlighted.  Intensity is in
+        arbitrary units (a.u.).  Middle: downstream spectra with absorbed
+        power law fit; Si and S lines at $1.85$, $2.45 \unit{keV}$ are clearly
+        visible.  Right: rim spectra with absorbed power law fit show that
+        rims in each region are likely free of thermal line emission.}
     \label{fig:spec}
@@
 % NOTE keep stated ranges of spectral indices, column densities up to date
-We fit spectra from each region's upstream and downstream sections to an
-absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) between $0.5$--$7
-\unit{keV}$ with photon index $\Gamma$, hydrogen column density $N_{\mt{H}}$,
-and a normalization as free parameters.  Table~\ref{tab:spec} lists best fit
-parameters and reduced $\chi^2$ values for all regions.  Spectra from thin rims
-(upstream sections) are well-fit by the power law model alone; the best-fit
-photon indices ($2.4$--$3$) and column densities ($0.6$--$0.8 \times 10^{22}
-\unit{cm^{-2}}$) are consistent with previous spectral fits to Tycho's
-nonthermal rims \citep{hwang2002, cassam-chenai2007}.
+We fit each region's rim and downstream spectra to an absorbed power law model
+(XSPEC 12.8.1, \texttt{phabs*powerlaw}) between $0.5$--$7 \unit{keV}$ with
+photon index $\Gamma$, hydrogen column density $N_{\mt{H}}$, and a
+normalization as free parameters.  Table~\ref{tab:spec} lists best fit
+parameters and reduced $\chi^2$ values for all regions.  Rim spectra are
+well-fit by the power law model alone; the best-fit photon indices ($2.4$--$3$)
+and column densities ($0.6$--$0.8 \times 10^{22} \unit{cm^{-2}}$) are
+consistent with previous spectral fits to Tycho's nonthermal rims
+\citep{hwang2002, cassam-chenai2007}.
 
@@
 % NOTE keep stated ranges, region numbers up to date
-% THIS IGNORES THE REGION 19 SPECTRUM FIT (!!)
-Spectra from sections downstream of the rims are generally poorly-fit,
+% THIS IGNORES THE BAD (insufficient counts) REGION 19 DOWNSTREAM SPECTRUM FIT (!!)
+Downstream spectra are generally poorly-fit by the absorbed power law model,
 reflecting thermal contamination from \ion{Si}{13} and \ion{S}{15} He$\alpha$
 line emission at $1.85$ and $2.45$ keV.  To confirm that thermal emission is
-dominated by these two lines near the shock, we also performed fits to
-downstream spectra with both lines excised ($1.7$--$2.0 \unit{keV}$,
-$2.3$--$2.6 \unit{keV}$ removed) or with both lines fitted to Gaussian
-profiles.  When the lines are excised from our fits, we obtain
-$\chi^2_{\mt{red}}$ values between $0.8$--$1.4$ excepting only Regions 5 and 20
-with $\chi^2_{\mt{red}} \sim 1.8$ due to the presence of many additional lines.
-When lines are fitted to Gaussian profiles, we find $\chi^2_{\mt{red}}$ values
-$0.83$--$1.22$, again excepting Regions 5, 20 which have $\chi^2_{\mt{red}}
-\sim 1.6$.  In both fits (lines excised or modeled), we find somewhat smaller
-best fit column densities ($0.32$--$0.74 \times 10^{22} \unit{cm^{-1}}$),
-but best fit photon indices ($2.52$--$3.05$) are consistent with those of the
-upstream spectra, confirming that the same synchrotron continuum may be
-recovered from beneath thermal line emission.
-
-\begin{table}
+dominated by these two lines near the shock, we also performed fits with (1)
+both lines excised ($1.7$--$2.0 \unit{keV}$, $2.3$--$2.6 \unit{keV}$ counts
+removed) and (2) with both lines fitted to Gaussian profiles.  Fits with lines
+excised yield $\chi^2_{\mt{red}}$ values between $0.8$--$1.4$, excepting only
+Regions 5 and 20 with $\chi^2_{\mt{red}} \sim 1.8$ due to the presence of
+additional thermal lines.  Fits with lines fitted to Gaussian profiles yield
+$\chi^2_{\mt{red}}$ values $0.83$--$1.22$, again excepting Regions 5, 20 which
+have $\chi^2_{\mt{red}} \sim 1.6$.  In both fits (lines excised or modeled), we
+find somewhat smaller best fit column densities ($0.32$--$0.74 \times 10^{22}
+\unit{cm^{-1}}$) but similar best fit photon indices ($2.52$--$3.05$), compared
+to those of the rim spectra.  The consistent photon indices confirm that the
+same synchrotron continuum may be recovered from beneath thermal line emission.
+
+\begin{table*}
     \scriptsize
@@
     \input{tab-spec.tex}
-\end{table}
-
-% This table is still useful, just to look at the parameters
-% (or to send around to collaborators, if needed)
+    \tablecomments{Absorbed power law fit parameters are photon index $\Gamma$
+        and hydrogen column density $N_{\mt{H}}$.  Horizontal rules group
+        individual regions into filaments.}
+    \tablecomments{(DRAFT) Region 5 has unusually poor chi-squared due to a
+        silicon line bump.  The 0.7--1 keV FWHM in Region 5 is $\abt 9\arcsec$
+        and very poorly-fit, being close to not measurable.  In the next
+        iteration of the data pipeline, I will cull the FWHMs by hand (Regions
+        1--3, 5, 11--12, 18--19 will not have FWHMS at 0.7--1 keV); after bad
+        FWHMs are removed, the spectral fits for Regions 5, 19 should improve.}
+\end{table*}
+
+% This table is still useful to look at the fit parameters (to make
+% qualitative statements about excised/Gaussian line fit quality,
+% or to send around to collaborators)
 %\begin{table*}
@@
 
+% Takeaway -- we are good to go
 Our spectral fitting confirms that all selected region are practically free of
 thermal line emission, as already suggested by visual inspection
-(Figure~\ref{fig:snr}).  Our exclusion of all $1.7$--$2 \unit{keV}$ photons
-further limits thermal contamination as $1.85 \unit{keV}$ Si line emission is
-over a third of Tycho's thermal flux as detected by \Chandra \citep{hwang2002}.
+(Figure~\ref{fig:snr}).  Our exclusion of $1.7$--$2 \unit{keV}$ photons in rim
+width measurements further limits thermal contamination as $1.85 \unit{keV}$ Si
+line emission is over a third of Tycho's thermal flux as detected by \Chandra
+\citep{hwang2002}.
 
@@
 % Check these (arcsec) numbers before final version.
-We obtained radial intensity profiles from $\abt 10$--$20\arcsec$ behind the
-shock to $\abt 5$--$10\arcsec$ in front for each of our regions in all five
-energy bands.  To increase signal-to-noise, we integrate along the shock
+We obtained radial intensity profiles in five energy bands from $\abt
+10$--$20\arcsec$ behind the shock to $\abt 5$--$10\arcsec$ in front for each
+region.  To increase signal-to-noise, we integrate along the shock
 ($5$--$23\arcsec$) in each region.  Plotted and fitted profiles are reported in
-vignetting and exposure-corrected intensity units; error bars are computed from
-raw counts assuming Poisson statistics.  Intensity profiles peak sharply
-within $\abt 2$--$3\arcsec$ behind the shock, demarcating our thin rims,
-then fall off gradually until thermal emission picks up further behind the
-shock.
+vignetting and exposure-corrected intensity units; error bars were computed from
+raw counts assuming Poisson statistics.  Intensity profiles peak sharply within
+$\abt 2$--$3\arcsec$ behind the shock, demarcating the thin rims, then fall off
+gradually until thermal emission picks up further behind the shock.
 
@@
 was set at the profile's outer edge (i.e., no data were removed).
+Figure~\ref{fig:profiles} illustrates the fit domain selection
 
@@
 fitting tractable, we fixed $\mu$ in all fits and considered $\mu = 0$, $1/3$,
-$1/2$, $1$, $1.5$, and $2$; recall that $\mu = 1/3$ and $1/2$ correspond to
-Kolmogorov and Kraichnan turbulence.  The remaining parameters $\eta_2$ and
-$B_0$ varied freely.
+$1/2$, $1$, $1.5$, and $2$.  In particular, nonlinear diffusion-energy
+scalings with $\mu = 1/3$ and $1/2$ may arise from Kolmogorov and Kraichnan
+turbulent energy spectra respectively \citep{reynolds2004}.  The remaining
+parameters $\eta_2$ and $B_0$ varied freely.
 
@@
 typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
-We fixed $a_b$ at $12$ different values and ran fits with $\eta_2$ and $B_0$
+We fixed $a_b$ at $14$ different values between $0.5$ and $0.002$ (sampling
+most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
 free.  Formally, we do not seek a best fit value of damping length $a_b$, so
@@
 function integrals).  We chose integration resolutions such that the
-fractional error in model FWHMs associated with halving or doubling each integration
-resolution (individually) is less than $1\%$ for the parameter space relevant
-to our filaments -- $\eta_2 \leq 10^3$ for the loss-limited model and $\eta_2
-\leq 10$ for the magnetic damping model).  In our error analysis, the maximum
-resolution errors in a sample of parameter space are typically $0.1$--$1\%$,
-but mean and median errors are typically an order of magnitude smaller that
-maximum errors.  Thus we expect numerical errors to be negligible.
+fractional error in model FWHMs associated with halving or doubling each
+integration resolution (individually) is less than $1\%$ for the parameter
+space relevant to our filaments -- $\eta_2 \leq 10^3$ for the loss-limited
+model and $\eta_2 \leq 10$ for the magnetic damping model).  In our error
+analysis, the maximum resolution errors in a sample of parameter space are
+typically $0.1$--$1\%$, but mean and median errors are typically an order of
+magnitude smaller that maximum errors.  Thus we expect numerical errors to be
+negligible.
 
@@
 exemplified by Regions 1 and 16.  Best fit results for all regions are
-summarized in Tables~\ref{tab:fits-all}, \ref{tab:fits-all-eta2one}.  In all
-tables, we report values of $\chi^2$ rather than $\chi^2_\mt{red}$ to ease
-comparison of different fits, as we often manually stepped one or two
-parameters that were held constant in fitting.
+summarized in Figure~\ref{fig:fits-all} and Tables~\ref{tab:fits-all},
+\ref{tab:fits-all-eta2one}.  In all tables, we report values of $\chi^2$ rather
+than $\chi^2_\mt{red}$ to ease comparison of different fits, as we often
+manually stepped one or two parameters that were held constant in fitting.
 
@@
 Modeled profiles with best fit FWHMs for Regions 1 and 16 are plotted in
-Figure~\ref{fig:rims}), and their derived best-fit FWHM-energy curves
+Figure~\ref{fig:rims}, and their derived best-fit FWHM-energy curves
 are plotted in Figure~\ref{fig:fits} alongside measured FWHMs.
@@
     }{}
-    \plotone{figures/full-man_err-prfs_01.pdf} \\
-    \plotone{figures/full-man_err-prfs_16.pdf}
+    \plotone{figures/prfs-fit-01.pdf} \\
+    \plotone{figures/prfs-fit-16.pdf}
     \caption{Best fit full model rim profile width predictions for Regions 1
@@
     \iftoggle{manuscript}{
-        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-01.pdf}
-        \includegraphics[width=0.46\textwidth]{figures/full-man_err-energywidth-16.pdf}
+        \includegraphics[width=0.46\textwidth]{figures/energywidth-01.pdf}
+        \includegraphics[width=0.46\textwidth]{figures/energywidth-16.pdf}
     }{
-        \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-01.pdf}
-        \includegraphics[width=0.23\textwidth]{figures/full-man_err-energywidth-16.pdf}
+        \includegraphics[width=0.23\textwidth]{figures/energywidth-01.pdf}
+        \includegraphics[width=0.23\textwidth]{figures/energywidth-16.pdf}
     }
-    \caption{Full model width predictions as a function of energy for Regions 1
-    (top) and 16 (bottom) with measured data.  Dotted/dashed curves plot
-    pure loss-limited fits with varying $\mu$, solid curve plots estimated best
-    model fit with moderate damping ($a_b < 0.01$).  Note that ordinate FWHM
-    axes do not match and are offset from the origin to better show model
-    predictions and data variation.
+    \caption{Loss-limited rim width predictions as a function of energy for
+    Regions 1 (top) and 16 (bottom), with measured data.  Dotted/dashed curves
+    plot pure loss-limited fits with varying $\mu$, solid curve plots estimated
+    best moderately damped fit ($a_b < 0.01$); the corresponding fit
+    parameters are given in Tables~\ref{tab:fits-loss}, \ref{tab:fits-damp}.
+    Note that ordinate FWHM axes do not match and are offset from the origin to
+    better show model predictions and data variation.
     \label{fig:fits}}
 \end{figure}
+
+\begin{figure*}
+    \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.8\textwidth]{figures/energywidth-subplot.pdf}
+    }{
+        \plotone{figures/energywidth-subplot.pdf}
+    }
+    \caption{Rim width predictions for loss-limited and damped fits with
+    $\mu = 1$ fixed for all regions.  Neither loss-limited nor damped fits
+    are clearly favored in describing the data.  Some damped model predictions
+    (e.g., Region 5) are not given at low energies if FWHMs cannot be
+    calculated for model profiles (modeled intensity behind thin rim exceeds
+    half-maximum of rim peak within model domain of $\abt 20\arcsec$).
+    Corresponding best fit parameters are given in Table~\ref{tab:fits-all}.
+    \label{fig:fits-all}}
+\end{figure*}
 
@@
 \begin{table}
+    \iftoggle{manuscript}{
+        \scriptsize
+    }{
         \tiny
+    }
     \centering
@@
     best $a_b$ value may be construed as removing one more dof.}
+    % NOTE UPDATE AS FWHMS UPDATED
 \end{table}
@@
     \input{tab-fits-all-eta2one.tex}
-    \tablecomments{See comments on Table~\ref{tab:fits-all-eta2one}.  Fits have
+    \tablecomments{See comments on Table~\ref{tab:fits-all}.  Fits have
     one additional dof as $\eta_2 = 1$ is fixed.}
@@
 caused by diffusion, which weakens width-energy dependence at higher energies.
-The photon energy at which advection and diffusion are comparably important
-($l_{\mt{ad}} = l_{\mt{diff}}$) is exactly the synchrotron roll-off energy,
+The photon energy at which $l_{\mt{ad}} = l_{\mt{diff}}$ is exactly the
+synchrotron roll-off energy,  % TODO citation if you can find it...
 $\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Then we expect diffusion to
-begin overtaking advection and depress $\mE$ towards $0$ in soft X-rays, as
-opposed to $\mE \abt -0.5$ expected when advection is important
+begin overtaking advection and push $\mE$ towards $0$ in soft X-rays, as
+opposed to $\mE \abt -0.5$ expected for strong advection
 (Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
 consistent with the framework of diffusive shock acceleration.
+We note that our model fits have not incorporated the additional constraint of
+synchrotron roll-off energy, which would in fact fix $\eta_2$ for a given value
+of $\mu$ (equation~\eqref{eq:rolloff}).
+% TODO explain why not, perhaps
 
@@
 % Can damping explain stuff?
-The next question is whether damping may also produce this effect, independent
-of assumptions on the shock acceleration process.  Conceptually, if damping
-controls rim widths past the cut-off energy, $|\mE|$ may slightly decrease or
-even increase as rims transition from being damping controlled to being
-diffusion loss-limited.  If damping is only important well below the cut-off
-energy, then we may see an increase in $|\mE|$ as advection becomes important.
-Although magnetic damping is able to fit observed rim widths, our model assumes
-diffusive shock acceleration in computing $\Ecut$ and hence we may not use our
-model fits to assess whether magnetic damping can independently account for
-decreasing $|\mE|$.  This applies for loss-limited fits as well; since $\eta_2$
-varies freely, $\Ecut$ may be anywhere -- and thus the model behavior is not
-necessarily physically reasonable.
+% Somewhat redundant (overlap with Section~\ref{sec:energydep})
+The next question is whether damping may also produce a decrease in $|\mE|$,
+independent of assumptions on the shock acceleration process.  Conceptually, if
+damping controls rim widths past the cut-off energy, $|\mE|$ may slightly
+decrease or even increase as rims transition from being damping controlled to
+being diffusion loss-limited.  If damping is only important well below the
+cut-off energy, then we may see an increase in $|\mE|$ as advection becomes
+important.  Although magnetic damping is able to fit observed rim widths, our
+model assumes diffusive shock acceleration in computing $\Ecut$ and hence we
+may not use our model fits to assess whether magnetic damping can independently
+account for decreasing $|\mE|$.  This applies for loss-limited fits as well;
+since $\eta_2$ varies freely, $\Ecut$ may be anywhere -- and thus the model
+behavior is not necessarily physically reasonable.
 
 % Curious effects of damping competing with other things
-Downstream energy losses in a well damped field (multiple $e$-folding
-lengths ($a_b$) downstream) may also introduce energy dependence in rim widths.
-Sufficiently energetic electrons will radiate and cool within the damping
-length $a_b$, but lower energy electrons will perceive a relatively constant
-field $\abt \Bmin$ downstream of the shock.  Synchrotron losses will
-``sieve'' out higher energy electrons as in the loss-limited model, and
-observed rim widths, if larger than $a_b$, may be somewhat loss-limited at low
-energies, well-confined by damping at moderate energies, then diffusion (or
-cut-off spectrum) limited at the highest energies.
+In a damped field scenario, synchrotron cooling far downstream of the shock
+(many $e$-folding lengths $a_b$) may also introduce energy dependence in rim
+widths.  Sufficiently energetic electrons will radiate and cool within the
+damping length $a_b$, but lower energy electrons propagating farther downstream
+will eventually radiate and cool in a relatively constant field $\abt \Bmin$.
+Synchrotron losses will ``sieve'' out higher energy electrons as in the
+loss-limited model, and observed rim widths, if larger than $a_b$, may be
+somewhat loss-limited at low energies, well-confined by damping at moderate
+energies, then diffusion (or cut-off spectrum) limited at the highest energies.
 
@@
 The damped model fits permit much smaller values of $B_0$, as expected.
-The maximum best-fit $B_0$ value observed is $600 \muG$, with most values
-typically below $300 \muG$.  The minimum value of $B_0$ is around $10$--$20
+The maximum best-fit $B_0$ value observed is $340 \muG$, with a majority of
+values below $100 \muG$.  The minimum value of $B_0$ is around $10$--$20
 \muG$, which is consistent with shock compression alone.
@@
 Regions 5 and 18 have best-fit $\eta_2$ values strictly below $\eta_2 = 1$
-within error.  Damped fits permit smaller values of $\eta_2$ in contrast to
-loss-limited models, perhaps as stronger damping and smaller $\eta_2$ have
-cancelling effects on rim widths (recalling that in the damped model, smaller
-$\eta_2$ gives larger rim widths).
+after accounting for error.  Damped fits favor smaller values of $\eta_2$ in
+contrast to loss-limited models, perhaps as stronger damping and smaller
+$\eta_2$ have cancelling effects on rim widths (recalling that with moderate
+damping, smaller $\eta_2$ counterintuitively gives larger rim widths).
 
 % A quick discussion of mu
-Our fits at multiple values of $\mu$ are not especially insightful.
-The $\chi^2$ values for individual fits are variable and quite large, so we are
-unable to favor or disfavor fits at different $\mu$ values.  But, neglecting
-caution, we observed that values of $\mu \geq 1$ are qualitatively favored by
-$\chi^2$ in almost all regions.  This trend may be an partially an artifact of
-the correlation between $B_0$ and $\eta_2$ as they are not entirely independent
-parameters, but they are less correlated for larger $\mu$; it may be said that
-fits at smaller $\mu$ may have fewer (non-integer) degrees of freedom,
-partially offsetting our observations.  \citetalias{ressler2014} also found
-better model fits for $\mu \geq 1$ in the remnant of SN 1006 and noted that
-\citet{reynolds2004} favored $\mu \geq 1$ on grounds of better modeled remnant
-morphology, but it remains uncertain whether $\mu \geq 1$ diffusion is truly
-preferred.
-
-We do not explore $\mu$ dependence extensively in the damped model, but we find
-that $\mu > 1$ permits smaller $B_0$ values and \emph{larger} $\eta_2$ values,
-in keeping with our previous discussion of the effects of $B_0$ and $\eta_2$ on
+Our loss-limited fits at multiple values of $\mu$ are not especially
+insightful.  The $\chi^2$ values for individual fits are variable and quite
+large, so we are unable to favor or disfavor fits at different $\mu$ values.
+But, neglecting the magnitude of our $\chi^2$ values, we observed that values
+of $\mu \geq 1$ are qualitatively favored by $\chi^2$ in almost all regions.
+This trend may be partially an artifact of the correlation between $B_0$ and
+$\eta_2$ as they are not entirely independent parameters, but they are less
+correlated for larger $\mu$; it may be said that fits at smaller $\mu$ may have
+fewer (non-integer) degrees of freedom, partially offsetting our observations.
+\citetalias{ressler2014} also found better model fits for $\mu \geq 1$ in the
+remnant of SN 1006 and noted that \citet{reynolds2004} favored $\mu \geq 1$ on
+grounds of better modeled remnant morphology, but it remains uncertain whether
+$\mu \geq 1$ diffusion is truly preferred.
+
+We do not explore $\mu$ dependence extensively in the damped model, but that
+$\mu > 1$ permits smaller $B_0$ values and \emph{larger} $\eta_2$ values, in
+keeping with our previous discussion of the effects of $B_0$ and $\eta_2$ on
 rim width in both loss-limited and damped models.
@@
 
-\begin{table*}[ht]
-    \scriptsize
-    \centering
-    \caption{$m_\mt{E}$ from best model fits, loss-limited and damped
-        \label{tab:fits-mE}}
-    \input{suppl-fits-mE.tex}
-    \tablecomments{Best fits correspond to those given in
-        Table~\ref{tab:fits-all}}
-\end{table*}
-
-\begin{figure}
-    \centering
-    \iftoggle{manuscript}{
-        \includegraphics[width=0.48\textwidth]{figures/full-std_err-mE-damp-all.pdf}
-        \includegraphics[width=0.48\textwidth]{figures/full-std_err-mE-damp-log.pdf}
-    }{
-        \plotone{figures/full-std_err-mE-damp-all.pdf}
-        \plotone{figures/full-std_err-mE-damp-log.pdf}
-    }
-    \caption{Curves of $\mE$ values for best damping fits for all regions.
-        Note the sharp contrast between most curves, and a small minority that
-        blow up at low energies.
-    \label{fig:mE}}
-\end{figure}
-
 Width-energy dependence is not as sensitive a discriminant on damping versus
-loss-limited models as may be intuitively expected.  Only in cases of very
-sharp energy drop-off (data and best loss-limited fit $\mE \sim -0.5$) is
-damping significantly disfavored as a control on rim widths (Region 18).  To
-illustrate this behavior in our fits more clearly, Table~\ref{tab:fits-mE}
-lists $\mE$ values as computed from both best loss-limited and damping fits.
-This condenses and quantifies the width-energy predictions shown in
-Figure~\ref{fig:fits}.
-
-Both loss-limited and damped fits do not perfectly capture sharp drop-offs
-(especially between $0.7$--$1 \unit{keV}$ and $1$--$2 \unit{keV}$), and the
-data are greatly scattered.  In most regions, best fit width-energy curves have
-$\mE \sim -0.2$ (Table~\ref{tab:fits-mE}).
-
-% Explain the spurious energy dependence thing
-When width-energy dependence is small, both loss-limited and damped rims give
+loss-limited models as may be intuitively expected.  Both loss-limited and
+damped fits do not perfectly capture sharp drop-offs (especially between
+$0.7$--$1 \unit{keV}$ and $1$--$2 \unit{keV}$), and the data are greatly
+scattered.  In most regions, best fit width-energy curves have $\mE \sim -0.2$.
+Only in cases of very sharp energy drop-off (data and best loss-limited fit
+$\mE \sim -0.5$) is damping significantly disfavored as a control on rim widths
+(Region 18).
+
+% Explain the dichotomy in energy dependence
+When width-energy dependence is weak, both loss-limited and damped rims give
 best fits with very similar shapes -- strong fields at the shock in both models
@@
 losses which act differentially on the range of electron energies we consider.
-% TODO horrific wording.  "act differentially?"
-
-% TODO somehow highlight this, or think of a way to differentiate the regions
-% Arbitrary yes, but I think it highlights the idea...
+
+\begin{figure}[h]
+    \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.48\textwidth]{figures/mE-damp.pdf}
+    }{
+        \plotone{figures/mE-damp.pdf}
+    }
+    \caption{Curves of $\mE$ values for best damping fits for all regions.
+        Note the sharp contrast between curves with roughly constant $\mE$ near
+        $0$ and curves with sharp drop-offs in $\mE$ (FWHMs increasing rapidly)
+        at low energies. Corresponding best fit parameters are given in
+        Table~\ref{tab:fits-all}. \label{fig:mE}}
+\end{figure}
+
+% Weak-field damping
 Each of these cases is illustrated in Figure~\ref{fig:rims}; in Region 1 the
 damping profiles are quite distinct from the loss-limited profiles, whereas in
-Region 16 they appear quite similar.  Regions 1, 2, 4, 5, 12, and 18 are best
-fit in a damping model with fields $B_0 < 30 \muG$; the remaining regions have
-$B_0 > 80 \muG$.  These regions are the same ones characterized by larger best
-fit $\mE$ values in Table~\ref{tab:fits-mE}, with $\mE \lesssim -0.3$
-generally, especially at lower energies.  The remaining regions are
-characterized by $\mE \sim -0.2$, or $\mE$ decreasing (stronger width-energy
-dependence) at \emph{higher} energies rather than lower energies.  The effect
-of stronger energy dependence is conceptually expected in the damping model
-when the advection lengthscale falls beneath the damping lengthscale at high
-energies (Section~\ref{sec:energydep}).
+Region 16 they appear quite similar; note how emission downstream of the shock
+Region 1's best damped fit is quite close to the intensity half-maximum.  To
+further distinguish between these cases, Figure~\ref{fig:mE} plots predicted
+$\mE$ values from the best damped fits of Table~\ref{tab:fits-all},
+extrapolated to lower photon energies.  Although only qualitative, we see that
+a subset of best fits give increasing large FWHMs at lower energies ($0.1$--$1
+\unit{keV}$) and hence $\mE$ falls strongly negative; the extrapolated curves
+cut off when a FWHM can no longer be measured due to emission downstream of the
+rim rising above the half-rim-maximum level.  These curves correspond to fits
+for Regions 1, 2, 4, 5, 10, 12, 18, and 19, which were all best fit by a
+damping model with fields $B_0 < 40 \muG$.  For convenience, we will say that
+the damped fits to our data give rise to ``weak-field'' damping, associated
+with comparatively weak magnetic fields and stronger emission intensity in a
+plateau immediately downstream of the thin rim.
+
+% Strong-field damping
+The near constant curves in Figure~\ref{fig:mE} trend towards $\mE = 0$ at low
+energy, indicating that rims are strongly energy independent.  At higher
+energy, they give way to more energy dependent rims ($\mE \sim -0.2$) as
+necessary to match our observed width-energy dependence in X-rays; as discussed
+in Section~\ref{sec:energydep}, the gradual increase in $|\mE|$ is expected in
+the damping model as advection and diffusion take control of rim widths.
+The best damped fits for these regions all have larger $B_0$ values than in the
+``weak-field'' damping case, although not dramatically larger.  We shall refer
+to these fits as giving rise to ``strong-field'' damping, associated with
+stronger magnetic fields, weaker emission intensity behind the thin rim, and
+clear rims (with measurable FWHMs) at low photon energies (at and below soft X-ray).
+
+% Explanation and caveats
+The distinction between ``weak-field'' and ``strong-field'' damping is not
+necessarily physically meaningful, given the large $\chi^2$ values on our
+model fitting.  Several regions are well-fit by either ``weak-field'' or
+``strong-field'' damping.  However, we believe that ``weak-field'' damping is
+often associated with data that are best described by stronger energy
+dependence, as quantified by $\mE$ values of best loss-limited and damped fits.
+We also note that due to the large divergence in FWHM values at low energies
+(relatively stable for ``strong-field'' fits versus extremely large for
+``weak-field'' fits), observations of synchrotron rims at radio wavelengths
+could better discriminate between these two classes of fits.
+We also note that the observed split in weak/strong-field damping at $B_0 = 40
+\muG$ may not be meaningful, as best fit behavior depends strongly on both
+$a_b$ and $\eta_2$ as well.  Nevertheless, the qualitative behavior of $B_0$ is
+suggestive; it may be that very strong fields at the shock ($\gtrsim 100 \muG$)
+will never give rise to ``weak-field''-like energy dependence.  The parameter
+space of damped fits remains to be explored, however.
+
+% SN 1006
+Our modeling also allows us to better explore the significance of rim width
+measurements in the remnant of SN 1006 by \citetalias{ressler2014}.  We fit our
+damping model to the averaged filament widths of SN 1006 measured by
+\citetalias{ressler2014}, using the same procedure as for Tycho.  We keep
+$\Bmin = 5 \muG$ fixed, although best fit magnetic fields for SN 1006 are
+smaller than those of Tycho due to much wider filaments in SN 1006.
+
+Damped fits are comparable to or better than loss-limited fits in 3 of 5
+filaments in SN 1006.  The two filaments with strongest energy dependence ($\mE
+\sim -0.5$) favor a loss-limited model with sub-Bohm diffusion ($\eta_2 \ll
+1$).  The width-energy dependence in SN 1006 ($\mE \sim -0.3$ to $-0.5$) is
+overall slightly stronger than in Tycho, and all of our best damped fits for SN
+1006 correspondingly fall into the ``weak-field'' case.  All best fit $B_0$
+values are less than $40 \muG$ in the damped model, compared to $\abt
+100$--$200 \muG$ in the loss-limited model.
+
+\note[Aaron]{Draft only: appendix includes tables and figures for SN 1006 fits}
 
@@
 be attributed to magnetic damping.  But, the bulk of radio emission in Tycho
-($r \lesssim 0.9 r_s$) may not be safely modeled as time-independent.
-
-Synchrotron radio emission is emitted by \~ GeV electrons and hence diffusion
+($r \lesssim 0.9 r_s$) likely cannot be modeled as a steady-state process.
+
+Synchrotron radio emission is emitted by GeV electrons and hence diffusion
 is essentially negligible; observed rims (or lack thereof) are primarily
@@
 
-The radio emission profiles from Tycho has been explored by
+Radio emission profiles from Tycho have been modeled by
 \citet{cassam-chenai2007} and \citet{morlino2012}; both studies assumed
@@
 structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
-results.  Complete rim profile fitting and subarcsecond radio profiles (as may
+results.  Complete rim profile fitting and sub-arcsecond radio profiles (as may
 be enabled by EVLA and ALMA) may better discriminate between models.
@@
 % ========
-\clearpage
+%\clearpage
 \appendix
@@
 
-\section{Best fit stuff with $\Bmin=2\muG$}
+% ================================
+% Best fit information for SN 1006
+% ================================
+\section{Best fits, SN 1006}
+
+Here we supply detailed best loss-limited and damped fit results for averaged
+filament widths in SN 1006, from \citet{ressler2014}.
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=0.7\textwidth]{figures/energywidth-subplot-sn1006.pdf}
+    \caption{Rim width predictions for loss-limited and damped fits with
+    $\mu = 1$ fixed for all regions, SN 1006.}
+\end{figure*}
+
+% Fit results for ALL regions, mu = 1, loss-limited and damped
+\begin{table}[h]
+    \footnotesize
+    \centering
+    \caption{Best model fits for all regions, $\mu = 1$}
+    \input{suppl-fits-all-sn1006.tex}
+    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
+        best damped fits select best $a_b$ value below $0.01$ (to $0.002$),
+        enforcing moderate damping.  All fits have 1 dof.  The manual selection
+        of a best $a_b$ value may be construed as removing one more dof.}
+\end{table}
+
+\begin{figure}
+    \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.48\textwidth]{figures/mE-damp-sn1006.pdf}
+    }{
+        \includegraphics[width=0.35\textwidth]{figures/mE-damp-sn1006.pdf}
+    }
+    \caption{Curves of $\mE$ values for best damping fits for all regions,
+        SN 1006}
+\end{figure}
+
+\begin{figure*}[h]
+    \centering
+    \includegraphics[width=0.48\textwidth]{figures/prfs-fit-sn1006-01.pdf}
+    \includegraphics[width=0.48\textwidth]{figures/prfs-fit-sn1006-02.pdf}
+    \includegraphics[width=0.48\textwidth]{figures/prfs-fit-sn1006-03.pdf}
+    \includegraphics[width=0.48\textwidth]{figures/prfs-fit-sn1006-04.pdf}
+    \includegraphics[width=0.48\textwidth]{figures/prfs-fit-sn1006-05.pdf}
+    \caption{Rim width predictions for loss-limited and damped fits with
+    $\mu = 1$ fixed for all regions, SN 1006.}
+\end{figure*}
+
+% ========================================
+% Best Tycho fits with Bmin = 2 microGauss
+% ========================================
+
+\clearpage
+\section{Best fits, Tycho, with $\Bmin=2\muG$}
 
@@
 }
+
+% =======================
+% Extra -- postage stamps
+% =======================
+
+%\clearpage
+%\section{Extra}
+%
+%% NB this blows up the file size...
+%\begin{figure*}[hb]
+%    \centering
+%    \plotone{figures/energywidth-subplot-stamp.pdf}
+%    \caption{Philatelics of Tycho's synchrotron rims with application to
+%    \Chandra publicity}
+%\end{figure*}
 
@@
 
-% --------------
-% SN 1006 tables
-% --------------
-%\clearpage
-%\section{Full model validation, SN 1006 (DRAFT ONLY)}
-%
-%For comparison to \citetalias{ressler2014}, we reproduce Sean's full model fit
-%table (Table~\ref{tab:sean}) and present full model fits with 2 and 3 energy
-%bands (Tables~\ref{tab:sn1006-2band} and \ref{tab:sn1006-3band}, respectively).
-%We don't compare simple model results, as they are identical (only the error
-%calculations differ).
-%The procedures of Tables~\ref{tab:sean},~\ref{tab:sn1006-2band} are not quite
-%the same.  Sean used $\mE$ at 2 keV instead of the $1$--$2$ keV width for
-%fitting, whereas I used both widths.  But, it should not matter much as
-%the fit often has $\chi^2 \sim 0$, either way (depending on the exact
-%measurements and values of $\mu$).
-%
-%Please take the errors with a grain of salt.  They are automatically
-%generated and \textbf{have not been manually validated}.  Some values may be
-%invalid, where my error-finding code failed and gave a best, conservative guess
-%of the error.
-%
-%\begin{table}[ht]
-%    \tiny
-%    \centering
-%    \caption{Sean's SN 1006 best fit parameters \citepalias[Table 8]{ressler2014}.
-%    \label{tab:sean}}
-%    \input{tab-sean.tex}
-%\end{table}
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{SN 1006 best fit parameters, 2 highest energy bands (full model).
-%    \label{tab:sn1006-2band}}
-%    \input{tab-sn1006-2band.tex}
-%\end{table*}
-%
-%\begin{table*}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{SN 1006 best fit parameters, 3 energy bands (full model).
-%    \label{tab:sn1006-3band}}
-%    \input{tab-sn1006-3band.tex}
-%\end{table*}
-
 % ==========

### 2014-10-30 code/models/models_disp.py

@@ -31,6 +31,11 @@ In the "metadata" pickle:
     fobj_all['inds'] = fobj.inds
     fobj_all['snr-pars'] = fobj.snr.config_log()
 
+    NOTE: kevs, data, eps ALREADY have inds applied
+    so do not reapply inds when recreating fitter object.
+    Bad design, should be set up to save "original" kevs/data/eps
+    then apply inds.  But leave for now...
+
 Aaron Tran
 August 2014
 """
@@ -248,6 +253,15 @@ def save_fits(p_list, fobj, mu_vals, outroot):
     with open('{}-fobj.json'.format(outroot), 'w') as fjson:
         json.dump(fobj_all, fjson, cls=LmfitJSONEncoder, indent=4)
 
+# =====================================================
+# Load best fits, compute FWHMs or return useful things
+# =====================================================
+
+# NOTE code to read/parse saved best fits is not well designed (Oct 28 2014)
+# there should be a hierarchy of items passed through / returned
+# to allow easy retrievals / operations with Fitter objects
+
+# NOT TOUCHING FOR NOW TO PRESERVE EXISTING FUNCTIONALITY
 def load_fit_pkls(inroot, want_fobj=False):
     """Generator that iterates over each fitted region/filament
     Input:
@@ -269,6 +283,144 @@ def load_fit_pkls(inroot, want_fobj=False):
             yield p_list, mu_vals, n+1, fobj_dict
         else:
             yield p_list, mu_vals, n+1
+
+def load_fit_pkls_new(inroot):
+    """Generator iterating over each fitted region/filament
+    Input:
+        inroot (str) is base file stem, e.g.,
+        ../../data-tycho/fwhms/model-fits/simp-man_err
+    Yield, for each region fitted:
+        list of Parameters()
+        list of mu values
+        Fitter() object
+        region number
+    """
+    npkls = len(glob('{}-[0-9]*-data.pkl'.format(inroot)))
+    for n in xrange(npkls):  # Enforces ordering
+        p_list, mu_vals, fobj = load_fit_pkl(inroot, n+1)
+        yield p_list, mu_vals, fobj, n+1
+
+
+def load_fit_pkl(inroot, n):
+    """Get best fit information/usables from specified fit pickle
+
+    Input:
+        inroot (str): base file stem for best fit pickles
+        n (int): region number for inroot
+    Output:
+        (p_list, mu_list, fobj)
+
+        p_list is list of lmfit.Parameters objects
+        mu_vals contains all fitted mu values
[…]

### 2014-10-30 code/models/models_exec.py

@@ -120,6 +120,7 @@ class Fitter(object):
 
     def width_full(self, mu, eta2, B0, **kwargs):
         """Full model widths for stored SNR and energy bands
+        Wrapper for models.width_cont, can pass through intensities/etc as well
 
         **kwargs passed directly to full model code (see models.width_cont)
         """

### 2014-10-31 code/models/snr_catalog.py
Tycho regions-6 fits, srcutlog fits; Kepler tables
Running Tycho regions-6, Kepler regions-3 through pipeline
Cell to run srcutlog fits for Tycho
APLpy script to generate Tycho figure for manuscript
Move images/notes for Tycho RGB images to higher level
Script to generate damped FWHM tables for Kepler

@@ -78,10 +78,10 @@ def make_kepler():
                      # 0.64 = radio spectral index, Green's SNR catalog
                      # consistent w/ DeLaney et al. (2002)
 
-    kepler.vs = 4.71e8 * kepler.dkpc/5 # Shock velocity, cm/s (with dkpc = 5)
-                        # mean measurements of Reg-4/5, Katsuda et al. (2008)
-                        # scaled to 5 kpc.  Vink (2008) give 5.25e8
-                        # but within error the values are barely consistent
+    kepler.vs = 5e8 * kepler.dkpc/5 # Shock velocity, cm/s (with dkpc = 5)
+                        # mean of measurements by Katsuda (2008), Vink (2008)
+                        # scaled to 5 kpc.  Katsuda gives 4.7e8; Vink, 5.25e8
+                        # within error the values are barely consistent
 
     kepler.cratio = 4.0  # Compression ratio, strong adiabatic shock (R-H)
 
@@ -100,6 +100,7 @@ def make_kepler():
                        'B0': (1e-6, 1e-2)}
 
     return kepler
+
 
 def make_tycho():
     """Physical parameters, model/fit settings for Tycho's SNR

### 2014-10-31 code/models/tables/gen_scripts/tab_kepler_all_20141031.py

@@ -1,0 +1,109 @@
+"""
+Tabulate FWHMs for Kepler for
+#1. no damping, all 6 mu values; default shock velocity (5000 km/s, 5 kpc)
+#   20+ B0 values (ask for 20, expect ~30)
+2. various magnetic damping scale lengths
+   50+ B0 values (ask for 50, expect 10--70)
+
+  `a_b` values I use are:
+      0.5,    0.05,   0.04,   0.03,
+      0.02,   0.015,  0.012,  0.011,
+      0.01,   0.009,  0.008,  0.007,
+      0.006,  0.005,  0.004,  0.003,  0.002
+
+Default rminarc, Bmin = 5 microGauss.
+151 eta2 values log-spaced between [0.01, 100] with 2x sampling in [0.1, 10].
+
+Numbers now hardcoded into table generating script (makes more sense)
+Call script with flag 0, 1, 2, 3 and it will load the correct values.
+I don't know why I didn't do this before (since the principle is that this
+script is essentially a "config" file of sorts).
+
+to try to balance the load of calculations (I have gone diagonally in this
+table).
+
+
+Aaron Tran
+2014 October 31
+"""
+
+from __future__ import division
+
+import argparse
+from datetime import datetime
+import numpy as np
+
+import models
+import snr_catalog as snrcat
+
+AB_VALS_ALL = [[0.5,  0.015,  0.008, 0.003],
+               [0.05, 0.012, 0.007, 0.006, 0.002],
+               [0.04, 0.011, 0.01, 0.005],
+               [0.03, 0.02,  0.009, 0.004]]
+
+# Numbers are generated from regions-3, background subtracted
+KEPLER_KEVS = np.array([0.7, 1.0, 2.0, 4.0])
+KEPLER_DATA_MIN = np.array([ 2.0,  1.32, 1.20,  0.90])
+KEPLER_DATA_MAX = np.array([ 3.3,  2.85, 2.65,  2.38])
+
+
+def main():
+    parser = argparse.ArgumentParser(description='Table generator')
+    parser.add_argument('num', help=('Instance of the script to run; '
+                                     'determines input a_b/v_s values. '
+                                     'Value between 0-3'))
+
+    args = parser.parse_args()
+    idx = int(args.num)
+
+    # vs/ab values to use in this instance
+    abvals = AB_VALS_ALL[idx]
+
[…]

### 2014-11-06 manuscript/paper-tycho.tex
Tycho regions-6 fits, srcutlog fits; Kepler tables
Running Tycho regions-6, Kepler regions-3 through pipeline
Cell to run srcutlog fits for Tycho
APLpy script to generate Tycho figure for manuscript
Move images/notes for Tycho RGB images to higher level
Script to generate damped FWHM tables for Kepler
Plots of param space, fix paper eta2=1 table
Fits for spectral index variation
Compute fits to harder X-ray tails to assess spectral index variation
Refactor PyXSPEC interfacing code to simplify adding fits etc
Notes on X-ray emission lines

@@
         &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
-        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
-        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
-        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
+        \left(100 \muG\right)
+        \left(2657 \unit{erg^2}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
+        &\left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
         \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
@@
 
-% TODO final figure should be higher quality, use vector overlay if possible
 \begin{figure}
@@
     \iftoggle{manuscript}{
-        \includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
+        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
     }{
-        \plotone{figures/f0-snr-inv.png}
+        %\plotone{figures/f0-snr-inv.png}
+        \plotone{figures/snr.pdf}
     }
@@
         individual regions into filaments.}
-    \tablecomments{(DRAFT) Region 5 has unusually poor chi-squared due to a
-        silicon line bump.  The 0.7--1 keV FWHM in Region 5 is $\abt 9\arcsec$
-        and very poorly-fit, being close to not measurable.  In the next
-        iteration of the data pipeline, I will cull the FWHMs by hand (Regions
-        1--3, 5, 11--12, 18--19 will not have FWHMS at 0.7--1 keV); after bad
-        FWHMs are removed, the spectral fits for Regions 5, 19 should improve.}
+\end{table*}
+
+\begin{table*}
+    \scriptsize
+    \centering
+    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
+    \input{suppl-spec-pt2.tex}
+    \tablecomments{As described in text,
+    we consider absorbed power law fits with lines fitted to two Gaussians
+    (here characterized by equivalent width and line energy), or with lines
+    manually excised.  See comments on Table~\ref{tab:spec}.}
 \end{table*}

### 2014-11-06 code/spectra/spec_var_fit.py

@@ -1,0 +1,149 @@
+"""
+Perform XSPEC fits to characterize spectral variations in filaments
+Aaron Tran
+
+Base fit is phabs*po with nH = 0.7 frozen.  Then we have some options:
+0. phabs*po alone
+1. phabs*po with S line excised (cut 2.3-2.6 keV)
+2. phabs*po with S line fit
+
+I will also run manual fits to consider other lines...
+Those may not get completely logged though
+"""
+
+import argparse
+import json
+import os
+import numpy as np
+
+import xspec as xs
+
+import regparse
+import spec_fit_utils as xsutils
+
+def main():
+    """Parse input and tell XSPEC what to do"""
+    parser = argparse.ArgumentParser(description=
+             ('Apply XSPEC model fits to all spectra w/ given filestem '
+              'and output best fit plots, parameters. '
+              'Run from spectra-containing directory '
+              'so XSPEC can locate response/background files.'))
+    parser.add_argument('specroot', help='Directory stem for spectra')
+    parser.add_argument('fittype', help=('Type of fit to apply: '
+                                         '0=phabs*po, '
+                                         '1=excise S line, '
+                                         '2=excise S, Ar lines, '
+                                         '3=fit S line'), type=int)
+    parser.add_argument('plotroot', help='Output stem for plots')
+    parser.add_argument('fitproot', help='Output stem for fit logs, data')
+    parser.add_argument('-v', '--verbose', action='store_true',
+                        help='verbose mode')
+
+    args = parser.parse_args()
+    specroot, pltroot, fitproot = args.specroot, args.plotroot, args.fitproot
+    ftype = args.fittype
+    verbose = args.verbose
+
+    # Check and create new directories if needed
+    regparse.check_dir(pltroot, verbose)
+    regparse.check_dir(fitproot, verbose)
+
+    n = regparse.count_files_regexp(specroot + r'_src[0-9]+_grp\.pi')
+    if verbose:
+        print '\n{} spectra to process'.format(n)
+    if verbose and wanterr:
+        print 'Computing errors from 90% confidence limits'
+
+    # Set up XSPEC for fitting
+    xsutils.init_xspec(verbose)
+    xs.Fit.nIterations = 2000
+
[…]

### 2014-11-20 manuscript/paper-tycho.tex
Add profile fits, fix spec.var.model, radio prfs
Entire profile fitting for both radio/X-ray data
Critical (output affecting) bug fix to modeling spectral variation
Ad hoc code to extract/parse/plot radio profiles
Split model parameter space plots to new notebook

@@
 % ========
-%\clearpage
+\clearpage
 \appendix
@@
     \includegraphics[width=0.7\textwidth]{figures/energywidth-subplot-sn1006.pdf}
-    \caption{Rim width predictions for loss-limited and damped fits with
-    $\mu = 1$ fixed for all regions, SN 1006.}
+    \caption{Rim width predictions for loss-limited (dashed) and damped fits
+        (solid) with $\mu = 1$ fixed for all regions, SN 1006.}
 \end{figure*}
@@
     \input{suppl-fits-all-sn1006.tex}
-    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
-        best damped fits select best $a_b$ value below $0.01$ (to $0.002$),
+    \tablecomments{Loss-limited fits have $\mu=1$ fixed;
+        best damped fits select best $a_b$ value between $0.002$ and $0.01$
+        (1.8--9 arcsec; $a_b$ is given in units of shock radius $r_s$),
         enforcing moderate damping.  All fits have 1 dof.  The manual selection
@@
 
+\clearpage
 \begin{figure}

### 2014-11-20 VLA/plot_radio_xray_prfs.py

@@ -1,0 +1,129 @@
+"""
+Plot roughly obtained X-ray/radio profiles
+
+# Note: scale/cmap settings not right for 1-1.7 keV image
+
+ds9 -rgb \
+    -red ../VLA/TYCHO_IF1.FITS \
+        -scale limits 0.00015 0.0035 \
+        -cmap value 2.25 0.55 \
+    -green 1-1.7kev_mosaic.fits \
+        -scale limits 7e-9 4e-7 \
+        -cmap value 3.59 0.12 \
+    -blue 4-7kev_mosaic.fits \
+        -scale limits 7e-9 4e-7 \
+        -cmap value 3.59 0.12 \
+    -rgb lock scale yes \
+    -asinh
+
+    pan: 0:25:15.764, +64:08:25.00
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+
+nyrs = 2009 - 1994  # Time between Chandra and VLA observations
+arcsec_per_yr = 0.3  # Katsuda et al. 2010
+px2arcsec_radio = 0.5  # Image scaling
+px2arcsec_xray = 0.492
+r_shock = 240  # arcsec
+r_rise = 2  # Dist of x-ray peak behind shock (arbitrary guess!)
+
+r_min = 200  # arcsec, plot bounds
+r_max = 250
+
+nums = [1,2,3,4]  # Labeling
+names = ['NNE', 'NW', 'WNW', 'SW']
+
+
+def main():
+    """Make subplot grid of profiles for all regions"""
+    plt.figure(figsize=(8,6))
+
+    for num, name in zip(nums, names):
+
+        prfs, scales = load_prf_data(num)
+        prf_radio, prf_xsoft, prf_xhard = prfs
+        scale_radio, scale_xsoft, scale_xhard = scales
+
+        plt.subplot(2, 2, num)
+        plt.plot(prf_radio[:,0], prf_radio[:,1] / scale_radio, '-r.',
+                 label='1.375 GHz')
+        plt.plot(prf_xsoft[:,0], prf_xsoft[:,1] / scale_xsoft, '-g.',
+                 label='1-1.7 keV')
+        plt.plot(prf_xhard[:,0], prf_xhard[:,1] / scale_xhard, '-b.',
+                 label='4-7 keV')
+
+        plt.xlim(r_min,r_max)
+        plt.ylim(ymin=0)
+        if num == 3:
+            plt.ylim(ymax=1.5)
+
[…]

### 2014-11-20 code/models/FullEfflength_port.py

@@ -170,6 +170,10 @@ def fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s, rminarc, icut, irmax,
         w = fwhm(rmesh, intensity, get_intensity)
         widths.append(w)
         if get_prfs:
+            # Tack on point at r=1
+            rmesh = np.append(rmesh, 1.0)
+            intensity = np.append(intensity, 0.0)
+            # Then save to return, after we're done
             rgrids.append(rmesh * rsarc)
             prfs.append(intensity)
 

### 2014-11-20 code/models/models.py

@@ -377,9 +377,127 @@ def mind_the_gaps(x, yaux, y, dy_max, f):
 
     return x, yaux, y  # Match function call order...
 
-# ========================================
-# Wrappers for full/simple model functions
-# ========================================
+
+# ======================================================
+# Code to fit extracted image profiles to model profiles
+# ======================================================
+
+def profile_fit(snr, kevs, prfs, epss, r_prfs, mu, eta2=None, B0=None,
+    r_trans=0, amp=1, ab_fit=None, mu_free=False, eta2_free=False,
+    B0_free=True, rminarc_f = 1.2, model_kws=None, **lmfit_kws):
+    """Fit measured thin rim profiles to model profiles, with single
+    translation and amplitude shift for profiles at all energies
+
+    The model_kws 'get_prfs', 'irad_adapt', 'rminarc' are set/overriden so that
+    profile fitting will work correctly.
+
+    Inputs:
+        snr, kevs as usual
+        prfs, epss, r_prfs are lists of profiles, errors, r_grids
+        mu, B0, eta2 (float) initial guesses
+        mu_free, eta2_free (bool) which parameters shall vary in fits?
+        ab_fit (float) if specified, allow ab to be a fit parameter
+            (if you don't want it to vary, specify via model_kws instead)
+            (BUT, enable idamp=True for this to work)
+        **lmfit_kws takes extra kwargs for lmfit.minimize (includes lsq kws)
+
+        model_kws={'icut':True, 'verbose':True, 'rminarc':60, ...}
+    Output:
+        lmfit.Minimizer with fit information / parameters
+    """
+    if model_kws is None:
+        model_kws = {}
+    model_kws['get_prfs'] = True
+    model_kws['irad_adapt'] = False
+
+    # require rminarc to be larger than r_prfs at all energies
+    # default safety factor 1.2
+    rminarc = []
+    for r_prf in r_prfs:
+        rminarc.append(max(r_prf) - min(r_prf))
+        # r_prf needn't be sorted, technically
+    model_kws['rminarc'] = rminarc_f * np.array(rminarc)
+
+    p = lmfit.Parameters()
+    for pstr in ['mu', 'B0', 'eta2']:
+        pval = locals()[pstr]
+        if pval is None:
+            pval = snr.par_init[pstr]
+        p.add(pstr, value=pval, vary=locals()[pstr+'_free'],
[…]

### 2014-12-03 manuscript/paper-tycho.tex
Update ms tables/plts, spectr disc, specvar ipynb
Manuscript table/plots generated for regions-6
Add text on srcutlog fits, spectral variation tests, sketch out
radio profile fitting / shape analysis.
Split spectral variation code to new ipynb (not tested)
Rename fitting ipynbs more usefully, clean radio prf fitting ipynb

@@
 off downstream, producing a shell-like morphology with bright X-ray and radio
-rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
-relatively strong synchrotron radiation, in conjunction with multiwavelength
-spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
-ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
-suggests that electrons are accelerated to PeV energies in young SNRs.
-Although synchrotron emission due to accelerated electrons does not imply
-acceleration of an unseen hadronic component, the prevailing theory of
-diffusive shock acceleration (DSA) should operate on both protons and
-electrons.  Efficient hadron acceleration in supernova remnant shocks is a
-prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
-``knee'' \citep{vink2012}.
+rims/filaments due to line-of-sight projection \citep{koyama1995}.  The strong
+and time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
+patnaude2007}, in conjunction with multiwavelength spectral modeling
+\citep{aharonian2004, acero2010, ackermann2013}, suggests that electrons are
+accelerated to PeV energies in young SNRs.  Although synchrotron emission due
+to accelerated electrons does not imply acceleration of an unseen hadronic
+component, the prevailing theory of diffusive shock acceleration (DSA) should
+operate on both positive ions and electrons.  Efficient hadron acceleration in
+supernova remnant shocks is a prime candidate source for galactic cosmic rays
+up to the cosmic ray spectrum's ``knee'' \citep{vink2012}.
 
@@
 rapidly radiate energy to account for the thinness of observed rims
-\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
-synchrotron flux from supernova remnants steepens at X-ray energies
-\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
-spectrum as predicted by diffusive shock acceleration \citep{webb1984}.  Many
-fundamental questions about the shock acceleration process remain to be
-answered.  Under what conditions do shocks accelerate particles efficiently?
-How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
-relevant observations and open questions to date.  The answers to these
-questions are broadly relevant to many astrophysical shocks, such as Earth's
-bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
-jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
-even cosmological shocks \citep{ryu2008}.
+\citep{bamba2003, vink2003, parizot2006}.  Furthermore, the synchrotron
+spectrum of supernova remnants steepens at X-ray energies \citep{reynolds1999},
+corresponding to a cut-off in the underlying electron spectrum as predicted by
+diffusive shock acceleration \citep{webb1984}.  Many fundamental questions
+about the shock acceleration process remain to be answered.  Under what
+conditions do shocks accelerate particles efficiently?  How are magnetic fields
+amplified in such shocks?  \citet{reynolds2008} reviews relevant observations
+and open questions to date.  The answers to these questions are broadly
+relevant to many astrophysical shocks, such as Earth's bow shock
+\citep{ellison1990}, starburst galaxies \citep{heckman1990}, jets of active
+galactic nuclei \citep{chen2014}, galaxy clusters \citep{van-weeren2010}, and
+cosmological shocks \citep{ryu2008}.
 % Expand on these questions -- plasma turbulence, Alfven waves, wave damping
@@
 advection.  Finally, the magnetic field strength may be quickly damped
-downstream of the shock, so that electrons may not radiate as efficiently and
-thin rims reflect the spatial structure of the field rather than efficient
-particle acceleration (and losses) and/or efficient synchrotron cooling
-\citep{pohl2005}.
+downstream of the shock, preventing electrons from radiating efficiently so
+that thin rims reflect the spatial structure of the field rather than efficient
+particle acceleration and synchrotron cooling \citep{pohl2005}.
 
@@
 Moreover, these controlling mechanisms predict different scalings for rim width
-as a function of energy.  In the limiting case of constant magnetic field and
-negligible particle diffusion, the rims are said to be synchrotron loss-limited
-and rim widths should narrow with increasing photon frequency $\nu$ as
-$\nu^{-1/2}$. Diffusion smears out rims at all energies with stronger effect at
-higher energies, yielding a slower drop-off in rim widths when diffusion
-dominates.  Magnetic damping, if at a length scale comparable to filament
-widths, also favors more energy-insensitive rim widths -- intuitively, if the
-magnetic field turns off, synchrotron radiation turns off regardless of
-electron energy.
+as a function of energy.  If the downstream magnetic field is constant and
+diffusion is negligible downstream of the shock, the rims are said to be
+synchrotron loss-limited and rim widths ($w$) should narrow with increasing
+photon frequency ($\nu$) as $w \propto \nu^{-1/2}$. Diffusion smears out rims
+at all energies with stronger effect at higher energies, yielding a slower
+drop-off in rim widths when diffusion dominates.  Magnetic damping, if at a
+length scale comparable to filament widths, also favors more energy-insensitive
+rim widths -- intuitively, if the magnetic field turns off, synchrotron
+radiation turns off regardless of electron energy.
 
 % Magnetic damping?
-Magnetic damping immediately behind the shock offers a tantalizing alternative
-explanation for filament rims that requires less extreme magnetic field
-amplification, and the possibility of damping in SNR shocks has not been fully
-tested \citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined
-radio and X-ray synchrotron rim profiles, but found that neither damping nor
-synchrotron losses matched radio profiles particularly well.  \citet{araya2010}
-measured rims at multiple energy bands in Cas A, but suggested that the rims
-only narrow more weakly than expected and did not consider magnetic damping.
+Magnetic damping immediately behind the shock offers an alternative explanation
+for filament rims that requires less extreme magnetic field amplification, and
+the possibility of damping in SNR shocks has not been fully tested
+\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined radio and
+X-ray synchrotron rim profiles, but found that neither damping nor synchrotron
+losses matched radio profiles particularly well.  \citet{araya2010} measured
+rims at multiple energy bands in Cas A, but suggested that the rims only narrow
+more weakly than expected and did not consider magnetic damping.
 \citet{rettig2012} gave model predictions for several historical SNRs and
@@
 damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
-further extended the idea of discriminating between damped or loss-limited
-rims by measuring rim width energy dependence in X-ray energies and found that
-rims consistently narrowed in the remnant of SN 1006.
+further extended the idea of discriminating between damped or loss-limited rims
+by measuring rim width energy dependence in X-ray energies and found that rims
+consistently narrowed in the remnant of SN 1006.
 
@@
 resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
-(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
-Furthermore, Tycho has been a prime target of study for determining whether
-hadrons are being accelerated in historic SNRs \citep[and references
-therein]{morlino2012}; understanding the acceleration process will also bear
-upon our understanding of CR acceleration in Tycho.
+(PI: J. Hughes) allows fine sampling of the remnant rims.  Furthermore, Tycho
+is a prime target of study to determine whether hadrons are being accelerated
+in historic SNRs \citep[and references therein]{morlino2012}; understanding the
+acceleration process for electrons will also bear upon our understanding of CR
+acceleration in Tycho.
 
@@
 presentation is somewhat abbreviated, but a fuller exposition and literature
-review is given by \citetalias{ressler2014}.
+review are given by \citetalias{ressler2014}.
 
@@
 
-% e- cutoff energy result
+% e- cut-off energy result
 With a diffusion coefficient in hand, we may determine the electron spectrum
@@
 % srcut constraint on diffusion
-As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
-flux, the synchrotron roll-off frequency may provide an independent observable
+As the DSA imposed electron cut-off results in a cut-off on SNR synchrotron
+flux, the synchrotron cut-off frequency may provide an independent observable
 to estimate shock diffusion and is given by:
-\begin{align} \label{eq:rolloff}
+\begin{align} \label{eq:cutoff}
     \nu_{\mt{cut}} =
@@
 The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
-rettig2012} assume $D(x) B^2(x)$ constant in order to make the equation
-semi-analytically tractable.  Although unphysical, we enforce this criterion by
-using a modified diffusion coefficient in our calculations following
+rettig2012} assume $D(x) B^2(x)$ constant in order to make
+equation~\eqref{eq:model} semi-analytically tractable.  Although unphysical, we
+enforce this criterion by using a modified diffusion coefficient in our
+calculations following
 \citet{rettig2012}, given as:
@@
 \end{equation}
-This does strengthens the spatial-dependence of the diffusion coefficient, as
+This strengthens the spatial-dependence of the diffusion coefficient, as
 compared to the expected $D(x) \propto 1/B(x)$.
-\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
-will check shortly}
+% TODO
+%\note[Aaron]{I am not certain whether this should be scaled by $\Bmin$ instead,
+%will check shortly}
 
@@
 widths at higher photon energies (advection: $l_\mt{ad} < a_b$;
-diffusion: $a_b < l_{\mt{diff}} < l_{\mt{ad}}$).
+diffusion: $l_{\mt{diff}} > l_{\mt{ad}}, a_b$).
 
@@
     regions 14--17, filament 5, regions 18--20.
-    \note[Aaron]{Inverted colors for draft only}
     \label{fig:snr}}
@@
 % NOTE keep stated ranges, region numbers up to date
-% THIS IGNORES THE BAD (insufficient counts) REGION 19 DOWNSTREAM SPECTRUM FIT (!!)
 Downstream spectra are generally poorly-fit by the absorbed power law model,
@@
 removed) and (2) with both lines fitted to Gaussian profiles.  Fits with lines
-excised yield $\chi^2_{\mt{red}}$ values between $0.8$--$1.4$, excepting only
-Regions 5 and 20 with $\chi^2_{\mt{red}} \sim 1.8$ due to the presence of
-additional thermal lines.  Fits with lines fitted to Gaussian profiles yield
-$\chi^2_{\mt{red}}$ values $0.83$--$1.22$, again excepting Regions 5, 20 which
-have $\chi^2_{\mt{red}} \sim 1.6$.  In both fits (lines excised or modeled), we
-find somewhat smaller best fit column densities ($0.32$--$0.74 \times 10^{22}
-\unit{cm^{-1}}$) but similar best fit photon indices ($2.52$--$3.05$), compared
-to those of the rim spectra.  The consistent photon indices confirm that the
-same synchrotron continuum may be recovered from beneath thermal line emission.
+excised yield $\chi^2_{\mt{red}}$ values between $1$--$5$.  Fits with lines
+fitted to Gaussian profiles yield $\chi^2_{\mt{red}}$ values $0.83$--$1.6$.  In
+both fits (lines excised or modeled), we find somewhat smaller best fit column
+densities ($0.3$--$0.8 \times 10^{22} \unit{cm^{-1}}$) but similar best fit
+photon indices ($2.6$--$3.1$), compared to those of the rim spectra.  The
+consistent photon indices indicate that the same synchrotron continuum is
+present beneath thermal line emission.
 
@@
 
-\begin{table*}
-    \scriptsize
-    \centering
-    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
-    \input{suppl-spec-pt2.tex}
-    \tablecomments{As described in text,
-    we consider absorbed power law fits with lines fitted to two Gaussians
-    (here characterized by equivalent width and line energy), or with lines
-    manually excised.  See comments on Table~\ref{tab:spec}.}
-\end{table*}
-
 % This table is still useful to look at the fit parameters (to make
@@
 %\begin{table*}
-%    \footnotesize
+%    \scriptsize
 %    \centering
 %    \caption{Region spectra fit parameters\label{tab:spec-pt2}}
-%    \input{tab-spec-pt2.tex}
+%    \input{suppl-spec-pt2.tex}
+%    \tablecomments{As described in text,
+%    we consider absorbed power law fits with lines fitted to two Gaussians
+%    (here characterized by equivalent width and line energy), or with lines
+%    manually excised.  See comments on Table~\ref{tab:spec}.}
 %\end{table*}
@@
 e.g., $0.7$--$1 \unit{keV}$ is assigned to $0.7 \unit{keV}$ and fitted to model
-profile widths at $0.7 \unit{keV}$.  Errors in our least squares fits average
-the positive and negative errors on each FWHM measurement.  For an input set of
-model parameters, we numerically computed intensity profiles and hence model
-FWHMs as detailed in Section~\ref{sec:transport}, and used a
-Levenberg-Marquardt fitting routine to identify best fit model parameters
-(subject to varied constraints on model parameters in the following paragraph).
+profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
+average the positive and negative errors on each FWHM measurement.  For an
+input set of model parameters, we numerically computed intensity profiles and
+hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
+Levenberg-Marquardt fitting routine to identify best fit model parameters.
 To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
@@
 % How we twiddled model knobs
-We first considered a purely loss-limited model (constant magnetic field
-$B_0$) with three parameters $\mu$, $\eta_2$, and $B_0$.  To make nonlinear
-fitting tractable, we fixed $\mu$ in all fits and considered $\mu = 0$, $1/3$,
-$1/2$, $1$, $1.5$, and $2$.  In particular, nonlinear diffusion-energy
-scalings with $\mu = 1/3$ and $1/2$ may arise from Kolmogorov and Kraichnan
-turbulent energy spectra respectively \citep{reynolds2004}.  The remaining
-parameters $\eta_2$ and $B_0$ varied freely.
+We first considered a purely loss-limited model (constant downstream magnetic
+field $B_0$) with three parameters $\mu$, $\eta_2$, and $B_0$.  To make
+nonlinear fitting tractable, we fixed $\mu$ in all fits and considered $\mu =
+0$, $1/3$, $1/2$, $1$, $1.5$, and $2$.  In particular, nonlinear
+diffusion-energy scalings with $\mu = 1/3$ and $1/2$ may arise from Kolmogorov
+and Kraichnan turbulent energy spectra respectively \citep{reynolds2004}.  The
+remaining parameters $\eta_2$ and $B_0$ varied freely.
 
@@
 our ``best'' damping fits report the value of $a_b$ yielding the smallest
-$\chi^2$ value.  Finally, we fixed $\mu = 1$ for all damped fits.
-
-% Variants on our fitting procedure
-To better explore the parameter space of model predictions, we also computed
-model fits with both $\eta_2 = 1$ and $\mu = 1$ fixed for both scenarios of
-constant and damped magnetic field.  We also attempted damping fits with
-$\Bmin = 2 \muG$, somewhat on the lower end of estimated galactic
-magnetic field values.
+$\chi^2$ value.  Finally, $\mu = 1$ was fixed for all damped fits.
 
@@
 % Model resolution error
-As the full model must be numerically solved, its predicted rim widths are
-subject to resolution error in the numerical integrals (discretization over
-radial coordinate, line-of-sight coordinate, electron distribution, Green's
-function integrals).  We chose integration resolutions such that the
-fractional error in model FWHMs associated with halving or doubling each
-integration resolution (individually) is less than $1\%$ for the parameter
-space relevant to our filaments -- $\eta_2 \leq 10^3$ for the loss-limited
-model and $\eta_2 \leq 10$ for the magnetic damping model).  In our error
-analysis, the maximum resolution errors in a sample of parameter space are
-typically $0.1$--$1\%$, but mean and median errors are typically an order of
-magnitude smaller that maximum errors.  Thus we expect numerical errors to be
-negligible.
+Predicted rim widths are subject to resolution error in the numerical integrals
+(discretization over radial coordinate, line-of-sight coordinate, electron
+distribution, Green's function integrals).  We chose integration resolutions
+such that the fractional error in model FWHMs associated with halving or
+doubling each integration resolution is less than $1\%$ for the parameter space
+relevant to our filaments.  In our error analysis, the maximum resolution
+errors in a sample of parameter space are typically $0.1$--$1\%$, but mean and
+median errors are typically an order of magnitude smaller that maximum errors.
 
@@
 % Present table of FWHM results
+Measured rim widths decrease with energy in most regions and energy bands.
 Table~\ref{tab:fwhms} reports FWHM measurements for all of our regions.
@@
 
-% Observations of mE and rim widths and stuff
-Measured rim widths decrease with energy in most regions and energy bands.
+% Observations of mE and rim widths, errors
 Although the measurement scatter is quite large, shown dramatically in the
@@
 negative and tend smoothly towards $0$ (weaker energy-dependence) with
-increasing energy.
-
-% Errors in rim widths
-The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
-reflecting the high quality of underlying \Chandra data as also seen in
+increasing energy.  The errors on FWHM measurements are typically $\abt 10\%$
+or smaller, reflecting the high quality \Chandra data as also seen in
 Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
@@
 arbitrary choice of profile fit function, and (2) variation in Tycho's rim
-morphology (see Figure~\ref{fig:profiles}).
+morphology (e.g., Figure~\ref{fig:profiles}).
 
@@
         (top) and 16 (bottom) for loss-limited and damped scenarios with
-        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Shaded
-        regions on damped profiles indicate the damping ($e$-folding)
-        lengthscale for the magnetic field.  Note that radial coordinate ($r$)
-        axes agree in each row (same region), but not in each column.
+        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
+        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
+        damped profiles indicate the magnetic field damping lengthscale $a_b$.
         \label{fig:rims}}
@@
     plot pure loss-limited fits with varying $\mu$, solid curve plots estimated
-    best moderately damped fit ($a_b < 0.01$); the corresponding fit
-    parameters are given in Tables~\ref{tab:fits-loss}, \ref{tab:fits-damp}.
-    Note that ordinate FWHM axes do not match and are offset from the origin to
-    better show model predictions and data variation.
+    best moderately damped fit ($a_b < 0.01$) with $\mu = 1$.  Relevant fit
+    parameters are given in Tables~\ref{tab:fits-loss} and \ref{tab:fits-damp}.
+    Note that ordinate FWHM axes are not the same and are offset from the
+    origin to better show model predictions and data variation.
     \label{fig:fits}}
@@
     Corresponding best fit parameters are given in Table~\ref{tab:fits-all}.
+    As in Figure~\ref{fig:fits}, $y$-axis limits vary and are offset from the
+    origin to better show model predictions and data.
     \label{fig:fits-all}}
@@
 % First address the broad trend of leveling energy dependence in mE)
-We suggest that our observed decrease in $|\mE|$ with increasing energy is
-caused by diffusion, which weakens width-energy dependence at higher energies.
-The photon energy at which $l_{\mt{ad}} = l_{\mt{diff}}$ is exactly the
-synchrotron roll-off energy,  % TODO citation if you can find it...
-$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Then we expect diffusion to
-begin overtaking advection and push $\mE$ towards $0$ in soft X-rays, as
-opposed to $\mE \abt -0.5$ expected for strong advection
-(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
-consistent with the framework of diffusive shock acceleration.
-We note that our model fits have not incorporated the additional constraint of
-synchrotron roll-off energy, which would in fact fix $\eta_2$ for a given value
-of $\mu$ (equation~\eqref{eq:rolloff}).
-% TODO explain why not, perhaps
-
-% This conclusion is based strictly on our measurements.
-% Our transport model hard-codes this width leveling through \Ecut
+We suggest that the observed decrease in $|\mE|$ with increasing energy
+(Table~\ref{tab:fwhms}) is caused by diffusion, which weakens width-energy
+dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
+l_{\mt{diff}}$ is exactly the synchrotron cut-off energy,
+% TODO citation if you can find it...
+$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Diffusion should begin
+overtaking advection and push $\mE$ towards $0$ in soft X-rays, as opposed to
+$\mE \abt -0.5$ expected for strong advection (Section~\ref{sec:energydep}).  A
+decrease in $|\mE|$ is then reassuringly consistent with the framework of
+diffusive shock acceleration.
 
 % Discuss variability in width measurements
-The large scatter in filament widths and hence point-wise computed $\mE$ values
-(Table~\ref{tab:fwhms}) does relegate our interpretation of $\mE$ to conjecture.
-Multiple regions show both increases and decreases in filament widths between
-energy bands, and we have seen that diffusion ($\eta_2$) is poorly constrained
-by our fit results.  Our averaged results should mitigate this natural
-measurement spread, however.
-
-% Can damping explain stuff?
-% Somewhat redundant (overlap with Section~\ref{sec:energydep})
-The next question is whether damping may also produce a decrease in $|\mE|$,
-independent of assumptions on the shock acceleration process.  Conceptually, if
-damping controls rim widths past the cut-off energy, $|\mE|$ may slightly
-decrease or even increase as rims transition from being damping controlled to
-being diffusion loss-limited.  If damping is only important well below the
-cut-off energy, then we may see an increase in $|\mE|$ as advection becomes
-important.  Although magnetic damping is able to fit observed rim widths, our
-model assumes diffusive shock acceleration in computing $\Ecut$ and hence we
-may not use our model fits to assess whether magnetic damping can independently
-account for decreasing $|\mE|$.  This applies for loss-limited fits as well;
-since $\eta_2$ varies freely, $\Ecut$ may be anywhere -- and thus the model
-behavior is not necessarily physically reasonable.
-
-% Curious effects of damping competing with other things
-In a damped field scenario, synchrotron cooling far downstream of the shock
-(many $e$-folding lengths $a_b$) may also introduce energy dependence in rim
-widths.  Sufficiently energetic electrons will radiate and cool within the
-damping length $a_b$, but lower energy electrons propagating farther downstream
-will eventually radiate and cool in a relatively constant field $\abt \Bmin$.
-Synchrotron losses will ``sieve'' out higher energy electrons as in the
-loss-limited model, and observed rim widths, if larger than $a_b$, may be
-somewhat loss-limited at low energies, well-confined by damping at moderate
-energies, then diffusion (or cut-off spectrum) limited at the highest energies.
-
-We revisit the effects of damping further below.  The observation of decreasing
-$|\mE|$, however, remains consistent with and expected from the theory of
-diffusive shock acceleration.
+The large scatter in filament widths and hence scatter in point-wise computed
+$\mE$ values (Table~\ref{tab:fwhms}) relegates our interpretation of $\mE$ to
+conjecture.  Filament widths both increase and decrease between energy bands in
+multiple regions, and diffusion ($\eta_2$) and hence $\Ecut$ are poorly
+constrained by our fit results.  Our averaged results should mitigate the
+effects of measurement scatter, however.
+
+% Can damping explain this mE trend? (a 2nd order effect)
+% forward reference the "weak-field" damping discussion
+Diffusion may be irrelevant if magnetic field damping can also cause the
+observed decrease in $|\mE|$ with energy, independent of the details of shock
+acceleration.  If damping controls rim widths at energies above the cut-off
+energy, $|\mE|$ may slightly decrease or even increase with energy as rims
+transition from being damping controlled to being diffusion loss-limited.  If
+damping is only important well below the cut-off energy, then $|\mE|$ may
+increase with energy as advection becomes important.  But, synchrotron
+losses far downstream of the shock (many $e$-folding lengths $a_b$) can also
+give rise to stronger rim width-energy dependence than expected for a damped
+magnetic field, which we discuss further in section~\ref{sec:damp-fit-disc}.
+The effect of damping upon $\mE(E)$ is somewhat uncertain.
 
@@
 
-% Discuss degeneracy in loss-limited and damped models both
-We now turn to our model fit parameters: magnetic field strength $B_0$ and
-scaled diffusion coefficient $\eta_2$.  Our loss-limited fit results are poorly
+% Discuss degeneracy in loss-limited model
+We now turn to the model fitting parameters: magnetic field strength $B_0$ and
+scaled diffusion coefficient $\eta_2$.  Loss-limited fits are poorly
 constrained as $B_0$ and $\eta_2$ may covary without strongly altering fit
 quality.  If diffusion is the primary control on rim width -- i.e.,
-$l_{\mt{diff}} > l_{\mt{ad}}$ and thus rim width $w \sim l_{\mt{diff}}$) --
-then $\eta_2$ and $B_0$ become degenerate as the product $\eta^{1/2}
-B_0^{-3/2}$ exerts most control on rim width $w$.  If advection is the primary
-control on rim width (widths narrow rapidly with energy, at $\mE \sim -0.5$),
-then $\eta_2 \ll 1$ becomes unimportant and the fit is better behaved with
+$l_{\mt{diff}} > l_{\mt{ad}}$ -- then $\eta_2$ and $B_0$ become degenerate as
+the product $\eta^{1/2} B_0^{-3/2}$ exerts most control on rim width $w \sim
+l_{\mt{diff}}$ (equation~\eqref{eq:ldiff}).  If advection is the primary
+control on rim width (widths narrow rapidly with energy; i.e., $\mE \sim
+-0.5$), then $\eta_2 \ll 1$ becomes unimportant and fits are well-behaved with
 effectively one free parameter.  The degeneracy of $B_0$ and $\eta_2$ is
-stronger for smaller values of $\mu$, although there appears no clear trend as
-to when a particular fit will be ill-constrained.
-
-In the damped model, a similar degeneracy is present but modified somewhat by
-the presence of damping.  For small values of $a_b$ (strong damping), increased
-diffusion $\eta_2$ can cause rim widths to \emph{narrow}, contrary to
-intuition; $B_0$ and $\eta_2$ generally covary in controlling rim widths, but
-the relationship is now less clear.  Speculatively, the opposition to
-downstream flow may be tied to the spatial variation of the diffusion
-coefficient, which gives rise to an additional term $-(\ptl D(x) / \ptl x)
-(\ptl f/\ptl x)$ that opposes downstream flow in equation~\eqref{eq:model}.
-
-% NOTE some of this discussion of parameter values could go
-% into results instead.
-
-% B0 lower bounds, etc. in loss-limited model
-In our loss-limited model fits, the minimum magnetic field strength we observe
-throughout the remnant, within stated errors, is $B_0 = 179 \muG$.  The minimum
-values of $B_0$ for each filament (1--5) are $179$, $254$, $287$, $458$, and
-$243 \muG$.  We observe the smallest $B_0$ values for $\eta_2$ approaching $0$
-and $\mu = 2$; intuitively, $\mu = 2$ gives stronger diffusion at higher
-energies ($>2\unit{keV}$) where it is most ``needed'' to reproduce the leveling
-off of filament widths and so $\mu = 2$ permits a smaller best-fit $\eta_2$ and
-hence smaller $B_0$.  Furthermore, when $\eta_2 = 1$ is fixed we find that
-$B_0$ is well-constrained in the loss-limited model, falling strictly between
-$180$--$500 \muG$ (Table~\ref{tab:fits-all-eta2one}).  In this scenario the
-range of $B_0$ values is directly correlated to the observed range of rim
-widths.  Our minimum loss-limited values of $B_0$ are consistent with prior
-estimates of $\abt 200$--$300 \muG$ for primarily advective transport
-\citep{volk2005, parizot2006, morlino2012}.  If loss-limited, Tycho's rims
-require strong magnetic field amplification -- at least $\abt 100\times$ the
-typical galactic field values of $\abt 2$--$3 \muG$, versus the expected
-$4\times$ amplification from a strong shock with compression ratio $r=4$.
-
-The damped model fits permit much smaller values of $B_0$, as expected.
+stronger for smaller values of $\mu$, although we observe no clear trend for
+the conditions under which a model fit is ill-constrained.
+
+% Then, degeneracy modification in the damping model
+The degeneracy in $B_0$ and $\eta_2$ is modified by the presence of damping.
+For small values of $a_b$ (strong damping), increased diffusion $\eta_2$ can
+cause rim widths to narrow counterintuitively.  Speculatively, spatial
+variation of the diffusion coefficient, which gives rise to a
+term $(\ptl D(x) / \ptl x) (\ptl f/\ptl x)$ in equation~\eqref{eq:model}, may
+oppose downstream advection by decreasing an effective velocity $v_d - \ptl
+D(x) / \ptl x$ and thus require thinner rims as $\eta_2$ and $\ptl D(x) / \ptl
+x$ increase.
+
+% B0 lower bounds in loss-limited model
+In loss-limited model fits, the minimum magnetic field strength throughout the
+remnant, within stated errors, is $B_0 = 179 \muG$.  The minimum values of
+$B_0$ for each filament (1--5) are $179$, $254$, $287$, $458$, and $243 \muG$.
+Best fit $B_0$ values are smallest for $\eta_2$ approaching $0$ and $\mu =
+2$; intuitively, $\mu = 2$ yields stronger diffusion at higher energies
+($>2\unit{keV}$) for fixed $\eta_2$, permitting a smaller best-fit $\eta_2$ and
+hence smaller $B_0$.  Furthermore, fixing $\eta_2 = 1$ constrains $B_0$ between
+$180$--$500 \muG$ (Table~\ref{tab:fits-all-eta2one}); the range of $B_0$ values
+is directly correlated to the observed range of rim widths.  Our minimum
+loss-limited values of $B_0$ are consistent with prior estimates of $\abt
+200$--$300 \muG$ for advection-dominated transport \citep{volk2005,
+parizot2006, morlino2012}.  If loss-limited, Tycho's rims require strong
+magnetic field amplification -- at least $\abt 100\times$ the typical galactic
+field values of $\abt 2$--$3 \muG$, versus the expected $4\times$ amplification
+from a strong shock with compression ratio $r=4$.
+
+Magnetic damping fits permit much smaller values of $B_0$, as expected.
 The maximum best-fit $B_0$ value observed is $340 \muG$, with a majority of
-values below $100 \muG$.  The minimum value of $B_0$ is around $10$--$20
-\muG$, which is consistent with shock compression alone.
-Fixing $\Bmin = 2 \muG$ instead of $5 \muG$ generally permits smaller
-fit $B_0$ values, though both $\eta_2$ and $B_0$ still display a large spread.
+values below $100 \muG$.  The minimum value of $B_0$ is around $10$--$20 \muG$,
+which is consistent with the expected compression ratio of $4$ for a strong
+shock and requires no field amplification.  Fixing $\Bmin = 2 \muG$ instead of
+$5 \muG$ permits smaller fit $B_0$ values, though fit values for both $\eta_2$
+and $B_0$ still display considerable scatter.
 
@@
 % acceleration and escape on the shock hydrodynamics.
-
 % \citet{rettig2012} used a measured filament lengthscale and considered
 % loss-limited and magnetic damping models separately for several historical
-% SNRs.  For Tycho: they report $B = 310 \muG$ with $\Ecut = 24
-% \unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
-% lengthscales, this is equivalent to our reporting of a diffusion coefficient
-% (?).  With magnetic damping, they report $B = 150 \muG$ and a larger
-% $\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
-% give $80$, $230 \muG$ for leptonic/hadronic models for gamma-ray
-% emission in Tycho.
+% SNRs.  For Tycho: $B = 310 \muG$ with $\Ecut = 24 \unit{TeV}$; since $\Ecut$
+% is set by balancing advective/diffusive lengthscales, this is equivalent to
+% our reporting of a diffusion coefficient (?).  With magnetic damping, they
+% report $B = 150 \muG$ and a larger $\Ecut = 34 \unit{TeV}$.
+% Taken from \citet{rettig2012}: \citet{acciari2011} give $80$, $230 \muG$ for
+% leptonic/hadronic models for gamma-ray emission in Tycho.
 
 % eta2
-% NOTE keep notes on eta2 < 1 updated (region 5 should be better, after I
-% remove the bad FWHM)
-The best-fit values of $\eta_2$, for both loss-limited and damped fits,
-are very poorly constrained.  In the loss-limited fits, we observe no clear
-trend of $\eta_2$ with $\mu$ (Table~\ref{tab:fits-loss}) excepting a general
-preference for smaller $\eta_2$ at $\mu > 1$.  Loss-limited fits are generally
-consistent with the Bohm limit on diffusion, favoring $\eta_2 \geq 1$; only
-Regions 5 and 18 have best-fit $\eta_2$ values strictly below $\eta_2 = 1$
-after accounting for error.  Damped fits favor smaller values of $\eta_2$ in
-contrast to loss-limited models, perhaps as stronger damping and smaller
-$\eta_2$ have cancelling effects on rim widths (recalling that with moderate
-damping, smaller $\eta_2$ counterintuitively gives larger rim widths).
+The best-fit values of $\eta_2$ for both loss-limited and damped fits are very
+poorly constrained.  Loss-limited fits show no clear trend of $\eta_2$ with
+$\mu$ (Table~\ref{tab:fits-loss}) except a general preference for smaller
+$\eta_2$ at $\mu > 1$.  Loss-limited fits are generally consistent with the
+Bohm limit on diffusion, favoring $\eta_2 \geq 1$; only Regions 5 and 18 have
+best-fit $\eta_2$ values strictly below $\eta_2 = 1$ after accounting for
+error.  Damped fits favor smaller values of $\eta_2$ in contrast to
+loss-limited models, perhaps as stronger damping and smaller $\eta_2$ have
+cancelling effects on rim widths (recalling that for moderate to strong
+damping, smaller $\eta_2$ gives larger rim widths).
 
@@
 Our loss-limited fits at multiple values of $\mu$ are not especially
-insightful.  The $\chi^2$ values for individual fits are variable and quite
-large, so we are unable to favor or disfavor fits at different $\mu$ values.
-But, neglecting the magnitude of our $\chi^2$ values, we observed that values
-of $\mu \geq 1$ are qualitatively favored by $\chi^2$ in almost all regions.
-This trend may be partially an artifact of the correlation between $B_0$ and
-$\eta_2$ as they are not entirely independent parameters, but they are less
-correlated for larger $\mu$; it may be said that fits at smaller $\mu$ may have
-fewer (non-integer) degrees of freedom, partially offsetting our observations.
-\citetalias{ressler2014} also found better model fits for $\mu \geq 1$ in the
-remnant of SN 1006 and noted that \citet{reynolds2004} favored $\mu \geq 1$ on
-grounds of better modeled remnant morphology, but it remains uncertain whether
-$\mu \geq 1$ diffusion is truly preferred.
-
-We do not explore $\mu$ dependence extensively in the damped model, but that
+insightful.  The $\chi^2$ values for individual fits are variable and large
+($\gg 1$), so we cannot favor or disfavor fits at different $\mu$ values.  But,
+neglecting the magnitude of our $\chi^2$ values, values of $\mu \geq 1$ are
+qualitatively favored by $\chi^2$ in almost all regions.  This trend may be
+partially an artifact of the correlation between $B_0$ and $\eta_2$ as they are
+not entirely independent parameters, but they are less correlated for larger
+$\mu$; fits at smaller $\mu$ may have fewer (non-integer) degrees of freedom,
+partially offsetting our observations.  \citetalias{ressler2014} also found
+better model fits for $\mu \geq 1$ in the remnant of SN 1006 and noted that
+\citet{reynolds2004} favored $\mu \geq 1$ on grounds of better modeled remnant
+morphology, but it remains uncertain whether $\mu \geq 1$ diffusion is truly
+preferred.
+
+We do not explore $\mu$ dependence extensively in the damped model, but
 $\mu > 1$ permits smaller $B_0$ values and \emph{larger} $\eta_2$ values, in
@@
 
-\subsubsection{Tycho distance estimates}
+\subsubsection{Effect of Tycho distance estimates on model fits}
 % TODO need to update for damping results!!!!!
@@
 observed behavior.
-\note[Aaron]{need a logic check here}
 
@@
 In the damped model, a larger distance $d$ will require larger damping lengths
-from magnetic turbulence; our values of $a_b$ should be unchanged, however, as
-$a_b$ here is given in units of shock radius $r_s$.
-% TODO run more fits with varying remnant distance...
-% After I've gotten new sets of numbers set up
-
-% -------------------------------------------------------------------------
-% Main null result -- cannot disfavor either damping or loss-limited models
-% -------------------------------------------------------------------------
+from magnetic turbulence.  But, fitted values of $a_b$ will remain unchanged as
+we report $a_b$ in units of shock radius $r_s$.
+
+% ----------------
+% Main null result
+% ----------------
 \subsection{Damping is poorly-constrained by X-ray width-energy dependence}
-
+\label{sec:damp-fit-disc}
+
+% Conclusion -- width-energy dependence is not so helpful
 Width-energy dependence is not as sensitive a discriminant on damping versus
@@
 damped fits do not perfectly capture sharp drop-offs (especially between
-$0.7$--$1 \unit{keV}$ and $1$--$2 \unit{keV}$), and the data are greatly
-scattered.  In most regions, best fit width-energy curves have $\mE \sim -0.2$.
-Only in cases of very sharp energy drop-off (data and best loss-limited fit
-$\mE \sim -0.5$) is damping significantly disfavored as a control on rim widths
-(Region 18).
+$0.7$--$1 \unit{keV}$ and $1$--$2 \unit{keV}$), and the data show large
+scatter.  In most regions, best fit width-energy curves have $\mE \sim -0.2$.
+Only in cases where rim widths drop very sharply (data and best loss-limited
+fit $\mE \sim -0.5$) is damping significantly disfavored as a control on rim
+widths (e.g., Region 18).
 
 % Explain the dichotomy in energy dependence
-When width-energy dependence is weak, both loss-limited and damped rims give
-best fits with very similar shapes -- strong fields at the shock in both models
-give very sharp drop-offs in rim intensity.  When energy dependence is larger,
-damping profiles can only yield energy dependent rims if magnetic fields are
-fairly small (say, $\lesssim 50 \muG$) and rim half-maximums are achieved some
-distance away from the damping lengthscale.  Away from the shock, magnetic
-damping has already weakened and electron losses are controlled by synchrotron
-losses which act differentially on the range of electron energies we consider.
-
-\begin{figure}[h]
+When width-energy dependence is weak, both loss-limited and damped models give
+best fits with very similar profiles -- strong fields at the shock in both models
+give very sharp drop-offs in rim intensity.  When width-energy dependence is
+stronger, damping profiles can only yield energy dependent rims if magnetic
+fields are fairly small (say, $\lesssim 50 \muG$) and rims decline to half
+maximum at a distance larger than the damping lengthscale.  Away from the
+shock, the magnetic field asymptotically approaches $B_{\mt{min}} = 5 \muG$ and
+observed emission is controlled by synchrotron losses acting differentially on
+the range of electron energies we consider.  Synchrotron radiation sieves out
+higher energy electrons as in the loss-limited model for rim widths, giving
+rise to energy dependent emission.  Each case is shown in
+Figure~\ref{fig:rims}; in Region 1 the damping profiles are quite distinct from
+the loss-limited profiles, whereas in Region 16 they appear quite similar; note
+that emission downstream of the shock Region 1's best damped fit is quite close
+to the intensity half-maximum.
+
+\begin{figure}
     \centering
@@
 % Weak-field damping
-Each of these cases is illustrated in Figure~\ref{fig:rims}; in Region 1 the
-damping profiles are quite distinct from the loss-limited profiles, whereas in
-Region 16 they appear quite similar; note how emission downstream of the shock
-Region 1's best damped fit is quite close to the intensity half-maximum.  To
-further distinguish between these cases, Figure~\ref{fig:mE} plots predicted
+To further distinguish between these cases, Figure~\ref{fig:mE} plots predicted
 $\mE$ values from the best damped fits of Table~\ref{tab:fits-all},
-extrapolated to lower photon energies.  Although only qualitative, we see that
-a subset of best fits give increasing large FWHMs at lower energies ($0.1$--$1
-\unit{keV}$) and hence $\mE$ falls strongly negative; the extrapolated curves
-cut off when a FWHM can no longer be measured due to emission downstream of the
-rim rising above the half-rim-maximum level.  These curves correspond to fits
-for Regions 1, 2, 4, 5, 10, 12, 18, and 19, which were all best fit by a
-damping model with fields $B_0 < 40 \muG$.  For convenience, we will say that
-the damped fits to our data give rise to ``weak-field'' damping, associated
-with comparatively weak magnetic fields and stronger emission intensity in a
-plateau immediately downstream of the thin rim.
+extrapolated to lower photon energies.  Several best fits predict increasingly
+large FWHMs at lower energies ($0.1$--$1 \unit{keV}$), cutting off at low
+energies when a FWHM is no longer measurable; this corresponds to a sharp
+drop in $\mE$ (already negative) at low energies These curves correspond to
+fits for Regions 1--5, 10--12, 15, and 18, which were all best fit by a
+damping model with fields $B_0 < 40 \muG$.  We refer to such model behavior as
+``weak-field'' damping, associated with weak magnetic fields and stronger
+emission intensity immediately downstream of the thin rim.
 
@@
 The near constant curves in Figure~\ref{fig:mE} trend towards $\mE = 0$ at low
-energy, indicating that rims are strongly energy independent.  At higher
-energy, they give way to more energy dependent rims ($\mE \sim -0.2$) as
-necessary to match our observed width-energy dependence in X-rays; as discussed
-in Section~\ref{sec:energydep}, the gradual increase in $|\mE|$ is expected in
-the damping model as advection and diffusion take control of rim widths.
-The best damped fits for these regions all have larger $B_0$ values than in the
-``weak-field'' damping case, although not dramatically larger.  We shall refer
-to these fits as giving rise to ``strong-field'' damping, associated with
-stronger magnetic fields, weaker emission intensity behind the thin rim, and
-clear rims (with measurable FWHMs) at low photon energies (at and below soft X-ray).
+energy, indicating that predicted rim widths are strongly energy independent.
+At higher energy, rims become energy dependent ($\mE \sim -0.2$) to match the
+observed width-energy dependence in X-rays.  The gradual increase in $|\mE|$
+with energy is expected in the damping model as advection and/or diffusion take
+control of rim widths at increasing energy, as discussed in
+Section~\ref{sec:energydep},  The best damped fits for these regions all have
+larger $B_0$ values than in the ``weak-field'' damping case.  We refer to these
+fits as giving rise to ``strong-field'' damping, associated with stronger
+magnetic fields, weaker emission intensity behind the thin rim, and clear rims
+with measurable FWHMs at low photon energies (at and below soft X-ray).
 
 % Explanation and caveats
-The distinction between ``weak-field'' and ``strong-field'' damping is not
-necessarily physically meaningful, given the large $\chi^2$ values on our
-model fitting.  Several regions are well-fit by either ``weak-field'' or
-``strong-field'' damping.  However, we believe that ``weak-field'' damping is
-often associated with data that are best described by stronger energy
-dependence, as quantified by $\mE$ values of best loss-limited and damped fits.
-We also note that due to the large divergence in FWHM values at low energies
-(relatively stable for ``strong-field'' fits versus extremely large for
-``weak-field'' fits), observations of synchrotron rims at radio wavelengths
-could better discriminate between these two classes of fits.
-We also note that the observed split in weak/strong-field damping at $B_0 = 40
-\muG$ may not be meaningful, as best fit behavior depends strongly on both
-$a_b$ and $\eta_2$ as well.  Nevertheless, the qualitative behavior of $B_0$ is
-suggestive; it may be that very strong fields at the shock ($\gtrsim 100 \muG$)
-will never give rise to ``weak-field''-like energy dependence.  The parameter
-space of damped fits remains to be explored, however.
+The distinction between weak- and strong-field damping may not
+be physically meaningful given the large $\chi^2$ values on our model fits.
+Several regions are well-fit by ``weak-field'' and ``strong-field'' damping
+alike (e.g., Region 3 in Tables~\ref{tab:fits-all},\ref{tab:fits-all-eta2one}).
+However, ``weak-field'' damping is often associated with data best fit with
+stronger energy dependence, as quantified by $\mE$ values of best loss-limited
+and damped fits.  The qualitative behavior of $B_0$ is suggestive; very strong
+fields at the shock ($\gtrsim 100 \muG$) do not appear compatible with
+``weak-field''-like energy dependence if the magnetic field is damped.
+
+%As ``weak-field'' and ``strong-field'' fits predict strongly differing FWHMs at
+%energies below soft X-rays, observations of synchrotron rims at radio
+%wavelengths may better discriminate between damping scenarios.
 
 % SN 1006
-Our modeling also allows us to better explore the significance of rim width
-measurements in the remnant of SN 1006 by \citetalias{ressler2014}.  We fit our
-damping model to the averaged filament widths of SN 1006 measured by
-\citetalias{ressler2014}, using the same procedure as for Tycho.  We keep
-$\Bmin = 5 \muG$ fixed, although best fit magnetic fields for SN 1006 are
-smaller than those of Tycho due to much wider filaments in SN 1006.
-
+Our modeling also allows us to reassess the significance of rim width-energy
+dependence in the remnant of SN 1006 presented by \citetalias{ressler2014}.  We
+fit averaged filament widths in SN 1006 measured by \citetalias{ressler2014} to
+our damping model using the same procedure as for Tycho.  We fix $\Bmin = 5
+\muG$, although best fit magnetic fields for SN 1006 are smaller than those of
+Tycho due to the much wider filaments of SN 1006.
 Damped fits are comparable to or better than loss-limited fits in 3 of 5
-filaments in SN 1006.  The two filaments with strongest energy dependence ($\mE
-\sim -0.5$) favor a loss-limited model with sub-Bohm diffusion ($\eta_2 \ll
-1$).  The width-energy dependence in SN 1006 ($\mE \sim -0.3$ to $-0.5$) is
-overall slightly stronger than in Tycho, and all of our best damped fits for SN
-1006 correspondingly fall into the ``weak-field'' case.  All best fit $B_0$
-values are less than $40 \muG$ in the damped model, compared to $\abt
-100$--$200 \muG$ in the loss-limited model.
-
-\note[Aaron]{Draft only: appendix includes tables and figures for SN 1006 fits}
-
-% ------------------------------------------------------------------
-% Next steps, observations of profiles (this might fit better above)
-% ------------------------------------------------------------------
-\subsection{Tactics for constraining diffusion}
-
-\subsubsection{Fits to whole damping profiles}
-
-The distinct profile shapes, of both thin rims and plateauing emission just
-downstream of the thin rims, may be more sensitive discriminants of
-loss-limited and damping models.  In particular, our best fits to data with
-moderate $\mE$ generally require small magnetic field $B_0$ and comparatively
-strong emission downstream of the thin rim, just below the rim half-maximum.
-Although the FWHMs accorded with those of the loss-limited, the profiles were
-quite different (Figure~\ref{fig:rims}).
-
-Moreover, we selected only regions on Tycho where a FWHM could be resolved.
-A subset of parameters (small damping lengths, small magnetic fields, and weak
-or even sub-Bohm diffusion) can produce weaker thin rims that do not decrease
-downstream to a half-maximum intensity; several nonthermal filaments around
-Tycho exhibit similar behavior of a weak rim at the shock, followed by strong
-downstream emission.  If profiles can be measured as far back as possible,
-while avoiding thermal emission, we may be able to place stronger constraints
-on allowed values of $B_0$, $\eta_2$, and $a_b$.
-
-\subsubsection{Radio rim measurements}
-
-Radio rims may provide an additional constraint on magnetic field structure.
-The presence of radio rims may reflect 1. age-limited electron propagation (set
-by the timescale needed to accelerate electrons and remnant expansion), 2.
-possible reverse shock accelerated electrons, or 3. magnetic damping.  In our
-steady-state transport model (equation~\eqref{eq:model}), the loss-limited
-model \emph{cannot} produce radio rims.  Thin rims of radio emission in Tycho,
-if not due to instabilities or other projected structure at the shock, can only
-be attributed to magnetic damping.  But, the bulk of radio emission in Tycho
-($r \lesssim 0.9 r_s$) likely cannot be modeled as a steady-state process.
-
-Synchrotron radio emission is emitted by GeV electrons and hence diffusion
-is essentially negligible; observed rims (or lack thereof) are primarily
-controlled by $B_0$ and $a_b$.  It further follows that we needn't worry about
-the precise electron cut-off energy, and we may be able to solve the transport
-equation analytically (or otherwise circumvent the questionable assumption that
-$D(x) B^2(x)$ is constant).  However, we note that our diffusion coefficients
-have assumed that the mean free path is set by gyroradius (linearly so if
-$\mu = 1$), and the Bohm limit $\eta = 1$ of our diffusion coefficients is
-merely an expected lower limit on diffusion.  We may need a more accurate model
-for particle diffusion at radio wavelengths.
-
-Radio emission profiles from Tycho have been modeled by
-\citet{cassam-chenai2007} and \citet{morlino2012}; both studies assumed
-moderate magnetic damping downstream of the shock.  Their discussions of radio
-profiles were undertaken in context of a broader, more concerted hydrodynamic
-modeling effort (which would be necessary to consider the internal radio
-emission, rather than just the shock front emission).  In future work we will
-consider a similar analysis as carried out in this paper, using radio rims to
-help constrain X-ray rim parameters.
-
-\subsubsection{Diffusion from synchrotron roll-off}
-
-A major independent observable is the synchrotron roll-off frequency.  If
-Bohm-like ($\mu = 1$) diffusion holds, the synchrotron roll-off is independent
-of magnetic field strength and thus grants another constraint on diffusion
-coefficient, within the assumption of DSA driven electron losses.  In this
-manner, \citet{parizot2006} estimated diffusion coefficients $\eta = 10, 5$ for
-compression ratios $4, 10$ in Tycho.
-
-We can measure the roll-off frequency in all regions, fix the diffusion
-coefficient at a given value of $\mu$, and obtain single parameter fits for
-$B_0$ (or two parameter fits for $B_0$ and $a_b$) at each value of $\mu$.
-Conceptually, this is comparable to our fits with $\eta_2 = 1$ fixed
-(Table~\ref{tab:fits-all-eta2one}) and should not greatly affect our
-conclusions.  However, if the diffusion coefficient from the roll-off frequency
-is indeed well-constrained, then parameter estimates based on deduced diffusion
-coefficients may be more reliable.
+filaments in SN 1006.  Two filaments with strong energy dependence ($\mE \sim
+-0.5$) favor a loss-limited model with sub-Bohm diffusion ($\eta_2 \ll 1$).
+The width-energy dependence in SN 1006 ($\mE \sim -0.3$ to $-0.5$) is overall
+slightly stronger than in Tycho, and the best damped fits for SN 1006 all fall
+into the ``weak-field'' case.  The best fit $B_0$ values are less than $40
+\muG$ in the damped model, compared to $\abt 100$--$200 \muG$ in the
+loss-limited model.
+
+% -------------------------------
+% srcutlog and spectral variation
+% -------------------------------
+\subsection{Spectral constraints on model fits}
+
+\subsubsection{Synchrotron cut-off measurements}
+
+Our model fits have not incorporated the synchrotron cut-off energy, which
+permits an estimate of diffusion coefficient $\eta_2$ for a given value of
+$\mu$ (equation~\eqref{eq:cutoff}) that is independent of magnetic field
+$B_0$.  For example, \citet{parizot2006} used measurements of synchrotron
+cut-off (and hence electron energy cut-off) to estimate diffusion coefficients
+$\eta = 10, 5$ for compression ratios $4, 10$ in Tycho.
+
+To measure synchrotron cut-offs in Tycho, we fitted rim spectra
+(Section~\ref{sec:spec}) to the XSPEC model \texttt{srcut}, modified to fit in
+log-frequency units.  Column density $N_{\mt{H}}$ and cut-off frequency
+$nu_{\mt{cut}}$ are free parameters; we fixed the radio spectral index $\alpha
+= 0.58$ as done in our profile modeling \citep{sun2011}.
+Table~\ref{tab:fits-srcutlog} presents the spectrum fit parameters and best
+loss-limited fits with $\nu_{\mt{cut}}$-derived $\eta_2$ fixed.
+Variation in $\mu$ has a small effect on best fits; Regions 1 and 16 have best
+fit values of $B_0$ increasing over $252$--$266 \muG$ and $660$--$700 \muG$
+respectively as $\mu$ ranges between $0$--$2$.
+
+The results are comparable to fits with $\eta_2 = 1$ fixed
+(Table~\ref{tab:fits-all-eta2one}).  The synchrotron cut-off frequency is
+typically $0.3 \unit{keV}$, though we note that Regions 11, 12 have unusually
+high cut-off frequencies.  Fitted $B_0$ values span $250$--$700 \muG$.
+We cannot deduce any particular insight from requiring that $\eta_2$ reflects
+the measured value of $\nu_{\mt{cut}}$.  But, if the diffusion coefficients are
+more reliable or physically reasonable, the derived estimates of $B_0$ may be
+more credible.
+
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Synchrotron roll-off, $\eta_2$, and fits for $\mu = 1$
+        \label{tab:fits-srcutlog}}
+    \begin{tabular}{@{}l ccc ccr@{}}
+    \toprule
+    {} & \multicolumn{3}{c}{\texttt{srcut} fit parameters}
+       & \multicolumn{3}{c}{Best fits for $\mu = 1$}\\
+    \cmidrule(lr){2-4} \cmidrule(l){5-7}
+    Region & $N_{\mt{H}}$ & $\nu_{\mt{cut}}$ & $\chi^2_{\mathrm{red}}$ (dof)
+           & $\eta_2$ & $B_0$ & $\chi^2$ \\
+    {} & ($10^{22} \mt{cm}^{-2}$) & (keV/$h$) & {}
+       & (-) & ($\mu$G) & {} \\
+    \midrule
+     1 & 0.62 & 0.30 & 1.17 (284) & 12.0 & 256 & 29.1 \\
+     2 & 0.60 & 0.30 & 1.08 (202) & 11.8 & 443 & 99.4 \\
+     3 & 0.68 & 0.33 & 1.14 (167) & 10.6 & 599 & 31.8 \\
+    \cmidrule{1-7}
+     4 & 0.61 & 0.29 & 1.15 (278) & 12.0 & 402 & 36.2 \\
+     5 & 0.64 & 0.27 & 1.11 (255) & 12.9 & 419 & 32.5 \\
+     6 & 0.64 & 0.29 & 0.93 (231) & 11.9 & 568 & 89.7 \\
+     7 & 0.71 & 0.23 & 1.14 (224) & 15.3 & 618 & 11.7 \\
+     8 & 0.66 & 0.41 & 0.96 (198) & 8.38 & 511 & 15.1 \\
+     9 & 0.73 & 0.30 & 0.88 (175) & 11.2 & 573 & 23.4 \\
+    10 & 0.68 & 0.36 & 0.96 (164) & 9.45 & 631 & 1.42 \\
+    \cmidrule{1-7}
+    11 & 0.61 & 0.55 & 1.07 (153) & 6.08 & 452 & 18.1 \\
+    12 & 0.57 & 0.88 & 0.90 (172) & 3.74 & 375 & 12.6 \\
+    13 & 0.59 & 0.38 & 1.09 (235) & 8.43 & 529 & 13.8 \\
+    \cmidrule{1-7}
+    14 & 0.54 & 0.23 & 0.95 (167) & 11.9 & 547 & 28.6 \\
+    15 & 0.57 & 0.29 & 1.03 (183) & 9.54 & 598 & 23.1 \\
+    16 & 0.58 & 0.32 & 1.12 (182) & 8.44 & 670 & 6.26 \\
+    17 & 0.59 & 0.30 & 0.94 (187) & 8.97 & 637 & 32.6 \\
+    \cmidrule{1-7}
+    18 & 0.55 & 0.19 & 1.13 (220) & 14.6 & 432 & 72.4 \\
+    19 & 0.57 & 0.34 & 0.99 (157) & 8.86 & 542 & 12.8 \\
+    20 & 0.55 & 0.31 & 1.07 (192) & 9.60 & 631 & 96.0 \\
+    \bottomrule
+    \end{tabular}
+    \tablecomments{\texttt{srcut} fits performed in log-frequency coordinates;
+    here $h$ is Planck's constant.  $\eta_2$ values are computed from
+    equation~\eqref{eq:cutoff} and held fixed in model fits.}
+\end{table}
+
+\subsubsection{Spectral softening}
+% Wording of spectral index changes/variation is inconsistent and unwieldy
+
+We also consider whether spectral variation may permit discrimination between
+loss-limited and damping models, as proposed by \citet{rettig2012}.  Electron
+energy losses will result in spectral softening downstream of the shock and
+thin rim, previously documented in Tycho by, e.g., \citet{cassam-chenai2007},
+but the precise spectral evolution depends on the assumed post-shock magnetic
+field structure (whether loss-limited or damped).  To quantify spectral
+softening, we consider the change in spectral index ($\Delta \Gamma$) between
+spectra taken at the thin rim and just downstream of the thin rim.
+
+% Measured spectra
+We fitted rim and downstream spectra (Section~\ref{sec:spec}) in each region
+between $2$--$7 \unit{keV}$ to an absorbed power law with column density
+$N_{\mt{H}}$ fixed at $0.7 \times 10^{22} \unit{cm^{-2}}$.  To account for
+thermal emission in downstream spectra, we excised $2.3$--$2.6$ and
+$3.0$--$3.2 \unit{keV}$ photons to remove \ion{S}{15} and \ion{Ar}{17}
+He$\alpha$ lines at $2.45$ and $3.11 \unit{keV}$ respectively.  Mean rim and
+downstream spectral indices were $2.94$ and $3.23$ respectively; the mean
+index change $\Delta \Gamma$ was $0.3$ (stdev: $0.2$).  Different approaches to
+removing thermal emission in downstream spectra (adding Gaussian component to
+fit \ion{S}{15} line; excising all $2$--$2.6 \unit{keV}$ photons) yielded a
+smaller spectral index $3.17$, with mean $\Delta \Gamma \abt 0.24$ (stdev:
+$0.22$ and $0.18$ respectively).
+
+% Model spectra
+% Needs rewrite
+We also computed model photon spectral indices as a function of energy for our
+best fit loss-limited and damping parameters with $\eta_2 = 1$ fixed
+(Table~\ref{tab:fits-all-eta2one}); specifically, we computed the $1
+\unit{keV}$ FWHM and radially integrated profiles from the forward shock to one
+FWHM behind the shock to obtain rim spectra, and integrate from one to two
+FWHMs behind the shock to obtain model downstream spectra.  The integration
+domains were chosen to roughly match the extraction regions of actual rim
+spectra (Section~\ref{sec:spec}).  We fitted the model spectra to a power law
+between $2$--$7 \unit{keV}$ to compare with our measurements.
+Figure~\ref{fig:specvar} plots model spectra with power law fits and spectral
+indices for Regions 1 and 16 as a function of photon energy.
+
+\begin{figure}[h]
+    \centering
+    \plotone{figures/plt-specvar-1.pdf} \\
+    \plotone{figures/plt-specvar-16.pdf}
+    \caption{Model spectra and spectral indices as a function of energy for
+    best damping fits with $\eta_2 = 1$, Regions 1 (top) and 16 (bottom).
+    Model spectra (left) plotted with best power law fits between 2--7 keV,
+    shaded on plot.  Spectral indices (right) demonstrate softer downstream
+    spectra and expected roll-off in the power-law synchrotron spectrum.
+    The power law fits yield rim/downstream indices of 2.37/2.44 for Region 1,
+    and 2.56/2.61 for Region 16; spectral index changes are 0.07 and 0.05, much
+    smaller than $\Delta\Gamma \sim 0.3$ from measured spectra.
+    \label{fig:specvar}}
+\end{figure}
+
+% Result
+Model parameters derived from FWHM width-energy fits are unable to reproduce
+the observed filament spectrum evolution.  The mean change $\Delta\Gamma$ was
+$0.05$ (stdev: $0.0005$) for loss-limited model profiles and $0.05$ (stdev:
+$0.02$) for damped model profiles.  For comparison, damped fits with varying
+$\eta_2$ (Table~\ref{tab:fits-all}) yield a mean $\Delta\Gamma$ of $0.07$
+(stdev: $0.03$).  Modeled spectral variation in all cases is inconsistent with
+the observed $\Delta\Gamma \sim 0.2$--$0.3$.
+Our damped model results disagree with those of \citet[][Fig.~4]{rettig2012},
+who predict spectral index changes of up to $\sim 0.15$ for strong damping.  To
+check our results, we followed the procedure of \citet{rettig2012} and
+attempted to reproduce their tables and figures.  We found reasonable agreement
+for loss-limited model spectra but could not reproduce their damped model
+spectra for the given parameters.  A weaker shock magnetic field (e.g., $B_0 =
+35 \muG$ vs. $85 \muG$, with downstream field $B_{\mt{min}} = 10 \muG$) gave
+spectral index variation closer to that reported by \citet{rettig2012}.
+
+% Interpretation
+The disagreement between modeled and observed spectral evolution behind the
+shock suggests that either model parameters ($B_0$, $\eta_2$, $a_b$) or our
+model assumptions are incorrect, in the damped case.
+Our results should be representative of the parameter space of damped model
+filaments.  Damped magnetic field fit values span $24$--$400 \muG$ with varied
+$a_b$ values; varying $\eta_2$ increased the mean $\Delta\Gamma$ slightly, but
+not enough to be consistent with our measurements.
+
+Small shock fields ($B_0 < 40 \muG$) are associated with stronger spectral
+variation ($\Delta\Gamma \sim 0.06$--$0.09$); if our model is reasonable,
+spectral variation may favor weak shock fields with little to no amplification.
+But, model index variations $<0.1$ still underpredict the observed
+$\Delta\Gamma \sim 0.3$.  If loss-limited model spectra are correct, the
+observation of weak $2$--$7 \unit{keV}$ spectral evolution between rim and
+downstream extraction regions would further favor magnetic field damping.
+
+% ----------------------------------------
+% Constraining rims via radio measurements
+% ----------------------------------------
+\subsection{Radio rims constrain damping scenarios}
+
+The presence of thin radio rims in Tycho may help constrain magnetic field
+damping.  Radio emission in Tycho arises from the same population of
+shock-accelerated electrons generating nonthermal X-ray rims.  But, $\abt$GeV
+electrons have cooling times of order $10^5$--$10^7 \unit{yr}$ in $10$--$100
+\muG$ magnetic fields.  Despite the extended population of radio synchrotron
+electrons, radio rims and decreases in emission intensity immediately behind
+the shock may be explained by magnetic damping.  If remnant-wide diffuse
+emission near the forward shock increases monotonically towards the center of
+the remnant, only magnetic field damping can cause emission to decrease.  A
+loss-limited field predicts monotonically increasing emission downstream of the
+forward shock in our steady-state transport model.
+
+We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
+with the VLA in A configuration in March 1994 (PI: D. Moffett); see
+\citet{reynoso1997} for a detailed presentation.  The half-power beam width of
+$\abt 1.5\arcsec$ just resolves thin radio rims and structure near the forward
+shock; the image is sampled at $0.5\arcsec$.  We shift radio profiles forward
+by $9\arcsec$ to correct for proper motion, assuming an $0.3\arcsec/\mt{yr}$
+expansion rate \citep{katsuda2010-tycho}.  Figure~\ref{fig:radio-snr} shows the
+extraction regions overlaying the radio image and the previous X-ray profile
+regions of Figure~\ref{fig:snr}.
+
+\begin{figure}
+    \centering
+    \plotone{figures/radio-snr.png}  % TODO a temporary image
+    \caption{Radio image of Tycho's SNR at $1.375 \unit{GHz}$ with linear
+    scaling.  Extraction regions (green) for joint radio and X-ray profile
+    analysis overlay region selections for X-ray rim width analysis
+    (Figure~\ref{fig:snr}). \label{fig:radio-snr}}
+\end{figure}
+
+\subsubsection{Combined radio and X-ray profile fitting}
+
+%% TODO Working at around here...  now pending some code work.
+
+Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
+($4$--$7\unit{keV}$) profiles from the plotted regions (Figure~\ref{fig:snr}),
+shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
+morphology, including thin rims with a trough and either increasing and
+decreasing emission towards the remnant interior.
+
+\begin{figure}
+    \centering
+    \plotone{figures/radio-prfs-subplot.pdf}
+    \caption{Radio (red) and nonthermal X-ray (blue) intensity profiles from
+    extraction regions shown in Figure~\ref{fig:radio-snr}.  Radio profiles are
+    shifted forward by $9\arcsec$ to correct for proper motion.  Both X-ray and
+    radio profiles are translated to place the $4$--$7 \unit{keV}$ rim $\abt
+    2\arcsec$ behind the forward shock radius $r_s = 240\arcsec$.  We emphasize
+    that the intensities and radial coordinate translations are chosen strictly
+    to aid visual comparison and are otherwise arbitrary.
+    \label{fig:radio-prfs}}
+\end{figure}
+
+Our model profiles are fully characterized by $B_0$, $a_b$, and $B_{\mt{min}}$,
+with $B_{\mt{min}} = 5 \muG$ fixed as before.  We neglect diffusion in modeling
+radio emission as particle energies are 3 orders of magnitude lower than in
+X-ray.  This also circumvents the unphysical assumption that $D(x) B^2(x)$ is
+constant, which was accepted in order to obtain Green's function solutions for
+our transport model, equation~\eqref{eq:model}.  But, as we previously assumed
+Bohm-like diffusion, another model for particle diffusion may be necessary at
+radio wavelengths.
+
+Radio emission profiles in Tycho have been modeled by \citet{cassam-chenai2007}
+and \citet{morlino2012} as part of broader hydrodynamic modeling studies,
+which permits modeling of emission throughout the remnant rather than just
+behind the shock.  Although a full time-dependent model may better capture all
+radio emission and nonthermal X-ray emission simultaneously, our simplified
+model should capture the essential physics for a very young remnant such as
+Tycho, for which the forward shock should be adiabatic.
+
+We extracted hard X-ray pro
+
+The distinct profile shapes of radio thin rims and rising or falling emission
+behind the thin rims, if rims are present, may be more sensitive discriminants
+of loss-limited and damping models.
+
+In particular, our best fits to data with moderate $\mE$ generally require
+small magnetic field $B_0$ and comparatively strong emission downstream of the
+thin rim, just below the rim half-maximum.  Although the FWHMs accorded with
+those of the loss-limited, the profiles were quite different
+(Figure~\ref{fig:rims}).
+
+\subsubsection{Radio rim shape analysis}
+
+Although radio and X-ray rim profiles are difficult to jointly model, we can
+use observed decreases in emission just behind the shock to constrain allowable
+model parameters.  Where a decrease in radio emission occurs behind the peak
+emission, the steepest decrease in emission allows us to bound the minimum
+magnetic field and the maximum allowable damping length -- i.e., we require a
+fast magnetic field drop-off with distance (for the assumed $B_{\mt{min}} = 5
+\muG$).
+
+Conversely, a continuous increase in emission requires a minimum damping
+length, as too small a damping length and moderate field strength will give
+rise to a radio rim.  However, diffuse remnant-wide radio emission may obscure
+a radio rim associated with the forward shock.  Thus, although a continuous
+rise in emission is consistent with weak damping (and loss-limited X-ray rims),
+we cannot rule out the possibility of magnetic damping.
+
+Table~\ref{tab:???} lists intensity drop-offs for radio and X-ray profiles in
+each region at various distances behind the peak (rim) emission, favoring the
+shortest possible distance to obtain a steep drop-off and better constrain
+$B_0$ and $a_b$.  Assuming $B_0 < 500 \muG$ in a damped model, we can also
+constrain the minimum
+
+Generate a slew of profile shapes, and ask that emission over XXX distance
+behind the shock NOT rise above the peak/rim distance.  This rules out the
+smallest damping lengths and fields (i.e., no trough at XXX distance...)
+
+Finally, if a trough is present in the radio rim, we may further
+
+In Figure~\ref{fig:radio-bound} we illustrate schematically
+
+\begin{figure}
+    \centering
+    \plotone{figures/radio-min-bound-6arcsec.pdf}
+    \caption{Maximum intensity drop-off within 6 arcsec of forward shock for
+        modeled 1.375 GHz radio profile.
+    \label{fig:radio-bound}}
+\end{figure}
 
@@
 $\eta_2$ can cause rim widths to narrow).
+
+However, the radio modeling assumes \emph{no diffusion} and should not be
+impacted by this potentially incorrect assumption.
 
@@
 \citep[e.g.,][]{parizot2006, rettig2012} and radio and gamma ray measurements
-\citep{acciari2011, morlino2012}.  We find that magnetic damping is equally
-capable of describing our observed data.  At small energy dependence the two
-models are indistinguishable and magnetic damping fits still favor moderately
-amplified magnetic fields.  At moderate energy dependence ($\mE \sim -0.3$),
-the damping model favors weaker magnetic fields, but modeled FWHMs may not
-be truly representative of thin rim widths.
+\citep{acciari2011, morlino2012}.  Loss-limited and magnetic damping models are
+equally capable of describing our observed data.  At small energy dependence
+the two models are indistinguishable and magnetic damping fits still favor
+moderately amplified magnetic fields.  At moderate energy dependence ($\mE \sim
+-0.3$), the damping model favors weaker magnetic fields, but modeled FWHMs may
+not be truly representative of thin rim widths and profiles.
 
@@
 the \Chandra Data Archive.
-This research has made extensive use of NASA's Astrophysics Data System.
+This research made extensive use of NASA's Astrophysics Data System.
+This research made use of APLpy, an open-source plotting package for Python
+hosted at \href{http://aplpy.github.com}{http://aplpy.github.com}.
 
@@
 \renewcommand{\thefigure}{A\arabic{figure}}
-
-% ==============================
-% \mE values for best-fit curves
-% ==============================
-%\section{Best fit width-energy curve $m_\mt{E}$ values}
-%
-%\begin{table*}[ht]
-%    \footnotesize
-%    \centering
-%    \caption{$m_\mt{E}$ computed from best loss-limited fit FWHMs}
-%    \input{suppl-fits-mE.tex}
-%\end{table*}
 
@@
 
-% =====================================================
-% Synchrotron roll-off energy and diffusion coefficient
-% =====================================================
+% ====================================================
+% Synchrotron cut-off energy and diffusion coefficient
+% ====================================================
 \clearpage
-\section{Derivation for synchrotron roll-off and diffusion}
-
-% This is NOT optimized for 2-column layout
+\section{Derivation for synchrotron cut-off and diffusion}
+
+% NOT optimized for 2-column layout
 
 Assume that a DSA model explains the observed e-/synchrotron spectra
-cut-off/roll-off.  We estimate e- cut-off energy by equating
+cut-off.  We estimate e- cut-off energy by equating
 $\tau_{\mt{accel}} = \tau_{\mt{synch}}$.  This gives (Parizot et al., 2006):
@@
 (\emph{I don't know if this equality was designed to exactly obtain the electron
-cutoff energy, or is just a rough/scaling relation -- pull up Drury (1983) to
+cut-off energy, or is just a rough/scaling relation -- pull up Drury (1983) to
 check this})
@@
 \end{equation}
-Now, we can convert this cut-off e- energy to a roll-off synchrotron energy by
+Now, we can convert this cut-off e- energy to a cut-off synchrotron energy by
 invoking the delta function assumption $\nu_{\mt{cut}} = c_m \Ecut^2 B$ with
-$c_m = 1.822 \times 10^{18}$.
+$c_m = 1.82 \times 10^{18}$.
 (\emph{Again, I don't know if this is an equality or just a scaling.  We'd need
@@
         \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( 100 \muG \right)
         \left( \frac{B}{100\muG} \right)^{-\frac{1-\mu}{1+\mu}}
@@
         \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( 100 \muG \right)
         \left( E_2 \right)^{-\frac{2(1-\mu)}{1+\mu}}
@@
         \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
+        \left( 100 \muG \right)
         \left( \frac{0.2657 \unit{erg^2\;G}}{B} \right)^{-\frac{1-\mu}{1+\mu}}
@@
 \]
-And, the magnetic field terms cancel!  Hey presto.
-Our final usable result is:
+And, the magnetic field terms cancel!  Our final usable result is:
 \begin{equation}
@@
         \left( 13.3 \unit{erg} \right)^{\frac{4}{1+\mu}}
-        \left( 0.2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
-        \left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
+        \left( 2657 \unit{erg^2\;G} \right)^{-\frac{1-\mu}{1+\mu}}
         \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
@@
 \end{equation}
+which depends only upon $v_s$ and $\eta_2$.
 

### 2014-12-03 VLA/ds9-tycho-radio.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+echo "Region file to load?"
+read -e reg
+
+ds9 -view layout vertical \
+    -colorbar orientation vertical \
+    -rgb \
+    -red TYCHO_IF1.FITS \
+        -scale limits 0.00015 0.0035 \
+        -cmap value 2.25 0.55 \
+    -green ../data-tycho/1-1.7kev_mosaic.fits \
+        -scale limits 7e-9 4e-7 \
+        -cmap value 3.59 0.12 \
+    -blue ../data-tycho/4-7kev_mosaic.fits \
+        -scale limits 7e-9 4e-7 \
+        -cmap value 3.59 0.12 \
+    -rgb lock scale yes \
+    -asinh \
+    -regions $reg

### 2014-12-03 manuscript/paper-tycho.tex
Merge VLA into data-tycho; new VLA/xray regions

@@
 with the VLA in A configuration in March 1994 (PI: D. Moffett); see
-\citet{reynoso1997} for a detailed presentation.  The half-power beam width of
-$\abt 1.5\arcsec$ just resolves thin radio rims and structure near the forward
-shock; the image is sampled at $0.5\arcsec$.  We shift radio profiles forward
-by $9\arcsec$ to correct for proper motion, assuming an $0.3\arcsec/\mt{yr}$
-expansion rate \citep{katsuda2010-tycho}.  Figure~\ref{fig:radio-snr} shows the
-extraction regions overlaying the radio image and the previous X-ray profile
-regions of Figure~\ref{fig:snr}.
+\citet{reynoso1997} for a detailed presentation.
+\emph{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
+The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
+and structure near the forward shock; the image is sampled at $0.5\arcsec$.  We
+shift radio profiles forward by $9\arcsec$ to correct for proper motion,
+assuming an $0.3\arcsec/\mt{yr}$ expansion rate \citep{katsuda2010-tycho}.
+Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
+image and the previous X-ray profile regions of Figure~\ref{fig:snr}.
 

### 2014-12-03 data-tycho/ds9-tycho-rgb-radio.sh

@@ -8,12 +8,12 @@ ds9 -view layout vertical \
     -red TYCHO_IF1.FITS \
         -scale limits 0.00015 0.0035 \
         -cmap value 2.25 0.55 \
-    -green ../data-tycho/1-1.7kev_mosaic.fits \
+    -green 1-1.7kev_mosaic.fits \
+        -scale limits 1e-8 3.5e-7 \
+        -cmap value 1.83 0.29 \
+    -blue 4-7kev_mosaic.fits \
         -scale limits 7e-9 4e-7 \
-        -cmap value 3.59 0.12 \
-    -blue ../data-tycho/4-7kev_mosaic.fits \
-        -scale limits 7e-9 4e-7 \
-        -cmap value 3.59 0.12 \
+        -cmap value 7.78 0.086 \
     -rgb lock scale yes \
     -asinh \
     -regions $reg

### 2014-12-05 manuscript/paper-tycho.tex
Better vla/xray regions, manual prf fits, pipeline
Flesh out pipeline to process/analyze radio and X-ray profiles jointly
Set up basic shape analysis and manual (eyeballing) profile fits
Settle on final-ish set of VLA/xray regions, pass through pipeline
Tycho proper motions from Katsuda
Generalize azimuth angle interpolation script

@@
 
+% General todo -- note that we ignore actual profile shape in xray FWHMs
+% and, effects of multiple overlapping filaments, etc...
+
 Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
@@
 shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
-morphology, including thin rims with a trough and either increasing and
+morphology, including thin rims with a trough and either increasing or
 decreasing emission towards the remnant interior.

### 2014-12-05 code/regions/azangle_interp.py

@@ -1,0 +1,97 @@
+"""
+
+Interpolate either shock velocities or proper motions, given a list of azimuth
+angles (generally, any azimuth-angle dependent parameter)
+
+Shock velocities: intended for data of Williams+(2013), which in turn averages
+data from Katsuda+(2010) and Reynoso+(1997) (X-ray, radio proper motion
+respectively)
+
+Proper motions: intended for data of Katsuda et al. (2010), using 2000-2007
+baseline wherever possible (2003-2007 baseline in SSW of remnant, that was
+obscured in 2000 observation)
+
+Aaron Tran
+Fall 2014
+"""
+
+from __future__ import division
+
+import argparse
+from datetime import datetime
+import numpy as np
+import os
+
+def main():
+    parser = argparse.ArgumentParser(description=
+             ('Linearly interpolate shock velocities or proper motions '
+              'from azimuth angles.  Assumes one or the other.'
+              'Outputs plaintext file w/ list of interpolated values'))
+
+    parser.add_argument('azfile', help='Plaintext file of az angles')
+    parser.add_argument('tabfile', help=('Plaintext table of az angles & qty '
+                                         'to interpolate in 1st/2nd columns'))
+    parser.add_argument('fout', help='Output plaintext filename')
+    parser.add_argument('-b', '--briantab', action='store_true',
+                        help='Flag if using Brian\'s velocs')
+    parser.add_argument('-s', '--scale', default=3./2.3, type=float,
+                        help=('Scale factor if using Brian\'s velocs; default '
+                              'value is (3 kpc / 2.3 kpc) = 1.304348'))
+    parser.add_argument('-n', '--nearest', action='store_true',
+                        help='Use nearest nhbr instead of linear interp')
+
+    args = parser.parse_args()
+    f_az, f_tab, f_out = args.azfile, args.tabfile, args.fout
+    briantab, scale = args.briantab, args.scale
+    nearest = args.nearest
+
+    az_angles = np.loadtxt(f_az)
+    tab = np.loadtxt(f_tab)
+    az_tab, par_tab = tab[:,0], tab[:,1]
+    if briantab:
+        par_tab *= 1e5  # Convert km/s to cm/s
+
+    # Pad table on each end to catch edge cases while interpolating
+    az_tab = np.insert(az_tab, [0, len(az_tab)],
[…]

### 2014-12-05 data-tycho/proper-motion/plot_motion.py

@@ -1,0 +1,44 @@
+"""
+One-off script to plot proper motions from Katsuda et al. (2010)
+Aaron Tran
+"""
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+a = np.loadtxt('tycho-motion.txt')
+
+def bin_f(vec, a, b, f=np.mean):
+    """For vector with columns of x, y coords, get mean y for a<x<b"""
+    msk = np.logical_and(vec[:,0] >= a, vec[:,0] < b)
+    if any(msk):
+        return f(vec[msk,1])
+    return np.nan
+
+bin_left = np.arange(0, 360, 60)
+bin_right = np.arange(60, 420, 60)
+bin_ctr = np.arange(30, 360, 60)
+a_mean = map(lambda x1,x2: bin_f(a,x1,x2,f=np.mean), bin_left, bin_right)
+a_std = map(lambda x1,x2: bin_f(a,x1,x2,f=np.std), bin_left, bin_right)
+
+plt.errorbar(a[:,0], a[:,1], yerr=a[:,2], fmt='ob')
+plt.errorbar(bin_ctr, a_mean, xerr=30*np.ones(len(a_mean)),
+             yerr=a_std, fmt='or')
+
+plt.xlabel('Azimuth angle east of north (deg.)')
+plt.ylabel('FS proper motion (arcsec/yr)')
+plt.tight_layout()
+plt.xlim((0,360))
+plt.savefig('tycho-motions.pdf')
+plt.show()
+
+print 'Data statistics'
+print 'Mean: {}, median: {}'.format(np.mean(a[:,1]), np.median(a[:,1]))
+print 'Min: {}, max: {}'.format(min(a[:,1]), max(a[:,1]))
+
+hdr = ('Binned (60 deg. sectors) Tycho proper motions; Katsuda et al. (2010)\n'
+       'Column 1: bin centers (az angle in deg., east of north)\n'
+       'Column 2: proper motion (arcsec/yr)\n'
+       'Column 3: stdev of averaged proper motion data (arcsec/yr)')
+np.savetxt('tycho-motion-bin.txt', np.array([list(bin_ctr), a_mean, a_std]).T,
+           fmt='%.4f', header=hdr)

### 2014-12-10 manuscript/paper-tycho.tex
Eyeball fits to VLA regions; new figs, paper
Manual profile fits for all VLA/X-ray regions, in plaintext and ipynb
Clean ipynb for radio prfs, generate ms figs
Paper draft updated and sent out

--- 2014-12-03 manuscript/paper-tycho.tex
@@
-%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
+\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
 %\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
 %\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
-\documentclass[iop, apj, numberedappendix]{emulateapj}
+%\documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 \newtoggle{manuscript}
-%\toggletrue{manuscript}
-\togglefalse{manuscript}
+\toggletrue{manuscript}
+%\togglefalse{manuscript}
 
@@
 
+% TODO define loss-limited properly...
+% ~210 words -- a little too long
 \begin{abstract}
@@
 magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
-coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
+coefficients (typically $\abt 1$--$10$).
+Corresponding thin rim radio rims require magnetic damping, however.  We
+jointly model radio and X-ray profiles and estimate magnetic damping length of
+order $1$--$5$\% of remnant radius, with magnetic field strengths $\abt
+50$--$400 \muG$ assuming Bohm diffusion.  Diffusion coefficients, magnetic
 field strengths, and magnetic damping lengthscales are somewhat degenerate in
-setting observed rim widths and drop-offs.  Although we cannot discriminate
-from width measurements alone, a combined study of X-ray and radio profiles may
-break the observed degeneracies to confirm or rule out turbulent magnetic field
-damping downstream of supernova remnant shocks.
+setting observed rim widths and drop-offs.
+Although the energy dependence of synchrotron rims cannot discriminate magnetic
+field structure, joint radio and X-ray modeling favors magnetic damping in
+Tycho's SNR.
 \end{abstract}
@@
     X-rays: ISM}
-
-% TODO GENERAL WARNING -- DATA MAY NOT ALL BE FULLY CONSISTENT AT THIS TIME.
-% (spectra/profiles/fwhms/fits).
 
@@
 \section{Nonthermal rim modeling}\label{sec:models}
-
-% Could just discuss one model...
-%We consider two particle transport models that we fit to measurements of
-%Tycho's thin rim widths.  We measure the rim full widths at half maximum
-%(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
-%model predictions of rim FWHMs at multiple photon energies, for various input
-%parameters.  The models accept four free parameters: magnetic field strength
-%$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
-%exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
-%length).
-
-% Twiddle-ables in our model (the most useful part, since just modeling
-% alone don't do much)
-%Our model fitting explores the space of varying diffusion (a bulk
-%representative of the underlying MHD turbulence and what have you)
-%and considers the two scenarios of constant magnetic field (resulting in
-%so-called loss-limited rims) and a damped field that falls off exponentially
-%behind the forward shock, as suggested by \citet{pohl2005}.
-% this might go at the front before we launch into model details.
 
@@
 
-%Different types of MHD turbulence may give rise to a non-linear energy
-%scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
-%Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
-%quasi-linear approximation for particle motion,
-%\note[Aaron]{I don't really know what this means}
-%predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
-%Particle gyroradii larger than field coherence length may also lead to
-%$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
-%and cites nothing.  I have no idea what this means.}
-
 % Define our diffusion coefficient, introduce fiducial energy
@@
     \iftoggle{manuscript}{
-        %\includegraphics[width=0.5\textwidth]{figures/f0-snr-inv.png}
+        \includegraphics[width=0.2\textwidth]{figures/snr.pdf}
     }{
-        %\plotone{figures/f0-snr-inv.png}
         \plotone{figures/snr.pdf}
@@
 each region and each energy band after subtracting a constant background term
-$\min(C_u, C_d)$.  We could not resolve a FWHM in 4 of 20 regions at 0.7--1 keV
+$\min(C_u, C_d)$.  We could not resolve a FWHM in 8 of 20 regions at 0.7--1 keV
 (Table~\ref{tab:fwhms}); in these regions, either the downstream FWHM bound
@@
 higher energy bands (1--7 keV).
-% NOTE review the FWHM rejection criterion, on the final set of regions
-% We will be blacklisting by hand, and we have to explain how we chose the
-% blacklisted ones.
 
@@
 % on the loss-limited model, and those fits are now out of date too...
-Errors on best fit parameters were computed by varying each fit parameter and
-obtaining a new best fit model, with one less degree of freedom, to find the
-parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.
+%Errors on best fit parameters were computed by varying each fit parameter and
+%obtaining a new best fit model, with one less degree of freedom, to find the
+%parameter limit such that $\Delta \chi^2 = 1$ for a roughly 1-$\sigma$ error.
 
@@
 % ----------------------------------------
-\subsection{Radio rims constrain damping scenarios}
-
-The presence of thin radio rims in Tycho may help constrain magnetic field
-damping.  Radio emission in Tycho arises from the same population of
-shock-accelerated electrons generating nonthermal X-ray rims.  But, $\abt$GeV
-electrons have cooling times of order $10^5$--$10^7 \unit{yr}$ in $10$--$100
-\muG$ magnetic fields.  Despite the extended population of radio synchrotron
-electrons, radio rims and decreases in emission intensity immediately behind
-the shock may be explained by magnetic damping.  If remnant-wide diffuse
-emission near the forward shock increases monotonically towards the center of
-the remnant, only magnetic field damping can cause emission to decrease.  A
-loss-limited field predicts monotonically increasing emission downstream of the
-forward shock in our steady-state transport model.
-
+\subsection{Radio rims require magnetic damping}
+
+% Introduction
+Thin radio rims spatially coincident with X-ray synchrotron rims may help
+constrain magnetic field damping.  Radio emission in Tycho arises from the same
+population of shock-accelerated electrons generating nonthermal X-ray rims.
+But, $\abt$GeV electrons have cooling times of order $10^5$--$10^7 \unit{yr}$
+in $10$--$100 \muG$ magnetic fields; synchrotron emission in the remnant
+interior may reflect the spatial structure of long-lived electrons interacting
+with a turbulent field rather than the advection of recently shock-accelerated
+electrons.
+Despite the extended population of radio synchrotron electrons, radio rims and
+decreases in emission intensity immediately behind the shock may be explained
+by magnetic damping.  If remnant-wide diffuse emission near the forward shock
+increases monotonically towards the center of the remnant, only magnetic field
+damping can cause emission to decrease.  A loss-limited field predicts
+monotonically increasing emission downstream of the forward shock in our
+steady-state transport model.
+% TODO Redundant
+
+% Procedure
 We extract radio profiles from a $1.375 \unit{GHz}$ image of Tycho taken
@@
 \citet{reynoso1997} for a detailed presentation.
-\emph{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
+\note[Aaron]{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
 The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
-and structure near the forward shock; the image is sampled at $0.5\arcsec$.  We
-shift radio profiles forward by $9\arcsec$ to correct for proper motion,
-assuming an $0.3\arcsec/\mt{yr}$ expansion rate \citep{katsuda2010-tycho}.
+and structure near the forward shock; the image is sampled at $0.5\arcsec$.
+%We shift radio profiles forward following X-ray proper motion measurements by
+%\citet{katsuda2010-tycho} over a 7 year baseline; the average shift is
+%$\abt4.5\arcsec$.
 Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
@@
 
-\subsubsection{Combined radio and X-ray profile fitting}
-
-%% TODO Working at around here...  now pending some code work.
-
+% Procedure: model computation
+To constrain magnetic field structure, we compare measured profiles to modeled
+profiles from the transport model of equation~\eqref{eq:model} for varying
+$B_0$ and $a_b$.  The parameters $B_{\mt{min}} = 5 \muG$, $\eta_2 = 1$, and
+$\mu = 1$ are held fixed.  Diffusion, in particular, is negligible for modeled
+radio emission as particle energies are 3 orders of magnitude lower than in
+X-ray.  Neglecting diffusion also circumvents the unphysical assumption that
+$D(x) B^2(x)$ is constant, which was invoked to obtain Green's function
+solutions to equation~\eqref{eq:model}.
+
+% Procedure: chi-by-eye "fitting"
+We align model profiles to measurements by eye, varying relative amplitudes and
+translations in radio and X-ray independently to best match the measured
+profiles.  We manually vary $B_0$ and $a_b$ and attempt to reproduce both the
+radio and X-ray rims.  Although ``fitting'' by eye cannot strongly constrain
+model parameters, we can compute values of $B_0$ and $a_b$ consistent with the
+observed profiles and qualitatively constrain magnetic damping throughout the
+remnant.  Results from a more involved nonlinear fit may not be more reliable
+as we cannot constrain spatially heterogeneous radio emission within
+the remnant.  Moreover, our transport model neglects self-similar downstream
+evolution of shocked plasma (decaying velocity, density, and magnetic field)
+and is unreliable far downstream of the shock.
+
+% Procedure: compare to previous work
+The procedure we adopt for radio and X-ray modeling contrasts strongly with the
+X-ray FWHM-width fitting, which neglected profile shape in favor of more robust
+FWHM measurements.  Here, manually fitting profiles instead of FWHMs allows us
+to consider radio and X-ray filaments that do not have well-defined FWHMs.
+Radio rims consistently do not fall below 50\% of the peak emission.  We are
+also able to use profiles from regions not previously considered due to the
+lack of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.
+
+% Results: morphology, individual regions, main figure
+We identify three classes of radio profiles: thin rims with downstream troughs,
+plateaus, and continuous rises.  Regions B, C, D (southern limb) show plateaus
+in radio emission.  Regions J, L, M (around NW) show continuous rises in
+emission.  All other regions have a radio rim within $15\arcsec$ of the forward
+shock, where the forward shock in radio is assumed at zero intensity.
 Figure~\ref{fig:radio-prfs} shows extracted radio and nonthermal X-ray
-($4$--$7\unit{keV}$) profiles from the plotted regions (Figure~\ref{fig:snr}),
-shown in Figure~\ref{fig:radio-prfs}.  The radio profiles show a range of
-morphology, including thin rims with a trough and either increasing and
-decreasing emission towards the remnant interior.
+($4$--$7\unit{keV}$) profiles for three well-fit regions with our best manually
+selected model profiles, illustrating each of the three radio profile types
+observed.
 
@@
     \centering
-    \plotone{figures/radio-prfs-subplot.pdf}
-    \caption{Radio (red) and nonthermal X-ray (blue) intensity profiles from
-    extraction regions shown in Figure~\ref{fig:radio-snr}.  Radio profiles are
-    shifted forward by $9\arcsec$ to correct for proper motion.  Both X-ray and
-    radio profiles are translated to place the $4$--$7 \unit{keV}$ rim $\abt
-    2\arcsec$ behind the forward shock radius $r_s = 240\arcsec$.  We emphasize
-    that the intensities and radial coordinate translations are chosen strictly
-    to aid visual comparison and are otherwise arbitrary.
+    % Slightly larger figures than given by \plotone
+    \includegraphics[width=0.46\textwidth]{figures/radio-fits-B.pdf} \\
+    \includegraphics[width=0.46\textwidth]{figures/radio-fits-K.pdf} \\
+    \includegraphics[width=0.46\textwidth]{figures/radio-fits-M.pdf}
+    \caption{Measured radio and X-ray profiles plotted with model profiles for
+    varying $a_b$ and $B_0$ in each region, showing typical parameters (and
+    ranges) required to reproduce radio and X-ray rims simultaneously in our
+    model.  Black solid curves in all regions plot our manually chosen best
+    model profiles.  Profiles are chosen to show varying radio rim morphology,
+    including plateaus (B), thin rims with troughs (K), and continuous rises
+    (M); these profiles show some of the best agreement of our selected
+    regions, but cf. Figure~\ref{fig:radio-prfs-meh}.  Profile radial
+    coordinates are shifted arbitrarily to aid visual comparison (following
+    proper motions of \citet{katsuda2010-tycho} where possible) but may not be
+    physically meaningful.  Negative radio intensity is associated with
+    deconvolution of raw VLA visibilities.
     \label{fig:radio-prfs}}
@@
 
-Our model profiles are fully characterized by $B_0$, $a_b$, and $B_{\mt{min}}$,
-with $B_{\mt{min}} = 5 \muG$ fixed as before.  We neglect diffusion in modeling
-radio emission as particle energies are 3 orders of magnitude lower than in
-X-ray.  This also circumvents the unphysical assumption that $D(x) B^2(x)$ is
-constant, which was accepted in order to obtain Green's function solutions for
-our transport model, equation~\eqref{eq:model}.  But, as we previously assumed
-Bohm-like diffusion, another model for particle diffusion may be necessary at
-radio wavelengths.
-
-Radio emission profiles in Tycho have been modeled by \citet{cassam-chenai2007}
-and \citet{morlino2012} as part of broader hydrodynamic modeling studies,
-which permits modeling of emission throughout the remnant rather than just
-behind the shock.  Although a full time-dependent model may better capture all
-radio emission and nonthermal X-ray emission simultaneously, our simplified
-model should capture the essential physics for a very young remnant such as
-Tycho, for which the forward shock should be adiabatic.
-
-We extracted hard X-ray pro
-
-The distinct profile shapes of radio thin rims and rising or falling emission
-behind the thin rims, if rims are present, may be more sensitive discriminants
-of loss-limited and damping models.
-
-In particular, our best fits to data with moderate $\mE$ generally require
-small magnetic field $B_0$ and comparatively strong emission downstream of the
-thin rim, just below the rim half-maximum.  Although the FWHMs accorded with
-those of the loss-limited, the profiles were quite different
-(Figure~\ref{fig:rims}).
-
-\subsubsection{Radio rim shape analysis}
-
-Although radio and X-ray rim profiles are difficult to jointly model, we can
-use observed decreases in emission just behind the shock to constrain allowable
-model parameters.  Where a decrease in radio emission occurs behind the peak
-emission, the steepest decrease in emission allows us to bound the minimum
-magnetic field and the maximum allowable damping length -- i.e., we require a
-fast magnetic field drop-off with distance (for the assumed $B_{\mt{min}} = 5
-\muG$).
-
-Conversely, a continuous increase in emission requires a minimum damping
-length, as too small a damping length and moderate field strength will give
-rise to a radio rim.  However, diffuse remnant-wide radio emission may obscure
-a radio rim associated with the forward shock.  Thus, although a continuous
-rise in emission is consistent with weak damping (and loss-limited X-ray rims),
-we cannot rule out the possibility of magnetic damping.
-
-Table~\ref{tab:???} lists intensity drop-offs for radio and X-ray profiles in
-each region at various distances behind the peak (rim) emission, favoring the
-shortest possible distance to obtain a steep drop-off and better constrain
-$B_0$ and $a_b$.  Assuming $B_0 < 500 \muG$ in a damped model, we can also
-constrain the minimum
-
-Generate a slew of profile shapes, and ask that emission over XXX distance
-behind the shock NOT rise above the peak/rim distance.  This rules out the
-smallest damping lengths and fields (i.e., no trough at XXX distance...)
-
-Finally, if a trough is present in the radio rim, we may further
-
-In Figure~\ref{fig:radio-bound} we illustrate schematically
+% Results: linchpin for damping model here
+A loss-limited rim model (constant magnetic field $B_0$) cannot produce thin
+radio rims.  Our model requires damping length $a_b \lesssim 0.1$ to produce a
+plateau or thin rim in radio emission.  For regions with thin radio rims, the
+best manually selected profiles have $B_0$ between $50$--$400 \muG$, neglecting
+only Region N which could not be modeled simultaneously in both X-ray and radio
+(Figure~\ref{fig:radio-prfs-meh}).  The damping length $a_b$ ranges between
+$0.01$--$0.03$, or $2$--$7\arcsec$.  The radio plateaus in regions B, C, D are
+compatible with damping lengths between $0.01$--$0.05$.  Continuous rises in
+radio emission are best modeled with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300
+\muG$.  Although damping lengths $a_b \gtrsim 0.1$ may not be physically
+meaningful, such large values of $a_b$ yield practically constant magnetic
+field behind the shock regardless.
+
+% TODO what happens if \Bmin = 2 \muG?!
+
+% Results: downstream emission should bound damping for an idealized,
+% spherically symmetric remnant
+The slope and depth of the radio emission decrease behind a thin rim also
+gives a soft bound on the minimum magnetic field and maximum allowable damping
+length, if other sources of radio emission increase monotonically downstream of
+the shock and thus do not give rise to radio rims.  The maximum plausible $a_b$
+is $\abt 0.01$--$0.05$ (1--5\% of shock radius, or $2$--$12\arcsec$); the
+minimum magnetic field is $\abt 20 \muG$ assuming $\Bmin = 5 \muG$, at least
+consistent with the expectation for a strong adiabatic shock.
 
@@
     \centering
-    \plotone{figures/radio-min-bound-6arcsec.pdf}
-    \caption{Maximum intensity drop-off within 6 arcsec of forward shock for
-        modeled 1.375 GHz radio profile.
-    \label{fig:radio-bound}}
+    \includegraphics[width=0.47\textwidth]{figures/radio-fits-I.pdf} \\
+    \includegraphics[width=0.47\textwidth]{figures/radio-fits-N.pdf}
+    \caption{Measured profiles that are less well-described by our model
+    profiles, compared to Figure~\ref{fig:radio-prfs}.  Region I shows
+    irregularly shaped radio rim.  Region N is a superposition of two filaments
+    that cannot be simultaneously well-modeled in both X-ray and radio,
+    requiring unrealistic magnetic fields or atypically small damping length to
+    reproduce the emission plateau behind the radio thin rim.
+    \label{fig:radio-prfs-meh}}
 \end{figure}
+
+% Discussion: confounding effects (and figure)
+Tycho's shock structure is more complex than assumed by our transport model.
+Moreover, emission in the remnant interior clearly shows spatial structure
+(Figure~\ref{fig:radio-snr}).  Figure \ref{fig:radio-prfs-meh} shows two
+regions that were poorly described by our model.  A majority of our regions
+have irregular rims; in at least 2--3 regions, this may be attributed to
+projection of multiple distinct filaments.  Others (e.g., Region K) show rims
+with slopes that cannot be matched by our models, whether too steep or
+shallow.  Shape mismatch may be attributed in part to point-spread mismatch,
+diffusion (e.g., $\eta_2 \neq 1$), shock precursors, or other effects.
+
+Nevertheless, our conclusion that thin radio rims require magnetic damping
+should be robust and independent of model assumptions.
+\citet{cassam-chenai2007}, for example, observed the same dichotomy in radio
+emission for constant and damped magnetic fields in modeled profiles of Tycho's
+shock from a self-similar hydrodynamic model with diffusive shock acceleration.
+Our model captures the essential physics for a very young remnant such as
+Tycho, for which the forward shock should be adiabatic.
+
+% TODO We have NOT considered the relative intensities of X-ray / radio rims!
 
@@
 even inverts the effect of $\eta_2$ on our model profiles (where larger
-$\eta_2$ can cause rim widths to narrow).
-
-However, the radio modeling assumes \emph{no diffusion} and should not be
-impacted by this potentially incorrect assumption.
+$\eta_2$ can cause rim widths to narrow).  Nevertheless, the modeled behavior
+is physically reasonable.  And, only X-ray profiles are impacted by the
+assumption on $D(x)$ as radio profiles assume no diffusion.
 
@@
 
-We measured the widths of thin synchrotron filaments around Tycho's supernova
-remnant and confirmed that our measured filaments are dominated by nonthermal
-emission with clearly measurable full widths at half maximum in 4--5 energy
-bands.  We find moderate narrowing of rim widths across the remnant,
-corroborating rim narrowing observed by \citet{ressler2014} in the remnant of
-SN 1006.  Our multiple measurements give loss-limited diffusion and magnetic fields
-broadly consistent with prior estimates from rim widths
-\citep[e.g.,][]{parizot2006, rettig2012} and radio and gamma ray measurements
-\citep{acciari2011, morlino2012}.  Loss-limited and magnetic damping models are
-equally capable of describing our observed data.  At small energy dependence
-the two models are indistinguishable and magnetic damping fits still favor
-moderately amplified magnetic fields.  At moderate energy dependence ($\mE \sim
--0.3$), the damping model favors weaker magnetic fields, but modeled FWHMs may
-not be truly representative of thin rim widths and profiles.
-
-As our data are not count limited, we suggest that additional proxies for
-diffusion and magnetic field are needed to establish or rule out the presence
-of damping at the shocks of young supernova remnants.  More sophisticated
-modeling of shock physics \citep[e.g.,][]{zirakashvili2014} and shock/filament
-structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
-results.  Complete rim profile fitting and sub-arcsecond radio profiles (as may
-be enabled by EVLA and ALMA) may better discriminate between models.
-
-% Further work -- radio
-%As has been noted by many workers, observations of radio synchrotron rims would
-%provide strong and immediate evidence for magnetic field damping (at the
-%lengthscales of said radio rims).  Previous workers have certainly tried
-%\citep{cassam-chenai2007, morlino2012} but it seems not easy.
-%A new epoch of VLA and \Chandra observations in this year (PIs: J. Hewitt, B.
-%Williams) will offer a rich dataset of sub-arcsecond observations that may
-%reveal more about rim morphology and perhaps even temporal variation over a 10+
-%year baseline (compare to \citet{katsuda2010-sn1006}).
+We measured the widths of several thin synchrotron filaments around Tycho's
+supernova remnant and found moderate narrowing of rim widths throughout the
+remnant, corroborating rim narrowing observed by \citet{ressler2014} in the
+remnant of SN 1006.  We confirmed that selected filaments are dominated by
+nonthermal emission and have clearly measurable full widths at half maximum in
+4--5 energy bands.
+
+A steady-state particle transport model with constant magnetic field gives
+diffusion coefficients and magnetic field strengths broadly consistent with
+prior estimates from rim widths \citep[e.g.,][]{parizot2006, rettig2012} and
+radio and gamma ray measurements \citep{acciari2011, morlino2012}.  The same
+model with a damped magnetic field is equally capable of describing our
+measured data.  At weak energy dependence the two models are indistinguishable
+and magnetic damping fits still favor moderately amplified magnetic fields.  At
+moderate energy dependence ($\mE \sim -0.3$), the damping model favors weaker
+magnetic fields, but modeled FWHMs may not be truly representative of thin rim
+widths and profiles.
+
+Thin radio synchrotron rims, however, can only be produced at the shock by
+magnetic damping.  Assuming shocked electrons account for most radio emission
+immediately downstream of Tycho's forward shock, we jointly model radio and
+X-ray profiles to measured profiles and find that damping lengths of $1$--$5$\%
+of the shock radius are required throughout most of the remnant; only a few
+(3/16) selected regions are plausibly consistent with a constant advected
+magnetic field.  Typical magnetic field strengths range between $50$--$400
+\muG$.  Although we cannot bound damping lengths and fields from our
+qualitative profile comparisons, our results are physically reasonable and are
+likely good to order-of-magnitude.
+
+%Additional proxies for diffusion and/or magnetic field are needed to better
+%constrain magnetic damping in the shocks of young supernova remnants.
+%
+%As our data are not count limited, we suggest that additional proxies for
+%diffusion and magnetic field are needed to establish or rule out the presence
+%of damping at the shocks of young supernova remnants.  More sophisticated
+%modeling of shock physics \citep[e.g.,][]{zirakashvili2014} and shock/filament
+%structure \citep[cf.][]{caprioli2013} may be necessary to improve modeling
+%results.
 
@@
 A.T. thanks CRESST for sponsorship/support at GSFC (any relevant grants?)
-B.J.W. NPP?
+We thank David Moffett for providing the VLA image used in this study.
 The scientific results reported in this article are based on data obtained from
@@
 This research made extensive use of NASA's Astrophysics Data System.
-This research made use of APLpy, an open-source plotting package for Python
-hosted at \href{http://aplpy.github.com}{http://aplpy.github.com}.
+This research also made use of APLpy, an open-source plotting package for
+Python hosted at \href{http://aplpy.github.com}{http://aplpy.github.com}.
 
 {\it Facilities:} \facility{CXO (ACIS-I)}
+
+% ==========
+% References
+% ==========
+\bibliographystyle{apj}  % AASTeX journal macros are supplied in ADS entries
+\bibliography{refs-snr}
 
@@
 
-Here we supply detailed best loss-limited and damped fit results for averaged
-filament widths in SN 1006, from \citet{ressler2014}.
+Here we give best loss-limited and damped fit results for averaged filament
+widths in SN 1006, taken from \citet{ressler2014}.
 
@@
 
-\clearpage
-\section{Best fits, Tycho, with $\Bmin=2\muG$}
-
-\begin{table}[ht]
-    \scriptsize
-    \centering
-    \caption{Best model fits for all regions, $\mu = 1$, $\Bmin=2\muG$}
-    \input{suppl-fits-all-bmin2.tex}
-\end{table}
-
-% As above but with eta2=1 fixed!
-\begin{table}[ht]
-    \scriptsize
-    \centering
-    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$,
-        $\Bmin=2\muG$}
-    \input{suppl-fits-all-bmin2-eta2one.tex}
-\end{table}
-
-% Only show these giant tables in 2col... no need to print these
-\iftoggle{manuscript}{
-}{
-    % ===============================
-    % Damping best fit sea of numbers
-    % ===============================
-    \clearpage
-    \section{Magnetic damping best fit tables}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
-        \input{suppl-fits-damp-f1.tex}
-    \end{table*}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
-        \input{suppl-fits-damp-f2.tex}
-    \end{table*}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
-        \input{suppl-fits-damp-f2-pt2.tex}
-    \end{table*}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
-        \input{suppl-fits-damp-f3.tex}
-    \end{table*}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
-        \input{suppl-fits-damp-f4.tex}
-    \end{table*}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
-        \input{suppl-fits-damp-f5.tex}
-    \end{table*}
-
-    % ================================
-    % Damping best fit tables, SN 1006
-    % ================================
-    \clearpage
-    \section{Magnetic damping fit tables, SN 1006}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to SN1006 filaments, $\mu = 1$}
-        \input{suppl-fits-damp-sn1006.tex}
-    \end{table*}
-
-    \clearpage
-    \section{Magnetic damping fit tables, SN 1006, no e- cutoff}
-
-    \begin{table*}[ht]
-        \scriptsize
-        \centering
-        \caption{Damped fits to SN1006 filaments, $\mu = 1$, no e- cutoff}
-        \input{suppl-fits-damp-nocut-sn1006.tex}
-    \end{table*}
-}
+%\clearpage
+%\section{Best fits, Tycho, with $\Bmin=2\muG$}
+%
+%\begin{table}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Best model fits for all regions, $\mu = 1$, $\Bmin=2\muG$}
+%    \input{suppl-fits-all-bmin2.tex}
+%\end{table}
+%
+%% As above but with eta2=1 fixed!
+%\begin{table}[ht]
+%    \scriptsize
+%    \centering
+%    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$,
+%        $\Bmin=2\muG$}
+%    \input{suppl-fits-all-bmin2-eta2one.tex}
+%\end{table}
+%
+%% Only show these giant tables in 2col... no need to print these
+%\iftoggle{manuscript}{
+%}{
+%    % ===============================
+%    % Damping best fit sea of numbers
+%    % ===============================
+%    \clearpage
+%    \section{Magnetic damping best fit tables}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
+%        \input{suppl-fits-damp-f1.tex}
+%    \end{table*}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
+%        \input{suppl-fits-damp-f2.tex}
+%    \end{table*}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
+%        \input{suppl-fits-damp-f2-pt2.tex}
+%    \end{table*}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
+%        \input{suppl-fits-damp-f3.tex}
+%    \end{table*}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
+%        \input{suppl-fits-damp-f4.tex}
+%    \end{table*}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
+%        \input{suppl-fits-damp-f5.tex}
+%    \end{table*}
+%
+%    % ================================
+%    % Damping best fit tables, SN 1006
+%    % ================================
+%    \clearpage
+%    \section{Magnetic damping fit tables, SN 1006}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to SN1006 filaments, $\mu = 1$}
+%        \input{suppl-fits-damp-sn1006.tex}
+%    \end{table*}
+%
+%    \clearpage
+%    \section{Magnetic damping fit tables, SN 1006, no e- cutoff}
+%
+%    \begin{table*}[ht]
+%        \scriptsize
+%        \centering
+%        \caption{Damped fits to SN1006 filaments, $\mu = 1$, no e- cutoff}
+%        \input{suppl-fits-damp-nocut-sn1006.tex}
+%    \end{table*}
+%}
 
@@
 \]
-And, the magnetic field terms cancel!  Our final usable result is:
+And, the magnetic field terms cancel.  Our final result
+(equation~\eqref{eq:cutoff}) is:
 \begin{equation}
@@
 
-% ==========
-% References
-% ==========
-\bibliographystyle{apj}  % AASTeX journal macros are supplied in ADS entries
-\bibliography{refs-snr}
-
 %\end{CJK}

### 2014-12-11 manuscript/paper-tycho.tex
Paper fixes; sent draft+diff around

@@
 \documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
+%\documentclass[iop, apj, numberedappendix]{emulateapj}
+
 %\documentclass[12pt,preprint]{aastex}  % one-column, single-spaced
 %\documentclass[iop, apj, numberedappendix, twocolappendix]{emulateapj}
-%\documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
-and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
-consistent with prior work on Tycho's SNR, whereas magnetic damping permits
-magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
-coefficients (typically $\abt 1$--$10$).
+and particle diffusion coefficients $\abt1$--$100\times$ Bohm values, whereas
+magnetic damping permits magnetic fields of $\abt 10$--$300 \muG$ and
+comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
 Corresponding thin rim radio rims require magnetic damping, however.  We
@@
 off downstream, producing a shell-like morphology with bright X-ray and radio
-rims/filaments due to line-of-sight projection \citep{koyama1995}.  The strong
-and time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
+rims/filaments due to line-of-sight projection \citep{koyama1995}.  Strong and
+time-variable synchrotron radiation \citep[e.g.,][]{uchiyama2007,
 patnaude2007}, in conjunction with multiwavelength spectral modeling
@@
 the possibility of damping in SNR shocks has not been fully tested
-\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} examined radio and
-X-ray synchrotron rim profiles, but found that neither damping nor synchrotron
-losses matched radio profiles particularly well.  \citet{araya2010} measured
-rims at multiple energy bands in Cas A, but suggested that the rims only narrow
-more weakly than expected and did not consider magnetic damping.
-\citet{rettig2012} gave model predictions for several historical SNRs and
-proposed discriminating based on filament spectra -- the expectation is that
-damped spectra are softer, loss-limited harder.  Recently, \citet{ressler2014}
-further extended the idea of discriminating between damped or loss-limited rims
-by measuring rim width energy dependence in X-ray energies and found that rims
-consistently narrowed in the remnant of SN 1006.
+\citep{pohl2005, marcowith2010}.  \citet{cassam-chenai2007} modeled radio and
+X-ray synchrotron rim profiles but could not simultaneously reproduce the
+intensities of observed X-ray and radio rims with damped or loss-limited
+magnetic fields.  \citet{araya2010} measured rims at multiple energy bands in
+Cas A, but suggested that the rims only narrow more weakly than expected and
+did not consider magnetic damping.  \citet{rettig2012} gave model predictions
+for several historical SNRs and proposed discriminating based on filament
+spectra -- the expectation is that damped spectra are softer, loss-limited
+harder.  Recently, \citet{ressler2014} further extended the idea of
+discriminating between damped or loss-limited rims by measuring rim width
+energy dependence in X-ray energies and found that rims consistently narrowed
+in the remnant of SN 1006.
 
@@
 and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
-and the implications for future studies of young supernova remnant shocks.
+and attempt to constrain damping through spectral variation downstream of the
+forward shock and considering both radio and X-ray rim morphology.
+%and the implications for future studies of young supernova remnant shocks.
 
@@
 and intuitive sense of diffusion strength regardless of the underlying electron
-energies.  We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.
+energies.
 
@@
 The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
-field, which varies in a damped model.  For simplicity, we assume that the
-shock acceleration process is set by the diffusion at the immediate shock and
-so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
+field, which varies in a damped model.  For simplicity, we assume that shock
+acceleration is controlled by diffusion at the immediate shock and so
+equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
 $B_0$.
-\note[Aaron]{Is this correct?  Can rederive the expression (particles
-penetrate some distance downstream, then back), but I'm not sure if it's even
-sensible with diffusion coefficient varying so sharply.}
-
-The solutions to equation~\eqref{eq:model} given by \citet{lerche1980,
-rettig2012} assume $D(x) B^2(x)$ constant in order to make
-equation~\eqref{eq:model} semi-analytically tractable.  Although unphysical, we
-enforce this criterion by using a modified diffusion coefficient in our
-calculations following
-\citet{rettig2012}, given as:
+
+The solutions to equation~\eqref{eq:model} given by \citet{lerche1980} assume
+$D(x) B^2(x)$ constant to render equation~\eqref{eq:model} semi-analytically
+tractable.  Although unphysical, we enforce this assumption by modifying the
+diffusion coefficient as, following \citet{rettig2012}:
 \begin{equation} \label{eq:ddamp}
@@
              \left[ \frac{\Bmin}{B_0} +
-                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2}
+                    \frac{B_0 - \Bmin}{B_0} e^{-x/a_b} \right]^{-2} .
 \end{equation}
@@
 predictions of rim shapes (within $\abt a_b$ of the shock front), but our
-results are complicated by the increasing importance of energy-dependent
-synchrotron losses downstream of the thin rim.  As we use FWHM as a singular
-proxy for rim shapes, our procedure is not able to discern the transition in
-shape downstream of the damped rim that may impact profile FWHMs, even as
-damping controls the main observed rim emission.
+results are complicated by energy-dependent synchrotron losses downstream of
+the thin rim.
 
@@
 % NOTE keep region/filament numbering up to date
-We selected 20 regions in 5 distinct filaments around Tycho's shock
+We selected 20 regions in 5 filaments around Tycho's shock
 (Figure~\ref{fig:snr}) based on the following criteria: (1) filaments should be
@@
 and hence are resolved by \textit{Chandra}'s point-spread function (PSF), which
-has FWHM of $\abt 1\arcsec$ at $4\arcmin$ off-axis.
+has FWHM $\lesssim 1\arcsec$ within $4\arcmin$ of the optical axis.
 
@@
     \iftoggle{manuscript}{
-        \includegraphics[width=0.2\textwidth]{figures/snr.pdf}
+        %\includegraphics[width=0.3\textwidth]{figures/snr.pdf}
+        \includegraphics[width=0.3\textwidth]{figures/snr-inv.png}
     }{
-        \plotone{figures/snr.pdf}
+        %\plotone{figures/snr.pdf}
+        \plotone{figures/snr-inv.png}
     }
@@
 We extracted spectra at and immediately behind thin rims in each region
-(``'rim'', ``downstream'' spectra respectively) to confirm that rim width
-measurements are not affected by contaminating thermal line emissions.  We
-used our empirical fits of rim profile shape (Section~\ref{sec:fwhms} below)
-to select two corresponding sections in each region for spectrum extraction.
-The rim section is the smallest sub-region containing the measured FWHM bounds
-from all energy bands.  The downstream section extends from the rim section's
-downstream edge to the farthest downstream profile fit domain bound, in all
-energy bands (fits of equation~\eqref{eq:prof}); i.e., the downstream section
-is bounded by the thin rim FWHM and the intensity plateau/trough behind the
-rim.  To illustrate our selections, Figure~\ref{fig:spec} plots example rim
-profiles ($4.5$--$7 \unit{keV}$) with the downstream and rim sections
-highlighted.
+(``rim'', ``downstream'' spectra respectively) to confirm that rim width
+measurements are not contaminated by thermal line emission.  The two extraction
+regions are determined by our empirical fits of rim profile shape
+(Section~\ref{sec:fwhms}).  The rim section is the smallest sub-region
+containing the measured FWHM bounds from all energy bands.  The downstream
+section extends from the rim section's downstream edge to the farthest
+downstream profile fit domain bound, in all energy bands (fits of
+equation~\eqref{eq:prof}); i.e., the downstream section is bounded by the thin
+rim FWHM and the intensity plateau/trough behind the rim.  To illustrate our
+selections, Figure~\ref{fig:spec} plots example rim profiles ($4.5$--$7
+\unit{keV}$) with the downstream and rim sections highlighted.
 
 % Spectrum data, binning, background
-Spectra taken from all enumerated \Chandra ObsIDs (Section~\ref{sec:regions})
-were grouped into bins of $\geq 15$ counts.  We extracted background spectra
-from circular regions (radius $\abt 30\arcsec$) around the remnant's exterior;
-each region's rim and downstream spectra subtracted the closest background
-region's spectrum.
+Spectra were binned such that each datum had $\geq 15$ counts.  We extracted
+background spectra from circular regions (radius $\abt 30\arcsec$) around the
+remnant's exterior; each region's rim and downstream spectra subtracted the
+closest background region's spectrum.
 % Background region size is valid for data-tycho/bkg-2/ selections
@@
 profile widths at $0.7 \unit{keV}$.  Width errors in our least squares fits
-average the positive and negative errors on each FWHM measurement.  For an
-input set of model parameters, we numerically computed intensity profiles and
-hence model FWHMs as detailed in Section~\ref{sec:transport}, and used a
-Levenberg-Marquardt fitting routine to identify best fit model parameters.
+average the positive and negative errors on each FWHM measurement.  For a given
+set of model parameters, we numerically computed intensity profiles and
+hence model FWHMs as detailed in Section~\ref{sec:transport}; we then used a
+Levenberg-Marquardt fitter to seek model parameters yielding best fit FWHMs.
 To assist the nonlinear fitting, we tabulated model FWHM values on a large grid
-of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid as
-initial guesses for fitting.
+of model parameters (primarily $\eta_2$ and $B_0$) and used best-fit grid
+parameters as initial guesses for fitting.
 % TODO this may be obsoleted if we recompute stuff...  I only computed errors
@@
 negative and tend smoothly towards $0$ (weaker energy-dependence) with
-increasing energy.  The errors on FWHM measurements are typically $\abt 10\%$
-or smaller, reflecting the high quality \Chandra data as also seen in
-Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
-part to (1) our profile fitting procedure, which depends on a somewhat
-arbitrary choice of profile fit function, and (2) variation in Tycho's rim
-morphology (e.g., Figure~\ref{fig:profiles}).
+increasing energy.  Errors on FWHM measurements are typically $\lesssim 10\%$,
+reflecting the high quality of the underlying \Chandra data.  Scatter in FWHM
+measurements may be attributed in part to (1) our profile fitting procedure,
+which depends on a somewhat arbitrary choice of profile fit function, and (2)
+variation in Tycho's rim morphology (e.g., Figure~\ref{fig:profiles}).
 
@@
     \iftoggle{manuscript}{
-        \epsscale{0.5}
-    }{}
+        \epsscale{0.7}
         \plotone{figures/prfs-fit-01.pdf} \\
         \plotone{figures/prfs-fit-16.pdf}
+        \epsscale{1}
+    }{
+        \plotone{figures/prfs-fit-01.pdf} \\
+        \plotone{figures/prfs-fit-16.pdf}
+    }
     \caption{Best fit full model rim profile width predictions for Regions 1
@@
 
-Here we first explore trends in our data and best-fit diffusion and magnetic
-fields.  We then discuss discrimination of the loss-limited and damping models
-(i.e., our ability to favor or constrain a finite value of $a_b$), and possible
-paths forward to better constrain our model parameters.
-
 % --------------------------------------------
@@
 dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
-l_{\mt{diff}}$ is exactly the synchrotron cut-off energy,
+l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy.
 % TODO citation if you can find it...
-$\abt 0.3 \unit{keV}$ in Tycho \citep{hwang2002}.  Diffusion should begin
-overtaking advection and push $\mE$ towards $0$ in soft X-rays, as opposed to
-$\mE \abt -0.5$ expected for strong advection (Section~\ref{sec:energydep}).  A
-decrease in $|\mE|$ is then reassuringly consistent with the framework of
-diffusive shock acceleration.
+Diffusion should begin overtaking advection and push $\mE$ towards $0$ in soft
+X-rays, as opposed to $\mE \abt -0.5$ expected for strong advection
+(Section~\ref{sec:energydep}).  A decrease in $|\mE|$ is then reassuringly
+consistent with the framework of diffusive shock acceleration.
 
@@
 conjecture.  Filament widths both increase and decrease between energy bands in
-multiple regions, and diffusion ($\eta_2$) and hence $\Ecut$ are poorly
+multiple regions, and diffusion $\eta_2$ and hence $\Ecut$ are poorly
 constrained by our fit results.  Our averaged results should mitigate the
@@
 % lad/ldiff scalings give eta/B0 scalings
-In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ while
-$B_0$ is approximately constant.  The advective lengthscale,
+In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ with
+$B_0$ approximately constant.  The advective lengthscale,
 equation~\eqref{eq:lad}, may be rearranged to obtain:
@@
 
-To measure synchrotron cut-offs in Tycho, we fitted rim spectra
+To measure synchrotron cut-offs in Tycho, we fitted ``rim'' spectra
 (Section~\ref{sec:spec}) to the XSPEC model \texttt{srcut}, modified to fit in
-log-frequency units.  Column density $N_{\mt{H}}$ and cut-off frequency
-$nu_{\mt{cut}}$ are free parameters; we fixed the radio spectral index $\alpha
-= 0.58$ as done in our profile modeling \citep{sun2011}.
-Table~\ref{tab:fits-srcutlog} presents the spectrum fit parameters and best
-loss-limited fits with $\nu_{\mt{cut}}$-derived $\eta_2$ fixed.
-Variation in $\mu$ has a small effect on best fits; Regions 1 and 16 have best
-fit values of $B_0$ increasing over $252$--$266 \muG$ and $660$--$700 \muG$
-respectively as $\mu$ ranges between $0$--$2$.
-
-The results are comparable to fits with $\eta_2 = 1$ fixed
-(Table~\ref{tab:fits-all-eta2one}).  The synchrotron cut-off frequency is
-typically $0.3 \unit{keV}$, though we note that Regions 11, 12 have unusually
-high cut-off frequencies.  Fitted $B_0$ values span $250$--$700 \muG$.
-We cannot deduce any particular insight from requiring that $\eta_2$ reflects
-the measured value of $\nu_{\mt{cut}}$.  But, if the diffusion coefficients are
-more reliable or physically reasonable, the derived estimates of $B_0$ may be
-more credible.
-
-\begin{table}
-    \scriptsize
-    \centering
-    \caption{Synchrotron roll-off, $\eta_2$, and fits for $\mu = 1$
-        \label{tab:fits-srcutlog}}
-    \begin{tabular}{@{}l ccc ccr@{}}
-    \toprule
-    {} & \multicolumn{3}{c}{\texttt{srcut} fit parameters}
-       & \multicolumn{3}{c}{Best fits for $\mu = 1$}\\
-    \cmidrule(lr){2-4} \cmidrule(l){5-7}
-    Region & $N_{\mt{H}}$ & $\nu_{\mt{cut}}$ & $\chi^2_{\mathrm{red}}$ (dof)
-           & $\eta_2$ & $B_0$ & $\chi^2$ \\
-    {} & ($10^{22} \mt{cm}^{-2}$) & (keV/$h$) & {}
-       & (-) & ($\mu$G) & {} \\
-    \midrule
-     1 & 0.62 & 0.30 & 1.17 (284) & 12.0 & 256 & 29.1 \\
-     2 & 0.60 & 0.30 & 1.08 (202) & 11.8 & 443 & 99.4 \\
-     3 & 0.68 & 0.33 & 1.14 (167) & 10.6 & 599 & 31.8 \\
-    \cmidrule{1-7}
-     4 & 0.61 & 0.29 & 1.15 (278) & 12.0 & 402 & 36.2 \\
-     5 & 0.64 & 0.27 & 1.11 (255) & 12.9 & 419 & 32.5 \\
-     6 & 0.64 & 0.29 & 0.93 (231) & 11.9 & 568 & 89.7 \\
-     7 & 0.71 & 0.23 & 1.14 (224) & 15.3 & 618 & 11.7 \\
-     8 & 0.66 & 0.41 & 0.96 (198) & 8.38 & 511 & 15.1 \\
-     9 & 0.73 & 0.30 & 0.88 (175) & 11.2 & 573 & 23.4 \\
-    10 & 0.68 & 0.36 & 0.96 (164) & 9.45 & 631 & 1.42 \\
-    \cmidrule{1-7}
-    11 & 0.61 & 0.55 & 1.07 (153) & 6.08 & 452 & 18.1 \\
-    12 & 0.57 & 0.88 & 0.90 (172) & 3.74 & 375 & 12.6 \\
-    13 & 0.59 & 0.38 & 1.09 (235) & 8.43 & 529 & 13.8 \\
-    \cmidrule{1-7}
-    14 & 0.54 & 0.23 & 0.95 (167) & 11.9 & 547 & 28.6 \\
-    15 & 0.57 & 0.29 & 1.03 (183) & 9.54 & 598 & 23.1 \\
-    16 & 0.58 & 0.32 & 1.12 (182) & 8.44 & 670 & 6.26 \\
-    17 & 0.59 & 0.30 & 0.94 (187) & 8.97 & 637 & 32.6 \\
-    \cmidrule{1-7}
-    18 & 0.55 & 0.19 & 1.13 (220) & 14.6 & 432 & 72.4 \\
-    19 & 0.57 & 0.34 & 0.99 (157) & 8.86 & 542 & 12.8 \\
-    20 & 0.55 & 0.31 & 1.07 (192) & 9.60 & 631 & 96.0 \\
-    \bottomrule
-    \end{tabular}
-    \tablecomments{\texttt{srcut} fits performed in log-frequency coordinates;
-    here $h$ is Planck's constant.  $\eta_2$ values are computed from
-    equation~\eqref{eq:cutoff} and held fixed in model fits.}
-\end{table}
+log-frequency units; we fix the radio spectral index $\alpha = 0.58$
+\citep{sun2011} as done in our profile modeling and fit for column density
+$N_{\mt{H}}$ and cut-off frequency $\nu_{\mt{cut}}$ in each region.  The
+fitted cut-off frequency is typically $0.3 \unit{keV/h}$, consistent with fits
+by \citet{hwang2002}, but Regions 11, 12 have unusually high cut-off
+frequencies $0.55$, $0.88 \unit{keV/h}$ consistent with harder rim spectra
+(Table~\ref{tab:spec}).
+
+Using the derived values of $\nu_{\mt{cut}}$ ($0.19$--$0.88 \unit{keV/h}$) and
+hence $\eta_2$ ($4$--$15$), we computed new loss-limited fits for all regions
+with cut-off derived values of $\eta_2$ fixed.  Fitted $B_0$ values span
+$250$--$700 \muG$.  Variation in $\mu$ has a smaller effect on best fits as we
+are able to derive different $\eta_2$ values as a function of $\mu$; Regions 1
+and 16 have best fit values of $B_0$ increasing over $252$--$266 \muG$ and
+$660$--$700 \muG$ respectively as $\mu$ ranges between $0$--$2$.  Our fits with
+cut-off derived values of $\eta_2$ are comparable to fits with $\eta_2 = 1$
+fixed (Table~\ref{tab:fits-all-eta2one}).  We are unable to deduce any insights
+from requiring that $\eta_2$ reflects measurements of $\nu_{\mt{cut}}$.  But,
+diffusion coefficients computed in this manner may give more credible derived
+estimates of $B_0$ if the DSA assumptions invoked are relevant.
 
@@
 
-We also consider whether spectral variation may permit discrimination between
-loss-limited and damping models, as proposed by \citet{rettig2012}.  Electron
-energy losses will result in spectral softening downstream of the shock and
-thin rim, previously documented in Tycho by, e.g., \citet{cassam-chenai2007},
-but the precise spectral evolution depends on the assumed post-shock magnetic
-field structure (whether loss-limited or damped).  To quantify spectral
-softening, we consider the change in spectral index ($\Delta \Gamma$) between
-spectra taken at the thin rim and just downstream of the thin rim.
+Spectral variation may also discriminate between loss-limited and damping
+models as proposed by \citet{rettig2012}.  Electron energy losses will result
+in spectral softening downstream of the shock and thin rim, previously
+documented in Tycho by, e.g., \citet{cassam-chenai2007}, but the precise
+spectral evolution depends on the assumed post-shock magnetic field structure
+(whether loss-limited or damped).  To quantify spectral softening, we consider
+the change in spectral index ($\Delta \Gamma$) between spectra taken at the
+thin rim and just downstream of the thin rim.
 
@@
 index change $\Delta \Gamma$ was $0.3$ (stdev: $0.2$).  Different approaches to
-removing thermal emission in downstream spectra (adding Gaussian component to
-fit \ion{S}{15} line; excising all $2$--$2.6 \unit{keV}$ photons) yielded a
-smaller spectral index $3.17$, with mean $\Delta \Gamma \abt 0.24$ (stdev:
-$0.22$ and $0.18$ respectively).
+removing thermal emission in downstream spectra -- adding a Gaussian component
+to fit \ion{S}{15} line, or excising all $2$--$2.6 \unit{keV}$ photons --
+yielded mean downstream spectral index $3.17$, with mean $\Delta \Gamma \abt
+0.24$ (stdev: $0.22$ and $0.18$ respectively).
 
@@
     \centering
+    \iftoggle{manuscript}{
+        \includegraphics[width=0.8\textwidth]{figures/plt-specvar-1.pdf} \\
+        \includegraphics[width=0.8\textwidth]{figures/plt-specvar-16.pdf}
+    }{
         \plotone{figures/plt-specvar-1.pdf} \\
         \plotone{figures/plt-specvar-16.pdf}
+    }
     \caption{Model spectra and spectral indices as a function of energy for
@@
 shock suggests that either model parameters ($B_0$, $\eta_2$, $a_b$) or our
-model assumptions are incorrect, in the damped case.
-Our results should be representative of the parameter space of damped model
-filaments.  Damped magnetic field fit values span $24$--$400 \muG$ with varied
-$a_b$ values; varying $\eta_2$ increased the mean $\Delta\Gamma$ slightly, but
-not enough to be consistent with our measurements.
-
-Small shock fields ($B_0 < 40 \muG$) are associated with stronger spectral
-variation ($\Delta\Gamma \sim 0.06$--$0.09$); if our model is reasonable,
-spectral variation may favor weak shock fields with little to no amplification.
-But, model index variations $<0.1$ still underpredict the observed
-$\Delta\Gamma \sim 0.3$.  If loss-limited model spectra are correct, the
-observation of weak $2$--$7 \unit{keV}$ spectral evolution between rim and
-downstream extraction regions would further favor magnetic field damping.
+model assumptions are incorrect, in the damped case.  Our results should be
+representative of the parameter space of damped model filaments.  Damped
+magnetic field fit values span $24$--$400 \muG$ with varied $a_b$ values;
+varying $\eta_2$ increased the mean $\Delta\Gamma$ slightly, but not enough to
+be consistent with our measurements.
+
+The modeled spectral variation appears to disfavor loss-limited rim widths, as
+the predicted $2$--$7 \unit{keV}$ spectral variation $\Delta\Gamma \sim 0.05$
+is consistent for all regions considered.  Damped magnetic fields, especially
+if relatively weak at the shock ($B_0 \lesssim 40 \muG$), appear associated
+with stronger spectral variation ($\Delta\Gamma \sim 0.06$--$0.09$).  Spectral
+variation may thus favor shock magnetic fields with little to no amplification.
+But, modeled $\Delta\Gamma$ values $< 0.1$ still underpredict observations of
+$\Delta\Gamma \sim 0.3$.
 
@@
 \citet{reynoso1997} for a detailed presentation.
-\note[Aaron]{Was data from all configurations merged?  Done by \citet{reynoso1997}.}
+\note[Aaron]{Q for Steve: Was data from all configurations merged?  Done by
+\citet{reynoso1997} it seems.  FITS header states A config. but would like to
+verify}
 The half-power beam width of $\abt 1.5\arcsec$ just resolves thin radio rims
@@
 %$\abt4.5\arcsec$.
-Figure~\ref{fig:radio-snr} shows the extraction regions overlaying the radio
-image and the previous X-ray profile regions of Figure~\ref{fig:snr}.
+We also extracted $4$--$7 \unit{keV}$ X-ray profiles in all regions from the
+previous archival \Chandra observation to jointly model radio and X-ray
+profiles, permitting somewhat firmer discrimination of plausible model
+parameters.  Figure~\ref{fig:radio-snr} shows the extraction regions overlaying
+the radio image and the previous X-ray profile regions of Figure~\ref{fig:snr}.
 
@@
     \centering
-    \plotone{figures/radio-snr.png}  % TODO a temporary image
+    \iftoggle{manuscript}{ % TODO a temporary image
+        \includegraphics[width=0.3\textwidth]{figures/radio-snr-inv.png}
+    }{
+        \plotone{figures/radio-snr-inv.png}
+    }
     \caption{Radio image of Tycho's SNR at $1.375 \unit{GHz}$ with linear
@@
 % Procedure: model computation
-To constrain magnetic field structure, we compare measured profiles to modeled
-profiles from the transport model of equation~\eqref{eq:model} for varying
-$B_0$ and $a_b$.  The parameters $B_{\mt{min}} = 5 \muG$, $\eta_2 = 1$, and
-$\mu = 1$ are held fixed.  Diffusion, in particular, is negligible for modeled
-radio emission as particle energies are 3 orders of magnitude lower than in
-X-ray.  Neglecting diffusion also circumvents the unphysical assumption that
-$D(x) B^2(x)$ is constant, which was invoked to obtain Green's function
-solutions to equation~\eqref{eq:model}.
+We compute model radio and X-ray measured profiles from the transport model of
+equation~\eqref{eq:model} for varying $B_0$ and $a_b$.  The parameters
+$B_{\mt{min}} = 5 \muG$, $\eta_2 = 1$, and $\mu = 1$ are held fixed.
+Diffusion, in particular, is negligible for modeled radio emission as particle
+energies are 3 orders of magnitude lower than in X-ray.  Neglecting diffusion
+also circumvents the unphysical assumption that $D(x) B^2(x)$ is constant,
+which was invoked to obtain Green's function solutions to
+equation~\eqref{eq:model}.
 
@@
 translations in radio and X-ray independently to best match the measured
-profiles.  We manually vary $B_0$ and $a_b$ and attempt to reproduce both the
-radio and X-ray rims.  Although ``fitting'' by eye cannot strongly constrain
-model parameters, we can compute values of $B_0$ and $a_b$ consistent with the
-observed profiles and qualitatively constrain magnetic damping throughout the
-remnant.  Results from a more involved nonlinear fit may not be more reliable
-as we cannot constrain spatially heterogeneous radio emission within
-the remnant.  Moreover, our transport model neglects self-similar downstream
-evolution of shocked plasma (decaying velocity, density, and magnetic field)
-and is unreliable far downstream of the shock.
-
-% Procedure: compare to previous work
-The procedure we adopt for radio and X-ray modeling contrasts strongly with the
-X-ray FWHM-width fitting, which neglected profile shape in favor of more robust
-FWHM measurements.  Here, manually fitting profiles instead of FWHMs allows us
-to consider radio and X-ray filaments that do not have well-defined FWHMs.
-Radio rims consistently do not fall below 50\% of the peak emission.  We are
-also able to use profiles from regions not previously considered due to the
-lack of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.
+profiles.  We manually seek values of $B_0$ and $a_b$ that best reproduce both
+radio and X-ray profiles.  Although ``fitting'' by eye cannot strongly
+constrain model parameters, we can find plausible values of $B_0$ and $a_b$
+and qualitatively constrain magnetic damping throughout the remnant.  Results
+from a more involved nonlinear fit may not be more reliable as we cannot
+constrain spatially heterogeneous radio emission within the remnant.  Moreover,
+our transport model neglects self-similar downstream evolution of shocked
+plasma (decaying velocity, density, and magnetic field) and is unreliable far
+downstream of the shock.
+
+The radio and X-ray profile modeling here contrasts strongly with our previous
+width-energy fitting from X-ray measurements alone, which neglected profile
+shape in favor of more robust FWHM measurements.  Manually fitting profiles
+allows us to consider radio and X-ray filaments that do not have well-defined
+FWHMs, especially as radio rims do not fall below 50\% of the peak emission.
+We can also use profiles from regions not previously considered due to the lack
+of an X-ray FWHM, especially in softer ($0.7$--$4$) X-rays.
 
@@
     \centering
+    \iftoggle{manuscript}{
+        \epsscale{0.6}
+        \plotone{figures/radio-fits-B.pdf} \\
+        \plotone{figures/radio-fits-K.pdf} \\
+        \plotone{figures/radio-fits-M.pdf}
+        \epsscale{1}
+    }{
         % Slightly larger figures than given by \plotone
@@
         \includegraphics[width=0.46\textwidth]{figures/radio-fits-M.pdf}
+    }
     \caption{Measured radio and X-ray profiles plotted with model profiles for
@@
     \centering
+    \iftoggle{manuscript}{
+        \epsscale{0.8}
+        \plotone{figures/radio-fits-I.pdf} \\
+        \plotone{figures/radio-fits-N.pdf}
+        \epsscale{1}
+    }{
         \includegraphics[width=0.47\textwidth]{figures/radio-fits-I.pdf} \\
         \includegraphics[width=0.47\textwidth]{figures/radio-fits-N.pdf}
-    \caption{Measured profiles that are less well-described by our model
-    profiles, compared to Figure~\ref{fig:radio-prfs}.  Region I shows
-    irregularly shaped radio rim.  Region N is a superposition of two filaments
-    that cannot be simultaneously well-modeled in both X-ray and radio,
-    requiring unrealistic magnetic fields or atypically small damping length to
-    reproduce the emission plateau behind the radio thin rim.
+    }
+    \caption{Measured profiles poorly described by our model profiles, compared
+    to Figure~\ref{fig:radio-prfs}.  Region I shows irregularly shaped radio
+    rim.  Region N contains two superposed filaments that cannot be modeled by
+    a single rim in both X-ray and radio; the narrow X-ray rim requires
+    atypically strong magnetic fields ($\sim 800 \muG$), and the emission
+    plateau behind the radio rim requires small damping lengths ($a_b \sim
+    0.005$).
     \label{fig:radio-prfs-meh}}
@@
 $\eta_2$ can cause rim widths to narrow).  Nevertheless, the modeled behavior
-is physically reasonable.  And, only X-ray profiles are impacted by the
+appears physically reasonable.  And, only X-ray profiles are impacted by the
 assumption on $D(x)$ as radio profiles assume no diffusion.

### 2014-12-16 manuscript/paper-tycho.tex
Imgs for paper/poster; minor code/paper tweaks
Clean code for parameter space grids
Update paper images; generate set of good images for poster
Organize code / notes for Tycho images

@@
-\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
-%\documentclass[iop, apj, numberedappendix]{emulateapj}
+%\documentclass[manuscript]{aastex}  % one-column, double-spaced GENERATE BIB
+\documentclass[iop, apj, numberedappendix]{emulateapj}
 
@@
 \newtoggle{manuscript}
-\toggletrue{manuscript}
-%\togglefalse{manuscript}
+%\toggletrue{manuscript}
+\togglefalse{manuscript}
 
@@
 and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
-and attempt to constrain damping through spectral variation downstream of the
-forward shock and considering both radio and X-ray rim morphology.
+and attempt to constrain damping by (1) measuring and modeling spectral variation
+downstream of the forward shock, and (2) jointly modeling both radio and X-ray
+rim morphology.
 %and the implications for future studies of young supernova remnant shocks.
@@
     \centering
-    \iftoggle{manuscript}{ % TODO a temporary image
+    \iftoggle{manuscript}{
         \includegraphics[width=0.3\textwidth]{figures/radio-snr-inv.png}
@@
         \plotone{figures/radio-snr-inv.png}
+        %\plotone{figures/radio-snr.eps}
     }
@@
 field behind the shock regardless.
-
-% TODO what happens if \Bmin = 2 \muG?!
+Our results are also insensitive to the assumed value of $\Bmin$; only model
+profiles with small magnetic fields ($B_0 \lesssim 100 \muG$) and/or small
+damping length ($a_b < 0.01$) are affected if we take $\Bmin = 2 \muG$ rather
+than $5 \muG$.
+% TODO rewrite for clarity (!)
 

### 2014-12-16 data-tycho/imgs/tycho_aplpy.py

@@ -1,10 +1,8 @@
 """
-Short script to generate Tycho image in APLpy
+Short script to generate Tycho images in APLpy
 Should not be run stand-alone (won't do much); run with:
 $ ipython --pylab
 and make any desired customizations.  Then, go ahead and save...
-
-Also misc utilities/tidbits in functions here
 
 Aaron Tran
 """
@@ -12,11 +10,86 @@ Aaron Tran
 import aplpy
 
 def main():
-    """Load Tycho image and tweak settings for one-column manuscript fig"""
+    #manuscript_fig_snr()
+    poster_fig_snr()
 
-    f = aplpy.FITSFigure('ds9rgb.fits', figsize=(5,4.5))  # Saved from DS9
-    f.show_rgb('ds9rgb.png')            # Saved from DS9
-    f.show_regions('../regions-6/regions-6-box.reg')  # f.remove_layer(...)
+# ================================
+# APLpy tidbits for poster figures
+# ================================
+
+#def poster_fig_snr_radio():
+#    """Tycho 1.375 GHz image with scalebar, attempt to match size/scale of
+#    other poster images"""
+#    f = aplpy.FITSFigure('../TYCHO_IF1.FITS', figsize=(10, 10))
+#    f.show_colorscale(vmin=0, vmax=0.0037, stretch='linear', cmap='hot')
+#    apply_tycho_frame(f, epoch='B1950')
+#
+#    prep_save_pdf(f, 'snr_radio_poster.pdf')
+#
+#
+#def poster_fig_snr_nonthermal():
+#    """Tycho 4-7keV mosaic with scalebar, showing nonthermal rims"""
+#    f = aplpy.FITSFigure('../4-7kev_mosaic.fits', figsize=(10, 10))
+#    f.show_colorscale(vmin=5e-9, vmax=1.25e-7, stretch='sqrt', cmap='hot')
+#    apply_tycho_frame(f, epoch='J2000')
+#
+#    prep_save_pdf(f, 'snr_4-7kev_poster.pdf')
+
+
+def poster_fig_snr():
+    """RGB figure of Tycho with X-ray region overlay, scalebar
+    Uses regions w/ larger text, thicker boxes"""
+    f = aplpy.FITSFigure('ds9rgb.fits', figsize=(10, 10))
+    f.show_rgb('ds9rgb.png')
+    f.show_regions('regs/regions-6-box-poster.reg')
[…]

### 2014-12-17 manuscript/paper-tycho.tex
adaptive rminarc bug fix; eta2=1 loss-lim fits
Update paper table w/eta2=1 fit #s (extremely minor changes)
Clean up notes/Qs/etc, minor updates to paper

@@
 
-% TODO define loss-limited properly...
-% ~210 words -- a little too long
 \begin{abstract}
 Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
-radiation at their forward shocks.  Thin rims have been taken to indicate that
-shock-accelerated electrons rapidly cool downstream of the shock, requiring
-strong magnetic field amplification.  But, magnetic field damping immediately
-behind the shock could produce similarly thin rims.  We measured rim widths
-around Tycho's supernova remnant in 5 energy bands using an archival $750
-\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
-energy and are well-described by either loss-limited or magnetically damped
-scenarios, hence X-ray rim widths alone cannot discriminate between models.
-Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
-and particle diffusion coefficients $\abt1$--$100\times$ Bohm values, whereas
-magnetic damping permits magnetic fields of $\abt 10$--$300 \muG$ and
-comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
-Corresponding thin rim radio rims require magnetic damping, however.  We
-jointly model radio and X-ray profiles and estimate magnetic damping length of
-order $1$--$5$\% of remnant radius, with magnetic field strengths $\abt
-50$--$400 \muG$ assuming Bohm diffusion.  Diffusion coefficients, magnetic
-field strengths, and magnetic damping lengthscales are somewhat degenerate in
-setting observed rim widths and drop-offs.
+radiation at their forward shocks.  Thin rims require strong magnetic field
+amplification if rim widths are limited by shock-accelerated electron energy
+losses.  But, magnetic field damping immediately behind the shock could produce
+similarly thin rims.  We measured rim widths around Tycho's supernova remnant
+in 5 energy bands using an archival $750 \unit{ks}$ \Chandra observation.  Rims
+consistently narrow with increasing energy and are well-described by either
+loss-limited or magnetically damped scenarios, hence X-ray rim widths alone
+cannot discriminate between models.  Loss-limited rims require amplified
+magnetic fields of $\abt200$--$1000 \muG$ and particle diffusion coefficients
+$\abt1$--$100\times$ Bohm values, whereas magnetic damping permits magnetic
+fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
+coefficients (typically $\abt 1$--$10$).  Corresponding thin rim radio rims
+require magnetic damping, however.  We jointly model radio and X-ray profiles
+and estimate magnetic damping length of order $1$--$5$\% of remnant radius,
+with magnetic field strengths $\abt 50$--$400 \muG$ assuming Bohm diffusion.
 Although the energy dependence of synchrotron rims cannot discriminate magnetic
@@
 
-% NOTE go through and double check tenses.
 We measured synchrotron rim full widths at half maximum (FWHMs) from an
@@
 are plotted in Figure~\ref{fig:fits} alongside measured FWHMs.
-The best fit model profiles do not quite match our measured rim profiles
+The best fit model profiles do not quite match measured rim profiles
 (Figure~\ref{fig:profiles}).  Our transport equation does not account for
@@
 ripples or other structure, and thermal emission downstream of the thin rim.
-Hence, fitting to FWHM measurements should be less sensitive to these effects
-as compared to directly fitting entire rim profiles to model predictions.
-We also note that although Figure~\ref{fig:rims} plots model profiles for
-$\mu = 1$ only, the best-fit FWHM-energy curves show that model profiles for
-$\mu \neq 1$ give very similar FWHM-energy dependence.  This is borne out in
-our best fit parameters in Tables~\ref{tab:fits-loss} and \ref{tab:fits-damp}.
+Fitting to multiple FWHM measurements should be robust to these effects as
+compared to directly fitting entire rim profiles to model predictions.
+Although Figure~\ref{fig:rims} plots model profiles for $\mu = 1$ only, the
+best-fit FWHM-energy curves show that model profiles for $\mu \neq 1$ give very
+similar FWHM-energy dependence.
 
@@
 \subsubsection{Effect of Tycho distance estimates on model fits}
-% TODO need to update for damping results!!!!!
-
-In our modeling we adopted a distance $d$ to Tycho of $3 \unit{kpc}$, but
-various estimates for Tycho's distance range between $2.3$--$4 \unit{kpc}$
-\citep{hayato2010}.  A larger remnant distance would increase both physical
-filament widths and shock velocity estimates from proper motion (as used in our
-models).
-
-% lad/ldiff scalings give eta/B0 scalings
-In the loss-limited model, we find roughly that $\eta_2 \propto d^2$ with
-$B_0$ approximately constant.  The advective lengthscale,
-equation~\eqref{eq:lad}, may be rearranged to obtain:
+
+Our models adopted a distance $d$ to Tycho of $3 \unit{kpc}$, but estimates for
+Tycho's distance range between $2.3$--$4 \unit{kpc}$ \citep{hayato2010}.  A
+larger remnant distance would increase both physical filament widths and shock
+velocity estimates from proper motion; we may then derive expected scalings for
+modeled $\eta_2$ and $B_0$ as functions of assumed distance $d$.  The advective
+lengthscale, equation~\eqref{eq:lad}, may be rearranged to obtain:
 \begin{align}
@@
 
-In practice, both advection and diffusion are important to our filament widths,
-but both scalings $\eta_2 \propto d^2$ and $B_0$ constant occur in model fits
-with varying distance.  When comparing full model fits with remnant distances
-of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from the idealized scaling
-is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for $\eta_2$.  As varying
-remnant distance $d$ leaves width-energy scaling $\mE$ invariant, the relative
-contributions of $l_{\mt{ad}}$ and $l_{\mt{diff}}$ should also be invariant.
-Then both lengthscales should scale simultaneously with $d$, yielding the
-observed behavior.
-
-% Damping and remnant distance
-In the damped model, a larger distance $d$ will require larger damping lengths
-from magnetic turbulence.  But, fitted values of $a_b$ will remain unchanged as
-we report $a_b$ in units of shock radius $r_s$.
+In practice, model fits with varying distance obey both scalings $\eta_2
+\propto d^2$ and $B_0$ constant.  When comparing full model fits with remnant
+distances of $3 \unit{kpc}$ and $4 \unit{kpc}$, the deviation from the
+idealized scaling is $\lesssim 1 \%$ for $B_0$ and $\abt 1$--$5\%$ for
+$\eta_2$.  As varying remnant distance $d$ leaves width-energy scaling $\mE$
+invariant, the relative contributions of $l_{\mt{ad}}$ and $l_{\mt{diff}}$
+should also be invariant.  Then both lengthscales should scale simultaneously
+with $d$, yielding the observed behavior.  In the damped model, a larger
+distance $d$ will require larger physical damping lengths from magnetic
+turbulence.  But, fitted values of $a_b$ should remain unchanged as we report
+$a_b$ in units of shock radius $r_s$.
 
@@
 
-Nevertheless, our conclusion that thin radio rims require magnetic damping
-should be robust and independent of model assumptions.
-\citet{cassam-chenai2007}, for example, observed the same dichotomy in radio
-emission for constant and damped magnetic fields in modeled profiles of Tycho's
-shock from a self-similar hydrodynamic model with diffusive shock acceleration.
-Our model captures the essential physics for a very young remnant such as
-Tycho, for which the forward shock should be adiabatic.
+Nevertheless, our conclusion that thin radio rims require magnetic damping is
+supported by more sophisticated modeling.  Hydrodynamic models with diffusive
+shock acceleration \citep{cassam-chenai2007, slane2014} also cannot produce
+radio profiles with narrow rims in a purely advected magnetic field.
+\citet{cassam-chenai2007} produced radio rims using a damped magnetic field,
+though they could not simultaneously reconcile predicted X-ray and radio
+intensities to observations.  Our model captures the essential physics for a
+very young remnant such as Tycho, for which the forward shock should be
+adiabatic.
 
@@
 The exponential variation in $D(x)$ (equation~\eqref{eq:ddamp}) may not be
-physically reasonable; as we have noted above, the assumption $D(x)
+physically reasonable; as noted above, the assumption $D(x)
 \propto 1 / B^2(x)$ gives rise to sharp gradients in diffusion coefficient and
@@
 
-% TODO question: we have been ignoring intensity.  What if, e.g.,
-% with strong diffusion particles get out of the damping zone faster and don't
-% even have a chance to radiate, or something like that?
+% TODO question: we have been ignoring intensity (absolute comparison).  What
+% if, e.g., with strong diffusion particles get out of the damping zone faster
+% and don't even have a chance to radiate?
 % I have no clue... check this, double check Sean's normalizations to be safe

### 2014-12-17 code/models/models.py

@@ -729,12 +729,13 @@ def width_cont(params, kevs, snr, verbose=True, rminarc=None, icut=None,
     if irad_adapt:
         iradmax_prelim = int(iradmax / 2.)  # Just a rough calculation
 
-        fwhms_prelim = fmp.fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s,
-                                   rminarc, icut, irmax, iradmax_prelim, ixmax,
-                                   idamp, damp_ab, damp_bmin, fgfname,
-                                   itmax, inmax, irhomax,
-                                   False, False,  # get_prfs / get_data
-                                   True)  # get_fwhms
+        out_prelim = fmp.fefflen(kevs, B0, eta2, mu, vs, v0, rs, rsarc, s,
+                                 rminarc, icut, irmax, iradmax_prelim, ixmax,
+                                 idamp, damp_ab, damp_bmin, fgfname,
+                                 itmax, inmax, irhomax,
+                                 False, False,  # get_prfs / get_data
+                                 True)  # get_fwhms
+        fwhms_prelim = out_prelim[0]
 
         # Replace error-code values
         res_msk, box_msk = _check_calc_errs(fwhms_prelim, rminarc)

### 2014-12-20 manuscript/paper-tycho.tex
Telecon notes; Bmin=0, l_ad/l_diff/etc plots
Add notes/todos from telecon; add cells/scripts addressing todos
Fit data with Bmin=0, compute/compare relevant lengthscales
Fix paper text; cut many tables/plots, update plots to eta2=1
Re-add srcutlog table to paper

@@
 resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
-(PI: J. Hughes) allows fine sampling of the remnant rims.  Furthermore, Tycho
+allows fine sampling of the remnant rims.  Furthermore, Tycho
 is a prime target of study to determine whether hadrons are being accelerated
@@
 We have assumed isotropic diffusion and consider only processes operating
-downstream of the shock.  More sophisticated treatments may explicitly treat
+downstream of the shock.  We also do not incorporate models for self-similar
+velocity and magnetic field evolution downstream of a spherical shock (e.g.,
+the well-known Sedov-Taylor solution).  A plane flow approximation should be
+reasonable as we only consider synchrotron emission within 10\% of the shock
+radius, $r_s$, from the forward shock.  % TODO CITATION AND REWORD.
+More sophisticated treatments may explicitly treat
 magnetic fields and diffusion across the shock, plasma streaming instabilities
-and particle losses, anisotropic diffusion, the DSA process and efficiency, and
-other details in great depth \citep[e.g.,][and references therein]{reville2013,
-bykov2014, ferrand2014}.
+and particle losses, anisotropic diffusion, injection/acceleration efficiency,
+and other details in great depth \citep[e.g.,][and references
+therein]{reville2013, bykov2014, ferrand2014}.
 
@@
 \end{equation}
-where $s$ is the line-of-sight coordinate.  Finally, we compute the full width
-at half maximum (FWHM) of the resulting intensity profile to compare to our
-measurements of rim width.
+where $s$ is the line-of-sight coordinate and $r_s$ is shock radius.  Finally,
+we compute the full width at half maximum (FWHM) of the resulting intensity
+profile to compare to our measurements of rim width.
 
@@
 \end{align}
+Here $B_0$ is the magnetic field immediately downstream of the shock, i.e.
+$B_0 = B(x=0)$.
 This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
@@
     l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
+% = \frac{v_d \sqrt{c_m}}{b} B_0^{-3/2} \nu^{-1/2}
 \end{equation}
@@
 \begin{equation} \label{eq:ldiff}
-    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
+    l_{\mt{diff}} = \sqrt{D \tsynch}
+                  \propto \eta^{1/2} B_0^{-(\mu+5)/4} \nu^{(\mu-1)/4}
+% = (C_d/b)^{1/2} c_m^{-(\mu-1)/4} \eta^{1/2} B_0^{-(\mu+5)/4} \nu^{(\mu-1)/4}
 \end{equation}
@@
 $\tsynch = 1 / (b B^2 E)$ with $b = 1.57 \times 10^{-3}$.
+For $\mu = 1$, note that $l_{\mt{diff}}$ is independent of $\nu$ and
+$l_{\mt{diff}} \propto B_0^{-3/2}$ matches the scaling of $l_{\mt{ad}}$.
 If both diffusion and magnetic field damping are negligible (whether at a small
@@
 \dataset[ADS/Sa.CXO\#obs/10093--10097]{ObsIDs: 10093--10097},
-\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}).
+\dataset[ADS/Sa.CXO\#obs/10902--10906]{10902--10906}); \citet{eriksen2011}
+present additional observation information.
 The total exposure time was $734 \unit{ks}$.
@@
     \caption{Best fit profiles with measured FWHMs demarcated for each energy
-        band in Region 1 (top) and Region 16 (bottom).  Energy bands increase
-        from left to right.  Data points in red were excluded from profile
-        fitting domains as described in text.}
+        band in Region 1 (top) and Region 16 (bottom).  Hereafter, we use
+        Regions 1 and 16 to illustrate results for profiles of differing
+        quality and absolute width.  We could not measure a $0.7$--$1
+        \unit{keV}$ FWHM in Region 1, reflected in Table~\ref{tab:fwhms}.  Data
+        in red were excluded from profile fit domains as described in text.}
     \label{fig:profiles}
@@
 typical intergalactic values of $\abt 2$--$3 \muG$ \citep{lyne1989, han2006}.
-We fixed $a_b$ at $14$ different values between $0.5$ and $0.002$ (sampling
+We stepped $a_b$ through $14$ different values between $0.5$ and $0.002$ (sampling
 most finely between $0.01$ and $0.002$) and ran fits with $\eta_2$ and $B_0$
-free.  Formally, we do not seek a best fit value of damping length $a_b$, so
-our ``best'' damping fits report the value of $a_b$ yielding the smallest
-$\chi^2$ value.  Finally, $\mu = 1$ was fixed for all damped fits.
+free.  For best fits, we report the value of $a_b$ yielding the smallest
+$\chi^2$ value, noting that our $a_b$ sampling is coarse.
 
@@
 \unit{mG}$ to be effectively unconstrained. % Change this if needed.
+% TODO "best-fit" vs. "best fit"... argh
 
@@
 
+% TODO we must restructure this text, since we are now not emphasizing Regions
+% 1/16 alone quite as much.  Just synthesize all together, use fig:fits to
+% explain that mu dependence is very weak.
+
+% TODO we could rewrite this all to say up front -- we work with eta2=1 unless
+% otherwise stated.  But that should wait until I review the new chain of
+% tables / figures w/ Rob and Brian.
+
 % Explain our approach
@@
 exemplified by Regions 1 and 16.  Best fit results for all regions are
-summarized in Figure~\ref{fig:fits-all} and Tables~\ref{tab:fits-all},
-\ref{tab:fits-all-eta2one}.  In all tables, we report values of $\chi^2$ rather
+summarized in Figure~\ref{fig:fits-all} and Table~\ref{tab:fits-all-eta2one}.
+In all tables, we report values of $\chi^2$ rather
 than $\chi^2_\mt{red}$ to ease comparison of different fits, as we often
@@
 % Explain a bit about model shapes, and the relative similarity in shapes
-Modeled profiles with best fit FWHMs for Regions 1 and 16 are plotted in
-Figure~\ref{fig:rims}, and their derived best-fit FWHM-energy curves
-are plotted in Figure~\ref{fig:fits} alongside measured FWHMs.
-The best fit model profiles do not quite match measured rim profiles
-(Figure~\ref{fig:profiles}).  Our transport equation does not account for
+The best-fit FWHM-energy curves for Regions 1 and 16 are plotted in
+Figure~\ref{fig:fits} alongside measured FWHMs.
+Our transport equation does not account for
 diffusive transport upstream of the shock, projection effects from shock
@@
 compared to directly fitting entire rim profiles to model predictions.
-Although Figure~\ref{fig:rims} plots model profiles for $\mu = 1$ only, the
-best-fit FWHM-energy curves show that model profiles for $\mu \neq 1$ give very
-similar FWHM-energy dependence.
-
-\begin{figure}
-    \centering
-    \iftoggle{manuscript}{
-        \epsscale{0.7}
-        \plotone{figures/prfs-fit-01.pdf} \\
-        \plotone{figures/prfs-fit-16.pdf}
-        \epsscale{1}
-    }{
-        \plotone{figures/prfs-fit-01.pdf} \\
-        \plotone{figures/prfs-fit-16.pdf}
-    }
-    \caption{Best fit full model rim profile width predictions for Regions 1
-        (top) and 16 (bottom) for loss-limited and damped scenarios with
-        $\mu = 1$ fixed; profiles are normalized to intensity $1$.  Model
-        parameters are given in Table~\ref{tab:fits-all}.  Shaded regions on
-        damped profiles indicate the magnetic field damping lengthscale $a_b$.
-        \label{fig:rims}}
-\end{figure}
 
@@
     \iftoggle{manuscript}{
-        \includegraphics[width=0.46\textwidth]{figures/energywidth-01.pdf}
-        \includegraphics[width=0.46\textwidth]{figures/energywidth-16.pdf}
+        \includegraphics[width=0.46\textwidth]{figures/energywidth-eta2one-01.pdf}
+        \includegraphics[width=0.46\textwidth]{figures/energywidth-eta2one-16.pdf}
     }{
-        \includegraphics[width=0.23\textwidth]{figures/energywidth-01.pdf}
-        \includegraphics[width=0.23\textwidth]{figures/energywidth-16.pdf}
+        \includegraphics[width=0.23\textwidth]{figures/energywidth-eta2one-01.pdf}
+        \includegraphics[width=0.23\textwidth]{figures/energywidth-eta2one-16.pdf}
     }
-    \caption{Loss-limited rim width predictions as a function of energy for
+    \caption{Best fit rim width-energy predictions for
     Regions 1 (top) and 16 (bottom), with measured data.  Dotted/dashed curves
     plot pure loss-limited fits with varying $\mu$, solid curve plots estimated
-    best moderately damped fit ($a_b < 0.01$) with $\mu = 1$.  Relevant fit
-    parameters are given in Tables~\ref{tab:fits-loss} and \ref{tab:fits-damp}.
+    best moderately damped fit ($a_b < 0.01$) with $\mu = 1$.  All fits hold
+    $\eta_2 = 1$ fixed; model parameters are given in
+    Tables~\ref{tab:fits-all-eta2one}.
     Note that ordinate FWHM axes are not the same and are offset from the
@@
     \caption{Rim width predictions for loss-limited and damped fits with
-    $\mu = 1$ fixed for all regions.  Neither loss-limited nor damped fits
+    $\mu = 1$ and $\eta_2=1$ fixed for all regions.  Neither loss-limited nor
+    damped fits
     are clearly favored in describing the data.  Some damped model predictions
@@
     half-maximum of rim peak within model domain of $\abt 20\arcsec$).
-    Corresponding best fit parameters are given in Table~\ref{tab:fits-all}.
+    Corresponding best fit parameters are given in
+    Table~\ref{tab:fits-all-eta2one}.
     As in Figure~\ref{fig:fits}, $y$-axis limits vary and are offset from the
@@
 
-% Fit results for ALL regions, mu = 1, loss-limited and damped
+% Fit results for ALL regions, mu = 1, eta2 free, loss-limited and damped
 % NOTE keep # of dofs updated
-\begin{table}
-    \iftoggle{manuscript}{
-        \scriptsize
-    }{
-        \tiny
-    }
-    \centering
-    \caption{Best model fits for all regions, $\mu = 1$
-    \label{tab:fits-all}}
-    \input{tab-fits-all.tex}
-    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
-    best damped fits select best $a_b$ value below $0.01$ from the range shown
-    in Table~\ref{tab:fits-damp}, enforcing moderate damping.  Fits for Regions
-    1, 2, 12, 18 have 2 dofs; all others have 3.  The manual selection of a
-    best $a_b$ value may be construed as removing one more dof.}
-    % NOTE UPDATE AS FWHMS UPDATED
-\end{table}
-
-In Table~\ref{tab:fits-all-eta2one} we also present best loss-limited and
+%\begin{table}
+%    \iftoggle{manuscript}{
+%        \scriptsize
+%    }{
+%        \tiny
+%    }
+%    \centering
+%    \caption{Best model fits for all regions, $\mu = 1$
+%    \label{tab:fits-all}}
+%    \input{tab-fits-all.tex}
+%    \tablecomments{Loss-limited fits fix $\mu=1$ to match the damping model;
+%    best damped fits select best $a_b$ value below $0.01$ from the range shown
+%    in Table~\ref{tab:fits-damp}, enforcing moderate damping.  Fits for Regions
+%    1, 2, 12, 18 have 2 dofs; all others have 3.  The manual selection of a
+%    best $a_b$ value may be construed as removing one more dof.}
+%    % NOTE UPDATE AS FWHMS UPDATED
+%\end{table}
+
+In Table~\ref{tab:fits-all-eta2one} we present best loss-limited and
 damped fits with $\eta_2 = 1$ fixed.  As before, both loss-limited and damped
@@
     \input{tab-fits-all-eta2one.tex}
-    \tablecomments{See comments on Table~\ref{tab:fits-all}.  Fits have
-    one additional dof as $\eta_2 = 1$ is fixed.}
+    \tablecomments{Best damped fits select best $a_b$ value below $0.01$ from
+    the range shown in Table~\ref{tab:fits-damp}, enforcing moderate damping.
+    Fits for Regions 1--3, 5, 11, 12, 18, and 19 have 3 degrees of freedom; all
+    others have 4.  The manual selection of a best $a_b$ value may be construed
+    as removing one additional dof.}
+\end{table}
+
+% TODO EXPLAIN/DISCUSS
+
+% As above but with eta2=1 fixed!
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Best model fits with $\Bmin = 0$ and $\mu = \eta_2 = 1$
+    \label{tab:fits-all-bminzero}}
+
+    \begin{tabular}{@{} l rr rrr @{}}
+    \toprule
+    {} & \multicolumn{2}{c}{Loss-limited}
+       & \multicolumn{3}{c}{Damped, $a_b \leq 0.01$} \\
+    \cmidrule(lr){2-3} \cmidrule(l){4-6}
+    Region & $B_0$ ($\mu$G) & $\chi^2$
+           & $B_0$ ($\mu$G) & $\chi^2$ & $a_b$ \\
+    \midrule
+    1 & 183 & 35.63 & 2.43 & 629.61 & 0.010 \\
+    2 & 313 & 80.81 & 239 & 100.66 & 0.010 \\
+    3 & 427 & 21.48 & 405 & 21.70 & 0.010 \\
+    \cmidrule{1-6}
+    4 & 285 & 51.30 & 174 & 43.82 & 0.010 \\
+    5 & 289 & 19.30 & 196 & 37.33 & 0.010 \\
+    6 & 411 & 174.32 & 90.2 & 61.50 & 0.005 \\
+    7 & 419 & 51.30 & 277 & 11.13 & 0.006 \\
+    8 & 388 & 48.06 & 205 & 9.92 & 0.006 \\
+    9 & 415 & 65.45 & 143 & 14.01 & 0.005 \\
+    10 & 466 & 17.28 & 307 & 1.60 & 0.005 \\
+    \cmidrule{1-6}
+    11 & 356 & 11.95 & 313 & 16.08 & 0.010 \\
+    12 & 318 & 9.60 & 258 & 15.45 & 0.010 \\
+    13 & 400 & 53.11 & 240 & 10.00 & 0.006 \\
+    \cmidrule{1-6}
+    14 & 384 & 103.43 & 52.3 & 9.90 & 0.005 \\
+    15 & 432 & 70.66 & 255 & 20.18 & 0.005 \\
+    16 & 493 & 15.13 & 430 & 3.88 & 0.006 \\
+    17 & 468 & 61.84 & 194 & 29.05 & 0.004 \\
+    \cmidrule{1-6}
+    18 & 283 & 27.87 & 206 & 71.82 & 0.010 \\
+    19 & 401 & 37.07 & 144 & 8.14 & 0.005 \\
+    20 & 464 & 122.00 & 140 & 94.37 & 0.004 \\
+    \bottomrule
+    \end{tabular}
+
+    \tablecomments{See comments for Table~\ref{tab:fits-all-eta2one}.}
 \end{table}
@@
 dependence at higher energies.  The photon energy at which $l_{\mt{ad}} =
-l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy.
+l_{\mt{diff}}$ is exactly the DSA-predicted synchrotron cut-off energy,
+$\abt0.3 \unit{keV}$ for Tycho \citep{hwang2002}.
 % TODO citation if you can find it...
@@
 cause rim widths to narrow counterintuitively.  Speculatively, spatial
-variation of the diffusion coefficient, which gives rise to a
-term $(\ptl D(x) / \ptl x) (\ptl f/\ptl x)$ in equation~\eqref{eq:model}, may
-oppose downstream advection by decreasing an effective velocity $v_d - \ptl
-D(x) / \ptl x$ and thus require thinner rims as $\eta_2$ and $\ptl D(x) / \ptl
-x$ increase.
+variation of the diffusion coefficient, which gives rise to a term $(\ptl D(x)
+/ \ptl x) (\ptl f/\ptl x)$ in equation~\eqref{eq:model}, may oppose downstream
+advection by imposing an effective velocity:
+\begin{equation}
+    v_d - \frac{\ptl D(x)}{\ptl x}
+\end{equation}
+thus requiring thinner rims as $\eta_2$ and $\ptl D(x) / \ptl x$ increase.
 
@@
 
+% TODO broadly, this section must be restructured to emphasize
+% that our division is VERY arbitrary.  I do NOT want the fit results to be
+% construed as physically meaningful.
+
+% The most useful result is just to explain -- damping plausibly works.
+
 % Explain the dichotomy in energy dependence
@@
 shock, the magnetic field asymptotically approaches $B_{\mt{min}} = 5 \muG$ and
-observed emission is controlled by synchrotron losses acting differentially on
+emission is controlled by synchrotron losses acting differentially on
 the range of electron energies we consider.  Synchrotron radiation sieves out
@@
 rise to energy dependent emission.  Each case is shown in
-Figure~\ref{fig:rims}; in Region 1 the damping profiles are quite distinct from
-the loss-limited profiles, whereas in Region 16 they appear quite similar; note
-that emission downstream of the shock Region 1's best damped fit is quite close
-to the intensity half-maximum.
+Figure~\ref{fig:rims}; in Region 1 the damping profiles evolve noticeably as
+compared to Region 16, with decreasing energy.
 
@@
     \iftoggle{manuscript}{
-        \includegraphics[width=0.48\textwidth]{figures/mE-damp.pdf}
+        \epsscale{0.7}
+        \plotone{figures/prfs-fit-damp-01.pdf} \\
+        \plotone{figures/prfs-fit-damp-16.pdf}
+        \epsscale{1}
     }{
-        \plotone{figures/mE-damp.pdf}
+        \plotone{figures/prfs-fit-damp-01.pdf} \\
+        \plotone{figures/prfs-fit-damp-16.pdf}
     }
-    \caption{Curves of $\mE$ values for best damping fits for all regions.
-        Note the sharp contrast between curves with roughly constant $\mE$ near
-        $0$ and curves with sharp drop-offs in $\mE$ (FWHMs increasing rapidly)
-        at low energies. Corresponding best fit parameters are given in
-        Table~\ref{tab:fits-all}. \label{fig:mE}}
+    \caption{Model predictions illustrate weak-field (Region 1) and
+        strong-field damping (Region 16) for damped best fit parameters with
+        $\mu=1$ and $\eta_2=1$ fixed.  In X-ray energies ($0.7$--$4.5
+        \unit{keV}$) model profiles are not strongly energy dependent, but
+        weak-field damping profiles evolve and do not show a measurable FWHM at
+        sufficiently low energies.
+        Profiles are normalized to peak thin rim intensity.  Model parameters
+        are given in Table~\ref{tab:fits-all-eta2one}.  Shaded regions on damped
+        profiles indicate damping lengthscale $a_b$.
+        \label{fig:rims}}
 \end{figure}
 
+% TODO discuss mE here for weak-field damping, even though we don't plot it
+% anymore.
+
 % Weak-field damping
-To further distinguish between these cases, Figure~\ref{fig:mE} plots predicted
-$\mE$ values from the best damped fits of Table~\ref{tab:fits-all},
-extrapolated to lower photon energies.  Several best fits predict increasingly
-large FWHMs at lower energies ($0.1$--$1 \unit{keV}$), cutting off at low
-energies when a FWHM is no longer measurable; this corresponds to a sharp
-drop in $\mE$ (already negative) at low energies These curves correspond to
-fits for Regions 1--5, 10--12, 15, and 18, which were all best fit by a
-damping model with fields $B_0 < 40 \muG$.  We refer to such model behavior as
+To discriminate, we observe that the best damped fit parameters for Regions
+1, 2, 4, 5, 10, 12, and 18 all predict a $1.375 \unit{GHz}$ radio emission
+profile with no measurable FWHM, whereas all other regions predict a measurable
+rim.  Moreover, these regions are all best fit with field $B_0 < 40 \muG$.
+We refer to this model behavior as
 ``weak-field'' damping, associated with weak magnetic fields and stronger
@@
 % Strong-field damping
-The near constant curves in Figure~\ref{fig:mE} trend towards $\mE = 0$ at low
-energy, indicating that predicted rim widths are strongly energy independent.
-At higher energy, rims become energy dependent ($\mE \sim -0.2$) to match the
-observed width-energy dependence in X-rays.  The gradual increase in $|\mE|$
-with energy is expected in the damping model as advection and/or diffusion take
+All other regions predict consistently thin rims with measurable thin rims at
+decreasing energy.  The width-energy dependence parameterized by $\mE$ trends
+towards zero at low energy, indicating that rim widths are comparatively energy
+independent.
+At higher energy, rims become moderately energy dependent ($\mE \sim -0.2$) to
+match the observed width-energy dependence in X-rays.  The gradual increase in
+$|\mE|$ with energy is expected in the damping model as advection and/or
+diffusion take
 control of rim widths at increasing energy, as discussed in
@@
 be physically meaningful given the large $\chi^2$ values on our model fits.
-Several regions are well-fit by ``weak-field'' and ``strong-field'' damping
-alike (e.g., Region 3 in Tables~\ref{tab:fits-all},\ref{tab:fits-all-eta2one}).
+Several regions may be well-fit by ``weak-field'' and ``strong-field'' damping
+alike.
 However, ``weak-field'' damping is often associated with data best fit with
@@
 
-% -------------------------------
-% srcutlog and spectral variation
-% -------------------------------
-\subsection{Spectral constraints on model fits}
-
-\subsubsection{Synchrotron cut-off measurements}
+% TODO Where does this go, where should we integrate this discussion about
+% profile shape w.r.t. width-energy dep. fitting?
+
+% TODO WRITE THIS CAPTION
+
+\begin{figure*}%[ht]
+    \plotone{figures/pargrid-eta2_1-model.pdf}
+    \caption{A grid of best fit parameters, yay!  WRITE THIS CAPTION.}
+    \label{fig:pargrid}
+\end{figure*}
+
+% --------
+% srcutlog
+% --------
+\subsection{Synchrotron cut-off constrains diffusion}
 
@@
 \citep{sun2011} as done in our profile modeling and fit for column density
-$N_{\mt{H}}$ and cut-off frequency $\nu_{\mt{cut}}$ in each region.  The
-fitted cut-off frequency is typically $0.3 \unit{keV/h}$, consistent with fits
-by \citet{hwang2002}, but Regions 11, 12 have unusually high cut-off
-frequencies $0.55$, $0.88 \unit{keV/h}$ consistent with harder rim spectra
-(Table~\ref{tab:spec}).
+$N_{\mt{H}}$ and cut-off frequency $\nu_{\mt{cut}}$ in each region.
+Table~\ref{tab:fits-srcutlog} lists best spectrum fit parameters for each
+region.  The fitted cut-off frequency is typically $0.3 \unit{keV/h}$,
+consistent with fits by \citet{hwang2002}, but Regions 11, 12 have unusually
+high cut-off frequencies $0.55$, $0.88 \unit{keV/h}$ consistent with harder rim
+spectra (Table~\ref{tab:spec}).
 
@@
 hence $\eta_2$ ($4$--$15$), we computed new loss-limited fits for all regions
-with cut-off derived values of $\eta_2$ fixed.  Fitted $B_0$ values span
-$250$--$700 \muG$.  Variation in $\mu$ has a smaller effect on best fits as we
-are able to derive different $\eta_2$ values as a function of $\mu$; Regions 1
-and 16 have best fit values of $B_0$ increasing over $252$--$266 \muG$ and
-$660$--$700 \muG$ respectively as $\mu$ ranges between $0$--$2$.  Our fits with
-cut-off derived values of $\eta_2$ are comparable to fits with $\eta_2 = 1$
-fixed (Table~\ref{tab:fits-all-eta2one}).  We are unable to deduce any insights
-from requiring that $\eta_2$ reflects measurements of $\nu_{\mt{cut}}$.  But,
-diffusion coefficients computed in this manner may give more credible derived
-estimates of $B_0$ if the DSA assumptions invoked are relevant.
-
-\subsubsection{Spectral softening}
+with cut-off derived values of $\eta_2$ fixed (Table~\ref{tab:fits-srcutlog}).
+Fitted $B_0$ values span $250$--$700 \muG$.  Variation in $\mu$ has a smaller
+effect on best fits as we are able to derive different $\eta_2$ values as a
+function of $\mu$; Regions 1 and 16 have best fit values of $B_0$ increasing
+over $252$--$266 \muG$ and $660$--$700 \muG$ respectively as $\mu$ ranges
+between $0$--$2$.  Our fits with cut-off derived values of $\eta_2$ are
+comparable to fits with $\eta_2 = 1$ fixed (Table~\ref{tab:fits-all-eta2one}).
+We are unable to deduce any insights from requiring that $\eta_2$ reflects
+measurements of $\nu_{\mt{cut}}$.  But, diffusion coefficients computed in this
+manner may give more credible derived estimates of $B_0$ if the DSA assumptions
+invoked are relevant.
+
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Synchrotron roll-off, $\eta_2$, and fits for $\mu = 1$
+    \label{tab:fits-srcutlog}}
+    \input{tab-srcutlog.tex}
+    \tablecomments{\texttt{srcut} fits performed in log-frequency coordinates;
+        here $h$ is Planck's constant. $\eta_2$ values are computed from
+        equation~\eqref{eq:cutoff} and held fixed in model fits.}
+\end{table}
+
+% ---------------------------
+% Spectral variation analysis
+% ---------------------------
+\subsection{Spectral softening and model fits}
 % Wording of spectral index changes/variation is inconsistent and unwieldy
@@
 $0.05$ (stdev: $0.0005$) for loss-limited model profiles and $0.05$ (stdev:
-$0.02$) for damped model profiles.  For comparison, damped fits with varying
-$\eta_2$ (Table~\ref{tab:fits-all}) yield a mean $\Delta\Gamma$ of $0.07$
-(stdev: $0.03$).  Modeled spectral variation in all cases is inconsistent with
-the observed $\Delta\Gamma \sim 0.2$--$0.3$.
+$0.02$) for damped model profiles.  Modeled spectral variation in all cases is
+inconsistent with the observed $\Delta\Gamma \sim 0.2$--$0.3$.
 Our damped model results disagree with those of \citet[][Fig.~4]{rettig2012},
@@
 \citet{reynoso1997} for a detailed presentation.
+% TODO update
 \note[Aaron]{Q for Steve: Was data from all configurations merged?  Done by
@@
 
+% Procedure: cont
 The radio and X-ray profile modeling here contrasts strongly with our previous
@@
     ranges) required to reproduce radio and X-ray rims simultaneously in our
-    model.  Black solid curves in all regions plot our manually chosen best
+    model.  \emph{Solid black curves} in all regions plot our manually chosen best
     model profiles.  Profiles are chosen to show varying radio rim morphology,
@@
 (Figure~\ref{fig:radio-prfs-meh}).  The damping length $a_b$ ranges between
-$0.01$--$0.03$, or $2$--$7\arcsec$.  The radio plateaus in regions B, C, D are
-compatible with damping lengths between $0.01$--$0.05$.  Continuous rises in
-radio emission are best modeled with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300
-\muG$.  Although damping lengths $a_b \gtrsim 0.1$ may not be physically
-meaningful, such large values of $a_b$ yield practically constant magnetic
-field behind the shock regardless.
+$0.01$--$0.03$, or $2$--$7\arcsec$.
+
+% TODO discuss how changing a_b / B_0 affect radio/X-ray rims, qualitatively
+
+The radio plateaus in regions B, C, D are compatible with damping lengths
+between $0.01$--$0.05$.  Continuous rises in radio emission are best modeled
+with $a_b \gtrsim 0.1$ and $B_0 \abt 200$--$300 \muG$.  Although damping
+lengths $a_b \gtrsim 0.1$ may not be physically meaningful, such large values
+of $a_b$ yield practically constant magnetic field behind the shock regardless.
 Our results are also insensitive to the assumed value of $\Bmin$; only model

### 2014-12-20 code/models/models_disp.py

@@ -206,6 +206,8 @@ def save_fits(p_list, fobj, mu_vals, outroot):
     Use the pkl though, seriously.
     The json is just a backup, for when Python/pickle/etc are obsolute
 
+    This DOES clobber any existing output!
+
     please see build_dataf for info on stored data!
 
     Input:
@@ -300,7 +302,6 @@ def load_fit_pkls_new(inroot):
         p_list, mu_vals, fobj = load_fit_pkl(inroot, n+1)
         yield p_list, mu_vals, fobj, n+1
 
-
 def load_fit_pkl(inroot, n):
     """Get best fit information/usables from specified fit pickle
 
@@ -329,8 +330,8 @@ def load_fit_pkl(inroot, n):
     fobj = mex.Fitter(p0.snr, fdict['kevs'], fdict['data'], fdict['eps'],
                       None,  # No table needed
                       inds=None, verbose=True)
+    fobj.title = fdict['title']
     return p_list, mu_vals, fobj
-
 
 def best_fit_fwhms(p_list, mu_vals, fobj, kevs_calc=None, mu_calc=None,
                    get_mask=False, verbose=True, **kwargs):

### 2014-12-23 manuscript/paper-tycho.tex
Finish telecon todos, update ms tables/plots
Address remaining telecon issues, minor ipynb refactoring.
Spectral variation, eyeball fits compared to width-energy.
Tables for eyeball fits, damped srcutlog fits.
New manuscript fig/table layout. Discard old figs/tables.
Add CASA tutorial notes/etc from Nov 2014.

@@
 Here $B_0$ is the magnetic field immediately downstream of the shock, i.e.
-$B_0 = B(x=0)$.
+$B_0 = B(x=0)$; our notation departs somewhat from typical notation in denoting
+downstream field by $B_0$.
 This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
@@
 
+% TODO discuss srcutlog fitting (move text up from below)
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Synchrotron roll-off, $\eta_2$, and fits for $\mu = 1$
+    \label{tab:spec-srcutlog}}
+    \input{tab-srcutlog.tex}
+    \tablecomments{\texttt{srcut} fits performed in log-frequency coordinates;
+        here $h$ is Planck's constant. $\eta_2$ values are computed from
+        equation~\eqref{eq:cutoff} and held fixed in model fits.}
+\end{table}
+
 % Takeaway -- we are good to go
@@
 
+% TODO cull/rewrite all references to tab:fits-loss, tab:fits-damp
+% Since tables are removed, adjust discussion of eta2, mu effects on fits.
+% and effects of varying ab value?
+
 % Observations on qualitative trends in fit parameters
@@
 % Example loss-limited fits
-\begin{table}
-    \scriptsize
-    \centering
-    \caption{Loss-limited fits for Regions 1, 16
-    \label{tab:fits-loss}}
-    \input{tab-fits-loss.tex}
-    \tablecomments{Model fits computed at several fixed values of $\mu$ with
-    $\eta_2$, $B_0$ free and constant magnetic field $B(x) = B_0$.
-    Region 1 has 2 degrees of freedom (dofs); Region 16, 3.}
-\end{table}
-
-% Example damping fits
-\begin{table}
-    \scriptsize
-    \centering
-    \caption{Magnetic damping fits for Regions 1, 16
-    \label{tab:fits-damp}}
-    \input{tab-fits-damp.tex}
-    \tablecomments{Model fits computed at several fixed values of $a_b$ with
-    $\eta_2$, $B_0$ free and damped magnetic field (equation~\eqref{eq:bdamp}).
-    Fit degrees of freedom are as in Table~\ref{tab:fits-loss}}
-\end{table}
+%\begin{table}
+%    \scriptsize
+%    \centering
+%    \caption{Loss-limited fits for Regions 1, 16
+%    \label{tab:fits-loss}}
+%    \input{tab-fits-loss.tex}
+%    \tablecomments{Model fits computed at several fixed values of $\mu$ with
+%    $\eta_2$, $B_0$ free and constant magnetic field $B(x) = B_0$.
+%    Region 1 has 2 degrees of freedom (dofs); Region 16, 3.}
+%\end{table}
+%
+%% Example damping fits
+%\begin{table}
+%    \scriptsize
+%    \centering
+%    \caption{Magnetic damping fits for Regions 1, 16
+%    \label{tab:fits-damp}}
+%    \input{tab-fits-damp.tex}
+%    \tablecomments{Model fits computed at several fixed values of $a_b$ with
+%    $\eta_2$, $B_0$ free and damped magnetic field (equation~\eqref{eq:bdamp}).
+%    Fit degrees of freedom are as in Table~\ref{tab:fits-loss}}
+%\end{table}
 
@@
 
-% As above but with eta2=1 fixed!
 \begin{table}
@@
     \input{tab-fits-all-eta2one.tex}
-    \tablecomments{Best damped fits select best $a_b$ value below $0.01$ from
-    the range shown in Table~\ref{tab:fits-damp}, enforcing moderate damping.
-    Fits for Regions 1--3, 5, 11, 12, 18, and 19 have 3 degrees of freedom; all
-    others have 4.  The manual selection of a best $a_b$ value may be construed
-    as removing one additional dof.}
+    \tablecomments{Fits for Regions 1--3, 5, 11, 12, 18, and 19 have 3 degrees
+    of freedom; all others have 4.  The choice of a best $a_b$ value may be
+    construed as removing one additional dof.}
 \end{table}
 
-% TODO EXPLAIN/DISCUSS
-
-% As above but with eta2=1 fixed!
+% Integrate srcutlog into textual discussion (!)
+
 \begin{table}
@@
     \centering
-    \caption{Best model fits with $\Bmin = 0$ and $\mu = \eta_2 = 1$
-    \label{tab:fits-all-bminzero}}
-
-    \begin{tabular}{@{} l rr rrr @{}}
-    \toprule
-    {} & \multicolumn{2}{c}{Loss-limited}
-       & \multicolumn{3}{c}{Damped, $a_b \leq 0.01$} \\
-    \cmidrule(lr){2-3} \cmidrule(l){4-6}
-    Region & $B_0$ ($\mu$G) & $\chi^2$
-           & $B_0$ ($\mu$G) & $\chi^2$ & $a_b$ \\
-    \midrule
-    1 & 183 & 35.63 & 2.43 & 629.61 & 0.010 \\
-    2 & 313 & 80.81 & 239 & 100.66 & 0.010 \\
-    3 & 427 & 21.48 & 405 & 21.70 & 0.010 \\
-    \cmidrule{1-6}
-    4 & 285 & 51.30 & 174 & 43.82 & 0.010 \\
-    5 & 289 & 19.30 & 196 & 37.33 & 0.010 \\
-    6 & 411 & 174.32 & 90.2 & 61.50 & 0.005 \\
-    7 & 419 & 51.30 & 277 & 11.13 & 0.006 \\
-    8 & 388 & 48.06 & 205 & 9.92 & 0.006 \\
-    9 & 415 & 65.45 & 143 & 14.01 & 0.005 \\
-    10 & 466 & 17.28 & 307 & 1.60 & 0.005 \\
-    \cmidrule{1-6}
-    11 & 356 & 11.95 & 313 & 16.08 & 0.010 \\
-    12 & 318 & 9.60 & 258 & 15.45 & 0.010 \\
-    13 & 400 & 53.11 & 240 & 10.00 & 0.006 \\
-    \cmidrule{1-6}
-    14 & 384 & 103.43 & 52.3 & 9.90 & 0.005 \\
-    15 & 432 & 70.66 & 255 & 20.18 & 0.005 \\
-    16 & 493 & 15.13 & 430 & 3.88 & 0.006 \\
-    17 & 468 & 61.84 & 194 & 29.05 & 0.004 \\
-    \cmidrule{1-6}
-    18 & 283 & 27.87 & 206 & 71.82 & 0.010 \\
-    19 & 401 & 37.07 & 144 & 8.14 & 0.005 \\
-    20 & 464 & 122.00 & 140 & 94.37 & 0.004 \\
-    \bottomrule
-    \end{tabular}
-
-    \tablecomments{See comments for Table~\ref{tab:fits-all-eta2one}.}
+    \caption{Best model fits for all regions, $\eta_2$ derived from
+        \texttt{srcut} fits
+    \label{tab:fits-all-srcutlog}}
+    \input{tab-fits-all-srcutlog.tex}
+    \tablecomments{$\eta_2$ values are computed from equation~\eqref{eq:cutoff}
+    and held fixed in model fits.  See comments for
+    Table~\ref{tab:fits-all-eta2one} as well.}
 \end{table}
@@
 thus requiring thinner rims as $\eta_2$ and $\ptl D(x) / \ptl x$ increase.
+
+% TODO discuss this a bit further.  Explain that it doesn't matter for us since
+% we are not exploring eta2 dependence of fits etc, but something useful to
+% note
 
@@
 
+\subsection{Lengthscale analysis}
+
+% TODO Short blurb
+
+\begin{figure}
+    \centering
+    \plotone{figures/lengthscales_fwhm.pdf} \\
+    \caption{Stuff
+        \label{fig:length}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \plotone{figures/lengthscales_fwhm_dimless.pdf} \\
+    \caption{Stuff.  Dashed line plots scaled FWHM = $4.6$, the projection
+        factor for a spherical shell (CITE)  % TODO
+        \label{fig:length-dimless}}
+\end{figure}
+
+\begin{table*}
+    \scriptsize
+    \centering
+    \caption{Lengthscale analysis
+        \label{tab:lengthscales}}
+    \input{tab-lengthscale.tex}
+    \tablecomments{All derived from fits with $\eta_2 = 1$ and such.  Ratio of
+        $l_{\mt{ad}}/l_{\mt{diff}}$ is same for loss-limited and damped fits
+    (see text).
+    All values computed at fiducial energy $2 \unit{keV}$.}
+\end{table*}
+
 % ----------------
@@
 
+% TODO move this up in discussion to EARLIER.
+
 Our model fits have not incorporated the synchrotron cut-off energy, which
@@
 $N_{\mt{H}}$ and cut-off frequency $\nu_{\mt{cut}}$ in each region.
-Table~\ref{tab:fits-srcutlog} lists best spectrum fit parameters for each
+Table~\ref{tab:fits-all-srcutlog} lists best spectrum fit parameters for each
 region.  The fitted cut-off frequency is typically $0.3 \unit{keV/h}$,
@@
 invoked are relevant.
-
-\begin{table}
-    \scriptsize
-    \centering
-    \caption{Synchrotron roll-off, $\eta_2$, and fits for $\mu = 1$
-    \label{tab:fits-srcutlog}}
-    \input{tab-srcutlog.tex}
-    \tablecomments{\texttt{srcut} fits performed in log-frequency coordinates;
-        here $h$ is Planck's constant. $\eta_2$ values are computed from
-        equation~\eqref{eq:cutoff} and held fixed in model fits.}
-\end{table}
 
@@
 
-% TODO We have NOT considered the relative intensities of X-ray / radio rims!
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Eyeballed fits
+        \label{tab:fits-eyeball}}
+    \input{tab-fits-eyeball.tex}
+    \tablecomments{$\infty$ indicates that we favor a loss-limited fit here
+    ($a_b > 10$\% of shock radius $r_s$)}
+\end{table}
 
@@
 
+% ======================================
+% Extra tables/fit information for Tycho
+% ======================================
+\section{Extra Tycho results}
+
+% TODO EXPLAIN/DISCUSS BMIN=ZERO INLINE (not here obviously)
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Best model fits with $\Bmin = 0$ and $\mu = \eta_2 = 1$}
+    \input{suppl-fits-all-bmin0-eta2one.tex}
+    \tablecomments{See comments for Table~\ref{tab:fits-all-eta2one}.}
+\end{table}
+
+% TODO EXPLAIN/DISCUSS ETA2 INLINE
+\begin{table}
+    \scriptsize
+    \centering
+    \caption{Best model fits with $\eta_2 = 10$ fixed}
+    \input{suppl-fits-all-eta2ten.tex}
+    \tablecomments{See comments for Table~\ref{tab:fits-all-eta2one}.}
+\end{table}
+
+% TODO EXPLAIN
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.5\textwidth]{figures/specvar-dgamma.pdf}
+    \caption{Spectral variation as a function of energy for damped best fit
+    parameters, w/ different choice of $\eta_2$.}
+\end{figure*}
+
 % ================================
@@
 % ================================
+\clearpage
 \section{Best fits, SN 1006}
@@
 
-\clearpage
-\begin{figure}
-    \centering
-    \iftoggle{manuscript}{
-        \includegraphics[width=0.48\textwidth]{figures/mE-damp-sn1006.pdf}
-    }{
-        \includegraphics[width=0.35\textwidth]{figures/mE-damp-sn1006.pdf}
-    }
-    \caption{Curves of $\mE$ values for best damping fits for all regions,
-        SN 1006}
-\end{figure}
-
 \begin{figure*}[h]
@@
 \end{figure*}
-
-% ========================================
-% Best Tycho fits with Bmin = 2 microGauss
-% ========================================
-
-%\clearpage
-%\section{Best fits, Tycho, with $\Bmin=2\muG$}
-%
-%\begin{table}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Best model fits for all regions, $\mu = 1$, $\Bmin=2\muG$}
-%    \input{suppl-fits-all-bmin2.tex}
-%\end{table}
-%
-%% As above but with eta2=1 fixed!
-%\begin{table}[ht]
-%    \scriptsize
-%    \centering
-%    \caption{Best model fits for all regions, $\mu = \eta_2 = 1$,
-%        $\Bmin=2\muG$}
-%    \input{suppl-fits-all-bmin2-eta2one.tex}
-%\end{table}
-%
-%% Only show these giant tables in 2col... no need to print these
-%\iftoggle{manuscript}{
-%}{
-%    % ===============================
-%    % Damping best fit sea of numbers
-%    % ===============================
-%    \clearpage
-%    \section{Magnetic damping best fit tables}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 1, $\mu = 1$}
-%        \input{suppl-fits-damp-f1.tex}
-%    \end{table*}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 2, $\mu = 1$}
-%        \input{suppl-fits-damp-f2.tex}
-%    \end{table*}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 2 (cont.), $\mu = 1$}
-%        \input{suppl-fits-damp-f2-pt2.tex}
-%    \end{table*}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 3, $\mu = 1$}
-%        \input{suppl-fits-damp-f3.tex}
-%    \end{table*}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 4, $\mu = 1$}
-%        \input{suppl-fits-damp-f4.tex}
-%    \end{table*}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to individual regions, Filament 5, $\mu = 1$}
-%        \input{suppl-fits-damp-f5.tex}
-%    \end{table*}
-%
-%    % ================================
-%    % Damping best fit tables, SN 1006
-%    % ================================
-%    \clearpage
-%    \section{Magnetic damping fit tables, SN 1006}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to SN1006 filaments, $\mu = 1$}
-%        \input{suppl-fits-damp-sn1006.tex}
-%    \end{table*}
-%
-%    \clearpage
-%    \section{Magnetic damping fit tables, SN 1006, no e- cutoff}
-%
-%    \begin{table*}[ht]
-%        \scriptsize
-%        \centering
-%        \caption{Damped fits to SN1006 filaments, $\mu = 1$, no e- cutoff}
-%        \input{suppl-fits-damp-nocut-sn1006.tex}
-%    \end{table*}
-%}
 

### 2014-12-23 code/models/models_disp.py

@@ -335,14 +335,13 @@ def load_fit_pkl(inroot, n):
 
 def best_fit_fwhms(p_list, mu_vals, fobj, kevs_calc=None, mu_calc=None,
                    get_mask=False, verbose=True, **kwargs):
-    """Compute model FWHMs from best fit pickle specified by inroot, n
-    n is indexed from 1 (!)
+    """Compute model FWHMs from parameter list, mu values, and Fitter() object
+    (obtained from best fit pickle methods)
 
     Input:
-        inroot (str): base file stem referring to files given by
-                          inroot + '-{:02d}-data.pkl'.format(n)
-                          inroot + '-{:02d}-fobj.pkl'.format(n)
-        n (int): region number for inroot
+        p_list: list of lmfit.Parameters() objects, one per mu in mu_vals
+        mu_vals: list of mu values fitted
+        fobj: models_exec.Fitter() object used for fits in p_list/mu_vals
         kevs_calc (list): energies (keV) at which to compute model FWHMs
                           if none specified, data keVs used
         mu_calc (list): mu values at which to get best fit parameters
